### 2018-04-18 Old/paper.tex
Moving PhD paper from Dropbox to github.

\documentclass[12pt]{article}

\usepackage[text={6in,8.1in},centering]{geometry}

\usepackage{enumerate}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathrsfs} % to use mathscr fonts

\usepackage{multicol}

\usepackage{epstopdf}
\usepackage{caption,subcaption}
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{algorithmicx,algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{verbatim,moreverb}
\usepackage{courier}

\lstset{ %
language=C++,               
basicstyle=\footnotesize,
numbers=left,                  
numberstyle=\tiny,     
stepnumber=1,         
numbersep=5pt,         
backgroundcolor=\color{white},  
showspaces=false,               
showstringspaces=false,         
showtabs=false,                 
columns=fullflexible,
frame=single,          
tabsize=2,          
captionpos=b,       
extendedchars=true,
xleftmargin=17pt,
framexleftmargin=17pt,
framexrightmargin=17pt,
framexbottommargin=4pt,
breaklines=true,       
breakatwhitespace=false, 
escapeinside={\%*}{*)}       
}

\newenvironment{block}{\begin{adjustwidth}{1.5cm}{1.5cm}\noindent}{\end{adjustwidth}}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\def\verbatimtabsize{4\relax}
\def\listingoffset{1em}
\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}

\newcommand{\vs}{\varsigma}

\headsep25pt\headheight20pt

\pagestyle{fancyplain}
\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
\cfoot{\ \hfill\tiny\sl Draft printed on \today}

\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables

\begin{document}
\begin{multicols}{2}

\section{Introduction}
China Mobile Hong Kong (CMHK) recently introduced such a secondary market.
CMHK’s 2cm (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data, with CMHK acting as a middleman both to match buyers
and sellers and to ensure that the sellers’ trading revenue and buyers’
purchased data are reflected on customers’ monthly bills. \cite{zheng}

In this work, we propose a distributed progressive second price (PSP) auction in
order to maximize social utility. We show that for cellular data allocated between multiple users there
exists a Nash market equilibria when all users bid their real marginal
valuation of the bandwidth resource. The P2P auction's (as in all auctions),
demand information is not known centrally, rather it is distributed in the
buyers' valuations. A basic goal is that the mechanism also be
\emph{distributed} in that the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the bids for that element only.

We suppose that each seller (resp. buyer) can submit a bid to the secondary
market consisting of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached where $\epsilon$ corresponds to a bid
fee to be paid to the ISP on completion of the transaction.

\subsection{Progressive Second Price Auctions}

The PSP auction first introduced in \cite{lazar} forms a part of the
overall market based allocation model. Consider a noncooperative game
where $I$ users buy the fixed amount of resource $D$ from one seller. Suppose
each user $i \in \mathcal{I}$ makes a bid $s = (p_i , d_i )$ to the seller,
where $p_i$ is the unit-price the user is willing to pay and $d_i$ is the
quantity the user desires. $s \equiv [s_i]_{i\in\mathcal{I}}$ is the bidding
profile and $s_{−i} \equiv [s_1 , \cdots , s_{i−1} , s_{i+1} , \cdots , s_N]$ is
the profile of user $i$’s opponents. The market price function (MPF) of user $i$ is defined as:
\begin{equation}
    P_i(z, s_i) = \inf\bigg\lbrace y\ge 0 : D - \displaystyle\sum_{p_k>y, k\ne i} d_k
\ge z \bigg\rbrace,
\end{equation}
which is interpreted as the minimum price a user bids in order to obtain the
resource $z$ given the opponents’ profile $s_−i$. Its inverse function $D_i$ is defined as follows:
\begin{equation}
    D_i(y, s_i) = \bigg\lbrack D - \displaystyle\sum_{p_k > y, k\ne i}
d_k\bigg\rbrack^+,
\end{equation}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}$. With this notation, the PSP allocation rule \cite{tuffin} is defined as
\begin{align}
    a_i(s) = \min\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k=p_i}d_k} D_i(p_i,
s_{-i})\big\rbrace, \\
    c_i(s) = \displaystyle\sum_{j\ne i} p_j \big[a_j(0; s_{-i}) -
a_j(s_i;s_{-i}\big],
\end{align}
where $a_i$ denotes the quantity user $i$ obtains by a bid price $p_i$ (when the
opponents bid $s_{−i}$) and the charge to user $i$ by the seller is denoted
$c_i$. $c_i$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.

We further modify the allocation rule in \cite{tuffin} in order to suit our
model. We argue that as there is no capacity bottleneck in our network as in
\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
take the maximum of the allocation rule. 
We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer maximizes its utility by placing bids with all sellers who are
able to fully meet their data requirements, similar to \cite{zheng}. 
We propose a \emph{data allocation rule},
{
\proposition{(Data allocation rule)}\label{allocation}
\begin{equation}
    a_i(s) = \max\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k=p_i}d_k}
D_i(p_i,s_{-i})\big\rbrace
\end{equation}
}
The modified allocation rule changes the market dynamics by adding a threshold
to buyer behavior; the strategy is now to submit bids to a subset of
players, rather than incuding an assumption that data infinitely divisibile.

(NOTE: move this?)
We extend the P2P rules as in \cite{semret} to include a \emph{local} market
price function as determined by the subset of nodes participating in the
auction. Therefore the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the $\epsilon$-best replies from the buyers. The
valuation function of seller $j$ is dependent on the buyers demand, and can be
modeled as a function of their potential revenue.

Absent the cost or revenue from trading data, users gain utility from consuming
data. We use the $\alpha$-fair utility functions \cite{tuffin} to model the
usage utility from consuming $d$ amount of data:
\begin{equation}
    \theta(d) = \frac{\sigma d^{1-\alpha}}{1-\alpha}
\end{equation}
where $\sigma$ is a positive constant representing (the scale) of the usage
utility and we take $\alpha \in [0, 1)$.
We verify that the user valuation above satisfies the conditions for an
\emph{elastic demand function}: (NOTE: this part seems in the wrong place)

\definition{\cite{lazar}}
A real valued function $\theta(\cdot)$ is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$; \\
        \emph{Verification:} (obvious)
    \item $\theta$ is differentiable; \\
        \emph{Verification:} The derivative, $\sigma d^{-\alpha}$, is positive assuming non-negative
data requirements.
    \item $\theta ' \ge 0$, and $\theta '$ is non-increasing and continuous; \\
        \emph{Verification:} $U$ is differentiable for all $d$, and therefore
continuous. Its derivative is a negative exponential, and so is non-increasing.
    \item There exists $\gamma > 0$, such that for all $z \in [0,D]$, $\theta
'(z) > 0$ implies that for all $\eta \in [0, z), \theta '(z) \le \theta '(\eta)
- \gamma(z - \eta)$. \\
        \emph{Verification:} Without loss of generality, we may set the scaling
constant $\sigma=1$, and compute the curvature $\gamma(\xi)$, where by definition,
$$
    \gamma = \frac{\theta''}{(1+\theta')^{3/2}} = \frac{-\alpha
\xi^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}.
$$
Using a Taylor theorem approximation,
\begin{align*}
    z^{-\alpha} &\le \eta^{-\alpha} + \frac{-\alpha
d^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}(z-\eta) \\
    & \le \eta^{-\alpha} +
\frac{\alpha}{2\sqrt{2} \xi}(z-\eta)  \\
    &\le \eta^{-\alpha} +
\frac{\alpha}{\xi}(z-\eta).
\end{align*}
Now, using Taylor repeatedly, simplifying and taking the limit as $\eta \rightarrow z$,
\begin{align*}
    z^{-\alpha} - \eta^{-\alpha} &\le -\alpha\eta^{-\alpha-1}(z-\eta) \\
    & \le \frac{-\alpha}{\xi}(z-\eta).
\end{align*}
And so, since $\xi \le \eta^{\alpha+1}$,
we may set
$$
    \gamma \ge
\frac{-\alpha\eta^{-(\alpha+1)^2}}{\big(1+(\eta^{-2\alpha(\alpha+1)})^{3/2}},
$$
which holds in the case that $z > 1$, and so assuming that there must be at least one
unit of data required for a user to have
a valuation,  we have that the concavity of $\theta'$ is shown by Squeeze theorem.
\end{itemize}

We may now define the user's utitlity function as
\begin{equation}\label{utility}
    u_i = \theta_i(a_i(s)) - c_i(s).
\end{equation}

Under the PSP rule, \cite{lazar} shows that given the opponents bids $s_{-i}$,
user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
(where $s_i$ is chosen to maximize $i$'s utility with $s_{-i}$ held constant), is
given by:
\begin{align}
\begin{split}
    v_i &= \sup\bigg\lbrace d \ge 0 : \theta '(d) > P_i(d), \\ 
&\displaystyle\int_0^d P_i(\eta) \ d\eta \le b_i\bigg\rbrace -
\frac{\epsilon}{\theta_i'(0)} \\
&\qquad\qquad \text{(best quantity reply)} \\
\end{split}\\
    w_i &= \theta_i'(v_i) \quad \text{(best unit-price reply)},
\end{align}
where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
has an elastic demand function.

In the Secondary Market \cite{zheng}, we intend to show that it is optimal for a
buyer to fully satisfy thier demand in a single auction, that is, a buyer
will purchase its required data from a single seller. (WHAT?? why do I think
this? Answer: defining the routes as the sellers who have the EXACT amount of
data that the buyer requires, thus the min route in \cite{lazar} is the same as the subset of
users who have just enough data to meet the buyer's needs)

\section{Related Work}

\section{The Problem Model}
\subsection{The Secondary Market}

We consider the set of $\mathcal{I} = {1, \cdots, I}$ users who purchase or sell
data from other users. A buyer is matched with sellers who enough leftover data
to satisfy thier demand, and will submit bids in order to maximize thier (private) valuation.
A user's identity $i \in \mathcal{I}$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not need to buy from j, then this means that the
user has the exact amout of data they require and we simply set $s^j_i = (0, 0)$.
A seller $j$ places an ask $s_j^j = (d_j^j, p_j^j)$, meaning $j$ is offering a
quantity $d_j^j$ , with a reserve unit price of $p_j^j$ . In other words, when the subscript and
superscript are the same, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.

Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, seller $j$ computes an
allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to user
$i$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the allocation
rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i
d_i^j$.

\subsection{User Behavior}

We define a \textbf{opt-out buyer} as a user $i\in\mathcal{I}$ with utility of
the form 
\begin{equation}
    u_i = \theta_i \circ e_i(a) - \displaystyle\sum_j c_i^j,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation that user
$i$ finds a matching seller $j$. An opt-out buyer's valuation
depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market. Buyer
$i$'s valuation may now be interpreted as a unit valuation $\theta_i$, scaled
by a function of quantity desired from the market. 
We define, in addition to the valuation and budget of user $i$, a generic
\textbf{data-provisioning vector} $\vs_i$.  Define, for any allocation $a$,
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq a_i^j\vs_i^j,
\end{equation}
and let
\begin{equation}
    e_i(a) \triangleq \max_{j\ne i} e_i^j(a).
\end{equation}

Deviating slightly from the
bottleneck player defined in \cite{semret}, in addition to taking the inverse
of the route-provisioning vector to suit the data problem, we omit the term $a_j^i$ from the lemma, as it is
assumed that buyers and sellers are separated (a seller does not also buy data
and vice versa).
(NOTE: proof should come easily! make sure!)

Consider a user seeking to prevent
data overage by purchasing enough data from a subset of other network users.
This user $i$ can be modeled as a opt-out buyer where $\vs_i^j$ denotes the
fraction of user $j$'s data aquired by user $i$. (TAKE OUT: Buyer $i$ has an incentive to
to maximize the amount of requested data from one seller, thereby minimizing
the bid fee paid to the ISP and still fufill thier data requirement.)
For the sellers that do not meet a $i$'s data requirements, a rational (utility-maximizing) buyer will
set $s_i^j = 0$, i.e. they will not place a bid, as in \cite{zheng}. Also we
note that since $i$ is not a seller, $d_i^i = 0$ and $a^i = 0$.

Suppose the total amount of seller $j$'s data on the network at the instance that
user $i$ joins the auction is $\chi_j$. For the service to function as desired,
the data transfer from each seller cannot exceed the total amount they have available,
i.e. $a_i^j \le \chi_j\vs_i^j$. This will hold simultaneously for all $j$ if
and only if $\chi_j \ge \max_j \ a_i^j \vs_i^j = e_i(a)$. Thus $e_i(a)$
lower-bounds the amount of data that each seller $j$ has in an auction. We
determine (explain further?) the
valuation of the transaction between seller $j$ and buyer $i$ is well-defined,
and the form of (\ref{opt-out}) is justified. (Does this make sense? and check
the MATH!)

In order to form the distributed auction, we set $\vs_i^j=1$ for all sellers
who offer enough data to meet the needs required by buyer $i$, and $\vs_i^j=0$ for
all other $j$. This restricts the number of auctions in which the user is able to
participate. We intend to show that this does not affect thier valuation, and
indeed, in this network setting, results in a shared network optima (a
global optimum). The formulation is inversely analogous to the thinnest allocation route for
bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
(\ref{opt-out}) reduces to the original form (\ref{utility}), defined in
\cite{semret} as "a simple buyer at a single resource element".

The seller, in our analysis, is an extension of the buyer, where the valuation
$\theta^j$ is dependent on the buyers. The natural utility is the potential
profit from buyer $i$, $u^j = \theta^j\circ e_i(a)$, where $\theta^j$ is the
potential revenue from the sale of data composed with buyer $i$'s opt-out value
$e_i(a)$. We derive the potential revenue as a function of demand $\varrho$ as in
\cite{semret}, $\forall \ y\ge 0$, the demand for $j$ at unit price $y$ is given by
$$
    \varrho^j(y) \triangleq \displaystyle\sum_{p_j^i\ge y} d_j^i,
$$
with inverse
$$
    f^j(z) \triangleq \sup\big\lbrace y\ge 0: \varrho^j(y) \ge z\big\rbrace.
$$
Therefore, we have the seller's valuation \cite{semret}, 
$$
    \theta^j\circ e_i(a) = \displaystyle\int_0^{e_i(a)} f^j(z) \ dz.
$$
We note the difference in subscript/superscript notation from \cite{semret},
 we emphasize the separation of buyers and sellers, and our
claim that the seller's valuation depends on the opt-out \emph{buyer demand}.
The proof remains the same from \cite{semret}.

\section{Network Data P2P Analysis}

\subsection{Equilibrium}

Consider an opt-out buyer $i\in\mathcal{I}$, participating in many auctions
simultaneously. Due to (\ref{opt-out}), a seller only has an incentive to change its
bid value if it increases its expected opt-out value $e_i$. This creates an
incentive for $i$ to coordinate its bids to maximize (DOUBLE MAX? DOES THIS
MAKE SENSE?) the number of available sellers (with respect to the demand
threshold), and therefore maximize its overall
utitlity. We show that, without loss of utility, a buyer $i$ can increase its
bid quantities $d_i$ to the level where the opt-out value $e_i^j$ is the same
for each
\emph{qualifying} seller $j$. We show that buyer coordination \cite{semret} holds in the
secondary data market under our assumptions.
{
\lemma{(Opt-out buyer coordination)} Let $i\in\mathcal{I}$ be a opt-out buyer.
For any profile $s_i = (d_i, p_i)$, let $a \equiv a(s)$ be the resulting data
tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
(z_i,p_i)$ where $\forall \ l \ne i$,
$$
    z_i^l = \frac{\big\lbrack e_i(a) \big\rbrack}{\vs_i^l},
$$
and
\begin{equation}\label{coordination}
    a_i^l(z_i,p_i) = z_i^l.
\end{equation}
}
\textbf{Proof:} We will show that
\begin{equation}
    u_i(s_i;s_{-i}) \equiv u_i(d_i,p_i) \le u_i(z_i,p_i)
\end{equation}
using the modified allocation rule from \cite{tuffin} and our current
formulation. $\forall \ l \in \mathcal{I}$,
\begin{align}
\begin{split}
    z_i^l &= e_i(a)/\vs_i^l = \big[\max_{j\ne i} e_i^j(a)\big]/ \vs_i^l\\
    & \ge  e_i^j(a) = a_i^j\vs_i^j/\vs_i^l\\
    & \ge \frac{d_i}{\sum_{k:p_k=p_i} d_k}d_i(p_i;s_i) \\
    & = \frac{d_i}{\sum_{k:p_k=p_i} d_k}\bigg[D-\displaystyle\sum_{p_k>y,k\ne
i} d_k\bigg]^+.
\end{split}
\end{align}
Using the allocation (\ref{allocation}) rule again, we have
\begin{align*}
    a_i^l(z_i,p_i) &= \max\bigg(z_i^l, \\
\frac{d_i}{\sum_{k:p_k=p_i} d_k}&\bigg[D-\displaystyle\sum_{p_k>y,k\ne
i} d_k^l\bigg]^+\bigg) \\
    &= z_i \\
    &= e_i(a)\vs_i^l,
\end{align*}
and (\ref{coordination}) is proven. Then we have that $e_i(a(z_i,p_i)) =
a_i^l(z_i,p_i)\vs_i^l
= e_i(a) \ \forall \ l\ne i$, and so
$\theta_i\circ e_i(a(z_i, p_i)) = \theta_i\circ e_i(a)$. Now, by definition of
the seller's valuation, $\forall \ l$,
$$
    e_i(a) \ge e_i^l(a) \Rightarrow z_i^l\vs_i^l \ge a_i^l\vs_i^l \Rightarrow
a_i^l \le z_i^l\le a_i^l(z_i,p_i).
$$ 
Additionally, we comment that $x_i$ is feasible, i.e. $\sum_l c_i^l(s) \le b_i$
as the factor $\vs$ separates the auction space, restricting the number of bids
a user may place (SAY THIS BETTER!). In effect, we are using the buyer demand
to partition the auction space, thereby optimizing the message space for the
ISP, and providing an optimal market space to host the buyers and sellers based
on their type.
(....AND!?) 
The rest of the proof follows as in \cite{semret}.

The idea of buyer coordination follows from \cite{lazar} (FINISH!)

(DOES THIS PROOF EVEN CHANGE?)
{
\proposition{(Network incentive compatibility)}
Let $i\in\mathcal{I}$ be an opt-out buyer, and fix all other users' bids
$s_{-i}$, as well as the sellers' bids $s_i^i$ (so $a^i$ is fixed). \\
Let 
\begin{align}
    z_i &= \sup\bigg\lbrace h\ge 0 : \\
& \theta_i(h) > \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j\bigg\rbrace, 
\end{align}
\begin{align}\label{price}
    \psi_i &= \sup\bigg\lbrace h\ge 0: \\
&\displaystyle\int_0^h \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j \ dh \le b_i\bigg\rbrace,
\end{align}
$e = \max(z_i, \psi_i - \epsilon / \theta_i'(0))^+$, and for each $j\ne i$, 
$$
    v_i^j = (e - a_j^i)\vs_i^j
$$
and 
$$
    w_i^j = \vs_i^j\theta_i'(e).
$$
Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
s_{-i})$.
} \\ \\
\textbf{Proof:} First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
and $\forall j$, $P_i^j$ is non-decreasing, \ref{price} implies $\theta_i'(e) >
\sum_{j\ne i} P_i^j(v_i^j)\vs_i^j$, and so $\forall j\ne i$,

\subsection{Efficiency}

\subsection{Convergence}

\end{multicols}

\begin{thebibliography}{9}

\bibitem{zheng}
L. Zheng, C. Joe-Wong, C. W. Tan, S. Ha and M. Chiangs, 
\textit{Secondary markets for mobile data: Feasibility and benefits of traded
data plans}, 2015 IEEE
Conference on Computer Communications (INFOCOM), Kowloon, 2015, pp. 1580-1588.

\bibitem{lazar}
A. A. Lazar and N. Semret, 
\textit{“Design and Analysis of the Progressive Second Price Auction for Network
Bandwidth Sharing,”} Telecommunication Systems, Special Issue on Network Economics, 2000.

\bibitem{semret} 
N. Semret, 
\textit{“Market Mechanisms for Network Resource Sharing,”
Ph.D. thesis}. 
Columbia University, 1999.

\bibitem{tuffin}
Bruno Tuffin,
\textit{Revisited Progressive Second Price Auction for Charging
Telecommunication Networks}.
[Research Report] RR-4176, INRIA, 2001.

\end{thebibliography}

\end{document}

### 2018-04-18 Old/paper_min.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 Old/paper.tex
@@
 
-We further modify the allocation rule in \cite{tuffin} in order to suit our
-model. We argue that as there is no capacity bottleneck in our network as in
-\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
-take the maximum of the allocation rule. 
-We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
-opt-out buyer maximizes its utility by placing bids with all sellers who are
-able to fully meet their data requirements, similar to \cite{zheng}. 
-We propose a \emph{data allocation rule},
-{
-\proposition{(Data allocation rule)}\label{allocation}
-\begin{equation}
-    a_i(s) = \max\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k=p_i}d_k}
-D_i(p_i,s_{-i})\big\rbrace
-\end{equation}
-}
-The modified allocation rule changes the market dynamics by adding a threshold
-to buyer behavior; the strategy is now to submit bids to a subset of
-players, rather than incuding an assumption that data infinitely divisibile.
-
-(NOTE: move this?)
 We extend the P2P rules as in \cite{semret} to include a \emph{local} market
@@
 sellers. As a buyer may have access to multiple auctions, the sellers will be
-dynamically influenced by the $\epsilon$-best replies from the buyers. The
-valuation function of seller $j$ is dependent on the buyers demand, and can be
-modeled as a function of their potential revenue.
+dynamically influenced by the $\epsilon$-best replies from the buyers. (need to
+start to explain the opt-out buyer here... is the basis for network
+equilibrium, as the optimal solution is to have the opt-out function the same
+for all sellers i.e. P2P theory..).
 
@@
 This user $i$ can be modeled as a opt-out buyer where $\vs_i^j$ denotes the
-fraction of user $j$'s data aquired by user $i$. (TAKE OUT: Buyer $i$ has an incentive to
+fraction of user $j$'s data aquired by user $i$. Buyer $i$ has an incentive to
 to maximize the amount of requested data from one seller, thereby minimizing
-the bid fee paid to the ISP and still fufill thier data requirement.)
-For the sellers that do not meet a $i$'s data requirements, a rational (utility-maximizing) buyer will
-set $s_i^j = 0$, i.e. they will not place a bid, as in \cite{zheng}. Also we
-note that since $i$ is not a seller, $d_i^i = 0$ and $a^i = 0$.
+the bid fee paid to the ISP and still fufill thier data requirement.
+For the sellers that do not meet a competing buyer $k$'s data requirements, a rational (utility-maximizing) buyer will
+set $s_k^j = 0$. We note that since $i$ is not a seller, $d_i^i = 0$ and $a^i = 0$.
 
@@
 participate. We intend to show that this does not affect thier valuation, and
-indeed, in this network setting, results in a shared network optima (a
-global optimum). The formulation is inversely analogous to the thinnest allocation route for
+indeed, in this network setting, results in
+(EEEK! say something else like... results in a shared network optima, or a
+global optimum.) the smallest
+number of auctions that the network participates in as a whole (NOTE: can I
+formulate this?), and is inversely analogous to the thinnest allocation route for
 bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
@@
 $e_i(a)$. We derive the potential revenue as a function of demand $\varrho$ as in
-\cite{semret}, $\forall \ y\ge 0$, the demand for $j$ at unit price $y$ is given by
+\cite{semret}, $\forall \ y\ge 0$, the demand for auction $j$ at unit price $y$ is given by
 $$
@@
 Therefore, we have the seller's valuation \cite{semret},
+$$
+    \theta^j(x) = \displaystyle\int_0^x f^j(z) \ dz,
+$$
+and 
 $$
@@
 Consider an opt-out buyer $i\in\mathcal{I}$, participating in many auctions
-simultaneously. Due to (\ref{opt-out}), a seller only has an incentive to change its
-bid value if it increases its expected opt-out value $e_i$. This creates an
-incentive for $i$ to coordinate its bids to maximize (DOUBLE MAX? DOES THIS
-MAKE SENSE?) the number of available sellers (with respect to the demand
-threshold), and therefore maximize its overall
-utitlity. We show that, without loss of utility, a buyer $i$ can increase its
-bid quantities $d_i$ to the level where the opt-out value $e_i^j$ is the same
-for each
-\emph{qualifying} seller $j$. We show that buyer coordination \cite{semret} holds in the
-secondary data market under our assumptions.
+simultaneously. Due to (\ref{opt-out}), data allocations are only valuable to the
+seller if they decrease the expected matching of buyer $i$ (i.e. the buyer finds another
+seller). This creates an incentive for $i$ to coordinate its bids
+to maximize the number of available sellers, and therefore maximize its overall
+utitlity. We show that, without loss of utility, a buyer $i$ can decrease its
+bid quantities $d_i$ to the level where the opt-out value is the same for all
+$j$ sellers. We show that buyer coordination \cite{semret} holds in the
+secondary data market.
 {
@@
 tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
-(z_i,p_i)$ where $\forall \ l \ne i$,
+(z_i,p_i)$ where $\forall \ j \ne i$,
 $$
-    z_i^l = \frac{\big\lbrack e_i(a) \big\rbrack}{\vs_i^l},
+    z_i^j = \big\lbrack e_i(a) \big\rbrack,
 $$
@@
 \begin{equation}\label{coordination}
-    a_i^l(z_i,p_i) = z_i^l.
+    a_i^j(z_i,p_i) = z_i^j.
 \end{equation}
@@
 using the modified allocation rule from \cite{tuffin} and our current
-formulation. $\forall \ l \in \mathcal{I}$,
+formulation. $\forall \ j \in \mathcal{I}$,
 \begin{align}
 \begin{split}
-    z_i^l &= e_i(a)/\vs_i^l = \big[\max_{j\ne i} e_i^j(a)\big]/ \vs_i^l\\
-    & \ge  e_i^j(a) = a_i^j\vs_i^j/\vs_i^l\\
-    & \ge \frac{d_i}{\sum_{k:p_k=p_i} d_k}d_i(p_i;s_i) \\
+    z_i^j &= e_i(a) = \max_{j\ne i} e_i^j(a)\\
+    & \le  e_i^j(a) = a_i^j\vs_i^j\\
+    & \le \frac{d_i}{\sum_{k:p_k=p_i} d_k}d_i(p_i;s_i) \\
     & = \frac{d_i}{\sum_{k:p_k=p_i} d_k}\bigg[D-\displaystyle\sum_{p_k>y,k\ne
@@
 \end{align}
-Using the allocation (\ref{allocation}) rule again, we have
+Using the allocation rule again, we have
 \begin{align*}
-    a_i^l(z_i,p_i) &= \max\bigg(z_i^l, \\
+    a_i^j(z_i,p_i) &= \min\bigg(z_i^j, \\
 \frac{d_i}{\sum_{k:p_k=p_i} d_k}&\bigg[D-\displaystyle\sum_{p_k>y,k\ne
-i} d_k^l\bigg]^+\bigg) \\
-    &= z_i \\
-    &= e_i(a)\vs_i^l,
+i} d_k\bigg]^+\bigg),
 \end{align*}
-and (\ref{coordination}) is proven. Then we have that $e_i(a(z_i,p_i)) =
-a_i^l(z_i,p_i)\vs_i^l
-= e_i(a) \ \forall \ l\ne i$, and so
-$\theta_i\circ e_i(a(z_i, p_i)) = \theta_i\circ e_i(a)$. Now, by definition of
-the seller's valuation, $\forall \ l$,
-$$
-    e_i(a) \ge e_i^l(a) \Rightarrow z_i^l\vs_i^l \ge a_i^l\vs_i^l \Rightarrow
-a_i^l \le z_i^l\le a_i^l(z_i,p_i).
-$$ 
-Additionally, we comment that $x_i$ is feasible, i.e. $\sum_l c_i^l(s) \le b_i$
-as the factor $\vs$ separates the auction space, restricting the number of bids
-a user may place (SAY THIS BETTER!). In effect, we are using the buyer demand
-to partition the auction space, thereby optimizing the message space for the
-ISP, and providing an optimal market space to host the buyers and sellers based
-on their type.
-(....AND!?) 
-The rest of the proof follows as in \cite{semret}.
-
-The idea of buyer coordination follows from \cite{lazar} (FINISH!)
-
-(DOES THIS PROOF EVEN CHANGE?)
+and (\ref{coordination}) is proven. We may now confirm that $e_i(a_i^j(z_i,p_i)) = a_i^j(z_i,p_i)
+= z_i = e_i(a) \ \forall \ j\ne i$.
+$\theta_i\circ e_i(a(z_i, p_i)) = e_i(a)$, 
 {
@@
 & \theta_i(h) > \displaystyle\sum_{j\ne i}
-P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j\bigg\rbrace, 
+P_i^j\big((h-a_j^i)\vs_i^j\big)\sigma_i^j\bigg\rbrace, 
 \end{align}
@@
 &\displaystyle\int_0^h \displaystyle\sum_{j\ne i}
-P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j \ dh \le b_i\bigg\rbrace,
+P_i^j\big((h-a_j^i)\vs_i^j\big)\sigma_i^j \ dh \le b_i\bigg\rbrace,
 \end{align}

### 2018-04-18 Old/paper_mod_save.tex
Moving PhD paper from Dropbox to github.

\documentclass[12pt]{article}

\usepackage[text={6in,8.1in},centering]{geometry}

\usepackage{enumerate}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathrsfs} % to use mathscr fonts

\usepackage{multicol}

\usepackage{epstopdf}
\usepackage{caption,subcaption}
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{algorithmicx,algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{verbatim,moreverb}
\usepackage{courier}

\lstset{ %
language=C++,               
basicstyle=\footnotesize,
numbers=left,                  
numberstyle=\tiny,     
stepnumber=1,         
numbersep=5pt,         
backgroundcolor=\color{white},  
showspaces=false,               
showstringspaces=false,         
showtabs=false,                 
columns=fullflexible,
frame=single,          
tabsize=2,          
captionpos=b,       
extendedchars=true,
xleftmargin=17pt,
framexleftmargin=17pt,
framexrightmargin=17pt,
framexbottommargin=4pt,
breaklines=true,       
breakatwhitespace=false, 
escapeinside={\%*}{*)}       
}

\newenvironment{block}{\begin{adjustwidth}{1.5cm}{1.5cm}\noindent}{\end{adjustwidth}}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\def\verbatimtabsize{4\relax}
\def\listingoffset{1em}
\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}

\newcommand{\vs}{\varsigma}
\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcI}{\mathcal{I}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\headsep25pt\headheight20pt

\pagestyle{fancyplain}
\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
\cfoot{\ \hfill\tiny\sl Draft printed on \today}

\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables

\begin{document}
\begin{multicols}{2}

\section{Introduction}
China Mobile Hong Kong (CMHK) recently introduced such a secondary market.
CMHK’s 2cm (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data, with CMHK acting as a middleman both to match buyers
and sellers and to ensure that the sellers’ trading revenue and buyers’
purchased data are reflected on customers’ monthly bills. \cite{zheng}

In this work, we propose a distributed progressive second price (PSP) auction in
order to maximize social utility. We show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria when all users bid their real marginal
valuation of the mobile data offered in the secondary market described in
\cite{zheng}. The P2P auction's (as in all auctions),
demand information is not known centrally, rather it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only. In this work, the proposed mechanism allows sellers submit bids to buyers
directly; there is no entity that holds a global market knowledge.

We suppose that each seller (resp. buyer) can submit a bid to the secondary
market consisting of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached where $\epsilon$ corresponds to a bid
fee to be paid to the ISP on completion of the transaction. (FEE IS FIXED OR
PER-UNIT? (will change market incentives slightly))
(DO WE MODEL ISP PROFIT? FUTURE WORK)

\subsection{Distributed Progressive Second Price Auctions}

The distributed PSP auction first introduced in \cite{lazar} forms a part of the
overall market based allocation model. Consider a noncooperative game
where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
amount of resource $D_i$ from a set of resources $\mcL = \lbrace 1,\cdots,L\rbrace$. Suppose
each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
seller of resource $l$,
where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^l] \in \mcL \times \mcI$ (BAD NOTATION?
SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
, s_I^l]_{l\in\mcL}$ is
the profile of user $i$’s opponents. In addition, the user type now includes a
\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
$i$'s path, i.e. $l(i) \in \lbrace l\in \mcL : r_i^l >0\rbrace$. 
The market now shares $L$ resources, with allocation:
$$
    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
$$
The market price function (MPF) of user $i$ is defined as:
% MARKET PRICE 
\begin{align*}
    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcL}P_i^l(z_i^l,
s_{-i}^l)r_i^l \\
    = \displaystyle\sum_{l\in\mcL}&\bigg(\inf\bigg\lbrace y\ge 0 :
\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
\end{align*}
which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
$\tilde{D_i}$ is defined as follows:
% INVERSE PRICE (ALLOCATION)
\begin{align*}
    \tilde{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\min_l\hat{D}_i^l/r_i^l\bigg) : \\
    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
\end{align*}
which means the maximum available quantity at a bid price of $y$ given
$s_{−i}$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
as:
% ALLOCATION RULE
\begin{align*}
    \tilde{a_i}(s) &= \min_i\big\lbrace d_i^{l(i)}, \\
 &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
s_{-i}^l)\big\rbrace,
\end{align*}
\begin{align*}
    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcL}
p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
\end{align*}
 $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
$p_i^{l(i)}$ (when the
opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
$c_i^{l(i)}$. $\sum_{l\in\mcL} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
user $i$ is removed from the auction. Note that the allocation rule is modified
from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
$p_i$ are not rejected.

We further modify the allocation rule in \cite{tuffin} in order to suit our
model. We argue that as there is no capacity bottleneck in our network as in
\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
take the maximum in the allocation rule. 
We propose a \emph{data allocation rule}:
{
% DATA ALLOCATION RULE
\proposition{(Data allocation rule)}
\begin{equation}\label{allocation}
    \bar{a}_i(s) = \max_i\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k= p_i}d_k}
D_i(p_i,s_{-i})\big\rbrace
\end{equation}
} \\
Intuitively, this rule indicates that a seller will allocate its data to the
buyer with the highest demand that can be satisfied (within its budget). 
An allocation rule is feasible \cite{lazar} if $\forall \ s$,
$$
    \displaystyle\sum_{i\in\mcI} a_i(s) \le Q
$$
and $\forall \ i\in\mcI$,
\begin{align*}
    a_i(s) &\le d_i \\
    c_i(s) &\le p_id_i.
\end{align*}
We claim
that (\ref{allocation}) is feasible, to be shown in our analysis (SAY
BETTER).
The modified allocation rule changes the market
dynamics by adding a demand threshold to buyer behavior; the strategy is now to
submit bids to a (thresholded) subset of users, rather than submitting bids to all sellers as in \cite{lazar}, however
we still hold the assumption that data is infinitely divisibile. 
We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
opt-out buyer restricts its pool of sellers by only submitting bids to sellers
who have sufficient data to meet their requirement.
(NOTE: TAKE MAX ONLY OR NEED TO INTRODUCE
A GAP VARIABLE?), similar to \cite{zheng}. 
We intend to show that the pricing model (\ref{price}) is sufficient to attain the desirable
property of truthfullness through incentive compatibility. (MOVE THIS? NEED OWN
WORDS?) We
reason that our formulation upholds the \emph{exclusion-compensation
principle}, and is a valid progressive second price auction to the extent that buyer $i$
pays for its allocation so as to exactly cover the ``social opportunity cost" which is given by the declared willingness to pay (bids) of the users who are excluded by $i$'s
presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

(NOTE: move this?)
We extend the P2P rules as in \cite{semret} to include a \emph{local} market
price function as determined by the subset of nodes participating in the
auction, where the user is the auctioneer. Therefore the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the $\epsilon$-best replies from the buyers. The
valuation function of seller $j$ is dependent on the buyers demand, and is
modeled as a function of their potential revenue \cite{semret}.

Absent the cost or revenue from trading data, users gain utility from consuming
data. We use the $\alpha$-fair utility functions \cite{zheng} to model the
usage utility from consuming $d$ amount of data:
\begin{equation}
    \theta(d) = \frac{\sigma d^{1-\alpha}}{1-\alpha}
\end{equation}
(AUGH! NEED X TO BE SO BIG COMPARED TO ALPHA! can we assume a minimum ask?)
where $\sigma$ is a positive constant representing (the scale) of the usage
utility and we take $\alpha \in [0, 1)$.
We verify that the user valuation above satisfies the conditions for an
\emph{elastic demand function}: (NOTE: this part seems in the wrong place)

\definition{\cite{lazar}}
A real valued function $\theta(\cdot)$ is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$; \\
        \emph{Verification:} (obvious)
    \item $\theta$ is differentiable; \\
        \emph{Verification:} The derivative, $\sigma d^{-\alpha}$, is positive assuming non-negative
data requirements.
    \item $\theta ' \ge 0$, and $\theta '$ is non-increasing and continuous; \\
        \emph{Verification:} $U$ is differentiable for all $d$, and therefore
continuous. Its derivative is a negative exponential, and so is non-increasing.
    \item There exists $\gamma > 0$, such that for all $z \in [0,D]$, $\theta
'(z) > 0$ implies that for all $\eta \in [0, z), \theta '(z) \le \theta '(\eta)
- \gamma(z - \eta)$. \\
        \emph{Verification:} Without loss of generality, we may set the scaling
constant $\sigma=1$, and compute the curvature $\gamma(\xi)$, where by definition,
$$
    \gamma = \frac{\theta''}{(1+\theta')^{3/2}} = \frac{-\alpha
\xi^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}.
$$
Using a Taylor theorem approximation,
\begin{align*}
    z^{-\alpha} &\le \eta^{-\alpha} + \frac{-\alpha
d^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}(z-\eta) \\
    & \le \eta^{-\alpha} +
\frac{\alpha}{2\sqrt{2} \xi}(z-\eta)  \\
    &\le \eta^{-\alpha} +
\frac{\alpha}{\xi}(z-\eta).
\end{align*}
Now, using Taylor repeatedly, simplifying and taking the limit as $\eta \rightarrow z$,
\begin{align*}
    z^{-\alpha} - \eta^{-\alpha} &\le -\alpha\eta^{-\alpha-1}(z-\eta) \\
    & \le \frac{-\alpha}{\xi}(z-\eta).
\end{align*}
And so, since $\xi \le \eta^{\alpha+1}$,
we may set
$$
    \gamma \ge
\frac{-\alpha\eta^{-(\alpha+1)^2}}{\big(1+(\eta^{-2\alpha(\alpha+1)})^{3/2}},
$$
which holds in the case that $z > 1$, and so assuming that there must be at least one
unit of data required for a user to have
a valuation,  we have that the concavity of $\theta'$ is shown by Squeeze theorem.
\end{itemize}

% USER UTILITY (7)
In the remainder of this paper we omit the bar in the data allocation rule for
simplicity of notation, so $\bar{a}_i = a_i$. We may now define the user's utitlity function as
\begin{equation}\label{utility}
    u_i = \theta_i(a_i(s)) - c_i(s).
\end{equation}

Under the PSP rule, \cite{lazar} shows that given the opponents bids $s_{-i}$,
user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
(where $s_i$ is chosen to maximize $i$'s utility with $s_{-i}$ held constant), is
given by:
\begin{align}
\begin{split}
    v_i &= \sup\bigg\lbrace d \ge 0 : \theta '(d) > P_i(d), \\ 
&\displaystyle\int_0^d P_i(\eta) \ d\eta \le b_i\bigg\rbrace -
\frac{\epsilon}{\theta_i'(0)} \\
&\qquad\qquad \text{(best quantity reply)} \\
\end{split}\\
    w_i &= \theta_i'(v_i) \quad \text{(best unit-price reply)},
\end{align}
where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
has an elastic demand function.

\emph{NOT GOOD\\
In the Secondary Market \cite{zheng}, we intend to show that it is optimal for a
buyer to fully satisfy thier demand in a single auction, that is, a buyer
will purchase its required data from a single seller. In the sub-optimal case,
the buyer will split its bid among multiple sellers. }

(ALSO NOT GOOD)
In the Secondary Market \cite{zheng}, we intend to show that it is optimal for a
buyer to satisfy thier demand by submitting equal bids to the subset of sellers
$\in \mcI$ who
meet their data threshold. (FIGURE OUT, WITH A
DATA GAP OR JUST THE MAX? PRICE DEPENDENT OR JUST DATA?)

\section{Related Work}
(HERE ADDRESS THE CENTRALIZED AUCTIONS FROM OTHER PAPERS... ISP CONTROLLED
ETC.. MENTION DISTRIBUTED NON-DATA PSP? AD-HOC? NOT SURE, IS MATCHING ALGORITHM
A NON-ISSUE? (probably))

\section{The Problem Model}
\subsection{The Secondary Market}

We consider the set of $\mcI = \lbrace 1, \cdots, I\rbrace$ users who purchase or sell
data from other users. A buyer is matched with sellers who enough leftover data
to satisfy thier demand, and will submit bids in order to maximize thier (private) valuation.
A user's identity $i \in \mcI$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. (STILL TRUE?) Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, then this means that
the user has the exact amout of data they require, or that seller $j$ does not have
enough data to satisfy the buyer's demand, and we simply set $s^j_i = (0, 0)$.
A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
quantity $d_j^j$ , with a reserve unit price of $p_j^j$ . In other words, when the subscript and
superscript are the same, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.
With this restriction, we note that since $i$ is not a seller, $d_i^i = 0$ and
$a^i = 0$. We may simplify the notation so that $s_j^j = (d_j^j, p_j^j) = s^j = (d^j, p^j)$.

Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, seller $j$ computes
an allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to
user $i$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$ (THIS MAY
NEED A SLIGHT MODIFICATION), and $c^j_i \le  p^j_i d_i^j$.

\section{Distributed PSP Analysis}
\subsection{User Behavior}

% OPT-OUT BUYER
We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
function as in \cite{semret},
\begin{equation}\label{opt-utility}
    u_i = \theta_i \circ e_i(a) - \displaystyle\sum_j c_i^j,
\end{equation}
where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation (FUTURE
WORK) that user
$i$ finds a matching seller $j$. An opt-out buyer's valuation
depends only on a scalar $e_i(a)$ which is a function of the
quantities of all the available data for sale in the secondary market.

Suppose the total amount of seller $j$'s data on the network at the instance that
user $i$ joins the auction is $\bar{b}^j$. For the service to function as desired,
the data transfer from each seller cannot exceed the total amount they have available,
i.e. $a_i^j \le \bar{b}^j$. (CHECK THE MATH!) This will hold simultaneously for each $j \in
\mcL_i$ if and only if $\bar{b}^j \ge \max_j \ a_i^j \vs_i^j = e_i(a)$.
(TERRIBLE NONSENSE) Thus $e_i(a)$
lower-bounds the amount of data that each seller $j$ has in an auction.
We define the set of \emph{qualifying sellers} for buyer $i$,
% QUALIFYING SELLERS
\begin{equation}\label{sellers}
     \mcL_i = \lbrace j \in \mcI : \bar{b}^j \ge e_i(a) \rbrace,
\end{equation}
and denote the set of buyers who submit bids to $j$ as $\mcI^j = \lbrace i\in\mcI : j \in
\mcL_i\rbrace.$

Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
place a bid, as in \cite{zheng}.

Buyer $i$'s valuation may now be interpreted as a unit valuation $\theta_i$, scaled
by a function of quantity desired from the market. 
We define, in addition to the valuation and budget of user $i$, a generic
\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
following (novel) strategy,
{
\theorem{(Opt-out buyer strategy)}\label{strategy}
Define, for any allocation $a$,
% OPT-OUT FUNCTION
\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
    e_i^j(a) \triangleq a_i^j\vs_i^j,
\end{equation}
and let
\begin{equation}
    e_i(a) \triangleq \min\bigg(\max_j e_i^j(a), \delta\bigg),
\end{equation}
where $\delta = \max_k d_k$ where $k\in \mcL_i$ and $s_i = (\delta,
\theta'(\delta)) \in S_i(s_{-i})$, where 
$$
    S_i(s_{-i}) = \bigg\lbrace s_i : \displaystyle\sum_j c_i^j(s_i;s_{-i}) \le b_i\bigg\rbrace,
$$
is given as in \cite{lazar} and $b_i$ is user $i$'s budget. In other words, the
buyer will always make a maximum feasible bid (WHY IS IT FEASIBLE? BETTER MIN
AND STAY IN AUCTION? PRICE OR QUANTITY?). 
Under this rule, the secondary market described in \cite{zheng} converges to a $\epsilon$-Nash equilibrium.
}\\
\textbf{Proof:}
We will prove the theorem by asserting that our formulation upholds the VGC
mechanism that is given in the properties of modern PSP. Namely,
\begin{itemize}
    \item Incentive compatibility
    \item Efficiency 
    \item Convergence
\end{itemize}

The seller, in our analysis, is an extension of the buyer, where the valuation
$\theta^j$ is dependent on the buyers, we will assume that buyers and sellers
are separated (a seller does not also buy data and vice versa).

The natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with opt-out value
$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
$\mcI^j$. Note that we have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
participate in any auction. Additionally, as the
value of the secondary market is its ability to fufill the data demands of its
users, we determine the
valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
and the form of (\ref{opt-out}) is justified. 
\iffalse
We may now define the maximum
quantity of \emph{data} at bid price $y$ given $s_{-i}$:
% NEW DEMAND
\begin{align}
\begin{split}
    \bar{D}_i(y,s_{-i}) &= \max_j \bigg(D_i^j(y,s_{-i}^j)\ \circ\ e_i\bigg)\\
    &= \max_j\bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\vs_k^j\bigg\rbrack^+.
\end{split}
\end{align}
\fi
(MOVE?)
Define, for a buyer $i$,
$$
    \ell_i =\min_{n\in\mcI} \bigg( \argmax_{\mcL_i' \subset \mcL_i, \vert\mcL_i'\vert =
n}\sum_{j\in\mcL_i'} d^j\bigg),
$$
and
\begin{equation}\label{minset}
    \bar{\mcL_i} = \bigg\lbrace j \in  \ell_i:
\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
\end{equation} 
where $\bar{\mcL_i} \subset \mcL_i$ is the
minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
(DO I WANT EXACTLY? ... YES) the demand $d_i$.
We note that as we assume $\forall \ j \in \mcL_i, d^j \ge
d_i$, the subset definition is expressed here for notational ease.
Additionally, we define, for a seller $j$,
$$
    \beta^j = \bigg\lbrace i\in\bar\mcI^j: \sum_i
d_i^j \le \bar{b}^j \bigg\rbrace,
$$
and so, similarly to (\ref{minset}),
\begin{equation}\label{maxset}
    \bar{\mcI}^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
\end{equation}
as the maximum subset of buyers $\in\mcI^j$ that $j$ can satisfy with budget
$\bar{b}^j$. The set $\beta^j$ is computed at each bidding iteration,
i.e., for $\tau >0$, 
\begin{align*}
    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\bar\mcI^j: \sum_i
        d_i^j \le \bar{b}^j \bigg\rbrace, \\
    \text{where}&\\
    \bar{b}^j &= b_j - \sum_{t\in
\tau} d_i^{j(t)}
\end{align*}
and $b^j$ is $j$'s original budget.

\subsection{Data Auction Mechanism}
We may now proceed to formally define the PSP auction.
The market price function (MPF) for a user in the secondary market
can now be described as follows:
% NEW MARKET PRICE
\begin{align}
\begin{split}
    \bar{P}_i(z, s_i) &= \displaystyle\sum_{j\in\bar\mcL_i}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\bar\mcL_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
\end{split}
\end{align}
where
\begin{align}
\begin{split}
    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\vs_k^j\bigg\rbrack^+,
\end{split}
\end{align}
which is interpreted as the minimum bid price, as in \cite{lazar}.
The inverse function
$\bar{D}_i$ is defined as
\begin{align}
\begin{split}
    \bar{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
\sum_{j\in\bar\mcL_i} \bar{D}_i^j \bigg) : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace.
\end{split}
\end{align}
The rules defined above describe the mechanism for the PSP auction given in
\cite{lazar}, however, in order to apply PSP to the data-sharing secondary market described in
\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
data-sharing model, it is not necessary to bid on a minimal route, and that our
formulation not only holds the desired VCG qualities, but minimizes the message
space and auction duration, resulting in a faster convergence time than the
classic throughput problem (EEEK!).

The potential revenue for $j$ at unit price $y$ is determined by the
demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\bar\mcI_j : p_i^j\ge y} d_i^j, 
\end{equation}
with ``inverse"
% SELLER REVENUE 
\begin{equation}\label{revenue}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z \ \forall \ i \in \bar\mcI_j\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
which it could be sold to any buyer $i\in \bar{\mcI}^j$.
Now, in order to derive the seller's valuation, we have the following,
{
% SELLER CONSTRAINTS
\proposition{(Seller constraints)}\label{constraints}
Let $j\in\mcL_i$ be a seller, and fix its allocation to $(a^j,c^j)$.
Formalizing the quantity threshold, the seller must satisfy the quantity
constraint, $\forall \ i \in\bar\mcI^j$,
\begin{equation}\label{quantity}
    d^j \ge d_i = e_i(a),
\end{equation}
and
\begin{equation}\label{budget}
    \displaystyle\sum_{i\in\bar\mcI^j} e_i^j(a) \le \sum_{i\in\bar\mcI^j} d^j_i \le b^j.
\end{equation}
In addition, for a seller who does not sell at a loss, the reserve price must
satisfy, $\forall \ i \in \bar\mcI^j$,
\begin{equation}\label{reserveprice}
   p^j \ge \min_{i\in\bar\mcI_j}\big({\theta_i}'(d_i^j)\big).
\end{equation}
}\\
\textbf{Proof:}
The first statement is an assumption, which we may enforce by (\ref{opt-out}),
and as a seller cannot sell more data than thier bid, (\ref{budget}) enforces
that there is a natural budget constraint for the seller. (\ref{reserveprice})
follows from the assumption that $j$ does not sell at a loss.

We may now define the seller $j$'s valuation. 
{
\proposition{(Seller valuation)}
% SELLER VALUATION
For any $i\in\bar\mcI^j$, 
\begin{equation}
    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
defining the function
$$
\mu_i^j = \frac{1}{\sum_{k\in\mcI_j:p_k^j=p_i^j} k},
$$
and an even smaller subset $\varrho\subset\bar\mcI^j$:
$$
    \varrho = \bigg\lbrace i \in \argmax_{\bar\mcI_j'\subset\bar\mcI_j}
\displaystyle\sum_{i\in\bar\mcI'} p_i^j : p_i^j \ge p_k^j \ \forall \ k\ne
i\bigg\rbrace,
$$
it follows that 
\begin{equation}\label{valuation}
    \theta^j = \displaystyle\sum_{i\in\varrho}
 \int_0^{e_i^j(a)} \mu_i^j f^j(z) \ dz.
\end{equation}
}
(COULD SIMPLIFY A LOT..)
\textbf{Proof:} 
We have that $\sum_{i\in\bar{\mcI_j}} d_i^j = 
\sum_{i\in\bar{\mcI}^j} e_i$ from (\ref{quantity}) and (\ref{budget}),
i.e. a seller will try and sell all of its data. The remainder of the proof
follows as in \cite{semret}.

\subsection{Formulation?}
Consider a user seeking to prevent
data overage by purchasing enough data from a subset of other network users.
This user $i$ can be modeled as a opt-out buyer where, as in \cite{semret}, $\vs_i^j$ denotes the
fraction of user $j$'s data aquired by user $i$. In order to form the
distributed auction, we set $\vs_i^j=1$ for all sellers who offer the enough data to meet the needs required by buyer $i$,
$\vs_i^j = 0$ for all other $j$. We intend to show that this does not affect thier valuation, and
indeed, in this network setting, results in a shared network optima (a
global optimum). The formulation is inversely analogous to the thinnest allocation route for
bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
(\ref{opt-utility}) reduces to the original form (\ref{utility}), defined in
\cite{semret} as ``a simple buyer at a single resource element", in other
words, (\ref{valuation}) where $i$ is fixed (MAKES SENSE?).

\section{VCG Analysis}
\subsection{Equilibrium}

Consider an opt-out buyer $i\in\mcI$. 
Due to (\ref{opt-out}), $i$ only has an incentive to change its bid
quantity if it increases its opt-out value $e_i$. 
(I THINK WE NEED PRICE TO COME IN SOON... MODIFIED ALLOCATION RULE!)
We show that, without loss of utility, $i$ can increase its
bid quantities $d_i$ to the level where the opt-out value $e_i$ 
 is the same for each qualifying seller $j \in\bar\mcL_i$. Therefore buyer
coordination holds in the secondary data market under our assumptions.
We note that in our analysis, by convention, $\infty\cdot 0 = 0$.
{
\lemma{(Opt-out buyer coordination)} Let $i\in\mcI$ be a opt-out buyer.
For any profile $s_i = (d_i, p_i)$, let $a \equiv a(s)$ be the resulting data
tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
(z_i,p_i)$ where $\forall \ j \ne i$,
$$
    z_i^j = \big\lbrack e_i(a) \big\rbrack},
$$
and
\begin{equation}\label{coordination}
    a_i^j(z_i,p_i) = z_i^j.
\end{equation}
}\\
\textbf{Proof:} (NOTE: DID NOT ADDRESS CLUTTERED NOTATION... DO LATER) We will show that
\begin{align*}
    u_i(s_i;s_{-i}) &\equiv u_i(d_i,p_i) \le u_i(z_i,p_i) \\
   &\equiv \theta_i(a_i((d_i,p_i);s)\vs_i) - c_i(s)\\
    & \le \theta_i(a_i((z_i,p_i);s_{-i})\vs_i) \\
    &-c_i((z_i,p_i);s_{-i}).
\end{align*}
Using (\ref{allocation}), we have $\forall \ l \in \mcL_i$, 
$$
    z_i^l \ge a_i^l(s) \ge \bar{D}_i^l((d_i, p_i^l);s), \\
$$
therefore,
\begin{align*}
    a_i^l((z_i,p_i);s)) &= \max\bigg\lbrace z_i^l, \\
    &\frac{z_i^l}{\sum_{k:p_k^l\ge p_i^l} d_k^l}
D_i^l((z_i,p_i^l);s)\bigg\rbrace
\end{align*}
implies that $\forall \ l \in \mcI$, and where $k \in \mcL_i$,
\begin{align}
\begin{split}
    z_i^l &= e_i(a) /\vs_i^l = \bigg[\min_l\big(\max_{l\ne i} e_i^j(a), \delta_i\big)\bigg]/ \vs_i^l\\
    &= \bigg[\min\big(\max_{j\ne i} e_i^j(a),\max_k(d_k : d_k < b_i)\big)\bigg]/ \vs_i^l\\
    & \ge  e_i^l(a) /\vs_i^l = a_i^l\vs_i^j/\vs_i^l = a_i^l\\
    & \ge \frac{d_i}{\sum_{k:p_k=p_i} d_k^l}d_i(p_i;s_i) \\
    & = \frac{d_i^l}{\sum_{k:p_k=p_i} d_k^l}\bigg[d_l^l-\displaystyle\sum_{p_k>y,k\ne
i} d_k^l\bigg]^+.
\end{split}
\end{align}
In other words, the buyer will bid the minimum of: 1) the entirety of the
sellers offer, and 2) the highest amount possible with respect to its budget $b_i$
such that it matches highest quantity from any bid in the auction. Using the allocation rule (\ref{allocation}) again, we have
\begin{align*}
    a_i^l(z_i,p_i) &= \max\bigg(z_i^l, \\
\frac{d_i^l}{\sum_{k:p_k=p_i} d_k^l}&\bigg[d_l^l-\displaystyle\sum_{p_k>y,k\ne
i} d_k^l\bigg]^+\bigg) \\
    &= z_i \\
    &= e_i(a) / \vs_i^l,
\end{align*}
and (\ref{coordination}) is proven.
We have that $e_i^l(a(z_i,p_i)) = a_i^l(z_i,p_i)\vs_i^l
= e_i(a) \ \forall \ l\ne i$, and so
$\theta_i\circ e_i(a(z_i, p_i)) = \theta_i\circ e_i(a)$. 
By the definition of utility,
\begin{align*}
    u_i(z_i,p_i) - u_i &= \theta_i\circ e_i(z_i,p_i)  - \displaystyle\sum_{l\ne
i}c_i(z_i,p_i) \\
    &- \theta_i(a_i(d_i,p_i)) - \displaystyle\sum_{l\ne i} c_i^l(s) \\
\end{align*}
(CHECK MATH!) Now, by definition of
the seller's valuation, $\forall \ l$,
\begin{align*}
    &=\displaystyle\sum_{l\ne i}\int_{a_i^l(z_i,p_i)}^{a_i^l} f^l(d_l^l
-z) \ dz \\
    e_i(a) &\ge e_i^l(a) \Rightarrow z_i^l\vs_i^l \ge a_i^l\vs_i^l \\
    &\Rightarrow a_i^l \le z_i^l\le a_i^l(z_i,p_i),
\end{align*}
Additionally, we comment that $x_i$ is feasible, i.e. $\sum_l c_i^l(s) \le b_i$
as the factor $\vs$ separates the auction space, restricting the number of bids
a user may place. In effect, we are using the buyer demand
to partition the auction space, thereby optimizing the message space for the
ISP, and providing an (BAD, DOESN'T MATTER) optimal market space to host the buyers and sellers based
on their type. 
(....AND!?) 
The rest of the proof follows as in \cite{semret}.
The idea of buyer coordination follows from \cite{lazar} (FINISH!)

In the case where no seller is offering enough data to satisfy a single user's
demand, the user is forced to submit bids to multiple sellers. According to (\ref{demand}) we claim that there is an incentive for the seller to
submit fractional bids (i.e. bid a fraction of thier leftover data) in the hopes
of maximizing the auction price in its
\emph{local} auction by including more sellers. To
formalize this we have the following lemma. (WILL NEED THIS LATER? BAD?)
{
\lemma{(Seller incentive)}\label{incentive}
Let $j$ be an opt-out buyer with fixed bid $(d^j,c^j)$. Then, in order to change the
quantity $d^j$ we must have, for some $k \in \mcI$,
\begin{equation}
       p_k^j \ge \max_i c_i^j\vs_i^j.
\end{equation}
}
\textbf{Proof:}
We will demonstrate a proof by cases:\\
(NEED TO THINK, I ONLY SAID THERE IS AN INCENTIVE TO DECREASE... STILL NEED
BOTH CASES THOUGH)\\
The idea is that as the sellers are decreasing their bid quantities, the buyers
are increasing them so that the result is distributed collaboration, resulting
in an inherent network matching $\rightarrow$ market equilibrium.
\emph{Case 1:} Suppose decrease $d$ (NEED PRICE? SHOULD NOT CHANGE FROM THEORY
BUT INCLUDE THIS FACT)\\
\emph{Case 2:} Increase $d$\\

(DOES THIS BELONG HERE?)
In addition, in the case that the seller does not know the exact amount of
leftover data available, then they may only sell enough data to ensure that
they will not become a buyer. (FUTURE WORK?)

{
\proposition{(Network incentive compatibility)}
(DOES THIS PROOF EVEN CHANGE? NEED TO START WORKING IT OUT)
Let $i\in\mcI$ be an opt-out buyer, and fix all other users' bids
$s_{-i}$, as well as the sellers' bids $s_i^i$ (so $a^i$ is fixed). \\
Let 
\begin{align}
    z_i &= \sup\bigg\lbrace h\ge 0 : \\
& \theta_i(h) > \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j\bigg\rbrace, 
\end{align}
\begin{align}\label{price}
    \psi_i &= \sup\bigg\lbrace h\ge 0: \\
&\displaystyle\int_0^h \displaystyle\sum_{j\ne i}
P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j \ dh \le b_i\bigg\rbrace,
\end{align}
$e = \max(z_i, \psi_i - \epsilon / \theta_i'(0))^+$, and for each $j\ne i$, 
$$
    v_i^j = (e - a_j^i)\vs_i^j
$$
and 
$$
    w_i^j = \vs_i^j\theta_i'(e).
$$
Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
s_{-i})$.
} \\ \\
\textbf{Proof:} First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
and $\forall j$, $P_i^j$ is non-decreasing, \ref{price} implies $\theta_i'(e) >
\sum_{j\ne i} P_i^j(v_i^j)\vs_i^j$, and so $\forall j\ne i$,

\subsection{Efficiency}

\subsection{Convergence}

\end{multicols}

\begin{thebibliography}{9}

\bibitem{zheng}
L. Zheng, C. Joe-Wong, C. W. Tan, S. Ha and M. Chiangs, 
\textit{Secondary markets for mobile data: Feasibility and benefits of traded
data plans}, 2015 IEEE
Conference on Computer Communications (INFOCOM), Kowloon, 2015, pp. 1580-1588.

\bibitem{lazar}
A. A. Lazar and N. Semret, 
\textit{“Design and Analysis of the Progressive Second Price Auction for Network
Bandwidth Sharing,”} Telecommunication Systems, Special Issue on Network Economics, 2000.

\bibitem{semret} 
N. Semret, 
\textit{“Market Mechanisms for Network Resource Sharing,”
Ph.D. thesis}. 
Columbia University, 1999.

\bibitem{tuffin}
Bruno Tuffin,
\textit{Revisited Progressive Second Price Auction for Charging
Telecommunication Networks}.
[Research Report] RR-4176, INRIA, 2001.

\end{thebibliography}

\end{document}

### 2018-04-18 Old/paper_mod_save2.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 Old/paper_mod_save.tex
@@
 valuation of the mobile data offered in the secondary market described in
-\cite{zheng}. The P2P auction's (as in all auctions),
+\cite{zheng}. The PSP auction's (as in all auctions),
 demand information is not known centrally, rather it is distributed in the
@@
 \begin{align*}
-    \tilde{a_i}(s) &= \min_i\big\lbrace d_i^{l(i)}, \\
+    \tilde{a_i}(s) &= \min\big\lbrace d_i^{l(i)}, \\
  &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
@@
 
-We further modify the allocation rule in \cite{tuffin} in order to suit our
-model. We argue that as there is no capacity bottleneck in our network as in
-\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
-take the maximum in the allocation rule. 
-We propose a \emph{data allocation rule}:
-{
-% DATA ALLOCATION RULE
-\proposition{(Data allocation rule)}
-\begin{equation}\label{allocation}
-    \bar{a}_i(s) = \max_i\big\lbrace d_i, \frac{d_i}{\sum_{k:p_k= p_i}d_k}
-D_i(p_i,s_{-i})\big\rbrace
-\end{equation}
-} \\
-Intuitively, this rule indicates that a seller will allocate its data to the
-buyer with the highest demand that can be satisfied (within its budget). 
 An allocation rule is feasible \cite{lazar} if $\forall \ s$,
@@
 \end{align*}
-We claim
-that (\ref{allocation}) is feasible, to be shown in our analysis (SAY
-BETTER).
-The modified allocation rule changes the market
-dynamics by adding a demand threshold to buyer behavior; the strategy is now to
-submit bids to a (thresholded) subset of users, rather than submitting bids to all sellers as in \cite{lazar}, however
-we still hold the assumption that data is infinitely divisibile. 
+
 We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
@@
 We consider the set of $\mcI = \lbrace 1, \cdots, I\rbrace$ users who purchase or sell
-data from other users. A buyer is matched with sellers who enough leftover data
-to satisfy thier demand, and will submit bids in order to maximize thier (private) valuation.
+data from other users. A buyer submits bids directly to sellers who enough leftover data
+to satisfy their demand, and will submit bids in order to maximize thier
+(private) valuation. We assume (SUPPOSE?) that the public information in the
+secondary market consists of a set of offers that are published by users
+wishing to sell their data overage. 
 A user's identity $i \in \mcI$ as a subscript indicates that the user
@@
 With this restriction, we note that since $i$ is not a seller, $d_i^i = 0$ and
-$a^i = 0$. We may simplify the notation so that $s_j^j = (d_j^j, p_j^j) = s^j = (d^j, p^j)$.
+$a^i = 0$. We may simplify the notation so that $s_j^j = (d_j^j, p_j^j) = s^j =
+(d^j, p^j)$. In our current formulation, we do not allow a seller to submit
+multiple bids $s^j$ (FUTURE WORK).
 
@@
 \end{equation}
-where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation (FUTURE
-WORK) that user
+where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation 
+(???? BAD) that user
 $i$ finds a matching seller $j$. An opt-out buyer's valuation
@@
 Suppose the total amount of seller $j$'s data on the network at the instance that
-user $i$ joins the auction is $\bar{b}^j$. For the service to function as desired,
-the data transfer from each seller cannot exceed the total amount they have available,
-i.e. $a_i^j \le \bar{b}^j$. (CHECK THE MATH!) This will hold simultaneously for each $j \in
-\mcL_i$ if and only if $\bar{b}^j \ge \max_j \ a_i^j \vs_i^j = e_i(a)$.
-(TERRIBLE NONSENSE) Thus $e_i(a)$
-lower-bounds the amount of data that each seller $j$ has in an auction.
+user $i$ joins the auction is $\bar{b}^j$. 
+The data transfer from each seller cannot exceed the total amount they have available,
+i.e. $a_i^j \le \bar{b}^j$. (CHECK THE MATH!) This will hold simultaneously for each $i \in
+\mcI$ if and only if $\bar{b}^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
+restricted to subset of buyers $\in\mcI$.
 We define the set of \emph{qualifying sellers} for buyer $i$,
@@
 \begin{equation}\label{sellers}
-     \mcL_i = \lbrace j \in \mcI : \bar{b}^j \ge e_i(a) \rbrace,
+     \mcL_i = \lbrace j \in \mcI : \bar{b}^j \ge d_i \rbrace,
 \end{equation}
@@
 rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
-place a bid, as in \cite{zheng}.
+place a bid, as in \cite{zheng}. The seller, in our analysis, is an extension of the buyer, where the valuation
+$\theta^j$ is dependent on the buyers, we will assume that buyers and sellers
+are separated (a seller does not also buy data and vice versa).
 
-Buyer $i$'s valuation may now be interpreted as a unit valuation $\theta_i$, scaled
+Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
+is also reasonable to expect that many sellers will come close to using their
+entire data cap, and only sell the fractional overage. Additionally, a buyer
+will most likely not purchase fractional amounts of data, as this would incur
+additional bid fees (...AND). In this case, we
+determine that a buyer must coordinate their bids among multiple sellers. (SAY
+MORE?) To aid in our analysis, we define, for a buyer $i$,
+% MIN SET
+$$
+    \ell_i =\argmax_{\mcL_i' \subset \mcL_i, \vert\mcL_i'\vert =
+n}\sum_{j\in\mcL_i'} d^j,
+$$
+where $n\in\mcI$ is chosen so that
+\begin{equation}\label{minset}
+    \bar{\mcL_i} = \bigg\lbrace j \in  \ell_i:
+\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
+\end{equation} 
+where $\bar{\mcL_i} \subset \mcL_i$ is the
+minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
+(DO I WANT EXACTLY? ... YES) the demand $d_i$.
+We note that as we assume $\forall \ j \in \mcL_i, d^j \ge
+d_i$, the subset definition is expressed here for notational ease.
+Additionally, we define, for a seller $j$,
+$$
+    \beta^j = \bigg\lbrace i\in\bar\mcI^j: 
+d_i \le \bar{b}^j \bigg\rbrace,
+$$
+and so, similarly to (\ref{minset}),
+% MAX SET
+\begin{equation}\label{maxset}
+    \bar{\mcI}^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
+\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
+\end{equation}
+as the maximum subset of buyers $\in\mcI^j$ that $j$ can satisfy with budget
+$\bar{b}^j$. The set $\beta^j$ is computed at each bidding iteration,
+i.e., for $\tau >0$, 
+\begin{align*}
+    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\bar\mcI^j: 
+        d_i \le \bar{b}^j \bigg\rbrace, \\
+    \text{where}&\\
+    \bar{b}^j &= b_j - \sum_{t\in
+\tau} d_i^{j(t)}
+\end{align*}
+and $b^j$ is $j$'s original budget.
+
+Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, scaled
 by a function of quantity desired from the market. 
@@
 Define, for any allocation $a$,
-% OPT-OUT FUNCTION
+% OPT-OUT STRATEGY
 \begin{equation}\label{opt-out}
     %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
-    e_i^j(a) \triangleq a_i^j\vs_i^j,
+    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
 \end{equation}
@@
 \begin{equation}
-    e_i(a) \triangleq \min\bigg(\max_j e_i^j(a), \delta\bigg),
+    e_i(a) \triangleq \min_j\bigg(e_i^j(a)\bigg),
 \end{equation}
-where $\delta = \max_k d_k$ where $k\in \mcL_i$ and $s_i = (\delta,
-\theta'(\delta)) \in S_i(s_{-i})$, where 
-$$
-    S_i(s_{-i}) = \bigg\lbrace s_i : \displaystyle\sum_j c_i^j(s_i;s_{-i}) \le b_i\bigg\rbrace,
-$$
-is given as in \cite{lazar} and $b_i$ is user $i$'s budget. In other words, the
+(REWORD) In other words, the
 buyer will always make a maximum feasible bid (WHY IS IT FEASIBLE? BETTER MIN
@@
 
-The seller, in our analysis, is an extension of the buyer, where the valuation
-$\theta^j$ is dependent on the buyers, we will assume that buyers and sellers
-are separated (a seller does not also buy data and vice versa).
-
 The natural utility is the potential
@@
 and the form of (\ref{opt-out}) is justified.
-\iffalse
-We may now define the maximum
-quantity of \emph{data} at bid price $y$ given $s_{-i}$:
-% NEW DEMAND
-\begin{align}
-\begin{split}
-    \bar{D}_i(y,s_{-i}) &= \max_j \bigg(D_i^j(y,s_{-i}^j)\ \circ\ e_i\bigg)\\
-    &= \max_j\bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\vs_k^j\bigg\rbrack^+.
-\end{split}
-\end{align}
-\fi
-(MOVE?)
-Define, for a buyer $i$,
-$$
-    \ell_i =\min_{n\in\mcI} \bigg( \argmax_{\mcL_i' \subset \mcL_i, \vert\mcL_i'\vert =
-n}\sum_{j\in\mcL_i'} d^j\bigg),
-$$
-and
-\begin{equation}\label{minset}
-    \bar{\mcL_i} = \bigg\lbrace j \in  \ell_i:
-\displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
-\end{equation} 
-where $\bar{\mcL_i} \subset \mcL_i$ is the
-minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
-(DO I WANT EXACTLY? ... YES) the demand $d_i$.
-We note that as we assume $\forall \ j \in \mcL_i, d^j \ge
-d_i$, the subset definition is expressed here for notational ease.
-Additionally, we define, for a seller $j$,
-$$
-    \beta^j = \bigg\lbrace i\in\bar\mcI^j: \sum_i
-d_i^j \le \bar{b}^j \bigg\rbrace,
-$$
-and so, similarly to (\ref{minset}),
-\begin{equation}\label{maxset}
-    \bar{\mcI}^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
-\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
-\end{equation}
-as the maximum subset of buyers $\in\mcI^j$ that $j$ can satisfy with budget
-$\bar{b}^j$. The set $\beta^j$ is computed at each bidding iteration,
-i.e., for $\tau >0$, 
-\begin{align*}
-    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\bar\mcI^j: \sum_i
-        d_i^j \le \bar{b}^j \bigg\rbrace, \\
-    \text{where}&\\
-    \bar{b}^j &= b_j - \sum_{t\in
-\tau} d_i^{j(t)}
-\end{align*}
-and $b^j$ is $j$'s original budget.
 
@@
     \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\vs_k^j\bigg\rbrack^+,
+    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+\vs_i^j,
 \end{split}
 \end{align}
-which is interpreted as the minimum bid price, as in \cite{lazar}.
+and is interpreted as the minimum bid price, as in \cite{lazar}.
 The inverse function
@@
 \end{align}
+We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
+$\bar\mcL_i$ at a bid price of $y$ given $s_{i}$.
+
 The rules defined above describe the mechanism for the PSP auction given in
@@
 
+In order to complete our formulation, we argue that as there is no capacity bottleneck in our network as in
+\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
+take the maximum in the allocation rule. 
+We propose a \emph{data allocation rule}:
+{
+% DATA ALLOCATION RULE
+\proposition{(Data allocation rule)}
+Given an auction of infinitely divisible data $j$, where user $j$ is the
+auctioneer, the data allocation rule is given as,
+\begin{equation}\label{allocation}
+    \bar{a}_i^j(s) = \max_i\big\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
+p_i^j}d_k^j}
+\bar{D}_i^j(p_i^j,s_{-i}^j)\big\rbrace
+\end{equation}
+where $i\in\bar\mcI^j$.
+} 
+\textbf{Proof}:
+Intuitively, this rule indicates that a seller will allocate its data to the
+buyer with the highest demand that can be satisfied (within its budget). 
+(\ref{allocation}) is feasible by (\ref{quantity}) and (\ref{budget}), in that
+$$
+    \displaystyle\sum_{i\in\mcI} a_i(s) \le \displaystyle\sum_{i\in\mcI} e_i(a)
+\le \sum_{j\in\mcI} b^j = \mathcal{D},
+$$
+where $\mathcal{D} = \sum_{j\in\mcI} d^j$ is the total amount data for sale in the secondary market.
+As the buyers ``control" the secondary market via their individual data demands,
+$\forall \ i\in\mcI$,
+\begin{align*}
+    a_i(s) &\le e_i(a) \le d_i \\
+    c_i(s) &\le p_id_i.
+\end{align*}
+where $c_i(s)$ remains unchanged from \cite{lazar}. (FINISH!)
+
 \subsection{Formulation?}
@@
 Consider an opt-out buyer $i\in\mcI$. 
-Due to (\ref{opt-out}), $i$ only has an incentive to change its bid
+(I THINK WE NEED PRICE TO COME IN SOON... MODIFIED ALLOCATION RULE!)
+Due to (\ref{opt-utility}), $i$ only has an incentive to change its bid
 quantity if it increases its opt-out value $e_i$. 
-(I THINK WE NEED PRICE TO COME IN SOON... MODIFIED ALLOCATION RULE!)
-We show that, without loss of utility, $i$ can increase its
+We show that, without loss of utility, $i$ can coordinate its
 bid quantities $d_i$ to the level where the opt-out value $e_i$ 
- is the same for each qualifying seller $j \in\bar\mcL_i$. Therefore buyer
+ is the same for each qualifying seller $j \in\bar\mcL_i$. We argue
+that without loss of utility, $i$ may choose a seller pool where a minimal subset
+of sellers guaranteed to satisfy demand where $i$ is able to play a
+``consistent" (SECOND GUESSING THIS!)
+strategy and still have feasible best replies, and buyer
 coordination holds in the secondary data market under our assumptions.
-We note that in our analysis, by convention, $\infty\cdot 0 = 0$.
+
+% COORDINATION
 {
 \lemma{(Opt-out buyer coordination)} Let $i\in\mcI$ be a opt-out buyer.
-For any profile $s_i = (d_i, p_i)$, let $a \equiv a(s)$ be the resulting data
+For any profile $s_i^j = (d_i, p_i)$, let $a^j \equiv a^j(s)$ be the resulting data
 tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
-(z_i,p_i)$ where $\forall \ j \ne i$,
+(z_i,p_i)$, where for any $j \in \bar\mcL_i$,
 $$
-    z_i^j = \big\lbrack e_i(a) \big\rbrack},
+    z_i^j =  \big\lbrack e_i(a)\big\rbrack\vs_i^j
 $$
@@
 \begin{equation}\label{coordination}
-    a_i^j(z_i,p_i) = z_i^j.
+    a_i^j(z_i,p_i) = z_i^j,
 \end{equation}
@@
 \textbf{Proof:} (NOTE: DID NOT ADDRESS CLUTTERED NOTATION... DO LATER) We will show that
+$$
+    u_i(s_i;s_{-i}) \equiv u_i(d_i,p_i) \le u_i(z_i,p_i) \\
+$$
+\iffalse
 \begin{align*}
-    u_i(s_i;s_{-i}) &\equiv u_i(d_i,p_i) \le u_i(z_i,p_i) \\
+    u_i(d_i,p_i) &\le u_i(z_i,p_i) \\
    &\equiv \theta_i(a_i((d_i,p_i);s)\vs_i) - c_i(s)\\
@@
 \end{align*}
-Using (\ref{allocation}), we have $\forall \ l \in \mcL_i$, 
+\fi
+From (\ref{allocation}), we have that
+\begin{align*}
+    a_i^j(z_i,p_i) &= \max_i\bigg\lbrace z_i^j, \\
+    &\frac{z_i^j}{\sum_{k:p_k^j= p_i^j} d_k^j}
+\bar{D}_i^j((z_i^j,p_i^j))\bigg\rbrace
+\end{align*}
+and by (\ref{opt-out}), 
 $$
-    z_i^l \ge a_i^l(s) \ge \bar{D}_i^l((d_i, p_i^l);s), \\
+    z_i^j = e_i(a) = \min_j\big(e_i^j(a), \delta\big).
 $$
-therefore,
+where $i$ chooses the subset of sellers. We address two cases:\\
+1. \emph{There exists a seller who can fully satisfy $i$'s demand.} \\
+In this case, $\vert\bar\mcL_i\vert = 1$, and the case is trivial as no
+coordination is necessary for a single bid.\\
+2. \emph{Buyer $i$'s demand can only be satisfied by a minimal subset of sellers.} \\
+Buyer $i$ maintains ordered set $\bar\mcL_i$ where the sellers with the
+largest bid are considered first. It remains to locate the seller $j^*$ where $\bar\mcL_i$ is such that a
+coordinated bid is possible.
+
+Let $n \le I \in \mathcal{Z}^+$ be chosen so that 
+\begin{equation}
+    \displaystyle\sum_{\bar\mcL_i} \frac{\min_j(d^j)}{d_i} =
+\displaystyle\sum_{\bar\mcL_i} \frac{d^{j^*}}{d_i} = d_i.
+\end{equation} 
+As $\ell_j$ is an ordered set, $i$ is able to choose a minimal subset of sellers
+$\bar\mcL_i \subset \mcL_i$ where a coordinated bid is possible.
+
+(ALSO COULD TAKE THE MIN AND USE ALL SELLERS... IS THIS BETTER?)
+Now, $\forall \ j \in\bar\mcL_i$,
+$$
+    z_i^j \le a_i^j(s) \le \bar{D}_i^j((d_i, p_i^j),s^j),
+$$
 \begin{align*}
-    a_i^l((z_i,p_i);s)) &= \max\bigg\lbrace z_i^l, \\
-    &\frac{z_i^l}{\sum_{k:p_k^l\ge p_i^l} d_k^l}
-D_i^l((z_i,p_i^l);s)\bigg\rbrace
+    z_i^j & =\min_j\big(a_i^j\vs_i^j, \delta\big) \\
+    &= \min_j(a_i^j(z_i,p_i)\vs_i^j,\delta) =  \\
 \end{align*}
-implies that $\forall \ l \in \mcI$, and where $k \in \mcL_i$,
-\begin{align}
-\begin{split}
-    z_i^l &= e_i(a) /\vs_i^l = \bigg[\min_l\big(\max_{l\ne i} e_i^j(a), \delta_i\big)\bigg]/ \vs_i^l\\
-    &= \bigg[\min\big(\max_{j\ne i} e_i^j(a),\max_k(d_k : d_k < b_i)\big)\bigg]/ \vs_i^l\\
-    & \ge  e_i^l(a) /\vs_i^l = a_i^l\vs_i^j/\vs_i^l = a_i^l\\
-    & \ge \frac{d_i}{\sum_{k:p_k=p_i} d_k^l}d_i(p_i;s_i) \\
-    & = \frac{d_i^l}{\sum_{k:p_k=p_i} d_k^l}\bigg[d_l^l-\displaystyle\sum_{p_k>y,k\ne
-i} d_k^l\bigg]^+.
-\end{split}
-\end{align}
-In other words, the buyer will bid the minimum of: 1) the entirety of the
-sellers offer, and 2) the highest amount possible with respect to its budget $b_i$
-such that it matches highest quantity from any bid in the auction. Using the allocation rule (\ref{allocation}) again, we have
+The buyer will bid the minimum of: 1) its data
+requirement, or
+2) The entirety of the sellers offer.
+Using the allocation rule (\ref{allocation}) again, we have
 \begin{align*}
@@
     &= z_i \\
-    &= e_i(a) / \vs_i^l,
+    &= e_i(a) ,
 \end{align*}

### 2018-04-18 Old/paper_mod_save3.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 Old/paper_mod_save2.tex
@@
 where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
-amount of resource $D_i$ from a set of resources $\mcL = \lbrace 1,\cdots,L\rbrace$. Suppose
+amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$. Suppose
 each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
@@
 quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
-[s_i^l] \in \mcL \times \mcI$ (BAD NOTATION?
+[s_i^l] \in \mcI \times \mcI$ (BAD NOTATION?
 SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
-, s_I^l]_{l\in\mcL}$ is
+, s_I^l]_{l\in\mcI}$ is
 the profile of user $i$’s opponents. In addition, the user type now includes a
@@
 an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
-$i$'s path, i.e. $l(i) \in \lbrace l\in \mcL : r_i^l >0\rbrace$. 
+$i$'s path, i.e. $l(i) \in \lbrace l\in \mcI : r_i^l >0\rbrace$. 
 The market now shares $L$ resources, with allocation:
@@
 \begin{align*}
-    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcL}P_i^l(z_i^l,
+    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
 s_{-i}^l)r_i^l \\
-    = \displaystyle\sum_{l\in\mcL}&\bigg(\inf\bigg\lbrace y\ge 0 :
+    = \displaystyle\sum_{l\in\mcI}&\bigg(\inf\bigg\lbrace y\ge 0 :
 \hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
@@
 \begin{align*}
-    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcL}
+    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcI}
 p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
@@
 opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
-$c_i^{l(i)}$. $\sum_{l\in\mcL} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
+$c_i^{l(i)}$. $\sum_{l\in\mcI} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
 user $i$ is removed from the auction. Note that the allocation rule is modified
@@
 The data transfer from each seller cannot exceed the total amount they have available,
-i.e. $a_i^j \le \bar{b}^j$. (CHECK THE MATH!) This will hold simultaneously for each $i \in
+i.e. $a_i^j \le \bar{b}^j$. This will hold simultaneously for each $i \in
 \mcI$ if and only if $\bar{b}^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
 restricted to subset of buyers $\in\mcI$.
-We define the set of \emph{qualifying sellers} for buyer $i$,
-% QUALIFYING SELLERS
-\begin{equation}\label{sellers}
-     \mcL_i = \lbrace j \in \mcI : \bar{b}^j \ge d_i \rbrace,
-\end{equation}
-and denote the set of buyers who submit bids to $j$ as $\mcI^j = \lbrace i\in\mcI : j \in
-\mcL_i\rbrace.$
-
 Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
@@
 $$
-    \ell_i =\argmax_{\mcL_i' \subset \mcL_i, \vert\mcL_i'\vert =
-n}\sum_{j\in\mcL_i'} d^j,
+    \ell_i =\argmax_{\mcI_i' \subset \mcI_i, \vert\mcI_i'\vert =
+n}\sum_{j\in\mcI_i'} d^j,
 $$
@@
 \begin{equation}\label{minset}
-    \bar{\mcL_i} = \bigg\lbrace j \in  \ell_i:
+    \mcI_i = \bigg\lbrace j \in  \ell_i:
 \displaystyle\sum_{j\in \ell_i} d^j = d_i \bigg\rbrace.
 \end{equation} 
-where $\bar{\mcL_i} \subset \mcL_i$ is the
+so $\mcI_i \subset \mcI$ is the
 minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
 (DO I WANT EXACTLY? ... YES) the demand $d_i$.
-We note that as we assume $\forall \ j \in \mcL_i, d^j \ge
-d_i$, the subset definition is expressed here for notational ease.
 Additionally, we define, for a seller $j$,
 $$
-    \beta^j = \bigg\lbrace i\in\bar\mcI^j: 
+    \beta^j = \bigg\lbrace i\in\mcI^j: 
 d_i \le \bar{b}^j \bigg\rbrace,
@@
 \begin{equation}\label{maxset}
-    \bar{\mcI}^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
+    \mcI^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
 \vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
 \end{equation}
-as the maximum subset of buyers $\in\mcI^j$ that $j$ can satisfy with budget
-$\bar{b}^j$. The set $\beta^j$ is computed at each bidding iteration,
+as the maximum subset of buyers that $j$ can satisfy with budget
+$\bar{b}^j$. The set $\beta^j$ is computed by $j$ before each auction (???),
 i.e., for $\tau >0$, 
 \begin{align*}
-    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\bar\mcI^j: 
+    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\mcI^j: 
         d_i \le \bar{b}^j \bigg\rbrace, \\
@@
 {
-\theorem{(Opt-out buyer strategy)}\label{strategy}
+\proposition{(Opt-out buyer strategy)}\label{strategy}
 Define, for any allocation $a$,
-% OPT-OUT STRATEGY
+% OPT-OUT BUYER STRATEGY
 \begin{equation}\label{opt-out}
@@
 \end{equation}
-and let
+and let $j^* \in \ell_i$ be the seller such that
+$j^* = n \le I \in \mathcal{Z}^+$ results in a subset $\bar\mcI_i\subset\mcI_i$ where 
+\begin{equation}\label{coordinate}
+    \displaystyle\sum_{\bar\mcI_i} \frac{\min_{j\in\ell_i}(d^j)}{d_i} =
+\displaystyle\sum_{\bar\mcI_i} \frac{d^{j^*}}{d_i} = d_i,
+\end{equation} 
+now let, 
 \begin{equation}
-    e_i(a) \triangleq \min_j\bigg(e_i^j(a)\bigg),
+    e_i(a) \triangleq e_i^{j^*}(a).
 \end{equation}
-(REWORD) In other words, the
-buyer will always make a maximum feasible bid (WHY IS IT FEASIBLE? BETTER MIN
-AND STAY IN AUCTION? PRICE OR QUANTITY?). 
-Under this rule, the secondary market described in \cite{zheng} converges to a $\epsilon$-Nash equilibrium.
+Then, we have that $e_i$
+is the optimal feasible strategy for buyer $i$.
 }\\
 \textbf{Proof:}
-We will prove the theorem by asserting that our formulation upholds the VGC
-mechanism that is given in the properties of modern PSP. Namely,
-\begin{itemize}
-    \item Incentive compatibility
-    \item Efficiency 
-    \item Convergence
-\end{itemize}
+In the case that there exists a seller who can completely satisfy a buyer's
+demand, $j^*=1$, and (\ref{coordinate}) holds. If such a buyer does not exist,
+as the set $\ell_i$ is an ordered set, $i$ may discover seller
+$j^*$ by computing $\ell_i$ iteratively. In the case that $d_i = \mathcal{D} =
+\sum_{j\in\mcI}d^j$, then $j^* = I$ and the buyer will submit bids to all
+sellers. If $d_i>I$, then the buyer (??? THINKING $\mcI_i$ BETTER, ALSO ADDRESS
+FEASIBLE AND OPTIMAL!)
 
@@
 
+% MECHANISM
 \subsection{Data Auction Mechanism}
@@
 % NEW MARKET PRICE
-\begin{align}
+\begin{align}\label{dataprice}
 \begin{split}
-    \bar{P}_i(z, s_i) &= \displaystyle\sum_{j\in\bar\mcL_i}P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\bar\mcL_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
+    \bar{P}_i&(z, s_i) = P_i(z,s_i)\circ e_i \\
+    &=\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
+s_{-i}^j)/\vs_i^j \\
+    &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
+    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg)/\vs_i^j,\\
 \end{split}
@@
 where
+% NEW ALLOCATION RULE
 \begin{align}
@@
     \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+\vs_i^j,
+    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
 \end{split}
@@
 The inverse function
+% NEW INVERSE DEMAND
 $\bar{D}_i$ is defined as
@@
     \bar{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
-\sum_{j\in\bar\mcL_i} \bar{D}_i^j \bigg) : \\
+\sum_{j\in\mcI_i} \bar{D}_i^j \bigg) : \\
     &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace.
@@
 We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
-$\bar\mcL_i$ at a bid price of $y$ given $s_{i}$.
-
+$\mcI_i$ at a bid price of $y$ given $s_{i}$.
+% DATA ALLOCATION RULE
+The data allocation rule is given as,
+\begin{equation}\label{dataallocation}
+    \bar{a}_i^j(s) = \min_{j\in\mcI_i}\big\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
+p_i^j}d_k^j}
+\bar{D}_i^j(p_i^j,s_{-i}^j)\big\rbrace
+\end{equation}
+with cost,
+\begin{align}\label{dataprice}
+\begin{split}
+    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI_i}\bigg\lbrack\sum_{j\in\mcI_i}
+\frac{p^j}{\vs_i^j} \bigg(\bar{a}_j(0; s_{-i}^j)\\
+    &-\bar{a}_j(s_i^j;s_{-i}^j)\bigg) \bigg\rbrack,
+\end{split}
+\end{align}
+where $\mcI_i$ is chosen as described in the buyer strategy.
 The rules defined above describe the mechanism for the PSP auction given in
@@
 \begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\bar\mcI_j : p_i^j\ge y} d_i^j, 
+    \rho^j(y) = \sum_{i\in\mcI_j : p_i^j\ge y} d_i^j, 
 \end{equation}
@@
     f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z \ \forall \ i \in \bar\mcI_j\big\rbrace.
+        \rho_i^j(y) \ge z \ \forall \ i \in \mcI_j\big\rbrace.
 \end{equation}
 For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
-which it could be sold to any buyer $i\in \bar{\mcI}^j$.
+which it could be sold to any buyer $i\in \mcI^j$.
 Now, in order to derive the seller's valuation, we have the following,
@@
 \proposition{(Seller constraints)}\label{constraints}
-Let $j\in\mcL_i$ be a seller, and fix its allocation to $(a^j,c^j)$.
+Let $j\in\mcI_i$ be a seller, and fix its allocation to $(a^j,c^j)$.
 Formalizing the quantity threshold, the seller must satisfy the quantity
-constraint, $\forall \ i \in\bar\mcI^j$,
+constraint, $\forall \ i \in\mcI^j$,
 \begin{equation}\label{quantity}
@@
 \begin{equation}\label{budget}
-    \displaystyle\sum_{i\in\bar\mcI^j} e_i^j(a) \le \sum_{i\in\bar\mcI^j} d^j_i \le b^j.
+    \displaystyle\sum_{i\in\mcI^j} e_i^j(a) \le \sum_{i\in\mcI^j} d^j_i \le b^j.
 \end{equation}
 In addition, for a seller who does not sell at a loss, the reserve price must
-satisfy, $\forall \ i \in \bar\mcI^j$,
+satisfy, $\forall \ i \in \mcI^j$,
 \begin{equation}\label{reserveprice}
-   p^j \ge \min_{i\in\bar\mcI_j}\big({\theta_i}'(d_i^j)\big).
+   p^j \ge \min_{i\in\mcI_j}\big({\theta_i}'(d_i^j)\big).
 \end{equation}
@@
 % SELLER VALUATION
-For any $i\in\bar\mcI^j$, 
+For any $i\in\mcI^j$, 
 \begin{equation}
@@
 $$
-and an even smaller subset $\varrho\subset\bar\mcI^j$:
+and an even smaller subset $\varrho\subset\mcI^j$:
 $$
-    \varrho = \bigg\lbrace i \in \argmax_{\bar\mcI_j'\subset\bar\mcI_j}
-\displaystyle\sum_{i\in\bar\mcI'} p_i^j : p_i^j \ge p_k^j \ \forall \ k\ne
+    \varrho = \bigg\lbrace i \in \argmax_{\mcI_j'\subset\mcI_j}
+\displaystyle\sum_{i\in\mcI'} p_i^j : p_i^j \ge p_k^j \ \forall \ k\ne
 i\bigg\rbrace,
@@
 \textbf{Proof:} 
-We have that $\sum_{i\in\bar{\mcI_j}} d_i^j = 
-\sum_{i\in\bar{\mcI}^j} e_i$ from (\ref{quantity}) and (\ref{budget}),
+We have that $\sum_{i\in{\mcI_j}} d_i^j = 
+\sum_{i\in\mcI^j} e_i$ from (\ref{quantity}) and (\ref{budget}),
 i.e. a seller will try and sell all of its data. The remainder of the proof
@@
 
-In order to complete our formulation, we argue that as there is no capacity bottleneck in our network as in
-\cite{lazar} and \cite{semret}, we are able to increase the bid quantity and
-take the maximum in the allocation rule. 
-We propose a \emph{data allocation rule}:
 {
-% DATA ALLOCATION RULE
-\proposition{(Data allocation rule)}
-Given an auction of infinitely divisible data $j$, where user $j$ is the
-auctioneer, the data allocation rule is given as,
-\begin{equation}\label{allocation}
-    \bar{a}_i^j(s) = \max_i\big\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
-p_i^j}d_k^j}
-\bar{D}_i^j(p_i^j,s_{-i}^j)\big\rbrace
-\end{equation}
-where $i\in\bar\mcI^j$.
-} 
-\textbf{Proof}:
-Intuitively, this rule indicates that a seller will allocate its data to the
-buyer with the highest demand that can be satisfied (within its budget). 
-(\ref{allocation}) is feasible by (\ref{quantity}) and (\ref{budget}), in that
-$$
-    \displaystyle\sum_{i\in\mcI} a_i(s) \le \displaystyle\sum_{i\in\mcI} e_i(a)
-\le \sum_{j\in\mcI} b^j = \mathcal{D},
-$$
-where $\mathcal{D} = \sum_{j\in\mcI} d^j$ is the total amount data for sale in the secondary market.
-As the buyers ``control" the secondary market via their individual data demands,
-$\forall \ i\in\mcI$,
-\begin{align*}
-    a_i(s) &\le e_i(a) \le d_i \\
-    c_i(s) &\le p_id_i.
-\end{align*}
-where $c_i(s)$ remains unchanged from \cite{lazar}. (FINISH!)
+\theorem{(Data Nash Equilibrium)}
+Using the rules of the data auction mechanism, the secondary market described in \cite{zheng} converges to a $\epsilon$-Nash equilibrium.
+}\\
+\textbf{Proof:}
+We will prove the theorem by asserting that our formulation upholds the VGC
+mechanism that is given in the properties of modern PSP. Namely,
+\begin{itemize}
+    \item Incentive compatibility
+    \item Efficiency 
+    \item Convergence
+\end{itemize}
 
@@
 fraction of user $j$'s data aquired by user $i$. In order to form the
-distributed auction, we set $\vs_i^j=1$ for all sellers who offer the enough data to meet the needs required by buyer $i$,
-$\vs_i^j = 0$ for all other $j$. We intend to show that this does not affect thier valuation, and
-indeed, in this network setting, results in a shared network optima (a
-global optimum). The formulation is inversely analogous to the thinnest allocation route for
+distributed auction, we set $1$ if seller $j$ has enough data to
+satisfy $i$'s demand, and $\vs_i^j=d_i$ otherwise. We intend to show that this
+does not affect thier valuation, and indeed, in this network setting, results in a shared network optima (a
+global optimum). The formulation is analogous to the thinnest allocation route for
 bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
@@
 \cite{semret} as ``a simple buyer at a single resource element", in other
-words, (\ref{valuation}) where $i$ is fixed (MAKES SENSE?).
+words, (\ref{valuation}) where $j$ is fixed (MAKES SENSE?).
 
@@
 bid quantities $d_i$ to the level where the opt-out value $e_i$ 
- is the same for each qualifying seller $j \in\bar\mcL_i$. We argue
+ is the same for each qualifying seller $j \in\mcI_i$. We argue
 that without loss of utility, $i$ may choose a seller pool where a minimal subset
@@
 {
-\lemma{(Opt-out buyer coordination)} Let $i\in\mcI$ be a opt-out buyer.
-For any profile $s_i^j = (d_i, p_i)$, let $a^j \equiv a^j(s)$ be the resulting data
+\lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
+Let $i\in\mcI$ be a opt-out buyer.
+For any profile $s_i^j = (d_i, p_i)$, let $a_i \equiv a_i(s)$ be the resulting data
 tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
-(z_i,p_i)$, where for any $j \in \bar\mcL_i$,
+(z_i,p_i)$, where for any $j \in \bar\mcI_i$, where $\bar\mcI_i$ is computed as
+in the buyer strategy,
 $$
-    z_i^j =  \big\lbrack e_i(a)\big\rbrack\vs_i^j
+    z_i^j =  \big\lbrack e_i(a)\big\rbrack
 $$
@@
 }\\
-\textbf{Proof:} (NOTE: DID NOT ADDRESS CLUTTERED NOTATION... DO LATER) We will show that
+\textbf{Proof:} (NOTE: DID NOT ADDRESS CLUTTERED NOTATION... DO LATER) 
+We have, by (\ref{opt-out}), $\forall \ i\in\mcI$, where $j\in\bar\mcI_i$,
 $$
-    u_i(s_i;s_{-i}) \equiv u_i(d_i,p_i) \le u_i(z_i,p_i) \\
+    z_i^j = \frac{a_i^j}{\vs_i^j} = e_i(a) = e_i^{j^*}(a) =
+\frac{a_i^{j^*}}{\vs_i^{j^*}} = z_i^{j^*}.
+$$
+Therefore $a_i^{j^*}(z_i,p_i) = a_i^j(z_i,p_i) = z_i^j$,
+and (\ref{coordination}) is proven.
+In order to determine that $i$ has no loss of utility, we will show that
+$$
+    u_i(d_i,p_i) \le u_i(z_i,p_i). \\
 $$
 \iffalse
+From (\ref{allocation}) and (\ref{coordination}), we have that, $\forall \ j\in \bar\mcI_i$,
 \begin{align*}
-    u_i(d_i,p_i) &\le u_i(z_i,p_i) \\
-   &\equiv \theta_i(a_i((d_i,p_i);s)\vs_i) - c_i(s)\\
-    & \le \theta_i(a_i((z_i,p_i);s_{-i})\vs_i) \\
-    &-c_i((z_i,p_i);s_{-i}).
+    e_i^j(z_i,p_i) &= \bigg\lbrack D^j - \sum_{p_k^j> y}
+d_k^j\bigg\rbrack^+/\vs_i^j \\
 \end{align*}
-\fi
-From (\ref{allocation}), we have that
+$$
+    z_i^j = z_i^{j^*}\le D_i^{j^*}(p_i^{j^*}, s^{j^*}) \le a_i^{j^*}(s) ,
+$$
+as the allocation rule will default to sell to the minimum amount of buyers
+(BAD, CHANGE ALLOCATION RULE?).
 \begin{align*}
@@
     &\frac{z_i^j}{\sum_{k:p_k^j= p_i^j} d_k^j}
-\bar{D}_i^j((z_i^j,p_i^j))\bigg\rbrace
+\bar{D}_i^j((z_i^j,p_i^j))\bigg\rbrace,
 \end{align*}
-and by (\ref{opt-out}), 
-$$
-    z_i^j = e_i(a) = \min_j\big(e_i^j(a), \delta\big).
-$$
-where $i$ chooses the subset of sellers. We address two cases:\\
+\begin{align*}
+    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
+    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
+\end{align*}
+
+So, 
+\begin{align*}
+   &\theta_i(a_i^j((d_i,p_i);s)\vs_i) - \displaystyle\sum_{j\in\bar\mcI_i}c_i^j(s)\\
+    & \le \theta_i(a_i((z_i,p_i);s_{-i})\vs_i) -c_i^j((z_i,p_i);s_{-i})
+\end{align*}
+\fi
+We address two cases:\\
 1. \emph{There exists a seller who can fully satisfy $i$'s demand.} \\
-In this case, $\vert\bar\mcL_i\vert = 1$, and the case is trivial as no
+In this case, $\vert\bar\mcI_i\vert = 1$, and the case is trivial as no
 coordination is necessary for a single bid.\\
 2. \emph{Buyer $i$'s demand can only be satisfied by a minimal subset of sellers.} \\
-Buyer $i$ maintains ordered set $\bar\mcL_i$ where the sellers with the
-largest bid are considered first. It remains to locate the seller $j^*$ where $\bar\mcL_i$ is such that a
+As buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
+largest bid are considered first, the seller $j^*$ defines the subset $\bar\mcI_i$ where a
 coordinated bid is possible. 
-
-Let $n \le I \in \mathcal{Z}^+$ be chosen so that 
-\begin{equation}
-    \displaystyle\sum_{\bar\mcL_i} \frac{\min_j(d^j)}{d_i} =
-\displaystyle\sum_{\bar\mcL_i} \frac{d^{j^*}}{d_i} = d_i.
-\end{equation} 
-As $\ell_j$ is an ordered set, $i$ is able to choose a minimal subset of sellers
-$\bar\mcL_i \subset \mcL_i$ where a coordinated bid is possible.
-
-(ALSO COULD TAKE THE MIN AND USE ALL SELLERS... IS THIS BETTER?)
-Now, $\forall \ j \in\bar\mcL_i$,
+% FALSE!
+\iffalse
+Now, $\forall \ j \in\bar\mcI_i$,
 $$
@@
 and (\ref{coordination}) is proven.
-We have that $e_i^l(a(z_i,p_i)) = a_i^l(z_i,p_i)\vs_i^l
-= e_i(a) \ \forall \ l\ne i$, and so
+\fi
+We have that $e_i^j(a(z_i,p_i)) = a_i^{j^*}(z_i,p_i)/\vs_i^{j^*} =
+e_i^{j^*}(a(z_i,p_i)) = e_i(a) \ \forall \ j$, and so
 $\theta_i\circ e_i(a(z_i, p_i)) = \theta_i\circ e_i(a)$. 
@@
 \begin{align*}
-    u_i(z_i,p_i) - u_i &= \theta_i\circ e_i(z_i,p_i)  - \displaystyle\sum_{l\ne
-i}c_i(z_i,p_i) \\
-    &- \theta_i(a_i(d_i,p_i)) - \displaystyle\sum_{l\ne i} c_i^l(s) \\
+    u_i(z_i,p_i) &- u_i = \theta_i\circ e_i^j(z_i,p_i)  -c_i^j(z_i,p_i) \\
+    &- \theta_i(a_i^j(d_i,p_i)) - \displaystyle\sum_{j} c_i^j(s) \\
 \end{align*}
-(CHECK MATH!) Now, by definition of
-the seller's valuation, $\forall \ l$,
+(CHECK MATH!) Therefore, by definition of
+the seller's valuation, $\forall \ j$,
 \begin{align*}
-    &=\displaystyle\sum_{l\ne i}\int_{a_i^l(z_i,p_i)}^{a_i^l} f^l(d_l^l
--z) \ dz \\
-    e_i(a) &\ge e_i^l(a) \Rightarrow z_i^l\vs_i^l \ge a_i^l\vs_i^l \\
-    &\Rightarrow a_i^l \le z_i^l\le a_i^l(z_i,p_i),
+    u_i(z_i,p_i) &- u_i \\
+    &=\displaystyle\sum_{j}\int_{a_i^j(z_i,p_i)}^{a_i^j} \theta^j(d^j
+-z) \ dz,
 \end{align*}
-Additionally, we comment that $x_i$ is feasible, i.e. $\sum_l c_i^l(s) \le b_i$
-as the factor $\vs$ separates the auction space, restricting the number of bids
-a user may place. In effect, we are using the buyer demand
-to partition the auction space, thereby optimizing the message space for the
-ISP, and providing an (BAD, DOESN'T MATTER) optimal market space to host the buyers and sellers based
-on their type. 
-(....AND!?) 
-The rest of the proof follows as in \cite{semret}.
-The idea of buyer coordination follows from \cite{lazar} (FINISH!)
+and so $\theta^j\ge 0 \Rightarrow u_i(z_i,p_i) - u_i \ge 0$. (In fact, is equal to
+zero). (EEK!)\\
+Additionally, we comment that $x_i$ is feasible, i.e. $\sum_j c_i^j(s) \le b_i$
+as $\sum_i d_i^{j^*}/\vs_i^j$ does not increase the demand of seller $i$.
+In effect, we are using the buyer demand
+to partition the auction space, thereby (NOT TRUE WITH COORDINATED BIDS? CAN I
+PROVE IT?) optimizing the message space for the
+ISP, and providing an optimal market space to host the buyers and sellers based
+on their type. \\
+(ALSO COULD TAKE THE MIN AND USE ALL SELLERS... OR STICK WITH ALLOWING DEMAND
+$d_i=d^j$, IS THIS BETTER?)
 
-In the case where no seller is offering enough data to satisfy a single user's
-demand, the user is forced to submit bids to multiple sellers. According to (\ref{demand}) we claim that there is an incentive for the seller to
+(WHY AM I BRINGING THIS UP?) According to
+(\ref{allocation}) we claim that there is an incentive for the seller to
 submit fractional bids (i.e. bid a fraction of thier leftover data) in the hopes
@@
 \lemma{(Seller incentive)}\label{incentive}
-Let $j$ be an opt-out buyer with fixed bid $(d^j,c^j)$. Then, in order to change the
+Let $j$ be a seller with fixed bid $(d^j,c^j)$. Then, in order to change the
 quantity $d^j$ we must have, for some $k \in \mcI$,
@@
 We will demonstrate a proof by cases:\\
-(NEED TO THINK, I ONLY SAID THERE IS AN INCENTIVE TO DECREASE... STILL NEED
-BOTH CASES THOUGH)\\
-The idea is that as the sellers are decreasing their bid quantities, the buyers
-are increasing them so that the result is distributed collaboration, resulting
-in an inherent network matching $\rightarrow$ market equilibrium.
-\emph{Case 1:} Suppose decrease $d$ (NEED PRICE? SHOULD NOT CHANGE FROM THEORY
-BUT INCLUDE THIS FACT)\\
+(NEED TO THINK...)\\
+The idea is that as the sellers are decreasing their bid quantities, so as to
+increase the subset of buyers where seller $j=j^*$. \\
+\emph{Case 1:} Suppose decrease $d$ (NEED PRICE HERE!) \\
 \emph{Case 2:} Increase $d$\\
@@
 
+We proceed to claim that the optimality of truth-telling holds in our
+formulation. It turns out that the optimal strategy is very
+similar to that of a single resource user. (MOVE) But instead of searching directly for
+the optimal quantity, the seller finds the optimal opt-out buyer $i$ , which is
+the largest one such that the marginal value is just greater than the market price.
+The role of the market price is played by the sum of the market prices at the
+different auctions, weighted by the data provisioning vector values. The actual bids are
+obtained by transforming the opt-out buyer's strategy back into the
+corresponding quantities to bid. As with a single resource,
+truth-telling is optimal for the buyer, i.e. in each auction, the buyer sets
+the bid price to the marginal value.
+% INCENTIVE COMPATIBILITY
 {
-\proposition{(Network incentive compatibility)}
-(DOES THIS PROOF EVEN CHANGE? NEED TO START WORKING IT OUT)
+\proposition{(Network incentive compatibility)}\label{incentivecompatibility}
 Let $i\in\mcI$ be an opt-out buyer, and fix all other users' bids
-$s_{-i}$, as well as the sellers' bids $s_i^i$ (so $a^i$ is fixed). \\
+$s_{-i}$, as well as the sellers' bids $s^j$ (so $a^j$ is fixed). \\
 Let 
 \begin{align}
-    z_i &= \sup\bigg\lbrace h\ge 0 : \\
-& \theta_i(h) > \displaystyle\sum_{j\ne i}
-P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j\bigg\rbrace, 
+\begin{split}
+    z_i &= \sup\bigg\lbrace h\ge 0 : 
+ {\theta_i}'(h) > \bar{P}_i^j(h)\bigg\rbrace, 
+\end{split}\\
+\begin{split}
+    \chi_i &= \sup\bigg\lbrace h\ge 0: 
+\displaystyle\int_0^h 
+    \bar{P}_i(h) \ dh \le b_i\bigg\rbrace,
+\end{split}
 \end{align}
-\begin{align}\label{price}
-    \psi_i &= \sup\bigg\lbrace h\ge 0: \\
-&\displaystyle\int_0^h \displaystyle\sum_{j\ne i}
-P_i^j\big((h-a_j^i)\vs_i^j\big)\vs^j \ dh \le b_i\bigg\rbrace,
-\end{align}
-$e = \max(z_i, \psi_i - \epsilon / \theta_i'(0))^+$, and for each $j\ne i$, 
+$e = \min(z_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
+\bar\mcI_i$, 
 $$
-    v_i^j = (e - a_j^i)\vs_i^j
+    v_i^j = e = v_i^{j^*}
 $$
@@
 $$
-    w_i^j = \vs_i^j\theta_i'(e).
+    w_i^j = w_i^{j^*} = \theta_i'(e).
 $$
@@
 } \\ \\
-\textbf{Proof:} First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
-and $\forall j$, $P_i^j$ is non-decreasing, \ref{price} implies $\theta_i'(e) >
-\sum_{j\ne i} P_i^j(v_i^j)\vs_i^j$, and so $\forall j\ne i$,
+\textbf{Proof:} For ease of notation, we may set assume that $j=j^*$ in our
+analysis. First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
+and $\forall j$, $P_i^j$ is non-decreasing, (\ref{dataprice}) implies
+$\theta_i'(e) >\sum_j P_i^j(v_i^j)/\vs_i^j$, due to $e$ being supremum, i.e.
+greater than the marginal value, same as in \cite{semret}. This,
+along with $i$'s strategy where $\vs_i^j = \vs_i^{j^*}$ for each
+$j\in\bar\mcI_i$, gives $\forall \ y,z \ge 0$,
+\begin{align*}
+    \displaystyle\sum_{j} y &> \bar{P_i}(z,s_{-i}) \\
+    &\Rightarrow y > P_i^j(z,s_{-i})/\vs_i^j\\
+    &\Rightarrow
+    z \le D_i^j(y,s_{-i})/\vs_i^j.
+\end{align*}
+Therefore, $\forall j \in\bar\mcI_i$, 
+\begin{align}
+\begin{split}
+    w_i^j & > {P}_i^j(v_i^j)/\vs_i^j \\
+    &\Rightarrow {D}_i^j = \frac{\lbrack d^j - d^j(w_i^j)\rbrack}{\vs_i^j}.
+\end{split}
+\end{align}
+Now, let $y_i = {\theta_i}'(z_i)$ and suppose $z_i = 0$, then $v_i=0 \Rightarrow
+a_i(t_i; s_{-i})=0$ and $i$'s coordinated bids (Lemma \ref{coordinationlemma})
+gives $\bar{D}_i(0,s_{-i}) =0$. 
+By choice of usage utility function $\theta$,
+$$
+w_i = {\theta_i}'(v_i) =\sigma v_i^{-\alpha} >  \sigma
+z_i^{-\alpha} = {\theta_i}'(z_i) = y_i,
+$$
+and since $D_i^j$ is non-decreasing, $D_i^j(y_i,s_{-i}) \ge z_i \ge v_i$.
+Thus, by (\ref{allocation})
+\begin{align*}
+    a_i^j(z_i,p_i) &= \max_i\bigg\lbrace z_i^j, \\
+    &\frac{z_i^j}{\sum_{k:p_k^j= p_i^j} d_k^j}
+\bar{D}_i^j((z_i^j,p_i^j))\bigg\rbrace,
+\end{align*}
+\begin{align*}
+    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
+    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
+\end{align*}
+\begin{align*}
+    \Rightarrow & a_i^j(t_i; s_{-i}) = v_i^j\vs_i^j \\
+    \Rightarrow & e_i^j \circ a(t_i;s_{-i}) = e.
+\end{align*}
+Therefore,
+\begin{align*}
+    u_i(t_i;s_{-i}) &= \displaystyle\int_0^\epsilon {\theta_i}'(\eta) \ d\eta -
+\sum_j \int_0^{v_i^j} P_i^j(z) \ dz \\
+    &= \int_0^\epsilon {\theta_i}'(\eta) \ d\eta - \sum_j\int_0^\epsilon
+P_i^j(\eta/\vs_i^j)/\vs_i^j \ d\eta.
+\end{align*}
+
+Now suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i(s_i;s_{-i}) > u_i(t_i;
+s_{-i}) + \epsilon$. Let $\xi = \min_k e_i^k\circ a_i^k(s)$, and $\forall \ j,
+\zeta_i^j = \xi\vs_i^j$ and $s_{i^*} = (\zeta_i,p_i)$. Then from
+(\ref{coordination}), $a_i^j(s_{i^*}; s_{-i}) = \zeta_i^j$, therefore
+\begin{align*}
+    u_i(s_{i^*};s_{-i}) = \displaystyle\int_0^\xi {\theta_i}'(\eta)\ d\eta -
+\sum_j\int_0^\xi P_i^j(\eta/\vs_i^j)/\vs_i^j \ d\eta.
+\end{align*}
+By Lemma \ref{coordinationlemma}, $u_i(s_{i^*}, s_{-i}) > u_i(t_i; s_{-i}) +
+\epsilon$, which is equivalent to 
+$$
+    \int_\epsilon^\xi {\theta_i}'(\eta) \ d\eta - \sum_j\int_\epsilon^\xi
+P_i^j(\eta/\vs_i^j)/\vs_i^j \ d\eta > \epsilon.
+$$
+(DO I NEED THE CONTRADICTION? YES TO SHOW $\ge 0$)
+
+We address the case where $e=\chi_i$, that is, the seller $j^*$'s data price is
+equal to the budget of buyer $i$ under the strategy given in
+(\ref{opt-out}), similarly to \cite{semret}, in this case any bid $s_{i^*}$
+where $u_i(s_{i^*}) > u_i(t_i)$ is not feasible, as the buyer would go over its
+budget.
+
+Finally, suppose that $j^* = I$, that is, $\bar\mcI_i = \mcI$. 
+In this case, if $u_i(s_{i^*}) > u_i(t_i)$, then
+the demand cannot be satisfied by the sellers and the bid is not feasible.
 

### 2018-04-18 Old/paper_mod_save4.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 Old/paper_mod_save3.tex
@@
 bids for that element only. In this work, the proposed mechanism allows sellers submit bids to buyers
-directly; there is no entity that holds a global market knowledge.
+directly; there is no entity that holds a global maret knowledge.
 
@@
 which means the maximum available quantity at a bid price of $y$ given
-$s_{−i}$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
+$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
 as:
@@
 
-We will introduce a player type called an \emph{opt-out buyer} in order to perform our analysis. The
+We will introduce a user type called an \emph{opt-out buyer} in order to perform our analysis. The
 opt-out buyer restricts its pool of sellers by only submitting bids to sellers
@@
 A GAP VARIABLE?), similar to \cite{zheng}. 
-We intend to show that the pricing model (\ref{price}) is sufficient to attain the desirable
+In addition, we define a generic
+\textbf{data-provisioning vector} $\vs$, held the user as part of its type
+along with its valuation and budget, . 
+We intend to show that the pricing model (\ref{dataprice}) is sufficient to attain the desirable
 property of truthfullness through incentive compatibility. (MOVE THIS? NEED OWN
@@
 data. We use the $\alpha$-fair utility functions \cite{zheng} to model the
-usage utility from consuming $d$ amount of data:
-\begin{equation}
+valuation from consuming $d$ amount of data:
+% BUYER VALUATION
+\begin{equation}\label{buyervaluation}
     \theta(d) = \frac{\sigma d^{1-\alpha}}{1-\alpha}
@@
 simplicity of notation, so $\bar{a}_i = a_i$. We may now define the user's utitlity function as
-\begin{equation}\label{utility}
+\begin{equation}\label{buyerutility}
     u_i = \theta_i(a_i(s)) - c_i(s).
@@
 the user has the exact amout of data they require, or that seller $j$ does not have
-enough data to satisfy the buyer's demand, and we simply set $s^j_i = (0, 0)$.
+enough data to satisfy the buyers' demand, and we simply set $s^j_i = (0, 0)$.
 A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
@@
 user $i$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
-allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$ (THIS MAY
-NEED A SLIGHT MODIFICATION), and $c^j_i \le  p^j_i d_i^j$.
+allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
+(I WANT TO EXPERIMENT WITH OTHER ALLOCATION RULES!, i.e. PARTIAL ALLOCATION IN
+GOOGLE WHITEPAPER)
 
@@
 We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
-function as in \cite{semret},
+function,
 \begin{equation}\label{opt-utility}
-    u_i = \theta_i \circ e_i(a) - \displaystyle\sum_j c_i^j,
+    u_i = \theta_i \circ e_i(a) - c_i,
 \end{equation}
 where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation 
-(???? BAD) that user
-$i$ finds a matching seller $j$. An opt-out buyer's valuation
+(EXPECTATION??? BAD) that user
+$i$ finds a matching seller(s) $\lbrace j \rbrace$. An opt-out buyers' valuation
 depends only on a scalar $e_i(a)$ which is a function of the
@@
 so $\mcI_i \subset \mcI$ is the
-minimal subset of sellers (which may be empty or unary) whose data can sum to \emph{exactly}
+minimal subset of sellers (which may be empty or unary) whose data is
+sufficient to sum to \emph{exactly}
 (DO I WANT EXACTLY? ... YES) the demand $d_i$.
@@
 as the maximum subset of buyers that $j$ can satisfy with budget
-$\bar{b}^j$. The set $\beta^j$ is computed by $j$ before each auction (???),
+$\bar{b}^j$. The set $\beta^j$ is computed by $j$ before each auction (??? or
+bid iteration),
 i.e., for $\tau >0$, 
@@
 
-Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, scaled
+% MECHANISM
+\subsection{Data Auction Mechanism}
+We may now proceed to formally define the PSP auction as a composition of the
+buyers and sellers in the secondary market, along with their respective
+strategies. We begin by defining the opt-out buyers' strategy.
+
+Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, given as
+the $\alpha$-fair utility in (\ref{buyervaluation}), scaled
 by a function of quantity desired from the market. 
-We define, in addition to the valuation and budget of user $i$, a generic
+We define, in addition to the valuation and budget of buyer $i$, a generic
 \textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
@@
 and let $j^* \in \ell_i$ be the seller such that
-$j^* = n \le I \in \mathcal{Z}^+$ results in a subset $\bar\mcI_i\subset\mcI_i$ where 
+$j^* = n \le I \in \mathcal{Z}^+$ results in a subset $\bar\mcI_i\subset\mcI$ where 
 \begin{equation}\label{coordinate}
@@
 Then, we have that $e_i$
-is the optimal feasible strategy for buyer $i$.
+is an optimal feasible strategy for buyer $i$.
 }\\
 \textbf{Proof:}
-In the case that there exists a seller who can completely satisfy a buyer's
+In the case that there exists a seller who can completely satisfy a buyers'
 demand, $j^*=1$, and (\ref{coordinate}) holds. If such a buyer does not exist,
 as the set $\ell_i$ is an ordered set, $i$ may discover seller
-$j^*$ by computing $\ell_i$ iteratively. In the case that $d_i = \mathcal{D} =
-\sum_{j\in\mcI}d^j$, then $j^* = I$ and the buyer will submit bids to all
-sellers. If $d_i>I$, then the buyer (??? THINKING $\mcI_i$ BETTER, ALSO ADDRESS
-FEASIBLE AND OPTIMAL!)
-
-The natural utility is the potential
-profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
-potential revenue from the sale of data composed with opt-out value
-$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
-$\mcI^j$. Note that we have chosen to omit the original cost of the data
-paid to the ISP, as a discussion of mobile data plans is outside the scope of this
-paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
-participate in any auction. Additionally, as the
+$j^*$ by computing $\ell_i$ iteratively. In the case that $d_i >
+\sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
+infeasible. (WHY WE NEED A NEW RULE ... THE PARTIAL ALLOCATION RULE, ALREADY PROVEN FEASIBLE
+AND TRUTHFUL)
+Additionally, as the
 value of the secondary market is its ability to fufill the data demands of its
@@
 valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
-and the form of (\ref{opt-out}) is justified.
+and the form of (\ref{opt-out}) is justified. We note that $\mcI_i$ is not the
+possible minimum subset $\in \mcI$, but is the minimal subset where a
+coordinated bid is possible.
 
-% MECHANISM
-\subsection{Data Auction Mechanism}
-We may now proceed to formally define the PSP auction.
-The market price function (MPF) for a user in the secondary market
+The market price function (MPF) for a buyer in the secondary market
 can now be described as follows:
@@
 \begin{split}
-    \bar{P}_i&(z, s_i) = P_i(z,s_i)\circ e_i \\
-    &=\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
-s_{-i}^j)/\vs_i^j \\
+    \bar{P}_i&(z, s_i) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
+s_{-i}^j) \\
     &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg)/\vs_i^j,\\
+    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
 \end{split}
@@
 \begin{align}
-\begin{split}
+\begin{split}\label{datacomposed}
     \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
+    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
 \end{split}
 \end{align}
-and is interpreted as the minimum bid price, as in \cite{lazar}.
+and is interpreted as the aggragate of minimum bid prices of buyer $i$ for bids
+over $\mcI_i$ given an opponent profile $s_{-i}$.
 The inverse function
@@
 $\bar{D}_i$ is defined as
-\begin{align}
+\begin{align}\label{datapriceinverse}
 \begin{split}
-    \bar{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
-\sum_{j\in\mcI_i} \bar{D}_i^j \bigg) : \\
-    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace.
+    \bar{D}_i(y, s_i) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
+\bar{D}_i^j \big) : \\
+    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
 \end{split}
@@
 We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
-$\mcI_i$ at a bid price of $y$ given $s_{i}$.
+$\mcI_i$ at a bid price of $y$ given $s_{-i}$. In this expression, we again note that
+the price is an aggragation of the \emph{individual} prices of the buyers. As it is
+possible that $\mcI_i \ne \mcI^j$, the reserve prices of the individual sellers
+may vary (THIS DOES NOT GO WITH PSP THEORY!)
 % DATA ALLOCATION RULE
-The data allocation rule is given as,
+The data allocation rule for seller $j$ is given as,
 \begin{equation}\label{dataallocation}
-    \bar{a}_i^j(s) = \min_{j\in\mcI_i}\big\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
+    \bar{a}_i^j(s) = \min_{j\in\mcI_i}\bigg\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
 p_i^j}d_k^j}
-\bar{D}_i^j(p_i^j,s_{-i}^j)\big\rbrace
+\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace
 \end{equation}
 with cost,
-\begin{align}\label{dataprice}
+\begin{align}\label{datacost}
 \begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI_i}\bigg\lbrack\sum_{j\in\mcI_i}
-\frac{p^j}{\vs_i^j} \bigg(\bar{a}_j(0; s_{-i}^j)\\
-    &-\bar{a}_j(s_i^j;s_{-i}^j)\bigg) \bigg\rbrack,
+    \bar{c}_i^j(s) &= 
+p^j \bigg(\bar{a}_j(0; s_{-i}^j)
+    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg) ,
 \end{split}
@@
 where $\mcI_i$ is chosen as described in the buyer strategy.
-The rules defined above describe the mechanism for the PSP auction given in
-\cite{lazar}, however, in order to apply PSP to the data-sharing secondary market described in
-\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
-data-sharing model, it is not necessary to bid on a minimal route, and that our
-formulation not only holds the desired VCG qualities, but minimizes the message
-space and auction duration, resulting in a faster convergence time than the
-classic throughput problem (EEEK!).
 
@@
     f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z \ \forall \ i \in \mcI_j\big\rbrace.
+        \rho_i^j(y) \ge z \ \forall \ i \in \mcI^j\big\rbrace.
 \end{equation}
@@
 which it could be sold to any buyer $i\in \mcI^j$.
-Now, in order to derive the seller's valuation, we have the following,
+Now, in order to derive the sellers' valuation, we have the following,
 {
@@
 \proposition{(Seller constraints)}\label{constraints}
-Let $j\in\mcI_i$ be a seller, and fix its allocation to $(a^j,c^j)$.
+Let $j\in\mcI_i$ be a seller with data (budget) $b^j$.
 Formalizing the quantity threshold, the seller must satisfy the quantity
@@
 
-We may now define the seller $j$'s valuation. 
+We may now define the seller $j$'s valuation (potential). 
 {
-\proposition{(Seller valuation)}
+\proposition{(Seller valuation)}\label{sellervaluation}
 % SELLER VALUATION
@@
 \end{equation}
-defining the function
-$$
-\mu_i^j = \frac{1}{\sum_{k\in\mcI_j:p_k^j=p_i^j} k},
-$$
-and an even smaller subset $\varrho\subset\mcI^j$:
-$$
-    \varrho = \bigg\lbrace i \in \argmax_{\mcI_j'\subset\mcI_j}
-\displaystyle\sum_{i\in\mcI'} p_i^j : p_i^j \ge p_k^j \ \forall \ k\ne
-i\bigg\rbrace,
-$$
 it follows that 
 \begin{equation}\label{valuation}
-    \theta^j = \displaystyle\sum_{i\in\varrho}
- \int_0^{e_i^j(a)} \mu_i^j f^j(z) \ dz.
+    \theta^j = \displaystyle\sum_{i\in\mcI^j}
+ \int_0^{e_i^j(a)} f^j(z) \ dz.
 \end{equation}
 }
-(COULD SIMPLIFY A LOT..)
 \textbf{Proof:} 
-We have that $\sum_{i\in{\mcI_j}} d_i^j = 
-\sum_{i\in\mcI^j} e_i$ from (\ref{quantity}) and (\ref{budget}),
-i.e. a seller will try and sell all of its data. The remainder of the proof
-follows as in \cite{semret}.
+We assume that a seller will try to maximize profit, and
+so there is an incentive sell all its data, so from Lemma
+\ref{sellervaluation},  $\sum_{i\in{\mcI^j}} d_i^j = 
+\sum_{i\in\mcI^j} e_i$,
+The remainder of the proof follows as in \cite{semret}.
+The sellers' natural utility is the potential
+profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
+potential revenue from the sale of data composed with opt-out value
+$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
+$\mcI^j$. Note that we have chosen to omit the original cost of the data
+paid to the ISP, as a discussion of mobile data plans is outside the scope of this
+paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
+participate in any auction.
 
+We claim that there is an incentive for the seller to
+accept fractional bids (i.e. sell fraction of thier data $d^j$). Reasonably,
+there may not exist a buyer such that $d_i = d^j$, in addition, a seller may accept
+fractional bids in order to
+maximize the revenue gained per unit of data sold over time.
+Finally, in the case that the seller does not know the exact amount of
+leftover data available, then they may only sell enough data to ensure that
+they will not become a buyer while they submit their total data overage to the
+secondary market. (FUTURE WORK?)
+% SELLER INCENTIVE
+{
+\lemma{(Seller incentive)}\label{incentive}
+Let $j$ be a buyer with fixed price $p^j$. Then, in order for $j$ to change its
+quantity $d^j$ we must have, for some $i \in \mcI^j$,
+\begin{equation}
+       p_i^j \ge p^j \qquad \text{and} \qquad d_i^j < d^j.
+\end{equation}
+}
+\textbf{Proof:}
+We will show that if the Lemma holds, then $j$
+(NEED TO THINK... NEED THIS OR FUTURE WORK?)\\
+
+The main contribution of this work is comprised by these rules, which we use to
+describe an auction mechanism inspired by the classic PSP throughput problem. In order to apply PSP to the data-sharing secondary market described in
+\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
+data-sharing model, it is not necessary to bid on a minimal route, and that our
+formulation not only holds the desired VCG qualities, but minimizes the message
+space and auction duration, resulting in a faster convergence time than the
+classic throughput problem (EEEK!).
+
+% DATA NASH EQ
 {
@@
 
-\subsection{Formulation?}
+\subsection{VCG Formulation}
 Consider a user seeking to prevent
@@
 does not affect thier valuation, and indeed, in this network setting, results in a shared network optima (a
-global optimum). The formulation is analogous to the thinnest allocation route for
-bandwidth given in \cite{lazar}. Reasonably, if only a single seller is available, then
+global optimum). The formulation is inspired to the thinnest allocation route for
+bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
+satisfy $i$'s demand, then
 (\ref{opt-utility}) reduces to the original form (\ref{utility}), defined in
-\cite{semret} as ``a simple buyer at a single resource element", in other
-words, (\ref{valuation}) where $j$ is fixed (MAKES SENSE?).
+\cite{semret} as ``a simple buyer at a single resource element".
 
+% VCG ANALYSIS
 \section{VCG Analysis}
@@
 
-% COORDINATION
+% BUYER COORDINATION
 {
@@
 tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
-(z_i,p_i)$, where for any $j \in \bar\mcI_i$, where $\bar\mcI_i$ is computed as
-in the buyer strategy,
+(z_i,p_i)$, where $\bar\mcI_i$ is computed as in the buyer strategy,
 $$
-    z_i^j =  \big\lbrack e_i(a)\big\rbrack
+    z_i^j = e_i(a)
 $$
@@
 \begin{equation}\label{coordination}
-    a_i^j(z_i,p_i) = z_i^j,
+    a_i^j(z_i,p_i) = z_i^{j^*},
 \end{equation}
 }\\
-\textbf{Proof:} (NOTE: DID NOT ADDRESS CLUTTERED NOTATION... DO LATER) 
-We have, by (\ref{opt-out}), $\forall \ i\in\mcI$, where $j\in\bar\mcI_i$,
+\textbf{Proof:}
+As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
+u_i(s_i;s_{-i})$. 
+We have, by (\ref{opt-out}) and (\ref{datacomposed}), $\forall \ j\in\bar\mcI_i$,
+\begin{align*}
+    z_i^{j^*} &= z_i^j = e_i(a) = e_i^{j^*}(a) \\
+    &\le \bigg\lbrack d^{j^*} - \sum_{p_k^j> y}
+d_k^{j^*}\bigg\rbrack^+/\vs_i^{j^*},
+\end{align*}
+and so
 $$
-    z_i^j = \frac{a_i^j}{\vs_i^j} = e_i(a) = e_i^{j^*}(a) =
-\frac{a_i^{j^*}}{\vs_i^{j^*}} = z_i^{j^*}.
+     a_i^j(z_i,p_i) = a_i^{j^*}(z_i,p_i) = z_i^{j^*}= e_i(a).
 $$
-Therefore $a_i^{j^*}(z_i,p_i) = a_i^j(z_i,p_i) = z_i^j$,
-and (\ref{coordination}) is proven.
 In order to determine that $i$ has no loss of utility, we will show that
 $$
-    u_i(d_i,p_i) \le u_i(z_i,p_i). \\
+    u_i(d_i,p_i) \le u_i(z_i,p_i).
 $$
-\iffalse
-From (\ref{allocation}) and (\ref{coordination}), we have that, $\forall \ j\in \bar\mcI_i$,
-\begin{align*}
-    e_i^j(z_i,p_i) &= \bigg\lbrack D^j - \sum_{p_k^j> y}
-d_k^j\bigg\rbrack^+/\vs_i^j \\
-\end{align*}
-$$
-    z_i^j = z_i^{j^*}\le D_i^{j^*}(p_i^{j^*}, s^{j^*}) \le a_i^{j^*}(s) ,
-$$
-as the allocation rule will default to sell to the minimum amount of buyers
-(BAD, CHANGE ALLOCATION RULE?).
-\begin{align*}
-    a_i^j(z_i,p_i) &= \max_i\bigg\lbrace z_i^j, \\
-    &\frac{z_i^j}{\sum_{k:p_k^j= p_i^j} d_k^j}
-\bar{D}_i^j((z_i^j,p_i^j))\bigg\rbrace,
-\end{align*}
-\begin{align*}
-    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
-\end{align*}
-
-So, 
-\begin{align*}
-   &\theta_i(a_i^j((d_i,p_i);s)\vs_i) - \displaystyle\sum_{j\in\bar\mcI_i}c_i^j(s)\\
-    & \le \theta_i(a_i((z_i,p_i);s_{-i})\vs_i) -c_i^j((z_i,p_i);s_{-i})
-\end{align*}
-\fi
 We address two cases:\\
@@
 2. \emph{Buyer $i$'s demand can only be satisfied by a minimal subset of sellers.} \\
-As buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
-largest bid are considered first, the seller $j^*$ defines the subset $\bar\mcI_i$ where a
+Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
+largest bid are considered first, the seller $j^*$ defines the minimal subset $\bar\mcI_i$ where a
 coordinated bid is possible. 
-% FALSE!
-\iffalse
-Now, $\forall \ j \in\bar\mcI_i$,
+From (\ref{dataallocation}) and (\ref{coordination}), we have that, $\forall \ j\in \bar\mcI_i$,
+\begin{align*}
+    e_i^j(z_i,p_i) &= \bigg\lbrack d^j - \sum_{p_k^j> y}
+d_k^j\bigg\rbrack^+/\vs_i^j 
+\end{align*}
+We have $e_i^j(a(z_i,p_i)) = a_i^{j^*}(z_i,p_i)/\vs_i^{j^*} = e_i(a)$, which
+implies that 
 $$
-    z_i^j \le a_i^j(s) \le \bar{D}_i^j((d_i, p_i^j),s^j),
+\theta_i\circ e_i(a(z_i,p_i)) = \theta_i\circ e_i(a).
 $$ 
+Therefore, by the definition of utility (\ref{buyerutility}),
 \begin{align*}
-    z_i^j & =\min_j\big(a_i^j\vs_i^j, \delta\big) \\
-    &= \min_j(a_i^j(z_i,p_i)\vs_i^j,\delta) =  \\
+    \theta_i\circ& e_i(a(z_i,p_i)) - \theta_i(a)) \\
+    &=  c_i^j(s) -c_i^{j^*}(z_i,p_i).
 \end{align*}
-The buyer will bid the minimum of: 1) its data
-requirement, or
-2) The entirety of the sellers offer.
-Using the allocation rule (\ref{allocation}) again, we have
-\begin{align*}
-    a_i^l(z_i,p_i) &= \max\bigg(z_i^l, \\
-\frac{d_i^l}{\sum_{k:p_k=p_i} d_k^l}&\bigg[d_l^l-\displaystyle\sum_{p_k>y,k\ne
-i} d_k^l\bigg]^+\bigg) \\
-    &= z_i \\
-    &= e_i(a) ,
-\end{align*}
-and (\ref{coordination}) is proven.
-\fi
-We have that $e_i^j(a(z_i,p_i)) = a_i^{j^*}(z_i,p_i)/\vs_i^{j^*} =
-e_i^{j^*}(a(z_i,p_i)) = e_i(a) \ \forall \ j$, and so
-$\theta_i\circ e_i(a(z_i, p_i)) = \theta_i\circ e_i(a)$. 
-By the definition of utility,
-\begin{align*}
-    u_i(z_i,p_i) &- u_i = \theta_i\circ e_i^j(z_i,p_i)  -c_i^j(z_i,p_i) \\
-    &- \theta_i(a_i^j(d_i,p_i)) - \displaystyle\sum_{j} c_i^j(s) \\
-\end{align*}
-(CHECK MATH!) Therefore, by definition of
-the seller's valuation, $\forall \ j$,
+Now using the definition of
+the buyers' valuation (\ref{buyervaluation}), we have $\forall \ i \in\mcI$,
 \begin{align*}
     u_i(z_i,p_i) &- u_i \\
-    &=\displaystyle\sum_{j}\int_{a_i^j(z_i,p_i)}^{a_i^j} \theta^j(d^j
--z) \ dz,
+    &=\displaystyle\sum_{\mcI_j}\bigg(\theta_i(a_i^j)-
+\theta_i(a_i^{j^*}(z_i,p_i))\bigg) 
 \end{align*}
-and so $\theta^j\ge 0 \Rightarrow u_i(z_i,p_i) - u_i \ge 0$. (In fact, is equal to
-zero). (EEK!)\\
-Additionally, we comment that $x_i$ is feasible, i.e. $\sum_j c_i^j(s) \le b_i$
-as $\sum_i d_i^{j^*}/\vs_i^j$ does not increase the demand of seller $i$.
+Now, from (\ref{dataallocation}), $\forall \ j\in\mcI_i$, $a_i(z_i,p_i) \le
+z_i^j \le a_i^j$ and $\theta_i\ge 0 \Rightarrow u_i(z_i,p_i) - u_i \ge 0,
+\ \forall \ i\in \mcI$, as is shown by the definition of the buyers' utility,
+(CAN USE THIS! VERY STRONG)
+$$
+     \sum_{\mcI_j}\bigg(\frac{\sigma (a_i^j)^{1-\alpha}}{1-\alpha}
+-\frac{\sigma (a_i^j(z_i,p_i))^{1-\alpha}}{1-\alpha}\bigg)
+     \ge 0.
+$$
+
+Additionally, since (\ref{opt-out}) does
+not increase the demand of seller $i$, $\sum_j c_i^j(s) \le b_i$, i.e. $x_i$ is feasible.
 In effect, we are using the buyer demand
 to partition the auction space, thereby (NOT TRUE WITH COORDINATED BIDS? CAN I
-PROVE IT?) optimizing the message space for the
+PROVE IT?->) optimizing the message space for the
 ISP, and providing an optimal market space to host the buyers and sellers based
 on their type. \\
-(ALSO COULD TAKE THE MIN AND USE ALL SELLERS... OR STICK WITH ALLOWING DEMAND
-$d_i=d^j$, IS THIS BETTER?)
-
-(WHY AM I BRINGING THIS UP?) According to
-(\ref{allocation}) we claim that there is an incentive for the seller to
-submit fractional bids (i.e. bid a fraction of thier leftover data) in the hopes
-of maximizing the auction price in its
-\emph{local} auction by including more sellers. To
-formalize this we have the following lemma. (WILL NEED THIS LATER? BAD?)
-{
-\lemma{(Seller incentive)}\label{incentive}
-Let $j$ be a seller with fixed bid $(d^j,c^j)$. Then, in order to change the
-quantity $d^j$ we must have, for some $k \in \mcI$,
-\begin{equation}
-       p_k^j \ge \max_i c_i^j\vs_i^j.
-\end{equation}
-}
-\textbf{Proof:}
-We will demonstrate a proof by cases:\\
-(NEED TO THINK...)\\
-The idea is that as the sellers are decreasing their bid quantities, so as to
-increase the subset of buyers where seller $j=j^*$. \\
-\emph{Case 1:} Suppose decrease $d$ (NEED PRICE HERE!) \\
-\emph{Case 2:} Increase $d$\\
-
-(DOES THIS BELONG HERE?)
-In addition, in the case that the seller does not know the exact amount of
-leftover data available, then they may only sell enough data to ensure that
-they will not become a buyer. (FUTURE WORK?)
+(ALSO COULD TAKE THE MIN AND USE ALL SELLERS... OR CHANGE ALLOCATION RULE AND
+NOT HAVE COORDINATION?)
 
 We proceed to claim that the optimality of truth-telling holds in our
-formulation. It turns out that the optimal strategy is very
-similar to that of a single resource user. (MOVE) But instead of searching directly for
-the optimal quantity, the seller finds the optimal opt-out buyer $i$ , which is
-the largest one such that the marginal value is just greater than the market price.
+formulation, where the market functions as a hybrid of \cite{semret} and
+\cite{zheng}. The seller
+finds the optimal opt-out buyer $i$ , which is the buyer with the largest demand such that the marginal value is greater than the market price.
 The role of the market price is played by the sum of the market prices at the
 different auctions, weighted by the data provisioning vector values. The actual bids are
-obtained by transforming the opt-out buyer's strategy back into the
+obtained by transforming the opt-out buyers' strategy back into the
 corresponding quantities to bid. As with a single resource,
@@
 the bid price to the marginal value.
-% INCENTIVE COMPATIBILITY
+% BUYER INCENTIVE COMPATIBILITY
 {
-\proposition{(Network incentive compatibility)}\label{incentivecompatibility}
-Let $i\in\mcI$ be an opt-out buyer, and fix all other users' bids
-$s_{-i}$, as well as the sellers' bids $s^j$ (so $a^j$ is fixed). \\
+\proposition{(Buyer incentive compatibility)}\label{buyerincentivecompatibility}
+Let $i\in\mcI$ be an opt-out buyer, and fix all other buyers' bids
+$s_{-i}$, as well as the sellers' bids $s^j$ (so $a_i$ is fixed). \\
 Let 
@@
 } \\ \\
-\textbf{Proof:} For ease of notation, we may set assume that $j=j^*$ in our
-analysis. First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
-and $\forall j$, $P_i^j$ is non-decreasing, (\ref{dataprice}) implies
-$\theta_i'(e) >\sum_j P_i^j(v_i^j)/\vs_i^j$, due to $e$ being supremum, i.e.
+\textbf{Proof:} For ease of notation, we may assume that bid
+$s_i^j=s_i^{j^*}$ and that each $j\in\bar\mcI_i$.
+First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
+and, $P_i^j$ is non-decreasing, (\ref{dataprice}) implies
+$\theta_i'(e) >\sum_j P_i^j(v_i^j)$, due to $e$ being supremum, i.e.
 greater than the marginal value, same as in \cite{semret}. This,
-along with $i$'s strategy where $\vs_i^j = \vs_i^{j^*}$ for each
-$j\in\bar\mcI_i$, gives $\forall \ y,z \ge 0$,
+along with $i$'s strategy, gives $\forall \ y,z \ge 0$,
 \begin{align*}
     \displaystyle\sum_{j} y &> \bar{P_i}(z,s_{-i}) \\
-    &\Rightarrow y > P_i^j(z,s_{-i})/\vs_i^j\\
+    &\Rightarrow y > P_i^j(z,s_{-i})\\
     &\Rightarrow
-    z \le D_i^j(y,s_{-i})/\vs_i^j.
+    z \le D_i^j(y,s_{-i})/\vs_i^j,
 \end{align*}
-Therefore, $\forall j \in\bar\mcI_i$, 
-\begin{align}
+and so,
+\begin{align}\label{figureout}
 \begin{split}
-    w_i^j & > {P}_i^j(v_i^j)/\vs_i^j \\
+    w_i^j & > {P}_i^j(v_i^j) \\
     &\Rightarrow {D}_i^j = \frac{\lbrack d^j - d^j(w_i^j)\rbrack}{\vs_i^j}.
@@
 gives $\bar{D}_i(0,s_{-i}) =0$. 
-By choice of usage utility function $\theta$,
+By choice of $i$'s valuation function $\theta$,
 $$
@@
 and since $D_i^j$ is non-decreasing, $D_i^j(y_i,s_{-i}) \ge z_i \ge v_i$.
-Thus, by (\ref{allocation})
+Thus, by (\ref{dataallocation}) and (\ref{figureout}),
 \begin{align*}
-    a_i^j(z_i,p_i) &= \max_i\bigg\lbrace z_i^j, \\
-    &\frac{z_i^j}{\sum_{k:p_k^j= p_i^j} d_k^j}
-\bar{D}_i^j((z_i^j,p_i^j))\bigg\rbrace,
-\end{align*}
-\begin{align*}
-    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
-\end{align*}
-\begin{align*}
-    \Rightarrow & a_i^j(t_i; s_{-i}) = v_i^j\vs_i^j \\
-    \Rightarrow & e_i^j \circ a(t_i;s_{-i}) = e.
+    a_i^j(t_i; s_{-i}) = v_i^j \\
+    e_i^j \circ a(t_i;s_{-i}) = e.
 \end{align*}
@@
 \begin{align*}
-    u_i(t_i;s_{-i}) &= \displaystyle\int_0^\epsilon {\theta_i}'(\eta) \ d\eta -
+    &\qquad u_i(t_i;s_{-i}) \\
+    &= \displaystyle\int_0^\epsilon {\theta_i}'(\eta) \ d\eta -
 \sum_j \int_0^{v_i^j} P_i^j(z) \ dz \\
     &= \int_0^\epsilon {\theta_i}'(\eta) \ d\eta - \sum_j\int_0^\epsilon
-P_i^j(\eta/\vs_i^j)/\vs_i^j \ d\eta.
+P_i^j(\eta/\vs_i^j) \ d\eta.
 \end{align*}
@@
 s_{-i}) + \epsilon$. Let $\xi = \min_k e_i^k\circ a_i^k(s)$, and $\forall \ j,
-\zeta_i^j = \xi\vs_i^j$ and $s_{i^*} = (\zeta_i,p_i)$. Then from
+\zeta_i^j = \xi/\vs_i^j$ and $s_{i^*} = (\zeta_i,p_i)$. Then from
 (\ref{coordination}), $a_i^j(s_{i^*}; s_{-i}) = \zeta_i^j$, therefore
 \begin{align*}
-    u_i(s_{i^*};s_{-i}) = \displaystyle\int_0^\xi {\theta_i}'(\eta)\ d\eta -
-\sum_j\int_0^\xi P_i^j(\eta/\vs_i^j)/\vs_i^j \ d\eta.
+    &\qquad u_i(s_{i^*};s_{-i}) \\
+    &= \displaystyle\int_0^\xi {\theta_i}'(\eta)\ d\eta -\sum_j\int_0^\xi P_i^j(\eta/\vs_i^j) \ d\eta.
 \end{align*}
@@
 $$
-    \int_\epsilon^\xi {\theta_i}'(\eta) \ d\eta - \sum_j\int_\epsilon^\xi
-P_i^j(\eta/\vs_i^j)/\vs_i^j \ d\eta > \epsilon.
+    \int_\epsilon^\xi {\theta_i}'(\eta) \ d\eta - \sum_j\int_0^\xi
+P_i^j(\eta/\vs_i^j) \ d\eta > \epsilon.
 $$
-(DO I NEED THE CONTRADICTION? YES TO SHOW $\ge 0$)
+The rest of the calculation follows as in \cite{semret} with the modified
+framework, i.e. both $\bar\epsilon = \epsilon + \epsilon/{\theta_i}'(0)$ and
+$\xi > \bar\epsilon$ show a contradiction.
+(DO I NEED TO SHOW THE CONTRADICTION?)
 
@@
 
+We proceed to examine the strategy of the seller. We argue that if
+truthfullness holds for both buyers and sellers, i.e. $p_i ={\theta_i}' \
+\forall j$ and $p^j = {\theta^j}' \ \forall i$, then there exists a market
+equilibrium.
+
+% SELLER INCENTIVE COMPATIBILITY
+{
+\proposition{(Seller incentive compatibility)}\label{sellerincentivecompatibility}
+Let $j\in\mcI$ be a seller, and fix all buyers' bids
+$s_i$. \\
+(DO I WANT TO DO THIS? DO I THINK IT WILL WORK? OR JUST HAVE SELLERS SPLIT
+THIER DATA LIKE BUYERS... COULD LEAD TO A MORE OPTIMAL SOLUTION THOUGH)
+... since $d^j$ is non-decreasing, as in \cite{lazar}, \cite{semret}
+}
+
+{
+\proposition{(Nash equilibrium)}
+WILL FOLLOW...
+}
 \subsection{Efficiency}
@@
 
+\bibitem{qpsp}
+Clare W. Qu, Peng Jia, and Peter E. Caines,
+\textit{Analysis of a Class of Decentralized Decision Processes: Quantized
+Progressive Second Price Auctions},
+2007 46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
+779-784.
+
 \end{thebibliography}

### 2018-04-18 Old/paper_mod_save5.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 Old/paper_mod_save4.tex
@@
 \usepackage{fancyhdr}
-\usepackage{algorithmicx,algpseudocode}
+\usepackage{algorithmicx}
+\usepackage[noend]{algpseudocode}
 \usepackage{changepage}
@@
 \usepackage{courier}
+\usepackage{algorithm}
 
@@
 \begin{align*}
-    \tilde{P_i}(z, s_i) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
+    \tilde{P_i}(z, s_{-i}) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
 s_{-i}^l)r_i^l \\
@@
 \begin{align*}
-    \tilde{D}_i(y, s_i) &= \sup\bigg\lbrace z\in \bigg( 0,
+    \tilde{D}_i(y, s_{-i}) &= \sup\bigg\lbrace z\in \bigg( 0,
 \min_l\hat{D}_i^l/r_i^l\bigg) : \\
@@
 (EXPECTATION??? BAD) that user
-$i$ finds a matching seller(s) $\lbrace j \rbrace$. An opt-out buyers' valuation
+$i$ finds matching seller(s). An opt-out buyers' valuation
 depends only on a scalar $e_i(a)$ which is a function of the
@@
 is also reasonable to expect that many sellers will come close to using their
-entire data cap, and only sell the fractional overage. Additionally, a buyer
-will most likely not purchase fractional amounts of data, as this would incur
-additional bid fees (...AND). In this case, we
+entire data cap, and only sell the fractional overage. In this case, we
 determine that a buyer must coordinate their bids among multiple sellers. (SAY
-MORE?) To aid in our analysis, we define, for a buyer $i$,
+MORE?) Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, given as
+the $\alpha$-fair utility in (\ref{buyervaluation}), scaled
+by a function of quantity desired from the market. 
+We define, in addition to the valuation and budget of buyer $i$, a generic
+\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type.
+Define, for any allocation $a$,
+% OPT-OUT BUYER STRATEGY
+\begin{equation}\label{opt-out}
+    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
+    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
+\end{equation}
+and define,
 % MIN SET
@@
     \ell_i =\argmax_{\mcI_i' \subset \mcI_i, \vert\mcI_i'\vert =
-n}\sum_{j\in\mcI_i'} d^j,
+n}\sum_{j\in\mcI_i'} d^j.
 $$
+Let $j^* \in \ell_i$ be the seller such that
+$j^* = n \le I \in \mathcal{Z}^+$ results in a minimal subset $\bar\mcI_i\subset\mcI$ where 
+\begin{equation}\label{coordinate}
+    \displaystyle\sum_{\bar\mcI_i} \frac{\min_{j\in\ell_i}(d^j)}{d_i} =
+\displaystyle\sum_{\bar\mcI_i} \frac{d^{j^*}}{d_i} = d_i.
+\end{equation} 
+Now let, 
+\begin{equation}\label{opt-quantity}
+    e_i(a) \triangleq e_i^{j^*}(a).
+\end{equation}
+% EXACTING STRATEGY, SAVE JUST IN CASE
+\iffalse
 where $n\in\mcI$ is chosen so that
@@
 (DO I WANT EXACTLY? ... YES) the demand $d_i$.
-Additionally, we define, for a seller $j$,
-$$
-    \beta^j = \bigg\lbrace i\in\mcI^j: 
-d_i \le \bar{b}^j \bigg\rbrace,
-$$
-and so, similarly to (\ref{minset}),
-% MAX SET
-\begin{equation}\label{maxset}
-    \mcI^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
-\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
-\end{equation}
-as the maximum subset of buyers that $j$ can satisfy with budget
-$\bar{b}^j$. The set $\beta^j$ is computed by $j$ before each auction (??? or
-bid iteration),
-i.e., for $\tau >0$, 
-\begin{align*}
-    \beta^{j(\tau+1)} &= \bigg\lbrace i\in\mcI^j: 
-        d_i \le \bar{b}^j \bigg\rbrace, \\
-    \text{where}&\\
-    \bar{b}^j &= b_j - \sum_{t\in
-\tau} d_i^{j(t)}
-\end{align*}
-and $b^j$ is $j$'s original budget.
-
-% MECHANISM
-\subsection{Data Auction Mechanism}
-We may now proceed to formally define the PSP auction as a composition of the
-buyers and sellers in the secondary market, along with their respective
-strategies. We begin by defining the opt-out buyers' strategy.
-
-Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, given as
-the $\alpha$-fair utility in (\ref{buyervaluation}), scaled
-by a function of quantity desired from the market. 
-We define, in addition to the valuation and budget of buyer $i$, a generic
-\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
-following (novel) strategy,
-{
-\proposition{(Opt-out buyer strategy)}\label{strategy}
-Define, for any allocation $a$,
-% OPT-OUT BUYER STRATEGY
-\begin{equation}\label{opt-out}
-    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
-    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
-\end{equation}
-and let $j^* \in \ell_i$ be the seller such that
-$j^* = n \le I \in \mathcal{Z}^+$ results in a subset $\bar\mcI_i\subset\mcI$ where 
-\begin{equation}\label{coordinate}
-    \displaystyle\sum_{\bar\mcI_i} \frac{\min_{j\in\ell_i}(d^j)}{d_i} =
-\displaystyle\sum_{\bar\mcI_i} \frac{d^{j^*}}{d_i} = d_i,
-\end{equation} 
-now let, 
-\begin{equation}
-    e_i(a) \triangleq e_i^{j^*}(a).
-\end{equation}
-Then, we have that $e_i$
-is an optimal feasible strategy for buyer $i$.
-}\\
-\textbf{Proof:}
-In the case that there exists a seller who can completely satisfy a buyers'
+\fi
+We note that in the case that there exists a seller who can completely satisfy a buyers'
 demand, $j^*=1$, and (\ref{coordinate}) holds. If such a buyer does not exist,
-as the set $\ell_i$ is an ordered set, $i$ may discover seller
-$j^*$ by computing $\ell_i$ iteratively. In the case that $d_i >
+as the set $\ell_i$ is an ordered set, $i$ may discover 
+$j^*$ by computing $\ell_i$. In the case that $d_i >
 \sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
@@
 valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
-and the form of (\ref{opt-out}) is justified. We note that $\mcI_i$ is not the
-possible minimum subset $\in \mcI$, but is the minimal subset where a
+and the form of (\ref{opt-quantity}) is justified. We also note that $\mcI_i$ is not the
+possible minimum subset $\in \mcI$ able to satisfy $i$'s demand, it is the minimal subset where a
 coordinated bid is possible.
 
+It is necessary that we determine there is an incentive for the seller to
+accept fractional bids (i.e. sell fraction of thier data $d^j$). Reasonably,
+there may not exist a buyer such that $d_i = d^j$, in addition, a seller may accept
+fractional bids in order to
+maximize the revenue gained per unit of data by increasing market competition
+(NEED CITE!).
+Finally, in the case that the seller does not know the exact amount of
+leftover data available, then they may only sell enough data to ensure that
+they will not become a buyer while they submit their total data overage to the
+secondary market. (FUTURE WORK?)
+(NOT SURE IF WE CAN ALLOCATE ON-THE-FLY AND HAVE MARKET EQ...)
+Define, for a seller $j$, the maximum subset of buyers that $j$ can satisfy its
+budget,
+% MAX SET
+\begin{equation}\label{maxset}
+    \mcI^j = \lbrace i\in\mcI : j \in \mcI_i\rbrace.
+    %\mcI^j = \max_{n\in\lbrace 1,\cdots, \vert \beta_j\vert\rbrace}\bigg(\argmax_{{\mcI^j}' \subset \mcI^j,
+    %\vert{\mcI^j}'\vert = n}\sum_{i\in{\mcI^j}'} d_i\bigg).
+\end{equation}
+\iffalse
+The set $\beta^j$ is computed by $j$ before each
+bid iteration. Suppose the auction duration is $\tau \in (0, \infty)$.
+For $t \in (0,\tau]$, 
+$$
+    \beta^{j(t+1)} = \bigg\lbrace i\in\mcI^j: d_i \le \bar{b}^j \bigg\rbrace, \\
+$$
+\fi
+Let the winner be determined by,
+\iffalse %SAVING IN CASE ITERATIVELY ASSIGNING DATA DOES NOT WORK
+$$
+    \ell_i =\argmax_{\mcI_i' \subset \mcI_i, \vert\mcI_i'\vert =
+n}\sum_{j\in\mcI_i'} d^j.
+$$
+Let $j^* \in \ell_i$ be the seller such that
+$j^* = n \le I \in \mathcal{Z}^+$ results in a minimal subset $\bar\mcI^j\subset\mcI$ where 
+\begin{equation}
+    \displaystyle\sum_{\bar\mcI^j} d_i^j = b^j.
+\end{equation} 
+\fi
+\begin{equation}\label{winner}
+    \bar{i} = \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j.
+\end{equation}
+\iffalse
+and so,
+$$
+    \bar{b}^{j(t+1)} = b^{j(t)} - \sum_{\bar{i}\in\mcI^j} d_{i^*}^{j(t)},
+$$
+\fi
+Also define
+$$
+    \ell^j =\argmax_{{\mcI^j}' \subset \mcI^j, \vert{\mcI^j}'\vert =
+n}\sum_{i\in{\mcI^j}'} p_i^j,
+$$
+and let $i^* \in \ell^j$ be the buyer such that
+$i^* = n \le I \in \mathcal{Z}^+$ results in a minimal subset $\bar\mcI^j\subset\mcI$ where 
+\begin{equation}
+    \displaystyle\sum_{i\in\bar\mcI^j} d_i^j > b^j.
+\end{equation} 
+Finally, define $j$'s reserve price as, 
+\begin{equation}\label{newprice}
+    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
+\end{equation}
+The potential revenue for $j$ at unit price $y$ is determined by the
+demand of the buyers. $\forall \ y\ge 0$, the demand is given by,
+% BUYER DEMAND 
+\begin{equation}\label{datademand}
+    \rho^j(y) = \sum_{i\in\mcI_j : p_i^j\ge y} d_i^j, 
+\end{equation}
+with ``inverse"
+% SELLER REVENUE 
+\begin{equation}\label{revenue}
+    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
+        \rho_i^j(y) \ge z \ \forall \ i \in \mcI^j\big\rbrace.
+\end{equation}
+For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
+which it could be sold to any buyer $i\in \mcI^j$.
+Now, in order to derive the sellers' valuation, we have the following,
+{
+% SELLER CONSTRAINTS
+\lemma{(Seller constraints)}\label{constraints}
+Let $j\in\mcI_i$ be a seller with data (budget) $b^j$.
+Formalizing the quantity threshold, the seller must satisfy the quantity
+constraint, $\forall \ i \in\mcI^j$,
+\begin{equation}\label{quantity}
+    d^j \ge d_i = e_i(a),
+\end{equation}
+and
+\begin{equation}\label{budget}
+    \displaystyle\sum_{i\in\mcI^j} e_i^j(a) \le \sum_{i\in\mcI^j} d^j_i \le b^j.
+\end{equation}
+In addition, for a seller who does not sell at a loss, the reserve price must
+satisfy, $\forall \ i \in \mcI^j$,
+\begin{equation}\label{reserveprice}
+   p^j \ge \min_{i\in\mcI^j}\big({\theta_i}'(d_i^j)\big).
+\end{equation}
+}\\
+\textbf{Proof:}
+The first statement is an assumption, which we may enforce by (\ref{opt-out}),
+and as a seller cannot sell more data than thier bid, (\ref{budget}) enforces
+that there is a natural budget constraint for the seller. (\ref{reserveprice})
+follows from the assumption that $j$ does not sell at a loss.
+
+We may now define the seller $j$'s valuation (potential). 
+{
+\lemma{(Seller valuation)}\label{sellervaluation}
+% SELLER VALUATION
+For any $i\in\mcI^j$, 
+\begin{equation}
+    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
+\end{equation}
+it follows that 
+\begin{equation}\label{valuation}
+    \theta^j = \displaystyle\sum_{i\in\mcI^j}
+ \int_0^{e_i^j(a)} f^j(z) \ dz.
+\end{equation}
+}
+\textbf{Proof:} 
+We assume that a seller will try to maximize profit, and
+so there is an incentive sell all its data, so from Lemma
+\ref{sellervaluation},  $\sum_{i\in{\mcI^j}} d_i^j = 
+\sum_{i\in\mcI^j} e_i$,
+The remainder of the proof follows as in \cite{semret}.
+The sellers' natural utility is the potential
+profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
+potential revenue from the sale of data composed with opt-out value
+$e_i(a)$ for each buyer $i\in\mcI^j$. Note that we have chosen to omit the original cost of the data
+paid to the ISP, as a discussion of mobile data plans is outside the scope of this
+paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
+participate in any auction.
+
+% MECHANISM
+\subsection{Data Auction Mechanism}
+We may now proceed to formally define the PSP auction as a composition of the
+buyers and sellers in the secondary market. 
 The market price function (MPF) for a buyer in the secondary market
@@
 \begin{split}
-    \bar{P}_i&(z, s_i) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
+    \bar{P}_i&(z, s_{-i}) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
 s_{-i}^j) \\
@@
 \begin{split}
-    \bar{D}_i(y, s_i) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
+    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
 \bar{D}_i^j \big) : \\
@@
 % DATA ALLOCATION RULE
-The data allocation rule for seller $j$ is given as,
-\begin{equation}\label{dataallocation}
-    \bar{a}_i^j(s) = \min_{j\in\mcI_i}\bigg\lbrace d_i^j, \frac{d_i^j}{\sum_{k:p_k^j=
+The data allocation rule is given as,
+\begin{align}\label{dataallocation}
+\begin{split}
+    \bar{a}_i(s) &= a_i(s) \circ e_i =
+\displaystyle\sum_{j\in\mcI_i}\bigg(\min\bigg\lbrace d_i^j/\vs_i^j,
+\\
+    &\frac{d_i^j}{\sum_{k:p_k^j=
 p_i^j}d_k^j}
-\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace
-\end{equation}
-with cost,
+\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace\bigg)
+\end{split}
+\end{align}
+with cost to the buyer,
+% DATA COST
 \begin{align}\label{datacost}
 \begin{split}
-    \bar{c}_i^j(s) &= 
+    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI_i} 
 p^j \bigg(\bar{a}_j(0; s_{-i}^j)
-    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg) ,
+    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg).
 \end{split}
 \end{align}
-where $\mcI_i$ is chosen as described in the buyer strategy.
 
-The potential revenue for $j$ at unit price $y$ is determined by the
-demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI_j : p_i^j\ge y} d_i^j, 
-\end{equation}
-with ``inverse"
-% SELLER REVENUE 
-\begin{equation}\label{revenue}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z \ \forall \ i \in \mcI^j\big\rbrace.
-\end{equation}
-For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
-which it could be sold to any buyer $i\in \mcI^j$.
-Now, in order to derive the sellers' valuation, we have the following,
-{
-% SELLER CONSTRAINTS
-\proposition{(Seller constraints)}\label{constraints}
-Let $j\in\mcI_i$ be a seller with data (budget) $b^j$.
-Formalizing the quantity threshold, the seller must satisfy the quantity
-constraint, $\forall \ i \in\mcI^j$,
-\begin{equation}\label{quantity}
-    d^j \ge d_i = e_i(a),
-\end{equation}
-and
-\begin{equation}\label{budget}
-    \displaystyle\sum_{i\in\mcI^j} e_i^j(a) \le \sum_{i\in\mcI^j} d^j_i \le b^j.
-\end{equation}
-In addition, for a seller who does not sell at a loss, the reserve price must
-satisfy, $\forall \ i \in \mcI^j$,
-\begin{equation}\label{reserveprice}
-   p^j \ge \min_{i\in\mcI_j}\big({\theta_i}'(d_i^j)\big).
-\end{equation}
-}\\
-\textbf{Proof:}
-The first statement is an assumption, which we may enforce by (\ref{opt-out}),
-and as a seller cannot sell more data than thier bid, (\ref{budget}) enforces
-that there is a natural budget constraint for the seller. (\ref{reserveprice})
-follows from the assumption that $j$ does not sell at a loss.
-
-We may now define the seller $j$'s valuation (potential). 
-{
-\proposition{(Seller valuation)}\label{sellervaluation}
-% SELLER VALUATION
-For any $i\in\mcI^j$, 
-\begin{equation}
-    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-it follows that 
-\begin{equation}\label{valuation}
-    \theta^j = \displaystyle\sum_{i\in\mcI^j}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-}
-\textbf{Proof:} 
-We assume that a seller will try to maximize profit, and
-so there is an incentive sell all its data, so from Lemma
-\ref{sellervaluation},  $\sum_{i\in{\mcI^j}} d_i^j = 
-\sum_{i\in\mcI^j} e_i$,
-The remainder of the proof follows as in \cite{semret}.
-The sellers' natural utility is the potential
-profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
-potential revenue from the sale of data composed with opt-out value
-$e_i(a)$ for each buyer $i$ that has $j$ in its set of qualified buyers
-$\mcI^j$. Note that we have chosen to omit the original cost of the data
-paid to the ISP, as a discussion of mobile data plans is outside the scope of this
-paper. This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
-participate in any auction.
-
-We claim that there is an incentive for the seller to
-accept fractional bids (i.e. sell fraction of thier data $d^j$). Reasonably,
-there may not exist a buyer such that $d_i = d^j$, in addition, a seller may accept
-fractional bids in order to
-maximize the revenue gained per unit of data sold over time.
-Finally, in the case that the seller does not know the exact amount of
-leftover data available, then they may only sell enough data to ensure that
-they will not become a buyer while they submit their total data overage to the
-secondary market. (FUTURE WORK?)
-% SELLER INCENTIVE
-{
-\lemma{(Seller incentive)}\label{incentive}
-Let $j$ be a buyer with fixed price $p^j$. Then, in order for $j$ to change its
-quantity $d^j$ we must have, for some $i \in \mcI^j$,
-\begin{equation}
-       p_i^j \ge p^j \qquad \text{and} \qquad d_i^j < d^j.
-\end{equation}
-}
-\textbf{Proof:}
-We will show that if the Lemma holds, then $j$
-(NEED TO THINK... NEED THIS OR FUTURE WORK?)\\
-
-The main contribution of this work is comprised by these rules, which we use to
+The main contribution of this work is comprised by the modified PSP rules,
+along with the user strategies, which we use to
 describe an auction mechanism inspired by the classic PSP throughput problem. In order to apply PSP to the data-sharing secondary market described in
-\cite{zheng} the idea of a ``route" is repurposed. We claim that in the
-data-sharing model, it is not necessary to bid on a minimal route, and that our
+\cite{zheng} the idea of a ``route" is repurposed, and by the use of the
+opt-out buyer, we are abel to achieve a market equilibrium. We claim that in
+the secondary market our
 formulation not only holds the desired VCG qualities, but minimizes the message
-space and auction duration, resulting in a faster convergence time than the
-classic throughput problem (EEEK!).
+space and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
+with respect to the classic throughput problem.
 
@@
 satisfy $i$'s demand, then
-(\ref{opt-utility}) reduces to the original form (\ref{utility}), defined in
+(\ref{opt-utility}) reduces to the original form, defined in
 \cite{semret} as ``a simple buyer at a single resource element".
+
+The sellers' auction will function as follows: at each bid iteration all buyers
+submit bids, and the winning bid is the buyer $i$ that has the highest price
+$p_i^j$. The seller allocates
+data to this winner, at which point all other buyers are able to bid again, and
+the winner leaves the auction (with the exception where multiple bidders bid
+the same price, where (\ref{dataallocation}) determines they will not fully
+satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
+sellers' data has been allocated. We design an algorithm based on the sellers'
+fractional allocation strategy.
+
+% SELLER STRATEGY
+
+\begin{algorithm}[H]
+\caption{(Seller fractional allocation)}
+\begin{algorithmic}[1]
+\State $p^{j(0)} \gets \min_{i\in\mcI^j} p_i^j$
+\State $s^{j(0)} \gets (p^j, d^j)$
+\While{$d^j > 0$}
+\State $\mcI^{j(t+1)} = \mcI^j\setminus \lbrace i \in \mcI^{j(t)}: d_i^j >
+\bar{b}^{j(t)}\rbrace$
+\State $ i^* \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
+\State $\bar{b}^{j(t+1)} \gets \bar{b}^j - d_{i^*}^{j}$
+%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
+\State $p^j \gets p_{i^*}^j$ and $d^j \gets \bar{b}^j$
+\State $s^{j(t+1)} \gets (d^j, p^j)$
+\If{$\ \exists \ i : s_i^{j(t+1)} \ne s_i^{j(t)}$}
+\State $\bar{b}^{j(t+1)} = \bar{b}^{j(t)}$
+\State Go to 4.
+\Else
+\State $i^* \gets \bar a_i(s)$
+\State $\beta^{j(t+1)} \gets \bigg\lbrace i\in\mcI^j: 
+        d_i \le \bar{b}^j \bigg\rbrace$
+\State Go to 4.
+\EndIf
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+We assume that each time that $s^j$ is updated it is shared with all
+participating buyers. At this point buyers have the opportunity to bid again,
+where a buyer that does not bid again is assumed to hold the same bid, since a
+buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. As we will show in our analysis, the buyers are bidding truthfully; the
+algorithm makes use of the fact that the sellers' valuation is determined by the market.
+The sellers' price is then a true market valuation and does not interfere with
+the PSP mechanism. (PROPOSITION AND PROOF?!)
 
@@
 Let $i\in\mcI$ be a opt-out buyer.
-For any profile $s_i^j = (d_i, p_i)$, let $a_i \equiv a_i(s)$ be the resulting data
+For any profile $s_i = (d_i, p_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
 tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
@@
 $s_i$. \\
-(DO I WANT TO DO THIS? DO I THINK IT WILL WORK? OR JUST HAVE SELLERS SPLIT
-THIER DATA LIKE BUYERS... COULD LEAD TO A MORE OPTIMAL SOLUTION THOUGH)
+(WANT TO SHOW DOES NOT RUIN VGG : 1. selling off data piecewise over time, 2.
+using the min price of sellers in the auction i.e. ${\theta_i}'(d_{i^*}^j) =
+p^j$ is OK, 3. that bids are still feasible
+AND optimal 3. the algorithm achieves economic equilibrium)
 ... since $d^j$ is non-decreasing, as in \cite{lazar}, \cite{semret}

### 2018-04-18 paper_wc.tex
Moving PhD paper from Dropbox to github.

\documentclass[12pt]{article}

\usepackage[text={6in,8.1in},centering]{geometry}

\usepackage{enumerate}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{mathrsfs} % to use mathscr fonts

\usepackage{multicol}
\usepackage{url}

\usepackage{epstopdf}
\usepackage{caption,subcaption}
\usepackage{pstricks}
\usepackage{pst-solides3d}
\usepackage{pstricks-add}
\usepackage{graphicx}
\usepackage{pst-tree}
\usepackage{pst-poly}
\usepackage{calc,ifthen}
\usepackage{float}\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{changepage}
\usepackage{color}
\usepackage{listings}
\usepackage{fancyvrb}
\usepackage{verbatim,moreverb}
\usepackage{courier}
\usepackage{algorithm}

\lstset{ %
language=C++,               
basicstyle=\footnotesize,
numbers=left,                  
numberstyle=\tiny,     
stepnumber=1,         
numbersep=5pt,         
backgroundcolor=\color{white},  
showspaces=false,               
showstringspaces=false,         
showtabs=false,                 
columns=fullflexible,
frame=single,          
tabsize=2,          
captionpos=b,       
extendedchars=true,
xleftmargin=17pt,
framexleftmargin=17pt,
framexrightmargin=17pt,
framexbottommargin=4pt,
breaklines=true,       
breakatwhitespace=false, 
escapeinside={\%*}{*)}       
}

\newenvironment{block}{\begin{adjustwidth}{1.5cm}{1.5cm}\noindent}{\end{adjustwidth}}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\def\verbatimtabsize{4\relax}
\def\listingoffset{1em}
\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}

\newcommand{\vs}{\varsigma}
\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcI}{\mathcal{I}}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\headsep25pt\headheight20pt

\pagestyle{fancyplain}
\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
\cfoot{\ \hfill\tiny\sl Draft printed on \today}

\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables

\begin{document}
\begin{multicols}{2}

\section{Abstract}

We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
gained by charging users a fixed fee for a maximum amount
of data usage in a month, i.e., a monthly data cap \cite{???}. 
2cm's (2nd exchange market) data exchange platform allows users to submit
bids to buy and sell data.
This usage model, is, as far as our knowledge, the first data trading
platform that allows customers to buy and sell their own data.
We describe a distributed auction mechanism for data exchange inspired by the
classic PSP throughput problem,
and prove that our distributed data exchange mechanism provides incentive
compatibility (social choice function), and that we have efficiency
using only partial valuation information of each participant in an exchange market.

In applying a distributed PSP implementation to CMHK market, we
find that
the market is able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and design our mechanism tp provide the functions
for effective communication between the connected users. We claim that in
this secondary market our formulation holds the desired VCG qualities through the construction of a
probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
with respect to the classic throughput problem.
and provide simulated results on convergence time to support our (FIND
COMPETITVE RATIO!), and a bound
on the convergence of our mechanism. We extend the works of cite!cite!
i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.

\section{Introduction}

In this work, we propose \emph{a distributed progressive second price (PSP) auction in
order to maximize social utility in the CMHK market}. Using the
distributed PSP mechanism on CMHKs data
exhange platform, we show that for cellular data allocated between multiple users there
exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
demand information is not known centrally, rather, it is distributed in the
buyers' valuations. The mechanism for an auction is defined
as \emph{distributed} when the allocations at any element depend only on
\emph{local} state: the quantity offered by the seller at that element, and the
bids for that element only \cite{lazar}. In this work, the proposed mechanism
allows the distribution of bids, where there are many ISPs each holding
thier own local auction; there is no entity that holds a global market knowledge.

In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
using its own demand functions). Buyers submit bids cyclically until an
($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.

(FEE IS FIXED OR
PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)

The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
CLAIM 'IS') described as a
pure-strategy progressive game with incomplete, but perfect information. (WHAT
DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
VALUATION.. FUTURE WORK)

The paper is organized as follows...

(MOVED: TO ORGANIZE)\\
The main contribution of this work 
is an auction mechanism inspired by the classic PSP throughput problem. In
order to apply a distributed PSP implementation to the CMHK market,
we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
to change their bid strategies, and as each user only has \emph{local}
information about the bidding environment, it is clear that an unconstrained
market, even with a finite number of users, could suffer from the communication
expense from numerous local auctions trading an infinitely divisible resource.
We will assume that the cost of participating in the CMHK secondary market is
absorbed by the bid fee, which could represent data used in submitting bids, or
a fee charged per unit of data, or a flat rate charged at the completion of the
purchase. It is worth mentioning that CMHK users are not allowed to resell data
purchased from the CMHK
market, additionally, the purchased data does not carry to the next
service period. Therefore, a market equilibrium, where
supply equals demand, requires that users maintain incentive for truthfullness
across a distributed setting.
We complete a comprehensive analysis of market dynamics, (FINISH)
To the best of our knowledge, this is the first work to provide a truthful
mechanism in a distributed setting for data-exchange based on market behavior.
\\
\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
restrictions introduced by the CMHK secondary market. We reserve this for
future work.

We claim that the CMHK market is
able to achieve an equilibrium as the sellers and buyers have an
incentive for a collaborative exchange, and as our mechanism provides
for effective communication between the connected users.

Despite the small message space, with many user types, there is no single
way to do the transformation from the direct revelation mechanism to the
desired one. Our mechanism is naturally designed by guessing
right direct-revelation-to-desired-mechanism transformation and building it
into the allocation rule to be the primary step in the design. This incentive for a user to
truthfully reveal its type is built into the user strategies. As in classic
mechanism design, we determine the equilibria as result of incentive
compatibility in our mechanism design. 
We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
but minimizes comminication overhead 
and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
with respect to the classic throughput problem.

This is the (built-in) transformation from the
direct-revelation mechanism to the desired message space.

\subsection{Distributed Progressive Second Price Auctions}

Progressive second price auctions (PSPs) were proposed
in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
scheme to provide consistent services for network bandwith users.
\cite{diffserve} conducts a game theoretic analysis, deriving
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria based on their game-theoretic
model. Constructing necessary and sufficient conditions for the stability
of the game allows the sustainability of any set
of service level agreement configurations between Internet service
providers.

We begin with a brief introduction to the distributed PSP auction for bandwith
sharing, first introduced by Lazar and Semret \cite{lazar}.
We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ network bandwidth users.
Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents. 
Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
bids $s_{-i}$,
user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
and is a Nash move
where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
budget, and every user has an elastic demand function.
Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
allocations awarded in auction $j$. 
An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.

% MECHANISM
\subsubsection{The PSP Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
function.
In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.

\section{Related Work}

\section{The Problem Model}

\subsection{The CMHK Market}

We construct the model for a PSP data auction for mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
Users prefer to participate in the CMHK secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which 
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We assume that data is a unary resource belonging to the seller, and
therefore we identify each local auction with the identity of the seller
$j\in\mcI$, and that the user valuation
\iffalse
is independently and identically
distributed (i.i.d.) and
\fi
satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}.
Finally, we assume in the CMHK market that a buyers' budget is always
sufficient, as the alternative is to pay the overage fee to the ISP.

The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
separated (a seller does not also buy data and vice versa). Thus, we may assume
that this is implied in our notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
$j$. For the purposes of our analysis, we will assume that a zero bid from a
buyer is equivalent to no bid.
A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
with the intent of offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$.

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
$i$ gains access to the full grid $s$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

\subsection{User Behavior}

We assume that the CMHK market does not have network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
bandwidth in wireless networks is not the focus of this paper. We
conduct a comprehensive analysis, deriving a globally optimal strategy suited for
users with local information in a distrubuted data-sharing model. 
Users in the CMHK market do not need to bid on a complete ``route", as in the
bandwidth allocation problem \cite{semret}. Instead, our mechanism allows a buyer
to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
will determine its bid quanities by,
\begin{equation}\label{opt-out}
    e_i(a) = [e_i^j(a)]_{j\in\mcI}.
\end{equation}
In a general sense, this abstraction applies our \emph{user strategy}
to the PSP rules.
% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is now of the form,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
the buyers' valuation of allocation $a$ across local markets (and thus multiple sellers).
In this way we extend the PSP rules described
in \cite{semret} to design equilibria across subsets of local data-exchange markets.

The sellers, $j\in\mcI$ are not associated with an opt-out function, we
consider their valuation to be a functional extension of the buyers, where
$\theta^j$ is constructed by buyer demand.
The sellers strategy can only be to determine the reserve price of their local
auction, using only information from buyers who have not opted out.
In our analysis, we demonstrate market dynamics, and further show evidence of symmetry in the strategies of
buyers and sellers.

\subsubsection{Market Dynamics}
The buyer demand largely motivates the market price function, however, the
distributed nature of the market prevents any single user from knowing the
market demand for a quantity of data. All users have knowledge of market
supply, as this is public information, however only buyers
are able to determine supply or demand across multiple auctions after time $t=0$, and then only from auctions
in which they participate. \\
\textbf{Remark:}
It is possible that a seller would be able to derive information about other
auctions by examining buyer bids over time, particularly if the seller had knowledge of the
buyer strategy. (FUTURE WORK?)\\
In order to represent the public platform of the secondary market, we model the ISP as
a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
in any auctions. At time $t=0$, a seller $k$ entering the market will have submitted bid
$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform.

A given demand may lead to diffent prices, which emerge directly from the users valuation
of the resources and, possibly, their decision strategies. The seller does not
require a priori demand information.
It is worth mentioning that the \emph{analysis} of the auction as
a game assumes some forms of demand and supply, to derive properties.
The mechanism itself does not require any knowledge of user demand or
valuation. 
\iffalse
The ISP overage
charge inducing an upper bound on the sellers' reserve prices implies that
supply will always be greater than demand, thereby reducing the sellers'
influence on market dynamics.
\fi

As the buyer valuation is elastic, even infinitesimal changes in the market dynamics can be
modeled. This, and the homogenous nature of data in the CMHK market, 
allows for the analysis of additional constraints imposed by the user
strategies. Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
A buyers' valuation of an amount of data represents how much a buyer is willing
to pay for that amount. 
This is equivalent to the bid price that
satisfies $\theta_i$ given a fixed amount of data. We determine the
buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
possible unit price. We have,
% BUYER PRICING 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
\end{equation}
where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
We determine that the market supply function is equivalent to buyer demand, and 
acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
% BUYER DEMAND 
\begin{equation}\label{datasupply}
    \rho_i(y) = \sum_{j\in\mcI : p_i^j\le y} D^j.
\end{equation}
We note that $f_i$ is such that
$i$ could still bid in \emph{any} auction $j\in\mcI$.
Therefore, in a coordinated bid, the utility-maximizing bid price is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers. We will later show, in Proposition
\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
bids, i.e. using the same bid for all auctions.
Using buyer bid quantity $e_i^j(a)$, from (\ref{opt-out}), 
we have the following Lemma,
{
% BUYER CONSTRAINTS
\lemma{(Buyer constraints)}\label{buyerconstraints}
Let $i\in\mcI$ be a buyer with bid, $s_i = (e_i(a), p_i)$, which must obey
the following constraints,
\begin{equation}\label{buyercapmax}
    \sum_{j\in\mcI} e^j_i(a) \le D_i,
\end{equation}
and, as $i$ is rational, and therefore utility-maximizing, $i$ must have
sufficient bids $s_i^j > 0$ so that,
\begin{equation}\label{buyercapmin}
    \sum_{j\in\mcI} d^j_i \ge D_i,
\end{equation}
where $d_i^j$ denotes the bid quantity of seller $j$.
}\\
\textbf{Proof:}
A rational buyer does not want to purchase extra data, as this would be
equivalent to overpaying, and so (\ref{buyercapmax}) holds. We also assume that
$i$ wants to fufill their data requirement, and so (\ref{buyercapmin}) implies
that $i$ submits positive bids to a set of buyers that will be able to fufill
their demand.

The seller is similarly represented, however a seller only has
information from buyers in its own auction, and may only be indirectly influenced by
buyers in other auctions. So from the perspective of the
seller we have a more direct interpretation of valuation as revenue.
We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
% BUYER DEMAND 
\begin{equation}\label{datademand}
    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} e_i^j(a), 
\end{equation}
and define the ``inverse" of the buyer demand function for seller $j$ as
potential revenue at unit price $y$, we have, 
% SELLER REVENUE 
\begin{equation}\label{sellerinversedemand}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
price. Now, we determine that, in addition to some natural constraints, the sellers' highest
``possible" price is conditioned by
additional restrictions on its pricing function, the motivation for which is
that a buyer has the choice to opt-out of any auction, and so seller $j$ has an
incentive to set its reserve price to include enough buyers to sell all its
data. Thus we have the following Lemma,
{
% SELLER CONSTRAINTS
\lemma{(Seller constraints)}\label{sellerconstraints}
Let $j\in\mcI$ be a seller with bid $s^j$, then $j$ must obey the following constraints.
A bid $s_i^j= (d_i^j, p_i^j)$, to buyer $i$ must be such that,
\begin{equation}\label{datacapmax}
    \sum_{i\in\mcI} d^j_i \le D^j,
\end{equation}
In addition, for a rational seller, the reserve price must
satisfy, $\forall \ i\in \mcI$,
\begin{equation}\label{reservepricemin}
   p_i^j \ge \min_{i\in\mcI}\big(p_i^j),
\end{equation}
and,
\begin{equation}\label{reservepricemax}
   p_i^j \le \max_{i\in\mcI}\big(p_i^j).
\end{equation}
Finally, as $j$ is rational, $j$ must submit enough bids $s_i^j >0$ so that,
\begin{equation}\label{datacapmin}
    \displaystyle\sum_{i\in\mcI} e_i^j(a) \ge D^j.
\end{equation}
}\\
\textbf{Proof:}
The first statement is obvious, 
a seller cannot sell more data than they have,
Then, (\ref{reservepricemin})
follows from the assumption that $j$ is rational, and so utility-maximization
acts as revenue maximization, a rational seller will not sell its
data at a price less than the lowest offer. Finally, as a rational seller will
attempt to maximize profit, and will try and sell all of its data, and so we
must have sufficient demand
from the buyers. Therefore, (\ref{reservepricemax}) and (\ref{datacapmin}) hold. Together, (\ref{datacapmax}) and
(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} e_i^j(a) >  D^j$. In
this case, by (\ref{dataallocation}), $j$ may submit a partial bid to a buyer
$i$ so that $\sum_{i\in\mcI} d^j_i = D^j$.

We proceed to determine the properties and characteristics of the user valuation functions. Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
distributed across the CMHK market via bids in local auctions. 
As such, buyer behavior is influenced by opponent bid profiles from multiple auctions.
We therefore determine that the valuation of any user must be modeled as a function of the entire
marketplace. Naturally, a buyers' valuation is aggragated over local markets, and the
sellers' valuation is aggragated over its own auction. We model the valuation of
users based on the opt-out user behavior, thereby including the buyers'
influence on the market. We have already introduced the composition $\theta_i
\circ e_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
(\ref{datademand}) and (\ref{sellerinversedemand}). We first note that, in
general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
$$
    \theta(x) = \int_0^x f(z) \ dz,
$$ 
as in \cite{semret}. Now, we have the following Lemma,
{
\lemma{(User valuation)}\label{uservaluation}
For any buyer $i\in\mcI$, the valuation of a potential
allocation $a$ is, 
\begin{equation}\label{buyervaluation}
    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
 \int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}
Now, we may define seller $j$'s valuation in terms of revenue, so we have,
\begin{equation}\label{sellervaluation}
    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ e_i^j(a) = \sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a buyer wants to minimize the cost of purchasing their data
requirement, at the same time ensuring they get the full allocation $e_i(a)$,
and so must minimally meet $j$'s reserve price. 
A seller will try to maximize profit, 
and so will try to sell all of its data.  By Lemma
\ref{buyerconstraints} and Lemma \ref{sellerconstraints}, we have,
$d_i^j = e_i^j(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j =
\sum_{i\in\mcI} e_i^j(a) = D^j = D_i$. It is worth observing that this result
does \emph{not} imply that $s_i=s^j$. Let $\xi$
be a unit of data from buyer bid quantity $e_i^j(a)$.
If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
similarly decrease. The lost potential revenue for seller $j$ is the price of
the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
$$
    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
$$
Thus (\ref{sellervaluation}) holds.
As we may use the same argument for (\ref{buyervaluation}), we complete the
proof with the observation that the function $f^j$ (resp. $f_i$) is the first
derivative of the valuation function with respect to
quantity, and therefore, in this context, represent the marginal valuations of the
users, ${\theta^j}'$ (resp. $\theta_i'$). Finally, the sellers' natural utility is the potential
profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
paid to the ISP, as it is not a component of our mechanism, and as a discussion
of mobile data plans is outside the scope of this paper.

\subsubsection{Buyer Strategy}

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that a seller may come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that some buyers must split their bids among multiple sellers. 
We propose the following strategy to determine when rational
(utility-maximizing) buyers will opt-out of a local auction. (QUESTIONING WHETHER OR NOT $\mcI_i$ SHOULD
BE ORDERED BY DATA, OR IF PRICE IS BETTER, PRETTY SURE IT IS OK, WILL FIND OUT
IN LATER PROOFS)
% BUYER STRATEGY
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Define any auction duration to be $\tau \in [0,\infty)$. 
Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
$t\in\tau$. % For any allocation $a$ at time $t$, let
% OPT-OUT BUYER STRATEGY
%\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
    %e_i^j(a) \triangleq a_i^j,
%\end{equation}
%and define,
Define the composition,
$$
     e_i^j \circ a = e_i^j(a) = \frac{a_i^j}{j},
$$
to be the buyer strategy with respect to quantity, and the set,
% MIN SET
$$
    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} D^j,
$$
where buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
\end{equation} 
The buyer strategy produces a minimal subset of sellers $\in \mcI$ 
able to satisfy buyer $i$'s demand. For 
fixed $n$ we will denote this subset,
\begin{equation}\label{sellers}
    \mcI_i \subset \mcI.
\end{equation}  
Now let $j^* = n \le I$ represent the seller with the least amount of data
$\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$, and define $i$'s bid
vector $e_i$ with respect to its strategy, where
\begin{equation}\label{opt-minallocation}
    e_i^j(a) \triangleq \begin{cases} e_i^{j^*}(a), \quad j\in\mcI^j,\\
            0, \quad j\ni\mcI^j.\end{cases}
\end{equation}
Now, (\ref{opt-minallocation}) holds $\forall \ j\in\mcI$,
and we have that $e_i$ defines an optimal feasible strategy for buyer $i$.
}\\
\textbf{Proof:}
We assume that a buyer will try and fill their data requirement.
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\mcI_i$ is ordered by the quantity of the sellers' bids, $i$ may discover 
$j^*$ by computing $\mcI_i$.
Suppose that $D_i >
\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
We model the ISP at time $t>0$ as a seller $\kappa$ with bid $s^\kappa =(d^\kappa, p^\kappa)$,
where $d^\kappa > D^j, \
\forall \ j\in\mcI_i$, and
$p^\kappa$ represents the overage fee for data set by the ISP, which we note is also the upper bound of the sellers'
pricing function, and so again (\ref{buyercoordinate}) holds.
Now, consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
The allocation rule (\ref{dataallocation}) determines that the data will be
split proportionally
between all buyers with the same unit price. 
It is possible that the resulting partial allocation of data to $i$ and $k$
would not satisfy some demand. As the two cases $i$ and $k$ are the same, we
will only consider one. Suppose seller $j$ updates its
bid to reflect the new data quantity, $j$'s bid quantity at time $(t+1)$,
$d_i^{j(t+1)}$, is such that
$d_i^{j(t+1)} < e_i^{j(t)}(a)$ where $e_i^{j(t)}(a)$ is $i$'s bid at time $t$.
Then, by the definition of $\mcI_i$, once the buyer implements its strategy, we can
only have that $j \ni \mcI_i$, or that $n$ has been increased so that and new seller(s)
enter the pool. 
Additionally, we consider the entrance of a new buyer $k$ at time $(t+1)$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
words, a new buyer $k$ may enter the market with a better price, decreasing the
value of $i$'s bid for sellers $\in\mcI_i$. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
$n$ so that
$$
    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
$$
and the subset $\mcI_i$ is large enough to balance the additional demand from
$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
and we determine that the opt-out strategy is optimal. We note that feasibility
is not addressed here, as we provide this analysis in Section \ref{???}.

Finally, we note that $\mcI_i$ is not the only
possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
minimal ordered subset where a
coordinated bid is possible, the reasoning for which we will address in Section
\ref{analysis}.

\subsubsection{Seller Strategy}
(POSSIBILITY OF SWITCHING TO BUYER POOL ORDERED BY DATA, IF SELLER POOL GETS
SWITCHED TOO)
In order to to develop the seller strategy, we examine the incentive of a
rational seller with only local information in a dynamic market of many
buyers and sellers. A local auction, examined independently, may appear as
single market with a single seller and many buyers, but is in fact a subset of the
larger data-exchange market, and is subject to the trends and dynamics
therewithin. A seller must determine allocations using only bids in its local market, while the buyers' response is based on the
allocations and resulting opponent bids from all auctions in its seller pool.
In addition, buyers are allowed to bid both dynamically and asychronously.

In order to
maximize revenue, the seller must also be able to respond dynamically to
address the mutation of competitive bids in its market. In order to do this, we
determine that the seller may modify its reserve price in response to the
changing market dynamics. (MORE!)
We will show that sellers are able to maximize revenue in restricted subset of
buyers in $\mcI$, and as such will attempt to facilitate a local market
equilibrium for this subset.

We describe the sellers' \emph{local} auction strategy for allocating its
data according to the constraints formed by the buyer strategy. A
local auction may be described as a progressive game of strategy with
incomplete, but perfect information, however in our analysis, as before, we will assume
complete information.
(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)

% SELLER LOCAL STRATEGY
{
\proposition{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
Define any auction duration to be $\tau \in [0,\infty)$. 
For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t\in\tau$.
Define
$$
    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
n}\sum_{i\in{\mcI}'} p_i^j,
$$
where,
\begin{equation}\label{sellercoordinate}
    n = \min( i \ \vert \ i \in\mcI^j(n) : \displaystyle\sum_{i\in\mcI} d_i^j \ge
D^j),
\end{equation} 
The determination of $n$ produces a minimal subset 
of buyers that maximizes $j$'s revenue at time $t$, which we will
denote, for fixed $n$, by,
\begin{equation}\label{buyers}
    \mcI^j \subset \mcI.
\end{equation} 
Define buyer $i^* = n-1 \le I$ as the buyer with the maximum price $\ni
\mcI^j$.
Then, for time $(t+1)$, set $j$'s reserve price to be, 
\begin{equation}\label{newprice}
    p_i^j = p_{i^*}^j + \epsilon,
\end{equation}
Let the winner at time $t$ be determined by,
\begin{equation}\label{winner}
    \bar{i} = \displaystyle\max_{i\in I^j} p_i^j,
\end{equation}
and update $j$'s total data to reflect the (tentative) allocation,
\begin{equation}\label{newbudget}
    D^{j(t+1)} = D^{j(t)} - e_{\bar{i}}^{j(t)}(a),
\end{equation}
Allowing $t$ to range over $\tau$, we have that (\ref{winner}) -
(\ref{newbudget}) produces a local market equilibrium. 
}\\
\textbf{Proof:}
We assume that the seller has enough data to satisfy at least one buyer,
and that they want to maximize their revenue.
In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
price offer, determined by (\ref{sellercoordinate}), 
Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
In this case, by (\ref{}) the seller must notify $i$ of a
fractional allocation by changing the bid vector at index $i$.
With this caveat, and Proposition \ref{buyerstrategy}, we have that the
aggragate demand of subset $\mcI^j$ is satisfied by seller $j$, as in Lemma
\ref{sellerconstraints}.
Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
that buyers are bidding truthfully, and so ${\theta_i}' + \epsilon
=p_i^j + \epsilon$.
Now, using
(\ref{sellervaluation}), we have, $\forall \ z\ge 0$,
\begin{align*}
    \int_0^{e_{i^*}^j(a)} f_{i}(z)\ dz &\le\int_0^{e_i^{j}(a)}
f^{j}(z) \ dz 
\end{align*}
and so,
$$
     \theta_i \circ e_{i^*}(a) \le \theta_i \circ e_i(a),
$$
which holds $\forall \ j \in \mcI_i$.
It follows that, using
%, using (\ref{buyercoordinate}), 
the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
for any $\epsilon$-best reply, 
$$
    p_i^j \le {\theta_i}'(v_i^j) + \epsilon,
$$
$\forall i \in \mcI^j$.
Therefore the choice of $p_i^j$ does not force any buyers out of the local
auction. Thus we determine the valuation between seller
$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
We note the special case where for winner $\bar{i}$, $\ \exists \ k\in\mcI^j$
such that $p_{\bar{i}}^j =
p_i^k$. In this case the seller again notifies the buyers of a fractional
allocation by changing $d_i^j$ and $d_k^j$ to reflect the proportional
division. Finally, in the case where winning buyer(s) \emph{opts-out} of the local
auction, where $j\in\mcI_i$ at time $t$, then at time $(t+1)$ $j\ne \mcI_i \Rightarrow s_i^{j(t+1)} = (0,0) \Rightarrow i \ne
\mcI^j$, which is mathematically analogous to the definition of opting-out in our
scenario. The seller may simply return the tentatively allocated data to $D^j$,
and recompute $\mcI^j$ and $p_{i^*}^j$, 
$$
    D^{j(t+1)} = D^{j(t)} + \displaystyle\sum_{i\in\Gamma} d_i^{j(t)}
$$
where $\Gamma$ represents the buyers who have opted-out from time $t$ to 
$(t+1)$, indicated by a zero bid from any buyer $\in \mcI^j$:
$$
    \Gamma = \lbrace i\in \mcI^j : s_i^{j(t+1)} = 0\rbrace.
$$

(NOTE - NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK IN
FRACTIONAL ALLOCATIONS? SAVE FOR NASH EQ PROOF? KEEP WITH t TO t+1?)

\subsubsection{Market Dynamics under Strategy}

We conclude this section by examining the relationship between the strategies of buyers and
sellers in local auctions. We model the impact of the dynamics of the
data-exchange market on a local auction $j$. As we have shown, the seller
is a functional extension of the buyer, with rules determined by the buyers'
behavior. This gives an auction $j$ a natural logical extension into the
global market through its buyers. We demonstrate that the symmetry between
buyer and seller rules stretches into a symmetry across subsets of local
auctions. Additionally, we identify a clear bound restricting the influence of
local auctions on each other. We have the following Lemma.
\newpage
% USER UNION
{
\lemma{(Valuation across local auctions)}\label{userunion}
For any $i,j\in \mcI$, 
\begin{equation}\label{jtoi}
j\in\mcI_i \Leftrightarrow i\in\mcI^j.
\end{equation}
Fix an auction $j\in\mcI$ and define the influence sets of users. 
The primary influencing set is given as,
%(ALL THE SELLERS FROM EACH BUYERS POOL)
\begin{equation}\label{lambda}
    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
\end{equation}
with secondary influencing set,
%(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
\begin{equation}\label{llambda}
    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
\end{equation}
\iffalse 
(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
\begin{equation}%\label{lambda}
    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
\end{equation}
(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
POOLS)
\begin{equation}%\label{llambda}
    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
\end{equation}
***********************************
\begin{equation}
    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
\end{equation}
\begin{equation}
    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
\end{equation}
and for each $i\in\mcI^j$ define,
\begin{equation}
    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
\bigg).
\end{equation}
we have $\forall \ i \in
\mcI^j$,
\begin{equation}\label{sym}
    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
\end{equation}

***********************************
\fi
Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$, we have that,
\begin{equation}\label{unioneq}
    \displaystyle\sum_{j\in\Lambda} \theta^j = \sum_{i\in\lambda} \theta_i.
\end{equation}
}\\
\textbf{Proof:}
A local auction $j\in\mcI$, is determined by the collection of buyer bid
profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
if and only if $i$'s bid is such that $p_i^j \ge p_{i^*}^j$, where
(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
price in auction $j$.
Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
Proposition \ref{buyerstrategy}, $i^*$
will add sellers to its pool until its demand is satisfied. Therefore for any
$j\in\mcI_i$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
holds.
Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)

Now, the subset $\mcI^j \subset \mcI$
determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
coordinated, truthful bid, $\mcI_i\subset \mcI$ 
will determine the unit price $p_{i}$ in buyer $i$'s bid.
The reserve price (\ref{newprice}) of seller $j$ is determined at time $t$, and is
the lowest price that $j$ will accept to perform any allocation.
Let $p_*^j = f^j \circ e_i^j(a) $ denote the reserve
price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ e_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
\ \forall \ k \in\mcI_i$. 
Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
\ref{sellerstrategy}, $\forall \ i \in \mcI^j$, we have that $p_i^* \ge p_*^k,
\ \forall \ k \in\mcI_i$.

\iffalse
Now, we have,
\begin{equation}\label{rho}
    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
\end{equation}
from (\ref{datademand}), (\ref{buyerinversedemand}),
(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
\fi

The incentive of each seller $\in\Lambda$ is to sell all of its data at the
best possible price. In the simplest case,
consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
$\lambda = \mcI^j$. 
Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we clearly
have that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
In all other cases, the sellers $\in\Lambda$ are competing to sell
their respective resources to buyers whose valuations are distributed across multiple auctions. 
%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
The set $\lambda$ represents all of the buyers influencing auction $j$, both
directly and indirectly. 
The bid price of buyer $i\in\mcI^j$ is determined by,
\begin{equation}\label{maxbid}
    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ e_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
\end{equation}
$\Lambda$ is the set of sellers that directly influence the bids of buyers
$\in\mcI^j$. the reserve price for auction $j$ is such that,
\begin{equation}\label{resprice}
    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
\end{equation}
by Proposition \ref{sellerstrategy}.

We have from Proposition \ref{sellerstrategy} that $j$ maintains a local market
equilibrium at time $t$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
and suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
that $p_*^q > p_*^j$. Then, a change in $q$'s valuation from time $t$ to $t+1$ will
directly impact seller $j$. If at time $t+1$ we still have that $i$ is the
buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
In each case we
have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
fixed time $t$, and so, $\forall \ i \in\mcI^j$,
\begin{align*}
    \int_0^{e_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ e_i^j(a)\\
    &= \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{align*}
therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
Furthermore, it follows that,
\begin{equation}\label{jdemand}
    \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f^j(z) \ dz =
\sum_{j\in\mcI_i}\int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}

Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
that $p_l^* < p_*^j$. We have that
the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, and so we must
have that $p_l^* < p_i^*$,
and necessarily, $p_i^* > p_l^*$ for
any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$. % \Rightarrow \theta_l^q > \theta_l^k$. 
Again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
\ni\mcI^q \Rightarrow p_*^q >
p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
buyer $i$. 
Lastly, 
in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
We have that for any $l\in\mcI^k$ such that $l\ni
\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
for $q\in\mcI_l$ or $\theta_l^q = 0$ for some $q\in\mcI_i$. Thus, any bid ouside of
our construction
has a zero valuation, with respect to buyers $\in\lambda$ and sellers
$\in\Lambda$. Thus, in all cases,
(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold.
We have,
\begin{equation}\label{idemand}
    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{e_i^k(a)}
f_i(z) \ dz,
\end{equation}
which holds for all buyers and sellers that satisfy (\ref{jtoi}).
Finally, using (\ref{jdemand}), (\ref{idemand}), 
\begin{align*}
    \int_0^{e_i^k(a)} f_i(z) \ dz &= \int_0^{e_i^k(a)} f^k(z) \ dz,
\end{align*}
and
\begin{align*}
    \int_0^{e_l^k(a)} f^k(z) \ dz &= \int_0^{e_l^k(a)} f_l(z) \ dz,
\end{align*}
and the result follows by construction, and the continuity of $\theta'$:
\begin{equation}
    \displaystyle\sum_{j\in\Lambda} \int_0^{D^j} f^j(z) \ dz =
\sum_{i\in\lambda}\int_0^{D_i} f_i(z) \ dz.
\end{equation}

For completeness, in the case where the ISP $\kappa$ 
does not adhere to the market dynamics, so $p^\kappa > p^j +
\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
bid fee.

(ADD TIME? INDUCTION GOES HERE? DID NOT SHOW!)

(OWN
WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
competing in multiple local auctions hosted by the sellers, the two games are
inter-dependent, and may be played on the same or on a different scale in
valuation, time (AND....).

PSP relies on the \emph{relevation prinicple}; the
PSP mechanism is able to demonstrate equlibrium by showing that PSP is
incentive-compatible. (MORE?)
Arrow's paradox is an impossibility theorem stating that when voters have three
or more distinct alternatives (options), no ranked voting electoral system can
convert the ranked preferences of individuals into a community-wide (complete
and transitive) ranking while also meeting a specified set of criteria:
unrestricted domain, non-dictatorship, Pareto efficiency and independence of
irrelevant alternatives.

Thus, (WHAT? FINISH, OWN WORDS)
The designer of a mechanism generally hopes either to design a mechanism
y() that "implements" a social choice function to find the
mechanism y() that maximizes some value criterion (e.g. profit)
Independence of irrelevant alternatives (IIA)
The IIA condition has three purposes (or effects)

Normative
Irrelevant alternatives should not matter.
Practical
Use of minimal information.
Strategic
Providing the right incentives for the truthful revelation of individual
preferences.

\subsection{PSP Formulation}

We intend to show that our auction
is rational and achieves the desired VCG properties, as does the original
formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
realistic, theoretic, and notational templates, we define optimal strategies for
CMHK users, and demonstrate that the development of a set PSP auction mechanisms
in a data exchange setting is able achieve a network equilibrium for cellular data.

% MECHANISM
\subsubsection{Data Auction Mechanism}\label{datamechanism}
We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the CMHK market, and which we will denote the \emph{data}
PSP rules. The rules presented here incorporate of the opt-out function with the
mechanism as in \cite{lazar}, which we note greatly simplifies our
analysis. 
The market price function (MPF) for a buyer in the CMHK market
can be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
s_{-i}^j) \circ e_i^j \\
    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
\end{split}
\end{align}
and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
order to obtain
data amount $z$ given opponent profile $s_{-i}$. We note that
the total minimum price for the buyer must be an aggragation of the
\emph{individual} prices of the buyers as it is possible that the reserve prices
of the individual sellers may vary.\\
\textbf{Remark:} We further note that except at points of discontinuity, from
Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\

%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
%buyer $i$'s bid quantity. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is: 
% NEW ALLOCATION RULE
\begin{align}
\begin{split}\label{datacomposed}
    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+.
\end{split}
\end{align}
% DATA ALLOCATION RULE
The resulting data allocation rule is a function of the local market
interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
\begin{split}
    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
    &= \min\bigg\lbrace e_i^j(a), \\
    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \big(
D_i^j(p_i^j,s_{-i}^j)\big)\bigg\rbrace,
\end{split}
\end{align}
noting that for the full allocation from all auctions we may simply aggregate
over the seller pool.
Finally we must have that the cost to the buyer adheres to the second price
rule for each local auction, with total cost to buyer $i$,
% DATA COST
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
p^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
\end{split}
\end{align}

\subsubsection{Mechanism Realization}\label{realization}

Consider a user seeking to prevent
data overage by purchasing enough data from a subset of other network users.
This user $i$ can be modeled as a opt-out buyer where, as in \cite{semret},
We intend to show that this network setting results in a shared network optima (a
global optimum). The formulation is inspired to the thinnest allocation route for
bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
satisfy $i$'s demand, then
(\ref{buyerutility}) reduces to the original form, defined in
\cite{semret} as ``a simple buyer at a single resource element".

The sellers' auction will function as follows: at each bid iteration all buyers
submit bids, and the winning bid is the buyer $i$ that has the highest price
$p_i^j$. The seller allocates
data to this winner, at which point all other buyers are able to bid again, and
the winner leaves the auction (with the exception where multiple bidders bid
the same price, where (\ref{dataallocation}) determines they will not fully
satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
sellers' data has been allocated. We design an algorithm based on the sellers'
fractional allocation strategy.

(NOTE - FIX TO UPDATED NOTATION!)
% SELLER ALGORITHM
\begin{algorithm}[H]
\caption{(Seller fractional allocation)}
\begin{algorithmic}[1]
\State $p^{j(0)} \gets \epsilon$
\State $s^{j(0)} \gets (p^j, D^j)$
\While{$D^j > 0$}
\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \lbrace i \in \mcI^{j(t)}: d_i^j >
D^{j(t)}\rbrace$
\State $ \bar{i} \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
\State $D^{j(t+1)} \gets D^{j(t)} - e_{\bar{i}}^{j(t)}(a)$
%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
\State $s^{j(t+1)} \gets (d^j, p^j)$
\If{$\ \exists \ i : s_i^{j(t+1)} \ne s_i^{j(t)}$}
\State $D^{j(t+1)} = D^{j(t)}$
\State $t \gets t+1$
\State Go to 4.
\Else
\State $\bar{i} \gets e_{\bar{i}}^j(a)$
%\State $\beta^{j(t+1)} \gets \bigg\lbrace i\in\mcI^j: 
%        d_i \le \bar{b}^j \bigg\rbrace$
\State $t \gets t+1$
\State Go to 4.
\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}
We assume that each time that $s^j$ is updated it is shared with all
participating buyers. At this point buyers have the opportunity to bid again,
where a buyer that does not bid again is assumed to hold the same bid, since a
buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. As we will show in our analysis, the buyers are bidding truthfully; the
algorithm makes use of the fact that the sellers' valuation is determined by
the buyers' market and upholds the PSP mechanism. (CHECK) (ALSO $j$ NEEDS TO
UPDATE FOR NEW BUYERS, $j$'S CONTROL)

(BUYER ALGORITHM? WHY NOT..., CLEANER)

% VCG ANALYSIS
\section{PSP Analysis}\label{analysis}
\subsection{Equilibrium}

Consider an opt-out buyer $i\in\mcI$. A PSP auction
allows for a buyer to react to opponents bids, and so its incentive is based on
the opponent profile.

Due to (\ref{buyerutility}), $i$ only has an incentive to change its bid
quantity if it increases its opt-out value $e_i$, and therefore its utility. 
We will show that $i$ can coordinate its
bids over $\mcI_i$ so that the opt-out value $e_i$ is the same for each
$j \in\mcI_i$, and therefore, without loss of utility, $i$ may choose a seller pool 
using a ``consistent" strategy, where for any $j\in \mcI_i$, $d_i^j = d_i^k, \
\forall \ k \in \mcI_i$, and still have feasible best replies. 
Our result shows that a buyer may select $\mcI_i$ in order to maximize its
utility while maintaining a coordinated bid strategy. 
It is intuitive that, if $j^*
< I$, a buyer may increase the size of $\mcI_i$, thereby lowering its bid
quantity while obtaining the same (potential) allocation $a_i$. 
(OWN WORDS!)
One important question to ask is why a bidder should bid with identical unit
prices on (j) all auctions and not reduce the unit price to a level where he still wins the
amount q i . The reason for this can be found in the pricing rule of the PSP auction. 
% BUYER COORDINATION
{
\lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
(z_i,y_i)$, where $\forall \ j \in \mcI_i$,
\begin{align*}
    z_i^j &= e_i^{j^*}(a), \\
    y_i^j &= \theta_i'(z_i^j).
\end{align*}
Furthermore,
\begin{equation}\label{allocationcoordination}
    a_i^j(z_i,y_i) = z_i^{j},
\end{equation}
and
\begin{equation}\label{costcoordination}
    c_i^j(z_i,y_i) = y_i^{j},
\end{equation}
where $i$'s strategy is as in Proposition \ref{buyerstrategy}.
}\\
\textbf{Proof:}
As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
u_i(s_i;s_{-i})$. In full notation, we intend to show
$$
    u_i((d_i,p_i);s) \le u_i((z_i,y_i);s_{-i}).
$$
If there exists a seller who can fully satisfy $i$'s demand,
then $\vert\mcI_i\vert = 1$, and the case is trivial as no
coordination is necessary for a single bid. (SPECIAL CASE OF MONOPOLY? THINK!)\\
Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
multiple sellers.
We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $u_i$.
Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
largest bid quantities are considered first; the index of seller $j^*$ defines
a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
$d_i^{j^*}$ is the minimum quantity offered by any $j\in \mcI_i$,
so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$; $\mcI_i$ also defines the
maximum quantity bid of any $k \ni \mcI_i$.
Thus by (\ref{buyercoordinate}) and (\ref{opt-minallocation}), $\forall \ j\in \mcI_i$,
$k\ni\mcI_i$,
$$
    e_i^k(a) \le z_i^j = e_i^{j^*}(a) \le e_i^{j}(a),
$$
and so, 
\begin{equation}\label{minimaleq}
    e_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+,
\end{equation}
The buyer valuation function (\ref{buyervaluation}), guarantees
that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
\ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
be accepted. 
As $D_i$ is non-decreasing, $\forall \ j\in \mcI_i$,
$k\ni\mcI_i$,
$$
    D_i^j(y_i^j) \ge D_i^j(p_i^{j^*})\ge D_i^j(p_i^{k}).
$$
Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
$e_k^{j^*}(a) \ge e_i^{j^*}(a)$ and so $d^j - d_k^j < z_i^{j}$, resulting in a
partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
set, (\ref{buyercoordinate}) states that $n$ is such that $e_i^{j*}(a)
\ge e_k^{j^*}(a)$ for any $k$, therefore such a buyer $k$ cannot exist.
\iffalse
We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
$$
    {\theta_i}'(e_i^{k}(a)) \ge {\theta_i}'(e_i^{j^*}(a)) \ge y_i^j.
$$
Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$...
\fi
Thus (\ref{minimaleq}) holds and so, by (\ref{dataallocation}),
\begin{align*}
     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j, \bigg\lbrack D^{j} - \sum_{p_k^{j}> y_i^{j}}
d_k^{j}\bigg\rbrack^+\bigg) \\
    &= z_i^{j}= e_i^{j^*}(a)
\end{align*}
where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
Now, since a buyer is only charged with the cost of excluding other players from the market, the
unit price does not influence the final charges. This unit price reflects the
valuation of the total resources gained from the multi-auction market, and so a buyer uses this price on all
auctions.
We have, $\forall \ j\  \in \mcI_i, \ \forall \ k \ni \ \mcI_i$,
$$
    y_i^j \ge p_i^j \ge p_{i^*}^j\ge p_i^k,
$$
and we observe that from (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
0 \ \forall \ y < p_{i^*}^j$, and so $y=0 \le \epsilon \Rightarrow e_i^j(a) = 0$,
and so clearly $z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
\begin{align*}
    \displaystyle\sum_{j\in\mcI_i} c_i^j(z_i,y_i) =\sum_{j\in\mcI_i}
c_i^j(z_i,p_i),
\end{align*}
thus (\ref{costcoordination}) simply shows that changing the price $p^j_i$ to $y^j_i$ does not exclude any
additional buyers, as the bid $p^j_i$ was already above the reserve price of any
seller $j \in \mcI_i$.
We proceed to demonstrate that $x_i$ does not result in a loss of utility for
buyer $i$; we will show that
$$
    u_i \le u_i(z_i,y_i).
$$
From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = e_i^j(a(z_i,y_i))$, 
and so,
$$
    \theta_i\circ e_i^j(a(z_i,y_i)) = \theta_i\circ e_i^j(a),
$$ 
which holds $\forall \ j\in\mcI_i$.
Therefore, by the definition of utility (\ref{buyerutility}),
and the buyers' valuation (\ref{buyervaluation}), 
\begin{align*}
    &\theta_i\circ e_i(a(z_i,y_i)) - \theta_i(a)\circ e_i(a) \\
    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - z) \ dz.
\end{align*}
Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
$\theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
%1. buyers have same d but diff p
%2. " same p but diff d i.e. d1 < d2
Finally, as we do
not increase the aggragate demand of the buyer, $\sum_{j\in\mcI_i} c_i^j(s) \le 
\sum_{j\in\mcI_i} b_i^j$, and so $x_i$ is feasible.

In effect, we are using the buyer demand
to partition the auction space based on their type (EXPLAIN). \\

\subsubsection{Incentive Compatibility}

We proceed to claim that the optimality of truth-telling holds in our
formulation, where the market functions as a hybrid of \cite{semret} and
\cite{zheng}. The opt-out buyers' market is comprised of the minimal subset of
sellers with the largest amounts of available data, described in the buyer strategy as $\mcI_i$.
To achieve incentive compatibility, we find that the opt-out buyer must choose this subset so that
its overall marginal value is greater than its market price.
The buyers' market price is calculated as the maximum of the reserve prices
of the sellers in the opt-out buyers' pool.
the market prices at the %different auctions, weighted by the data provisioning vector values.
The actual bids are
obtained from the opt-out buyers' strategy. The quantity to bid is given
by the auction mechanism, i.e. (\ref{dataprice}) and (\ref{datacomposed}), as
the maximim possible quantity of data that a buyer $i$ can bid over its seller
pool while maintaining its aggragate marginal valuation greater than the aggragate of
minimum prices maintained by the sellers in $i$'s pool.
As with a single resource, \cite{semret} and
\cite{lazar}, we show that truth-telling is optimal for the buyer, i.e. in each auction, the buyer sets
the bid price to the marginal value.

Seller $j$'s reserve price is determined by a
buyer $i \ni \mcI^j$, and therefore, even if this price is zero,
then $p^j = \epsilon \ge 0$.

We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
there exists a local market
equilibrium (NOTE: NOT GLOBAL! YET). We have the following Proposition. For
completeness, we use the full notation. (BAD SENTENCE)

{
\proposition{(Incentive compatibility in local auctions)}
For any seller $j$, let time $t \in \tau$ be fixed and for any buyer $i\in
\mcI^j$, let $s_{-i}$ also be fixed. )VALIDATE: FOR ALL j) Define,
\begin{align}
\begin{split}\label{eta}
    \eta_i &= \sup\bigg\lbrace x\ge 0 : 
 {\theta_i}'(x) > \bar{P}_i^j(x)\bigg\rbrace, 
\end{split}\\
\begin{split}\label{chi}
    \chi_i &= \sup\bigg\lbrace x\ge 0: 
\displaystyle\int_0^x 
    \bar{P}_i(x) \ dx \le \sum_{j\in\mcI_i}b_i^j \bigg\rbrace,
\end{split}
\end{align}
$z = \min(\eta_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
\mcI_i$, 
$$
    v_i^j = e_i^{j^*}(z) 
$$
and 
$$
    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
$$
Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
s_{-i})$.
%and fix $j$'s reserve price $p^j$ as is defined by (\ref{newprice}). 
With reserve prices $p^j >0$, there exists a ``truthful" local game embeddeded
in each local auction, and thus an equilibrium point for the local auction. 
}\\
\textbf{Proof:}
For the buyer, we show that $t_i$ is an $\epsilon$-best reply. That is,
$$
    u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;s_{-i}).
$$
Let $z = \eta_i^j$. We have that $i\in\mcI^j$, 
and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
max of the reserve prices $p_i^j,\ \forall \ j\in\mcI_i$, therefore
(\ref{eta}) is such that,
$$
    \theta_i'(z) > \bar{P}_i^j(z),
$$ 
which implies, as (MORE) $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
we have $\forall \ j \in \mcI_i$, 
\begin{align*}
    w_i^j &> P_i^j(v_i^j) \\
    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
\end{align*}
And so, by (\ref{dataallocation}),
\begin{align*}
    a_i^j(t_i) &= v_i^j \\
    \Rightarrow \displaystyle\sum_{j\in\mcI_i} a_i^j(t_i) &= z.
\end{align*}
Therefore,
\begin{align*}
    \displaystyle\sum_{j\in\mcI_i}&\int_0^{v_i^j} P_i^j(x) \ dx =  \int_0^{z}
    \bar{P}_i^j(x) \ dx \\
    &= \sum_{j\in\mcI_i}\int_0^{e_i^j(z)} P_i^j(x) \ dx.
\end{align*}
Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
s_{-i}) + \epsilon$. The buyer coordinated strategy, from Propositions
\ref{coordinationlemma} and
\ref{buyerstrategy}, gives $s_{i^*} = (e_i\circ a_i(s), \ \theta_i'(z)) =
(z_i, c_i)$, where
for each $j\in \mcI$, $a_i^j(s_{i^*}; s_{-i}) = z_i^j$,
then clearly $u_i(s_{i*}, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
u_i(s_i;s_{-i}) > \epsilon$. Denoting $z_i^j$ (fixed) as $\zeta$, 
$$
    \int_z^{\zeta} {\theta_i}'(x) \ dx- \int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
$$
For concave valuation functions, the first-order derivative of $\theta$ at point
$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
/ \theta'(0)$ guarantees that new bids will differ by at least
$\epsilon$, and as such, buyer $i$ will remain in
any local auction with reserve price determined by (\ref{???}). We therefore
verify that,
$$
    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
dx \le \epsilon,
$$
and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
$$
    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
$$
If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
exist.

We consider the other term in the minimization; let $z=\chi_i$. We have that
For any coordinated bid $s_i$ such that $u_i(z_i, c_i) > u_i(t_i)+
\epsilon$, then $\zeta > z
\Rightarrow c_i(s_{i}) > b_i$, and so is infeasible. 
Finally, by Lemma \ref{userunion}, for a single buyer-seller interaction, we
have that $f_i = f^j \Rightarrow \theta_i \circ e_i^j = \theta^j \circ e_i^j$.
Therefore $\theta_i' = {\theta^j}'$. We have by Proposision
\ref{sellerstrategy} and (\ref{???}eqn 30), that $\theta^j = \max_{i\in\mcI^j}
\theta_i$, and so for any $i\in\mcI^j, \theta^j(z) \ge \theta_i(z)$, and so $j$
cannot set a higher reserve price, and also cannot sell more data than the buyers'
bids, so we have that $j$'s bid is both truthful and optimal.
\\----------------------REF-------------------------\\
% NEW MARKET PRICE
\begin{align}
\begin{split}
    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
s_{-i}^j) \\
    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
\end{split}
\end{align}
% NEW ALLOCATION RULE
\begin{align}
\begin{split}
    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
\end{split}
\end{align}
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
    D^j \big] : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
\end{split}
\end{align}
% DATA ALLOCATION RULE
\begin{align}
    a_i^j(s) \\
    &= \min\bigg\lbrace e_i^j(D_i),
    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
\end{align}
% DATA COST
\begin{align}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
p^j \bigg(ai^j(0; s_{-i}^j)
    -a_i^j(s_i^j;s_{-i}^j)\bigg).
\end{split}
\end{align}
% BUYER DEMAND 
\begin{equation}
    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
\end{equation}
% BUYER REVENUE 
\begin{equation}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
\end{equation}
% SELLER REVENUE 
\begin{equation}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
\begin{equation}
    \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{equation}
\begin{equation}
    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
 \int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}
\begin{equation}
    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
\begin{equation}
    d_i^j \ge e_i^j(a)
\end{equation}
\begin{equation}
    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
\end{equation}
\begin{equation}
    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
\end{equation}
\begin{equation}
   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
\end{equation}
\\----------------------------------------------------\\
(SELLER FINISH)\\
This forms a ``truthful" local game embeddeded within $j$'s auction with strategy space
restricted to $\epsilon$-best replies from buyers $\in \mcI^j$. Therefore we have that a
fixed point in the ``truthful" local game is a fixed point for the auction. We
further argue that as the set $\mcI^j$ is
computed at each bid iteration, that our result holds for time $(t+1) \in \tau$.

{
\lemma{(Static Data Nash Equilibrium)} 
}

% DATA NASH EQ
{
\theorem{(Data Nash Equilibrium)}
Using the rules of the data auction mechanism, the CMHK
\cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
equilibrium. 
}\\
\textbf{Proof:}
2. using the min price of sellers in the auction i.e. ${\theta_i}'(d_{i^*}^j) =
p^j$ is OK, \\
3. that bids are still feasible AND optimal \\
4. the algorithm achieves global economic equilibrium)\\
\textbf{NEED TO COVER:}\\
1. Change in buyer valuation \\
2. New buyers\\
3. Not enough buyers \\
4. Not enough data\\
\textbf{TRY:}\\
Sellers only act when the resources obtained by the buyers influence their
respective reserve prices, which agrees with the seller stragety of attempting
to sell their data in the first iteration. Therefore we claim there exists a
market stability and therefore, the existence of a Nash equilibrium. As the
valuation of the sellers is derived by the demand of the buyers, who are
bidding equivalent bids over a minimum subset of buyers, we claim that the seller
strategy, along with the seller constraint (\ref{??}) results in a global
market equilibrium.
We have shown that the local
equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
Now, suppose that buyer $i^*$ computes its best response $s_i^j = (v_i^j, w_i^j)$
Finally, suppose that
a buyer $k$ enters the market such that for some buyer $l\in\mcI^j$,
$$
    \displaystyle\sum_{i\in\mcI^j} p_i^je_i^j(a) + p_k^je_k^j(a) \ge
\sum_{i\in\mcI^j} p_i^je_i^j(a) - p_l^je_l^j(a),
$$
that is,

NOTES: (today)\\
2. finish seller incentive compat\\
3. work on progression\\
4. check reserve price = monopoly price

\subsection{Efficiency}

Formally, the
mechanism is equilbriumcient if at equilibrium, the allocation maximizes
$\sum_i\theta_i(a_i)$.
(NEED OWN WORDS)
The objective in designing the auction is that, at equilbrium, resources al-
ways go to those who value them most. Indeed, the PSP mechanism does
have that property. This can be loosely argued as follows: for each player,
the marginal valuation is never greater than the bid price of any opponent
who is getting a non-zero allocation. Thus, whenever there is a player j
whose marginal valuation is less than player i 's and j is getting a non-zero
allocation, i can take some away from j , paying a price less than i 's marginal
valuation, i.e. increasing u i , but also increasing the total value, since i 's
marginal value is greater. Thus at equilibrium, i.e. when no one can unilat-
erally increase P their utility, the total value is maximized.

\subsection{Convergence}

\end{multicols}

\begin{thebibliography}{9}

\bibitem{zheng}
L. Zheng, C. Joe-Wong, C. W. Tan, S. Ha and M. Chiangs, 
\textit{Secondary markets for mobile data: Feasibility and benefits of traded
data plans}, 2015 IEEE
Conference on Computer Communications (INFOCOM), Kowloon, 2015, pp. 1580-1588.

\bibitem{lazar}
A. A. Lazar and N. Semret, 
\textit{“Design and Analysis of the Progressive Second Price Auction for Network
Bandwidth Sharing,”} Telecommunication Systems, Special Issue on Network Economics, 2000.

\bibitem{semret} 
N. Semret, 
\textit{“Market Mechanisms for Network Resource Sharing,”
Ph.D. thesis}. 
Columbia University, 1999.

\bibitem{tuffin}
Bruno Tuffin,
\textit{Revisited Progressive Second Price Auction for Charging
Telecommunication Networks}.
[Research Report] RR-4176, INRIA, 2001.

\bibitem{qpsp}
Clare W. Qu, Peng Jia, and Peter E. Caines,
\textit{Analysis of a Class of Decentralized Decision Processes: Quantized
Progressive Second Price Auctions},
46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
779-784.

\bibitem{cmhk}
\textit{China Mobile Hong Kong Company Limited}.
\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html}.
2018

\bibitem{iia}
Andreu Mas-Colell, Michael Dennis Whinston, and Jerry R. Green, 
\textit{Microeconomic Theory}. Oxford University Press. 1995. p. 794.

\bibitem{matt}
Matthias Roggendorf and Fernando Beltr{\'a}n,
\textit{Simulation Model for the Dynamic Allocation of Network Resources in a
Competitive Wireless Scenario}. Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
pp. 54 - 64.

\bibitem{diffserve}
N. Semret, R. R. F. Liao, A. T. Campbell and A. A. Lazar, 
\textit{Pricing, provisioning and peering: dynamic markets for differentiated Internet services and
implications for network interconnections}, in IEEE Journal on Selected Areas in
Communications, vol. 18, no. 12, pp. 2499-2513, Dec. 2000.

\end{thebibliography}

\end{document}

### 2018-04-18 paper_wc_4-12.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 paper_wc.tex
@@
 
-In applying a distributed PSP implementation to CMHK market, we
+In applying a distributed PSP implementation to CMHK's secondary market, we
 find that
@@
 In this work, we propose \emph{a distributed progressive second price (PSP) auction in
-order to maximize social utility in the CMHK market}. Using the
+order to maximize social utility in this secondary market}. Using the
 distributed PSP mechanism on CMHKs data
@@
 
-(MOVED: TO ORGANIZE)\\
-The main contribution of this work 
-is an auction mechanism inspired by the classic PSP throughput problem. In
-order to apply a distributed PSP implementation to the CMHK market,
-we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the communication
-expense from numerous local auctions trading an infinitely divisible resource.
-We will assume that the cost of participating in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. It is worth mentioning that CMHK users are not allowed to resell data
-purchased from the CMHK
-market, additionally, the purchased data does not carry to the next
-service period. Therefore, a market equilibrium, where
-supply equals demand, requires that users maintain incentive for truthfullness
-across a distributed setting.
-We complete a comprehensive analysis of market dynamics, (FINISH)
-To the best of our knowledge, this is the first work to provide a truthful
-mechanism in a distributed setting for data-exchange based on market behavior.
-\\
-\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
-restrictions introduced by the CMHK secondary market. We reserve this for
-future work.
-
-We claim that the CMHK market is
-able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and as our mechanism provides
-for effective communication between the connected users.
-
-Despite the small message space, with many user types, there is no single
-way to do the transformation from the direct revelation mechanism to the
-desired one. Our mechanism is naturally designed by guessing
-right direct-revelation-to-desired-mechanism transformation and building it
-into the allocation rule to be the primary step in the design. This incentive for a user to
-truthfully reveal its type is built into the user strategies. As in classic
-mechanism design, we determine the equilibria as result of incentive
-compatibility in our mechanism design. 
-We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead 
-and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
-with respect to the classic throughput problem.
-
-This is the (built-in) transformation from the
-direct-revelation mechanism to the desired message space.
-
 \subsection{Distributed Progressive Second Price Auctions}
@@
 of service level agreement configurations between Internet service
-providers.
+providers to be determined.
 
@@
 % MECHANISM
-\subsubsection{The PSP Mechanism}\label{mechanism}
+\subsubsection{The Mechanism}\label{mechanism}
 The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
@@
 revenue \cite{lazar}.
-The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
+We have the definition of an elastic valuation function. In the PSP market, a
+user is considered truthful if their bid price equals their marginal valuation,
+i.e. $p_i^j = {\theta_i^j}'$.
 \definition{\cite{lazar}}
@@
 \end{itemize}
-The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
-function.
-In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
 
@@
 \section{The Problem Model}
-
 \subsection{The CMHK Market}
 
-We construct the model for a PSP data auction for mobile users
+We begin to construct the model for a PSP data auction for  mobile users
 particpating in CMHK's secondary data-sharing market.
@@
 rational. 
-Users prefer to participate in the CMHK secondary market as it allows them to purchase
+ Users prefer to participate in the secondary market as it allows them to purchase
 additional data for a cost less than the overage fee set by the ISP. 
@@
 (private) valuation functions. 
-In general, user preferences are defined by a utility function, $u$, which 
+In general, user preferences are defined by a utility function, $u$, which typically
 represents a users' valuation of an allocation minus the price.
@@
 data. 
-We assume that data is a unary resource belonging to the seller, and
-therefore we identify each local auction with the identity of the seller
-$j\in\mcI$, and that the user valuation
-\iffalse
-is independently and identically
-distributed (i.i.d.) and
-\fi
-satisfies the conditions for an
+We will assume that the user valuation satisfies the conditions for an
 \emph{elastic demand function}, as in \cite{lazar}. 
-Finally, we assume in the CMHK market that a buyers' budget is always
-sufficient, as the alternative is to pay the overage fee to the ISP.
-
-The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
+As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
 the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
-separated (a seller does not also buy data and vice versa). Thus, we may assume
-that this is implied in our notation.
+imply using the PSP bid profile notation.
 A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
@@
 not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
-$j$. For the purposes of our analysis, we will assume that a zero bid from a
-buyer is equivalent to no bid.
-A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
-with the intent of offering a
+and seller $j$.
+A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
 quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
@@
 total amount of data requested by buyer $i$. 
+Finally, we assume that data is a unary resource belonging to the seller, and
+therefore can identify each local auction
+with the identity of the seller $j\in\mcI$.
 
@@
 from each auction in which it is participating, and therefore
-in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
-$i$ gains access to the full grid $s$. However, 
+in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
+$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
+(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
 sellers can only gain information about the market grid by observing buyer
@@
 In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
+auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
 influence the CMHK market dynamics, with the sellers taking a secondary role
@@
 
+The main contribution of this work 
+is an auction mechanism inspired by the classic PSP throughput problem. In
+order to apply a distributed PSP implementation to CMHK's secondary market,
+we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
+to change their bid strategies, and as each user only has \emph{local}
+information about the bidding environment, it is clear that an unconstrained
+market, even with a finite number of users, could suffer from the communication
+expense from numerous local auctions trading an infinitely divisible resource.
+We will assume that the cost of participatingn in the CMHK secondary market is
+absorbed by the bid fee, which could represent data used in submitting bids, or
+a fee charged per unit of data, or a flat rate charged at the completion of the
+purchase. We perform a simple survey of these bid fee models, we
+provide some idea of the expected revenue of the mobile data ISP (NEED
+STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
+market, additionally, the purchased data expires (does not carry to the next
+service period). Therefore, a simple definition of market equilibrium, where
+supply equals demand, is insufficent to complete a comprehensive analysis of
+the CMHK data-exchange market behavior. We will make an attempt to address why
+our formulation at least partially considers some of these issues (BAD), such
+as the impact of the bid fee on user behavior. (MOVE SOME OF THIS UP)
+Finally, we  .... (WHAT? COMPLETE THE THOUGHT)
+
+We claim that the market is
+able to achieve an equilibrium as the sellers and buyers have an
+incentive for a collaborative exchange, our mechanism provides the functions
+for the effective communication between the connected users. It was shown in
+\cite{lazar} that a $2$-dimensional message space is sufficient for the PSP
+auction. Using a restricted message space is essential for the distributed
+nature of our design (EXPLAIN), however, as a given message can come from many
+possible types, there is no single
+way to do the transformation from the direct revelation mechanism to the
+desired one. This is equivalent to guessing the
+right direct-revelation-to-desired-mechanism transformation and building it
+into the allocation rule from the start. (FINISH!)
+We claim that in
+this secondary market our formulation not only holds the desired VCG qualities,
+but minimizes comminication overhead (and so possibly fees paid to the ISP)
+and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
+with respect to the classic throughput problem.
+
 \subsection{User Behavior}
 
-We assume that the CMHK market does not have network
-bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper. We
-conduct a comprehensive analysis, deriving a globally optimal strategy suited for
-users with local information in a distrubuted data-sharing model. 
-Users in the CMHK market do not need to bid on a complete ``route", as in the
-bandwidth allocation problem \cite{semret}. Instead, our mechanism allows a buyer
-to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
+We are not concerned with network
+bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
+we reason that there remains an optimal user strategy. As a user no longer needs
+to bid on a complete (but arbitrary)
+cluster of nodes with minimum bandwidth allocation (defined as a route in
+\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
 utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
-part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
-will determine its bid quanities by,
-\begin{equation}\label{opt-out}
-    e_i(a) = [e_i^j(a)]_{j\in\mcI}.
-\end{equation}
-In a general sense, this abstraction applies our \emph{user strategy}
+market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
+its market behavior. In a general sense, $e$ applies our user \emph{strategy}
 to the PSP rules.
+Our reserve price function is determined by the subset of nodes participating in the
+auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
+auctions will be influenced only by the submission of bids from buyers to
+sellers. As a buyer may have access to multiple auctions, the sellers will be
+dynamically influenced by the market via the $\epsilon$-best replies from the
+buyers. We demonstrate that as the valuation function of seller $j$ is dependent
+on the buyers demand, and further show evidence of symmetry in the strategies of
+buyers and sellers.
+
+\subsubsection{Buyer Strategy}
+
 % OPT-OUT BUYER
 We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is now of the form,
+function $\theta_i$, the value of the allocation minus the cost,
 \begin{equation}\label{buyerutility}
@@
 \end{equation}
-where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
-the buyers' valuation of allocation $a$ across local markets (and thus multiple sellers).
-In this way we extend the PSP rules described
-in \cite{semret} to design equilibria across subsets of local data-exchange markets.
-
-The sellers, $j\in\mcI$ are not associated with an opt-out function, we
-consider their valuation to be a functional extension of the buyers, where
-$\theta^j$ is constructed by buyer demand.
-The sellers strategy can only be to determine the reserve price of their local
-auction, using only information from buyers who have not opted out.
-In our analysis, we demonstrate market dynamics, and further show evidence of symmetry in the strategies of
-buyers and sellers.
-
-\subsubsection{Market Dynamics}
-The buyer demand largely motivates the market price function, however, the
-distributed nature of the market prevents any single user from knowing the
-market demand for a quantity of data. All users have knowledge of market
-supply, as this is public information, however only buyers
-are able to determine supply or demand across multiple auctions after time $t=0$, and then only from auctions
-in which they participate. \\
-\textbf{Remark:}
-It is possible that a seller would be able to derive information about other
-auctions by examining buyer bids over time, particularly if the seller had knowledge of the
-buyer strategy. (FUTURE WORK?)\\
-In order to represent the public platform of the secondary market, we model the ISP as
-a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
-in any auctions. At time $t=0$, a seller $k$ entering the market will have submitted bid
-$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform.
-
-A given demand may lead to diffent prices, which emerge directly from the users valuation
-of the resources and, possibly, their decision strategies. The seller does not
-require a priori demand information.
-It is worth mentioning that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, to derive properties.
-The mechanism itself does not require any knowledge of user demand or
-valuation. 
-\iffalse
-The ISP overage
-charge inducing an upper bound on the sellers' reserve prices implies that
-supply will always be greater than demand, thereby reducing the sellers'
-influence on market dynamics.
-\fi
-
-As the buyer valuation is elastic, even infinitesimal changes in the market dynamics can be
-modeled. This, and the homogenous nature of data in the CMHK market, 
-allows for the analysis of additional constraints imposed by the user
-strategies. Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
-A buyers' valuation of an amount of data represents how much a buyer is willing
-to pay for that amount. 
-This is equivalent to the bid price that
-satisfies $\theta_i$ given a fixed amount of data. We determine the
-buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
-possible unit price. We have,
-% BUYER PRICING 
-\begin{equation}\label{buyerinversedemand}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
-\end{equation}
-where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
-$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
-We determine that the market supply function is equivalent to buyer demand, and 
-acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
-% BUYER DEMAND 
-\begin{equation}\label{datasupply}
-    \rho_i(y) = \sum_{j\in\mcI : p_i^j\le y} D^j.
-\end{equation}
-We note that $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Therefore, in a coordinated bid, the utility-maximizing bid price is the
-lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers. We will later show, in Proposition
-\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
-bids, i.e. using the same bid for all auctions.
-Using buyer bid quantity $e_i^j(a)$, from (\ref{opt-out}), 
-we have the following Lemma,
-{
-% BUYER CONSTRAINTS
-\lemma{(Buyer constraints)}\label{buyerconstraints}
-Let $i\in\mcI$ be a buyer with bid, $s_i = (e_i(a), p_i)$, which must obey
-the following constraints,
-\begin{equation}\label{buyercapmax}
-    \sum_{j\in\mcI} e^j_i(a) \le D_i,
-\end{equation}
-and, as $i$ is rational, and therefore utility-maximizing, $i$ must have
-sufficient bids $s_i^j > 0$ so that,
-\begin{equation}\label{buyercapmin}
-    \sum_{j\in\mcI} d^j_i \ge D_i,
-\end{equation}
-where $d_i^j$ denotes the bid quantity of seller $j$.
-}\\
-\textbf{Proof:}
-A rational buyer does not want to purchase extra data, as this would be
-equivalent to overpaying, and so (\ref{buyercapmax}) holds. We also assume that
-$i$ wants to fufill their data requirement, and so (\ref{buyercapmin}) implies
-that $i$ submits positive bids to a set of buyers that will be able to fufill
-their demand.
-
-The seller is similarly represented, however a seller only has
-information from buyers in its own auction, and may only be indirectly influenced by
-buyers in other auctions. So from the perspective of the
-seller we have a more direct interpretation of valuation as revenue.
-We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} e_i^j(a), 
-\end{equation}
-and define the ``inverse" of the buyer demand function for seller $j$ as
-potential revenue at unit price $y$, we have, 
-% SELLER REVENUE 
-\begin{equation}\label{sellerinversedemand}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
-price. Now, we determine that, in addition to some natural constraints, the sellers' highest
-``possible" price is conditioned by
-additional restrictions on its pricing function, the motivation for which is
-that a buyer has the choice to opt-out of any auction, and so seller $j$ has an
-incentive to set its reserve price to include enough buyers to sell all its
-data. Thus we have the following Lemma,
-{
-% SELLER CONSTRAINTS
-\lemma{(Seller constraints)}\label{sellerconstraints}
-Let $j\in\mcI$ be a seller with bid $s^j$, then $j$ must obey the following constraints.
-A bid $s_i^j= (d_i^j, p_i^j)$, to buyer $i$ must be such that,
-\begin{equation}\label{datacapmax}
-    \sum_{i\in\mcI} d^j_i \le D^j,
-\end{equation}
-In addition, for a rational seller, the reserve price must
-satisfy, $\forall \ i\in \mcI$,
-\begin{equation}\label{reservepricemin}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j),
-\end{equation}
-and,
-\begin{equation}\label{reservepricemax}
-   p_i^j \le \max_{i\in\mcI}\big(p_i^j).
-\end{equation}
-Finally, as $j$ is rational, $j$ must submit enough bids $s_i^j >0$ so that,
-\begin{equation}\label{datacapmin}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \ge D^j.
-\end{equation}
-}\\
-\textbf{Proof:}
-The first statement is obvious, 
-a seller cannot sell more data than they have,
-Then, (\ref{reservepricemin})
-follows from the assumption that $j$ is rational, and so utility-maximization
-acts as revenue maximization, a rational seller will not sell its
-data at a price less than the lowest offer. Finally, as a rational seller will
-attempt to maximize profit, and will try and sell all of its data, and so we
-must have sufficient demand
-from the buyers. Therefore, (\ref{reservepricemax}) and (\ref{datacapmin}) hold. Together, (\ref{datacapmax}) and
-(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} e_i^j(a) >  D^j$. In
-this case, by (\ref{dataallocation}), $j$ may submit a partial bid to a buyer
-$i$ so that $\sum_{i\in\mcI} d^j_i = D^j$.
-
-We proceed to determine the properties and characteristics of the user valuation functions. Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-distributed across the CMHK market via bids in local auctions. 
-As such, buyer behavior is influenced by opponent bid profiles from multiple auctions.
-We therefore determine that the valuation of any user must be modeled as a function of the entire
-marketplace. Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We model the valuation of
-users based on the opt-out user behavior, thereby including the buyers'
-influence on the market. We have already introduced the composition $\theta_i
-\circ e_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
-(\ref{datademand}) and (\ref{sellerinversedemand}). We first note that, in
-general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
-$$
-    \theta(x) = \int_0^x f(z) \ dz,
-$$ 
-as in \cite{semret}. Now, we have the following Lemma,
-{
-\lemma{(User valuation)}\label{uservaluation}
-For any buyer $i\in\mcI$, the valuation of a potential
-allocation $a$ is, 
-\begin{equation}\label{buyervaluation}
-    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-Now, we may define seller $j$'s valuation in terms of revenue, so we have,
-\begin{equation}\label{sellervaluation}
-    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ e_i^j(a) = \sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-}
-\textbf{Proof:} 
-We assume that a buyer wants to minimize the cost of purchasing their data
-requirement, at the same time ensuring they get the full allocation $e_i(a)$,
-and so must minimally meet $j$'s reserve price. 
-A seller will try to maximize profit, 
-and so will try to sell all of its data.  By Lemma
-\ref{buyerconstraints} and Lemma \ref{sellerconstraints}, we have,
-$d_i^j = e_i^j(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j =
-\sum_{i\in\mcI} e_i^j(a) = D^j = D_i$. It is worth observing that this result
-does \emph{not} imply that $s_i=s^j$. Let $\xi$
-be a unit of data from buyer bid quantity $e_i^j(a)$.
-If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
-similarly decrease. The lost potential revenue for seller $j$ is the price of
-the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
-$$
-    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
-$$
-Thus (\ref{sellervaluation}) holds.
-As we may use the same argument for (\ref{buyervaluation}), we complete the
-proof with the observation that the function $f^j$ (resp. $f_i$) is the first
-derivative of the valuation function with respect to
-quantity, and therefore, in this context, represent the marginal valuations of the
-users, ${\theta^j}'$ (resp. $\theta_i'$). Finally, the sellers' natural utility is the potential
-profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
-paid to the ISP, as it is not a component of our mechanism, and as a discussion
-of mobile data plans is outside the scope of this paper.
-
-\subsubsection{Buyer Strategy}
+where $e_i : [0, \infty)^I \rightarrow [0,\infty), \ \forall \ i \in \mcI$. 
+We extend the P2P rules described
+in \cite{semret} to account for a set of \emph{local} data-exchange markets.
+
+Suppose the total amount of seller $j$'s data on the network at the instance that
+user $i$ joins the auction is $D^j$. 
+A sellers' allocation cannot exceed the total amount they have available,
+i.e. $\sum_{i\in\mcI} a_i^j \le D^j$. This will hold simultaneously for each $i \in
+\mcI$ if and only if 
+\begin{equation}\label{isp}
+    D^j \ge \sum_{i\in\mcI} \ D_i.
+\end{equation}
+We define the only ``seller" to satisfy (\ref{isp}) to be the ISP.
+We will show that in our
+algorithm, sellers are restricted to subset of buyers $\in\mcI$, and provide a
+buyer strategy defining when a rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
+extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
+We assume that buyers and sellers are separated (a seller does not also buy
+data and vice versa).
 
@@
 entire data cap, and only sell the fractional overage. In this case, we
-determine that some buyers must split their bids among multiple sellers. 
-We propose the following strategy to determine when rational
-(utility-maximizing) buyers will opt-out of a local auction. (QUESTIONING WHETHER OR NOT $\mcI_i$ SHOULD
-BE ORDERED BY DATA, OR IF PRICE IS BETTER, PRETTY SURE IT IS OK, WILL FIND OUT
-IN LATER PROOFS)
+determine that buyers must split their bids among multiple sellers. 
+We propose the following strategy, 
 % BUYER STRATEGY
@@
 \end{equation} 
-The buyer strategy produces a minimal subset of sellers $\in \mcI$ 
-able to satisfy buyer $i$'s demand. For 
+The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
 fixed $n$ we will denote this subset,
@@
 \end{equation}  
-Now let $j^* = n \le I$ represent the seller with the least amount of data
-$\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$, and define $i$'s bid
-vector $e_i$ with respect to its strategy, where
+Now let $j^* = n \le I$, and define,
 \begin{equation}\label{opt-minallocation}
-    e_i^j(a) \triangleq \begin{cases} e_i^{j^*}(a), \quad j\in\mcI^j,\\
-            0, \quad j\ni\mcI^j.\end{cases}
-\end{equation}
-Now, (\ref{opt-minallocation}) holds $\forall \ j\in\mcI$,
-and we have that $e_i$ defines an optimal feasible strategy for buyer $i$.
+    e_i(a) \triangleq e_i^{j^*}(a)
+\end{equation}
+$\forall \ j \in \mcI_i$.
+As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
+we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
 }\\
 \textbf{Proof:}
-We assume that a buyer will try and fill their data requirement.
+
+We assume that a buyer wants to fufill their data requirement.
 In the case that there exists a seller who can completely satisfy a buyers'
 demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
-as the set $\mcI_i$ is ordered by the quantity of the sellers' bids, $i$ may discover 
+as the set $\mcI_i$ is an ordered set, $i$ may discover 
 $j^*$ by computing $\mcI_i$.
-Suppose that $D_i >
+If we suppose that $D_i >
 \sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
-We model the ISP at time $t>0$ as a seller $\kappa$ with bid $s^\kappa =(d^\kappa, p^\kappa)$,
-where $d^\kappa > D^j, \
+We model the ISP as a seller $\kappa$ with bid $s^\kappa =(D^\kappa, P^\kappa)$,
+where $D^\kappa > D^j, \
 \forall \ j\in\mcI_i$, and
-$p^\kappa$ represents the overage fee for data set by the ISP, which we note is also the upper bound of the sellers'
+$P^k$ represents the overage fee for data set by the ISP, which is also the upper bound of the sellers'
 pricing function, and so again (\ref{buyercoordinate}) holds.
-Now, consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
-The allocation rule (\ref{dataallocation}) determines that the data will be
-split proportionally
+Now consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
+The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
 between all buyers with the same unit price. 
 It is possible that the resulting partial allocation of data to $i$ and $k$
-would not satisfy some demand. As the two cases $i$ and $k$ are the same, we
-will only consider one. Suppose seller $j$ updates its
-bid to reflect the new data quantity, $j$'s bid quantity at time $(t+1)$,
-$d_i^{j(t+1)}$, is such that
-$d_i^{j(t+1)} < e_i^{j(t)}(a)$ where $e_i^{j(t)}(a)$ is $i$'s bid at time $t$.
-Then, by the definition of $\mcI_i$, once the buyer implements its strategy, we can
-only have that $j \ni \mcI_i$, or that $n$ has been increased so that and new seller(s)
+would not satisfy some demand. As the two cases $i$ and $k$ are the same, we consider such
+a seller $i$. Suppose seller $j$ updates its
+bid to reflect the new data quantity, so that $d_i^{j(t+1)} < d_i^{j(t)}$ (NOTE:
+IS THE DIRECTION OF THE BID CONFUSING?, i.e. $d_i^j$ from buyer (rhs) or seller
+(lhs) unclear? does it matter?) Then, by the definition of $\ell_i$, we can
+only have that $j \ni \mcI_i$, or that $n$ has been increased, and new seller(s)
 enter the pool. 
-Additionally, we consider the entrance of a new buyer $k$ at time $(t+1)$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
-words, a new buyer $k$ may enter the market with a better price, decreasing the
-value of $i$'s bid for sellers $\in\mcI_i$. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
+Additionally, we consider that at time $(t+1)$, we can have a 
+new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
+words, a new buyer $k$ may enter the market with a better price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
 $n$ so that
@@
 $k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal. We note that feasibility
-is not addressed here, as we provide this analysis in Section \ref{???}.
+and we determine that the opt-out strategy is optimal.
 
@@
 minimal ordered subset where a
-coordinated bid is possible, the reasoning for which we will address in Section
-\ref{analysis}.
+coordinated bid is possible, the reasoning for which we will address in further analysis (Section
+\ref{analysis}).
+
+\subsubsection{Buyer Influence}
+The buyer demand is a key market influence (SILLY SENTENCE), as the buyer
+valuation is elastic, even infintesimal changes in the market dynamics can be
+modeled. $\forall \ y\ge 0$, we determine that the market demand for $D^j$ is given by,
+% BUYER DEMAND 
+\begin{equation}\label{datademand}
+    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
+\end{equation}
+
+Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
+which is distributed across the secondary market via bids in local auctions. 
+Buyer behavior is influenced by opponent bid profiles from multiple auctions.
+The valuation of any user, however, is a function of the entire marketplace.  
+We first define the ``inverse" demand for any buyer $i$,
+% BUYER REVENUE 
+\begin{equation}\label{buyerinversedemand}
+    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
+        \rho^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
+\end{equation}
+For a given demand $\rho^j$, $f_i$ maps the $z$th unit of data to the lowest
+possible unit price. \\
+\textbf{Remark:} In a coordinated bid, $f_i$ is such that
+$i$ could still bid in \emph{any} auction $j\in\mcI$.
+Naturally, the coordinated bid is the
+lowest unit cost of the buyer to participate in all auctions, and corresponds to
+the maximum reserve price amongst the sellers.
+
+The seller is represented by a similar function, however a seller only has a
+single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
+seller we have a more direct interpretation of revenue.
+We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
+% SELLER REVENUE 
+\begin{equation}\label{sellerinversedemand}
+    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
+        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
+\end{equation}
+where $f^j$ maps to the highest possible unit data price.
+Thus we have the following Lemma. 
+{
+\lemma{(User valuation)}\label{uservaluation}
+For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
+\begin{equation}\label{singlevaluation}
+    \theta_i^j \circ e_i^j(a) = \int_0^{e_i^j(a)} f_i(z) \ dz,
+\end{equation}
+it follows that 
+\begin{equation}\label{buyervaluation}
+    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
+ \int_0^{e_i^j(a)} f_i(z) \ dz.
+\end{equation}
+Similarly, seller $j$'s valuation is,
+\begin{equation}\label{sellervaluation}
+    \theta^j \circ e_i(a) = \displaystyle\sum_{i\in\mcI}
+ \int_0^{e_i^j(a)} f^j(z) \ dz.
+\end{equation}
+}
+\textbf{Proof:} 
+We assume that a buyer wants to minimize the cost of purchasing their data
+requirement, at the same time ensuring they get the full allocation $e_i(a)$,
+and so must minimally meet $j$'s reserve price.
+A seller will try to maximize profit for any given allocation $a$,
+and will try to sell all of its data, and so 
+$d_i^j = e_i(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
+\sum_{i\in\mcI} e_i(a)$,
+The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
+(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)
+
+We note that except at points of discontinuity, we have
+$P_i(z) = f_i(z)$. This mechanism generalizes Vickrey
+(``second-price") auctions which are for nondivisible objects.
+
+The sellers' natural utility is the potential
+profit $u^j = \theta^j \circ e_i(a) $, where $\theta^j$ is the
+potential revenue from the sale of data composed with each buyers' opt-out
+value, $e_i(a)$. 
+We have chosen to omit the original cost of the data
+paid to the ISP, as a discussion of mobile data plans is outside the scope of this
+paper.
+
+As $j$'s behavior is restricted by
+the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
+{
+% SELLER CONSTRAINTS
+\lemma{(Seller constraints)}\label{constraints}
+Let $j$ be a seller with total data amount $D^j$.
+First, the seller must satisfy the quantity
+constraint, 
+\begin{equation}\label{quantity}
+    d_i^j \ge e_i^j(a)
+\end{equation}
+and
+\begin{equation}\label{budget}
+    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
+\end{equation}
+which implies, for any $i\in\mcI$,
+\begin{equation}\label{partialallocation}
+    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
+\end{equation}
+In addition, for a rational seller, the reserve price must
+satisfy, $\forall \ i\in \mcI$,
+\begin{equation}\label{reserveprice}
+   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
+\end{equation}
+}\\
+\textbf{Proof:}
+The first statement is obvious, 
+a seller cannot sell more data than indicated in their bid, (\ref{budget}) and
+(\ref{partialallocation}) enforce
+a data constraint for the seller. Finally, (\ref{reserveprice})
+follows from the assumption that $j$ is rational, and so utility-maximization
+acts as revenue maximization; a rational seller will not sell its
+data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)
 
 \subsubsection{Seller Strategy}
-(POSSIBILITY OF SWITCHING TO BUYER POOL ORDERED BY DATA, IF SELLER POOL GETS
-SWITCHED TOO)
-In order to to develop the seller strategy, we examine the incentive of a
-rational seller with only local information in a dynamic market of many
-buyers and sellers. A local auction, examined independently, may appear as
-single market with a single seller and many buyers, but is in fact a subset of the
-larger data-exchange market, and is subject to the trends and dynamics
-therewithin. A seller must determine allocations using only bids in its local market, while the buyers' response is based on the
-allocations and resulting opponent bids from all auctions in its seller pool.
-In addition, buyers are allowed to bid both dynamically and asychronously.
-
-In order to
-maximize revenue, the seller must also be able to respond dynamically to
-address the mutation of competitive bids in its market. In order to do this, we
-determine that the seller may modify its reserve price in response to the
-changing market dynamics. (MORE!)
-We will show that sellers are able to maximize revenue in restricted subset of
-buyers in $\mcI$, and as such will attempt to facilitate a local market
-equilibrium for this subset.
+In order to to develop the seller strategy, it is necessary we determine 
+that a seller has an incentive to
+accept fractional (CHANGE TO PARTIAL? PICK ONE) bids (i.e. sell a fraction of
+their data $D^j$). Reasonably,
+there may not exist a buyer such that $D_i = D^j$. \cite{zheng} reasons that the seller does not know the exact amount of
+leftover data available, and so they may only sell enough data to ensure that
+they will not become a buyer while they submit their total data overage to the
+secondary market. Buyers are allowed to
+bid both dynamically and asychronously, and as a seller determines allocations using only bids
+in its local market. Therefore, in order to
+maximize the revenue gained per unit of data the seller must respond to the
+varation of competitive bids in its market (MORE? FUTURE WORK? CITE?).
 
 We describe the sellers' \emph{local} auction strategy for allocating its
-data according to the constraints formed by the buyer strategy. A
-local auction may be described as a progressive game of strategy with
-incomplete, but perfect information, however in our analysis, as before, we will assume
-complete information.
+data according to the constraints formed by the buyer strategy. As
+local auction is progressive, and influenced by the $\epsilon$-best replies of
+the buyers, we will need the following Lemma. 
+We now define the local auction, which we describe, when coupled with the buyer
+responses, as a progressive game of strategy with incomplete, but perfect
+information (SAY MORE?).
 (BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
@@
 {
-\proposition{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t\in\tau$.
+\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
+Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
+For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
 Define
@@
 \end{equation} 
-The determination of $n$ produces a minimal subset 
-of buyers that maximizes $j$'s revenue at time $t$, which we will
-denote, for fixed $n$, by,
+We have, for any fixed $n$ at time $t$, a minimal subset 
+of buyers that maximizes $j$'s revenue, which we will
+denote,
 \begin{equation}\label{buyers}
@@
 \end{equation} 
-Define buyer $i^* = n-1 \le I$ as the buyer with the maximum price $\ni
-\mcI^j$.
-Then, for time $(t+1)$, set $j$'s reserve price to be, 
+Define buyer $i^* = n \le I$.
+Then, for time $(t+1)$, set $j$'s reserve price as 
 \begin{equation}\label{newprice}
-    p_i^j = p_{i^*}^j + \epsilon,
+    p_i^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon,
 \end{equation}
@@
 \end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{winner}) -
-(\ref{newbudget}) produces a local market equilibrium. 
+Allowing $t$ to range over $\tau$, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
+%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
+market equilibrium. (BLAST I RUINED THE EQ) % from time $t$ to $(t+1) \in \tau$. 
 }\\
@@
 In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}), 
-Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
-In this case, by (\ref{}) the seller must notify $i$ of a
-fractional allocation by changing the bid vector at index $i$.
-With this caveat, and Proposition \ref{buyerstrategy}, we have that the
-aggragate demand of subset $\mcI^j$ is satisfied by seller $j$, as in Lemma
-\ref{sellerconstraints}.
+price offer, determined by (\ref{sellercoordinate}), where $i^*$ loses by: (1)
+$i^*$ is excluded from $I^j$ or (2) $i^*$s demand is not met, noting as well
+that any $i\ni \mcI^j$ is also a loser. 
+In this case, by (\ref{quantity}) the seller must notify the buyer of a
+fractional allocation.
+
+%As the set of buyers is
+%computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
+%at equilibrium as it is designed so that the data offered by
+%seller $j$ equals the aggregate demand of the buyers \cite{???}
+With this caveat, we have that the aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
 Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that buyers are bidding truthfully, and so ${\theta_i}' + \epsilon
-=p_i^j + \epsilon$.
-Now, using
-(\ref{sellervaluation}), we have, $\forall \ z\ge 0$,
+that the buyer is bidding truthfully, and so ${\theta_i}' + \epsilon
+=p_i^j + \epsilon$, and as $\mcI^j\subset \mcI$, we
+note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
+(\ref{singlevaluation}), we have, $\forall \ z\ge 0$,
 \begin{align*}
@@
 
-\subsubsection{Market Dynamics under Strategy}
-
 We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. We model the impact of the dynamics of the
-data-exchange market on a local auction $j$. As we have shown, the seller
+sellers in local auctions. As we have shown, the seller
 is a functional extension of the buyer, with rules determined by the buyers'
-behavior. This gives an auction $j$ a natural logical extension into the
-global market through its buyers. We demonstrate that the symmetry between
-buyer and seller rules stretches into a symmetry across subsets of local
-auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. We have the following Lemma.
-\newpage
+behavior. Consequentially, we have the following Lemma.
+
 % USER UNION
@@
 \end{equation}
-Fix an auction $j\in\mcI$ and define the influence sets of users. 
-The primary influencing set is given as,
-%(ALL THE SELLERS FROM EACH BUYERS POOL)
+Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
 \begin{equation}\label{lambda}
-    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
-\end{equation}
-with secondary influencing set,
-%(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
-\begin{equation}\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
-\iffalse 
-(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
-\begin{equation}%\label{lambda}
-    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
-\end{equation}
-(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
-POOLS)
-\begin{equation}%\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
-***********************************
-\begin{equation}
-    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
-\begin{equation}
+    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
+\end{equation}
+\begin{equation}\label{lambda}
+    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
+\end{equation}
+\begin{equation}\label{lambda}
     \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
@@
 and for each $i\in\mcI^j$ define,
-\begin{equation}
+\begin{equation}\label{ilambda}
     \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
@@
 \end{equation}
-we have $\forall \ i \in
-\mcI^j$,
+(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
+\equiv s_i^j \in \mcI$)
+Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
 \begin{equation}\label{sym}
@@
 \end{equation}
-
-***********************************
-\fi
-Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$, we have that,
-\begin{equation}\label{unioneq}
-    \displaystyle\sum_{j\in\Lambda} \theta^j = \sum_{i\in\lambda} \theta_i.
-\end{equation}
+(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
+HAPPEN)
 }\\
@@
 profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $i$'s bid is such that $p_i^j \ge p_{i^*}^j$, where
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price in auction $j$.
+if and only if $p_i^j \ge p_{i^*}^j$.
 Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
@@
 will add sellers to its pool until its demand is satisfied. Therefore for any
-$j\in\mcI_i$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
+$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
 holds.
-Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
-of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
-s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
-\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
-
-Now, the subset $\mcI^j \subset \mcI$
+
+The subset $\mcI^j \subset \mcI$
 determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
@@
 will determine the unit price $p_{i}$ in buyer $i$'s bid.
-The reserve price (\ref{newprice}) of seller $j$ is determined at time $t$, and is
+(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
+price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
 the lowest price that $j$ will accept to perform any allocation.
-Let $p_*^j = f^j \circ e_i^j(a) $ denote the reserve
+Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
+\ref{sellerstrategy},
+we have that for each $i \in \mcI^j$, 
+$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
+Let $p_*^j=p_{i^*}^j$ denote the reserve
 price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ e_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
-\ \forall \ k \in\mcI_i$. 
-Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy}, $\forall \ i \in \mcI^j$, we have that $p_i^* \ge p_*^k,
-\ \forall \ k \in\mcI_i$.
-
-\iffalse
+[p_i^j]_{i\ni\mcI^j}$.
 Now, we have,
+%Fix any buyer $i\in\mcI^j$.
 \begin{equation}\label{rho}
     \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
+\end{equation}
+and, $\forall \ i \in \mcI^j$, 
+\begin{equation}\label{invrho}
+    f_i \circ e_i^j(a) \ge p_*^j,
+\end{equation}
+and, $\forall \ k \in \mcI_i$, 
+\begin{equation}\label{invrho}
+    p_*^j \ge f^k \circ e_i^k(a) ,
 \end{equation}
@@
 [p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-\fi
-
-The incentive of each seller $\in\Lambda$ is to sell all of its data at the
-best possible price. In the simplest case,
-consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
-\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
-$\lambda = \mcI^j$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we clearly
-have that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-In all other cases, the sellers $\in\Lambda$ are competing to sell
+
+The sellers $\in\Lambda$ are competing to sell
 their respective resources to buyers whose valuations are distributed across multiple auctions. 
 %By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-The set $\lambda$ represents all of the buyers influencing auction $j$, both
-directly and indirectly. 
-The bid price of buyer $i\in\mcI^j$ is determined by,
-\begin{equation}\label{maxbid}
-    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ e_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
-\end{equation}
-$\Lambda$ is the set of sellers that directly influence the bids of buyers
-$\in\mcI^j$. the reserve price for auction $j$ is such that,
-\begin{equation}\label{resprice}
-    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
-\end{equation}
-by Proposition \ref{sellerstrategy}.
-
-We have from Proposition \ref{sellerstrategy} that $j$ maintains a local market
-equilibrium at time $t$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
-and suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Then, a change in $q$'s valuation from time $t$ to $t+1$ will
-directly impact seller $j$. If at time $t+1$ we still have that $i$ is the
-buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
-thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
-recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
-In each case we
-have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
-fixed time $t$, and so, $\forall \ i \in\mcI^j$,
+Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
+for any $k\ne j \in \mcI_i$. 
+Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
+$\forall \ i \in \mcI^j$,
+\begin{equation}\label{feq}
+    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
+\end{equation}
+where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
+Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
+Since,
+$$
+    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
+$$ 
+there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
+we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
+It follows that buyer $i$'s bid price is given by,
+\begin{equation}\label{iprice}
+    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
+\end{equation}
+
+%where $p_i^*$ represents $i$'s coordinated bid price,
+%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
+This holds for any
+$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
+Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
+denote each as $f$ in the remainder of the proof.
+
+Now, using (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
+$i\in\mcI^j$ to be, (HERE)
+(SHOW THAT $\Lambda$ IS DISJOINT!)
+\begin{equation}\label{sumrho}
+    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p_*^k) =
+\sum_{k\in\mcI_i\cup\mcI^j}
+e_i^k(a),
+\end{equation}
+where $p^k$ is the highest unit price in the feasible set $\mcI_i\cup\mcI_k$.
+Thus we determine the aggregate demand from buyer
+$i\in\mcI^j$ over the set of intersecting markets $\Lambda$ to be, 
+\begin{equation}\label{sumrho}
+    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p^*) =
+\sum_{k\in\mcI_i\cup\mcI^j}
+e_i^k(a),
+\end{equation}
+where $p^* = \max(p^k), \ \forall \ k \in\Lambda$, and corresponds to the
+highest reserve price over all the sellers. 
+Now, by the continuity of $\theta'$, (AND)
 \begin{align*}
-    \int_0^{e_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ e_i^j(a)\\
-    &= \int_0^{e_i^j(a)} f_i(z) \ dz,
+     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\mcI_i\cup\mcI^j}\int_0^{e_i^k(a)}
+f(z) \ dz\bigg)\\
+     &=\displaystyle\sum_{i\in\mcI^j} \theta_i \circ e_i(a) \\
+     &= \sum_{k\in\mcI_i\cup\mcI^j}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
+f(z) \ dz\bigg)\\
+     &= \sum_{k\in\mcI_i\cup\mcI^j}\theta^j \circ e_i(a)\\
+     &= (\theta_i \circ \theta^j) \circ e_i(a).
 \end{align*}
-therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-Furthermore, it follows that,
-\begin{equation}\label{jdemand}
-    \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f^j(z) \ dz =
-\sum_{j\in\mcI_i}\int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-
-Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$. We have that
-the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, and so we must
-have that $p_l^* < p_i^*$,
-and necessarily, $p_i^* > p_l^*$ for
-any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
-p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$. % \Rightarrow \theta_l^q > \theta_l^k$. 
-Again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
-\ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$. 
-Lastly, 
-in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
-for $q\in\mcI_l$ or $\theta_l^q = 0$ for some $q\in\mcI_i$. Thus, any bid ouside of
-our construction
-has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$. Thus, in all cases,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold.
-We have,
-\begin{equation}\label{idemand}
-    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{e_i^k(a)}
-f_i(z) \ dz,
-\end{equation}
-which holds for all buyers and sellers that satisfy (\ref{jtoi}).
-Finally, using (\ref{jdemand}), (\ref{idemand}), 
+
+\iffalse
+************************
+Proposition \ref{buyerstrategy} defines $e_i^j(a) = D_i/ 2$, and so $0 <
+e_i^j(a)$.
+************************
+\fi
+\iffalse
+Suppose $\exists \ i \in\mcI^j$ such that $\mcI_i = j$, so that $j$ is the only
+seller in $\Lambda$.
+, and $i$'s bid quantity,
+\begin{equation}\label{iquantity}
+    d_i^* = \circ e_i(a) = \frac{a_i^j}{j},
+\end{equation}
+where $j=j^* = \argmin$ for each $i\in\mcI^j$, thus $d_i^*$ represents $i$'s coordinated bid quantity, and we have
+$s_i^j = (p_i^*,d_i^*), \ \forall \ j$ such that $s_i^j > 0$,
+\fi
+\iffalse
+
+*****************************************************************************************************
+From (\ref{jtoi}), $i\in\mcI^j \Rightarrow
+j\in \mcI_i$, so $i\in \mcI^j \cup \mcI^j$, 
+Using (\ref{buyerinversedemand}), we have the valuation of $j\in\mcI_i$,
+%$i\in\bigcap_{i\in\mcI^j}\mcI_i$,
 \begin{align*}
-    \int_0^{e_i^k(a)} f_i(z) \ dz &= \int_0^{e_i^k(a)} f^k(z) \ dz,
+      \theta^j \circ e = \sum_{k\in\mcI_i\cup\mcI^j}}&\int_0^{e_i^k(a)} f(z) \ dz,
 \end{align*}
-and
+and by (\ref{sellerinversedemand}), we have the valuation of $j$ fixed, 
 \begin{align*}
-    \int_0^{e_l^k(a)} f^k(z) \ dz &= \int_0^{e_l^k(a)} f_l(z) \ dz,
+      \theta^j \circ e = \sum_{i\in\mcI^j}&\int_0^{e_i^j(a)} f(z) \ dz,
 \end{align*}
-and the result follows by construction, and the continuity of $\theta'$:
-\begin{equation}
-    \displaystyle\sum_{j\in\Lambda} \int_0^{D^j} f^j(z) \ dz =
-\sum_{i\in\lambda}\int_0^{D_i} f_i(z) \ dz.
-\end{equation}
+and thus we have the valuation of $\Lambda^j$,
+\begin{align*}
+     \displaystyle\sum_{i\in\mcI^j} \bigg(\sum_{k\in\Lambda}&\int_0^{e_i^k(a)}
+f(z) \ dz\bigg).
+\end{align*}
+\\(FINISH!)\\
+$$
+     \displaystyle\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda}\int_0^{e_k^j(a)}
+f(z) \ dz\bigg).
+$$
+----------------HERE--------------\\
+(HOW TO MAKE SETS THE SAME???)
+Now we consider $\Lambda_i$. For each buyer $i\in\mcI^j$, we have that $p_i^j
+\ge p_i^k$
+
+Now, for $\Lambda_i \cap \Lambda^j$, and by the continuity of $\theta'$,
+\begin{align*}
+     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\Lambda_i}\int_0^{e_i^k(a)}
+f(z) \ dz\bigg)\\
+     &= \sum_{k\in\Lambda_i}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
+f(z) \ dz\bigg)\\
+      &= \sum_{k\in\Lambda^j}\bigg(\sum_{j\in\mcI_i}\int_0^{e_k^j(a)}
+f(z) \ dz\bigg)\\
+      &=\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda^j}\int_0^{e_k^j(a)}
+f(z) \ dz\bigg).
+\end{align*}
+
+(WHAT?)\\
+Therefore, $\Lambda$ is such that $j\ni \mcI_i, \ \forall \ i \ni \mcI^j$. In other words, $\Lambda$ is a
+disjoint set in the global marketplace with respect to $j$.
+****************************************************************************************************
+\fi
 
 For completeness, in the case where the ISP $\kappa$ 
-does not adhere to the market dynamics, so $p^\kappa > p^j +
+does not adhere to the market dynamics, so $P^\kappa > p^j +
 \epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
@@
 We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the CMHK market, and which we will denote the \emph{data}
+buyers and sellers in the secondary market, which we will denote the \emph{data}
 PSP rules. The rules presented here incorporate of the opt-out function with the
@@
 analysis. 
-The market price function (MPF) for a buyer in the CMHK market
+The market price function (MPF) for a buyer in the secondary market
 can be described as follows:
@@
 the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices
-of the individual sellers may vary.\\
-\textbf{Remark:} We further note that except at points of discontinuity, from
-Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
-
+\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
 %To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
@@
 \begin{split}\label{datacomposed}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+.
+    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
 \end{split}
 \end{align}
-% DATA ALLOCATION RULE
-The resulting data allocation rule is a function of the local market
-interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
-allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
+it follows that the inverse price function is aggregated over all local auctions
+$j\in \mcI$,
+% NEW INVERSE DEMAND
+\begin{align}\label{datapriceinverse}
 \begin{split}
-    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
-    &= \min\bigg\lbrace e_i^j(a), \\
-    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \big(
-D_i^j(p_i^j,s_{-i}^j)\big)\bigg\rbrace,
+    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
+    D^j \big] : \\
+    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
 \end{split}
 \end{align}
-noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool.
 Finally we must have that the cost to the buyer adheres to the second price
@@
 \end{align}
+% DATA ALLOCATION RULE
+The resulting data allocation rule is a function of the local market
+interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
+allocation from auction $j$ is,
+% and so for profile $s_i$, for any $i \in \mcI$,
+\begin{align}\label{dataallocation}
+    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
+    &= \min\bigg\lbrace e_i^j \circ D_i, \\
+    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \circ
+D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
+\end{align}
+noting that for the full allocation from all auctions we may simply aggregate
+over the seller pool, as in the previous definitions.
 
@@
 \theorem{(Data Nash Equilibrium)}
-Using the rules of the data auction mechanism, the CMHK
+Using the rules of the data auction mechanism, the secondary market described in
 \cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
@@
 \subsection{Efficiency}
-
-Formally, the
-mechanism is equilbriumcient if at equilibrium, the allocation maximizes
-$\sum_i\theta_i(a_i)$.
 (NEED OWN WORDS)

### 2018-04-18 paper_wc_proof.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 paper_wc_4-12.tex
@@
 Finally, we assume that data is a unary resource belonging to the seller, and
-therefore can identify each local auction
+therefore we identify each local auction
 with the identity of the seller $j\in\mcI$.
@@
 from each auction in which it is participating, and therefore
-in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
-$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
-(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
+in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
+$i$ gains access to the full grid $s$. However, 
 sellers can only gain information about the market grid by observing buyer
@@
 bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
-we reason that there remains an optimal user strategy. As a user no longer needs
+we reason that there remains an optimal user strategy suited for the
+data-sharing model. As a user no longer needs
 to bid on a complete (but arbitrary)
@@
 \end{equation}
-Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
+Fix an auction $j\in\mcI$ and define the influence sets of users. 
+The primary influencing set is given as,
+(ALL THE SELLERS FROM EACH BUYERS POOL)
 \begin{equation}\label{lambda}
-    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
-\end{equation}
-\begin{equation}\label{lambda}
+    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
+\end{equation}
+with secondary influencing set,
+(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
+\begin{equation}\label{llambda}
+    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
+\end{equation}
+(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
+\begin{equation}%\label{lambda}
+    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
+\end{equation}
+(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
+POOLS)
+\begin{equation}%\label{llambda}
+    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
+\end{equation}
+\iffalse 
+***********************************
+\begin{equation}
+    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
+\end{equation}
+\begin{equation}
     \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
@@
 and for each $i\in\mcI^j$ define,
-\begin{equation}\label{ilambda}
+\begin{equation}
     \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
@@
 \end{equation}
-(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
-\equiv s_i^j \in \mcI$)
-Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
+we have $\forall \ i \in
+\mcI^j$,
 \begin{equation}\label{sym}
@@
 \end{equation}
-(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
+
+***********************************
+\fi
+Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$, (ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
 HAPPEN)
@@
 profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $p_i^j \ge p_{i^*}^j$.
+if and only if $i$'s bid is such that $p_i^j \ge p_{i^*}^j$, where
+(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
+price in auction $j$.
 Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
@@
 will add sellers to its pool until its demand is satisfied. Therefore for any
-$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
+$j\in\mcI_i$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
 holds.
-
-The subset $\mcI^j \subset \mcI$
+Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
+of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
+s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
+\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
+
+Now, the subset $\mcI^j \subset \mcI$
 determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
@@
 will determine the unit price $p_{i}$ in buyer $i$'s bid.
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
+The reserve price (\ref{newprice}) of seller $j$ is determined at time $t$, and is
 the lowest price that $j$ will accept to perform any allocation.
+Let $p_*^j = f^j \circ e_i^j(a) $ denote the reserve
+price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
+[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ e_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
+\ \forall \ k \in\mcI_i$. 
 Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy},
-we have that for each $i \in \mcI^j$, 
-$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
-Let $p_*^j=p_{i^*}^j$ denote the reserve
-price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$.
+\ref{sellerstrategy}, $\forall \ i \in \mcI^j$, we have that $p_i^* \ge p_*^k,
+\ \forall \ k \in\mcI_i$.
+
+\iffalse
 Now, we have,
-%Fix any buyer $i\in\mcI^j$.
 \begin{equation}\label{rho}
     \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-and, $\forall \ i \in \mcI^j$, 
-\begin{equation}\label{invrho}
-    f_i \circ e_i^j(a) \ge p_*^j,
-\end{equation}
-and, $\forall \ k \in \mcI_i$, 
-\begin{equation}\label{invrho}
-    p_*^j \ge f^k \circ e_i^k(a) ,
 \end{equation}
@@
 [p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-
-The sellers $\in\Lambda$ are competing to sell
+\fi
+
+The incentive of each seller $\in\Lambda$ is to sell all of its data at the
+best possible price. In the simplest case,
+consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
+\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
+$\lambda = \mcI^j$. 
+Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we clearly
+have that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+In all other cases, the sellers $\in\Lambda$ are competing to sell
 their respective resources to buyers whose valuations are distributed across multiple auctions. 
 %By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
-for any $k\ne j \in \mcI_i$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
-$\forall \ i \in \mcI^j$,
-\begin{equation}\label{feq}
-    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
-\end{equation}
-where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
-Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
-Since,
-$$
-    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
-$$ 
-there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
-we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
-It follows that buyer $i$'s bid price is given by,
-\begin{equation}\label{iprice}
-    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
-\end{equation}
-
-%where $p_i^*$ represents $i$'s coordinated bid price,
-%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
-This holds for any
-$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
-Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
-denote each as $f$ in the remainder of the proof.
-
-Now, using (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
-$i\in\mcI^j$ to be, (HERE)
-(SHOW THAT $\Lambda$ IS DISJOINT!)
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p_*^k) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^k$ is the highest unit price in the feasible set $\mcI_i\cup\mcI_k$.
-Thus we determine the aggregate demand from buyer
-$i\in\mcI^j$ over the set of intersecting markets $\Lambda$ to be, 
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p^*) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^* = \max(p^k), \ \forall \ k \in\Lambda$, and corresponds to the
-highest reserve price over all the sellers. 
-Now, by the continuity of $\theta'$, (AND)
+The set $\lambda$ represents all of the buyers influencing auction $j$, both
+directly and indirectly. 
+The bid price of buyer $i\in\mcI^j$ is determined by,
+\begin{equation}\label{maxbid}
+    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ e_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
+\end{equation}
+$\Lambda$ is the set of sellers that directly influence the bids of buyers
+$\in\mcI^j$. the reserve price for auction $j$ is such that,
+\begin{equation}\label{resprice}
+    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
+\end{equation}
+by Proposition \ref{sellerstrategy}.
+
+We have from Proposition \ref{sellerstrategy} that $j$ maintains a local market
+equilibrium at time $t$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
+and suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
+that $p_*^q > p_*^j$. Then, a change in $q$'s valuation from time $t$ to $t+1$ will
+directly impact seller $j$. If at time $t+1$ we still have that $i$ is the
+buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
+thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
+recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
+In each case we
+have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
+fixed time $t$, and so, $\forall \ i \in\mcI^j$,
 \begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\mcI_i\cup\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &=\displaystyle\sum_{i\in\mcI^j} \theta_i \circ e_i(a) \\
-     &= \sum_{k\in\mcI_i\cup\mcI^j}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &= \sum_{k\in\mcI_i\cup\mcI^j}\theta^j \circ e_i(a)\\
-     &= (\theta_i \circ \theta^j) \circ e_i(a).
+    \int_0^{e_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ e_i^j(a)\\
+    &= \int_0^{e_i^j(a)} f_i(z) \ dz,
 \end{align*}
-
+therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+Furthermore, using (\ref{datademand}), it follows that,
+\begin{equation}\label{jdemand}
+    \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f_i(z) \ dz = \int_0^{D^j}
+f^j(z) \ dz.
+\end{equation}
+
+Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
+some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
+p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
+Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
+that $p_l^* < p_*^j$. We have that
+the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, and so we must
+have that $p_l^* < p_i^*$,
+and necessarily, $p_i^* > p_l^*$ for
+any buyer $l\in\lambda$ such that $l\ni \mcI^j$. 
+Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
+p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
+$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$. % \Rightarrow \theta_l^q > \theta_l^k$. 
+Again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
+\ni\mcI^q \Rightarrow p_*^q >
+p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
+buyer $i$. 
+Lastly, 
+in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
+We have that for any $l\in\mcI^k$ such that $l\ni
+\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
+for $q\in\mcI_l$ or $\theta_l^q = 0$ for $q\in\mcI_i$. Thus, any bid ouside of
+our construction
+has a zero valuation, with respect to buyers $\in\lambda$ and sellers
+$\in\Lambda$. We have,
+\begin{equation}\label{idemand}
+    \displaystyle\int_0^{D_i} f_i(z) \ dz = \sum_{k\in\mcI_i}\int_0^{e_i^k(a)}
+f_i(z) \ dz,
+\end{equation}
+\begin{align*}
+  \int_0^{D^j} f^j(z) \ dz = \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f^j(z) \ dz = \int_0^{e_l^k(a)} f^k(z) \ dz.
+\end{align*}
+Thus, by construction, 
 \iffalse
-************************
-Proposition \ref{buyerstrategy} defines $e_i^j(a) = D_i/ 2$, and so $0 <
-e_i^j(a)$.
-************************
+\begin{align*}
+    \displaystyle\sum_{i\in\mcI^j} &\bigg( \sum_{k\in\mcI_i} \int_0^{e_i^k(a)}
+f^k(z) \ dz \bigg) \\
+    &= \sum_{i\in\mcI^j}\bigg(\sum_{k\in\mcI_i}\bigg(\sum_{l\in\mcI^k}\int_0^{e_l^k(a)} f^k(z) \ dz.
+\bigg)\bigg)
+\end{align*}
 \fi
-\iffalse
-Suppose $\exists \ i \in\mcI^j$ such that $\mcI_i = j$, so that $j$ is the only
-seller in $\Lambda$.
-, and $i$'s bid quantity,
-\begin{equation}\label{iquantity}
-    d_i^* = \circ e_i(a) = \frac{a_i^j}{j},
-\end{equation}
-where $j=j^* = \argmin$ for each $i\in\mcI^j$, thus $d_i^*$ represents $i$'s coordinated bid quantity, and we have
-$s_i^j = (p_i^*,d_i^*), \ \forall \ j$ such that $s_i^j > 0$,
-\fi
-\iffalse
-
-*****************************************************************************************************
-From (\ref{jtoi}), $i\in\mcI^j \Rightarrow
-j\in \mcI_i$, so $i\in \mcI^j \cup \mcI^j$, 
-Using (\ref{buyerinversedemand}), we have the valuation of $j\in\mcI_i$,
-%$i\in\bigcap_{i\in\mcI^j}\mcI_i$,
+the continuity of $\theta$, and using (\ref{jdemand}), (\ref{idemand}),
 \begin{align*}
-      \theta^j \circ e = \sum_{k\in\mcI_i\cup\mcI^j}}&\int_0^{e_i^k(a)} f(z) \ dz,
+    \int_0^{e_i^k(a)} f_i(z) \ dz &= \int_0^{e_i^k(a)} f^k(z) \ dz \\
+    = \int_0^{e_l^k(a)} f^k(z) \ dz &= \int_0^{e_l^k(a)} f_l(z) \ dz \\
 \end{align*}
-and by (\ref{sellerinversedemand}), we have the valuation of $j$ fixed, 
-\begin{align*}
-      \theta^j \circ e = \sum_{i\in\mcI^j}&\int_0^{e_i^j(a)} f(z) \ dz,
-\end{align*}
-and thus we have the valuation of $\Lambda^j$,
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} \bigg(\sum_{k\in\Lambda}&\int_0^{e_i^k(a)}
-f(z) \ dz\bigg).
-\end{align*}
-\\(FINISH!)\\
-$$
-     \displaystyle\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg).
-$$
-----------------HERE--------------\\
-(HOW TO MAKE SETS THE SAME???)
-Now we consider $\Lambda_i$. For each buyer $i\in\mcI^j$, we have that $p_i^j
-\ge p_i^k$
-
-Now, for $\Lambda_i \cap \Lambda^j$, and by the continuity of $\theta'$,
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\Lambda_i}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &= \sum_{k\in\Lambda_i}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-      &= \sum_{k\in\Lambda^j}\bigg(\sum_{j\in\mcI_i}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg)\\
-      &=\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda^j}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg).
-\end{align*}
-
-(WHAT?)\\
-Therefore, $\Lambda$ is such that $j\ni \mcI_i, \ \forall \ i \ni \mcI^j$. In other words, $\Lambda$ is a
-disjoint set in the global marketplace with respect to $j$.
-****************************************************************************************************
-\fi
-
+Finally, we have,
+\begin{equation}
+    \displaystyle\sum_{j\in\Lambda} \int_0^{e_i^j(a)} f_i(z) \ dz = \sum_{i\in\lambda}\int_0^{D^j} f^j(z) \ dz.
+\end{equation}
+
+\vspace{3cm}
+(KEEP GOING! YOU ARE DOING GREAT!)\\
 For completeness, in the case where the ISP $\kappa$ 
@@
     \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
-    &= \min\bigg\lbrace e_i^j \circ D_i, \\
-    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \circ
-D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
+    &= \min\bigg\lbrace e_i^j(D_i), \\
+    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \big(
+D_i^j(p_i^j,s_{-i}^j)\big)\bigg\rbrace,
 \end{align}

### 2018-04-18 paper_wc_save_4.tex
Moving PhD paper from Dropbox to github.

--- 2018-04-18 paper_wc_4-12.tex
@@
 
-Progressive second price auctions (PSPs) were proposed
-in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
-scheme to provide consistent services for network bandwith users.
-\cite{diffserve} conducts a game theoretic analysis, deriving
-optimal strategies for buyers and brokers, and further shows the existence
-of networkwide market equilibria based on their game-theoretic
-model. Constructing necessary and sufficient conditions for the stability
-of the game allows the sustainability of any set
-of service level agreement configurations between Internet service
-providers to be determined.
-
-We begin with a brief introduction to the distributed PSP auction for bandwith
-sharing, first introduced by Lazar and Semret \cite{lazar}.
-We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ network bandwidth users.
+\subsubsection{Allocation using PSP}
+
+We begin with a brief introduction to the generalized distributed PSP auction, first introduced by Lazar and Semret \cite{lazar}.
+We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users.
+
 Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
@@
 pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
+[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i−1}^j , s_{i+1}^j , \cdots
 , s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents.
+
 Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
 bids $s_{-i}$,
-user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
-and is a Nash move
-where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
-budget, and every user has an elastic demand function.
-Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
-an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
-by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
-allocations awarded in auction $j$. 
-An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
-
-% MECHANISM
-\subsubsection{The Mechanism}\label{mechanism}
-The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
-problem of network bandwidth allocation, and is analyzed as a noncooperative
-game where $i\in\mcI$ agents buy the
-fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
-The market price function (MPF) for a buyer-seller pair is,
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
-    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
-\end{split}
-\end{align}
-and is the of minimum prices a user bids in
-order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is,
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
-\end{split}
-\end{align}
-where $D^j$ is the total amount of bandwith that user $j$ has to offer.
-% DATA ALLOCATION RULE
-For each $i \in \mcI$, the allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
-\end{align}
-Finally, we have the cost of the allocation,
-% DATA COST
-\begin{align}\label{datacost}
-    c_i^j(s) = \displaystyle\sum_{k\ne i} 
-p_k^j \big[a_k^j(0; s_{-i}^j)
-    -a_k^j(s_i^j;s_{-i}^j)\big].
-\end{align}
-
-It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
-equilibria for differentiated services
-allocated between multiple agents when all players bid their real marginal valuation
-of the bandwidth resource. In other words, the PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive
-compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
-principle}, user $i$
+user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
+where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
+has an elastic demand function.
+
+Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, there exists
+an allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to
+each user $i\in\mcI$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
+allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
+
+We intend to show that our auction
+is rational and achieves the desired VCG properties, as does the original
+formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
+realistic, theoretic, and notational templates, we define optimal strategies for
+CMHK users, and demonstrate that the development of a set PSP auction mechanisms
+in a data exchange setting is able achieve a network equilibrium for cellular data.
+
+We intend to show that our PSP constraints are
+sufficient to attain the desirable property of truthfullness through incentive compatibility. We
+reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
+principle}, and is a valid progressive second price auction to the extent that buyer $i$
 pays for its allocation so as to exactly cover the ``social opportunity cost"
@@
 revenue \cite{lazar}.
-We have the definition of an elastic valuation function. In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
-\definition{\cite{lazar}}
-A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta(0) = 0$,
-    \item $\theta$ is differentiable,
-    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
-{\theta}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
+
+We will introduce a user type called an \emph{opt-out buyer} in order to perform our analysis. The
+opt-out buyer restricts its pool of sellers. We extend the P2P rules described
+in \cite{semret} to account for a set of \emph{local} data-exchange markets.
+Our reserve price function is determined by the subset of nodes participating in the
+auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
+auctions will be influenced only by the submission of bids from buyers to
+sellers. As a buyer may have access to multiple auctions, the sellers will be
+dynamically influenced by the market via the $\epsilon$-best replies from the
+buyers. We demonstrate that as the valuation function of seller $j$ is dependent
+on the buyers demand, that the strategies of buyers and sellers may differ
+drastically depending on the market.
 
@@
 \section{The Problem Model}
-\subsection{The CMHK Market}
-
-We begin to construct the model for a PSP data auction for  mobile users
-particpating in CMHK's secondary data-sharing market.
-Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
-data from other users. We again define the bidding profile for any user to be 
-$s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
-cellular network. We assume that users are selfish, and therefore
-rational. 
- Users prefer to participate in the secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
-Thus we assume that all users submit bids in order to maximize their
+\subsection{The Secondary Market}
+
+We define the set of users, $\mcI = \lbrace 1, \cdots, I\rbrace$, who purchase or sell
+data from other users. A buyer submits bids directly to sellers, where we
+assume that all users submit bids in order to maximize their
 (private) valuation functions.
-In general, user preferences are defined by a utility function, $u$, which typically
-represents a users' valuation of an allocation minus the price.
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We will assume that the user valuation satisfies the conditions for an
-\emph{elastic demand function}, as in \cite{lazar}. 
-As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
-the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation.
-A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
-belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
-the bid belongs to a \textbf{seller}.
-Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
+
+(TERRIBLE, FUTURE WORK) public information in the
+secondary market consists of a set of offers that are published by users
+wishing to sell their data overage.
+
+A user's identity $i \in \mcI$ as a subscript indicates that the user
+is a buyer, and a superscript indicates the seller.
+Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
 meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
 a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
-auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
-(0,0)$. Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$.
-A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
-quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
-with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
-stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
-by the user type, whether or not they are  a buyer or a seller. 
-To further clarify our analysis, we will emphasize the separation of buyers and
-sellers using
-$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
-In other words, a bid $s^j =
-[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
-secondary market. The notational conventions of the bid vectors are essentially 
-slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
-[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
-Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
-d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
-d_i^j$ represent the
-total amount of data requested by buyer $i$. 
-Finally, we assume that data is a unary resource belonging to the seller, and
-therefore can identify each local auction
-with the identity of the seller $j\in\mcI$.
-
-Consider the grid of bid proiles, $s$, representing the distributed PSP auction
-mechanism in the CMHK market, each buyer $i$ will
-have information from each seller $j$, as well as opponent profiles $s_{-i}$
-from each auction in which it is participating, and therefore
-in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
-$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
-(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
-sellers can only gain information about the market grid by observing buyer
-behavior in their local auction.
-In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
-influence the CMHK market dynamics, with the sellers taking a secondary role
-(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
+auctions; if a user $i$ does not submit a bid to $j$, then this means that
+the user has the exact amout of data they require, or that seller $j$ does not have
+enough data to satisfy the buyers demand, and we simply set $s_i^j = (0, 0)$.
+A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
+quantity $d^j$ , with a reserve unit price of $p^j$ . In other words, for a
+superscript, the bid is understood as an offer in the secondary
+market; we assume that data is a unary resource belonging to the seller, and
+therefore can identify the data (for sale) with the identity of the user.
+To further clarify this restriction, we note that since $i$ is not a seller,
+the superscript notation will not be used, as $d^i = 0$ and
+$a^i = 0$. In our current formulation, we do not allow a seller to submit
+multiple bids to the secondary market (FUTURE WORK).
+
+% MECHANISM
+\subsection{Data Auction Mechanism}\label{mechanism}
+We now proceed to formally define the PSP auction, which determines the actions 
+buyers and sellers in the secondary market. We will denote the \emph{data} PSP rules
+by including an overbar, in order to emphasize that they have been changed from
+the original forms described in \cite{lazar}.
+The market price function (MPF) for a buyer in the secondary market
+can now be described as follows:
+% NEW MARKET PRICE
+\begin{align}\label{dataprice}
+\begin{split}
+    \bar{P}_i&(z, s_{-i}) =\displaystyle\sum_{j\in\mcI_i}P_i^j(z_i^j,
+s_{-i}^j) \\
+    &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
+    {\bar{D}_i^j}(y,s_{-i}^j) \ge z\bigg\rbrace \bigg),\\
+\end{split}
+\end{align}
+and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
+order to obtain
+data amount $z$ given an opponent profile $s_{-i}$. We note that
+the total minimum price for the buyer must be an aggragation of the
+\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
+%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
+%buyer $i$'s bid quantity. 
+The maximum available quantity of data from seller
+$j$ at price $y$ given $s_{-i}$ is: 
+% NEW ALLOCATION RULE
+\begin{align}
+\begin{split}\label{datacomposed}
+    \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
+    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
+\end{split}
+\end{align}
+and we have the inverse price function as an aggragate over all local auctions
+$j\in \mcI_i$,
+% NEW INVERSE DEMAND
+\begin{align}\label{datapriceinverse}
+\begin{split}
+    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI_i}\bigg(\sup\bigg\lbrace z\in \big( 0,
+\bar{D}_i^j \big) : \\
+    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
+\end{split}
+\end{align}
+% DATA ALLOCATION RULE
+The data allocation rule is given as in \cite{semret}, however with the
+influence of the opt-out buyer strategy, the resulting allocation is a function of the total amount of data
+required by buyer $i$ composed with its opt-out value and the allocation relies
+on the incentives of the seller, so that $\forall \ i \in \mcI^j$,
+% and so for profile $s_i$, for any $i \in \mcI$,
+\begin{align}\label{dataallocation}
+\begin{split}
+    \bar{a}_i(s) &= a_i(s) \circ e_i =
+\displaystyle\sum_{j\in\mcI_i}\bigg(\min\bigg\lbrace d_i^j,
+\\
+    &\frac{d_i^j}{\sum_{k:p_k^j=
+p_i^j}d_k^j}
+\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace\bigg).
+\end{split}
+\end{align}
+Finally, we must have that the cost to the buyer adheres to the second price rule for each local auction:
+% DATA COST
+\begin{align}\label{datacost}
+\begin{split}
+    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI_i} 
+p^j \bigg(\bar{a}_j(0; s_{-i}^j)
+    -\bar{a}_j(s_i^j;s_{-i}^j)\bigg).
+\end{split}
+\end{align}
 
@@
 order to apply a distributed PSP implementation to CMHK's secondary market,
-we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
+we utilize our opt-out buyer and seller strategies in order to analize the
+behavior of the resulting dynamical market. As both buyers and sellers are able
 to change their bid strategies, and as each user only has \emph{local}
@@
 
+\section{Distributed PSP Analysis}
+
 \subsection{User Behavior}
 
-We are not concerned with network
-bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
-we reason that there remains an optimal user strategy. As a user no longer needs
-to bid on a complete (but arbitrary)
-cluster of nodes with minimum bandwidth allocation (defined as a route in
-\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
-utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
-its market behavior. In a general sense, $e$ applies our user \emph{strategy}
-to the PSP rules.
-Our reserve price function is determined by the subset of nodes participating in the
-auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
-auctions will be influenced only by the submission of bids from buyers to
-sellers. As a buyer may have access to multiple auctions, the sellers will be
-dynamically influenced by the market via the $\epsilon$-best replies from the
-buyers. We demonstrate that as the valuation function of seller $j$ is dependent
-on the buyers demand, and further show evidence of symmetry in the strategies of
-buyers and sellers.
+We assume that users are selfish, and therefore
+rational. Users prefer to participate in the secondary market as it allows them to purchase
+additional data for a cost less than the overage fee set by the ISP. 
+In general, user preferences are defined by a utility function, for any $i\in\mcI$,
+\begin{align*}
+    u_i : &S \rightarrow (-\infty, \infty) \\
+          &s \rightarrow u_i(s).
+\end{align*}
 
@@
 
+Absent the cost or revenue from trading data, CMHK users gain utility from consuming
+data. 
+We will assume that the buyer valuation satisfies the conditions for an
+\emph{elastic demand function}: 
+\definition{\cite{lazar}}
+A real valued function, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta_i(0) = 0$,
+    \item $\theta_i$ is differentiable,
+    \item ${\theta_i}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
+     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
+${\theta_i}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le
+{\theta_i}'(\eta)
+- \gamma(z - \eta)$. 
+\end{itemize}
+
 % OPT-OUT BUYER
-We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $\theta_i$, the value of the allocation minus the cost,
+We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
+function,
 \begin{equation}\label{buyerutility}
@@
 \end{equation}
-where $e_i : [0, \infty)^I \rightarrow [0,\infty), \ \forall \ i \in \mcI$. 
-We extend the P2P rules described
-in \cite{semret} to account for a set of \emph{local} data-exchange markets.
+where $e_i : [0, \infty) \rightarrow [0,\infty)$ is %the expectation 
+a function that maps buyer $i$'s data quantity (requirement) to matching
+seller(s). We note that the opt-out buyers valuation depends only on a scalar $e_i(a)$ which is a function of the
+quantities of all the available data for sale in the secondary market.
 
 Suppose the total amount of seller $j$'s data on the network at the instance that
-user $i$ joins the auction is $D^j$. 
+user $i$ joins the auction is $b^j$. 
 A sellers' allocation cannot exceed the total amount they have available,
-i.e. $\sum_{i\in\mcI} a_i^j \le D^j$. This will hold simultaneously for each $i \in
-\mcI$ if and only if 
-\begin{equation}\label{isp}
-    D^j \ge \sum_{i\in\mcI} \ D_i.
-\end{equation}
-We define the only ``seller" to satisfy (\ref{isp}) to be the ISP.
-We will show that in our
-algorithm, sellers are restricted to subset of buyers $\in\mcI$, and provide a
-buyer strategy defining when a rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
+i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
+\mcI$ if and only if $b^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
+restricted to subset of buyers $\in\mcI$.
+Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
+rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
 extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
@@
 entire data cap, and only sell the fractional overage. In this case, we
-determine that buyers must split their bids among multiple sellers. 
+determine that a buyer must coordinate their bids among multiple sellers. 
+Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
+moderated by the function $e_i$ which maps its data requirement to the distributed market. 
 We propose the following strategy, 
@@
 Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t\in\tau$. % For any allocation $a$ at time $t$, let
+$t\in\tau$. For any allocation $a$ at time $t$, let
 % OPT-OUT BUYER STRATEGY
-%\begin{equation}\label{opt-out}
+\begin{equation}\label{opt-out}
     %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
-    %e_i^j(a) \triangleq a_i^j,
-%\end{equation}
-%and define,
-Define the composition,
-$$
-     e_i^j \circ a = e_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity, and the set,
+    e_i^j(a) \triangleq a_i^j,
+\end{equation}
+and define,
 % MIN SET
 $$
-    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
-n}\sum_{j\in\mcI'} D^j,
-$$
-where buyer $i$ chooses its seller pool by determining $n$, where
+    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
+n}\sum_{j\in\mcI'} d^j.
+$$
+Buyer $i$ chooses its seller pool by determining $n$, where
 \begin{equation}\label{buyercoordinate}
@@
     %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
-    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
-\end{equation} 
-The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
-fixed $n$ we will denote this subset,
+    n = \argmin_{j\in \ell_i}(n d^j\ge d_i\rbrace,
+\end{equation} 
+which produces a minimal subset 
 \begin{equation}\label{sellers}
-    \mcI_i \subset \mcI.
+    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
 \end{equation} 
@@
 \begin{equation}\label{opt-minallocation}
-    e_i(a) \triangleq e_i^{j^*}(a)
-\end{equation}
-$\forall \ j \in \mcI_i$.
-As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
-we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
+    e_i(a) \triangleq e_i^{j^*}(a).
+\end{equation}
+
+We have that $e_i$ defines an optimal feasible strategy for buyer $i$ for any
+time $t\in\tau$.
 }\\
 \textbf{Proof:}
-
 We assume that a buyer wants to fufill their data requirement.
@@
 demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
-as the set $\mcI_i$ is an ordered set, $i$ may discover 
-$j^*$ by computing $\mcI_i$.
-If we suppose that $D_i >
-\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
-We model the ISP as a seller $\kappa$ with bid $s^\kappa =(D^\kappa, P^\kappa)$,
-where $D^\kappa > D^j, \
-\forall \ j\in\mcI_i$, and
-$P^k$ represents the overage fee for data set by the ISP, which is also the upper bound of the sellers'
+as the set $\ell_i$ is an ordered set, $i$ may discover 
+$j^*$ by computing $\ell_i$. If we suppose that $d_i >
+\sum_{j\in\mcI}d^j$, then $j^* > I$ and $\ell_i = \emptyset$, 
+we model the ISP as a seller $k$ with bid $s^k =(d^k, p^k)$, where $d^k > d^j, \
+\forall \ j\in\mcI_i$, an
+$p^k$ is the overage fee for data set by the ISP, which is also the upper bound of the sellers'
 pricing function, and so again (\ref{buyercoordinate}) holds.
-Now consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
+As prices are a bounded set, we consider some $k \ne i \in
+\mcI$ where $p_i^j = p_k^j$. 
 The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
 between all buyers with the same unit price. 
-It is possible that the resulting partial allocation of data to $i$ and $k$
-would not satisfy some demand. As the two cases $i$ and $k$ are the same, we consider such
-a seller $i$. Suppose seller $j$ updates its
-bid to reflect the new data quantity, so that $d_i^{j(t+1)} < d_i^{j(t)}$ (NOTE:
-IS THE DIRECTION OF THE BID CONFUSING?, i.e. $d_i^j$ from buyer (rhs) or seller
-(lhs) unclear? does it matter?) Then, by the definition of $\ell_i$, we can
-only have that $j \ni \mcI_i$, or that $n$ has been increased, and new seller(s)
-enter the pool. 
-Additionally, we consider that at time $(t+1)$, we can have a 
-new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
-words, a new buyer $k$ may enter the market with a better price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
+This would result in a partial allocation of data to $i$ and $k$, and so neither
+buyer would satisfy thier demand as expected. (NOT QUITE SURE
+HOW I WANT TO HANDLE THIS YET ... WANT PROPORTIONAL SPLIT TO WORK WITH PARTIAL
+DATA ALLOCATION FOR BUYERS AND SELLERS)
+Additionally, we consider the transition from time $t$ to time $(t+1)$, and a
+new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other words, a new buyer $k$ may enter the market with a better
+price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
 $n$ so that
 $$
-    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
+    e_i^{(t+1)}(a) = e_i^{(t)}(a) - e_k^{(t)}(a),
 $$
@@
 valuation is elastic, even infintesimal changes in the market dynamics can be
-modeled. $\forall \ y\ge 0$, we determine that the market demand for $D^j$ is given by,
+modeled. $\forall \ y\ge 0$, we determine that the demand for $j$ is given by,
 % BUYER DEMAND 
@@
 
-Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-which is distributed across the secondary market via bids in local auctions. 
-Buyer behavior is influenced by opponent bid profiles from multiple auctions.
-The valuation of any user, however, is a function of the entire marketplace.  
-We first define the ``inverse" demand for any buyer $i$,
-% BUYER REVENUE 
-\begin{equation}\label{buyerinversedemand}
+Buyers are influenced by each others' behavior, each buyer has an incentive to
+remain a participant in all of the auctions.
+We define the ``inverse" demand for any buyer $i$,
+% SELLER REVENUE 
+\begin{equation}\label{revenue}
     f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-For a given demand $\rho^j$, $f_i$ maps the $z$th unit of data to the lowest
-possible unit price. \\
-\textbf{Remark:} In a coordinated bid, $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Naturally, the coordinated bid is the
-lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers.
-
-The seller is represented by a similar function, however a seller only has a
-single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
-seller we have a more direct interpretation of revenue.
-We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
+        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
+\end{equation}
+For a given demand $\rho^j$, $f_i$ maps a unit of data to the lowest price at
+which $i$ \emph{could} buy the unit from \emph{any} seller $j\in\mcI$. This is the
+lowest potential unit cost of the buyer, and corresponds to the maximum reserve
+price amongst the sellers. 
+The revenue for $j$ at unit price $y$ is also determined by the
+demand of the buyers.
+We define the ``inverse" of the buyer demand function for seller $j$:
 % SELLER REVENUE 
-\begin{equation}\label{sellerinversedemand}
+\begin{equation}\label{revenue}
     f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
+        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
 \end{equation}
@@
 For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
-\begin{equation}\label{singlevaluation}
-    \theta_i^j \circ e_i^j(a) = \int_0^{e_i^j(a)} f_i(z) \ dz,
+\begin{equation}\label{buyerprice}
+    \theta_i^j \circ e_i = \int_0^{e_i^j(a)} f_i(z) \ dz,
 \end{equation}
 it follows that 
-\begin{equation}\label{buyervaluation}
-    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
+\begin{equation}\label{valuation}
+    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
  \int_0^{e_i^j(a)} f_i(z) \ dz.
@@
 \begin{equation}\label{sellervaluation}
-    \theta^j \circ e_i(a) = \displaystyle\sum_{i\in\mcI}
+    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
  \int_0^{e_i^j(a)} f^j(z) \ dz.
@@
 and will try to sell all of its data, and so 
-$d_i^j = e_i(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
-\sum_{i\in\mcI} e_i(a)$,
+$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = b^j =
+\sum_{i\in\mcI} e_i$,
 The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
@@
 
-We note that except at points of discontinuity, we have
-$P_i(z) = f_i(z)$. This mechanism generalizes Vickrey
-(``second-price") auctions which are for nondivisible objects.
-
 The sellers' natural utility is the potential
-profit $u^j = \theta^j \circ e_i(a) $, where $\theta^j$ is the
-potential revenue from the sale of data composed with each buyers' opt-out
-value, $e_i(a)$. 
+profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
+potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
 We have chosen to omit the original cost of the data
@@
 \lemma{(Seller constraints)}\label{constraints}
-Let $j$ be a seller with total data amount $D^j$.
+Let $j$ be a seller with budget $b^j$.
 First, the seller must satisfy the quantity
@@
 \begin{equation}\label{quantity}
-    d_i^j \ge e_i^j(a)
+    d^j \ge e_i(a)
 \end{equation}
@@
 \begin{equation}\label{budget}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
+    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j,
 \end{equation}
@@
 \begin{equation}\label{partialallocation}
-    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
+    e_i^j(a) \le b^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
 \end{equation}
 In addition, for a rational seller, the reserve price must
-satisfy, $\forall \ i\in \mcI$,
+satisfy 
 \begin{equation}\label{reserveprice}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
+   p^j \ge \min_{i\in\mcI}\big(p_i^j).
 \end{equation}
@@
 (\ref{partialallocation}) enforce
-a data constraint for the seller. Finally, (\ref{reserveprice})
+the budget constraint for the seller. Finally, (\ref{reserveprice})
 follows from the assumption that $j$ is rational, and so utility-maximization
@@
 accept fractional (CHANGE TO PARTIAL? PICK ONE) bids (i.e. sell a fraction of
-their data $D^j$). Reasonably,
-there may not exist a buyer such that $D_i = D^j$. \cite{zheng} reasons that the seller does not know the exact amount of
+their budget $b^j$). Reasonably,
+there may not exist a buyer such that $d_i = b^j$. \cite{zheng} reasons that the seller does not know the exact amount of
 leftover data available, and so they may only sell enough data to ensure that
@@
 For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
-Define
-$$
-    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
+Let the winner at time $t$ be determined by,
+\begin{equation}\label{winner}
+    \bar{i} = \displaystyle\max_{i}\sum_{i\in I^j} p_i^j,
+\end{equation}
+and define
+$$
+    \ell^j =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
 n}\sum_{i\in{\mcI}'} p_i^j,
@@
 \begin{equation}\label{sellercoordinate}
-    n = \min( i \ \vert \ i \in\mcI^j(n) : \displaystyle\sum_{i\in\mcI} d_i^j \ge
-D^j),
-\end{equation} 
-We have, for any fixed $n$ at time $t$, a minimal subset 
-of buyers that maximizes $j$'s revenue, which we will
-denote,
+    n = \argmin_{i\in\ell^j}(\displaystyle\sum_{i\in\mcI} d_i^j >
+b^j),
+\end{equation} 
+which gives $j$ a minimal subset 
 \begin{equation}\label{buyers}
-    \mcI^j \subset \mcI.
-\end{equation} 
-Define buyer $i^* = n \le I$.
+    \mcI^j = \lbrace i \in \mcI : i < n\rbrace \subset \mcI
+\end{equation} 
+of buyers that maximizes $j$'s revenue.
+Define buyer $i^* = n \le I$ in the ordered set $\ell^j$.
 Then, for time $(t+1)$, set $j$'s reserve price as 
 \begin{equation}\label{newprice}
-    p_i^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon,
-\end{equation}
-Let the winner at time $t$ be determined by,
-\begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i\in I^j} p_i^j,
-\end{equation}
-and update $j$'s total data to reflect the (tentative) allocation,
+    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
+\end{equation}
+and update $j$'s budget to reflect the (tentative) allocation,
 \begin{equation}\label{newbudget}
-    D^{j(t+1)} = D^{j(t)} - e_{\bar{i}}^{j(t)}(a),
+    \bar{b}^{j(t+1)} = b^{j(t)} - d_{i^*}^{j(t)}.
 \end{equation}
@@
 In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}), where $i^*$ loses by: (1)
-$i^*$ is excluded from $I^j$ or (2) $i^*$s demand is not met, noting as well
-that any $i\ni \mcI^j$ is also a loser. 
-In this case, by (\ref{quantity}) the seller must notify the buyer of a
-fractional allocation.
-
+price offer, determined by (\ref{sellercoordinate}),
 %As the set of buyers is
@@
 %seller $j$ equals the aggregate demand of the buyers \cite{???}
-With this caveat, we have that the aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
+and so we have that the aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
 Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that the buyer is bidding truthfully, and so ${\theta_i}' + \epsilon
-=p_i^j + \epsilon$, and as $\mcI^j\subset \mcI$, we
+that the buyer is bidding truthfully, and so $p^j = {\theta_i}' + \epsilon
+=p_i^j + \epsilon$, therefore $p^j$ is known, and as $\mcI^j\subset \mcI$, we
 note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
@@
 \begin{align*}
-    \int_0^{e_{i^*}^j(a)} f_{i}(z)\ dz &\le\int_0^{e_i^{j}(a)}
+    \int_0^{e_{i^*}^{j}(a)} f^{j}(z)\ dz &\le\int_0^{e_i^{j}(a)}
 f^{j}(z) \ dz 
@@
 $$
-     \theta_i \circ e_{i^*}(a) \le \theta_i \circ e_i(a),
-$$
-which holds $\forall \ j \in \mcI_i$.
+    \theta^j\circ e_{i^*}(a) \le \theta^j\circ e_i(a),
+$$
+which holds $\forall \ i \in \mcI^j$.
 It follows that, using
@@
 $$
-    p_i^j \le {\theta_i}'(v_i^j) + \epsilon,
+    p^j \le {\theta_i}'(v_i^j) + \epsilon,
 $$
 $\forall i \in \mcI^j$.
-Therefore the choice of $p_i^j$ does not force any buyers out of the local
+Therefore the choice of $p^j$ does not force any buyers out of the local
 auction. Thus we determine the valuation between seller
@@
 equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-We note the special case where for winner $\bar{i}$, $\ \exists \ k\in\mcI^j$
-such that $p_{\bar{i}}^j =
-p_i^k$. In this case the seller again notifies the buyers of a fractional
-allocation by changing $d_i^j$ and $d_k^j$ to reflect the proportional
-division. Finally, in the case where winning buyer(s) \emph{opts-out} of the local
-auction, where $j\in\mcI_i$ at time $t$, then at time $(t+1)$ $j\ne \mcI_i \Rightarrow s_i^{j(t+1)} = (0,0) \Rightarrow i \ne
-\mcI^j$, which is mathematically analogous to the definition of opting-out in our
-scenario. The seller may simply return the tentatively allocated data to $D^j$,
-and recompute $\mcI^j$ and $p_{i^*}^j$, 
-$$
-    D^{j(t+1)} = D^{j(t)} + \displaystyle\sum_{i\in\Gamma} d_i^{j(t)}
-$$
-where $\Gamma$ represents the buyers who have opted-out from time $t$ to 
-$(t+1)$, indicated by a zero bid from any buyer $\in \mcI^j$:
-$$
-    \Gamma = \lbrace i\in \mcI^j : s_i^{j(t+1)} = 0\rbrace.
-$$
-
-(NOTE - NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK IN
-FRACTIONAL ALLOCATIONS? SAVE FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
-
-We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. Consequentially, we have the following Lemma.
-
-% USER UNION
-{
-\lemma{(Valuation across local auctions)}\label{userunion}
-For any $i,j\in \mcI$, 
-\begin{equation}\label{jtoi}
-j\in\mcI_i \Leftrightarrow i\in\mcI^j.
-\end{equation}
-Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
-\begin{equation}\label{lambda}
-    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
-\end{equation}
-and for each $i\in\mcI^j$ define,
-\begin{equation}\label{ilambda}
-    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
-\bigg).
-\end{equation}
-(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
-\equiv s_i^j \in \mcI$)
-Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
-\begin{equation}\label{sym}
-    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
-\end{equation}
-(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
-HAPPEN)
-}\\
-\textbf{Proof:}
-A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $p_i^j \ge p_{i^*}^j$.
-Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
-If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
-Proposition \ref{buyerstrategy}, $i^*$
-will add sellers to its pool until its demand is satisfied. Therefore for any
-$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
-holds.
-
-The subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
-coordinated, truthful bid, $\mcI_i\subset \mcI$ 
-will determine the unit price $p_{i}$ in buyer $i$'s bid.
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
-the lowest price that $j$ will accept to perform any allocation.
-Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy},
-we have that for each $i \in \mcI^j$, 
-$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
-Let $p_*^j=p_{i^*}^j$ denote the reserve
-price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$.
-Now, we have,
-%Fix any buyer $i\in\mcI^j$.
-\begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-and, $\forall \ i \in \mcI^j$, 
-\begin{equation}\label{invrho}
-    f_i \circ e_i^j(a) \ge p_*^j,
-\end{equation}
-and, $\forall \ k \in \mcI_i$, 
-\begin{equation}\label{invrho}
-    p_*^j \ge f^k \circ e_i^k(a) ,
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-
-The sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
-%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
-for any $k\ne j \in \mcI_i$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
-$\forall \ i \in \mcI^j$,
-\begin{equation}\label{feq}
-    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
-\end{equation}
-where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
-Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
-Since,
-$$
-    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
-$$ 
-there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
-we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
-It follows that buyer $i$'s bid price is given by,
-\begin{equation}\label{iprice}
-    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
-\end{equation}
-
-%where $p_i^*$ represents $i$'s coordinated bid price,
-%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
-This holds for any
-$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
-Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
-denote each as $f$ in the remainder of the proof.
-
-Now, using (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
-$i\in\mcI^j$ to be, (HERE)
-(SHOW THAT $\Lambda$ IS DISJOINT!)
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p_*^k) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^k$ is the highest unit price in the feasible set $\mcI_i\cup\mcI_k$.
-Thus we determine the aggregate demand from buyer
-$i\in\mcI^j$ over the set of intersecting markets $\Lambda$ to be, 
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p^*) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^* = \max(p^k), \ \forall \ k \in\Lambda$, and corresponds to the
-highest reserve price over all the sellers. 
-Now, by the continuity of $\theta'$, (AND)
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\mcI_i\cup\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &=\displaystyle\sum_{i\in\mcI^j} \theta_i \circ e_i(a) \\
-     &= \sum_{k\in\mcI_i\cup\mcI^j}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &= \sum_{k\in\mcI_i\cup\mcI^j}\theta^j \circ e_i(a)\\
-     &= (\theta_i \circ \theta^j) \circ e_i(a).
-\end{align*}
-
-\iffalse
-************************
-Proposition \ref{buyerstrategy} defines $e_i^j(a) = D_i/ 2$, and so $0 <
-e_i^j(a)$.
-************************
-\fi
-\iffalse
-Suppose $\exists \ i \in\mcI^j$ such that $\mcI_i = j$, so that $j$ is the only
-seller in $\Lambda$.
-, and $i$'s bid quantity,
-\begin{equation}\label{iquantity}
-    d_i^* = \circ e_i(a) = \frac{a_i^j}{j},
-\end{equation}
-where $j=j^* = \argmin$ for each $i\in\mcI^j$, thus $d_i^*$ represents $i$'s coordinated bid quantity, and we have
-$s_i^j = (p_i^*,d_i^*), \ \forall \ j$ such that $s_i^j > 0$,
-\fi
-\iffalse
-
-*****************************************************************************************************
-From (\ref{jtoi}), $i\in\mcI^j \Rightarrow
-j\in \mcI_i$, so $i\in \mcI^j \cup \mcI^j$, 
-Using (\ref{buyerinversedemand}), we have the valuation of $j\in\mcI_i$,
-%$i\in\bigcap_{i\in\mcI^j}\mcI_i$,
-\begin{align*}
-      \theta^j \circ e = \sum_{k\in\mcI_i\cup\mcI^j}}&\int_0^{e_i^k(a)} f(z) \ dz,
-\end{align*}
-and by (\ref{sellerinversedemand}), we have the valuation of $j$ fixed, 
-\begin{align*}
-      \theta^j \circ e = \sum_{i\in\mcI^j}&\int_0^{e_i^j(a)} f(z) \ dz,
-\end{align*}
-and thus we have the valuation of $\Lambda^j$,
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} \bigg(\sum_{k\in\Lambda}&\int_0^{e_i^k(a)}
-f(z) \ dz\bigg).
-\end{align*}
-\\(FINISH!)\\
-$$
-     \displaystyle\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg).
-$$
-----------------HERE--------------\\
-(HOW TO MAKE SETS THE SAME???)
-Now we consider $\Lambda_i$. For each buyer $i\in\mcI^j$, we have that $p_i^j
-\ge p_i^k$
-
-Now, for $\Lambda_i \cap \Lambda^j$, and by the continuity of $\theta'$,
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\Lambda_i}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &= \sum_{k\in\Lambda_i}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-      &= \sum_{k\in\Lambda^j}\bigg(\sum_{j\in\mcI_i}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg)\\
-      &=\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda^j}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg).
-\end{align*}
-
-(WHAT?)\\
-Therefore, $\Lambda$ is such that $j\ni \mcI_i, \ \forall \ i \ni \mcI^j$. In other words, $\Lambda$ is a
-disjoint set in the global marketplace with respect to $j$.
-****************************************************************************************************
-\fi
-
-For completeness, in the case where the ISP $\kappa$ 
-does not adhere to the market dynamics, so $P^\kappa > p^j +
-\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
-bid fee.
-
-(ADD TIME? INDUCTION GOES HERE? DID NOT SHOW!)
-
-(OWN
+(NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK? SAVE
+FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
+
+(TRY FRACTIONAL ALLOCATION AS A SEPARATE AUCTION? FOR EXTRAS)
+
+We conclude this section by reasoning that the user behavior restrictions are
+necessary to formally define (and restrain) the incentives of the users. (OWN
 WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
@@
 inter-dependent, and may be played on the same or on a different scale in
-valuation, time (AND....).
-
-PSP relies on the \emph{relevation prinicple}; the
+valuation, time (AND....). PSP relies on the \emph{relevation prinicple}; the
 PSP mechanism is able to demonstrate equlibrium by showing that PSP is
@@
 \subsection{PSP Formulation}
-
-We intend to show that our auction
-is rational and achieves the desired VCG properties, as does the original
-formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
-realistic, theoretic, and notational templates, we define optimal strategies for
-CMHK users, and demonstrate that the development of a set PSP auction mechanisms
-in a data exchange setting is able achieve a network equilibrium for cellular data.
-
-% MECHANISM
-\subsubsection{Data Auction Mechanism}\label{datamechanism}
-We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the secondary market, which we will denote the \emph{data}
-PSP rules. The rules presented here incorporate of the opt-out function with the
-mechanism as in \cite{lazar}, which we note greatly simplifies our
-analysis. 
-The market price function (MPF) for a buyer in the secondary market
-can be described as follows:
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
-s_{-i}^j) \circ e_i^j \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
-order to obtain
-data amount $z$ given opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
-%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
-%buyer $i$'s bid quantity. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is: 
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}\label{datacomposed}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
-\end{split}
-\end{align}
-it follows that the inverse price function is aggregated over all local auctions
-$j\in \mcI$,
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
-    D^j \big] : \\
-    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
-\end{split}
-\end{align}
-Finally we must have that the cost to the buyer adheres to the second price
-rule for each local auction, with total cost to buyer $i$,
-% DATA COST
-\begin{align}\label{datacost}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-p^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
-    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
-% DATA ALLOCATION RULE
-The resulting data allocation rule is a function of the local market
-interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
-allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
-    &= \min\bigg\lbrace e_i^j \circ D_i, \\
-    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \circ
-D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
-\end{align}
-noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool, as in the previous definitions.
-
-\subsubsection{Mechanism Realization}\label{realization}
-
 Consider a user seeking to prevent
@@
 This user $i$ can be modeled as a opt-out buyer where, as in \cite{semret},
-We intend to show that this network setting results in a shared network optima (a
+$\vs_i^j$ corresponds to a fraction of user $j$'s data aquired by user $i$. In order to form the
+distributed auction, we set $1$ if seller $j$ has enough data to
+satisfy $i$'s demand, and $\vs_i^j=d_i$ otherwise. We intend to show that this
+does not affect their valuation, and indeed, in this network setting, results in a shared network optima (a
 global optimum). The formulation is inspired to the thinnest allocation route for
@@
 
-(NOTE - FIX TO UPDATED NOTATION!)
 % SELLER ALGORITHM
@@
 \begin{algorithmic}[1]
-\State $p^{j(0)} \gets \epsilon$
-\State $s^{j(0)} \gets (p^j, D^j)$
-\While{$D^j > 0$}
+\State $p^{j(0)} \gets \min_{i\in\mcI^j} p_i^j$
+\State $s^{j(0)} \gets (p^j, b^j)$
+\While{$b^j > 0$}
 \State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \lbrace i \in \mcI^{j(t)}: d_i^j >
-D^{j(t)}\rbrace$
-\State $ \bar{i} \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
-\State $D^{j(t+1)} \gets D^{j(t)} - e_{\bar{i}}^{j(t)}(a)$
+\bar{b}^{j(t)}\rbrace$
+\State $ i^* \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
+\State $\bar{b}^{j(t+1)} \gets \bar{b}^j - d_{i^*}^{j}$
 %\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
-\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
+\State $p^j \gets p_{i^*}^j+\epsilon/2$ and $d^j \gets \bar{b}^j$
 \State $s^{j(t+1)} \gets (d^j, p^j)$
 \If{$\ \exists \ i : s_i^{j(t+1)} \ne s_i^{j(t)}$}
-\State $D^{j(t+1)} = D^{j(t)}$
-\State $t \gets t+1$
+\State $\bar{b}^{j(t+1)} = \bar{b}^{j(t)}$
 \State Go to 4.
 \Else
-\State $\bar{i} \gets e_{\bar{i}}^j(a)$
+\State $i^* \gets \bar a_i(s)$
 %\State $\beta^{j(t+1)} \gets \bigg\lbrace i\in\mcI^j: 
 %        d_i \le \bar{b}^j \bigg\rbrace$
-\State $t \gets t+1$
 \State Go to 4.
@@
 prices on (j) all auctions and not reduce the unit price to a level where he still wins the
-amount q i . The reason for this can be found in the pricing rule of the PSP auction. 
+amount q i . The reason for this can be found in the pricing rule of the PSP auction. Since a
+player is only charged with the cost of excluding other players from the market, the
+unit price does not influence the final charges. Since this unit price reflects the
+valuation of the total resources gained from the multi-auction market a player uses this price on all
+auctions
+
 % BUYER COORDINATION
@@
 Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
-For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
-allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
+For any profile $s_i = (d_i, p_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
+allocation. For any fixed $s_{-i}$, a better reply for $i$ is $x_i =
 (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
 \begin{align*}
-    z_i^j &= e_i^{j^*}(a), \\
-    y_i^j &= \theta_i'(z_i^j).
+    z_i^j &= e_i(a), \\
+    y_i^j &= \theta_i(e) \\ &(\text{BETTER NOTATION!})
 \end{align*}
-Furthermore,
-\begin{equation}\label{allocationcoordination}
-    a_i^j(z_i,y_i) = z_i^{j},
-\end{equation}
-and
-\begin{equation}\label{costcoordination}
-    c_i^j(z_i,y_i) = y_i^{j},
+and furthermore,
+\begin{equation}\label{coordination}
+    a_i^j(z_i,y_i) = z_i^{j^*},
 \end{equation}
@@
 $$
-    u_i((d_i,p_i);s) \le u_i((z_i,y_i);s_{-i}).
+    u_i((d_i,p_i);s) \le u_i((z_i,p_i);s_{-i}).
 $$
@@
 multiple sellers.
-We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
-$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $u_i$.
+We will show that $i$ may increase $\vert\mcI_i\vert$, without decreasing $u_i$,
+so that the coordinated bid is optimal as in Proposition \ref{opt-out}. 
 Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
@@
 $d_i^{j^*}$ is the minimum quantity offered by any $j\in \mcI_i$,
-so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$; $\mcI_i$ also defines the
+so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$ and also defines the
 maximum quantity bid of any $k \ni \mcI_i$.
-Thus by (\ref{buyercoordinate}) and (\ref{opt-minallocation}), $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    e_i^k(a) \le z_i^j = e_i^{j^*}(a) \le e_i^{j}(a),
-$$
-and so, 
+Thus by (\ref{opt-out}) and (\ref{opt-minallocation}), $\forall \ j\in \mcI_i$,
+$$
+    z_i^j = e_i(a) = e_i^{j^*}(a)  \le e_i^{j}(a),
+$$
+and for any $j\in\mcI_i$, we have $\forall \ l \ni \mcI_i$,
 \begin{equation}\label{minimaleq}
-    e_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+,
-\end{equation}
-The buyer valuation function (\ref{buyervaluation}), guarantees
-that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
+e_i^{l}(a) 
+     \le \bigg\lbrack d^{j} - \sum_{p_k^{l}> p_{i^*}^{j}} d_k^{l}\bigg\rbrack^+,
+\end{equation}
+where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
 \ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
-be accepted. 
-As $D_i$ is non-decreasing, $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j^*})\ge D_i^j(p_i^{k}).
-$$
-Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$e_k^{j^*}(a) \ge e_i^{j^*}(a)$ and so $d^j - d_k^j < z_i^{j}$, resulting in a
+be accepted. We are looking for the set where, for any $j\in\mcI_i$, $\theta_i'(d_i^j) \ge
+p_{i^*}^j$, and for any $i\in\mcI^j$, $e_i^j \le b^j$.
+
+Now, as any $l \ni \mcI_i$ ... for any
+$j\in\mcI_i$
+(LOOK FOR $i^* = j^*$? I.E. the minimum bid = the max losing price)
+
+1. buyers have same d but diff p
+2. " same p but diff d i.e. d1 < d2
+
+The inequality follows from
+(\ref{dataallocation}) and that $P_i^j$ is non-decreasing, so $p_i^j \le p_i^{j^*} \ \forall \ j \ni \mcI_i$.
+Now, by (\ref{dataallocation}),
+\begin{align*}
+     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j{^*}, \bigg\lbrack d^{j} - \sum_{p_k^{j}> p_i^{j^*}}
+d_k^{j}\bigg\rbrack^+\bigg) \\
+    &= z_i^{j^*}= e_i(a)
+\end{align*}
+by definition, and (\ref{minimaleq}) is proven.
+%we have that buyers will submit equal bids to a minimum subset of sellers $\mcI_i$.
+We proceed to demonstrate that $x_i$ does not result in a loss of utility for
+buyer $i$; we will show that
+$$
+    u_i \le u_i(z_i,p_i).
+$$
+From (\ref{minimaleq}), we have $a_i^{j}(z_i,p_i) = z_i^{j^*} = e_i(a(z_i,p_i))$, which
+implies that 
+$$
+\theta_i\circ e_i(a(z_i,p_i)) = \theta_i\circ e_i(a).
+$$ 
+Therefore, by the definition of utility (\ref{buyerutility}),
+and the sellers' valuation (\ref{singlevaluation}), 
+\begin{align*}
+    &\theta_i\circ e_i(a(z_i,p_i)) - \theta_i(a)) \\
+    &= u_i(z_i,p_i) - u_i =  c_i^j -c_i^{j^*}(z_i,p_i)\\
+    &= \displaystyle\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d^j - z) \ dz.
+\end{align*}
+Then, noting that $\theta_i\ge 0$, $\forall \ j\in\mcI_i$, $a_i(z_i,p_i) \le
+z_i^j \le a_i^j \Rightarrow u_i(z_i,p_i) - u_i \ge 0$.
+To illustrate our result, suppose there exists buyer $k\in \mcI^j$, such that
+$e_k^j(a) \ge e_i^j(a)
+\rightarrow p_k^j > p_i^{j}$ and so $d^j - d_k^j < z_i^{j*}$, resulting in a
 partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
 As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $e_i^{j*}(a)
-\ge e_k^{j^*}(a)$ for any $k$, therefore such a buyer $k$ cannot exist.
-\iffalse
-We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
-$$
-    {\theta_i}'(e_i^{k}(a)) \ge {\theta_i}'(e_i^{j^*}(a)) \ge y_i^j.
-$$
-Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$...
-\fi
-Thus (\ref{minimaleq}) holds and so, by (\ref{dataallocation}),
-\begin{align*}
-     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j, \bigg\lbrack D^{j} - \sum_{p_k^{j}> y_i^{j}}
-d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= e_i^{j^*}(a)
-\end{align*}
-where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
-Now, since a buyer is only charged with the cost of excluding other players from the market, the
-unit price does not influence the final charges. This unit price reflects the
-valuation of the total resources gained from the multi-auction market, and so a buyer uses this price on all
-auctions.
-We have, $\forall \ j\  \in \mcI_i, \ \forall \ k \ni \ \mcI_i$,
-$$
-    y_i^j \ge p_i^j \ge p_{i^*}^j\ge p_i^k,
-$$
-and we observe that from (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
-0 \ \forall \ y < p_{i^*}^j$, and so $y=0 \le \epsilon \Rightarrow e_i^j(a) = 0$,
-and so clearly $z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
-\begin{align*}
-    \displaystyle\sum_{j\in\mcI_i} c_i^j(z_i,y_i) =\sum_{j\in\mcI_i}
-c_i^j(z_i,p_i),
-\end{align*}
-thus (\ref{costcoordination}) simply shows that changing the price $p^j_i$ to $y^j_i$ does not exclude any
-additional buyers, as the bid $p^j_i$ was already above the reserve price of any
-seller $j \in \mcI_i$.
-We proceed to demonstrate that $x_i$ does not result in a loss of utility for
-buyer $i$; we will show that
-$$
-    u_i \le u_i(z_i,y_i).
-$$
-From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = e_i^j(a(z_i,y_i))$, 
-and so,
-$$
-    \theta_i\circ e_i^j(a(z_i,y_i)) = \theta_i\circ e_i^j(a),
-$$ 
-which holds $\forall \ j\in\mcI_i$.
-Therefore, by the definition of utility (\ref{buyerutility}),
-and the buyers' valuation (\ref{buyervaluation}), 
-\begin{align*}
-    &\theta_i\circ e_i(a(z_i,y_i)) - \theta_i(a)\circ e_i(a) \\
-    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
-    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - z) \ dz.
-\end{align*}
-Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
-$\theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
-%1. buyers have same d but diff p
-%2. " same p but diff d i.e. d1 < d2
-Finally, as we do
-not increase the aggragate demand of the buyer, $\sum_{j\in\mcI_i} c_i^j(s) \le 
-\sum_{j\in\mcI_i} b_i^j$, and so $x_i$ is feasible.
+set, (\ref{buyercoordinate}) states that $n$ is such that $e_i(a) = e_i^{j*}(a)
+\ge e_k(a)$. By (\ref{}), such a buyer $k$ cannot exist. 
+Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$.
+
+Finally, since (\ref{opt-out}) does
+not increase the demand of seller $i$, $\sum_j c_i^j(s) \le b_i$, and so $x_i$ is feasible.
 
 In effect, we are using the buyer demand
-to partition the auction space based on their type (EXPLAIN). \\
+to partition the auction space, thereby 
+controlling (optimizing?) the message space (EXPLAIN) for the
+ISP, and providing an optimal market space to host the buyers and sellers based
+on their type. \\
 
@@
 \cite{zheng}. The opt-out buyers' market is comprised of the minimal subset of
-sellers with the largest amounts of available data, described in the buyer strategy as $\mcI_i$.
+sellers with the largest budgets, described in the buyer strategy as $\mcI_i$.
 To achieve incentive compatibility, we find that the opt-out buyer must choose this subset so that
 its overall marginal value is greater than its market price.
-The buyers' market price is calculated as the maximum of the reserve prices
+The buyers' market price is calculated as the sum of reserve prices
 of the sellers in the opt-out buyers' pool.
@@
 the maximim possible quantity of data that a buyer $i$ can bid over its seller
-pool while maintaining its aggragate marginal valuation greater than the aggragate of
+pool while maintaining a marginal valuation greater than the aggragate of
 minimum prices maintained by the sellers in $i$'s pool.
@@
 the bid price to the marginal value.
-
-Seller $j$'s reserve price is determined by a
-buyer $i \ni \mcI^j$, and therefore, even if this price is zero,
-then $p^j = \epsilon \ge 0$.
-
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a local market
-equilibrium (NOTE: NOT GLOBAL! YET). We have the following Proposition. For
-completeness, we use the full notation. (BAD SENTENCE)
-
+% BUYER INCENTIVE COMPATIBILITY
 {
-\proposition{(Incentive compatibility in local auctions)}
-For any seller $j$, let time $t \in \tau$ be fixed and for any buyer $i\in
-\mcI^j$, let $s_{-i}$ also be fixed. )VALIDATE: FOR ALL j) Define,
+\proposition{(Buyer incentive compatibility)}\label{buyerincentivecompatibility}
+Let $i\in\mcI$ be an opt-out buyer, and fix all other buyers' bids
+$s_{-i}$, as well as the sellers' bids $s^j$ (so $a_i$ is fixed). \\
+Let 
 \begin{align}
-\begin{split}\label{eta}
-    \eta_i &= \sup\bigg\lbrace x\ge 0 : 
- {\theta_i}'(x) > \bar{P}_i^j(x)\bigg\rbrace, 
+\begin{split}
+    z_i &= \sup\bigg\lbrace h\ge 0 : 
+ {\theta_i}'(h) > \bar{P}_i^j(h)\bigg\rbrace, 
 \end{split}\\
-\begin{split}\label{chi}
-    \chi_i &= \sup\bigg\lbrace x\ge 0: 
-\displaystyle\int_0^x 
-    \bar{P}_i(x) \ dx \le \sum_{j\in\mcI_i}b_i^j \bigg\rbrace,
+\begin{split}
+    \chi_i &= \sup\bigg\lbrace h\ge 0: 
+\displaystyle\int_0^h 
+    \bar{P}_i(h) \ dh \le b_i\bigg\rbrace,
 \end{split}
 \end{align}
-$z = \min(\eta_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
+$e = \min(z_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
 \mcI_i$, 
 $$
-    v_i^j = e_i^{j^*}(z) 
+    v_i^j = e = v_i^{j^*}
 $$
@@
 $$
-    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
+    w_i^j = w_i^{j^*} = \theta_i'(e).
 $$
@@
 s_{-i})$.
-%and fix $j$'s reserve price $p^j$ as is defined by (\ref{newprice}). 
-With reserve prices $p^j >0$, there exists a ``truthful" local game embeddeded
-in each local auction, and thus an equilibrium point for the local auction. 
-}\\
-\textbf{Proof:}
-For the buyer, we show that $t_i$ is an $\epsilon$-best reply. That is,
-$$
-    u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;s_{-i}).
-$$
-Let $z = \eta_i^j$. We have that $i\in\mcI^j$, 
-and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
-max of the reserve prices $p_i^j,\ \forall \ j\in\mcI_i$, therefore
-(\ref{eta}) is such that,
-$$
-    \theta_i'(z) > \bar{P}_i^j(z),
-$$ 
-which implies, as (MORE) $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
-we have $\forall \ j \in \mcI_i$, 
+} \\ \\
+\textbf{Proof:} For ease of notation, we may assume that bid
+$s_i^j=s_i^{j^*}$ and that each $j\in\mcI_i$.
+First suppose $e = z_i$. Since $\theta_i'$ is non-increasing
+and, $P_i^j$ is non-decreasing, (\ref{dataprice}) implies
+$\theta_i'(e) >\sum_j P_i^j(v_i^j)$, due to $e$ being supremum, i.e.
+greater than the marginal value, same as in \cite{semret}. This,
+along with $i$'s strategy, gives $\forall \ y,z \ge 0$,
 \begin{align*}
-    w_i^j &> P_i^j(v_i^j) \\
-    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
+    \displaystyle\sum_{j} y &> \bar{P_i}(z,s_{-i}) \\
+    &\Rightarrow y > P_i^j(z,s_{-i})\\
+    &\Rightarrow
+    z \le D_i^j(y,s_{-i})/\vs_i^j,
 \end{align*}
-And so, by (\ref{dataallocation}),
+and so,
+\begin{align}\label{figureout}
+\begin{split}
+    w_i^j & > {P}_i^j(v_i^j) \\
+    &\Rightarrow {D}_i^j = \frac{\lbrack d^j - d^j(w_i^j)\rbrack}{\vs_i^j}.
+\end{split}
+\end{align}
+Now, let $y_i = {\theta_i}'(z_i)$ and suppose $z_i = 0$, then $v_i=0 \Rightarrow
+a_i(t_i; s_{-i})=0$ and $i$'s coordinated bids (Lemma \ref{coordinationlemma})
+gives $\bar{D}_i(0,s_{-i}) =0$. 
+By the assumptions made in the definition of $i$'s valuation function $\theta_i$,
+$$
+w_i = {\theta_i}'(v_i) > {\theta_i}'(z_i) = y_i,
+$$
+and as $D_i^j$ is non-decreasing, $D_i^j(y_i,s_{-i}) \ge z_i \ge v_i$.
+Thus, by (\ref{dataallocation}) and (\ref{figureout}),
 \begin{align*}
-    a_i^j(t_i) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\mcI_i} a_i^j(t_i) &= z.
+    a_i^j(t_i; s_{-i}) = v_i^j \\
+    e_i^j \circ a(t_i;s_{-i}) = e.
 \end{align*}
@@
 \begin{align*}
-    \displaystyle\sum_{j\in\mcI_i}&\int_0^{v_i^j} P_i^j(x) \ dx =  \int_0^{z}
-    \bar{P}_i^j(x) \ dx \\
-    &= \sum_{j\in\mcI_i}\int_0^{e_i^j(z)} P_i^j(x) \ dx.
+    &\qquad u_i(t_i;s_{-i}) \\
+    &= \displaystyle\int_0^\epsilon {\theta_i}'(\eta) \ d\eta -
+\sum_j \int_0^{v_i^j} P_i^j(z) \ dz \\
+    &= \int_0^\epsilon {\theta_i}'(\eta) \ d\eta - \sum_j\int_0^\epsilon
+P_i^j(\eta/\vs_i^j) \ d\eta.
 \end{align*}
-Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
-s_{-i}) + \epsilon$. The buyer coordinated strategy, from Propositions
-\ref{coordinationlemma} and
-\ref{buyerstrategy}, gives $s_{i^*} = (e_i\circ a_i(s), \ \theta_i'(z)) =
-(z_i, c_i)$, where
-for each $j\in \mcI$, $a_i^j(s_{i^*}; s_{-i}) = z_i^j$,
-then clearly $u_i(s_{i*}, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
-u_i(s_i;s_{-i}) > \epsilon$. Denoting $z_i^j$ (fixed) as $\zeta$, 
-$$
-    \int_z^{\zeta} {\theta_i}'(x) \ dx- \int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
-$$
-For concave valuation functions, the first-order derivative of $\theta$ at point
-$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
-/ \theta'(0)$ guarantees that new bids will differ by at least
-$\epsilon$, and as such, buyer $i$ will remain in
-any local auction with reserve price determined by (\ref{???}). We therefore
-verify that,
-$$
-    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
-dx \le \epsilon,
-$$
-and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
-$$
-    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
-\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
-$$
-If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
-$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
-\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
-Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
-\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
-exist.
-
-We consider the other term in the minimization; let $z=\chi_i$. We have that
-For any coordinated bid $s_i$ such that $u_i(z_i, c_i) > u_i(t_i)+
-\epsilon$, then $\zeta > z
-\Rightarrow c_i(s_{i}) > b_i$, and so is infeasible. 
-Finally, by Lemma \ref{userunion}, for a single buyer-seller interaction, we
-have that $f_i = f^j \Rightarrow \theta_i \circ e_i^j = \theta^j \circ e_i^j$.
-Therefore $\theta_i' = {\theta^j}'$. We have by Proposision
-\ref{sellerstrategy} and (\ref{???}eqn 30), that $\theta^j = \max_{i\in\mcI^j}
-\theta_i$, and so for any $i\in\mcI^j, \theta^j(z) \ge \theta_i(z)$, and so $j$
-cannot set a higher reserve price, and also cannot sell more data than the buyers'
-bids, so we have that $j$'s bid is both truthful and optimal.
-\\----------------------REF-------------------------\\
-% NEW MARKET PRICE
-\begin{align}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
-\end{split}
-\end{align}
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
-    D^j \big] : \\
-    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
-\end{split}
-\end{align}
-% DATA ALLOCATION RULE
-\begin{align}
-    a_i^j(s) \\
-    &= \min\bigg\lbrace e_i^j(D_i),
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
-\end{align}
-% DATA COST
-\begin{align}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-p^j \bigg(ai^j(0; s_{-i}^j)
-    -a_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
-% BUYER DEMAND 
-\begin{equation}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
-\end{equation}
-% BUYER REVENUE 
-\begin{equation}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-% SELLER REVENUE 
-\begin{equation}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-\begin{equation}
-    \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
-\end{equation}
-\begin{equation}
-    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-\begin{equation}
-    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-\begin{equation}
-    d_i^j \ge e_i^j(a)
-\end{equation}
-\begin{equation}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
-\end{equation}
-\begin{equation}
-    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
-\end{equation}
-\begin{equation}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
-\end{equation}
-\\----------------------------------------------------\\
-(SELLER FINISH)\\
-This forms a ``truthful" local game embeddeded within $j$'s auction with strategy space
+
+Now suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i(s_i;s_{-i}) > u_i(t_i;
+s_{-i}) + \epsilon$. Let $\xi = \min_k e_i^k\circ a_i^k(s)$, and $\forall \ j,
+\zeta_i^j = \xi/\vs_i^j$ and $s_{i^*} = (\zeta_i,p_i)$. Then from
+(\ref{coordination}), $a_i^j(s_{i^*}; s_{-i}) = \zeta_i^j$, therefore
+\begin{align*}
+    &\qquad u_i(s_{i^*};s_{-i}) \\
+    &= \displaystyle\int_0^\xi {\theta_i}'(\eta)\ d\eta -\sum_j\int_0^\xi P_i^j(\eta/\vs_i^j) \ d\eta.
+\end{align*}
+By Lemma \ref{coordinationlemma}, $u_i(s_{i^*}, s_{-i}) > u_i(t_i; s_{-i}) +
+\epsilon$, which is equivalent to 
+$$
+    \int_\epsilon^\xi {\theta_i}'(\eta) \ d\eta - \sum_j\int_0^\xi
+P_i^j(\eta/\vs_i^j) \ d\eta > \epsilon.
+$$
+The rest of the calculation follows as in \cite{semret} with the modified
+framework, i.e. both $\bar\epsilon = \epsilon + \epsilon/{\theta_i}'(0)$ and
+$\xi > \bar\epsilon$ show a contradiction.
+(DO I NEED TO SHOW THE CONTRADICTION?)
+
+We address the case where $e=\chi_i$, that is, the seller $j^*$'s data price is
+equal to the budget of buyer $i$ under the strategy given in
+(\ref{opt-out}), similarly to \cite{semret}, in this case any bid $s_{i^*}$
+where $u_i(s_{i^*}) > u_i(t_i)$ is not feasible, as the buyer would go over its
+budget.
+
+Finally, suppose that $j^* = I$, that is, $\mcI_i = \mcI$. 
+In this case, if $u_i(s_{i^*}) > u_i(t_i)$, then
+the demand cannot be satisfied by the sellers and the bid is not feasible.
+
+We proceed to examine the strategy of the seller. As we have shown, the seller
+is a functional extension of the buyer, with rules determined by the buyers'
+behavior. As we have shown, the buyers are bidding truthfully, according to the
+rule of incentive compatibility. Seller $j$'s reserve price is determined by a
+buyer $i \in \mcI \setminus \mcI^j$, and therefore, even if this price is zero,
+then $p^j = \epsilon \ge 0$.
+We argue that if truthfullness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
+\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then there exists a market
+equilibrium. We have the following Lemma.
+
+{
+\lemma{(Incentive compatibility in local auctions)}
+For any seller $j$, let time $t \in \tau$ be fixed, as well as bids from $j$'s
+seller pool, so that $s_i$ is fixed $\forall \ i \in\mcI^j$. The
+``$\epsilon$-best" reply for seller $j$ is,
+$$
+    s^j = (b^j, p^j),
+$$
+defined by Proposition \ref{sellerstrategy}.
+%and fix $j$'s reserve price $p^j$ as is defined by (\ref{newprice}). 
+The sellers' ``truthful" strategy, combined with Proposition
+\ref{buyerincentivecompatibility}, forms a
+``truthful" local game embeddeded within $j$'s auction, and an equilibrium of
+the embedded game is an equlibrium point for the local auction. 
+}\\
+\textbf{Proof:}
+We have that $p^j$ is the lowest price that $j$
+will accept to perform any allocation. By the definition of ``reserve
+price", $j$ is willing to buy its own budget $b^j$ at price $p^j$. This forms a
+``truthful" local game embeddeded within $j$'s auction with strategy space
 restricted to $\epsilon$-best replies from buyers $\in \mcI^j$. Therefore we have that a
-fixed point in the ``truthful" local game is a fixed point for the auction. We
-further argue that as the set $\mcI^j$ is
+fixed point in the ``truthful" local game is a fixed point for the auction.
+To see this, we observe that from (\ref{datacomposed}), $\forall \ i \in \mcI^j$, $\bar{D}_i^j(y, s_{-i}) =
+0 \ \forall \ y < p^j$, and so $y=0 \le \epsilon \Rightarrow e_i^j(a) = 0$. We
+further argue that by Lemma \ref{buyerresponse}, and as the set $\mcI^j$ is
 computed at each bid iteration, that our result holds for time $(t+1) \in \tau$.
+(NEED MORE? EACH CASE IN 4.3?)
 
@@
 Progressive Second Price Auctions},
-46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
+2007 46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
 779-784.
@@
 \textit{China Mobile Hong Kong Company Limited}.
-\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html}.
+\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html} 
 2018
@@
 
-\bibitem{matt}
-Matthias Roggendorf and Fernando Beltr{\'a}n,
-\textit{Simulation Model for the Dynamic Allocation of Network Resources in a
-Competitive Wireless Scenario}. Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
-pp. 54 - 64.
-
-\bibitem{diffserve}
-N. Semret, R. R. F. Liao, A. T. Campbell and A. A. Lazar, 
-\textit{Pricing, provisioning and peering: dynamic markets for differentiated Internet services and
-implications for network interconnections}, in IEEE Journal on Selected Areas in
-Communications, vol. 18, no. 12, pp. 2499-2513, Dec. 2000.
-
 \end{thebibliography}

### 2018-04-20 paper_wc.tex
Switching to sigma, reviewing Lemma 4.4

@@
 \newcommand{\mcI}{\mathcal{I}}
+\newcommand{\g}{\sigma}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \begin{split}
-    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
-    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
+    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
 \end{split}
@@
 \begin{split}
-    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
+    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
 \end{split}
@@
 \begin{align}\label{dataallocation}
-    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
+    a_i^j(s) &= \min\bigg( d_i^j, 
+    D_i^j(p_i^j,s_{-i}^j)\bigg).
 \end{align}
@@
 \begin{equation}\label{opt-out}
-    e_i(a) = [e_i^j(a)]_{j\in\mcI}.
+    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
 \end{equation}
@@
 \begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ e_i(a) - c_i,
+    u_i = \theta_i \circ \g_i(a) - c_i,
 \end{equation}
@@
 in any auctions. At time $t=0$, a seller $k$ entering the market will have submitted bid
-$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform.
+$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform. We assume that the auction
+begins at time $t>0$, and so $j$ will increment through a single iteration,
+initializing bid prices.
 
@@
 bids, i.e. using the same bid for all auctions.
-Using buyer bid quantity $e_i^j(a)$, from (\ref{opt-out}), 
+Using buyer bid quantity $\g_i^j(a)$, from (\ref{opt-out}), 
 we have the following Lemma,
@@
 \lemma{(Buyer constraints)}\label{buyerconstraints}
-Let $i\in\mcI$ be a buyer with bid, $s_i = (e_i(a), p_i)$, which must obey
+Let $i\in\mcI$ be a buyer with bid, $s_i = (\g_i(a), p_i)$, which must obey
 the following constraints,
 \begin{equation}\label{buyercapmax}
-    \sum_{j\in\mcI} e^j_i(a) \le D_i,
+    \sum_{j\in\mcI} \g^j_i(a) \le D_i,
 \end{equation}
@@
 \begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} e_i^j(a), 
+    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} \g_i^j(a), 
 \end{equation}
@@
 \begin{equation}\label{datacapmin}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \ge D^j.
+    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j.
 \end{equation}
@@
 from the buyers. Therefore, (\ref{reservepricemax}) and (\ref{datacapmin}) hold. Together, (\ref{datacapmax}) and
-(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} e_i^j(a) >  D^j$. In
+(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} \g_i^j(a) >  D^j$. In
 this case, by (\ref{dataallocation}), $j$ may submit a partial bid to a buyer
@@
 \begin{equation}\label{buyervaluation}
-    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
+    \theta_i \circ \g_i(a) = \displaystyle\sum_{j\in\mcI}
+ \int_0^{\g_i^j(a)} f_i(z) \ dz.
 \end{equation}
@@
 \begin{equation}\label{sellervaluation}
-    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ e_i^j(a) = \sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
+    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ \g_i^j(a) = \sum_{i\in\mcI}
+ \int_0^{\g_i^j(a)} f^j(z) \ dz.
 \end{equation}
@@
 \ref{buyerconstraints} and Lemma \ref{sellerconstraints}, we have,
-$d_i^j = e_i^j(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j =
-\sum_{i\in\mcI} e_i^j(a) = D^j = D_i$. It is worth observing that this result
+$d_i^j = \g_i^j(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j =
+\sum_{i\in\mcI} \g_i^j(a) = D^j = D_i$. It is worth observing that this result
 does \emph{not} imply that $s_i=s^j$. Let $\xi$
-be a unit of data from buyer bid quantity $e_i^j(a)$.
+be a unit of data from buyer bid quantity $\g_i^j(a)$.
 If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
@@
 
+\subsection{PSP Formulation}
+
+We intend to show that our auction
+is rational and achieves the desired VCG properties, as does the original
+formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
+realistic, theoretic, and notational templates, we define optimal strategies for
+CMHK users, and demonstrate that the development of a set PSP auction mechanisms
+in a data exchange setting is able achieve a network equilibrium for cellular data.
+
+% MECHANISM
+\subsubsection{Data Auction Mechanism}\label{datamechanism}
+We now proceed to formally define the PSP auction, which determines the actions 
+buyers and sellers in the CMHK market, and which we will denote the \emph{data}
+PSP rules. The rules presented here incorporate of the opt-out function with the
+mechanism as in \cite{lazar}, which we note greatly simplifies our
+analysis. 
+The market price function (MPF) for a buyer in the CMHK market
+can be described as follows:
+% NEW MARKET PRICE
+\begin{align}\label{dataprice}
+\begin{split}
+    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
+s_{-i}^j) \\
+    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
+    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z) \bigg\rbrace \bigg),\\
+\end{split}
+\end{align}
+and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
+order to obtain
+data amount $z$ given opponent profile $s_{-i}$. We note that
+the total minimum price for the buyer must be an aggragation of the
+\emph{individual} prices of the buyers as it is possible that the reserve prices
+of the individual sellers may vary.\\
+\textbf{Remark:} We further note that except at points of discontinuity, from
+Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
+%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
+%buyer $i$'s bid quantity. 
+The maximum available quantity of data in auction
+$j$ at unit price $y$ given $s_{-i}^j$ is: 
+% NEW ALLOCATION RULE
+\begin{align}
+\begin{split}\label{datacomposed}
+    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+.
+\end{split}
+\end{align}
+% DATA ALLOCATION RULE
+The resulting data allocation rule is a function of the local market
+interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
+allocation from auction $j$ is,
+% and so for profile $s_i$, for any $i \in \mcI$,
+\begin{align}\label{dataallocation}
+\begin{split}
+    \bar{a}_i^j(&s) = \g_i^j \circ a_i^j(s) \\
+    &= \min\bigg\lbrace \g_i^j(a), 
+    \frac{d_i^j}{\displaystyle\sum_{p_k^j= p_i^j}d_k^j} 
+D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
+\end{split}
+\end{align}
+noting that for the full allocation from all auctions we may simply aggregate
+over the seller pool.
+Finally we must have that the cost to the buyer adheres to the second price
+rule for each local auction, with total cost to buyer $i$,
+% DATA COST
+\begin{align}\label{datacost}
+\begin{split}
+    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
+    p_i^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
+    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
+\end{split}
+\end{align}
+
+\subsection{Market Strategy}
 \subsubsection{Buyer Strategy}
@@
 determine that some buyers must split their bids among multiple sellers. 
-We propose the following strategy to determine when rational
-(utility-maximizing) buyers will opt-out of a local auction. (QUESTIONING WHETHER OR NOT $\mcI_i$ SHOULD
+(DO I WANT ISP UPDATE?, MORE FAIR NOT TO, OVERHEAD EITHER WAY)
+We assume that sellers update their bids with the ISP, which is modeled as a
+``buyer" $\kappa$. (CAN I GIVE SELLERS A CHOICE TO UPDATE WITH ISP?)
+(WITHOUT UPDATED KNOWLEDGE, WE CAN HAVE FAIRNESS/)
+A new sellers' bid, $(D^j, \epsilon)$, is public knowledge, however the buyer does not have
+price information until joining the auction. (FINISH!)
+We reason that buyers,
+in addition to fufilling their data requirement, have incentive to join
+multiple auctions in order to compare prices. Each seller that buyer $i$ adds
+to its pool potentially decreases $i$'s bid quantity in all other auctions, and
+so each buyer $i\in\mcI$ directly impacts other buyers in auctions where buyers intersect.
+Indeed, each auction joined has the potential to decrease the price a buyer
+will pay for its data. We therefore introduce a fee paid by the buyer in order
+to join an auction, to be absorbed by the bid fee $\epsilon$, creating
+incentive for the buyer to minimize its seller pool. This has the effect of
+equity on the buyers. A buyers equity may be considerd work done to find
+sellers, monetary fees, or effort of communication from participation, and so
+is naturally absorbed by the bid fee as characterized in \cite{semret}.
+
+Thus, we determine when rational (utility-maximizing) buyers opt-out of a local auction. 
+We propose the following strategy, 
+(QUESTIONING WHETHER OR NOT $\mcI_i$ SHOULD
 BE ORDERED BY DATA, OR IF PRICE IS BETTER, PRETTY SURE IT IS OK, WILL FIND OUT
@@
 Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t\in\tau$. % For any allocation $a$ at time $t$, let
+$t>0\in\tau$, and let $a$ be $i$'s desired allocation. 
 % OPT-OUT BUYER STRATEGY
-%\begin{equation}\label{opt-out}
-    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
-    %e_i^j(a) \triangleq a_i^j,
-%\end{equation}
-%and define,
 Define the composition,
 $$
-     e_i^j \circ a = e_i^j(a) = \frac{a_i^j}{j},
+     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
 $$
@@
     n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
+    %n = \min\bigg( j\ \vert\ j\in \mcI_i(n): \sum_{k\in\mcI_i}\frac{D^k}{k}\ge
 \end{equation} 
@@
 \begin{equation}\label{opt-minallocation}
-    e_i^j(a) \triangleq \begin{cases} e_i^{j^*}(a), \quad j\in\mcI^j,\\
+    \g_i^j(a) \triangleq \begin{cases} \g_i^{j^*}(a), \quad j\in\mcI^j,\\
             0, \quad j\ni\mcI^j.\end{cases}
@@
 Now, (\ref{opt-minallocation}) holds $\forall \ j\in\mcI$,
-and we have that $e_i$ defines an optimal feasible strategy for buyer $i$.
+and we have that $\g_i$ defines an optimal strategy for buyer $i$.
 }\\
@@
 $d_i^{j(t+1)}$, is such that
-$d_i^{j(t+1)} < e_i^{j(t)}(a)$ where $e_i^{j(t)}(a)$ is $i$'s bid at time $t$.
+$d_i^{j(t+1)} < \g_i^{j(t)}(a)$ where $\g_i^{j(t)}(a)$ is $i$'s bid at time $t$.
 Then, by the definition of $\mcI_i$, once the buyer implements its strategy, we can
@@
 $$
-    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
+    \g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a),
 $$
@@
 $k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal. We note that feasibility
-is not addressed here, as we provide this analysis in Section \ref{???}.
+and we determine that the opt-out strategy is optimal.\\
+\textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
+are complementary. In fact, the buyer strategy is the first term in the
+minimum, the seconda term being owned by the buyer.
 
@@
 \subsubsection{Seller Strategy}
-(POSSIBILITY OF SWITCHING TO BUYER POOL ORDERED BY DATA, IF SELLER POOL GETS
-SWITCHED TOO)
+(POSSIBILITY OF SWITCHING TO BUYER POOL ORDERED BY DATA, SHOULD THEY BE
+OPPOSITE?)
 In order to to develop the seller strategy, we examine the incentive of a
@@
 In addition, buyers are allowed to bid both dynamically and asychronously. 
-
 In order to
@@
 determine that the seller may modify its reserve price in response to the
-changing market dynamics. (MORE!)
+changing market dynamics.
+
 We will show that sellers are able to maximize revenue in restricted subset of
 buyers in $\mcI$, and as such will attempt to facilitate a local market
-equilibrium for this subset.
-
-We describe the sellers' \emph{local} auction strategy for allocating its
-data according to the constraints formed by the buyer strategy. A
-local auction may be described as a progressive game of strategy with
+equilibrium for this subset. A local auction $j$ converges when all buyer bids
+remain the same over a time step, that is, if $\forall \ i \in\mcI$,
+$s_i^{j(t+1)} = s_i^{j(t)}$, at which point the allocation is stable, the data
+is sold, and the auction ends. In the sellers' local environment, we determine
+that the best course of action is to maximize revenue, and then try to keep its
+buyer pool stable until convergence occurs. Thus, the seller strategy is
+complementary to that of the buyers, and is designed to achieve and maintain a
+local market equilibrium.
+
+We describe a \emph{local} auction strategy for data allocation, where the seller is unaware of the existence of other auctions, and so
+the seller behavior is the same in the case of a single buyer, a small buyer set, and in the
+extreme case, where all buyers $i\in\mcI$ participate. We again note that the
+seller must initialize the strategy with a first iteration, and so the auction
+is defined for time $t>0$.
+In our model, a local auction may be described as a progressive game of strategy with
 incomplete, but perfect information, however in our analysis, as before, we will assume
 complete information. 
-(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
+(BUYERS ARRIVE AS A POISSON PROCESS? FUTURE WORK)
 
@@
 Define any auction duration to be $\tau \in [0,\infty)$. 
-For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t\in\tau$.
-Define
+For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t>0\in\tau$.
+Define the set,
 $$
@@
 \end{equation} 
-The determination of $n$ produces a minimal subset 
+where $n$ produces a minimal subset 
 of buyers that maximizes $j$'s revenue at time $t$, which we will
@@
 \end{equation} 
-Define buyer $i^* = n-1 \le I$ as the buyer with the maximum price $\ni
+Define buyer $i^* = n-1 \le I$ as the buyer with the maximum bid price $\ni
 \mcI^j$.
@@
 \begin{equation}\label{newprice}
-    p_i^j = p_{i^*}^j + \epsilon,
+    p_i^{j(t+1)} = p_{i^*}^{j(t)} + \epsilon,
 \end{equation}
@@
 \begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i\in I^j} p_i^j,
+    \bar{i} = \displaystyle\max_{i\in I^j} p_i^{j(t)},
 \end{equation}
 and update $j$'s total data to reflect the (tentative) allocation,
-\begin{equation}\label{newbudget}
-    D^{j(t+1)} = D^{j(t)} - e_{\bar{i}}^{j(t)}(a),
-\end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{winner}) -
+\begin{equation}\label{newdata}
+    D^{j(t+1)} = D^{j(t)} - \g_{\bar{i}}^{j(t)}(a),
+\end{equation}
+Allowing $t$ to range over $\tau$, we have that (\ref{sellercoordinate}) -
 (\ref{newbudget}) produces a local market equilibrium. 
@@
 \textbf{Proof:}
-We assume that the seller has enough data to satisfy at least one buyer,
-and that they want to maximize their revenue.
-In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
+We assume that the seller will try to maximize its revenue. In the case where
+$\vert\mcI^j\vert =1$, then if $\g_i^j(a)=D^j$, then $j$'s market is at equilibrium.
+Otherwise, we arrive at the case of multiple buyers, which we note includes the
+case where $\g_i^j(a) < D^j$, which is reflected trivially here.
+
+For auction $j$ with multiple buyers, $i^*$ is the \emph{losing} buyer with the highest unit
 price offer, determined by (\ref{sellercoordinate}), 
 Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
-In this case, by (\ref{}) the seller must notify $i$ of a
+In this case, by (\ref{datacapmin}) the seller must notify $i$ of a
 fractional allocation by changing the bid vector at index $i$.
@@
 Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that buyers are bidding truthfully, and so ${\theta_i}' + \epsilon
-=p_i^j + \epsilon$.
-Now, using
-(\ref{sellervaluation}), we have, $\forall \ z\ge 0$,
-\begin{align*}
-    \int_0^{e_{i^*}^j(a)} f_{i}(z)\ dz &\le\int_0^{e_i^{j}(a)}
-f^{j}(z) \ dz 
-\end{align*}
-and so,
-$$
-     \theta_i \circ e_{i^*}(a) \le \theta_i \circ e_i(a),
-$$
-which holds $\forall \ j \in \mcI_i$.
-It follows that, using
-%, using (\ref{buyercoordinate}), 
-the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
-for any $\epsilon$-best reply, 
-$$
-    p_i^j \le {\theta_i}'(v_i^j) + \epsilon,
-$$
-$\forall i \in \mcI^j$.
-Therefore the choice of $p_i^j$ does not force any buyers out of the local
-auction. Thus we determine the valuation between seller
+that buyers are bidding truthfully, and so the new reserve price $p_{i^*}^j +
+\epsilon ={\theta_{i^*}}' + \epsilon$. For clarity, let the reserve price be denoted by
+$p_*^j$.
+Now, by the point elasticity of (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}) (PROVE POINT ELASTICITY?), we have that, $\forall \ z\ge 0$,
+$$
+    f_{i^*}(z) < f^j(z) \le f_i(z), 
+$$
+which holds $\forall \ i \in \mcI^j$, and $\forall \ j \in \mcI_i$.
+We claim that the choice of reserve price $p_*^j$ does not force any buyers out
+of the local auction. To show this, we use the assumption of truthful bids, and
+the fact that since the auction begins at time $t>0$, buyers will
+bid at least once. In a truthful reply, the term $\epsilon/\theta_i'(0)$
+ensures that a new bid price differs from the last bid price by at least
+$\epsilon$. Suppose the auction starts at equilibrium, so $\sum_{i\in\mcI^j}
+\g_i^j(a) = D^j$ at time $t=0$. The reserve price $p_*^j$ set at time $t=0$
+begins the auction with the first bid iteration, and so at $t>0$, $\forall \ i \in
+\mcI^j$, we have that $p_i^j - p_*^j \ge \epsilon$.
+Now, in the case where at $t=0$, $\sum_{i\in\mcI^j} \g_i^j(a) > D^j$, by
+(\ref{dataallocation}), the seller notifies (any) buyer $k$ with the lowest bid price of a fractional allocation by changing
+$d_k^j$ thus by Proposition \ref{buyerstrategy}, $k$ decreases its demand until
+$\g_i^j(a) \le d_i^j$. Then, as the seller computes the set $\mcI^j$ at each time
+step, a new $i^*$ may be chosen and the buyers bid again.
+Suppose $\exists \ k \in \mcI^j$ such that $\forall \ l \ \in
+\mcI_k, \ i\ni \mcI^l \ \forall \ i\ne k\in\mcI^j$. That is, $k$ is
+disconnected from all other buyers $i\in\mcI^j$, and suppose that $d_k^j$
+is partial allocation at $t>0$, and further suppose that there are many
+$l\in\mcI_k$ where $\vert \mcI^l\vert > \vert\mcI^j\vert$. The more buyers an
+auction has, the more likely that cases will occur that cause buyers to rebid,
+particularly if auctions $l\in\mcI_k$ have overlapping buyers, then $k$ may
+opt-out of auction $j$, i.e. $s_k^{j(t)} \ne s_k^{j(t+1)} =
+0$, then the seller may simply return the tentatively allocated data to $D^j$.
+Finally, we note that if for some $i\in\mcI^j \ \exists \ k\in\mcI^j$
+such that $p_{i}^j = p_k^j$, then the seller again notifies the buyers of a fractional
+allocation by changing $d_i^j$ and $d_k^j$ by (\ref{dataallocation}).
+Thus we determine the valuation between seller
 $j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
-equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-We note the special case where for winner $\bar{i}$, $\ \exists \ k\in\mcI^j$
-such that $p_{\bar{i}}^j =
-p_i^k$. In this case the seller again notifies the buyers of a fractional
-allocation by changing $d_i^j$ and $d_k^j$ to reflect the proportional
-division. Finally, in the case where winning buyer(s) \emph{opts-out} of the local
-auction, where $j\in\mcI_i$ at time $t$, then at time $(t+1)$ $j\ne \mcI_i \Rightarrow s_i^{j(t+1)} = (0,0) \Rightarrow i \ne
-\mcI^j$, which is mathematically analogous to the definition of opting-out in our
-scenario. The seller may simply return the tentatively allocated data to $D^j$,
-and recompute $\mcI^j$ and $p_{i^*}^j$, 
-$$
-    D^{j(t+1)} = D^{j(t)} + \displaystyle\sum_{i\in\Gamma} d_i^{j(t)}
-$$
-where $\Gamma$ represents the buyers who have opted-out from time $t$ to 
-$(t+1)$, indicated by a zero bid from any buyer $\in \mcI^j$:
-$$
-    \Gamma = \lbrace i\in \mcI^j : s_i^{j(t+1)} = 0\rbrace.
-$$
-
-(NOTE - NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK IN
-FRACTIONAL ALLOCATIONS? SAVE FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
+equlibirium created by $j$ is independently stable from time $t$ to $(t+1)$.
 
@@
 global market through its buyers. We demonstrate that the symmetry between
-buyer and seller rules stretches into a symmetry across subsets of local
+buyer and seller behavior, consequently strategies, stretches into a symmetry across subsets of local
 auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. We have the following Lemma.
-\newpage
+local auctions on each other. We have the following Lemma,
 % USER UNION
@@
 \end{equation}
-Fix an auction $j\in\mcI$ and define the influence sets of users. 
+Fix an auction $j\in\mcI$ with duration $\tau$ and define the influence sets of users. 
 The primary influencing set is given as,
@@
 \end{equation}
-***********************************
-\begin{equation}
-    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
-\begin{equation}
-    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
-\end{equation}
-and for each $i\in\mcI^j$ define,
-\begin{equation}
-    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
-\bigg).
-\end{equation}
-we have $\forall \ i \in
-\mcI^j$,
-\begin{equation}\label{sym}
-    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
-\end{equation}
-
-***********************************
 \fi
-Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$, we have that,
+Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
 \begin{equation}\label{unioneq}
@@
 A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $i$'s bid is such that $p_i^j \ge p_{i^*}^j$, where
+profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
+if and only if $i$'s bid is such that $p_i^j > p_{i^*}^j$, where
 (\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price in auction $j$.
-Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
-If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
-Proposition \ref{buyerstrategy}, $i^*$
-will add sellers to its pool until its demand is satisfied. Therefore for any
-$j\in\mcI_i$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
+price in auction $j$. By (\ref{buyerinversedemand}) $p_i^j \ge
+p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
+shift, caused by the underlying dynamics.
+Consider $k\in\mcI^j$ where for example, new buyers enter the auction, or increase
+thier bid prices, so that $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
+$s_k^j>0$ at time $t$. 
+By Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
+Suppose that at time $t$, $j$'s market is at equilibrium, i.e. $\sum_{i\in\mcI^j} = D^j$, and
+no buyer rebids. Unless $k$ adds a seller with a higher reserve
+price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
+auction will end. Otherwise, at some time $t\in[t+1,\tau]$, we must have that $\g_k^j <
+D^j$, and $k$ opts-out. Finally, overlooking market transitions and messaging
+overhead, we have that,
+$\forall \ i\in\mcI^j$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and (\ref{jtoi})
 holds.
+\iffalse
 Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
@@
 \equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
+\fi
 
@@
 the lowest price that $j$ will accept to perform any allocation.
-Let $p_*^j = f^j \circ e_i^j(a) $ denote the reserve
+Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
 price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ e_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
+[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
 \ \forall \ k \in\mcI_i$. 
@@
 \begin{equation}\label{maxbid}
-    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ e_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
+    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
 \end{equation}
@@
 \begin{align*}
-    \int_0^{e_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ e_i^j(a)\\
-    &= \int_0^{e_i^j(a)} f_i(z) \ dz,
+    \int_0^{\g_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ \g_i^j(a)\\
+    &= \int_0^{\g_i^j(a)} f_i(z) \ dz,
 \end{align*}
@@
 \begin{equation}\label{jdemand}
-    \displaystyle\sum_{i\in\mcI^j}\int_0^{e_i^j(a)} f^j(z) \ dz =
-\sum_{j\in\mcI_i}\int_0^{e_i^j(a)} f_i(z) \ dz.
+    \displaystyle\sum_{i\in\mcI^j}\int_0^{\g_i^j(a)} f^j(z) \ dz =
+\sum_{j\in\mcI_i}\int_0^{\g_i^j(a)} f_i(z) \ dz.
 \end{equation}
@@
 \begin{equation}\label{idemand}
-    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{e_i^k(a)}
+    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
 f_i(z) \ dz,
@@
 \begin{align*}
-    \int_0^{e_i^k(a)} f_i(z) \ dz &= \int_0^{e_i^k(a)} f^k(z) \ dz,
+    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
 \end{align*}
@@
 \begin{align*}
-    \int_0^{e_l^k(a)} f^k(z) \ dz &= \int_0^{e_l^k(a)} f_l(z) \ dz,
+    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz,
 \end{align*}
@@
 preferences.
-
-\subsection{PSP Formulation}
-
-We intend to show that our auction
-is rational and achieves the desired VCG properties, as does the original
-formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
-realistic, theoretic, and notational templates, we define optimal strategies for
-CMHK users, and demonstrate that the development of a set PSP auction mechanisms
-in a data exchange setting is able achieve a network equilibrium for cellular data.
-
-% MECHANISM
-\subsubsection{Data Auction Mechanism}\label{datamechanism}
-We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the CMHK market, and which we will denote the \emph{data}
-PSP rules. The rules presented here incorporate of the opt-out function with the
-mechanism as in \cite{lazar}, which we note greatly simplifies our
-analysis. 
-The market price function (MPF) for a buyer in the CMHK market
-can be described as follows:
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
-s_{-i}^j) \circ e_i^j \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
-order to obtain
-data amount $z$ given opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices
-of the individual sellers may vary.\\
-\textbf{Remark:} We further note that except at points of discontinuity, from
-Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
-
-%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
-%buyer $i$'s bid quantity. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is: 
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}\label{datacomposed}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+.
-\end{split}
-\end{align}
-% DATA ALLOCATION RULE
-The resulting data allocation rule is a function of the local market
-interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
-allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-\begin{split}
-    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
-    &= \min\bigg\lbrace e_i^j(a), \\
-    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \big(
-D_i^j(p_i^j,s_{-i}^j)\big)\bigg\rbrace,
-\end{split}
-\end{align}
-noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool.
-Finally we must have that the cost to the buyer adheres to the second price
-rule for each local auction, with total cost to buyer $i$,
-% DATA COST
-\begin{align}\label{datacost}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-p^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
-    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
 
@@
 \end{algorithm}
-We assume that each time that $s^j$ is updated it is shared with all
+We assume that each time step that $s^j$ is updated it is shared with all
 participating buyers. At this point buyers have the opportunity to bid again,
@@
 \proposition{(Incentive compatibility in local auctions)}
-For any seller $j$, let time $t \in \tau$ be fixed and for any buyer $i\in
+For any seller $j$, let time $t>0 \in \tau$ be fixed and for any buyer $i\in
 \mcI^j$, let $s_{-i}$ also be fixed. )VALIDATE: FOR ALL j) Define,

### 2018-04-20 paper_wc.tex
Down to mechanism realization.

@@
 and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
-$j$. For the purposes of our analysis, we will assume that a zero bid from a
+$j$. We additionally determine that a user who does not submit a bid is holding
+its previous bid, either zero or nonzero. For the purposes of our analysis, we will assume that a zero bid from a
 buyer is equivalent to no bid.
@@
 
-\subsection{User Behavior}
+\subsection{User Valuation}
 
@@
 
-\subsubsection{Market Dynamics}
+\subsubsection{Valuation under Market Dynamics}
 The buyer demand largely motivates the market price function, however, the
@@
 
-\subsection{PSP Formulation}
+\subsection{PSP for Data-Exchange}
 
@@
 
-\subsection{Market Strategy}
+\subsection{User Behavior}
 \subsubsection{Buyer Strategy}
@@
 determine that some buyers must split their bids among multiple sellers. 
-(DO I WANT ISP UPDATE?, MORE FAIR NOT TO, OVERHEAD EITHER WAY)
+(DO I WANT ISP UPDATE?, MORE FAIR NOT TO?)
 We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. (CAN I GIVE SELLERS A CHOICE TO UPDATE WITH ISP?)
-(WITHOUT UPDATED KNOWLEDGE, WE CAN HAVE FAIRNESS/)
+``buyer" $\kappa$. (CAN I GIVE SELLERS A CHOICE TO UPDATE WITH ISP? WITHOUT
+KNOWLEDGE -> FAIRNESS?)
 A new sellers' bid, $(D^j, \epsilon)$, is public knowledge, however the buyer does not have
@@
 Indeed, each auction joined has the potential to decrease the price a buyer
-will pay for its data. We therefore introduce a fee paid by the buyer in order
-to join an auction, to be absorbed by the bid fee $\epsilon$, creating
-incentive for the buyer to minimize its seller pool. This has the effect of
-equity on the buyers. A buyers equity may be considerd work done to find
+will pay for its data, in exchange for additional messaging overhead, possible
+fees, and increased competition from other buyers. We determine that this aspect of
+a buyers' valuation represents equity, the liabilies from which may be considered work done to find
 sellers, monetary fees, or effort of communication from participation, and so
@@
 
+The buyer strategy bids in auctions with the highest quantity bids first,
+a natural exploitation of the demand curve. A new seller entering the market
+with a large quantity bid will be in high demand. This behavior contributes to market price
+stability, as seller valuation is determined by buyer demand, and as such, the
+buyer strategy drives sellers towards similar quantity bids, and therefore
+similar prices. Market equilibrium is achieved when each buyer has equal bids in
+each auction. Our bidding strategy is inspired by \cite{lazar}, and we also
+hold buyers to consistent bids, where buyers sumbit identical bids to a
+subset of sellers with the highest offers.
 Thus, we determine when rational (utility-maximizing) buyers opt-out of a local auction. 
 We propose the following strategy, 
-(QUESTIONING WHETHER OR NOT $\mcI_i$ SHOULD
-BE ORDERED BY DATA, OR IF PRICE IS BETTER, PRETTY SURE IT IS OK, WILL FIND OUT
-IN LATER PROOFS)
 % BUYER STRATEGY
@@
 vector $e_i$ with respect to its strategy, where
-\begin{equation}\label{opt-minallocation}
+\begin{equation}\label{opt-eq}
     \g_i^j(a) \triangleq \begin{cases} \g_i^{j^*}(a), \quad j\in\mcI^j,\\
@@
 \end{equation}
-Now, (\ref{opt-minallocation}) holds $\forall \ j\in\mcI$,
+Now, (\ref{opt-eq}) holds $\forall \ j\in\mcI$,
 and we have that $\g_i$ defines an optimal strategy for buyer $i$.
@@
 will only consider one. Suppose seller $j$ updates its
-bid to reflect the new data quantity, $j$'s bid quantity at time $(t+1)$,
-$d_i^{j(t+1)}$, is such that
-$d_i^{j(t+1)} < \g_i^{j(t)}(a)$ where $\g_i^{j(t)}(a)$ is $i$'s bid at time $t$.
-Then, by the definition of $\mcI_i$, once the buyer implements its strategy, we can
-only have that $j \ni \mcI_i$, or that $n$ has been increased so that and new seller(s)
-enter the pool. 
-Additionally, we consider the entrance of a new buyer $k$ at time $(t+1)$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
+bid to reflect the new data quantity, where
+$d_i^{j(t+1)} < \g_i^{j(t)}(a)$. First, $i$ sets its bid to $s_i^j = 0$, and
+from the new subset $\mcI_i$, submits bids (PARALLEL OR SEQUENTIAL?) until
+$\sum_{j\in\mcI_i} d_i^j \ge D_i$, by (\ref{buyercapmin}).
+Now, we consider the case where a new buyer $k$ with bid
+price $p_k^j > p_i^j$ for some $j \ \in \mcI_i$, in other
 words, a new buyer $k$ may enter the market with a better price, decreasing the
-value of $i$'s bid for sellers $\in\mcI_i$. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
-$n$ so that
+value of $i$'s bid for $j\in\mcI_i$. In this case, by (\ref{buyercoordinate}),
+$i$ will choose $\mcI_i$ so that,
 $$
@@
 $$
-and the subset $\mcI_i$ is large enough to balance the additional demand from
+and so $\mcI_i$ is large enough to balance the additional demand from
 $k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
@@
 are complementary. In fact, the buyer strategy is the first term in the
-minimum, the seconda term being owned by the buyer.
+minimum, the second term being owned by the seller.
 
@@
 possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
-minimal ordered subset where a
-coordinated bid is possible, the reasoning for which we will address in Section
+minimal subset where a coordinated bid is possible.
 \ref{analysis}.
@@
 \subsubsection{Seller Strategy}
-(POSSIBILITY OF SWITCHING TO BUYER POOL ORDERED BY DATA, SHOULD THEY BE
-OPPOSITE?)
 In order to to develop the seller strategy, we examine the incentive of a
@@
 Allowing $t$ to range over $\tau$, we have that (\ref{sellercoordinate}) -
-(\ref{newbudget}) produces a local market equilibrium. 
+(\ref{newdata}) produces a local market equilibrium. 
 }\\
@@
 \begin{equation}\label{unioneq}
-    \displaystyle\sum_{j\in\Lambda} \theta^j = \sum_{i\in\lambda} \theta_i.
+    \displaystyle\sum_{j\in\Lambda} \theta_i^j = \sum_{i\in\lambda} \theta_i^j.
 \end{equation}
@@
 Now, the subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
-coordinated, truthful bid, $\mcI_i\subset \mcI$ 
-will determine the unit price $p_{i}$ in buyer $i$'s bid.
-The reserve price (\ref{newprice}) of seller $j$ is determined at time $t$, and is
+determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
+coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
+determines the unit price $p_{i}$ in buyer $i$'s bid.
+The reserve price (\ref{newprice}) of seller $j$ is determined at each
+transition, and is
 the lowest price that $j$ will accept to perform any allocation.
 Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ the (coordinated) bid price of buyer $i$, i.e. $p_i^k = p_i^*,
+price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
+[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
 \ \forall \ k \in\mcI_i$. 
-Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy}, $\forall \ i \in \mcI^j$, we have that $p_i^* \ge p_*^k,
+Using Proposition
+\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
 \ \forall \ k \in\mcI_i$.
@@
 $\lambda = \mcI^j$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we clearly
-have that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
+clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
 In all other cases, the sellers $\in\Lambda$ are competing to sell
@@
 \end{equation}
-$\Lambda$ is the set of sellers that directly influence the bids of buyers
-$\in\mcI^j$. the reserve price for auction $j$ is such that,
+$\Lambda$ is the set of sellers directly influencing the bids of buyers
+in auction $j$. Now, the reserve price for auction $j$ is such that,
 \begin{equation}\label{resprice}
@@
 by Proposition \ref{sellerstrategy}. 
-
-We have from Proposition \ref{sellerstrategy} that $j$ maintains a local market
-equilibrium at time $t$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
-and suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Then, a change in $q$'s valuation from time $t$ to $t+1$ will
-directly impact seller $j$. If at time $t+1$ we still have that $i$ is the
+Also, in the absence of transitions, caused by multi-auction market dynamics, we have 
+that $j$ maintains a local market
+equilibrium from time $t$ to $(t+1)$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
+and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
+that $p_*^q > p_*^j$. Fixing all other bids, a change in $q$'s valuation from time $t$ to $t+1$ will
+directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
 buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
@@
 have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
-fixed time $t$, and so, $\forall \ i \in\mcI^j$,
+some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
 \begin{align*}
@@
 Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$. We have that
+that $p_l^* < p_*^j$, and
 the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, and so we must
-have that $p_l^* < p_i^*$,
-and necessarily, $p_i^* > p_l^*$ for
-any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so,
+$$
+    p_*^k \le p_l^* < p_*^j \le p_i^*,
+$$
+for any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
 p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$. % \Rightarrow \theta_l^q > \theta_l^k$. 
-Again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
+$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
+which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
 \ni\mcI^q \Rightarrow p_*^q >
@@
 buyer $i$. 
-Lastly, 
-in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
+Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
 We have that for any $l\in\mcI^k$ such that $l\ni
@@
 has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$. Thus, in all cases,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold.
-We have,
+$\in\Lambda$, and therefore cannot cause transitions to occur except through a
+shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
+(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
+bids in any auction $\mcI^q$, where $q\in \mcI_l$ and $q\ni \Lambda$,
+we have, for any $i\in\mcI^j$,
 \begin{equation}\label{idemand}
     \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
-f_i(z) \ dz,
-\end{equation}
-which holds for all buyers and sellers that satisfy (\ref{jtoi}).
+f^k(z) \ dz,
+\end{equation}
+which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
+\ref{sellerstrategy}..
 Finally, using (\ref{jdemand}), (\ref{idemand}), 
@@
 \begin{equation}
-    \displaystyle\sum_{j\in\Lambda} \int_0^{D^j} f^j(z) \ dz =
-\sum_{i\in\lambda}\int_0^{D_i} f_i(z) \ dz.
+    \sum_{i\in\lambda}\int_0^{\g_i^j(a)} f^j(z) \ dz = \sum_{j\in\Lambda}\int_0^{\g_i^j(a)} f_i(z) \ dz.
 \end{equation}
@@
 bid fee.
-
-(ADD TIME? INDUCTION GOES HERE? DID NOT SHOW!)
-
-(OWN
-WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
-competing in multiple local auctions hosted by the sellers, the two games are
-inter-dependent, and may be played on the same or on a different scale in
-valuation, time (AND....).
-
-PSP relies on the \emph{relevation prinicple}; the
-PSP mechanism is able to demonstrate equlibrium by showing that PSP is
-incentive-compatible. (MORE?)
-Arrow's paradox is an impossibility theorem stating that when voters have three
-or more distinct alternatives (options), no ranked voting electoral system can
-convert the ranked preferences of individuals into a community-wide (complete
+(NEED TO DO BETTER WITH TIME?)
+
+As a result of user behavior, and subsequent strategies, we determine that the data-exchange market is
+semi-partitioned, consisting of unions as in Lemma \ref{userunion}. The unions are inter-dependent in a predictable way. However, as
+each auction may be played on the same or on a different scale in
+valuation, time and quantity, the rate at which market fluctuations occur is
+impossible to predict (NEED HELP!). 
+Arrow's paradox is an impossibility theorem stating that when buyers have three
+or more distinct alternatives (auctions), no deterministic ranking system can
+convert the ranked preferences of users into a market-wide (complete
 and transitive) ranking while also meeting a specified set of criteria:
 unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives.
-
-Thus, (WHAT? FINISH, OWN WORDS)
-The designer of a mechanism generally hopes either to design a mechanism
-y() that "implements" a social choice function to find the
-mechanism y() that maximizes some value criterion (e.g. profit)
-Independence of irrelevant alternatives (IIA)
-The IIA condition has three purposes (or effects)
-
-Normative
-Irrelevant alternatives should not matter.
-Practical
-Use of minimal information.
-Strategic
-Providing the right incentives for the truthful revelation of individual
-preferences.
-
-\subsubsection{Mechanism Realization}\label{realization}
+irrelevant alternatives. It follows that the case where
+$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}) does not exist, and is purely a potential,
+theoretical ideal. (DOES IT????)
+
+Nonetheless, we claim that our mechanism is normative, that irrelevant
+alternatives should not matter, it is practical, uses minimal information,
+strategy, and provides the right incentives for the truthful revelation of individual preferences. 
+(EXPAND)
+
+\subsection{Mechanism Realization}\label{realization}
 

### 2018-04-24 paper_wc.tex
Finished elastic demand, starting incentive compat over lambdas (experimental).

@@
 The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
-CLAIM 'IS') described as a
-pure-strategy progressive game with incomplete, but perfect information. (WHAT
+CLAIM 'IS') described as a \emph{locally}
+pure-strategy progressive game with incomplete, but perfect information.
+ you have perfect information, since you know what each move of the opponent is.
+However, since you do not know the payoff function of the other player (which
+will affect its behavior even if it does not alter your own victory conditions),
+it is a game of incomplete information.
+In the overall market analysis assumes complete, but perfect information.
+
+ (WHAT
 DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
@@
 therefore we identify each local auction with the identity of the seller
-$j\in\mcI$, and that the user valuation
-\iffalse
-is independently and identically
-distributed (i.i.d.) and
-\fi
-satisfies the conditions for an
+$j\in\mcI$.
+We further show that user valuation satisfies the conditions for an
 \emph{elastic demand function}, as in \cite{lazar}.
@@
 in any auctions. At time $t=0$, a seller $k$ entering the market will have submitted bid
-$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform. We assume that the auction
-begins at time $t>0$, and so $j$ will increment through a single iteration,
+$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform. A buyer entering the market
+at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
+(SAY BETTER!) is initialized as 
+an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
+probability $\mathcal{P}$,
+$$
+    \mathcal{P}[\epsilon\le X \le \kappa] =
+\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
+ds,
+$$
+where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
+density function of $X$.
+%may represent by some homogenous function of degree one (EXPAND?). 
+Thus the auction
+begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
 initializing bid prices.
@@
 A given demand may lead to diffent prices, which emerge directly from the users valuation
-of the resources and, possibly, their decision strategies. The seller does not
+of the resources and their decision strategies. The seller does not
 require a priori demand information.
 It is worth mentioning that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, to derive properties.
+a game assumes some forms of demand and supply, in order to derive properties.
 The mechanism itself does not require any knowledge of user demand or
@@
 \begin{equation}\label{datasupply}
-    \rho_i(y) = \sum_{j\in\mcI : p_i^j\le y} D^j.
+    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
 \end{equation}
@@
 that a buyer has the choice to opt-out of any auction, and so seller $j$ has an
-incentive to set its reserve price to include enough buyers to sell all its
+incentive to set its reserve price to sell the maximum amount of
 data. Thus we have the following Lemma,
@@
 influence on the market. We have already introduced the composition $\theta_i
-\circ e_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
+\circ \g_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
 (\ref{datademand}) and (\ref{sellerinversedemand}). We first note that, in
@@
 \end{equation}
-Now, we may define seller $j$'s valuation in terms of revenue, so we have,
+Now, we may define seller $j$'s valuation in terms of revenue,
 \begin{equation}\label{sellervaluation}
@@
 \end{equation}
+We have that $\theta_i$ and $\theta^j$ are elastic valuation functions, with
+derivatives
+${\theta_i}$ and ${\theta^j}'$ satisfing the conditions of elastic demand.
 }
 \textbf{Proof:} 
+Let $\xi$
+be a unit of data from buyer bid quantity $\g_i^j(a)$.
+If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
+similarly decrease. The lost potential revenue for seller $j$ is the price of
+the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
+$$
+    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
+$$
+Thus (\ref{sellervaluation}) holds.
+As we may use the same argument for (\ref{buyervaluation}), as such, we will
+denote $f_i=f^j=f$ for the remainder of the proof. We observe that the function
+$f$ is the first
+derivative of the valuation function with respect to
+quantity. Letting $\theta_i=\theta^j=\theta$, the existence of the derivative implies $\theta$ 
+is continuous, and therefore, in this context, $f$ represents
+the marginal valuation of the user, ${\theta}'$. Also, clearly
+$\theta(0)=\theta(\sigma(0)) = 0$. Now, as we consider data to be an infinitely
+divisible resource, we have a continuous interval between allocations $a$ and
+$b$, where $a\le b$. Now, as $\theta$ is continuous, for some $c\in[a,b]$, 
+$$
+\theta'(c) = \lim_{x\to c}\frac{\theta(x) - \theta(c)}{x-c} = f(c),
+$$
+and so $f=\theta'$ is continuous at $c\in[a,b]$, and so as $a\ge 0$, 
+$\theta'\ge 0$. Finally, we have that concavity follows from the demand
+function. Then, as $\theta'$ is
+non-increasing, we may denote its derivative $\gamma \le 0$,
+and taking the derivative of the Taylor approximation, we have, $\theta'(z) \le
+\theta'(\eta) + \gamma(z-\eta)$.
+
 We assume that a buyer wants to minimize the cost of purchasing their data
-requirement, at the same time ensuring they get the full allocation $e_i(a)$,
+requirement, at the same time ensuring they get the full allocation $\g_i(a)$,
 and so must minimally meet $j$'s reserve price. 
@@
 \sum_{i\in\mcI} \g_i^j(a) = D^j = D_i$. It is worth observing that this result
-does \emph{not} imply that $s_i=s^j$. Let $\xi$
-be a unit of data from buyer bid quantity $\g_i^j(a)$.
-If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
-similarly decrease. The lost potential revenue for seller $j$ is the price of
-the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
-$$
-    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
-$$
-Thus (\ref{sellervaluation}) holds.
-As we may use the same argument for (\ref{buyervaluation}), we complete the
-proof with the observation that the function $f^j$ (resp. $f_i$) is the first
-derivative of the valuation function with respect to
-quantity, and therefore, in this context, represent the marginal valuations of the
-users, ${\theta^j}'$ (resp. $\theta_i'$). Finally, the sellers' natural utility is the potential
+does \emph{not} imply that $s_i=s^j$. 
+Finally, the sellers' natural utility is the potential
 profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
@@
 \begin{split}\label{datacomposed}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+.
+    \bar{D}_i^j(y,s_{-i}^j) &= \g_i^j \circ D_i^j( y,s_{-i}^j)\\
+    &= \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
 \end{split}
@@
     &= \min\bigg\lbrace \g_i^j(a), 
-    \frac{d_i^j}{\displaystyle\sum_{p_k^j= p_i^j}d_k^j} 
+    \frac{\g_i^j(a)}{\displaystyle\sum_{p_k^j= p_i^j}\g_k^j(a)} 
 D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
@@
 \end{align}
+\textbf{Remark:} The cost to buyer $i$ adds up the willingness
+of all buyers excluded by player $i$ to pay for quantity $\bar{a}_i^j$. i.e.
+$$
+    c_i^j(s) = \displaystyle\int_0^{\bar{a}_i^j} P_i^j(z, s_{-i}) \ dz.
+$$
+This is the ``social opportunity cost" of the PSP pricing rule.
+
+The formulation is inspired to the thinnest allocation route for
+bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
+satisfy $i$'s demand, then
+(\ref{buyerutility}) reduces to the original form, defined in
+\cite{semret} as ``a simple buyer at a single resource element".
+
+(OWN WORDS!)
+The cost function will therefore be a stepwise-linear function, which is
+increasing in slope with each new bidder excluded from the market.
 
 \subsection{User Behavior}
+
 \subsubsection{Buyer Strategy}
@@
 determine that some buyers must split their bids among multiple sellers.
-(DO I WANT ISP UPDATE?, MORE FAIR NOT TO?)
+
 We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. (CAN I GIVE SELLERS A CHOICE TO UPDATE WITH ISP? WITHOUT
-KNOWLEDGE -> FAIRNESS?)
-A new sellers' bid, $(D^j, \epsilon)$, is public knowledge, however the buyer does not have
-price information until joining the auction. (FINISH!)
-We reason that buyers,
+``buyer" $\kappa$. 
+A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids, is public
+knowledge. Also, we reason that buyers,
 in addition to fufilling their data requirement, have incentive to join
-multiple auctions in order to compare prices. Each seller that buyer $i$ adds
+multiple auctions in order to compare prices.
+Each seller that buyer $i$ adds
 to its pool potentially decreases $i$'s bid quantity in all other auctions, and
@@
 will pay for its data, in exchange for additional messaging overhead, possible
-fees, and increased competition from other buyers. We determine that this aspect of
+fees, and increased competition from other buyers. This aspect of
 a buyers' valuation represents equity, the liabilies from which may be considered work done to find
@@
 
-The buyer strategy bids in auctions with the highest quantity bids first,
+The buyer strategy bids in auctions with the highest quantities first,
 a natural exploitation of the demand curve. A new seller entering the market
-with a large quantity bid will be in high demand. This behavior contributes to market price
-stability, as seller valuation is determined by buyer demand, and as such, the
-buyer strategy drives sellers towards similar quantity bids, and therefore
+with a large quantity of data will be in high demand. This behavior contributes to market price
+stability, as seller valuation is determined by buyer demand, the
+buyer strategy tends towards equal valuation of all local markets, and therefore
 similar prices. Market equilibrium is achieved when each buyer has equal bids in
@@
 $$
-where buyer $i$ chooses its seller pool by determining $n$, where
+where buyer $i$ chooses its seller pool by determining $n$, for $j\in\mcI_i$,
 \begin{equation}\label{buyercoordinate}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
-    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
-    %n = \min\bigg( j\ \vert\ j\in \mcI_i(n): \sum_{k\in\mcI_i}\frac{D^k}{k}\ge
+    \min\big\lbrace n \in \mcI \ \vert \ n D^n\ge D_i\big\rbrace. 
 \end{equation} 
@@
 \begin{equation}\label{sellercoordinate}
-    n = \min( i \ \vert \ i \in\mcI^j(n) : \displaystyle\sum_{i\in\mcI} d_i^j \ge
-D^j),
-\end{equation} 
-where $n$ produces a minimal subset 
+    \min\bigg\lbrace n \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(n)}d_i^j
+\ge D^j \bigg\rbrace,
+\end{equation} 
+so that $n$ produces a minimal subset 
 of buyers that maximizes $j$'s revenue at time $t$, which we will
@@
 (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
-bids in any auction $\mcI^q$, where $q\in \mcI_l$ and $q\ni \Lambda$,
-we have, for any $i\in\mcI^j$,
+bids in any auction $\mcI^q$, where $q\in \mcI_l \setminus \Lambda$,
+we have, $\forall \ k\in\mcI_i$,
 \begin{equation}\label{idemand}
@@
 \ref{sellerstrategy}..
-Finally, using (\ref{jdemand}), (\ref{idemand}), 
+Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
 \begin{align*}
@@
 and the result follows by construction, and the continuity of $\theta'$:
-\begin{equation}
+\begin{equation}\label{union-eq}
     \sum_{i\in\lambda}\int_0^{\g_i^j(a)} f^j(z) \ dz = \sum_{j\in\Lambda}\int_0^{\g_i^j(a)} f_i(z) \ dz.
@@
 
-\subsection{Mechanism Realization}\label{realization}
-
 Consider a user seeking to prevent
-data overage by purchasing enough data from a subset of other network users.
-This user $i$ can be modeled as a opt-out buyer where, as in \cite{semret},
-We intend to show that this network setting results in a shared network optima (a
-global optimum). The formulation is inspired to the thinnest allocation route for
-bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
-satisfy $i$'s demand, then
-(\ref{buyerutility}) reduces to the original form, defined in
-\cite{semret} as ``a simple buyer at a single resource element".
-
+data overage charges by purchasing data from a subset of other network users.
 The sellers' auction will function as follows: at each bid iteration all buyers
@@
 satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
-sellers' data has been allocated. We design an algorithm based on the sellers'
-fractional allocation strategy.
-
-(NOTE - FIX TO UPDATED NOTATION!)
+sellers' data has been allocated. 
+Each time step, $s^j$ is updated it is shared with all
+participating buyers. At this point buyers have the opportunity to bid again,
+where a buyer that does not bid again is assumed to hold the same bid, since a
+buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
+define a single iteration of the auction, wher a seller updates bid vector
+$s^j$, and the buyers' response $s_i$, to comprise a single time step.
+
 % SELLER ALGORITHM
 \begin{algorithm}[H]
-\caption{(Seller fractional allocation)}
+\caption{(Seller progressive allocation)}
 \begin{algorithmic}[1]
-\State $p^{j(0)} \gets \epsilon$
-\State $s^{j(0)} \gets (p^j, D^j)$
-\While{$D^j > 0$}
-\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \lbrace i \in \mcI^{j(t)}: d_i^j >
-D^{j(t)}\rbrace$
-\State $ \bar{i} \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
-\State $D^{j(t+1)} \gets D^{j(t)} - e_{\bar{i}}^{j(t)}(a)$
+\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
+\emptyset$, compute
+$\mcI^{j(0)}$
+\State Update $s^j$ 
+\While{$D^j(t) > 0$}
+\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
+\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
 %\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
@@
 \State $s^{j(t+1)} \gets (d^j, p^j)$
-\If{$\ \exists \ i : s_i^{j(t+1)} \ne s_i^{j(t)}$}
-\State $D^{j(t+1)} = D^{j(t)}$
+\State Update $s^j$
+\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
+\For{$k \in \bar\mcI$}
+\If{$p_k^j < p_{i*}^j$}
+\State $D^{j(t+1)} = d_k^{j}$
+\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
+\EndIf
+\EndFor
+\State Compute $\mcI^{j(t)}$
+\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
 \State $t \gets t+1$
 \State Go to 4.
-\Else
-\State $\bar{i} \gets e_{\bar{i}}^j(a)$
-%\State $\beta^{j(t+1)} \gets \bigg\lbrace i\in\mcI^j: 
-%        d_i \le \bar{b}^j \bigg\rbrace$
-\State $t \gets t+1$
-\State Go to 4.
-\EndIf
 \EndWhile
@@
 \end{algorithm}
-We assume that each time step that $s^j$ is updated it is shared with all
-participating buyers. At this point buyers have the opportunity to bid again,
-where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. As we will show in our analysis, the buyers are bidding truthfully; the
-algorithm makes use of the fact that the sellers' valuation is determined by
-the buyers' market and upholds the PSP mechanism. (CHECK) (ALSO $j$ NEEDS TO
-UPDATE FOR NEW BUYERS, $j$'S CONTROL)
-
-(BUYER ALGORITHM? WHY NOT..., CLEANER)
+Finally, we give a simple example of a convergence to a local market equilibrium, where the buyers are assumed to respond with their
+$\epsilon$-best replies.
+\begin{center}
+\begin{tabular}{c|c|c}
+Name & Bid total & Unit price\\
+\hline
+A & 50 & 1\\ 
+B & 40 & 1.2\\
+C & 26 & 1.5\\
+D & 20 & 2\\
+E & 14 & 2.2
+\end{tabular}
+\end{center}
+Let $s^{(1)} = [(65,\epsilon)]_{i\in\mcI}$ and
+$s^{(2)}=[(85,\epsilon)]_{i\in\mcI}$. The buyer bids are as follows: 
+\begin{align*}
+    s_A &= [(0,0), (50,1)], \\
+    s_B &= [(0,0), (40,1.2)], \\
+    s_C &= [(0,0),(26,1.5)], \\
+    s_D &= [(0,0),(20,2)], \\
+    s_E &= [(0,0), (14,2.2)]. 
+\end{align*}
+Then at $t=1$, we have 
+bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}), (20,p^{(2)}),\\
+(14,p^{(2)})]$, and so  $(D^{(2)},p^{(2)}) = (85, 1+\epsilon)$, The buyer response is,
+\begin{align*}
+    s_A &= [(50,1), (0,0)], \\
+    s_B &= [(40,1.2), (0,0)], \\
+    s_C &= [(0,0),(26,p^{(2)})], \\
+    s_D &= [(0,0),(20,p^{(2)})], \\
+    s_E &= [(0,0),(14,p^{(2)})].
+\end{align*}
+At $t=2$, $(D^{(1)},p^{(1)}) = (65,1+\epsilon)$, with
+bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0),\\ (0,0),
+(0,0)]$. $(D^{(2)},p^{(2)}) = (25, 1+\epsilon)$. Then,
+\begin{align*}
+    s_A &= [(25,p^{(1)}), (25,p^{(2)})], \\
+    s_B &= [(40,p^{(1)}), (0,0)], \\
+\end{align*}
+where we have removed bids to indicate winner(s) with a tentative allocation.
+At $t=3$, $(D^{(1)},p^{(1)}) = (50,1+\epsilon)$, with
+bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0),\\ (0,0),
+(0,0)]$. $(D^{(2)},p^{(2)}) = (0, 1+\epsilon)$ and $s^{(2)}=[(25,p^{(1)}),
+(0,0), (26,p^{(2)}), (20,p^{(2)}),\\(14,p^{(2)})]$. Then,
+\begin{align*}
+    s_A &= [(25,p^{(1)}), (0,0))].
+\end{align*}
+At $t=4$ the auction ends.\\
+\textbf{Remark:} In the case where market resources do not satisfy (\ref{buyercapmin}), however as
+this constraint is not restricted in time, we reason that in the case of
+insufficient data in the market buyers may wait for additional sellers or
+purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, for (\ref{datacapmin}) in
+the case of insufficient demand, where we may assume that data is held at time
+$t=0$ by $\kappa$ at bid price $\epsilon$.
 
@@
 \section{PSP Analysis}\label{analysis}
+
 \subsection{Equilibrium}
 
-Consider an opt-out buyer $i\in\mcI$. A PSP auction
-allows for a buyer to react to opponents bids, and so its incentive is based on
-the opponent profile.
-
-Due to (\ref{buyerutility}), $i$ only has an incentive to change its bid
-quantity if it increases its opt-out value $e_i$, and therefore its utility. 
-We will show that $i$ can coordinate its
-bids over $\mcI_i$ so that the opt-out value $e_i$ is the same for each
-$j \in\mcI_i$, and therefore, without loss of utility, $i$ may choose a seller pool 
-using a ``consistent" strategy, where for any $j\in \mcI_i$, $d_i^j = d_i^k, \
-\forall \ k \in \mcI_i$, and still have feasible best replies. 
+We intend to show evidence shared network optima (a
+global optimum). 
+A buyer $i\in\mcI$ will have incentive to change its bid
+quantity if it increases its opt-out value $\g_i$, and therefore its utility (\ref{buyerutility}). 
+We will show that, without loss of utility, buyer $i$ may  
+use a ``consistent" bid strategy within its seller pool, i.e. $d_i^j = d_i^k, \
+\forall \ j,k \in \mcI_i$, and as such,
+Proposition \ref{buyerstrategy} supports an optimal strategy with respect to
+(\ref{buyerutility}). 
 Our result shows that a buyer may select $\mcI_i$ in order to maximize its
 utility while maintaining a coordinated bid strategy. 
-It is intuitive that, if $j^*
-< I$, a buyer may increase the size of $\mcI_i$, thereby lowering its bid
+Reasonably, if $j^*< I$, a buyer may increase the size of its seller pool
+$\mcI_i$, thereby lowering its coordinated bid
 quantity while obtaining the same (potential) allocation $a_i$. 
-(OWN WORDS!)
-One important question to ask is why a bidder should bid with identical unit
-prices on (j) all auctions and not reduce the unit price to a level where he still wins the
-amount q i . The reason for this can be found in the pricing rule of the PSP auction. 
+As buyer $i$ submits identical bids to multiple auctions, the bid price must be
+as high as the highest reserve price $p_i^j \in \mcI_i$.
+Buyer $i$'s bid then has identical bid price $p_i^j \forall \ j \in\mcI_i$. 
+We further note that $i$ optimal strategy does not require reducing its bid price to a
+minimum in each auction, where
+the bid quantity $\g_i^j(a)$ is still fufilled. The pricing rule of the PSP
+auction dictates that a buyer $i$ will pay the cost of excluding other players from
+the auction, and as $i$'s bid price reflects its valuation of it data
+requirement $D_i$ across all local markets, we have identical bid prices in
+each auction where $s_i^j>0$. Obviously, if $j\ni\mcI_i$, then $\theta_i^j = 0$.
+
 % BUYER COORDINATION
@@
 Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
-For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
+For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be a
+tentative data
 allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
@@
 \begin{align*}
-    z_i^j &= e_i^{j^*}(a), \\
+    z_i^j &= \g_i^{j^*}(a), \\
     y_i^j &= \theta_i'(z_i^j).
@@
 $$
-If there exists a seller who can fully satisfy $i$'s demand,
+Now, if there exists a seller who can fully satisfy $i$'s demand,
 then $\vert\mcI_i\vert = 1$, and the case is trivial as no
-coordination is necessary for a single bid. (SPECIAL CASE OF MONOPOLY? THINK!)\\
+coordination is necessary for a single bid. %(SPECIAL CASE OF MONOPOLY? THINK!)\\
 Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
@@
 We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
-$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $u_i$.
-Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
+$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $\sum_{j\in\mcI_i}u_i^j$.
+Buyer $i$ maintains ordered set $\mcI_i$ where the sellers with the
 largest bid quantities are considered first; the index of seller $j^*$ defines
 a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity offered by any $j\in \mcI_i$,
-so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$; $\mcI_i$ also defines the
-maximum quantity bid of any $k \ni \mcI_i$.
-Thus by (\ref{buyercoordinate}) and (\ref{opt-minallocation}), $\forall \ j\in \mcI_i$,
+$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$,
+so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$. 
+Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
 $k\ni\mcI_i$,
 $$
-    e_i^k(a) \le z_i^j = e_i^{j^*}(a) \le e_i^{j}(a),
-$$
-and so, 
+    \g_i^k(a) \le z_i^j = \g_i^{j^*}(a) \le \g_i^{j}(a),
+$$
+and so, using (\ref{union-eq}), 
 \begin{equation}\label{minimaleq}
-    e_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+,
-\end{equation}
-The buyer valuation function (\ref{buyervaluation}), guarantees
+    \g_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
+\end{equation}
+Now, the buyer valuation function (\ref{buyervaluation}), guarantees
 that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
@@
 be accepted. 
-As $D_i$ is non-decreasing, $\forall \ j\in \mcI_i$,
+As $\bar{D}_i^j$ is non-decreasing, $\forall \ j\in \mcI_i$,
 $k\ni\mcI_i$,
@@
 $$
+\iffalse
 Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$e_k^{j^*}(a) \ge e_i^{j^*}(a)$ and so $d^j - d_k^j < z_i^{j}$, resulting in a
-partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
+$\g_k^{j^*}(a) \ge \g_i^{j^*}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
+partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
 As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $e_i^{j*}(a)
-\ge e_k^{j^*}(a)$ for any $k$, therefore such a buyer $k$ cannot exist.
-\iffalse
+set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j*}(a)
+\ge \g_k^{j^*}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
 We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
@@
 where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
-Now, since a buyer is only charged with the cost of excluding other players from the market, the
-unit price does not influence the final charges. This unit price reflects the
-valuation of the total resources gained from the multi-auction market, and so a buyer uses this price on all
-auctions.
-We have, $\forall \ j\  \in \mcI_i, \ \forall \ k \ni \ \mcI_i$,
-$$
-    y_i^j \ge p_i^j \ge p_{i^*}^j\ge p_i^k,
-$$
-and we observe that from (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
-0 \ \forall \ y < p_{i^*}^j$, and so $y=0 \le \epsilon \Rightarrow e_i^j(a) = 0$,
-and so clearly $z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
+From (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
+0 \ \forall \ y < p_{i^*}^j$, and $\bar{D}_i^j(y, s_{-i}) =0 \le \epsilon
+\Rightarrow \g_i^j(a) = 0 \Rightarrow z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
 \begin{align*}
@@
 seller $j \in \mcI_i$.
-We proceed to demonstrate that $x_i$ does not result in a loss of utility for
-buyer $i$; we will show that
+We proceed to show that $x_i$ does not result in a loss of utility for
+buyer $i$, that is,
 $$
@@
 $$
-From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = e_i^j(a(z_i,y_i))$, 
+From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = \g_i^j(a(z_i,y_i))$, 
 and so,
 $$
-    \theta_i\circ e_i^j(a(z_i,y_i)) = \theta_i\circ e_i^j(a),
+    \theta_i\circ \g_i^j(a(z_i,y_i)) = \theta_i\circ \g_i^j(a),
 $$ 
@@
 \begin{align*}
-    &\theta_i\circ e_i(a(z_i,y_i)) - \theta_i(a)\circ e_i(a) \\
+    &\theta_i\circ \g_i(a(z_i,y_i)) - \theta_i(a)\circ \g_i(a) \\
     &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
-    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - z) \ dz.
+    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - x) \ dx.
 \end{align*}
 Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
-$\theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
-%1. buyers have same d but diff p
-%2. " same p but diff d i.e. d1 < d2
-Finally, as we do
-not increase the aggragate demand of the buyer, $\sum_{j\in\mcI_i} c_i^j(s) \le 
-\sum_{j\in\mcI_i} b_i^j$, and so $x_i$ is feasible.
-
-In effect, we are using the buyer demand
-to partition the auction space based on their type (EXPLAIN). \\
+$z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
+%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
 
@@
 
-We proceed to claim that the optimality of truth-telling holds in our
-formulation, where the market functions as a hybrid of \cite{semret} and
-\cite{zheng}. The opt-out buyers' market is comprised of the minimal subset of
-sellers with the largest amounts of available data, described in the buyer strategy as $\mcI_i$.
-To achieve incentive compatibility, we find that the opt-out buyer must choose this subset so that
-its overall marginal value is greater than its market price.
-The buyers' market price is calculated as the maximum of the reserve prices
-of the sellers in the opt-out buyers' pool.
-the market prices at the %different auctions, weighted by the data provisioning vector values.
-The actual bids are
-obtained from the opt-out buyers' strategy. The quantity to bid is given
-by the auction mechanism, i.e. (\ref{dataprice}) and (\ref{datacomposed}), as
-the maximim possible quantity of data that a buyer $i$ can bid over its seller
-pool while maintaining its aggragate marginal valuation greater than the aggragate of
-minimum prices maintained by the sellers in $i$'s pool.
-As with a single resource, \cite{semret} and
-\cite{lazar}, we show that truth-telling is optimal for the buyer, i.e. in each auction, the buyer sets
-the bid price to the marginal value.
-
-Seller $j$'s reserve price is determined by a
-buyer $i \ni \mcI^j$, and therefore, even if this price is zero,
-then $p^j = \epsilon \ge 0$.
-
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a local market
-equilibrium (NOTE: NOT GLOBAL! YET). We have the following Proposition. For
-completeness, we use the full notation. (BAD SENTENCE)
+The property of truthfullness is an essential component of equilibrium in
+second-price markets. The strategies described in this paper have removed the
+necessity for a user to determine its own valuation function, and due to our
+construction, we intend to show that truthful bids are optimal for all users,
+i.e. bid prices are to the marginal value as determined by market dynamics. 
+To achieve incentive compatibility, we find that the opt-out buyer must choose
+this subset so that its overall marginal value is greater than its market price.
+
+(DO I NEED TO PROVE CONTINUITY TOO?)
 
 {
-\proposition{(Incentive compatibility in local auctions)}
-For any seller $j$, let time $t>0 \in \tau$ be fixed and for any buyer $i\in
-\mcI^j$, let $s_{-i}$ also be fixed. )VALIDATE: FOR ALL j) Define,
+\proposition{(Incentive compatibility across local auctions)}
+Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
+$t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
+buyer $i\in \mcI^j$, (DO I WANT LAMBDA? SO MANY CASES) let $s_k$ also be fixed $\forall \ k\ni i \in \lambda$. Define,
 \begin{align}
@@
     \eta_i &= \sup\bigg\lbrace x\ge 0 : 
- {\theta_i}'(x) > \bar{P}_i^j(x)\bigg\rbrace, 
+ {\theta_i}'(x) > \displaystyle\sum_{k\in\lambda} P_k^j(x)\bigg\rbrace, 
 \end{split}\\
 \begin{split}\label{chi}
-    \chi_i &= \sup\bigg\lbrace x\ge 0: 
-\displaystyle\int_0^x 
-    \bar{P}_i(x) \ dx \le \sum_{j\in\mcI_i}b_i^j \bigg\rbrace,
+    \chi_i &= \sup\bigg\lbrace x\ge 0: x \le
+\displaystyle\sum_{k\in\lambda}D_i^j(\theta_i'(x)) \bigg\rbrace,
 \end{split}
@@
 $$
-    v_i^j = e_i^{j^*}(z) 
+    v_i^j = \g_i^{j^*}(z) 
 $$
@@
 \textbf{Proof:}
+
 For the buyer, we show that $t_i$ is an $\epsilon$-best reply. That is,
@@
 $$
-Let $z = \eta_i^j$. We have that $i\in\mcI^j$, 
+Let $z = \eta_i^j$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
+price of auction $j$, and $p_i^*= f_i \circ \g_i^j(a)$ denote the (coordinated) bid price of buyer $i$. 
+We have that $i\in\mcI^j$, 
 and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
@@
 \\----------------------------------------------------\\
-(SELLER FINISH)\\
 This forms a ``truthful" local game embeddeded within $j$'s auction with strategy space
@@
 computed at each bid iteration, that our result holds for time $(t+1) \in \tau$.
+
+A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
+profile $s$,
+from which no player has a unilateral incentive to deviate (Johari, 2004)
+
+As a result of auction initialization, a seller $j$'s valuation defines its
+reserve price to be determined
+by a buyer $i \ni \mcI^j$, even if this price is zero, we have that $p^j = \epsilon \ge 0$.
+We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
+\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
+there exists a local market equilibrium extending over a subset of connected
+local markets. We have the following Proposition.
 

### 2018-04-26 paper_wc.tex
Rework user union.

@@
-\documentclass[12pt]{article}
-
-\usepackage[text={6in,8.1in},centering]{geometry}
+%\documentclass[journal,comsoc]{IEEEtran}
+\documentclass[sigconf, anonymous]{acmart}
+
+%\usepackage[text={6in,8.1in},centering]{geometry}
 
@@
 
-\lstset{ %
-language=C++,               
-basicstyle=\footnotesize,
-numbers=left,                  
-numberstyle=\tiny,     
-stepnumber=1,         
-numbersep=5pt,         
-backgroundcolor=\color{white},  
-showspaces=false,               
-showstringspaces=false,         
-showtabs=false,                 
-columns=fullflexible,
-frame=single,          
-tabsize=2,          
-captionpos=b,       
-extendedchars=true,
-xleftmargin=17pt,
-framexleftmargin=17pt,
-framexrightmargin=17pt,
-framexbottommargin=4pt,
-breaklines=true,       
-breakatwhitespace=false, 
-escapeinside={\%*}{*)}       
-}
-
-\newenvironment{block}{\begin{adjustwidth}{1.5cm}{1.5cm}\noindent}{\end{adjustwidth}}
-
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{corollary}{Corollary}[section]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\def\verbatimtabsize{4\relax}
-\def\listingoffset{1em}
-\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
-\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
-\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}
-
 \newcommand{\vs}{\varsigma}
@@
 
+\iffalse
+
+\newtheorem{proposition}{Proposition}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\newtheorem{corFollary}{Corollary}[section]
+\newtheorem{sublemma}{Lemma}[lemma]
+\theoremstyle{definition}
+\newtheorem{definition}{Definition}[section]
+
 \headsep25pt\headheight20pt
-
+\setcounter{secnumdepth}{4}
 \pagestyle{fancyplain}
@@
 \cfoot{\ \hfill\tiny\sl Draft printed on \today}
-
 \setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
 
+\fi
+
+%---------------ACM CCS---------------------%
+\fancyhf{} % Remove fancy page headers 
+\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
+\fancyfoot[C]{\thepage}
+
+\setcopyright{none} % No copyright notice required for submissions
+\acmConference[?]%Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
+\acmYear{2017}
+
+\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
+%-------------------------------------------%
+
 \begin{document}
-\begin{multicols}{2}
-
-\section{Abstract}
-
+%\begin{multicols}{2}
+\title{Title?}
+
+\begin{abstract}
 We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
@@
 market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
+\end{abstract}
+
+\iffalse
+% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10002978.10003029.10011703</concept_id>
+<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
+
+\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
+
+\keywords{template; formatting; pickling} % TODO: replace with your keywords
+\fi
+\maketitle
 
@@
 
+(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
+SENTENCES)
 In this work, we propose \emph{a distributed progressive second price (PSP) auction in
@@
 
-(FEE IS FIXED OR
-PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)
-
-The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
-CLAIM 'IS') described as a \emph{locally}
+(HOW DO WE MODEL ISP REVENUE? FUTURE WORK?)
+
+The form of the auction mechanism presented here is described as a \emph{locally}
 pure-strategy progressive game with incomplete, but perfect information.
- you have perfect information, since you know what each move of the opponent is.
-However, since you do not know the payoff function of the other player (which
-will affect its behavior even if it does not alter your own victory conditions),
-it is a game of incomplete information.
-In the overall market analysis assumes complete, but perfect information.
-
- (WHAT
-DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
-VALUATION.. FUTURE WORK)
-
-The paper is organized as follows...
-
-(MOVED: TO ORGANIZE)\\
+In a distributed setting, local markets have perfect local information, since you know what each move of the opponent is.
+However, since users are not aware of behavior in other auctions, it is a game of incomplete information.
+We complete a comprehensive analysis of market dynamics, and will assume
+complete and perfect information in order to verify properties and validate
+results of the auction mechanism.
+
+(TO ORGANIZE)\\
 The main contribution of this work 
@@
 across a distributed setting.
-We complete a comprehensive analysis of market dynamics, (FINISH)
 To the best of our knowledge, this is the first work to provide a truthful
@@
 able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and as our mechanism provides
-for effective communication between the connected users.
+incentive for a collaborative exchange, and as our mechanism provides incentives
+for optimal, effective communication between the connected users.
 
@@
 way to do the transformation from the direct revelation mechanism to the
-desired one. Our mechanism is naturally designed by guessing
+desired one. Our mechanism is designed by guessing
 right direct-revelation-to-desired-mechanism transformation and building it
@@
 
+The strategies described in this paper have removed the
+necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
+construction of the user strategy space results in truthful bids that are optimal for all users,
+i.e. bid prices are to the marginal value as determined by market dynamics. 
 This is the (built-in) transformation from the
 direct-revelation mechanism to the desired message space.
+
+The paper is organized as follows...
 
@@
 bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper. We
-conduct a comprehensive analysis, deriving a globally optimal strategy suited for
+bandwidth in wireless networks is not the focus of this paper. We derive a globally optimal strategy suited for
 users with local information in a distrubuted data-sharing model.
-Users in the CMHK market do not need to bid on a complete ``route", as in the
-bandwidth allocation problem \cite{semret}. Instead, our mechanism allows a buyer
+
+Our mechanism allows a buyer
 to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
@@
 We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is now of the form,
+function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
 \begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ \g_i(a) - c_i,
+    u_i = \theta_i \circ (\g_i(a)) - c_i,
 \end{equation}
 where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
-the buyers' valuation of allocation $a$ across local markets (and thus multiple sellers).
+the buyers' valuation of allocation $a$ across local markets (and thus multiple
+sellers), and $\theta_i(\g_i(a)) - \g_i(\varrho)$ represents the buyers'
+corresponding debit.  
 In this way we extend the PSP rules described
@@
 supply, as this is public information, however only buyers
-are able to determine supply or demand across multiple auctions after time $t=0$, and then only from auctions
+are able to determine supply or demand across multiple auctions, and then only from auctions
 in which they participate. \\
@@
 buyer strategy. (FUTURE WORK?)\\
-In order to represent the public platform of the secondary market, we model the ISP as
-a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
-in any auctions. At time $t=0$, a seller $k$ entering the market will have submitted bid
-$s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform. A buyer entering the market
-at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER!) is initialized as 
-an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
-probability $\mathcal{P}$,
-$$
-    \mathcal{P}[\epsilon\le X \le \kappa] =
-\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
-ds,
-$$
-where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
-density function of $X$.
-%may represent by some homogenous function of degree one (EXPAND?). 
-Thus the auction
-begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
-initializing bid prices.
-
-A given demand may lead to diffent prices, which emerge directly from the users valuation
-of the resources and their decision strategies. The seller does not
-require a priori demand information.
-It is worth mentioning that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, in order to derive properties.
-The mechanism itself does not require any knowledge of user demand or
-valuation. 
-\iffalse
-The ISP overage
-charge inducing an upper bound on the sellers' reserve prices implies that
-supply will always be greater than demand, thereby reducing the sellers'
-influence on market dynamics.
-\fi
-
-As the buyer valuation is elastic, even infinitesimal changes in the market dynamics can be
-modeled. This, and the homogenous nature of data in the CMHK market, 
-allows for the analysis of additional constraints imposed by the user
-strategies. Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
+
+In a multi-auction market, each auction a buyer joins has the potential to
+decrease the potential cost of its data. However, increasing the size of the
+auction implies a certain risk, which we may interpret as a potential and
+definite
+liability. Increasing the number of transactions causes additional messaging
+overhead, fees, and increased competition from other buyers. 
+A transaction also causes potential indirect costs, which may be considered work done to find
+sellers, or effort of communication from participation. A seller
+has the potential for greater profit with each new buyer in its auction, taking 
+the same risk.
+%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
+%and the individual. We denote the potential indirect costs of participation of
+%each user as $\varrho$.
+The liability of any user is naturally absorbed into the bid fee $\epsilon$,
+as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
+dependent on the association between two users and their market positions, in
+addition to the underlying network structure. Now, both sellers and buyers must consider
+the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
+OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)
+
+Elastic valuation functions allow for even infinitesimal changes in the market
+dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
+allows for the analysis of constraints imposed by the user strategies. 
+Buyers may directly impact each other in local market intersections.
+Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
 A buyers' valuation of an amount of data represents how much a buyer is willing
 to pay for that amount. 
-This is equivalent to the bid price that
-satisfies $\theta_i$ given a fixed amount of data. We determine the
+This is equivalent to the bid price, given a fixed amount of data,
+satisfying $\theta_i$. We determine the
 buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
@@
 lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers. We will later show, in Proposition
-\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
-bids, i.e. using the same bid for all auctions.
-Using buyer bid quantity $\g_i^j(a)$, from (\ref{opt-out}), 
-we have the following Lemma,
-{
-% BUYER CONSTRAINTS
-\lemma{(Buyer constraints)}\label{buyerconstraints}
-Let $i\in\mcI$ be a buyer with bid, $s_i = (\g_i(a), p_i)$, which must obey
-the following constraints,
-\begin{equation}\label{buyercapmax}
-    \sum_{j\in\mcI} \g^j_i(a) \le D_i,
-\end{equation}
-and, as $i$ is rational, and therefore utility-maximizing, $i$ must have
-sufficient bids $s_i^j > 0$ so that,
-\begin{equation}\label{buyercapmin}
-    \sum_{j\in\mcI} d^j_i \ge D_i,
-\end{equation}
-where $d_i^j$ denotes the bid quantity of seller $j$.
-}\\
-\textbf{Proof:}
-A rational buyer does not want to purchase extra data, as this would be
-equivalent to overpaying, and so (\ref{buyercapmax}) holds. We also assume that
-$i$ wants to fufill their data requirement, and so (\ref{buyercapmin}) implies
-that $i$ submits positive bids to a set of buyers that will be able to fufill
-their demand.
-
-The seller is similarly represented, however a seller only has
+the maximum reserve price amongst the sellers. 
+%We will later show, in Proposition
+%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
+%bids, i.e. using the same bid for all auctions.
+
+A seller only has
 information from buyers in its own auction, and may only be indirectly influenced by
@@
 and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
-price. Now, we determine that, in addition to some natural constraints, the sellers' highest
-``possible" price is conditioned by
-additional restrictions on its pricing function, the motivation for which is
-that a buyer has the choice to opt-out of any auction, and so seller $j$ has an
-incentive to set its reserve price to sell the maximum amount of
-data. Thus we have the following Lemma,
-{
-% SELLER CONSTRAINTS
-\lemma{(Seller constraints)}\label{sellerconstraints}
-Let $j\in\mcI$ be a seller with bid $s^j$, then $j$ must obey the following constraints.
-A bid $s_i^j= (d_i^j, p_i^j)$, to buyer $i$ must be such that,
-\begin{equation}\label{datacapmax}
-    \sum_{i\in\mcI} d^j_i \le D^j,
-\end{equation}
-In addition, for a rational seller, the reserve price must
-satisfy, $\forall \ i\in \mcI$,
-\begin{equation}\label{reservepricemin}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j),
-\end{equation}
-and,
-\begin{equation}\label{reservepricemax}
-   p_i^j \le \max_{i\in\mcI}\big(p_i^j).
-\end{equation}
-Finally, as $j$ is rational, $j$ must submit enough bids $s_i^j >0$ so that,
-\begin{equation}\label{datacapmin}
-    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j.
-\end{equation}
-}\\
-\textbf{Proof:}
-The first statement is obvious, 
-a seller cannot sell more data than they have,
-Then, (\ref{reservepricemin})
-follows from the assumption that $j$ is rational, and so utility-maximization
-acts as revenue maximization, a rational seller will not sell its
-data at a price less than the lowest offer. Finally, as a rational seller will
-attempt to maximize profit, and will try and sell all of its data, and so we
-must have sufficient demand
-from the buyers. Therefore, (\ref{reservepricemax}) and (\ref{datacapmin}) hold. Together, (\ref{datacapmax}) and
-(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} \g_i^j(a) >  D^j$. In
-this case, by (\ref{dataallocation}), $j$ may submit a partial bid to a buyer
-$i$ so that $\sum_{i\in\mcI} d^j_i = D^j$.
-
-We proceed to determine the properties and characteristics of the user valuation functions. Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-distributed across the CMHK market via bids in local auctions. 
-As such, buyer behavior is influenced by opponent bid profiles from multiple auctions.
-We therefore determine that the valuation of any user must be modeled as a function of the entire
-marketplace. Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We model the valuation of
-users based on the opt-out user behavior, thereby including the buyers'
-influence on the market. We have already introduced the composition $\theta_i
+price.
+
+The valuation of any user must be modeled as a function of the entire
+marketplace. 
+Naturally, a buyers' valuation is aggragated over local markets, and the
+sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
 \circ \g_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
@@
 \theta'(\eta) + \gamma(z-\eta)$.
-
-We assume that a buyer wants to minimize the cost of purchasing their data
-requirement, at the same time ensuring they get the full allocation $\g_i(a)$,
-and so must minimally meet $j$'s reserve price. 
-A seller will try to maximize profit, 
-and so will try to sell all of its data.  By Lemma
-\ref{buyerconstraints} and Lemma \ref{sellerconstraints}, we have,
-$d_i^j = \g_i^j(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j =
-\sum_{i\in\mcI} \g_i^j(a) = D^j = D_i$. It is worth observing that this result
-does \emph{not} imply that $s_i=s^j$. 
-Finally, the sellers' natural utility is the potential
+$\qed$
+
+Utility is defined by their valuation, and is the basis for user behavior. 
+The sellers' natural utility is the potential
 profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
@@
 of mobile data plans is outside the scope of this paper.  
-
+Now, a rational user will try
+to maximize its utility, thus, user incentive manifests as a
+response to market dynamics. A buyer has the choice to
+opt-out of any auction, and as a seller will try to sell the maximum amount of
+data, the highest possible reserve price is conditioned by ``natural" constraints. Utility-maximization 
+acts as revenue maximization for a rational seller, and as cost minimization for a
+rational buyer. Thus, for each user $p_i^j \ge \min\big(p_i^j)$ and $p_i^j \le
+\max\big(p_i^j)$, which holds $\forall \ i, j\in\mcI$ such that $s_i^j>0$.
+Now, rational buyer does not want to purchase extra data, as this would be
+equivalent to overpaying, however $i$ submits positive bids to a set of
+sellers, and a rational seller will attempt to maximize profit, and so will try and sell all of
+its data. Therefore,
+\begin{equation}\label{bidcap}
+    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j \quad\text{and}\quad
+\sum_{j\in\mcI} d^j_i \ge D_i,
+\end{equation}
+which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
+constraint from our formulation.
+Thus, at equilibrium all users are satisfied, and 
+$D^j = D_i$, although we observe that this result
+does \emph{not} imply that $s_i=s^j$.
+
+We further determine that the set of buyers and sellers participating
+in a single equilibrium is bounded by the potential indirect costs of
+participation. We will denote this individual cost to each user as
+$\varrho$. The indirect cost is the portion of the bid fee
+$\epsilon$ that is dependent on the underlying network and the individual.
+Observing that $\varrho$ indirectly effects user utility,
+and therefore acts to establish a natural budget for each user. We give this
+constraint as, 
+\begin{equation}\label{poolbnd}
+    u \le \varrho,
+\end{equation}
+which may be interpreted as the effort a rational user is willing to expend
+on its message space, and serves to limit the size of the buyer/seller pools.
+
+Finally, it is worth mention that the \emph{analysis} of the auction as
+a game assumes some forms of demand and supply, in order to derive properties.
+The mechanism itself does not require any knowledge of user demand or
+valuation. 
 \subsection{PSP for Data-Exchange}
-
-We intend to show that our auction
-is rational and achieves the desired VCG properties, as does the original
-formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
-realistic, theoretic, and notational templates, we define optimal strategies for
-CMHK users, and demonstrate that the development of a set PSP auction mechanisms
-in a data exchange setting is able achieve a network equilibrium for cellular data.
 
@@
 is also reasonable to expect that a seller may come close to using their
-entire data cap, and only sell the fractional overage. In this case, we
-determine that some buyers must split their bids among multiple sellers.
-
-We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. 
-A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids, is public
-knowledge. Also, we reason that buyers,
-in addition to fufilling their data requirement, have incentive to join
-multiple auctions in order to compare prices.
-Each seller that buyer $i$ adds
-to its pool potentially decreases $i$'s bid quantity in all other auctions, and
-so each buyer $i\in\mcI$ directly impacts other buyers in auctions where buyers intersect.
-Indeed, each auction joined has the potential to decrease the price a buyer
-will pay for its data, in exchange for additional messaging overhead, possible
-fees, and increased competition from other buyers. This aspect of
-a buyers' valuation represents equity, the liabilies from which may be considered work done to find
-sellers, monetary fees, or effort of communication from participation, and so
-is naturally absorbed by the bid fee as characterized in \cite{semret}.
-
+entire data cap, and only sell the fractional overage. In this case, a buyer
+must split its bid among multiple sellers. 
 The buyer strategy bids in auctions with the highest quantities first,
@@
 buyer strategy tends towards equal valuation of all local markets, and therefore
-similar prices. Market equilibrium is achieved when each buyer has equal bids in
+similar prices. If a buyers' demand is not satisfied, they will need to bid in
+markets with smaller data quantities, and so will bid on a larger portion of
+the sellers' bid quantity, increasing their unit price. Market equilibrium is achieved when each buyer has equal bids in
 each auction. Our bidding strategy is inspired by \cite{lazar}, and we also
 hold buyers to consistent bids, where buyers sumbit identical bids to a
-subset of sellers with the highest offers.
+subset of sellers with the highest offers. In the remainder of this section, we
+will make the assumption of truthful bids from the buyer, although this
+analysis is left to Section \ref{analysis}.
 Thus, we determine when rational (utility-maximizing) buyers opt-out of a local auction. 
@@
 {
-\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
+\lemma{(Opt-out buyer strategy)}\label{buyerstrategy}
 Define any auction duration to be $\tau \in [0,\infty)$. 
@@
 $$
-to be the buyer strategy with respect to quantity, and the set,
+to be the buyer strategy with respect to quantity, and similarly for $\varrho$.
+Also define the set,
 % MIN SET
@@
 $$
-where buyer $i$ chooses its seller pool by determining $n$, for $j\in\mcI_i$,
-\begin{equation}\label{buyercoordinate}
-    \min\big\lbrace n \in \mcI \ \vert \ n D^n\ge D_i\big\rbrace. 
-\end{equation} 
+where buyer $i$ chooses its seller pool by determining $n$ as,
+\begin{align}
+\begin{split}\label{buyercoordinate}
+    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
+    %\wedge \sum_{j\in\mcI(n)}&\g_i^j(\varrho) \le \sum_{j\in\mcI(n)} \theta_i^j(\g_i^j(a)) \big\rbrace. 
+    %&\wedge \g_i(\varrho) \le \theta_i(\g_i(a)) \big\rbrace. 
+\end{split}
+\end{align} 
 The buyer strategy produces a minimal subset of sellers $\in \mcI$ 
-able to satisfy buyer $i$'s demand. For 
+able to satisfy buyer $i$'s demand while ensuring that the size of $\mcI^j$
+does not allow the overhead to outweigh the valuation of the data. For 
 fixed $n$ we will denote this subset,
@@
 $\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$, and define $i$'s bid
-vector $e_i$ with respect to its strategy, where
+vector $\g_i$ with respect to its strategy, where
 \begin{equation}\label{opt-eq}
@@
 \end{equation}
+and define bid price $p_i^j = \theta_i'(\g_i^j(a))$.
 Now, (\ref{opt-eq}) holds $\forall \ j\in\mcI$,
-and we have that $\g_i$ defines an optimal strategy for buyer $i$.
+and we have an optimal strategy for buyer $i$.
 }\\
@@
 \sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
-We model the ISP at time $t>0$ as a seller $\kappa$ with bid $s^\kappa =(d^\kappa, p^\kappa)$,
+We model the ISP at time $t>0$ as a seller $\kappa$ with bid $s^\kappa
+=(d^\kappa, p^\kappa)$,
 where $d^\kappa > D^j, \
@@
 $p^\kappa$ represents the overage fee for data set by the ISP, which we note is also the upper bound of the sellers'
-pricing function, and so again (\ref{buyercoordinate}) holds.
-Now, consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
+pricing function.
+Consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
 The allocation rule (\ref{dataallocation}) determines that the data will be
@@
 $d_i^{j(t+1)} < \g_i^{j(t)}(a)$. First, $i$ sets its bid to $s_i^j = 0$, and
-from the new subset $\mcI_i$, submits bids (PARALLEL OR SEQUENTIAL?) until
-$\sum_{j\in\mcI_i} d_i^j \ge D_i$, by (\ref{buyercapmin}).
+from the new subset $\mcI_i$, submits bids until
+$\sum_{j\in\mcI_i} \g(a)_i^j \ge D_i$, by (\ref{bidcap}).
 Now, we consider the case where a new buyer $k$ with bid
@@
 value of $i$'s bid for $j\in\mcI_i$. In this case, by (\ref{buyercoordinate}),
-$i$ will choose $\mcI_i$ so that,
-$$
-    \g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a),
-$$
+$i$ will choose $\mcI_i$ so that, $\g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a)$,
 and so $\mcI_i$ is large enough to balance the additional demand from
-$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal.\\
+$k$. Finally, we consider the case where $\vert\mcI^j\vert = I$, where the
+demand of buyer $i$ exceeds the supply, and the case where $\g_i(\varrho) >
+\theta_i(\g_i(a))$, where the overhead exceeds the current valuation of the
+data. Then, by (\ref{buyerinversedemand}), the valuation of the data increases until either
+the demand is satisfied, the debit from the overhead costs are balanced
+(\ref{poolbnd}), or the upper bound of the sellers' reserve price
+$p^\kappa$ is reached. Thus, as in each case we have that $i$ is able to satisfy thier demand,
+and we determine that the opt-out strategy is optimal.
+$\qed$\\
 \textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
@@
 Finally, we note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
-minimal subset where a coordinated bid is possible.
-\ref{analysis}.
+possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, in fact, by
+restricting the size of the set $\mcI_i$, we would be able to improve the
+computation time of buyer $i$, at the cost of increasing the price.
 
@@
 {
-\proposition{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
+\lemma{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
 Define any auction duration to be $\tau \in [0,\infty)$. 
@@
 Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
-In this case, by (\ref{datacapmin}) the seller must notify $i$ of a
-fractional allocation by changing the bid vector at index $i$.
+In this case, by (\ref{bidcap}) the seller must notify $i$ of a
+partial allocation by changing the bid vector at index $i$.
 With this caveat, and Proposition \ref{buyerstrategy}, we have that the
@@
 $p_*^j$.
-Now, by the point elasticity of (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}) (PROVE POINT ELASTICITY?), we have that, $\forall \ z\ge 0$,
-$$
-    f_{i^*}(z) < f^j(z) \le f_i(z), 
-$$
+Now, by the elasticity of (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}), we have that, $\forall \ z\ge 0$,
+$f_{i^*}(z) < f^j(z) \le f_i(z)$,
 which holds $\forall \ i \in \mcI^j$, and $\forall \ j \in \mcI_i$.
@@
 the fact that since the auction begins at time $t>0$, buyers will
-bid at least once. In a truthful reply, the term $\epsilon/\theta_i'(0)$
-ensures that a new bid price differs from the last bid price by at least
+bid at least once. As will be addressed in further analysis, we assume
+that a new bid price differs from the last bid price by at least
 $\epsilon$. Suppose the auction starts at equilibrium, so $\sum_{i\in\mcI^j}
@@
 Now, in the case where at $t=0$, $\sum_{i\in\mcI^j} \g_i^j(a) > D^j$, by
-(\ref{dataallocation}), the seller notifies (any) buyer $k$ with the lowest bid price of a fractional allocation by changing
-$d_k^j$ thus by Proposition \ref{buyerstrategy}, $k$ decreases its demand until
+(\ref{dataallocation}), the seller notifies (any) buyer $k$ with the lowest bid
+price of a partial allocation by changing
+$d_k^j$ thus by Proposition \ref{buyerstrategy}, $k$ either decreases its
+demand or increases its valuation until
 $\g_i^j(a) \le d_i^j$. Then, as the seller computes the set $\mcI^j$ at each time
@@
 Finally, we note that if for some $i\in\mcI^j \ \exists \ k\in\mcI^j$
-such that $p_{i}^j = p_k^j$, then the seller again notifies the buyers of a fractional
+such that $p_{i}^j = p_k^j$, then the seller again notifies the buyers of a
+partial
 allocation by changing $d_i^j$ and $d_k^j$ by (\ref{dataallocation}).
@@
 equlibirium created by $j$ is independently stable from time $t$ to $(t+1)$. 
+$\qed$
 
@@
 {
-\lemma{(Valuation across local auctions)}\label{userunion}
+\proposition{(Valuation across local auctions)}\label{userunion}
 For any $i,j\in \mcI$, 
@@
 \fi
+Define $\Delta = \Lambda \cup \lambda$.
 Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
-\begin{equation}\label{unioneq}
+\begin{equation}\label{union-eq}
     \displaystyle\sum_{j\in\Lambda} \theta_i^j = \sum_{i\in\lambda} \theta_i^j.
@@
 A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $i$'s bid is such that $p_i^j > p_{i^*}^j$, where
+profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. It follows from
+(\ref{lambda}) and (\ref{llambda}) that $\Delta$ is defined by a seller $j\in\mcI$, where each
+user $k\in\Delta$ has some direct or indirect influence on $j$. 
+We may identify $\Delta$ by its dominant seller, and we let $\Delta^j$ denote $j$'s
+influencing sets. We have that, 
+\begin{equation}\label{iff}
+    i\in\mcI^j \Leftrightarrow p_i^j > p_{i^*}^j,
+\end{equation}
+where
 (\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
@@
 shift, caused by the underlying dynamics.
-Consider $k\in\mcI^j$ where for example, new buyers enter the auction, or increase
-thier bid prices, so that $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
-$s_k^j>0$ at time $t$. 
-By Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
+Consider $k\in\mcI^j$ where, for example, some buyer(s) enter the auction and
+so (\ref{iff}) implies that
+$\sum_{i\in\mcI^j} \g_i^j(a) > D^j$. Now, $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
+$s_k^j>0$ at time $t$ will cause a transition, where, by Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
 Suppose that at time $t$, $j$'s market is at equilibrium, i.e. $\sum_{i\in\mcI^j} = D^j$, and
@@
 that $j$ maintains a local market
-equilibrium from time $t$ to $(t+1)$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
+equilibrium from time $t$ to $(t+1)$.
+Consider a subset $\Delta^j$, by
+Proposition \ref{userunion}, a transition occurs in 2 cases. (1) If $i\in\mcI^j$
+decreases its bid quantity so that $\sum_{i\in\mcI^j}
+\g_i^j(a) < D^j$, and (2) buyer $i^*$, defined in Proposition
+\ref{sellerstrategy} increases its valuation so that $p_{i^*}^j <
+p_*^j$. Clearly, if $i^*$ increases its valuation,
+then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Now, consider a
+seller $k^*\in\mcI_{i^*}$. Since $p_{i^*}^j <
+p_*^j$, we have that $k^*\ni\Lambda\subset \Delta^j\Rightarrow \mcI^{k^*} \ni
+\lambda$. Now, suppose at the end of some time step, $p_*^{k^*} > p_*^j$, and
+consider a buyer $l^*\in\mcI^{k^*}$. Clearly, if $l^*\in\mcI^j$, then $j$'s
+valuation wil increase. Suppose $l^*\ni\mcI^j$, from Proposition \ref{userunion}, if $l^*\in\mcI^k\subset
+\Delta^j$, for some $k\in\mcI_i$, where $i\in\Delta^j$, then either
+$k^*\ni\mcI_i$ or $\exists \ q\in\mcI_i$ such that $p_*^q \ge p_*^{k^*}$. In
+the former case, the valuation of $k\in\mcI_i$ and $j$ will increase.
+In the latter case, $p_*^q \ge p_*^{k^*}$ for some
+$q\in\mcI_i$, and then only the valuation of $j$ will increase. We have that $j$ is
+directly influenced by our choice of seller $k^*$, and observe that
+$i\in\mcI^j$ is free to increase its valuation within $\Delta^j$.
+
+Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
 and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a change in $q$'s valuation from time $t$ to $t+1$ will
+that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand from time $t$ to $t+1$ will
 directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
@@
 some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
-\begin{align*}
-    \int_0^{\g_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ \g_i^j(a)\\
-    &= \int_0^{\g_i^j(a)} f_i(z) \ dz,
-\end{align*}
+\begin{equation}\label{jdemand}
+    \int_0^{\g_i^j(a)} f^j(z) \ dz 
+    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
+\end{equation}
 therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-Furthermore, it follows that,
-\begin{equation}\label{jdemand}
-    \displaystyle\sum_{i\in\mcI^j}\int_0^{\g_i^j(a)} f^j(z) \ dz =
-\sum_{j\in\mcI_i}\int_0^{\g_i^j(a)} f_i(z) \ dz.
-\end{equation}
 
@@
 buyer $i$. 
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
+Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q =
+0$ for $q\in\mcI_i$.
 We have that for any $l\in\mcI^k$ such that $l\ni
@@
 Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
-\begin{align*}
+\begin{align}\label{tieqtk}
     \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
-\end{align*}
+\end{align}
 and
-\begin{align*}
-    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz,
-\end{align*}
-and the result follows by construction, and the continuity of $\theta'$:
-\begin{equation}\label{union-eq}
-    \sum_{i\in\lambda}\int_0^{\g_i^j(a)} f^j(z) \ dz = \sum_{j\in\Lambda}\int_0^{\g_i^j(a)} f_i(z) \ dz.
-\end{equation}
+\begin{align}\label{tkeqtl}
+    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
+\end{align}
+Thus, with a slight abuse of notation for clarity,
+\begin{equation}\label{funion-eq}
+    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
+\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
+\end{equation}
+where the result follows by construction, and the continuity of $\theta'$.
+$\qed$
 
@@
 
-As a result of user behavior, and subsequent strategies, we determine that the data-exchange market is
-semi-partitioned, consisting of unions as in Lemma \ref{userunion}. The unions are inter-dependent in a predictable way. However, as
-each auction may be played on the same or on a different scale in
-valuation, time and quantity, the rate at which market fluctuations occur is
-impossible to predict (NEED HELP!). 
-Arrow's paradox is an impossibility theorem stating that when buyers have three
-or more distinct alternatives (auctions), no deterministic ranking system can
-convert the ranked preferences of users into a market-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives. It follows that the case where
-$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}) does not exist, and is purely a potential,
-theoretical ideal. (DOES IT????)
-
-Nonetheless, we claim that our mechanism is normative, that irrelevant
-alternatives should not matter, it is practical, uses minimal information,
-strategy, and provides the right incentives for the truthful revelation of individual preferences. 
-(EXPAND)
+\subsubsection{Mechanism Realization}
+
+In order to represent the public platform of the secondary market, we model the ISP as
+a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
+in any auctions. At time $t=0$, a seller $k$ entering the market will have
+submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
+seller does not require a priori demand information to enter the market.
+(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
+IMPLICATIONS?)
+We assume that sellers update their bids with the ISP, which is modeled as a
+``buyer" $\kappa$. 
+A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
+knowledge. 
+\iffalse
+A buyer entering the market
+at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
+(SAY BETTER!) is initialized as 
+an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
+probability $\mathcal{P}$,
+$$
+    \mathcal{P}[\epsilon\le X \le \kappa] =
+\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
+ds,
+$$
+where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
+density function of $X$.
+\fi
+%may represent by some homogenous function of degree one (EXPAND?). 
+Thus the auction
+begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
+initializing bid prices.
 
@@
 sellers' data has been allocated. 
-Each time step, $s^j$ is updated it is shared with all
-participating buyers. At this point buyers have the opportunity to bid again,
-where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
-define a single iteration of the auction, wher a seller updates bid vector
-$s^j$, and the buyers' response $s_i$, to comprise a single time step.
-
 % SELLER ALGORITHM
+\begin{center}
 \begin{algorithm}[H]
@@
 \State $t \gets t+1$
-\State Go to 4.
 \EndWhile
@@
 \end{algorithm}
-Finally, we give a simple example of a convergence to a local market equilibrium, where the buyers are assumed to respond with their
+\end{center}
+Each time step, $s^j$ is updated it is shared with all
+participating buyers. At this point buyers have the opportunity to bid again,
+where a buyer that does not bid again is assumed to hold the same bid, since a
+buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
+define a single iteration of the auction, wher a seller updates bid vector
+$s^j$, and the buyers' response $s_i$, to comprise a single time step.
+
+% SELLER ALGORITHM
+\begin{center}
+\begin{algorithm}[H]
+\caption{(Buyer response)}
+\begin{algorithmic}[1]
+\State $p_{i(0)} \gets \epsilon$, $s_{i(0)} \gets (p_i, D_i)$, $D_t \gets D_i$, compute
+$\mcI_{i(0)}$
+\State Update $s_i$ 
+\While{$D_i(t) > 0$}
+\State $D_{i(t+1)}^j \gets \sum_{j\in\mcI_i}\g_i^{j(t)}(a)$
+\If{$D_{i(t+1)}^j < D_t$}
+    \State Compute $\mcI_{i(t)}$
+    \State $p_i \gets \theta_i(\g_i(a))$
+\EndIf
+\State $s_{i(t+1)} \gets (\g_i(a), p_i)$
+\State Update $s_i$
+\State $D_{i(t+1)}^j \gets D_{i(t)}^j$
+\State $t \gets t+1$
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+\end{center}
+Finally, we give a simple example of convergence to a local market equilibrium, where the buyers are assumed to respond with their
 $\epsilon$-best replies.
@@
 Then at $t=1$, we have 
-bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}), (20,p^{(2)}),\\
+bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}),\\ (20,p^{(2)}),
 (14,p^{(2)})]$, and so  $(D^{(2)},p^{(2)}) = (85, 1+\epsilon)$, The buyer response is,
@@
 At $t=2$, $(D^{(1)},p^{(1)}) = (65,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0),\\ (0,0),
+bid vector $s^{(1)}=[(25,p^{(1)}),\\ (40,p^{(1)}), (0,0), (0,0),
 (0,0)]$. $(D^{(2)},p^{(2)}) = (25, 1+\epsilon)$. Then,
@@
 At $t=3$, $(D^{(1)},p^{(1)}) = (50,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0),\\ (0,0),
+bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0), (0,0),
 (0,0)]$. $(D^{(2)},p^{(2)}) = (0, 1+\epsilon)$ and $s^{(2)}=[(25,p^{(1)}),
@@
 At $t=4$ the auction ends.\\
-\textbf{Remark:} In the case where market resources do not satisfy (\ref{buyercapmin}), however as
+\textbf{Remark:} In the case where market resources do not satisfy (\ref{bidcap}), however as
 this constraint is not restricted in time, we reason that in the case of
 insufficient data in the market buyers may wait for additional sellers or
-purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, for (\ref{datacapmin}) in
+purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, in
 the case of insufficient demand, where we may assume that data is held at time
@@
 $z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
+$\qed$
 %Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
@@
 second-price markets. The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, and due to our
-construction, we intend to show that truthful bids are optimal for all users,
+necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
+construction of the user strategy space results in truthful bids that are optimal for all users,
 i.e. bid prices are to the marginal value as determined by market dynamics. 
@@
 this subset so that its overall marginal value is greater than its market price.
-
+We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
+has incentive to change its bid as a result of a market shift or partial
+allocation. We now show the necessary condition of a truthful reply, new bid
+prices must differ from the last by at least $\epsilon$, and prove that the
+resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
+In a truthful reply, the term $\epsilon/\theta_i'(0)$
+ensures that a new bid price differs from the last bid price by at least
+$\epsilon$, thereby ensuring that a buyer does not change its bid without
+correcting the effects of unstable transitions.
+We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
+\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
+there exists a local market equilibrium extending over a subset of connected
+local markets. We have the following Proposition. 
 (DO I NEED TO PROVE CONTINUITY TOO?)
@@
 $t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
-buyer $i\in \mcI^j$, (DO I WANT LAMBDA? SO MANY CASES) let $s_k$ also be fixed $\forall \ k\ni i \in \lambda$. Define,
+buyer $i\in \mcI^j$, (DO I WANT LAMBDA? SO MANY CASES) let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
 \begin{align}
 \begin{split}\label{eta}
-    \eta_i &= \sup\bigg\lbrace x\ge 0 : 
- {\theta_i}'(x) > \displaystyle\sum_{k\in\lambda} P_k^j(x)\bigg\rbrace, 
-\end{split}\\
-\begin{split}\label{chi}
-    \chi_i &= \sup\bigg\lbrace x\ge 0: x \le
-\displaystyle\sum_{k\in\lambda}D_i^j(\theta_i'(x)) \bigg\rbrace,
+    \chi_i &= \bigg\lbrace x\in [0,D_i] : 
+ {\theta_i}'(x) > \max_{j\in\Lambda}P_i^j(x)\bigg\rbrace, 
 \end{split}
 \end{align}
-$z = \min(\eta_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
-\mcI_i$, 
-$$
-    v_i^j = \g_i^{j^*}(z) 
+and $z = \sup(\chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
+\Lambda$, 
+$$
+    v_i^j = \g_i^{j}(z),
 $$
@@
 s_{-i})$.
-%and fix $j$'s reserve price $p^j$ as is defined by (\ref{newprice}). 
-With reserve prices $p^j >0$, there exists a ``truthful" local game embeddeded
-in each local auction, and thus an equilibrium point for the local auction. 
+With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
+in the global market, and thus denoting $\Gamma= \Lambda \cup \lambda$, we have
+an equilibrium point in $\Gamma$. 
 }\\
 \textbf{Proof:}
-
-For the buyer, we show that $t_i$ is an $\epsilon$-best reply. That is,
+We claim that $t_i$ is an $\epsilon$-best reply for buyer $i$. That is,
 $$
@@
 $$
-Let $z = \eta_i^j$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
+As a result of auction initialization, a seller $j$'s valuation defines its
+reserve price to be determined
+by a buyer $i \ni \lambda$, even if this price is zero, we have that $p^j =
+\epsilon \ge 0 \ \forall \ j \in\Lambda$.
+Let $z = \sup(\chi_i^j)$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
 price of auction $j$, and $p_i^*= f_i \circ \g_i^j(a)$ denote the (coordinated) bid price of buyer $i$. 
@@
 and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
-max of the reserve prices $p_i^j,\ \forall \ j\in\mcI_i$, therefore
+max of the reserve prices $p_*^j,\ \forall \ j\in\mcI_i$, therefore
 (\ref{eta}) is such that,
 $$
-    \theta_i'(z) > \bar{P}_i^j(z),
-$$ 
-which implies, as (MORE) $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
+    \theta_i'(z) > \max_{j\in\Lambda}P_i^j(v_i^j),
+$$ 
+which implies, as $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
 we have $\forall \ j \in \mcI_i$, 
@@
 \begin{align*}
-    a_i^j(t_i) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\mcI_i} a_i^j(t_i) &= z.
+    a_i^j(t_i;s_{-i}) &= v_i^j \\
+    \Rightarrow \displaystyle\sum_{j\in\Lambda} a_i^j(t_i;s_{-i}) &= z.
 \end{align*}
-Therefore,
+Therefore, $\forall \ j\in\Lambda$ and $\forall \ i \in \lambda$ such that
+(\ref{tieqtk}) and (\ref{tkeqtl}) hold,
 \begin{align*}
-    \displaystyle\sum_{j\in\mcI_i}&\int_0^{v_i^j} P_i^j(x) \ dx =  \int_0^{z}
-    \bar{P}_i^j(x) \ dx \\
-    &= \sum_{j\in\mcI_i}\int_0^{e_i^j(z)} P_i^j(x) \ dx.
+    \int_0^{v_i^j} \bar{P}_i(x) \ dx 
+    = \sum_{j\in\Lambda}\int_0^{\g_i^j(z)} P_i^j(x) \ dx.
 \end{align*}
+It follows that,
+$$
+    u_i(t_i;s_{-i}) = \int_0^{z} \theta_i'(x) \ dx -  \g_i \ \circ \int_0^{z} \bar{P}_i(x) \ dx.
+$$
 Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
-s_{-i}) + \epsilon$. The buyer coordinated strategy, from Propositions
+s_{-i}) + \epsilon$. Propositions
 \ref{coordinationlemma} and
-\ref{buyerstrategy}, gives $s_{i^*} = (e_i\circ a_i(s), \ \theta_i'(z)) =
-(z_i, c_i)$, where
-for each $j\in \mcI$, $a_i^j(s_{i^*}; s_{-i}) = z_i^j$,
-then clearly $u_i(s_{i*}, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
-u_i(s_i;s_{-i}) > \epsilon$. Denoting $z_i^j$ (fixed) as $\zeta$, 
-$$
-    \int_z^{\zeta} {\theta_i}'(x) \ dx- \int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
+\ref{buyerstrategy}, define the coordinated bid, $\nu_i=(\zeta_i, p_i)$,
+% = (\g_i\circ a_i(s), \ \theta_i'(z)) = (z_i, c_i),$
+using (\ref{tieqtk}) and (\ref{tkeqtl}),
+for each $j\in \Lambda$, $\g_i^j(a_i^j(\nu_i; s_{-i})) = \zeta_i^j$,
+then clearly $u_i(\nu_i, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
+u_i(s_i;s_{-i}) > \epsilon$. Denoting $\zeta_i^j$ (fixed) as $\zeta$, 
+$$
+    \int_z^{\zeta} {\theta_i}'(x) \ dx-\int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
 $$
@@
 $\epsilon$, and as such, buyer $i$ will remain in
-any local auction with reserve price determined by (\ref{???}). We therefore
+any local auction with reserve price determined by (\ref{newprice}). We therefore
 verify that,
@@
 exist.
-
-We consider the other term in the minimization; let $z=\chi_i$. We have that
-For any coordinated bid $s_i$ such that $u_i(z_i, c_i) > u_i(t_i)+
-\epsilon$, then $\zeta > z
-\Rightarrow c_i(s_{i}) > b_i$, and so is infeasible. 
-Finally, by Lemma \ref{userunion}, for a single buyer-seller interaction, we
-have that $f_i = f^j \Rightarrow \theta_i \circ e_i^j = \theta^j \circ e_i^j$.
-Therefore $\theta_i' = {\theta^j}'$. We have by Proposision
-\ref{sellerstrategy} and (\ref{???}eqn 30), that $\theta^j = \max_{i\in\mcI^j}
-\theta_i$, and so for any $i\in\mcI^j, \theta^j(z) \ge \theta_i(z)$, and so $j$
-cannot set a higher reserve price, and also cannot sell more data than the buyers'
-bids, so we have that $j$'s bid is both truthful and optimal.
-\\----------------------REF-------------------------\\
-% NEW MARKET PRICE
-\begin{align}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
-\end{split}
-\end{align}
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
-    D^j \big] : \\
-    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
-\end{split}
-\end{align}
-% DATA ALLOCATION RULE
-\begin{align}
-    a_i^j(s) \\
-    &= \min\bigg\lbrace e_i^j(D_i),
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
-\end{align}
-% DATA COST
-\begin{align}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-p^j \bigg(ai^j(0; s_{-i}^j)
-    -a_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
-% BUYER DEMAND 
-\begin{equation}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
-\end{equation}
-% BUYER REVENUE 
-\begin{equation}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-% SELLER REVENUE 
-\begin{equation}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-\begin{equation}
-    \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
-\end{equation}
-\begin{equation}
-    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-\begin{equation}
-    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-\begin{equation}
-    d_i^j \ge e_i^j(a)
-\end{equation}
-\begin{equation}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
-\end{equation}
-\begin{equation}
-    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
-\end{equation}
-\begin{equation}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
-\end{equation}
-\\----------------------------------------------------\\
-This forms a ``truthful" local game embeddeded within $j$'s auction with strategy space
-restricted to $\epsilon$-best replies from buyers $\in \mcI^j$. Therefore we have that a
-fixed point in the ``truthful" local game is a fixed point for the auction. We
-further argue that as the set $\mcI^j$ is
-computed at each bid iteration, that our result holds for time $(t+1) \in \tau$.
+Finally, as we may consider $\Delta \subset \mcI$ to be a
+multi-auction game, our user strategies form a ``truthful" local game 
+with strategy space restricted to $\epsilon$-best replies from buyers $\in
+\lambda$. Therefore we have that a fixed point in the ``truthful" game is a fixed point for the auction. 
+$\qed$\\
+For completeness, we address the sellers bids, and include the following corollary to support our result.
+{
+\corollary{Seller cooperation.}
+We claim that $s^j$ is both truthful and optimal.
+}\\
+\textbf{Proof:}
+For a single buyer-seller interaction, (\ref{jtoi}) gives that $\theta_i =
+\theta^j \Rightarrow \theta_i' = {\theta^j}'$. Thus, we have by symmetry, as the buyers' bids are
+truthful, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
+and cannot sell more data than the buyers' aggragated bid quantities.
+The result follows by Lemma \ref{userunion} and Lemma \ref{buyercoordinate}.\\
+
+The data-sharing market consists of a inter-dependent sets of these
+multi-auction games around fixed points.  Clearly, the union of all possible
+sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. Consider two subsets, $\Delta^j$
+and $\Delta^k$, at equilibrium, and a shared
+buyer $i\in (\lambda^j \cup \lambda^k)$, where
+$\lambda^j\subset\Delta^j$, and  $\lambda^k\subset \Delta^k$.  By Lemma
+\ref{userunion}, a transition is induced in $\Delta^k$ by $\Delta^j$ if and only if
+$\exists \ l \in \Lambda^j$ such that $p_*^{l} > p_*^{q}$, for some
+$q\in\Lambda^k$. We claim that the shared buyers
+between the different subsets $\Delta$ form a heirarchical structure, and that
+there can only be a single primary fixed point, and this seller determines
+the equilibrium price in the global market. Now, consider the set of sellers across all $\Delta$,
+$\bigcup_{j\in\mcI}\Lambda^j$.
+
+%Consider
+%again $q\in\mcI_i$, and the subset $\Delta^q$, where $p_*^q \ge p_*^j$, and
+%a buyer $l\in\lambda\subset\Delta^q$ chosen in the same way as $l^*$.
 
@@
 from which no player has a unilateral incentive to deviate (Johari, 2004)
-
-As a result of auction initialization, a seller $j$'s valuation defines its
-reserve price to be determined
-by a buyer $i \ni \mcI^j$, even if this price is zero, we have that $p^j = \epsilon \ge 0$.
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a local market equilibrium extending over a subset of connected
-local markets. We have the following Proposition.
+(EXPAND)
+We first show the existence of a \emph{static} Nash equilibrium, where buyers have fixed reserve
+prices.
 
 {
-\lemma{(Static Data Nash Equilibrium)} 
+\lemma{(Static Nash Equilibrium)} 
 }
 
+As a result of user behavior, and subsequent strategies, we determine that the
+global data-exchange market behaves in a predictable way. However, as
+each auction may be played on the same or on a different scale in
+valuation, time and quantity, the rate at which market fluctuations occur is
+impossible to predict (NEED HELP!). 
+Arrow's paradox is an impossibility theorem stating that when buyers have three
+or more distinct alternatives (auctions), no deterministic ranking system can
+convert the ranked preferences of users into a market-wide (complete
+and transitive) ranking while also meeting a specified set of criteria:
+unrestricted domain, non-dictatorship, Pareto efficiency and independence of
+irrelevant alternatives. It follows that the case where
+$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
+is disjoint.
+
+Nonetheless, we claim that our mechanism is normative, that irrelevant
+alternatives should not matter, it is practical, uses minimal information,
+strategy, and provides the right incentives for the truthful revelation of individual preferences. 
+(EXPAND)
 % DATA NASH EQ
 {
-\theorem{(Data Nash Equilibrium)}
+\theorem{(Nash Equilibrium)}
 Using the rules of the data auction mechanism, the CMHK
@@
 \textbf{Proof:}
-2. using the min price of sellers in the auction i.e. ${\theta_i}'(d_{i^*}^j) =
-p^j$ is OK, \\
-3. that bids are still feasible AND optimal \\
-4. the algorithm achieves global economic equilibrium)\\
-\textbf{NEED TO COVER:}\\
-1. Change in buyer valuation \\
-2. New buyers\\
-3. Not enough buyers \\
-4. Not enough data\\
-\textbf{TRY:}\\
-Sellers only act when the resources obtained by the buyers influence their
-respective reserve prices, which agrees with the seller stragety of attempting
-to sell their data in the first iteration. Therefore we claim there exists a
-market stability and therefore, the existence of a Nash equilibrium. As the
-valuation of the sellers is derived by the demand of the buyers, who are
-bidding equivalent bids over a minimum subset of buyers, we claim that the seller
-strategy, along with the seller constraint (\ref{??}) results in a global
-market equilibrium.
-We have shown that the local
-equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-Now, suppose that buyer $i^*$ computes its best response $s_i^j = (v_i^j, w_i^j)$
-Finally, suppose that
-a buyer $k$ enters the market such that for some buyer $l\in\mcI^j$,
-$$
-    \displaystyle\sum_{i\in\mcI^j} p_i^je_i^j(a) + p_k^je_k^j(a) \ge
-\sum_{i\in\mcI^j} p_i^je_i^j(a) - p_l^je_l^j(a),
-$$
-that is,
-
-NOTES: (today)\\
-2. finish seller incentive compat\\
-3. work on progression\\
-4. check reserve price = monopoly price
 
@@
 
-\end{multicols}
+%\end{multicols}
 

### 2018-04-27 paper_wc.tex
Last corollary!

@@
 i.e. $p_i^j = {\theta_i^j}'$.
+
+\subsection{Motivation for Privacy/Security}(NEW SECTION)
+
+A property of PSP is that the user valuations are held private.
+
+1. The seller doesn't update with the ISP, and so does not know the market price
+ in the data-exchange market.\\
+2. The auction is distributed, so there is no collusion between sellers and
+ISP.\\
+3. The mechanism is self-contained, and only requires participation. (THINK!)
+4. Better economy, as few users will get data plans with a lot of data, make
+money, allowing others to have cheaper data plans and not pay a lot for
+texting, phone calls (Buzzfeed). Free market capitalism! \\
+(CONCERN HERE ABOUT THROTTLING)
 
@@
 auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. We have the following Lemma,
+local auctions on each other. Defining a single iteration of the auction, where a seller updates bid vector
+$s^j$, and the buyers' response $s_i$, to comprise a single time step, and we have the following Lemma,
 % USER UNION
@@
 A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. It follows from
-(\ref{lambda}) and (\ref{llambda}) that $\Delta$ is defined by a seller $j\in\mcI$, where each
-user $k\in\Delta$ has some direct or indirect influence on $j$. 
-We may identify $\Delta$ by its dominant seller, and we let $\Delta^j$ denote $j$'s
-influencing sets. We have that, 
+profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. Using Proposition \ref{sellerstrategy} and (\ref{jtoi}), we have that, 
 \begin{equation}\label{iff}
@@
 p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
-shift, caused by the underlying dynamics.
-Consider $k\in\mcI^j$ where, for example, some buyer(s) enter the auction and
+shift caused by the underlying dynamics.
+Consider $k\in\mcI^j$ at time $t$ where, for example, some buyer(s) enter the auction, and
 so (\ref{iff}) implies that
 $\sum_{i\in\mcI^j} \g_i^j(a) > D^j$. Now, $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
-$s_k^j>0$ at time $t$ will cause a transition, where, by Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
-Suppose that at time $t$, $j$'s market is at equilibrium, i.e. $\sum_{i\in\mcI^j} = D^j$, and
-no buyer rebids. Unless $k$ adds a seller with a higher reserve
+$s_k^j>0$ will cause $k$ to initiate a shift. By Proposition \ref{buyerstrategy}, $k$ will set $s_k^j=0$, and begin to add sellers to its pool.
+Suppose that at time $t$, $j$'s market is at equilibrium, i.e.
+$\sum_{i\in\mcI^j} \g_i^j(a) = D^j$, and fixing all other bids, so 
+no buyer $i\in\mcI^j$ rebids. Unless $k$ adds a seller with a higher reserve
 price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
-auction will end. Otherwise, at some time $t\in[t+1,\tau]$, we must have that $\g_k^j <
-D^j$, and $k$ opts-out. Finally, overlooking market transitions and messaging
+auction ends. Otherwise, at some time $t\in[t+1,\tau]$, we must have that
+$\g_k^j \le D^j$, and $k$ rejoins auction $j$ or opts-out. Finally, overlooking market shifts and messaging
 overhead, we have that,
@@
 The reserve price (\ref{newprice}) of seller $j$ is determined at each
-transition, and is
+shift, and is
 the lowest price that $j$ will accept to perform any allocation.
@@
 \end{equation}
-by Proposition \ref{sellerstrategy}. 
-Also, in the absence of transitions, caused by multi-auction market dynamics, we have 
-that $j$ maintains a local market
-equilibrium from time $t$ to $(t+1)$.
-Consider a subset $\Delta^j$, by
-Proposition \ref{userunion}, a transition occurs in 2 cases. (1) If $i\in\mcI^j$
+from (\ref{newprice}). Now, by Proposition \ref{sellerstrategy}, in the absence
+of external influences caused by multi-auction market dynamics, we have 
+that $j$ maintains a local market equilibrium from time $t$ to $(t+1)$.
+From (\ref{lambda}) and (\ref{llambda}), $\Delta$ is defined by a seller $j\in\mcI$, where each
+user $k\in\Delta$ has some direct or indirect influence on $j$. 
+We may identify $\Delta$ by its dominant seller, and we denote $\Delta^j = \Lambda^j
+\cup \lambda^j$.
+
+Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
+some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
+p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
+Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
+that $p_l^* < p_*^j$, and
+the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so, $p_*^k \le
+p_l^* < p_*^j \le p_i^*$, %<---- MAKE AN EQUATION?
+for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
+p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
+$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
+which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
+\ni\mcI^q \Rightarrow p_*^q >
+p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
+buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
+(\ref{iff}).
+Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
+0$, for some $g\in\mcI_i$.
+We have that for any $l\in\mcI^k$ such that $l\ni
+\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
+where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
+p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
+a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
+such that $p_*^g \ge p_*^j$. Thus, we
+determine a direct influence as $l\in\mcI^k
+\cap \Lambda^j$, such that $p_l^* > p_i^*$,
+and an indirect influence as, for any $l\in\mcI^k
+\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
+
+Now, consider the subset $\Lambda^j$, by
+Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
 decreases its bid quantity so that $\sum_{i\in\mcI^j}
-\g_i^j(a) < D^j$, and (2) buyer $i^*$, defined in Proposition
-\ref{sellerstrategy} increases its valuation so that $p_{i^*}^j <
-p_*^j$. Clearly, if $i^*$ increases its valuation,
-then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Now, consider a
-seller $k^*\in\mcI_{i^*}$. Since $p_{i^*}^j <
-p_*^j$, we have that $k^*\ni\Lambda\subset \Delta^j\Rightarrow \mcI^{k^*} \ni
-\lambda$. Now, suppose at the end of some time step, $p_*^{k^*} > p_*^j$, and
-consider a buyer $l^*\in\mcI^{k^*}$. Clearly, if $l^*\in\mcI^j$, then $j$'s
-valuation wil increase. Suppose $l^*\ni\mcI^j$, from Proposition \ref{userunion}, if $l^*\in\mcI^k\subset
-\Delta^j$, for some $k\in\mcI_i$, where $i\in\Delta^j$, then either
-$k^*\ni\mcI_i$ or $\exists \ q\in\mcI_i$ such that $p_*^q \ge p_*^{k^*}$. In
-the former case, the valuation of $k\in\mcI_i$ and $j$ will increase.
-In the latter case, $p_*^q \ge p_*^{k^*}$ for some
-$q\in\mcI_i$, and then only the valuation of $j$ will increase. We have that $j$ is
-directly influenced by our choice of seller $k^*$, and observe that
-$i\in\mcI^j$ is free to increase its valuation within $\Delta^j$.
-
-Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
+\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
+\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
+p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
 and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand from time $t$ to $t+1$ will
-directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
-buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
-thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
-recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
+that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
+directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
+buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
+recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
+will attempt to regain equilibrium.
+Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
+then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
+seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
+p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
+\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
+case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
+where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).
+
 In each case we
@@
 therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-
-Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$, and
-the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so,
-$$
-    p_*^k \le p_l^* < p_*^j \le p_i^*,
-$$
-for any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
-p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
-which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
-\ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$. 
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q =
-0$ for $q\in\mcI_i$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
-for $q\in\mcI_l$ or $\theta_l^q = 0$ for some $q\in\mcI_i$. Thus, any bid ouside of
+Thus, any bid ouside of
 our construction
 has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$, and therefore cannot cause transitions to occur except through a
+$\in\Lambda$, and therefore cannot cause shifts to occur except through a
 shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
 (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
-bids in any auction $\mcI^q$, where $q\in \mcI_l \setminus \Lambda$,
+bids in any auction $q \ni \Lambda^j$,
 we have, $\forall \ k\in\mcI_i$,
@@
 seller does not require a priori demand information to enter the market.
+Also, a new sellers' bid, $(D^j, \epsilon)$, is public knowledge. 
+\iffalse
 (DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
@@
 ``buyer" $\kappa$. 
-A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
-knowledge. 
-\iffalse
+\fi
 A buyer entering the market
 at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER!) is initialized as 
+(SAY BETTER! ALSO DO I REALLY NEED THE I.I.D?) is initialized as 
 an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
@@
 density function of $X$.
-\fi
 %may represent by some homogenous function of degree one (EXPAND?). 
@@
 where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
-define a single iteration of the auction, wher a seller updates bid vector
-$s^j$, and the buyers' response $s_i$, to comprise a single time step.
+buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$.
 
@@
 $\epsilon$, thereby ensuring that a buyer does not change its bid without
-correcting the effects of unstable transitions.
+correcting the effects of unstable shifts.
 We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
@@
 {
-\proposition{(Incentive compatibility across local auctions)}
+\proposition{(Incentive compatibility across local auctions)}\label{incentive}
 Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
@@
 {
-\corollary{Seller cooperation.}
+\corollary{(Seller cooperation)}
 We claim that $s^j$ is both truthful and optimal.
@@
 multi-auction games around fixed points.  Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. Consider two subsets, $\Delta^j$
-and $\Delta^k$, at equilibrium, and a shared
-buyer $i\in (\lambda^j \cup \lambda^k)$, where
-$\lambda^j\subset\Delta^j$, and  $\lambda^k\subset \Delta^k$.  By Lemma
-\ref{userunion}, a transition is induced in $\Delta^k$ by $\Delta^j$ if and only if
-$\exists \ l \in \Lambda^j$ such that $p_*^{l} > p_*^{q}$, for some
-$q\in\Lambda^k$. We claim that the shared buyers
+sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
 between the different subsets $\Delta$ form a heirarchical structure, and that
 there can only be a single primary fixed point, and this seller determines
-the equilibrium price in the global market. Now, consider the set of sellers across all $\Delta$,
-$\bigcup_{j\in\mcI}\Lambda^j$.
-
-%Consider
-%again $q\in\mcI_i$, and the subset $\Delta^q$, where $p_*^q \ge p_*^j$, and
-%a buyer $l\in\lambda\subset\Delta^q$ chosen in the same way as $l^*$.
-
+the equilibrium price in the global market. (EXPAND) We have the following
+Corollary, 
+{
+\corollary{(Primary fixed point)}
+Let the set of shared buyers be denoted as,
+$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
+sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
+$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
+\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then
+$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
+k\ne j\in\overline{\Lambda}$. 
+}\\
+\textbf{Proof:}
+We assume a finite number of users, with continuous valuation functions bounded both
+above and below. From the assumption that $\overline{\Lambda}$ is not a
+partition, we have that,
+$$
+    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
+$$
+is the primary seller $j$, and we have the market price $p_*^j$ from,
+$$
+    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
+\lambda^k,
+$$
+and the result follows from Lemma \ref{uservaluation}, Proposition
+\ref{userunion} and Proposition \ref{incentive}.
+$\qed$\\
+(USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
+
+\subsubsection{Nash Equilibrium}
 A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
@@
 \lemma{(Static Nash Equilibrium)} 
+Let the duration of an auction $j$ be $\tau \in (0,\infty)$, and fix the
+sellers reserve prices at $t=0, \ \forall \ j\in\mcI$.
+Using the rules of the data auction mechanism, the multi-auction game converges to a $\epsilon$-Nash equilibrium. In the network auction
+game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
+equilibrium. 
 }
@@
 {
-\theorem{(Nash Equilibrium)}
+\theorem{(Dynamic Nash Equilibrium)}
 Using the rules of the data auction mechanism, the CMHK

### 2018-05-03 paper_wc.tex
Started set theoretical analysis.

@@
 The market price function (MPF) for a buyer-seller pair is,
-% NEW MARKET PRICE
+% MARKET PRICE
 \begin{align}\label{dataprice}
@@
 $j$ at unit price $y$ given $s_{-i}^j$ is,
-% NEW INVERSE DEMAND
+% INVERSE DEMAND
 \begin{align}\label{datapriceinverse}
@@
 revenue \cite{lazar}.
+{
+\definition{(Nash Equilibrium)}
+A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
+profile $s$,
+from which no player has a unilateral incentive to deviate (Johari, 2004)
+(EXPAND?)
+}\\
+
 The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
@@
 particpating in CMHK's secondary data-sharing market.
-Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
+Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
 data from other users. We again define the bidding profile for any user to be 
@@
 , s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
-cellular network. We assume that users are selfish, and therefore
-rational. 
-Users prefer to participate in the CMHK secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
+Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
+$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} S_i^j(s_{-i})$ the
+set of opponent profiles. We assume that the users are connected.
+A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
+additional data for a cost less than the overage fee set by the ISP. We assume
+that users are selfish, and therefore rational. 
 Thus we assume that all users submit bids in order to maximize their
@@
 \end{equation}
-where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
-the buyers' valuation of allocation $a$ across local markets (and thus multiple
-sellers), and $\theta_i(\g_i(a)) - \g_i(\varrho)$ represents the buyers'
-corresponding debit.  
+where the composition of the elastic valuation function $\theta_i$ with $\g_i$
+distributes a buyers' valuation of allocation $a$ across local markets (and thus
+multiple sellers).
 In this way we extend the PSP rules described
@@
 $y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
-We determine that the market supply function is equivalent to buyer demand, and 
+We determine that the market supply function corresponds to an extreme of
+possible buyer demand, and 
 acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
@@
 Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
+(THE ABOVE IS GOOD, BUT DOESN'T FIT MY CONSTRUCTION, CHANGE TO BELOW?)
+The market price function (MPF) for a buyer in the CMHK market
+is determined per (\ref{buyerinversedemand}), and is defined as,
+% NEW MARKET PRICE
+\begin{align}\label{dataprice}
+\begin{split}
+    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
+s_{-i}^j) \\
+    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
+    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ j\in\mcI \bigg\rbrace \bigg),\\
+\end{split}
+\end{align}
+and is interpreted as the price that buyer $i$ bids in
+order to obtain
+data amount $z$ given opponent profile $s_{-i}$.
+The sellers pricing function is according to (\ref{sellerinversedemand}), 
+\begin{align}\label{dataprice}
+\begin{split}
+    &\bar{P}^j(z, s_{-i}) =\displaystyle\sum_{i\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
+s_{-i}^j) \\
+    &= \sum_{j\in\mcI}\bigg(\sup\bigg\lbrace y\ge 0 : 
+    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ i\in\mcI \bigg\rbrace \bigg).\\
+\end{split}
+\end{align}
+We note that
+the total price cannot be an aggragation of the
+\emph{individual} bid prices as it is possible that the reserve prices
+of the individual sellers may vary, which contradicts
+(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}).\\
+\textbf{Remark:} We further note that except at points of discontinuity, from
+Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
 %To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
@@
 \end{align}
+It follows from the upper-semicontinuity of $D_i^j$ that for $s_{-i}^j$ fixed, $\forall \ y,z \ge 0$,
+\begin{equation}\label{dtop}
+    \g_i^j(z) \le \g_i^j \circ D_i^j(y,s_{-i}^j) \Leftrightarrow y \ge \g_i^j
+\circ P_i^j(z,s_{-i}^j).
+\end{equation}
 % DATA ALLOCATION RULE
@@
 $$
-to be the buyer strategy with respect to quantity, and similarly for $\varrho$.
+to be the buyer strategy with respect to quantity.
 Also define the set,
@@
 the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so, $p_*^k \le
-p_l^* < p_*^j \le p_i^*$, %<---- MAKE AN EQUATION?
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
+have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
+where,
+\begin{equation}\label{ordering}
+    p_*^k \le p_l^* < p_*^j \le p_i^*,
+\end{equation} 
 for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
@@
 \ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
-p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
+p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the
+lowest bid price, the ``lowest clearing player",
 and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
@@
 \end{center}
-Finally, we give a simple example of convergence to a local market equilibrium, where the buyers are assumed to respond with their
+Finally, we give a simple example of convergence to a local market equilibrium,
+where the buyers are assumed to respond with their truthful,
 $\epsilon$-best replies.
@@
 allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
-(z_i,y_i)$, where $\forall \ j \in \mcI_i$,
+\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
 \begin{align*}
-    z_i^j &= \g_i^{j^*}(a), \\
+    z_i^j &= \g_i^{j}(a), \\
     y_i^j &= \theta_i'(z_i^j).
@@
 a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$,
-so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$. 
+$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$.
 Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    \g_i^k(a) \le z_i^j = \g_i^{j^*}(a) \le \g_i^{j}(a),
-$$
+$k\ni\mcI_i$, $\g_i^k(a) \le z_i^j = \g_i^{j}(a)$,
 and so, using (\ref{union-eq}), 
 \begin{equation}\label{minimaleq}
-    \g_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
+    \g_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
 \end{equation}
@@
 $$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j^*})\ge D_i^j(p_i^{k}).
+    D_i^j(y_i^j) \ge D_i^j(p_i^{j})\ge D_i^j(p_i^{k}).
 $$
@@
 Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$\g_k^{j^*}(a) \ge \g_i^{j^*}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
+$\g_k^{j}(a) \ge \g_i^{j}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
 partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
 As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j*}(a)
-\ge \g_k^{j^*}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
+set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j}(a)
+\ge \g_k^{j}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
 We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
 $$
-    {\theta_i}'(e_i^{k}(a)) \ge {\theta_i}'(e_i^{j^*}(a)) \ge y_i^j.
+    {\theta_i}'(\g_i^{k}(a)) \ge {\theta_i}'(\g_i^{j}(a)) \ge y_i^j.
 $$
@@
 d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= e_i^{j^*}(a)
+    &= z_i^{j}= \g_i^{j}(a)
 \end{align*}
@@
 \forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a local market equilibrium extending over a subset of connected
-local markets. We have the following Proposition. 
-(DO I NEED TO PROVE CONTINUITY TOO?)
+there exists a market equilibrium extending over a subset of connected
+local markets. 
+For a buyer $i$, define have the set of possible $\epsilon$-best replies,
+\begin{equation}\label{e-bid}
+    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
+u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
+\end{equation}
+and the set of \emph{truthful} bids, 
+\begin{equation}\label{t-bid}
+    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
+\wedge p_i = \theta_i'(z)\rbrace,
+\end{equation}
+where $\wedge$ denotes the logical ``and" operator. The ``strategic" set $T_i$
+is restricted by Proposition \ref{buyerstrategy}. In the remainder of our
+analysis we limit the strategy space to our construction, and so we have the
+bid for buyer $i$, $S_i=\Pi_{j\in\mcI_i} S_i^j$, and the opponent bid, $S_{-i}
+=\Pi_{j\in\mcI_i} S_i^j(s_{-i})$ 
+We have the following Proposition,
 
@@
 $t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
-buyer $i\in \mcI^j$, (DO I WANT LAMBDA? SO MANY CASES) let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
+buyer $i\in \mcI^j$, let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
 \begin{align}
@@
 Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
-(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
+(v_i,w_i) \in T_i\cap S_i^\epsilon(s_{-i})$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
 s_{-i})$.
 With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
-in the global market, and thus denoting $\Gamma= \Lambda \cup \lambda$, we have
-an equilibrium point in $\Gamma$. 
+$\in\Delta$. Therefore, a fixed point $\in \Delta$ is a fixed point in
+the multi-auction game. 
 }\\
@@
 $\qed$\\
-For completeness, we address the sellers bids, and include the following corollary to support our result.
+
+We have proven that buyers will submit bids according to their marginal
+valuations. Now, in the interest of completeness (BAD SENTENCE), we extend our result to be
+all-inclusive. As a result of the PSP multi-auction in the constructed strategy
+space, we find a well-defined mathematical structure manifests as a result of bid
+correspondence. The game-theoritical basis of our argument is complemented by,
+and benefits by (NEED? extension to) an abstract-theoretical analysis.
+Motivated by the symmetric nature of supply and demand we provide further rigor
+by mathematical construction. Thus, we begin with the definition of
+correspondence,
 {
-\corollary{(Seller cooperation)}
-We claim that $s^j$ is both truthful and optimal.
+\definition{(Correspondence)}
+An ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
+$Y$, i.e. any subset of the Cartesian product $X\times Y$.
+}
+Now, in an economic model, the mapping $(\mcI,\mcI,R)$ is a map from the
+elements of $\mcI$ to the power set $\mathcal{P}(\mcI)$. The most obvious
+example of a correspondence in our model is the buyers' best response
+$B_i^\epsilon$, where, for the multi-auction,
+$\Pi_{j\in\mcI} S_i^j$ and $\Pi_{j\in\mcI} S_{-i}^j$ are power sets under the
+identity relation, e.g $(S_i, S_i,\Pi\in\mcI S_i)$. The auction
+progresses by repeated mappings, where the full strategy space is the
+correspondence
+$(\Pi_{j\in\mcI}S_i,\Pi_{j\in\mcI}S_{-i},\Pi_{j\in\mcI}S_i^\epsilon)$ and
+finally, the best response is given as a reaction correspondence $B_i^\epsilon$
+defined by the mixed-strategy game.
+
+Thus, we address the sellers bids, and include the following corollary to support our result.
+{
+\corollary{Data-bid correspondence (seller cooperation)}
+For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is (NEED THIS? consistent with) a truthful
+$\epsilon$-best reply.
 }\\
 \textbf{Proof:}
-For a single buyer-seller interaction, (\ref{jtoi}) gives that $\theta_i =
-\theta^j \Rightarrow \theta_i' = {\theta^j}'$. Thus, we have by symmetry, as the buyers' bids are
-truthful, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
-and cannot sell more data than the buyers' aggragated bid quantities.
-The result follows by Lemma \ref{userunion} and Lemma \ref{buyercoordinate}.\\
-
-The data-sharing market consists of a inter-dependent sets of these
-multi-auction games around fixed points.  Clearly, the union of all possible
+We claim there exists an equivalence relation $R$ that naturally evolves in the
+strategy space. For a seller $j$, let $y=\theta_i'(\g_i^(a))$ for a buyer $i$. We have that, for any allocation $a$, 
+\begin{equation}\label{eqrel}
+        R \equiv (\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))) = (\g_i^j(a),y),
+\end{equation}
+defines equivalence $i \thicksim j$, where we use the definition of set
+equality based on first-order logic with equality. By definition, 
+$\forall \ i, \ \forall \ j, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
+\Rightarrow i \thicksim j$. This is the converse of (\ref{jtoi}). Formally, the
+axiom states that a set is \emph{uniquely} determined by its members.
+$R$ is defined by the bid price and
+reserve price of buyer $i$ and seller $j$, respectively. We
+have, for any $z\ge 0$,
+\begin{equation}\label{eqrel}
+        R \equiv i\thicksim j \equiv \theta_i'(z) - {\theta^j}'(z)\ge\epsilon
+\end{equation}
+defines equivalence $i \thicksim j$. Equivalence class $[i]$ is by definition
+the market supply at the buyers' valuation $\theta_i'$. Clearly, $k\thicksim k,
+\ \forall \ k\in\Delta$, and $\epsilon \ge \theta_i'(z) - {\theta^j}'(z)$
+%, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
+%and cannot sell more data than the buyers' aggragated bid quantities.
+The result follows by symmetry, and as the buyers' bids are
+truthful, and by (\ref{newprice}),Lemma \ref{userunion} and Lemma
+\ref{buyercoordinate}.$\qed$\\
+
+The ease by which the game is constructed is a consequence of the the cartesian
+product on a 2-dimensional message space.
+
+The reserve price $\epsilon$ acts as a placeholder for a seller submitting an
+auction to the ISP. As was proven in \cite{lazar}, the positive reserve price allows us to
+restrict our analysis to continuous, truthful bids. The strategy space of
+truthful bids is a collection of truthful bid, or ``strategy", vectors.
+From the original proof by \cite{lazar}, we observe that the collection of
+unconstrained truthful bids, $T_i = \Pi_{j\in\mcI} T_i^j$, may not be a subset
+of the collection of $\epsilon$-best replies, $\Pi_{\in\mcI} S_i^\epsilon$.         
+%An essential component of determining the existence of a Nash equilibrium is 
+For this work, it suffices to show the continuity of the set of truthful
+$\epsilon$-best replys, which we will denote $B_i^\epsilon = T_i\cap S_i^\epsilon$, in opponent bid profiles $S_{-i}$.
+
+{
+\lemma{(Continuity of $\epsilon$-best reply on $\Delta$)}
+Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
+$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
+}\\
+\textbf{Proof:}
+Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
+$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
+the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
+We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
+$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
+we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ \overline{P}])$
+is a product of closed subsets of compact sets. Then, as a closed
+subset of a compact set is compact, and by Tychonoff's theorem, $\g_i \circ
+B_i^\epsilon$
+is compact subset of $B_i^\epsilon$. Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
+definition of $\Delta$ and the product, 
+\begin{align*}
+    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
+    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
+[0,\overline{P}]\bigg)
+    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
+[0,\overline{P}]\bigg) \\
+    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
+\times \lambda^j \subset T.
+\end{align*}
+The result follows from the fact that $t_i$ is continuous in $s_i$, as was
+proven in \cite{semret}, and as a finite union of compact sets is a compact set.
+$\qed$
+on any subset $\lbrace
+s_{-i}\in S_i : \ \forall \ z > 0, \overline{P} \ge P_i(z,s_{-i}) \ge
+\underline{P} \rbrace$, where $0<\underline{P}\le \overline{P} < \infty$
+(HERE) The dimension of a linear space is defined as the maximal number of linearly
+independent vectors or, equivalently, as the minimal number of vectors that span
+the space
+
+We now restrict our analysis to truthful $\epsilon$-best replies, $B^\epsilon$.
+
+{
+\corollary{Hemicontinuity of $\Delta$}
+}
+
+The data-sharing market consists of inter-dependent sets of these
+multi-auction games around possible fixed points.  Clearly, the union of all possible
 sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
-between the different subsets $\Delta$ form a heirarchical structure, and that
-there can only be a single primary fixed point, and this seller determines
-the equilibrium price in the global market. (EXPAND) We have the following
-Corollary, 
+between the different subsets $\Delta$ form a sufficiently connected set that
+the heirarchy described in Proposition \ref{userunion} holds. Then,
+there can only be a single primary fixed point, where the sellers' reserve
+price is an equilibrium price in the global market. 
+We first address the analytical approach, and demonstrate properties of
+$\Delta$ as a finite-dimensional linear topological space. We have that the
+reserve price of the sellers, and the bid price of the buyers is constant
+within an interval of length 2$\epsilon$. We have that 
+(HERE) We have the following
+Corollary, (MIGHT NEED TO REDEFINE.. NOT CLEAR IS A SEQUENCE, SHOULD BE
+SEQUENCE OF PRICES INSTEAD OF USERS?) 
 {
@@
 $\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
-\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then
+\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
+for a fixed time $t$,
 $\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
@@
 }\\
+(CAN PROBABLY USE ALL BUYERS HERE... BECAUSE OF INF)
 \textbf{Proof:}
@@
 above and below. From the assumption that $\overline{\Lambda}$ is not a
-partition, we have that,
+partition, we have that the limits exist with respect to bid price $p_i^j$, 
 $$
@@
 \ref{userunion} and Proposition \ref{incentive}.
-$\qed$\\
+(NEED TO SHOW THEY ARE EQUAL...)
+%$\qed$\\
 (USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
 
-\subsubsection{Nash Equilibrium}
-A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
-profile $s$,
-from which no player has a unilateral incentive to deviate (Johari, 2004)
-(EXPAND)
-We first show the existence of a \emph{static} Nash equilibrium, where buyers have fixed reserve
-prices.
-
+We show that our bidding strategy is
+part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
+equilibrium, where the sellers reserve prices are fixed.
 {
 \lemma{(Static Nash Equilibrium)} 
-Let the duration of an auction $j$ be $\tau \in (0,\infty)$, and fix the
-sellers reserve prices at $t=0, \ \forall \ j\in\mcI$.
-Using the rules of the data auction mechanism, the multi-auction game converges to a $\epsilon$-Nash equilibrium. In the network auction
-game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
-equilibrium. 
-}
+Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
+let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
+sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
+Using the rules of the data auction mechanism applied independently by each
+user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
+}\\
+\textbf{Proof:}
+(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
+As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
+$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
+$T=\Pi_{k\in\Lambda^j} T_k$. Now, $t$
+represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
+and we may use Brouwer's fixed point theorem, as in \cite{semret},
 
 As a result of user behavior, and subsequent strategies, we determine that the
-global data-exchange market behaves in a predictable way. However, as
+data-exchange market behaves in a predictable way. However,
 each auction may be played on the same or on a different scale in
-valuation, time and quantity, the rate at which market fluctuations occur is
+valuation, time and quantity, and so the rate at which market fluctuations occur is
 impossible to predict (NEED HELP!). 
@@
 strategy, and provides the right incentives for the truthful revelation of individual preferences.
+
+(DEFINITION.. USE?)
+In the General Symmetric Game, p is an evolutionarily stable mixed strategy if
+there is a (small) positive number y such that when any other mixed strategy q
+invades p at any level x < y, the fitness of an organism playing p is strictly
+greater than the fitness of an organism playing q.
 (EXPAND)
@@
 Formally, the
-mechanism is equilbriumcient if at equilibrium, the allocation maximizes
+mechanism is efficient, if, at equilibrium, the allocation maximizes
 $\sum_i\theta_i(a_i)$.
@@
 
+\bibitem{maille}
+Patrick Maillé.
+\textit{Market Clearing Price and Equilibria of the Progressive Second Price
+Mechanism},
+RAIRO - Operations Research, EDP Sciences, 2007, 41 (4), pp.465-478.
+
 \end{thebibliography}

### 2018-05-05 paper_wc.tex
Topology of best-reply

@@
 Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
-$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} S_i^j(s_{-i})$ the
+$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
 set of opponent profiles. We assume that the users are connected.
@@
 
+We interpret the collection of local auctions as collection of congestion games,
+where a buyers' payoff depends on the dynamics of the set of local auctions it
+``chooses".
 In a multi-auction market, each auction a buyer joins has the potential to
@@
 on its message space, and serves to limit the size of the buyer/seller pools. 
+Additionally, in congestion games,
+overly-frequent bid updates can result in an auction being
+overloaded, similarly to a DOS (denial-of-service) attack, thus the
+``liability" component of $\epsilon$ attempts to regulate bid flooding.
 
@@
 local markets. 
-For a buyer $i$, define have the set of possible $\epsilon$-best replies,
+For a buyer $i$, define the set of possible $\epsilon$-best replies,
 \begin{equation}\label{e-bid}
@@
 \end{equation}
-where $\wedge$ denotes the logical ``and" operator. The ``strategic" set $T_i$
-is restricted by Proposition \ref{buyerstrategy}. In the remainder of our
-analysis we limit the strategy space to our construction, and so we have the
-bid for buyer $i$, $S_i=\Pi_{j\in\mcI_i} S_i^j$, and the opponent bid, $S_{-i}
-=\Pi_{j\in\mcI_i} S_i^j(s_{-i})$ 
+where $\wedge$ denotes the logical ``and" operator. We note that the ``strategic" set $T_i$
+is restricted by Proposition \ref{buyerstrategy}.
 We have the following Proposition,
@@
 
-We have proven that buyers will submit bids according to their marginal
-valuations. Now, in the interest of completeness (BAD SENTENCE), we extend our result to be
-all-inclusive. As a result of the PSP multi-auction in the constructed strategy
-space, we find a well-defined mathematical structure manifests as a result of bid
-correspondence. The game-theoritical basis of our argument is complemented by,
-and benefits by (NEED? extension to) an abstract-theoretical analysis.
-Motivated by the symmetric nature of supply and demand we provide further rigor
-by mathematical construction. Thus, we begin with the definition of
+The strategy space of is comprised of a collection of bid, or ``strategy", vectors that
+together, describe the collection of congestion games. A change in buyer $i$'s
+utility, resulting from a change in strategy, equals the change in
+the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
+formulated by mapping the incentives of all users in a local auction to a
+single function. The goal of our analysis is to therefore construct a global potential function that encompasses
+all local markets. Then, we may determine a Nash equilibrium by finding a local
+optima of the potential function. Additionally, as the potential function also
+iterates, it may be used in an analysis of convergence. The
+convergence of a Nash equilibrium results from the progression of
+$\epsilon$-best replies, where each subsequent bid is a unilateral
+improvement, provided that $t_i$ is continuous in opponent profiles.
+From the original proof by \cite{lazar}, we observe that the collection of
+unconstrained truthful bids may be a subset
+of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
+%An essential component of determining the existence of a Nash equilibrium is 
+For this work, it suffices to show the continuity of the set of truthful
+$\epsilon$-best replies in the set of opponent bid profiles.
+In order to address continuity in a global sense, we must demonstrate
+continuity in the construction of our model.
+Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
+and determine the
+existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
 correspondence,
@@
 \definition{(Correspondence)}
-An ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
+A correspondence is mathematically defined as an ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
 $Y$, i.e. any subset of the Cartesian product $X\times Y$.
 }
-Now, in an economic model, the mapping $(\mcI,\mcI,R)$ is a map from the
-elements of $\mcI$ to the power set $\mathcal{P}(\mcI)$. The most obvious
+
+In an economic model, a correspondence $(S_i,S_{-i},R)$ defines a map from $S_i$
+to the power set $S_{-i}$, where $R$ is a binary relation, i.e. $R \subset
+S_i\times S_{-i}$. The classic
 example of a correspondence in our model is the buyers' best response
 $B_i^\epsilon$, where, for the multi-auction,
-$\Pi_{j\in\mcI} S_i^j$ and $\Pi_{j\in\mcI} S_{-i}^j$ are power sets under the
-identity relation, e.g $(S_i, S_i,\Pi\in\mcI S_i)$. The auction
-progresses by repeated mappings, where the full strategy space is the
-correspondence
-$(\Pi_{j\in\mcI}S_i,\Pi_{j\in\mcI}S_{-i},\Pi_{j\in\mcI}S_i^\epsilon)$ and
-finally, the best response is given as a reaction correspondence $B_i^\epsilon$
-defined by the mixed-strategy game.
-
-Thus, we address the sellers bids, and include the following corollary to support our result.
+$S_i$ and $S_{-i}$ are built by repeatedly using the
+cartesian product over bid profiles. The power set 
+$S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
+product of ordered sets. 
+The best response is a reaction correspondence
+defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
+S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
+profiles $S_{-i}$. \\
+\textbf{Remark:} 
+The ease by which the game is constructed is a consequence of the the cartesian
+product on a 2-dimensional message space. \\
+A natural induced topology of this space is the product
+topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.
+
+Motivated by the symmetric nature of supply and demand, we determine the
+game-theoritical argument is complemented by an abstract-theoretical analysis.
+In fact, we may even be philosophically motivated, as the truth value of a bid
+is determined only by how it relates to markets, and whether it provides an
+accurate correspondence. Using a set-theoretical approach to address the sellers
+bids, we derive our result from the symmetry of supply and demand,
+(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
+\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
+\ref{buyercoordinate}, and include the following corollary,
 {
 \corollary{Data-bid correspondence (seller cooperation)}
-For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is (NEED THIS? consistent with) a truthful
+Let $\Delta$ be defined as in Lemma (\ref{userunion}).
+For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
 $\epsilon$-best reply.
@@
 \textbf{Proof:}
-We claim there exists an equivalence relation $R$ that naturally evolves in the
-strategy space. For a seller $j$, let $y=\theta_i'(\g_i^(a))$ for a buyer $i$. We have that, for any allocation $a$, 
+We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
+strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
+We use the the axiom of set equality,
+based on first-order logic with equality, which states that,  
+$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
+\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
+Then, for any allocation $a$, we may define the relation, $i\thicksim
+j$,
 \begin{equation}\label{eqrel}
-        R \equiv (\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))) = (\g_i^j(a),y),
-\end{equation}
-defines equivalence $i \thicksim j$, where we use the definition of set
-equality based on first-order logic with equality. By definition, 
-$\forall \ i, \ \forall \ j, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
-\Rightarrow i \thicksim j$. This is the converse of (\ref{jtoi}). Formally, the
-axiom states that a set is \emph{uniquely} determined by its members.
-$R$ is defined by the bid price and
-reserve price of buyer $i$ and seller $j$, respectively. We
-have, for any $z\ge 0$,
-\begin{equation}\label{eqrel}
-        R \equiv i\thicksim j \equiv \theta_i'(z) - {\theta^j}'(z)\ge\epsilon
-\end{equation}
-defines equivalence $i \thicksim j$. Equivalence class $[i]$ is by definition
-the market supply at the buyers' valuation $\theta_i'$. Clearly, $k\thicksim k,
-\ \forall \ k\in\Delta$, and $\epsilon \ge \theta_i'(z) - {\theta^j}'(z)$
-%, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
-%and cannot sell more data than the buyers' aggragated bid quantities.
-The result follows by symmetry, and as the buyers' bids are
-truthful, and by (\ref{newprice}),Lemma \ref{userunion} and Lemma
-\ref{buyercoordinate}.$\qed$\\
-
-The ease by which the game is constructed is a consequence of the the cartesian
-product on a 2-dimensional message space.
-
-The reserve price $\epsilon$ acts as a placeholder for a seller submitting an
-auction to the ISP. As was proven in \cite{lazar}, the positive reserve price allows us to
-restrict our analysis to continuous, truthful bids. The strategy space of
-truthful bids is a collection of truthful bid, or ``strategy", vectors.
-From the original proof by \cite{lazar}, we observe that the collection of
-unconstrained truthful bids, $T_i = \Pi_{j\in\mcI} T_i^j$, may not be a subset
-of the collection of $\epsilon$-best replies, $\Pi_{\in\mcI} S_i^\epsilon$.         
-%An essential component of determining the existence of a Nash equilibrium is 
-For this work, it suffices to show the continuity of the set of truthful
-$\epsilon$-best replys, which we will denote $B_i^\epsilon = T_i\cap S_i^\epsilon$, in opponent bid profiles $S_{-i}$.
+        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
+        \big(\g_i^j(a),y)\big).
+\end{equation}
+Formally, the axiom states that a set is \emph{uniquely} determined by its
+members. It follows that $\thicksim$ defines equality of bids using a static
+analysis with respect to equilibrium, where all users who are not changing thier
+bids are considered equal.\\
+\textbf{Remark:} Equality is both an equivalence relation and a partial order,
+and therefore is reflexive, transitive, symmetric and antisymmetric. \\
+Now, we may define the mapping $s \mapsto [s]$,
+\begin{equation}\label{indeqrel}
+         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
+\end{equation}o
+noting that equality in the bid quantity is implicity satisfied and $z =
+\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
+buyer-seller pair. Without loss of generality, let $S = \Pi_{j\in\mcI} \big(
+\Pi_{i\in\mcI} S_i^j$. The indicator function is the canonical mapping,
+$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
+topology is preserved, the set of all indicator
+functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
+S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
+\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
+$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$.
 
 {
-\lemma{(Continuity of $\epsilon$-best reply on $\Delta$)}
+\proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
 Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
@@
 $\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
-we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ \overline{P}])$
-is a product of closed subsets of compact sets. Then, as a closed
-subset of a compact set is compact, and by Tychonoff's theorem, $\g_i \circ
-B_i^\epsilon$
-is compact subset of $B_i^\epsilon$. Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
+we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
+\overline{P}]^{\vert \mcI^j\vert})$
+is a product of closed subsets of compact sets. Now, we have that a closed
+subset of a compact set is compact and the resulting product topology gives
+Tychonoff's theorem. every product of a
+compact space is compact, we have $\g_i \circ B_i^\epsilon$
+is compact subset of $B_i^\epsilon$.
+ Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
 definition of $\Delta$ and the product, 
@@
 
-We now restrict our analysis to truthful $\epsilon$-best replies, $B^\epsilon$.
+%We have proven that buyers will submit bids according to their marginal
+%valuations. Now, in the interest of completeness (BAD SENTENCE), 
+We have that all bids represent $\epsilon$-best replies, and, as was proven in
+\cite{lazar}, the sellers' positive reserve price implies that bids are
+truthful. Finally, by properties determined by the construction of a mixed strategy
+symmetric game with a 2-dimensional message space, we may now restrict our
+analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.
 
@@
 $t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
-$T=\Pi_{k\in\Lambda^j} T_k$. Now, $t$
+$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
 represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
@@
 strategy, and provides the right incentives for the truthful revelation of individual preferences.
+
+The rules of the PSP
+multi-auction drive market mutations that evolve and are regulated by the user
+strategies.
+(HERE)
 

### 2018-05-05 paper_wc.tex
Intro and problem (real world application)

@@
 This usage model, is, as far as our knowledge, the first data trading
-platform that allows customers to buy and sell their own data.
+platform that allows customers to buy and sell their own data. The study of
+auction behavior in a data-exchange market distributed over mobile devices is
+largely unexplored.
 We describe a distributed auction mechanism for data exchange inspired by the
@@
 
-(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
-SENTENCES)
 In this work, we propose \emph{a distributed progressive second price (PSP) auction in
-order to maximize social utility in the CMHK market}. Using the
-distributed PSP mechanism on CMHKs data
-exhange platform, we show that for cellular data allocated between multiple users there
-exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
+order to maximize social utility in a shared-data market}
+A quality of the PSP auction is that
 demand information is not known centrally, rather, it is distributed in the
@@
 bids for that element only \cite{lazar}. In this work, the proposed mechanism
-allows the distribution of bids, where there are many ISPs each holding
-thier own local auction; there is no entity that holds a global market knowledge.
+allows the distribution of bids, where there are many auctioneers, each holding
+thier own local auction, and there is no single entity holds a global market knowledge.
 
@@
 ($\epsilon$-Nash) equilibrium is reached and a local auction is concluded. 
-
-(HOW DO WE MODEL ISP REVENUE? FUTURE WORK?)
-
 The form of the auction mechanism presented here is described as a \emph{locally}
 pure-strategy progressive game with incomplete, but perfect information.
-In a distributed setting, local markets have perfect local information, since you know what each move of the opponent is.
-However, since users are not aware of behavior in other auctions, it is a game of incomplete information.
-We complete a comprehensive analysis of market dynamics, and will assume
-complete and perfect information in order to verify properties and validate
-results of the auction mechanism.
-
-(TO ORGANIZE)\\
-The main contribution of this work 
-is an auction mechanism inspired by the classic PSP throughput problem. In
-order to apply a distributed PSP implementation to the CMHK market,
-we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
+In the distributed setting, we assume users have a binary type, either seller,
+i.e. auctioneer, or buyer. The perspective of strategy changes according to the user
+type. We assume unilateral strategies, and so sellers are unable to
+derive opponent information from buyer bids, and a buyer recieves updates but
+may not be aware of the behavior of opponent strategies in other markets.
+We complete a comprehensive analysis of market dynamics, and will assume for
+our analysis a game of complete and perfect information in order to verify
+properties and validate results of the auction mechanism.
+
+The body of this work describes an evolutionary system that drives an auction
+mechanism inspired by the classic PSP throughput problem \cite{lazar}. In
+order derive a distributed PSP implementation that arrives at an optimal
+objective,
+we analyze the behavior of users in a dynamical data exchange market. 
+It is known from \emph{Arrow's Theorem}, that in a multi-auction model, no deterministic strategy can
+provide a mapping of the preferences of users into a market-wide (complete
+and transitive) strategy while also meeting a specified set of criteria:
+unrestricted domain, non-dictatorship, Pareto efficiency and independence of
+irrelevant alternatives. 
+Therfore, as both buyers and sellers are able
+to change their bid strategies, and as each user only has \emph{local}
+information about the bidding environment, it is clear that a better market
+position can only be determined by an adaptive, or evolutionary, strategy.
+In other words, a move to a beter market position is synonymous to a
+strategic bid. In modern auctions, a strategy must meet a certain set of
+criteria: 1) truthfulness as a dominant strategy, 2) individual rationality/
+selfishness.  
+A Nash market equilibrium, where
+supply equals demand, requires that users maintain incentive for truthfulness
+across a distributed setting.
+As both buyers and sellers are able
 to change their bid strategies, and as each user only has \emph{local}
 information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the communication
-expense from numerous local auctions trading an infinitely divisible resource.
-We will assume that the cost of participating in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. It is worth mentioning that CMHK users are not allowed to resell data
-purchased from the CMHK
-market, additionally, the purchased data does not carry to the next
-service period. Therefore, a market equilibrium, where
-supply equals demand, requires that users maintain incentive for truthfullness
-across a distributed setting.
-To the best of our knowledge, this is the first work to provide a truthful
-mechanism in a distributed setting for data-exchange based on market behavior.
-\\
-\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
-restrictions introduced by the CMHK secondary market. We reserve this for
-future work.
-
-We claim that the CMHK market is
-able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and as our mechanism provides incentives
-for optimal, effective communication between the connected users.
-
-Despite the small message space, with many user types, there is no single
-way to do the transformation from the direct revelation mechanism to the
-desired one. Our mechanism is designed by guessing
-right direct-revelation-to-desired-mechanism transformation and building it
-into the allocation rule to be the primary step in the design. This incentive for a user to
-truthfully reveal its type is built into the user strategies. As in classic
-mechanism design, we determine the equilibria as result of incentive
-compatibility in our mechanism design. 
-We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
+market, even with a finite number of users, could suffer from the
+expense of many local auctions trading an infinitely divisible resource.
+
+Using the CMHKs data exhange platform as a host for our distributed strategic
+PSP mechanism, we show that in the market of one-time transaction payoffs,
+where the exchange is a quantity of cellular data transferred between multiple
+users, that there exists a primary $\epsilon$-Nash market equilibrium that is
+the winning dominant strategy in the multi-auction system.
+To the best of our knowledge, this is the first work to provide a comprehensive
+derivation of a truthful mechanism in a distributed setting for
+data-resource-exchange based on market behavior. In addition, we are the first
+to adapt the PSP mechanism to be contained within a market topology. The market
+topology and the user strategy are organically determined by the impact of user
+actions, 1) and 2), on market dynamics, and so determines a minimally optimal objective
+representing user valuation globally, and so fufills an additional property of
+economy over time and space. We further include the ISP as a deaf and blind
+user, who nonetheless holds the power to create a monopoly, thereby providing a free
+market space in which the market may operate, and real-world implications.
+
+We claim that our mechanism is designed to optimally progress towards an
+equilibrium by providing users with an incentive framework, and so rational
+users choose a market-collaborative exchage. 
+%\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
+%restrictions introduced by the CMHK secondary market. We reserve this for
+%future work.
+In classic mechanism design, with multiple user types, there is no single
+way to design the transformation from the direct revelation mechanism to its
+corresponding computational design. We apply a modifier to the PSP mechanism in
+order to mutate the strategy space, following dynamic user
+correspendence. As in \cite{lazar}, we take the direct
+approach by guessing the right modifier, and context, such that we have the
+desired result by composition with the PSP rules. 
+As in \cite{lazar}, the incentive for a
+user to truthfully reveal its type is built into the user strategies. Then,
+local equilibria follow as a result of incentive
+compatibility characterizing best strategy moves. \\ 
+\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
+referencing mechanism design and game theory, respectively.\\
+We claim that our formulation not only holds the desired VCG qualities,
 but minimizes comminication overhead 
@@
 
-The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
-construction of the user strategy space results in truthful bids that are optimal for all users,
-i.e. bid prices are to the marginal value as determined by market dynamics. 
+The user strategies are organic in that they are natural, or
+induced by the dynamic market itself. Thus, according to second-price strategy,
+we have an autonomous, self-updating (NEW WORD) and inclusive optimization, defined in terms of the multi-objective solution.
 This is the (built-in) transformation from the
-direct-revelation mechanism to the desired message space.
-
-The paper is organized as follows...
+direct-revelation mechanism to the desired message space, (OWN WORDS) where each user
+message defines a strategic point, which we may interpret as a move to a better
+market position. Then, in the limit of the data-model, a user reveals its
+valuation of a quantitiy of data-resource over the whole range of possible demands.
+
+The paper is organized as follows... (TODO)
 
@@
 
-\subsection{Motivation for Privacy/Security}(NEW SECTION)
-
-A property of PSP is that the user valuations are held private.
-
-1. The seller doesn't update with the ISP, and so does not know the market price
- in the data-exchange market.\\
-2. The auction is distributed, so there is no collusion between sellers and
-ISP.\\
-3. The mechanism is self-contained, and only requires participation. (THINK!)
-4. Better economy, as few users will get data plans with a lot of data, make
-money, allowing others to have cheaper data plans and not pay a lot for
-texting, phone calls (Buzzfeed). Free market capitalism! \\
-(CONCERN HERE ABOUT THROTTLING)
-
 \section{Related Work}
 
+VCG possible outcomes are characterized by bipartite matchings
+
 \section{The Problem Model}
@@
 \subsection{The CMHK Market}
+
+We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
+Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
+gained by charging users a fixed fee for a maximum amount
+of data usage in a month, i.e., a monthly data cap \cite{???}. 
+2cm's (2nd exchange market) data exchange platform allows users to submit
+bids to buy and sell data.
 
@@
 
+\subsection{The Data Market Problem}
+
+We address several topics under discussion in the real-monetary market of virtual
+data ownership. The issue of digital property is a well-known debate. The
+proliferation of services that are moving from grid to node communication
+outdates algorithms designed for optimization in this space. Direct and
+network-based communication between mobille devices allows for a simple
+mutation of classic optimization models. We will assume that the cost of participating in the CMHK secondary market is
+absorbed by the bid fee, which could represent data used in submitting bids, or
+a fee charged per unit of data, or a flat rate charged at the completion of the
+purchase. Thus, the bid fee acts to limit market iterations. \cite{semret}
+provides a proof, where convergence time is inversely related to $\epsilon$.
+Our design extends the pricing function:
+\begin{itemize}
+    \item A mutation characterized by a new variable cost, absorbed into the bid fee,
+        represents the
+        fact that CMHK users are denied resale and carryover of shared data, effectively creating
+        a form of liability with each transaction. 
+\end{itemize}
+This additonal fee acts as a regulate the mechanism behavior itself, as in a
+real-world situation, it is not ideal for fully-connected, asychronous
+user-to-user communication, which would obviously thrash the network. The
+mutation of the bid fee $\epsilon$ is based on real-world parameters associated
+with individual users. This information may be collected from a specific
+device's configuration, i.e. enabled roaming, daily data restrictions etc.
+We claim that our mechanism is self-regulating, and furthermore, optimized to satisfy the
+needs of the individual.
+
+A defining property of PSP is that user valuations are held private. 
+The CMHK model provides a unique opportunity for social equilibrium, as it
+allows users to share data without sharing the same data plan, a restriction in
+most ISPs, such as \cite{att}. We reason that the CMHK secondary-market
+approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
+as they have historically come close to monopolizing regional markets, leading
+to consumer abuse. Our mechanism
+takes advantage of the opportunity for full generalization provided by CMHK.
+Because CMHK is a generalization of more restrictive ISP practices, it is simple
+to adapt our mechanism to the data-sharing
+plans published by any ISP, i.e. the family, or corporate, data-sharing plan
+\cite{att}.
+We argue that data-sharing plans in general may be
+biased against the end-user. Adding devices to a shared-data plan includes a
+base fee for other services that have relatively small demand in comparison to
+the demand for data. Effectively, users must pay for services that go unused in
+order to increase the amount of data for a shared plan. Flexible data-sharing
+plans are similar to the CMHK market, where a limited number of devices may
+share a single data plan. A shared-data plan, however limited, offers better economy
+by creating primary users with a service package with a lot of data, and
+limited number of secondary users that are only using data \cite{att}.
+The CMHK model allows for primary and secondary users to freely correspond,
+without the restriction of a static primary-secondary user association.
+This effectively creates a competitive secondary market, and contributes to the
+dynamics of a free-market economy. Market competition is a desirable quality in
+free markets, and is encouraged, particularly in wireless and data services. In
+fact, California Legistature has recently passed laws promoting
+competition and enforcing fair practice of ISPs \cite{cabill}.
+
+We determine the need for privacy to extend from the users to the data-sharing market, in
+order to protect market fairness and exploitation of information by the ISP. In
+our model, free-market exchange is protected as privacy is integrated into the
+mechanism. Our design extends end-user privacy by the following: 
+\begin{itemize}
+    \item A mutation of user type, where
+    the ISP is represented by the blind, deaf user $\kappa$. Then, 
+    sellers do not update pricing information with the ISP, thereby hiding
+    its local market price in the data-exchange market. As the ISP has limited
+    information from its ``competitor", it is unable to sabatoge prices derived
+    from fair market competition.
+    \item The mechanism is self-contained, as prices are derived from market
+    dynamics, and only requires user participation,
+    therefore there cannot be any nefarious or criminal entity influencing
+    market dynamics.
+\end{itemize}
+Thus, we claim that our model supports and protects the secondary market, allowing it
+to be in direct competition with its parent ISP, and so contributes to the
+regulation of ISPs \cite{fedbill} and supports a regional free-market economy
+with respect to wireless data \cite{cabill}.
+
+In the original bandwidth-sharing model, the allocation role defines the active edges in a network for a particular bidder. 
+The flexibily of correspondance, and
+the ability for instantaneous communication in the distributed wireless network, allows for a more general, and
+thus adaptive strategy. We therefore introduce additional restrictions on
+defining properties of PSP multi-auctions, and claim they are normal.
+
 \subsection{User Valuation}
 
-We assume that the CMHK market does not have network
-bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper. We derive a globally optimal strategy suited for
+We address the market risks and securities in the CMHK secondary market. 
+We provide a game-theoretic model of a real market progression, which we use to
+derive, then define, adaptive variables. 
+We assume that the data-sharing market does not have network
+bottlenecks (although congestion is a similar, albeit separate issue), which is purely a bandwidth problem, as in \cite{semret}, and as
+bandwidth in wireless networks is not the focus of this paper, we derive a globally optimal strategy suited for
 users with local information in a distrubuted data-sharing model.
@@
 
+\bibitem{att}
+\textit{AT\&T Mobile Share Flex Plans}
+\url{https://www.att.com/plans/wireless/mobile-share-flex.html}
+2018
+
+\bibitem{cabill}
+\textit{Communications: broadband Internet access service}, S.B. 822. Reg. Sess.
+2017-2018. (2018).
+
+\bibitem{fedbill}
+\textit{No Rate Regulation of Broadband Internet Access Act},H.R. 2666, 114th
+Cong. (2016).
+
 \end{thebibliography}

### 2018-05-07 paper_wc.tex
Reworked problem model.

@@
 \begin{abstract}
-We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
-Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
-gained by charging users a fixed fee for a maximum amount
-of data usage in a month, i.e., a monthly data cap \cite{???}. 
-2cm's (2nd exchange market) data exchange platform allows users to submit
-bids to buy and sell data.
-This usage model, is, as far as our knowledge, the first data trading
-platform that allows customers to buy and sell their own data. The study of
-auction behavior in a data-exchange market distributed over mobile devices is
-largely unexplored.
-We describe a distributed auction mechanism for data exchange inspired by the
-classic PSP throughput problem,
-and prove that our distributed data exchange mechanism provides incentive
-compatibility (social choice function), and that we have efficiency
-using only partial valuation information of each participant in an exchange market.
-
-In applying a distributed PSP implementation to CMHK market, we
-find that
-the market is able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and design our mechanism tp provide the functions
-for effective communication between the connected users. We claim that in
-this secondary market our formulation holds the desired VCG qualities through the construction of a
-probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
+
+%Verizon and At\&T, two major Internet service providers (ISPs), are offering
+%shared data plans, where multiple users may purchase and share a single pool of
+%data. 
+We investigate data-exchange platforms for wireless users. The
+2cm (2nd exchange market) creates a secondary market where users can buy and sell data from each other.
+The ISP owns and moderates 2cm, which prevents the secondary market from
+acting as a competitor, and provides the ISP with free market research.
+Competition is desired, as it provides incentive for the ISP to protect
+and care for its end users.
+In this work, we design a strategy space, and a distributed Progressive Second Price (PSP) mechanism
+that extends individual privacy to the global space, allowing a secondary market to compete with its parent ISP. 
+The PSP auction has a single degree of freedom, the reserve price. We suggest
+that data exchange markets allow for greater flexibility in mechanism
+design due to the connectedness of the wireless network, and the fact that data
+exchange is a pure ``point of sale" market.
+We propose additional degrees of freedom, and derive modifiers
+to represent the deformation of the strategy space. 
+Using a game theoretic analysis, we derive a new strategic
+framework, removing restrictions that are dependent only on bandwidth. We
+model user valuation as a strategic response to market dynamics, and propose
+the resulting self-contained, self-balancing pricing system. 
+We examine mutations in market dynamics resulting from the new modifiers, and
+using set theory, we prove that the symmetry of our strategy space provides built-in
+conditions for convergence, and upholds the properties of truthfulness, efficiency and
+incentive compatibility, arriving at a Nash equlibirium.
+\end{abstract}
+
+\iffalse
+We further provide bounds on the auction duration, 
 with respect to the classic throughput problem.
@@
 market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
-\end{abstract}
+\fi
 
@@
 
-In this work, we propose \emph{a distributed progressive second price (PSP) auction in
-order to maximize social utility in a shared-data market}
+In this work, we propose a PSP auction mechanism for a secondary data
+market's valuations to be hidden from its parent ISP.
 A quality of the PSP auction is that
@@
 as \emph{distributed} when the allocations at any element depend only on
-\emph{local} state: the quantity offered by the seller at that element, and the
-bids for that element only \cite{lazar}. In this work, the proposed mechanism
-allows the distribution of bids, where there are many auctioneers, each holding
-thier own local auction, and there is no single entity holds a global market knowledge.
-
-In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
-using its own demand functions). Buyers submit bids cyclically until an
-($\epsilon$-Nash) equilibrium is reached and a local auction is concluded. 
-The form of the auction mechanism presented here is described as a \emph{locally}
+\emph{local} state, no single entity holds a global market knowledge. We consider the multi-auction, where there are many auctioneers, each holding
+thier own local auction. The auction mechanism may be described as
 pure-strategy progressive game with incomplete, but perfect information.
+
+In a PSP mechanism, bids consist of (1) a quantity and
+(2) a unit-price. Buyers submit bids until an
+($\epsilon$-Nash) equilibrium is reached.
+
 In the distributed setting, we assume users have a binary type, either seller,
-i.e. auctioneer, or buyer. The perspective of strategy changes according to the user
-type. We assume unilateral strategies, and so sellers are unable to
-derive opponent information from buyer bids, and a buyer recieves updates but
-may not be aware of the behavior of opponent strategies in other markets.
-We complete a comprehensive analysis of market dynamics, and will assume for
-our analysis a game of complete and perfect information in order to verify
-properties and validate results of the auction mechanism.
-
-The body of this work describes an evolutionary system that drives an auction
-mechanism inspired by the classic PSP throughput problem \cite{lazar}. In
-order derive a distributed PSP implementation that arrives at an optimal
-objective,
-we analyze the behavior of users in a dynamical data exchange market. 
-It is known from \emph{Arrow's Theorem}, that in a multi-auction model, no deterministic strategy can
-provide a mapping of the preferences of users into a market-wide (complete
-and transitive) strategy while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives. 
-Therfore, as both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that a better market
-position can only be determined by an adaptive, or evolutionary, strategy.
-In other words, a move to a beter market position is synonymous to a
-strategic bid. In modern auctions, a strategy must meet a certain set of
-criteria: 1) truthfulness as a dominant strategy, 2) individual rationality/
-selfishness.  
-A Nash market equilibrium, where
-supply equals demand, requires that users maintain incentive for truthfulness
-across a distributed setting.
-As both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the
-expense of many local auctions trading an infinitely divisible resource.
-
-Using the CMHKs data exhange platform as a host for our distributed strategic
-PSP mechanism, we show that in the market of one-time transaction payoffs,
-where the exchange is a quantity of cellular data transferred between multiple
-users, that there exists a primary $\epsilon$-Nash market equilibrium that is
-the winning dominant strategy in the multi-auction system.
+i.e. auctioneer, or buyer, and so user strategy changes according to the user
+type.
+
+We use game theory to show that the PSP mechanism, when applied to a
+pure ``point-of-sale" market, results in a primary
+$\epsilon$-Nash market equilibrium that is the dominant strategy in the
+multi-auction system.
 To the best of our knowledge, this is the first work to provide a comprehensive
-derivation of a truthful mechanism in a distributed setting for
-data-resource-exchange based on market behavior. In addition, we are the first
-to adapt the PSP mechanism to be contained within a market topology. The market
+derivation of a truthful mechanism that is self-contained within a dynamic market
+topology. The market
 topology and the user strategy are organically determined by the impact of user
-actions, 1) and 2), on market dynamics, and so determines a minimally optimal objective
+behavior on market dynamics, and so determines a minimally optimal objective
 representing user valuation globally, and so fufills an additional property of
-economy over time and space. We further include the ISP as a deaf and blind
+economy over time and space. We further model the ISP as a deaf and blind
 user, who nonetheless holds the power to create a monopoly, thereby providing a free
@@
 
-We claim that our mechanism is designed to optimally progress towards an
-equilibrium by providing users with an incentive framework, and so rational
-users choose a market-collaborative exchage. 
+The market strategy is based on providing users with an incentive framework, and
+so rational users choose a collaborative exchage. 
 %\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
@@
 \textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
-referencing mechanism design and game theory, respectively.\\
+from mechanism design and game theory, respectively.\\
+\iffalse
 We claim that our formulation not only holds the desired VCG qualities,
@@
 with respect to the classic throughput problem. 
+\fi
 
 The user strategies are organic in that they are natural, or
-induced by the dynamic market itself. Thus, according to second-price strategy,
-we have an autonomous, self-updating (NEW WORD) and inclusive optimization, defined in terms of the multi-objective solution.
+induced by the dynamic market itself. In other words, adhering to the second-price rule,
+where price is derived from autonomous demand, we have a strategic
+progressive auction, and a multi-objective equilibria.
 This is the (built-in) transformation from the
@@
 
+The secondary market applies the PSP auction rules over a wireless network. The
+wireless users' data incentives create a pure ``point-of-sale" market. We prove
+that there exists a primary $\epsilon$-Nash market equilibrium that is
+the dominant strategy in the multi-auction system.
+To the best of our knowledge, this is the first work to provide a comprehensive
+derivation of a truthful mechanism that is self-contained within a dynamic market
+topology. The market topology and the user strategy are organically determined by the impact of user
+behavior on market dynamics. We determine a globally optimal objective, and a
+strategy that satisfies the desires properties of competition, and
+economy over time and space.
+
+We address several topics under discussion in the real-monetary market of virtual
+data ownership. The proliferation of services that are moving from grid-based to node-based communication
+calls for algorithms designed for optimization in this space. Direct and
+network-based communication between mobille devices allows for a simple
+mutation of classic optimization models.
+
+The secondary market provides a unique opportunity for social equilibrium, as it
+allows users to share data without sharing the same data plan, a restriction in
+most ISPs, such as \cite{att}. We reason that a secondary market
+approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
+as they have historically come close to monopolizing regional markets, leading
+to consumer abuse. Our mechanism
+takes advantage of the opportunity for full generalization provided by CMHK.
+Our secondary market is adapted from the idea behind 2cm, the goal of allowing
+users to buy and sell data. We claim that it is simple
+to adapt our mechanism to the data share
+plans published by any major ISP, for example AT\&T's data share plan \cite{att}.
+We argue that data-sharing plans in general may be
+biased against the end-user. Adding devices to a shared-data plan includes a
+base fee for other services that have relatively small demand in comparison to
+the demand for data. Effectively, users must pay for services that go unused in
+order to increase the amount of data for a shared plan. Flexible data-sharing
+plans are similar to the CMHK market, where a limited number of devices may
+share a single data plan. A shared-data plan, however limited, offers better economy
+by creating primary users with a service package with a lot of data, and
+limited number of secondary users that are only using data \cite{att}.
+The CMHK model allows for primary and secondary users to freely correspond,
+without the restriction of a static primary-secondary user association.
+This effectively creates a competitive secondary market, and contributes to the
+dynamics of a free-market economy. Market competition is a desirable quality in
+free markets, and is encouraged, particularly in wireless and data services. In
+fact, California Legistature has recently passed laws promoting
+competition and enforcing fair practice of ISPs \cite{cabill}.
 The paper is organized as follows... (TODO)
 
-\subsection{Distributed Progressive Second Price Auctions}
+\section{Related Work}
+
+Progressive second price auctions (PSPs) were proposed
+in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
+scheme to provide consistent services for network bandwith users.
+\cite{diffserve} conducts a game theoretic analysis, deriving
+optimal strategies for buyers and brokers, and further shows the existence
+of networkwide market equilibria based on their game-theoretic
+model. Constructing necessary and sufficient conditions for the stability
+of the game allows the sustainability of any set
+of service level agreement configurations between Internet service
+providers.
+It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
+equilibria for differentiated services
+allocated between multiple agents when all players bid their real marginal valuation
+of the bandwidth resource. In other words, the PSP constraints are
+sufficient to attain the desirable property of truthfullness through incentive
+compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
+principle}, user $i$
+pays for its allocation so as to exactly cover the ``social opportunity cost"
+which is given by the declared willingness to pay (bids) of the users who are
+excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
+revenue \cite{lazar}.
+
+In \cite{zheng}, the ISP matches buyers and
+sellers to each other, and determines the amount
+of data that users can buy or sell. A buyer always pays her
+bid price for any data bought, and similarly a seller always
+receives his bid price, with any differences between the amounts
+paid and received acts as revenue for the ISP.
+%Then, the ISP will match buyers and sellers so as to optimize its revenue.
+
+Most previously studied data auctions aim to mitigate net-
+work congestion. For example, \cite{pubacs} considers a scheme in
+which users place bids on each transmitted data packet and the
+ISP admits packets in order of decreasing bids.
+
+%\iffalse
+\section{Distributed Progressive Second Price Auctions}
 
@@
 i.e. $p_i^j = {\theta_i^j}'$.
-
-\section{Related Work}
-
-VCG possible outcomes are characterized by bipartite matchings
+%\fi
 
@@
 \subsection{The CMHK Market}
-
-We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
-Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
-gained by charging users a fixed fee for a maximum amount
-of data usage in a month, i.e., a monthly data cap \cite{???}. 
-2cm's (2nd exchange market) data exchange platform allows users to submit
-bids to buy and sell data.
 
@@
 We further show that user valuation satisfies the conditions for an
-\emph{elastic demand function}, as in \cite{lazar}.
+elastic demand function.
+\iffalse:
+\definition{(Elastic demand) \cite{lazar}}
+A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta(0) = 0$,
+    \item $\theta$ is differentiable,
+    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
+     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
+${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
+{\theta}'(\eta)
+- \gamma(z - \eta)$. 
+\end{itemize}
+\fi
+In the PSP market, a
+user is considered truthful if their bid price equals their marginal valuation,
+i.e. $p_i^j = {\theta_i^j}'$.
 Finally, we assume in the CMHK market that a buyers' budget is always
@@
 auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
-influence the CMHK market dynamics, with the sellers taking a secondary role
+influence global market dynamics, with the sellers taking a secondary role
 (FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
@@
 
-We address several topics under discussion in the real-monetary market of virtual
-data ownership. The issue of digital property is a well-known debate. The
-proliferation of services that are moving from grid to node communication
-outdates algorithms designed for optimization in this space. Direct and
-network-based communication between mobille devices allows for a simple
-mutation of classic optimization models. We will assume that the cost of participating in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. Thus, the bid fee acts to limit market iterations. \cite{semret}
-provides a proof, where convergence time is inversely related to $\epsilon$.
-Our design extends the pricing function:
-\begin{itemize}
-    \item A mutation characterized by a new variable cost, absorbed into the bid fee,
-        represents the
-        fact that CMHK users are denied resale and carryover of shared data, effectively creating
-        a form of liability with each transaction. 
-\end{itemize}
-This additonal fee acts as a regulate the mechanism behavior itself, as in a
-real-world situation, it is not ideal for fully-connected, asychronous
-user-to-user communication, which would obviously thrash the network. The
-mutation of the bid fee $\epsilon$ is based on real-world parameters associated
-with individual users. This information may be collected from a specific
-device's configuration, i.e. enabled roaming, daily data restrictions etc.
-We claim that our mechanism is self-regulating, and furthermore, optimized to satisfy the
-needs of the individual.
-
-A defining property of PSP is that user valuations are held private. 
-The CMHK model provides a unique opportunity for social equilibrium, as it
-allows users to share data without sharing the same data plan, a restriction in
-most ISPs, such as \cite{att}. We reason that the CMHK secondary-market
-approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
-as they have historically come close to monopolizing regional markets, leading
-to consumer abuse. Our mechanism
-takes advantage of the opportunity for full generalization provided by CMHK.
-Because CMHK is a generalization of more restrictive ISP practices, it is simple
-to adapt our mechanism to the data-sharing
-plans published by any ISP, i.e. the family, or corporate, data-sharing plan
-\cite{att}.
-We argue that data-sharing plans in general may be
-biased against the end-user. Adding devices to a shared-data plan includes a
-base fee for other services that have relatively small demand in comparison to
-the demand for data. Effectively, users must pay for services that go unused in
-order to increase the amount of data for a shared plan. Flexible data-sharing
-plans are similar to the CMHK market, where a limited number of devices may
-share a single data plan. A shared-data plan, however limited, offers better economy
-by creating primary users with a service package with a lot of data, and
-limited number of secondary users that are only using data \cite{att}.
-The CMHK model allows for primary and secondary users to freely correspond,
-without the restriction of a static primary-secondary user association.
-This effectively creates a competitive secondary market, and contributes to the
-dynamics of a free-market economy. Market competition is a desirable quality in
-free markets, and is encouraged, particularly in wireless and data services. In
-fact, California Legistature has recently passed laws promoting
-competition and enforcing fair practice of ISPs \cite{cabill}.
-
-We determine the need for privacy to extend from the users to the data-sharing market, in
-order to protect market fairness and exploitation of information by the ISP. In
-our model, free-market exchange is protected as privacy is integrated into the
-mechanism. Our design extends end-user privacy by the following: 
-\begin{itemize}
-    \item A mutation of user type, where
-    the ISP is represented by the blind, deaf user $\kappa$. Then, 
-    sellers do not update pricing information with the ISP, thereby hiding
-    its local market price in the data-exchange market. As the ISP has limited
-    information from its ``competitor", it is unable to sabatoge prices derived
-    from fair market competition.
-    \item The mechanism is self-contained, as prices are derived from market
-    dynamics, and only requires user participation,
-    therefore there cannot be any nefarious or criminal entity influencing
-    market dynamics.
-\end{itemize}
-Thus, we claim that our model supports and protects the secondary market, allowing it
-to be in direct competition with its parent ISP, and so contributes to the
-regulation of ISPs \cite{fedbill} and supports a regional free-market economy
-with respect to wireless data \cite{cabill}.
+We determine the need for privacy in the data-sharing market. In \cite{zheng},
+it is assumed that the ISP interferes in 2cm (market) dynamics, and will maximize the
+gap between supply and demand in each transaction, exacting the difference as
+revenue. We notice that this market behavior is suspiciously monopolistic, as a
+single entity holds the global market power. It is further claimed in
+\cite{zheng} that user bids are truthful as they are guaranteed to receive
+their bid. We argue that this model represents an ``unwitting" buyer and an
+equally uninformed seller, as they have no intution of fair market value.
+Thus, in the interest of social good, we aim to provide a method to arrest
+anti-competitive conduct by ISPs. Thus our motivation to adapt the PSP auction,
+as it is easily distributed, and further has the property that user valuation
+functions are private. We propose an alternative to the centralized data
+exchange market that will prevent the exploitation of wireless users by their ISPs.
+
+We aim to design a distributed PSP auction, and a strategic framework that
+determines the bidding behavior of users in a wireless network.
+The auction design must must meet a certain set of known
+criteria: 1) \emph{truthfulness}, 2) \emph{individual rationality/
+selfishness}, 3) \emph{social welfare maximization}. For the secondary data exchange
+market, we determine that the
+strategy space must meet additional criteria: 4) \emph{privacy and
+independence from the ISP}, 5) \emph{locally fair division}, and vg)
+\emph{minimize crossover in buyer/ seller pools}.
+Thus, we propose a strategic framework to replace centralized data exchange
+markets, e.g. 2cm. The framework will act as a host for our distributed PSP
+mechanism, defining the strategy space and directing user correspondance.
+
+We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
+part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
+will determine its bid quanities by,
+\begin{equation}\label{opt-out}
+    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
+\end{equation}
+In a general sense, $\g_i$ applies our user strategy to the PSP rules.
+
+\subsubsection{Truthfulness.}
+We prove that the dominant strategy for buyers is to submit coordinated bids,
+where all bids the buyer submits are equal. Our motivation for coordinated bids
+comes from the idea of potential games \cite{shapely}. In potential games, the
+incentive of all users to change strategy can be expressed as a single global
+function. We map the incentive of a buyer over all auctions $j\in\mcI$ to a
+single potential function. This is a standard method that is used often, as it
+simplfies the analysis of both strategy and auction design. 
+We define the composition,
+$$
+     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
+$$
+to be the buyer strategy with respect to quantity. We will prove that for each
+buyer $i\in\mcI$ that $g_i^j(a)$ is equal $\forall \ j$. Finally, we prove the necessary condition of an $\epsilon$-best
+reply: a new bid price must differ from the last by at least $\epsilon$.
+Thus, our strategic bid is an $\epsilon$-best response.
+
+\subsubsection{Individual rationality.}
+We prove that a buyer cannot have a negative utility. Our
+strategic framework creates an incentive for the seller to maintain a local
+equilibrium, where supply equals demand. 
+We define the reserve price for seller $j$ as,
+\begin{equation}\label{newprice}
+    p_*^{j} = p_{i^*}^{j} + \epsilon,
+\end{equation}
+where $i^*$ is the highest losing bidder with respect to bid price.
+We claim that the choice of reserve price $p_*^j$ does not force any buyers out
+of the local auction. 
+A truthful bid implies that the new bid price differs from the last bid price by at least
+$\epsilon$. As a seller must distribute bid vectors to all
+buyers in its auction, we reason that the seller may employ a strategic caveat.
+The seller will notify a buyer who is subject to a market shift by changing its
+bid at the appropate index, and provide a proof by cases.
+
+\subsubsection{Social welfare maximization.}
+We claim that this is a natural consequence of PSP. Additionally,
+the mechanism is self-contained, and as prices are derived from market dynamics, there cannot be any nefarious or
+criminal entity negatively influencing the market.
 
@@
 
+\subsubsection{Privacy and independence from the ISP.}
+ In
+our model, free-market exchange is protected as privacy is integrated into the
+mechanism. Our design enforces privacy by a mutation of user type, where
+the ISP is represented by the blind, deaf user $\kappa$, who does not participate
+in any auctions, but nonetheless holds the power to create a monopoly. At time $t=0$, a seller $j$ entering the market will have
+submitted bid $s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
+platform, and so the initial bid $s_\kappa^j$, is public knowledge. 
+The, the auction
+begins at time $t>0$, and at $t=0$, $j$ will,
+initializing its reserve price by holding a single bid iteration.
+Sellers do not update pricing information with the ISP, thereby hiding
+its local market price in the data-exchange market. As the ISP has limited
+information from its ``competitor", it is unable to sabatoge prices derived
+from fair market competition.
+Thus, we claim that our model supports and protects the secondary market, allowing it
+to be in direct competition with its parent ISP, and so contributes to the
+regulation of ISPs \cite{fedbill} and supports a regional free-market economy
+with respect to wireless data \cite{cabill}.
+We will assume that the cost of participating in the secondary market is
+absorbed by the bid fee, which could represent data used in submitting bids, or
+a fee charged per unit of data, or a flat rate charged at the completion of the
+purchase. We do not model ISP revenue, but assume it may be extracted from the
+bid fee at $t=0$.
+
+\subsubsection{Locally fair division.}
+
+\subsubsection{Minimize crossover in buyer/ seller pools.}
+%A mutation characterized by a new variable cost, absorbed into the bid fee,
+%represents the fact that CMHK users are denied resale and carryover of shared
+%data, effectively creating a form of liability with each transaction. 
+We determine that the set of buyers and sellers participating
+in a single equilibrium is bounded by the potential indirect costs of
+participation. We will denote this individual cost to each user as
+$\varrho$. The indirect cost is the portion of the bid fee
+$\epsilon$ that is dependent on the underlying network and the individual.
+Observing that $\varrho$ indirectly effects user utility,
+and therefore acts to establish a natural budget for each user. We give this
+constraint as, 
+\begin{equation}\label{poolbnd}
+    u \le \varrho,
+\end{equation}
+which may be interpreted as the effort a rational user is willing to expend
+on its message space, and serves to limit the size of the buyer/seller pools. 
+This information may be collected from a specific
+device's configuration, i.e. enabled roaming, daily data restrictions.
+It is clear that an unconstrained
+market, even with a finite number of users, could suffer from the
+expense of many local auctions trading an infinitely divisible resource, thus
+$\varrho$ is interpreted as
+the ``liability" component of $\epsilon$ attempts to regulate network congestion.
+
+In order derive a distributed PSP implementation that arrives at an optimal
+objective,
+we analyze the behavior of users in a dynamical data exchange market. 
+Buyers and sellers are able
+to change their bid strategies asychronously and serially, using local information to determine their strategy. 
+A users' local strategy space is therefore nondeterministic, and the prefererences of users
+are subject to change, i.e. binary dependence.
+Then, from \emph{Arrow's Theorem}, we have that no deterministic strategy can
+provide a mapping of the preferences of users into a market-wide (complete
+and transitive) strategy. As individual bids cannot map to a general objective, a better market
+position can only be determined by an adaptive strategy.
+We define a move to a better market position to be synonymous with a
+strategic bid.
+
+\section{Strategic Framework}
+
 \subsection{User Valuation}
 
-We address the market risks and securities in the CMHK secondary market. 
+We address the market risks and securities in our secondary data exchange market. 
 We provide a game-theoretic model of a real market progression, which we use to
 derive, then define, adaptive variables. 
-We assume that the data-sharing market does not have network
-bottlenecks (although congestion is a similar, albeit separate issue), which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper, we derive a globally optimal strategy suited for
+Assuming equal bandwidth for all users, and derive a globally optimal strategy suited for
 users with local information in a distrubuted data-sharing model.
@@
 utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
-part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
-will determine its bid quanities by,
-\begin{equation}\label{opt-out}
-    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
-\end{equation}
-In a general sense, this abstraction applies our \emph{user strategy}
-to the PSP rules.
+market. 
 % OPT-OUT BUYER
@@
 It is possible that a seller would be able to derive information about other
-auctions by examining buyer bids over time, particularly if the seller had knowledge of the
-buyer strategy. (FUTURE WORK?)\\
-
-We interpret the collection of local auctions as collection of congestion games,
+auctions by examining buyer bids over time, particularly if the seller had
+knowledge of the buyer strategy. In this work, we assume sellers are unable to derive opponent information from buyer bids. \\
+
+We interpret the collection of local auctions as collection of strategic games
+of incomplete but perfect information,
 where a buyers' payoff depends on the dynamics of the set of local auctions it
@@
 does \emph{not} imply that $s_i=s^j$.
-
-We further determine that the set of buyers and sellers participating
-in a single equilibrium is bounded by the potential indirect costs of
-participation. We will denote this individual cost to each user as
-$\varrho$. The indirect cost is the portion of the bid fee
-$\epsilon$ that is dependent on the underlying network and the individual.
-Observing that $\varrho$ indirectly effects user utility,
-and therefore acts to establish a natural budget for each user. We give this
-constraint as, 
-\begin{equation}\label{poolbnd}
-    u \le \varrho,
-\end{equation}
-which may be interpreted as the effort a rational user is willing to expend
-on its message space, and serves to limit the size of the buyer/seller pools. 
-Additionally, in congestion games,
-overly-frequent bid updates can result in an auction being
-overloaded, similarly to a DOS (denial-of-service) attack, thus the
-``liability" component of $\epsilon$ attempts to regulate bid flooding.
 
@@
 noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool.
+over the seller pool. \\
+\textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
+are complementary. In fact, the buyer strategy is the first term in the
+minimum, the second term being owned by the seller. \\
 Finally we must have that the cost to the buyer adheres to the second price
@@
 % OPT-OUT BUYER STRATEGY
-Define the composition,
-$$
-     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity.
+
 Also define the set,
@@
 and we determine that the opt-out strategy is optimal.
-$\qed$\\
-\textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
-are complementary. In fact, the buyer strategy is the first term in the
-minimum, the second term being owned by the seller.
+$\qed$
 
@@
 \mcI^j$.
-Then, for time $(t+1)$, set $j$'s reserve price to be, 
-\begin{equation}\label{newprice}
-    p_i^{j(t+1)} = p_{i^*}^{j(t)} + \epsilon,
-\end{equation}
 Let the winner at time $t$ be determined by,
@@
 With this caveat, and Proposition \ref{buyerstrategy}, we have that the
-aggragate demand of subset $\mcI^j$ is satisfied by seller $j$, as in Lemma
-\ref{sellerconstraints}.
+aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
 Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
@@
 
-In order to represent the public platform of the secondary market, we model the ISP as
-a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
-in any auctions. At time $t=0$, a seller $k$ entering the market will have
-submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
-seller does not require a priori demand information to enter the market.
-Also, a new sellers' bid, $(D^j, \epsilon)$, is public knowledge. 
 \iffalse
@@
 %may represent by some homogenous function of degree one (EXPAND?).
-Thus the auction
-begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
-initializing bid prices.
 
@@
 has incentive to change its bid as a result of a market shift or partial
-allocation. We now show the necessary condition of a truthful reply, new bid
-prices must differ from the last by at least $\epsilon$, and prove that the
-resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
-In a truthful reply, the term $\epsilon/\theta_i'(0)$
+allocation. In a truthful reply, the term $\epsilon/\theta_i'(0)$
 ensures that a new bid price differs from the last bid price by at least
@@
 
-The strategy space of is comprised of a collection of bid, or ``strategy", vectors that
-together, describe the collection of congestion games. A change in buyer $i$'s
+The strategy space is comprised of a collection of bid, or ``strategy", vectors that
+together, may be represented as a collection of potential functions, where change in buyer $i$'s
 utility, resulting from a change in strategy, equals the change in
@@
 
+\bibitem{shapley}
+Dov Monderer and Loyd Shapley. 
+\textit{Potential Games}, Games and Economic Behavior. 14: 124–143. (1996).
+
 \end{thebibliography}

### 2019-08-21 April/paper_recovered.tex
On hold.

--- 2018-05-05 paper_wc.tex
@@
 
-(HOW DO WE MODEL ISP REVENUE? FUTURE WORK?)
-
-The form of the auction mechanism presented here is described as a \emph{locally}
+(FEE IS FIXED OR
+PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)
+
+The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
+CLAIM 'IS') described as a \emph{locally}
 pure-strategy progressive game with incomplete, but perfect information.
-In a distributed setting, local markets have perfect local information, since you know what each move of the opponent is.
-However, since users are not aware of behavior in other auctions, it is a game of incomplete information.
-We complete a comprehensive analysis of market dynamics, and will assume
-complete and perfect information in order to verify properties and validate
-results of the auction mechanism.
-
-(TO ORGANIZE)\\
+ you have perfect information, since you know what each move of the opponent is.
+However, since you do not know the payoff function of the other player (which
+will affect its behavior even if it does not alter your own victory conditions),
+it is a game of incomplete information.
+In the overall market analysis assumes complete, but perfect information.
+
+ (WHAT
+DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
+VALUATION.. FUTURE WORK)
+
+The paper is organized as follows...
+
+(MOVED: TO ORGANIZE)\\
 The main contribution of this work 
@@
 across a distributed setting.
+We complete a comprehensive analysis of market dynamics, (FINISH)
 To the best of our knowledge, this is the first work to provide a truthful
@@
 able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and as our mechanism provides incentives
-for optimal, effective communication between the connected users.
+incentive for a collaborative exchange, and as our mechanism provides
+for effective communication between the connected users.
 
@@
 
-The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
-construction of the user strategy space results in truthful bids that are optimal for all users,
-i.e. bid prices are to the marginal value as determined by market dynamics. 
 This is the (built-in) transformation from the
 direct-revelation mechanism to the desired message space.
-
-The paper is organized as follows...
 
@@
 The market price function (MPF) for a buyer-seller pair is,
-% MARKET PRICE
+% NEW MARKET PRICE
 \begin{align}\label{dataprice}
@@
 $j$ at unit price $y$ given $s_{-i}^j$ is,
-% INVERSE DEMAND
+% NEW INVERSE DEMAND
 \begin{align}\label{datapriceinverse}
@@
 revenue \cite{lazar}.
-{
-\definition{(Nash Equilibrium)}
-A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
-profile $s$,
-from which no player has a unilateral incentive to deviate (Johari, 2004)
-(EXPAND?)
-}\\
-
 The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
@@
 
-\subsection{Motivation for Privacy/Security}(NEW SECTION)
-
-A property of PSP is that the user valuations are held private.
-
-1. The seller doesn't update with the ISP, and so does not know the market price
- in the data-exchange market.\\
-2. The auction is distributed, so there is no collusion between sellers and
-ISP.\\
-3. The mechanism is self-contained, and only requires participation. (THINK!)
-4. Better economy, as few users will get data plans with a lot of data, make
-money, allowing others to have cheaper data plans and not pay a lot for
-texting, phone calls (Buzzfeed). Free market capitalism! \\
-(CONCERN HERE ABOUT THROTTLING)
-
 \section{Related Work}
@@
 particpating in CMHK's secondary data-sharing market.
-Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
+Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
 data from other users. We again define the bidding profile for any user to be 
@@
 , s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
-$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
-set of opponent profiles. We assume that the users are connected.
-A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. We assume
-that users are selfish, and therefore rational. 
+As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
+cellular network. We assume that users are selfish, and therefore
+rational. 
+Users prefer to participate in the CMHK secondary market as it allows them to purchase
+additional data for a cost less than the overage fee set by the ISP. 
 Thus we assume that all users submit bids in order to maximize their
@@
 bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper. We derive a globally optimal strategy suited for
+bandwidth in wireless networks is not the focus of this paper. We
+conduct a comprehensive analysis, deriving a globally optimal strategy suited for
 users with local information in a distrubuted data-sharing model.
@@
 \end{equation}
-where the composition of the elastic valuation function $\theta_i$ with $\g_i$
-distributes a buyers' valuation of allocation $a$ across local markets (and thus
-multiple sellers).
+where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
+the buyers' valuation of allocation $a$ across local markets (and thus multiple
+sellers), and $\theta_i(\g_i(a)) - \g_i(\varrho)$ represents the buyers'
+corresponding debit.  
 In this way we extend the PSP rules described
@@
 
-We interpret the collection of local auctions as collection of congestion games,
-where a buyers' payoff depends on the dynamics of the set of local auctions it
-``chooses".
 In a multi-auction market, each auction a buyer joins has the potential to
@@
 $y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
-We determine that the market supply function corresponds to an extreme of
-possible buyer demand, and 
+We determine that the market supply function is equivalent to buyer demand, and 
 acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
@@
 on its message space, and serves to limit the size of the buyer/seller pools.
-Additionally, in congestion games,
-overly-frequent bid updates can result in an auction being
-overloaded, similarly to a DOS (denial-of-service) attack, thus the
-``liability" component of $\epsilon$ attempts to regulate bid flooding.
-
-Finally, it is worth mention that the \emph{analysis} of the auction as
+
+Finally, it is worth mentioning that the \emph{analysis} of the auction as
 a game assumes some forms of demand and supply, in order to derive properties.
@@
 Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
-(THE ABOVE IS GOOD, BUT DOESN'T FIT MY CONSTRUCTION, CHANGE TO BELOW?)
-The market price function (MPF) for a buyer in the CMHK market
-is determined per (\ref{buyerinversedemand}), and is defined as,
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ j\in\mcI \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-and is interpreted as the price that buyer $i$ bids in
-order to obtain
-data amount $z$ given opponent profile $s_{-i}$.
-The sellers pricing function is according to (\ref{sellerinversedemand}), 
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}^j(z, s_{-i}) =\displaystyle\sum_{i\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\sup\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ i\in\mcI \bigg\rbrace \bigg).\\
-\end{split}
-\end{align}
-We note that
-the total price cannot be an aggragation of the
-\emph{individual} bid prices as it is possible that the reserve prices
-of the individual sellers may vary, which contradicts
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}).\\
-\textbf{Remark:} We further note that except at points of discontinuity, from
-Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
 %To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
@@
 \end{align}
-It follows from the upper-semicontinuity of $D_i^j$ that for $s_{-i}^j$ fixed, $\forall \ y,z \ge 0$,
-\begin{equation}\label{dtop}
-    \g_i^j(z) \le \g_i^j \circ D_i^j(y,s_{-i}^j) \Leftrightarrow y \ge \g_i^j
-\circ P_i^j(z,s_{-i}^j).
-\end{equation}
 % DATA ALLOCATION RULE
@@
 $$
-to be the buyer strategy with respect to quantity.
+to be the buyer strategy with respect to quantity, and similarly for $\varrho$.
 Also define the set,
@@
 auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. Defining a single iteration of the auction, where a seller updates bid vector
-$s^j$, and the buyers' response $s_i$, to comprise a single time step, and we have the following Lemma,
+local auctions on each other. We have the following Lemma,
 % USER UNION
@@
 \begin{equation}\label{lambda}
-    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
+    \Delta = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
 \end{equation}
@@
 \fi
-Define $\Delta = \Lambda \cup \lambda$.
 Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
@@
 A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. Using Proposition \ref{sellerstrategy} and (\ref{jtoi}), we have that, 
-\begin{equation}\label{iff}
-    i\in\mcI^j \Leftrightarrow p_i^j > p_{i^*}^j,
-\end{equation}
-where
+profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
+if and only if $i$'s bid is such that $p_i^j > p_{i^*}^j$, where
 (\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
@@
 p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
-shift caused by the underlying dynamics.
-Consider $k\in\mcI^j$ at time $t$ where, for example, some buyer(s) enter the auction, and
-so (\ref{iff}) implies that
-$\sum_{i\in\mcI^j} \g_i^j(a) > D^j$. Now, $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
-$s_k^j>0$ will cause $k$ to initiate a shift. By Proposition \ref{buyerstrategy}, $k$ will set $s_k^j=0$, and begin to add sellers to its pool.
-Suppose that at time $t$, $j$'s market is at equilibrium, i.e.
-$\sum_{i\in\mcI^j} \g_i^j(a) = D^j$, and fixing all other bids, so 
-no buyer $i\in\mcI^j$ rebids. Unless $k$ adds a seller with a higher reserve
+shift, caused by the underlying dynamics.
+Consider $k\in\mcI^j$ where for example, new buyers enter the auction, or increase
+thier bid prices, so that $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
+$s_k^j>0$ at time $t$. 
+By Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
+Suppose that at time $t$, $j$'s market is at equilibrium, i.e. $\sum_{i\in\mcI^j} = D^j$, and
+no buyer rebids. Unless $k$ adds a seller with a higher reserve
 price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
-auction ends. Otherwise, at some time $t\in[t+1,\tau]$, we must have that
-$\g_k^j \le D^j$, and $k$ rejoins auction $j$ or opts-out. Finally, overlooking market shifts and messaging
+auction will end. Otherwise, at some time $t\in[t+1,\tau]$, we must have that $\g_k^j <
+D^j$, and $k$ opts-out. Finally, overlooking market transitions and messaging
 overhead, we have that,
@@
 The reserve price (\ref{newprice}) of seller $j$ is determined at each
-shift, and is
+transition, and is
 the lowest price that $j$ will accept to perform any allocation.
@@
 \end{equation}
-from (\ref{newprice}). Now, by Proposition \ref{sellerstrategy}, in the absence
-of external influences caused by multi-auction market dynamics, we have 
-that $j$ maintains a local market equilibrium from time $t$ to $(t+1)$.
-From (\ref{lambda}) and (\ref{llambda}), $\Delta$ is defined by a seller $j\in\mcI$, where each
-user $k\in\Delta$ has some direct or indirect influence on $j$. 
-We may identify $\Delta$ by its dominant seller, and we denote $\Delta^j = \Lambda^j
-\cup \lambda^j$.
-
-Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$, and
-the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
-have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
-where,
-\begin{equation}\label{ordering}
-    p_*^k \le p_l^* < p_*^j \le p_i^*,
-\end{equation} 
-for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
-p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
-which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
-\ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
-(\ref{iff}).
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
-0$, for some $g\in\mcI_i$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
-where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
-p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
-a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
-such that $p_*^g \ge p_*^j$. Thus, we
-determine a direct influence as $l\in\mcI^k
-\cap \Lambda^j$, such that $p_l^* > p_i^*$,
-and an indirect influence as, for any $l\in\mcI^k
-\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
-
-Now, consider the subset $\Lambda^j$, by
-Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
-decreases its bid quantity so that $\sum_{i\in\mcI^j}
-\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
-\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
-p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the
-lowest bid price, the ``lowest clearing player",
+by Proposition \ref{sellerstrategy}. 
+Also, in the absence of transitions, caused by multi-auction market dynamics, we have 
+that $j$ maintains a local market
+equilibrium from time $t$ to $(t+1)$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
 and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
-directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
-buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
-recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
-will attempt to regain equilibrium.
-Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
-then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
-seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
-p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
-\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
-case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
-where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).
-
+that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand from time $t$ to $t+1$ will
+directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
+buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
+thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
+recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
 In each case we
@@
 therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-Thus, any bid ouside of
+
+Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
+some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
+p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
+Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
+that $p_l^* < p_*^j$, and
+the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so,
+$$
+    p_*^k \le p_l^* < p_*^j \le p_i^*,
+$$
+for any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
+p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
+$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
+which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
+\ni\mcI^q \Rightarrow p_*^q >
+p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
+buyer $i$. 
+Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q =
+0$ for $q\in\mcI_i$.
+We have that for any $l\in\mcI^k$ such that $l\ni
+\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
+for $q\in\mcI_l$ or $\theta_l^q = 0$ for some $q\in\mcI_i$. Thus, any bid ouside of
 our construction
 has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$, and therefore cannot cause shifts to occur except through a
+$\in\Lambda$, and therefore cannot cause transitions to occur except through a
 shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
 (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
-bids in any auction $q \ni \Lambda^j$,
+bids in any auction $\mcI^q$, where $q\in \mcI_l \setminus \Lambda$,
 we have, $\forall \ k\in\mcI_i$,
@@
 seller does not require a priori demand information to enter the market.
-Also, a new sellers' bid, $(D^j, \epsilon)$, is public knowledge. 
-\iffalse
 (DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
@@
 ``buyer" $\kappa$. 
-\fi
+A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
+knowledge. 
+\iffalse
 A buyer entering the market
 at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER! ALSO DO I REALLY NEED THE I.I.D?) is initialized as 
+(SAY BETTER!) is initialized as 
 an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
@@
 density function of $X$.
+\fi
 %may represent by some homogenous function of degree one (EXPAND?). 
@@
 where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$.
+buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
+define a single iteration of the auction, wher a seller updates bid vector
+$s^j$, and the buyers' response $s_i$, to comprise a single time step.
 
@@
 \end{center}
-Finally, we give a simple example of convergence to a local market equilibrium,
-where the buyers are assumed to respond with their truthful,
+Finally, we give a simple example of convergence to a local market equilibrium, where the buyers are assumed to respond with their
 $\epsilon$-best replies.
@@
 allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
-\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
+(z_i,y_i)$, where $\forall \ j \in \mcI_i$,
 \begin{align*}
-    z_i^j &= \g_i^{j}(a), \\
+    z_i^j &= \g_i^{j^*}(a), \\
     y_i^j &= \theta_i'(z_i^j).
@@
 a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$.
+$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$,
+so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$. 
 Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$, $\g_i^k(a) \le z_i^j = \g_i^{j}(a)$,
+$k\ni\mcI_i$,
+$$
+    \g_i^k(a) \le z_i^j = \g_i^{j^*}(a) \le \g_i^{j}(a),
+$$
 and so, using (\ref{union-eq}), 
 \begin{equation}\label{minimaleq}
-    \g_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
+    \g_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
 \end{equation}
@@
 $$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j})\ge D_i^j(p_i^{k}).
+    D_i^j(y_i^j) \ge D_i^j(p_i^{j^*})\ge D_i^j(p_i^{k}).
 $$
@@
 Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$\g_k^{j}(a) \ge \g_i^{j}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
+$\g_k^{j^*}(a) \ge \g_i^{j^*}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
 partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
 As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j}(a)
-\ge \g_k^{j}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
+set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j*}(a)
+\ge \g_k^{j^*}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
 We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
 $$
-    {\theta_i}'(\g_i^{k}(a)) \ge {\theta_i}'(\g_i^{j}(a)) \ge y_i^j.
+    {\theta_i}'(e_i^{k}(a)) \ge {\theta_i}'(e_i^{j^*}(a)) \ge y_i^j.
 $$
@@
 d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= \g_i^{j}(a)
+    &= z_i^{j}= e_i^{j^*}(a)
 \end{align*}
@@
 second-price markets. The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
-construction of the user strategy space results in truthful bids that are optimal for all users,
+necessity for a user to determine its own valuation function, and due to our
+construction, we intend to show that truthful bids are optimal for all users,
 i.e. bid prices are to the marginal value as determined by market dynamics. 
@@
 $\epsilon$, thereby ensuring that a buyer does not change its bid without
-correcting the effects of unstable shifts.
+correcting the effects of unstable transitions.
 We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
 \forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a market equilibrium extending over a subset of connected
-local markets. 
-For a buyer $i$, define the set of possible $\epsilon$-best replies,
-\begin{equation}\label{e-bid}
-    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
-u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
-\end{equation}
-and the set of \emph{truthful} bids, 
-\begin{equation}\label{t-bid}
-    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
-\wedge p_i = \theta_i'(z)\rbrace,
-\end{equation}
-where $\wedge$ denotes the logical ``and" operator. We note that the ``strategic" set $T_i$
-is restricted by Proposition \ref{buyerstrategy}.
-We have the following Proposition,
+there exists a local market equilibrium extending over a subset of connected
+local markets. We have the following Proposition. 
+(DO I NEED TO PROVE CONTINUITY TOO?)
 
 {
-\proposition{(Incentive compatibility across local auctions)}\label{incentive}
+\proposition{(Incentive compatibility across local auctions)}
 Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
 $t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
-buyer $i\in \mcI^j$, let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
+buyer $i\in \mcI^j$, (DO I WANT LAMBDA? SO MANY CASES) let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
 \begin{align}
@@
 Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
-(v_i,w_i) \in T_i\cap S_i^\epsilon(s_{-i})$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
+(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
 s_{-i})$.
 With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
-$\in\Delta$. Therefore, a fixed point $\in \Delta$ is a fixed point in
-the multi-auction game. 
+in the global market, and thus denoting $\Gamma= \Lambda \cup \lambda$, we have
+an equilibrium point in $\Gamma$. 
 }\\
@@
 $\qed$\\
-
-The strategy space of is comprised of a collection of bid, or ``strategy", vectors that
-together, describe the collection of congestion games. A change in buyer $i$'s
-utility, resulting from a change in strategy, equals the change in
-the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
-formulated by mapping the incentives of all users in a local auction to a
-single function. The goal of our analysis is to therefore construct a global potential function that encompasses
-all local markets. Then, we may determine a Nash equilibrium by finding a local
-optima of the potential function. Additionally, as the potential function also
-iterates, it may be used in an analysis of convergence. The
-convergence of a Nash equilibrium results from the progression of
-$\epsilon$-best replies, where each subsequent bid is a unilateral
-improvement, provided that $t_i$ is continuous in opponent profiles.
-From the original proof by \cite{lazar}, we observe that the collection of
-unconstrained truthful bids may be a subset
-of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
-%An essential component of determining the existence of a Nash equilibrium is 
-For this work, it suffices to show the continuity of the set of truthful
-$\epsilon$-best replies in the set of opponent bid profiles.
-In order to address continuity in a global sense, we must demonstrate
-continuity in the construction of our model.
-Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
-and determine the
-existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
-correspondence,
+For completeness, we address the sellers bids, and include the following corollary to support our result.
 {
-\definition{(Correspondence)}
-A correspondence is mathematically defined as an ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
-$Y$, i.e. any subset of the Cartesian product $X\times Y$.
-}
-
-In an economic model, a correspondence $(S_i,S_{-i},R)$ defines a map from $S_i$
-to the power set $S_{-i}$, where $R$ is a binary relation, i.e. $R \subset
-S_i\times S_{-i}$. The classic
-example of a correspondence in our model is the buyers' best response
-$B_i^\epsilon$, where, for the multi-auction,
-$S_i$ and $S_{-i}$ are built by repeatedly using the
-cartesian product over bid profiles. The power set 
-$S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
-product of ordered sets. 
-The best response is a reaction correspondence
-defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
-S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
-profiles $S_{-i}$. \\
-\textbf{Remark:} 
-The ease by which the game is constructed is a consequence of the the cartesian
-product on a 2-dimensional message space. \\
-A natural induced topology of this space is the product
-topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.
-
-Motivated by the symmetric nature of supply and demand, we determine the
-game-theoritical argument is complemented by an abstract-theoretical analysis.
-In fact, we may even be philosophically motivated, as the truth value of a bid
-is determined only by how it relates to markets, and whether it provides an
-accurate correspondence. Using a set-theoretical approach to address the sellers
-bids, we derive our result from the symmetry of supply and demand,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
-\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
-\ref{buyercoordinate}, and include the following corollary,
-{
-\corollary{Data-bid correspondence (seller cooperation)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}).
-For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
-$\epsilon$-best reply.
+\corollary{Seller cooperation.}
+We claim that $s^j$ is both truthful and optimal.
 }\\
 \textbf{Proof:}
-We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
-strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
-We use the the axiom of set equality,
-based on first-order logic with equality, which states that,  
-$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
-\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
-Then, for any allocation $a$, we may define the relation, $i\thicksim
-j$,
-\begin{equation}\label{eqrel}
-        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
-        \big(\g_i^j(a),y)\big).
-\end{equation}
-Formally, the axiom states that a set is \emph{uniquely} determined by its
-members. It follows that $\thicksim$ defines equality of bids using a static
-analysis with respect to equilibrium, where all users who are not changing thier
-bids are considered equal.\\
-\textbf{Remark:} Equality is both an equivalence relation and a partial order,
-and therefore is reflexive, transitive, symmetric and antisymmetric. \\
-Now, we may define the mapping $s \mapsto [s]$,
-\begin{equation}\label{indeqrel}
-         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
-\end{equation}o
-noting that equality in the bid quantity is implicity satisfied and $z =
-\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
-buyer-seller pair. Without loss of generality, let $S = \Pi_{j\in\mcI} \big(
-\Pi_{i\in\mcI} S_i^j$. The indicator function is the canonical mapping,
-$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
-topology is preserved, the set of all indicator
-functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
-S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
-\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
-$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$.
-
-{
-\proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
-$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
-}\\
-\textbf{Proof:}
-Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
-$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
-the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
-We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
-$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
-we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
-\overline{P}]^{\vert \mcI^j\vert})$
-is a product of closed subsets of compact sets. Now, we have that a closed
-subset of a compact set is compact and the resulting product topology gives
-Tychonoff's theorem. every product of a
-compact space is compact, we have $\g_i \circ B_i^\epsilon$
-is compact subset of $B_i^\epsilon$.
- Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
-definition of $\Delta$ and the product, 
-\begin{align*}
-    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
-    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
-[0,\overline{P}]\bigg)
-    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
-[0,\overline{P}]\bigg) \\
-    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
-\times \lambda^j \subset T.
-\end{align*}
-The result follows from the fact that $t_i$ is continuous in $s_i$, as was
-proven in \cite{semret}, and as a finite union of compact sets is a compact set.
-$\qed$
-on any subset $\lbrace
-s_{-i}\in S_i : \ \forall \ z > 0, \overline{P} \ge P_i(z,s_{-i}) \ge
-\underline{P} \rbrace$, where $0<\underline{P}\le \overline{P} < \infty$
-(HERE) The dimension of a linear space is defined as the maximal number of linearly
-independent vectors or, equivalently, as the minimal number of vectors that span
-the space
-
-%We have proven that buyers will submit bids according to their marginal
-%valuations. Now, in the interest of completeness (BAD SENTENCE), 
-We have that all bids represent $\epsilon$-best replies, and, as was proven in
-\cite{lazar}, the sellers' positive reserve price implies that bids are
-truthful. Finally, by properties determined by the construction of a mixed strategy
-symmetric game with a 2-dimensional message space, we may now restrict our
-analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.
-
-{
-\corollary{Hemicontinuity of $\Delta$}
-}
-
-The data-sharing market consists of inter-dependent sets of these
-multi-auction games around possible fixed points.  Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
-between the different subsets $\Delta$ form a sufficiently connected set that
-the heirarchy described in Proposition \ref{userunion} holds. Then,
-there can only be a single primary fixed point, where the sellers' reserve
-price is an equilibrium price in the global market. 
-We first address the analytical approach, and demonstrate properties of
-$\Delta$ as a finite-dimensional linear topological space. We have that the
-reserve price of the sellers, and the bid price of the buyers is constant
-within an interval of length 2$\epsilon$. We have that 
-(HERE) We have the following
-Corollary, (MIGHT NEED TO REDEFINE.. NOT CLEAR IS A SEQUENCE, SHOULD BE
-SEQUENCE OF PRICES INSTEAD OF USERS?) 
-{
-\corollary{(Primary fixed point)}
-Let the set of shared buyers be denoted as,
-$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
-sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
-$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
-\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
-for a fixed time $t$,
-$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
-k\ne j\in\overline{\Lambda}$. 
-}\\
-(CAN PROBABLY USE ALL BUYERS HERE... BECAUSE OF INF)
-\textbf{Proof:}
-We assume a finite number of users, with continuous valuation functions bounded both
-above and below. From the assumption that $\overline{\Lambda}$ is not a
-partition, we have that the limits exist with respect to bid price $p_i^j$, 
-$$
-    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
-$$
-is the primary seller $j$, and we have the market price $p_*^j$ from,
-$$
-    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
-\lambda^k,
-$$
-and the result follows from Lemma \ref{uservaluation}, Proposition
-\ref{userunion} and Proposition \ref{incentive}.
-(NEED TO SHOW THEY ARE EQUAL...)
-%$\qed$\\
-(USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
-
-We show that our bidding strategy is
-part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
-equilibrium, where the sellers reserve prices are fixed.
+For a single buyer-seller interaction, (\ref{jtoi}) gives that $\theta_i =
+\theta^j \Rightarrow \theta_i' = {\theta^j}'$. Thus, we have by symmetry, as the buyers' bids are
+truthful, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
+and cannot sell more data than the buyers' aggragated bid quantities.
+The result follows by Lemma \ref{userunion} and Lemma \ref{buyercoordinate}.\\
+
+The data-sharing market consists of a inter-dependent sets of these
+multi-auction games around fixed points. We have that $\Delta$ is defined by a seller $j\in\mcI$, where each
+user $k\in\Delta$ has some direct or indirect influence on $j$. 
+We may identify $\Delta$ by its dominant seller. Let $\Delta^j$ denote $j$'s
+influencing sets. Clearly, the union of all possible
+sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. Consider two subsets, $\Delta^j$
+and $\Delta^k$, at equilibrium, and a shared
+buyer $i\in (\lambda^j \cup \lambda^k)$, where
+$\lambda^j\subset\Delta^j$, and  $\lambda^k\subset \Delta^k$.  By Lemma
+\ref{userunion}, a transition is induced in $\Delta^k$ by $\Delta^j$ if and only if
+$\exists \ l \in \Lambda^j$ such that $p_*^{l} > p_*^{q}$, for some
+$q\in\Lambda^k$. We claim that the shared buyers
+between the different subsets $\Delta$ form a heirarchical structure, and that
+there can only be a single primary fixed point, and this seller determines
+the equilibrium price in the global market. Consider a subset $\Delta^j$. Clearly, if $i^*$, from Proposition
+\ref{sellerstrategy}, increases its valuation,
+then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider a
+seller $k^*\in\mcI_{i^*}$. Since $p_{i^*}^j <
+p_*^j$, we have that $k^*\ni\Lambda\subset \Delta^j\Rightarrow \mcI^{k^*} \ni
+\lambda$. Now, suppose at the end of some time step, $p_*^{k^*} > p_*^j$, and
+consider a buyer $l^*\in\mcI^{k^*}$. Clearly, if $l^*\in\mcI^j$, then $j$'s
+valuation wil increase. Suppose $l^*\ni\mcI^j$, from Proposition \ref{userunion}, if $l^*\in\mcI^k\subset
+\Delta^j$, for some $k\in\mcI_i$, where $i\in\Delta^j$, then either
+$k^*\ni\mcI_i$ or $\exists \ q\in\mcI_i$ such that $p_*^q \ge p_*^{k^*}$. In
+the former case, the valuation of $k\in\mcI_i$ and $j$ will increase.
+In the latter case, $p_*^q \ge p_*^{k^*}$ for some
+$q\in\mcI_i$, and then only the valuation of $j$ will increase. We have that $j$ is
+directly influenced by our choice of seller $k^*$, and observe that
+$i\in\mcI^j$ is free to increase its valuation within $\Delta^j$. 
+Now, consider the set of sellers across all $\Delta$,
+$\bigcup_{j\in\mcI}\Lambda^j$.
+
+%Consider
+%again $q\in\mcI_i$, and the subset $\Delta^q$, where $p_*^q \ge p_*^j$, and
+%a buyer $l\in\lambda\subset\Delta^q$ chosen in the same way as $l^*$.
+
+A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
+profile $s$,
+from which no player has a unilateral incentive to deviate (Johari, 2004)
+(EXPAND)
+We first show the existence of a \emph{static} Nash equilibrium, where buyers have fixed reserve
+prices.
+
 {
 \lemma{(Static Nash Equilibrium)} 
-Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
-let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
-sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
-Using the rules of the data auction mechanism applied independently by each
-user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
-}\\
-\textbf{Proof:}
-(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
-As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
-$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
-$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
-represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
-and we may use Brouwer's fixed point theorem, as in \cite{semret},
+}
 
 As a result of user behavior, and subsequent strategies, we determine that the
-data-exchange market behaves in a predictable way. However,
+global data-exchange market behaves in a predictable way. However, as
 each auction may be played on the same or on a different scale in
-valuation, time and quantity, and so the rate at which market fluctuations occur is
+valuation, time and quantity, the rate at which market fluctuations occur is
 impossible to predict (NEED HELP!). 
@@
 strategy, and provides the right incentives for the truthful revelation of individual preferences. 
-
-The rules of the PSP
-multi-auction drive market mutations that evolve and are regulated by the user
-strategies.
-(HERE)
-
-(DEFINITION.. USE?)
-In the General Symmetric Game, p is an evolutionarily stable mixed strategy if
-there is a (small) positive number y such that when any other mixed strategy q
-invades p at any level x < y, the fitness of an organism playing p is strictly
-greater than the fitness of an organism playing q.
 (EXPAND)
@@
 {
-\theorem{(Dynamic Nash Equilibrium)}
+\theorem{(Nash Equilibrium)}
 Using the rules of the data auction mechanism, the CMHK
@@
 Formally, the
-mechanism is efficient, if, at equilibrium, the allocation maximizes
+mechanism is equilbriumcient if at equilibrium, the allocation maximizes
 $\sum_i\theta_i(a_i)$.
@@
 
-\bibitem{maille}
-Patrick Maillé.
-\textit{Market Clearing Price and Equilibria of the Progressive Second Price
-Mechanism},
-RAIRO - Operations Research, EDP Sciences, 2007, 41 (4), pp.465-478.
-
 \end{thebibliography}

### 2019-08-21 April/paper_varrho.tex
On hold.

--- 2019-08-21 April/paper_recovered.tex
@@
-%\documentclass[journal,comsoc]{IEEEtran}
-\documentclass[sigconf, anonymous]{acmart}
-
-%\usepackage[text={6in,8.1in},centering]{geometry}
+\documentclass[12pt]{article}
+
+\usepackage[text={6in,8.1in},centering]{geometry}
 
@@
 
-\newcommand{\vs}{\varsigma}
-\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcI}{\mathcal{I}}
-\newcommand{\g}{\sigma}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-\iffalse
+\lstset{ %
+language=C++,               
+basicstyle=\footnotesize,
+numbers=left,                  
+numberstyle=\tiny,     
+stepnumber=1,         
+numbersep=5pt,         
+backgroundcolor=\color{white},  
+showspaces=false,               
+showstringspaces=false,         
+showtabs=false,                 
+columns=fullflexible,
+frame=single,          
+tabsize=2,          
+captionpos=b,       
+extendedchars=true,
+xleftmargin=17pt,
+framexleftmargin=17pt,
+framexrightmargin=17pt,
+framexbottommargin=4pt,
+breaklines=true,       
+breakatwhitespace=false, 
+escapeinside={\%*}{*)}       
+}
+
+\newenvironment{block}{\begin{adjustwidth}{1.5cm}{1.5cm}\noindent}{\end{adjustwidth}}
 
@@
 
+\def\verbatimtabsize{4\relax}
+\def\listingoffset{1em}
+\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
+\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
+\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}
+
+\newcommand{\vs}{\varsigma}
+\newcommand{\mcL}{\mathcal{L}}
+\newcommand{\mcI}{\mathcal{I}}
+\newcommand{\g}{\sigma}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
+
 \headsep25pt\headheight20pt
-\setcounter{secnumdepth}{4}
+
 \pagestyle{fancyplain}
@@
 \cfoot{\ \hfill\tiny\sl Draft printed on \today}
+
 \setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
 
-\fi
-
-%---------------ACM CCS---------------------%
-\fancyhf{} % Remove fancy page headers 
-\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
-\fancyfoot[C]{\thepage}
-
-\setcopyright{none} % No copyright notice required for submissions
-\acmConference[?]%Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
-\acmYear{2017}
-
-\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
-%-------------------------------------------%
-
 \begin{document}
-%\begin{multicols}{2}
-\title{Title?}
-
-\begin{abstract}
+\begin{multicols}{2}
+
+\section{Abstract}
+
 We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
@@
 market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
-\end{abstract}
-
-\iffalse
-% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002978.10003029.10011703</concept_id>
-<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
-
-\keywords{template; formatting; pickling} % TODO: replace with your keywords
-\fi
-\maketitle
 
@@
 
-(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
-SENTENCES)
 In this work, we propose \emph{a distributed progressive second price (PSP) auction in
@@
 
-Our mechanism allows a buyer
+In a multi-auction market, each auction a buyer joins has the potential to
+decrease the potential cost of its data, in exchange for additional messaging overhead, possible
+fees, and increased competition from other buyers. This aspect of
+a user transaction represents potential \emph{indirect} costs, which may be considered work done to find
+sellers, monetary fees, or effort of communication from participation. A seller
+has the potential for greater profit with each new buyer in its auction, with
+the same liabilites. We
+define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
+and the individual. We denote the potential indirect costs of participation of
+each user as $\varrho$. Our mechanism allows a buyer
 to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
@@
 \begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ (\g_i(a)) - c_i,
+    u_i = \theta_i \circ (\g_i(a)) - \g_i(\varrho) - c_i,
 \end{equation}
@@
 supply, as this is public information, however only buyers
-are able to determine supply or demand across multiple auctions, and then only from auctions
+are able to determine supply or demand across multiple auctions after time $t=0$, and then only from auctions
 in which they participate. \\
@@
 buyer strategy. (FUTURE WORK?)\\
-
-In a multi-auction market, each auction a buyer joins has the potential to
-decrease the potential cost of its data. However, increasing the size of the
-auction implies a certain risk, which we may interpret as a potential and
-definite
-liability. Increasing the number of transactions causes additional messaging
-overhead, fees, and increased competition from other buyers. 
-A transaction also causes potential indirect costs, which may be considered work done to find
-sellers, or effort of communication from participation. A seller
-has the potential for greater profit with each new buyer in its auction, taking 
-the same risk.
-%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
-%and the individual. We denote the potential indirect costs of participation of
-%each user as $\varrho$.
-The liability of any user is naturally absorbed into the bid fee $\epsilon$,
-as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
-dependent on the association between two users and their market positions, in
-addition to the underlying network structure. Now, both sellers and buyers must consider
-the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
-OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)
-
-Elastic valuation functions allow for even infinitesimal changes in the market
-dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
-allows for the analysis of constraints imposed by the user strategies. 
-Buyers may directly impact each other in local market intersections.
-Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
+In order to represent the public platform of the secondary market, we model the ISP as
+a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
+in any auctions. At time $t=0$, a seller $k$ entering the market will have
+submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
+seller does not require a priori demand information to enter the market.
+
+(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
+IMPLICATIONS?)
+We assume that sellers update their bids with the ISP, which is modeled as a
+``buyer" $\kappa$. 
+A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
+knowledge. 
+\iffalse
+A buyer entering the market
+at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
+(SAY BETTER!) is initialized as 
+an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
+probability $\mathcal{P}$,
+$$
+    \mathcal{P}[\epsilon\le X \le \kappa] =
+\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
+ds,
+$$
+where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
+density function of $X$.
+\fi
+%may represent by some homogenous function of degree one (EXPAND?). 
+Thus the auction
+begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
+initializing bid prices.
+
+It is worth mentioning that the \emph{analysis} of the auction as
+a game assumes some forms of demand and supply, in order to derive properties.
+The mechanism itself does not require any knowledge of user demand or
+valuation. 
+\iffalse
+The ISP overage
+charge inducing an upper bound on the sellers' reserve prices implies that
+supply will always be greater than demand, thereby reducing the sellers'
+influence on market dynamics.
+\fi
+
+As the buyer valuation is elastic, even infinitesimal changes in the market dynamics can be
+modeled. This, and the homogenous nature of data in the CMHK market, 
+allows for the analysis of additional constraints imposed by the user
+strategies. Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
 A buyers' valuation of an amount of data represents how much a buyer is willing
 to pay for that amount. 
-This is equivalent to the bid price, given a fixed amount of data,
-satisfying $\theta_i$. We determine the
+This is equivalent to the bid price that
+satisfies $\theta_i$ given a fixed amount of data. We determine the
 buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
@@
 lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers. 
-%We will later show, in Proposition
-%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
-%bids, i.e. using the same bid for all auctions.
-
-A seller only has
+the maximum reserve price amongst the sellers. We will later show, in Proposition
+\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
+bids, i.e. using the same bid for all auctions.
+Using buyer bid quantity $\g_i^j(a)$, from (\ref{opt-out}), 
+we have the following Lemma,
+{
+% BUYER CONSTRAINTS
+\lemma{(Buyer constraints)}\label{buyerconstraints}
+Let $i\in\mcI$ be a buyer with bid, $s_i = (\g_i(a), p_i)$, which must obey
+the following constraints,
+\begin{equation}\label{buyercapmax}
+    \sum_{j\in\mcI} \g^j_i(a) \le D_i,
+\end{equation}
+and, as $i$ is rational, and therefore utility-maximizing, $i$ must have
+sufficient bids $s_i^j > 0$ so that,
+\begin{equation}\label{buyercapmin}
+    \sum_{j\in\mcI} d^j_i \ge D_i,
+\end{equation}
+where $d_i^j$ denotes the bid quantity of seller $j$.
+}\\
+\textbf{Proof:}
+A rational buyer does not want to purchase extra data, as this would be
+equivalent to overpaying, and so (\ref{buyercapmax}) holds. We also assume that
+$i$ wants to fufill their data requirement, and so (\ref{buyercapmin}) implies
+that $i$ submits positive bids to a set of buyers that will be able to fufill
+their demand.
+
+The seller is similarly represented, however a seller only has
 information from buyers in its own auction, and may only be indirectly influenced by
@@
 and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
-price.
-
-The valuation of any user must be modeled as a function of the entire
-marketplace. 
-Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
+price. Now, we determine that, in addition to some natural constraints, the sellers' highest
+``possible" price is conditioned by
+additional restrictions on its pricing function, the motivation for which is
+that a buyer has the choice to opt-out of any auction, and so seller $j$ has an
+incentive to set its reserve price to sell the maximum amount of
+data. Thus we have the following Lemma,
+{
+% SELLER CONSTRAINTS
+\lemma{(Seller constraints)}\label{sellerconstraints}
+Let $j\in\mcI$ be a seller with bid $s^j$, then $j$ must obey the following constraints.
+A bid $s_i^j= (d_i^j, p_i^j)$, to buyer $i$ must be such that,
+\begin{equation}\label{datacapmax}
+    \sum_{i\in\mcI} d^j_i \le D^j,
+\end{equation}
+In addition, for a rational seller, the reserve price must
+satisfy, $\forall \ i\in \mcI$,
+\begin{equation}\label{reservepricemin}
+   p_i^j \ge \min_{i\in\mcI}\big(p_i^j),
+\end{equation}
+and,
+\begin{equation}\label{reservepricemax}
+   p_i^j \le \max_{i\in\mcI}\big(p_i^j).
+\end{equation}
+Finally, as $j$ is rational, $j$ must submit enough bids $s_i^j >0$ so that,
+\begin{equation}\label{datacapmin}
+    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j.
+\end{equation}
+}\\
+\textbf{Proof:}
+The first statement is obvious, 
+a seller cannot sell more data than they have,
+Then, (\ref{reservepricemin})
+follows from the assumption that $j$ is rational, and so utility-maximization
+acts as revenue maximization, a rational seller will not sell its
+data at a price less than the lowest offer. Finally, as a rational seller will
+attempt to maximize profit, and will try and sell all of its data, and so we
+must have sufficient demand
+from the buyers. Therefore, (\ref{reservepricemax}) and (\ref{datacapmin}) hold. Together, (\ref{datacapmax}) and
+(\ref{datacapmin}) address the case where $\sum_{i\in\mcI} \g_i^j(a) >  D^j$. In
+this case, by (\ref{dataallocation}), $j$ may submit a partial bid to a buyer
+$i$ so that $\sum_{i\in\mcI} d^j_i = D^j$.
+
+We proceed to determine the properties and characteristics of the user valuation functions. Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
+distributed across the CMHK market via bids in local auctions. 
+As such, buyer behavior is influenced by opponent bid profiles from multiple auctions.
+We therefore determine that the valuation of any user must be modeled as a function of the entire
+marketplace. Naturally, a buyers' valuation is aggragated over local markets, and the
+sellers' valuation is aggragated over its own auction. We model the valuation of
+users based on the opt-out user behavior, thereby including the buyers'
+influence on the market. We have already introduced the composition $\theta_i
 \circ \g_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
@@
 \theta'(\eta) + \gamma(z-\eta)$.
-$\qed$
-
-Utility is defined by their valuation, and is the basis for user behavior. 
-The sellers' natural utility is the potential
+
+We assume that a buyer wants to minimize the cost of purchasing their data
+requirement, at the same time ensuring they get the full allocation $\g_i(a)$,
+and so must minimally meet $j$'s reserve price. 
+A seller will try to maximize profit, 
+and so will try to sell all of its data.  By Lemma
+\ref{buyerconstraints} and Lemma \ref{sellerconstraints}, we have,
+$d_i^j = \g_i^j(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j =
+\sum_{i\in\mcI} \g_i^j(a) = D^j = D_i$. It is worth observing that this result
+does \emph{not} imply that $s_i=s^j$. 
+Finally, the sellers' natural utility is the potential
 profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
@@
 of mobile data plans is outside the scope of this paper.
-Now, a rational user will try
-to maximize its utility, thus, user incentive manifests as a
-response to market dynamics. A buyer has the choice to
-opt-out of any auction, and as a seller will try to sell the maximum amount of
-data, the highest possible reserve price is conditioned by ``natural" constraints. Utility-maximization 
-acts as revenue maximization for a rational seller, and as cost minimization for a
-rational buyer. Thus, for each user $p_i^j \ge \min\big(p_i^j)$ and $p_i^j \le
-\max\big(p_i^j)$, which holds $\forall \ i, j\in\mcI$ such that $s_i^j>0$.
-Now, rational buyer does not want to purchase extra data, as this would be
-equivalent to overpaying, however $i$ submits positive bids to a set of
-sellers, and a rational seller will attempt to maximize profit, and so will try and sell all of
-its data. Therefore,
-\begin{equation}\label{bidcap}
-    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j \quad\text{and}\quad
-\sum_{j\in\mcI} d^j_i \ge D_i,
-\end{equation}
-which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
-constraint from our formulation.
-Thus, at equilibrium all users are satisfied, and 
-$D^j = D_i$, although we observe that this result
-does \emph{not} imply that $s_i=s^j$.
-
-We further determine that the set of buyers and sellers participating
-in a single equilibrium is bounded by the potential indirect costs of
-participation. We will denote this individual cost to each user as
-$\varrho$. The indirect cost is the portion of the bid fee
-$\epsilon$ that is dependent on the underlying network and the individual.
-Observing that $\varrho$ indirectly effects user utility,
-and therefore acts to establish a natural budget for each user. We give this
-constraint as, 
-\begin{equation}\label{poolbnd}
-    u \le \varrho,
-\end{equation}
-which may be interpreted as the effort a rational user is willing to expend
-on its message space, and serves to limit the size of the buyer/seller pools.
-
-Finally, it is worth mentioning that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, in order to derive properties.
-The mechanism itself does not require any knowledge of user demand or
-valuation. 
+
 \subsection{PSP for Data-Exchange}
+
+We intend to show that our auction
+is rational and achieves the desired VCG properties, as does the original
+formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
+realistic, theoretic, and notational templates, we define optimal strategies for
+CMHK users, and demonstrate that the development of a set PSP auction mechanisms
+in a data exchange setting is able achieve a network equilibrium for cellular data.
 
@@
 is also reasonable to expect that a seller may come close to using their
-entire data cap, and only sell the fractional overage. In this case, a buyer
-must split its bid among multiple sellers. 
+entire data cap, and only sell the fractional overage. In this case, we
+determine that some buyers must split their bids among multiple sellers. 
+A given demand may lead to diffent prices, which emerge directly from the users valuation
+of the resources and their decision strategies. Also, we reason that buyers,
+in addition to fufilling their data requirement, have incentive to join
+multiple auctions in order to compare prices.
+Each seller that buyer $i$ adds
+to its pool potentially decreases $i$'s bid quantity in all other auctions, and
+so each buyer $i\in\mcI$ directly impacts other buyers in auctions where buyers intersect.
 The buyer strategy bids in auctions with the highest quantities first,
@@
 {
-\lemma{(Opt-out buyer strategy)}\label{buyerstrategy}
+\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
 Define any auction duration to be $\tau \in [0,\infty)$. 
@@
 \begin{split}\label{buyercoordinate}
-    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
+    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \\
     %\wedge \sum_{j\in\mcI(n)}&\g_i^j(\varrho) \le \sum_{j\in\mcI(n)} \theta_i^j(\g_i^j(a)) \big\rbrace. 
-    %&\wedge \g_i(\varrho) \le \theta_i(\g_i(a)) \big\rbrace. 
+    &\wedge \g_i(\varrho) \le \theta_i(\g_i(a)) \big\rbrace. 
 \end{split}
@@
 from the new subset $\mcI_i$, submits bids until
-$\sum_{j\in\mcI_i} \g(a)_i^j \ge D_i$, by (\ref{bidcap}).
+$\sum_{j\in\mcI_i} d_i^j \ge D_i$, by (\ref{buyercapmin}).
 Now, we consider the case where a new buyer $k$ with bid
@@
 value of $i$'s bid for $j\in\mcI_i$. In this case, by (\ref{buyercoordinate}),
-$i$ will choose $\mcI_i$ so that, $\g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a)$,
+$i$ will choose $\mcI_i$ so that,
+$$
+    \g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a),
+$$
 and so $\mcI_i$ is large enough to balance the additional demand from
@@
 \theta_i(\g_i(a))$, where the overhead exceeds the current valuation of the
-data. Then, by (\ref{buyerinversedemand}), the valuation of the data increases until either
-the demand is satisfied, the debit from the overhead costs are balanced
-(\ref{poolbnd}), or the upper bound of the sellers' reserve price
+data. Then, by(\ref{buyerinversedemand}), the valuation of the data increases until either
+the demand is satisfied, the debit from the overhead costs are balanced, or the upper bound of the sellers' reserve price
 $p^\kappa$ is reached. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal.
-$\qed$\\
+and we determine that the opt-out strategy is optimal.\\
 \textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
@@
 {
-\lemma{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
+\proposition{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
 Define any auction duration to be $\tau \in [0,\infty)$. 
@@
 Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
-In this case, by (\ref{bidcap}) the seller must notify $i$ of a
+In this case, by (\ref{datacapmin}) the seller must notify $i$ of a
 partial allocation by changing the bid vector at index $i$.
@@
 (\ref{sellerinversedemand}), we have that, $\forall \ z\ge 0$,
-$f_{i^*}(z) < f^j(z) \le f_i(z)$,
+$$
+    f_{i^*}(z) < f^j(z) \le f_i(z), 
+$$
 which holds $\forall \ i \in \mcI^j$, and $\forall \ j \in \mcI_i$.
@@
 equlibirium created by $j$ is independently stable from time $t$ to $(t+1)$.
-$\qed$
 
@@
 {
-\proposition{(Valuation across local auctions)}\label{userunion}
+\lemma{(Valuation across local auctions)}\label{userunion}
 For any $i,j\in \mcI$, 
@@
 and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand from time $t$ to $t+1$ will
+that $p_*^q > p_*^j$. Fixing all other bids, a change in $q$'s valuation from time $t$ to $t+1$ will
 directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
@@
 some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
+\begin{align*}
+    \int_0^{\g_i^j(a)} f^j(z) \ dz &= \theta_i^j \circ \g_i^j(a)\\
+    &= \int_0^{\g_i^j(a)} f_i(z) \ dz,
+\end{align*}
+therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+Furthermore, it follows that,
 \begin{equation}\label{jdemand}
-    \int_0^{\g_i^j(a)} f^j(z) \ dz 
-    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
-\end{equation}
-therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+    \displaystyle\sum_{i\in\mcI^j}\int_0^{\g_i^j(a)} f^j(z) \ dz =
+\sum_{j\in\mcI_i}\int_0^{\g_i^j(a)} f_i(z) \ dz.
+\end{equation}
 
@@
 buyer $i$. 
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q =
-0$ for $q\in\mcI_i$.
+Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q = 0$.
 We have that for any $l\in\mcI^k$ such that $l\ni
@@
 \begin{align}\label{tkeqtl}
-    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
+    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz,
 \end{align}
-Thus, with a slight abuse of notation for clarity,
+and the result follows by construction, and the continuity of $\theta'$:
 \begin{equation}\label{funion-eq}
-    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
-\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
-\end{equation}
-where the result follows by construction, and the continuity of $\theta'$.
-$\qed$
+    \sum_{i\in\lambda}\int_0^{\g_i^j(a)} f^j(z) \ dz = \sum_{j\in\Lambda}\int_0^{\g_i^j(a)} f_i(z) \ dz.
+\end{equation}
 
@@
 
-\subsubsection{Mechanism Realization}
-
-In order to represent the public platform of the secondary market, we model the ISP as
-a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
-in any auctions. At time $t=0$, a seller $k$ entering the market will have
-submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
-seller does not require a priori demand information to enter the market.
-(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
-IMPLICATIONS?)
-We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. 
-A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
-knowledge. 
-\iffalse
-A buyer entering the market
-at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER!) is initialized as 
-an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
-probability $\mathcal{P}$,
-$$
-    \mathcal{P}[\epsilon\le X \le \kappa] =
-\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
-ds,
-$$
-where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
-density function of $X$.
-\fi
-%may represent by some homogenous function of degree one (EXPAND?). 
-Thus the auction
-begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
-initializing bid prices.
+As a result of user behavior, and subsequent strategies, we determine that the data-exchange market is
+semi-partitioned, consisting of unions as in Lemma \ref{userunion}. The unions are inter-dependent in a predictable way. However, as
+each auction may be played on the same or on a different scale in
+valuation, time and quantity, the rate at which market fluctuations occur is
+impossible to predict (NEED HELP!). 
+Arrow's paradox is an impossibility theorem stating that when buyers have three
+or more distinct alternatives (auctions), no deterministic ranking system can
+convert the ranked preferences of users into a market-wide (complete
+and transitive) ranking while also meeting a specified set of criteria:
+unrestricted domain, non-dictatorship, Pareto efficiency and independence of
+irrelevant alternatives. It follows that the case where
+$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
+is disjoint.
+
+Nonetheless, we claim that our mechanism is normative, that irrelevant
+alternatives should not matter, it is practical, uses minimal information,
+strategy, and provides the right incentives for the truthful revelation of individual preferences. 
+(EXPAND)
 
@@
 % SELLER ALGORITHM
-\begin{center}
 \begin{algorithm}[H]
@@
 \end{algorithm}
-\end{center}
 Each time step, $s^j$ is updated it is shared with all
@@
 \end{algorithm}
-\end{center}
 Finally, we give a simple example of convergence to a local market equilibrium, where the buyers are assumed to respond with their
@@
 Then at $t=1$, we have 
-bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}),\\ (20,p^{(2)}),
+bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}), (20,p^{(2)}),\\
 (14,p^{(2)})]$, and so  $(D^{(2)},p^{(2)}) = (85, 1+\epsilon)$, The buyer response is,
@@
 At $t=2$, $(D^{(1)},p^{(1)}) = (65,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}),\\ (40,p^{(1)}), (0,0), (0,0),
+bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0),\\ (0,0),
 (0,0)]$. $(D^{(2)},p^{(2)}) = (25, 1+\epsilon)$. Then,
@@
 At $t=3$, $(D^{(1)},p^{(1)}) = (50,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0), (0,0),
+bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0),\\ (0,0),
 (0,0)]$. $(D^{(2)},p^{(2)}) = (0, 1+\epsilon)$ and $s^{(2)}=[(25,p^{(1)}),
@@
 At $t=4$ the auction ends.\\
-\textbf{Remark:} In the case where market resources do not satisfy (\ref{bidcap}), however as
+\textbf{Remark:} In the case where market resources do not satisfy (\ref{buyercapmin}), however as
 this constraint is not restricted in time, we reason that in the case of
 insufficient data in the market buyers may wait for additional sellers or
-purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, in
+purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, for (\ref{datacapmin}) in
 the case of insufficient demand, where we may assume that data is held at time
@@
 $z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
-$\qed$
 %Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
@@
 With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
-in the global market, and thus denoting $\Gamma= \Lambda \cup \lambda$, we have
+in the global market, and thus denoting $\Gamma= \Lambda \cup \Lambda$, we have
 an equilibrium point in $\Gamma$. 
@@
 exist.
-Finally, as we may consider $\Delta \subset \mcI$ to be a
-multi-auction game, our user strategies form a ``truthful" local game 
-with strategy space restricted to $\epsilon$-best replies from buyers $\in
+{
+\sublemma{Seller cooperation.}
+We claim that, in addition, $s^j$ is both truthful and optimal.
+For a single buyer-seller interaction, (\ref{jtoi}) gives that $\theta_i =
+\theta^j \Rightarrow \theta_i' = {\theta^j}'$. Thus, by symmetry, and as by
+(\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
+and cannot sell more data than the buyers' aggragated bid quantities.
+The result follows by Lemma \ref{userunion} and Lemma \ref{buyercoordinate}.
+}\\
+
+Finally, as we may consider the subset $\Lambda \cup \lambda$ to be a
+multi-auction game, our user strategies form a ``truthful" local game $\subset
+\mcI$ with strategy space restricted to $\epsilon$-best replies from buyers $\in
 \lambda$. Therefore we have that a fixed point in the ``truthful" game is a fixed point for the auction.
-$\qed$\\
-For completeness, we address the sellers bids, and include the following corollary to support our result.
-{
-\corollary{Seller cooperation.}
-We claim that $s^j$ is both truthful and optimal.
-}\\
-\textbf{Proof:}
-For a single buyer-seller interaction, (\ref{jtoi}) gives that $\theta_i =
-\theta^j \Rightarrow \theta_i' = {\theta^j}'$. Thus, we have by symmetry, as the buyers' bids are
-truthful, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
-and cannot sell more data than the buyers' aggragated bid quantities.
-The result follows by Lemma \ref{userunion} and Lemma \ref{buyercoordinate}.\\
-
-The data-sharing market consists of a inter-dependent sets of these
-multi-auction games around fixed points. We have that $\Delta$ is defined by a seller $j\in\mcI$, where each
-user $k\in\Delta$ has some direct or indirect influence on $j$. 
-We may identify $\Delta$ by its dominant seller. Let $\Delta^j$ denote $j$'s
-influencing sets. Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. Consider two subsets, $\Delta^j$
-and $\Delta^k$, at equilibrium, and a shared
-buyer $i\in (\lambda^j \cup \lambda^k)$, where
-$\lambda^j\subset\Delta^j$, and  $\lambda^k\subset \Delta^k$.  By Lemma
-\ref{userunion}, a transition is induced in $\Delta^k$ by $\Delta^j$ if and only if
-$\exists \ l \in \Lambda^j$ such that $p_*^{l} > p_*^{q}$, for some
-$q\in\Lambda^k$. We claim that the shared buyers
-between the different subsets $\Delta$ form a heirarchical structure, and that
-there can only be a single primary fixed point, and this seller determines
-the equilibrium price in the global market. Consider a subset $\Delta^j$. Clearly, if $i^*$, from Proposition
-\ref{sellerstrategy}, increases its valuation,
-then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider a
-seller $k^*\in\mcI_{i^*}$. Since $p_{i^*}^j <
-p_*^j$, we have that $k^*\ni\Lambda\subset \Delta^j\Rightarrow \mcI^{k^*} \ni
-\lambda$. Now, suppose at the end of some time step, $p_*^{k^*} > p_*^j$, and
-consider a buyer $l^*\in\mcI^{k^*}$. Clearly, if $l^*\in\mcI^j$, then $j$'s
-valuation wil increase. Suppose $l^*\ni\mcI^j$, from Proposition \ref{userunion}, if $l^*\in\mcI^k\subset
-\Delta^j$, for some $k\in\mcI_i$, where $i\in\Delta^j$, then either
-$k^*\ni\mcI_i$ or $\exists \ q\in\mcI_i$ such that $p_*^q \ge p_*^{k^*}$. In
-the former case, the valuation of $k\in\mcI_i$ and $j$ will increase.
-In the latter case, $p_*^q \ge p_*^{k^*}$ for some
-$q\in\mcI_i$, and then only the valuation of $j$ will increase. We have that $j$ is
-directly influenced by our choice of seller $k^*$, and observe that
-$i\in\mcI^j$ is free to increase its valuation within $\Delta^j$. 
-Now, consider the set of sellers across all $\Delta$,
-$\bigcup_{j\in\mcI}\Lambda^j$.
-
-%Consider
-%again $q\in\mcI_i$, and the subset $\Delta^q$, where $p_*^q \ge p_*^j$, and
-%a buyer $l\in\lambda\subset\Delta^q$ chosen in the same way as $l^*$.
+
+We determine that the data-sharing market consists of a union of these multi-auction games around fixed points. Clearly, the union of all possible
+sets $\Delta = \Lambda \cup \lambda$ covers $\mcI$. Consider two subsets, $A$
+and $B$, at equilibrium, and a shared
+buyer $k\in \lambda_A \cup \lambda_B$.  By Lemma
+\ref{userunion}, a transition is induced in $B$ by $A$ if and only if
+$\exists \ j \in \Lambda_A$ such that $p_*^{j}\ge p_*^{k}$, for some
+$k\in\Lambda_B$. We claim that the shared buyers
+between the different subsets form a heirarchical structure over the subsets
+$\Delta$.
 
@@
 (EXPAND)
-We first show the existence of a \emph{static} Nash equilibrium, where buyers have fixed reserve
+We first have the static Nash equilibrium, where buyers have fixed reserve
 prices.
@@
 {
-\lemma{(Static Nash Equilibrium)} 
+\lemma{(Static Data Nash Equilibrium)} 
 }
 
-As a result of user behavior, and subsequent strategies, we determine that the
-global data-exchange market behaves in a predictable way. However, as
-each auction may be played on the same or on a different scale in
-valuation, time and quantity, the rate at which market fluctuations occur is
-impossible to predict (NEED HELP!). 
-Arrow's paradox is an impossibility theorem stating that when buyers have three
-or more distinct alternatives (auctions), no deterministic ranking system can
-convert the ranked preferences of users into a market-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives. It follows that the case where
-$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
-is disjoint.
-
-Nonetheless, we claim that our mechanism is normative, that irrelevant
-alternatives should not matter, it is practical, uses minimal information,
-strategy, and provides the right incentives for the truthful revelation of individual preferences. 
-(EXPAND)
 % DATA NASH EQ
 {
-\theorem{(Nash Equilibrium)}
+\theorem{(Data Nash Equilibrium)}
 Using the rules of the data auction mechanism, the CMHK
@@
 
-%\end{multicols}
+\end{multicols}
 

### 2019-08-21 April/paper_wc_recovered.tex
On hold.

--- 2018-04-18 paper_wc_4-12.tex
@@
 , s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents.
+
 Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
@@
 budget, and every user has an elastic demand function.
+
 Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
-an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
+an allocation rule $a(s^j) \in d^j = [d_1^j, \cdots , d_I^j]$, where $a^j_i$ is the quantity allocated
 by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
@@
 
-% MECHANISM
-\subsubsection{The Mechanism}\label{mechanism}
-The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
-problem of network bandwidth allocation, and is analyzed as a noncooperative
-game where $i\in\mcI$ agents buy the
-fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
-The market price function (MPF) for a buyer-seller pair is,
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
-    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
-\end{split}
-\end{align}
-and is the of minimum prices a user bids in
-order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is,
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
-\end{split}
-\end{align}
-where $D^j$ is the total amount of bandwith that user $j$ has to offer.
-% DATA ALLOCATION RULE
-For each $i \in \mcI$, the allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
-\end{align}
-Finally, we have the cost of the allocation,
-% DATA COST
-\begin{align}\label{datacost}
-    c_i^j(s) = \displaystyle\sum_{k\ne i} 
-p_k^j \big[a_k^j(0; s_{-i}^j)
-    -a_k^j(s_i^j;s_{-i}^j)\big].
-\end{align}
-
-It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
-equilibria for differentiated services
-allocated between multiple agents when all players bid their real marginal valuation
-of the bandwidth resource. In other words, the PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive
-compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
-principle}, user $i$
+Each user has a \emph{valuation} $\theta(a(s)$, which is the total value of its allocation.
+
+We intend to show that our auction
+is rational and achieves the desired VCG properties, as does the original
+formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
+realistic, theoretic, and notational templates, we define optimal strategies for
+CMHK users, and demonstrate that the development of a set PSP auction mechanisms
+in a data exchange setting is able achieve a network equilibrium for cellular data.
+
+We intend to show that our PSP constraints are
+sufficient to attain the desirable property of truthfullness through incentive compatibility. We
+reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
+principle}, and is a valid progressive second price auction to the extent that buyer $i$
 pays for its allocation so as to exactly cover the ``social opportunity cost"
@@
 revenue \cite{lazar}.
-We have the definition of an elastic valuation function. In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
-\definition{\cite{lazar}}
-A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta(0) = 0$,
-    \item $\theta$ is differentiable,
-    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
-{\theta}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
-
-\section{Related Work}
-
-\section{The Problem Model}
-\subsection{The CMHK Market}
-
-We begin to construct the model for a PSP data auction for  mobile users
-particpating in CMHK's secondary data-sharing market.
-Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
-data from other users. We again define the bidding profile for any user to be 
-$s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
-cellular network. We assume that users are selfish, and therefore
-rational. 
- Users prefer to participate in the secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
-Thus we assume that all users submit bids in order to maximize their
-(private) valuation functions. 
-In general, user preferences are defined by a utility function, $u$, which typically
-represents a users' valuation of an allocation minus the price.
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We will assume that the user valuation satisfies the conditions for an
-\emph{elastic demand function}, as in \cite{lazar}. 
-As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
-the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation.
-A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
-belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
-the bid belongs to a \textbf{seller}.
-Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
-meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
-a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
-auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
-(0,0)$. Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$.
-A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
-quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
-with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
-stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
-by the user type, whether or not they are  a buyer or a seller. 
-To further clarify our analysis, we will emphasize the separation of buyers and
-sellers using
-$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
-In other words, a bid $s^j =
-[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
-secondary market. The notational conventions of the bid vectors are essentially 
-slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
-[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
-Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
-d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
-d_i^j$ represent the
-total amount of data requested by buyer $i$. 
-Finally, we assume that data is a unary resource belonging to the seller, and
-therefore can identify each local auction
-with the identity of the seller $j\in\mcI$.
-
-Consider the grid of bid proiles, $s$, representing the distributed PSP auction
-mechanism in the CMHK market, each buyer $i$ will
-have information from each seller $j$, as well as opponent profiles $s_{-i}$
-from each auction in which it is participating, and therefore
-in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
-$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
-(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
-sellers can only gain information about the market grid by observing buyer
-behavior in their local auction.
-In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
-influence the CMHK market dynamics, with the sellers taking a secondary role
-(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
-
-The main contribution of this work 
-is an auction mechanism inspired by the classic PSP throughput problem. In
-order to apply a distributed PSP implementation to CMHK's secondary market,
-we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the communication
-expense from numerous local auctions trading an infinitely divisible resource.
-We will assume that the cost of participatingn in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. We perform a simple survey of these bid fee models, we
-provide some idea of the expected revenue of the mobile data ISP (NEED
-STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
-market, additionally, the purchased data expires (does not carry to the next
-service period). Therefore, a simple definition of market equilibrium, where
-supply equals demand, is insufficent to complete a comprehensive analysis of
-the CMHK data-exchange market behavior. We will make an attempt to address why
-our formulation at least partially considers some of these issues (BAD), such
-as the impact of the bid fee on user behavior. (MOVE SOME OF THIS UP)
-Finally, we  .... (WHAT? COMPLETE THE THOUGHT)
-
-We claim that the market is
-able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, our mechanism provides the functions
-for the effective communication between the connected users. It was shown in
-\cite{lazar} that a $2$-dimensional message space is sufficient for the PSP
-auction. Using a restricted message space is essential for the distributed
-nature of our design (EXPLAIN), however, as a given message can come from many
-possible types, there is no single
-way to do the transformation from the direct revelation mechanism to the
-desired one. This is equivalent to guessing the
-right direct-revelation-to-desired-mechanism transformation and building it
-into the allocation rule from the start. (FINISH!)
-We claim that in
-this secondary market our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead (and so possibly fees paid to the ISP)
-and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
-with respect to the classic throughput problem.
-
-\subsection{User Behavior}
 
@@
 utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
-its market behavior. In a general sense, $e$ applies our user \emph{strategy}
-to the PSP rules.
+market. We define an \textbf{opt-out
+value}, $e$, as a function that when composed with our user type to describes
+its market behavior. In a general sense, $e$ is %the expectation 
+a function that maps a buyer $i$ to matching seller(s).
+
+We have the transform $e: \mathcal{X} \rightarrow \mathcal{Y}$, where
+$\mathcal{Y} \subset \mathcal{X}$, and any
+composition of the opt-out value $e$ with another function $x \in \mathcal{X}$
+results in the scalar application of $e$ to $x$. In other words, for any
+$x\in\mathcal{X}$, and $\mathcal{Y} \subset \mathcal{X}$,
+$$
+    e\circ x = \begin{cases} e(x), \qquad &x \in \mathcal{Y} \\
+                             0, \qquad &x \ni \mathcal{Y}.
+\end{cases}
+$$
+% OPT-OUT BUYER
+We define a \emph{opt-out buyer} as a user $i\in\mcI$ with quasi-linear utility
+function, the value of the allocation minus the cost,
+\begin{equation}\label{buyerutility}
+    u_i = \theta_i \circ e - c_i,
+\end{equation}
+where $e(\theta_i) : [0, \infty)_{i\in\mcI} \rightarrow [0,\infty)_{i\in\mcI}$. 
+We extend the P2P rules described
+in \cite{semret} to account for a set of \emph{local} data-exchange markets.
 Our reserve price function is determined by the subset of nodes participating in the
@@
 buyers. We demonstrate that as the valuation function of seller $j$ is dependent
-on the buyers demand, and further show evidence of symmetry in the strategies of
-buyers and sellers.
-
-\subsubsection{Buyer Strategy}
-
-% OPT-OUT BUYER
-We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $\theta_i$, the value of the allocation minus the cost,
-\begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ e_i(a) - c_i,
-\end{equation}
-where $e_i : [0, \infty)^I \rightarrow [0,\infty), \ \forall \ i \in \mcI$. 
-We extend the P2P rules described
-in \cite{semret} to account for a set of \emph{local} data-exchange markets.
-
-Suppose the total amount of seller $j$'s data on the network at the instance that
-user $i$ joins the auction is $D^j$. 
-A sellers' allocation cannot exceed the total amount they have available,
-i.e. $\sum_{i\in\mcI} a_i^j \le D^j$. This will hold simultaneously for each $i \in
-\mcI$ if and only if 
-\begin{equation}\label{isp}
-    D^j \ge \sum_{i\in\mcI} \ D_i.
-\end{equation}
-We define the only ``seller" to satisfy (\ref{isp}) to be the ISP.
-We will show that in our
-algorithm, sellers are restricted to subset of buyers $\in\mcI$, and provide a
-buyer strategy defining when a rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
-extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
-We assume that buyers and sellers are separated (a seller does not also buy
-data and vice versa).
-
-Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
-is also reasonable to expect that a seller may come close to using their
-entire data cap, and only sell the fractional overage. In this case, we
-determine that buyers must split their bids among multiple sellers. 
-We propose the following strategy, 
-% BUYER STRATEGY
-{
-\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t\in\tau$. % For any allocation $a$ at time $t$, let
-% OPT-OUT BUYER STRATEGY
-%\begin{equation}\label{opt-out}
-    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
-    %e_i^j(a) \triangleq a_i^j,
-%\end{equation}
-%and define,
-Define the composition,
-$$
-     e_i^j \circ a = e_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity, and the set,
-% MIN SET
-$$
-    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
-n}\sum_{j\in\mcI'} D^j,
-$$
-where buyer $i$ chooses its seller pool by determining $n$, where
-\begin{equation}\label{buyercoordinate}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
-    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
-\end{equation} 
-The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
-fixed $n$ we will denote this subset,
-\begin{equation}\label{sellers}
-    \mcI_i \subset \mcI.
-\end{equation}  
-Now let $j^* = n \le I$, and define,
-\begin{equation}\label{opt-minallocation}
-    e_i(a) \triangleq e_i^{j^*}(a)
-\end{equation}
-$\forall \ j \in \mcI_i$.
-As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
-we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
-}\\
-\textbf{Proof:}
-
-We assume that a buyer wants to fufill their data requirement.
-In the case that there exists a seller who can completely satisfy a buyers'
-demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
-as the set $\mcI_i$ is an ordered set, $i$ may discover 
-$j^*$ by computing $\mcI_i$.
-If we suppose that $D_i >
-\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
-We model the ISP as a seller $\kappa$ with bid $s^\kappa =(D^\kappa, P^\kappa)$,
-where $D^\kappa > D^j, \
-\forall \ j\in\mcI_i$, and
-$P^k$ represents the overage fee for data set by the ISP, which is also the upper bound of the sellers'
-pricing function, and so again (\ref{buyercoordinate}) holds.
-Now consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
-The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
-between all buyers with the same unit price. 
-It is possible that the resulting partial allocation of data to $i$ and $k$
-would not satisfy some demand. As the two cases $i$ and $k$ are the same, we consider such
-a seller $i$. Suppose seller $j$ updates its
-bid to reflect the new data quantity, so that $d_i^{j(t+1)} < d_i^{j(t)}$ (NOTE:
-IS THE DIRECTION OF THE BID CONFUSING?, i.e. $d_i^j$ from buyer (rhs) or seller
-(lhs) unclear? does it matter?) Then, by the definition of $\ell_i$, we can
-only have that $j \ni \mcI_i$, or that $n$ has been increased, and new seller(s)
-enter the pool. 
-Additionally, we consider that at time $(t+1)$, we can have a 
-new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
-words, a new buyer $k$ may enter the market with a better price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
-$n$ so that
-$$
-    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
-$$
-and the subset $\mcI_i$ is large enough to balance the additional demand from
-$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal.
-
-Finally, we note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
-minimal ordered subset where a
-coordinated bid is possible, the reasoning for which we will address in further analysis (Section
-\ref{analysis}).
-
-\subsubsection{Buyer Influence}
-The buyer demand is a key market influence (SILLY SENTENCE), as the buyer
-valuation is elastic, even infintesimal changes in the market dynamics can be
-modeled. $\forall \ y\ge 0$, we determine that the market demand for $D^j$ is given by,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
-\end{equation}
-
-Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-which is distributed across the secondary market via bids in local auctions. 
-Buyer behavior is influenced by opponent bid profiles from multiple auctions.
-The valuation of any user, however, is a function of the entire marketplace.  
-We first define the ``inverse" demand for any buyer $i$,
-% BUYER REVENUE 
-\begin{equation}\label{buyerinversedemand}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-For a given demand $\rho^j$, $f_i$ maps the $z$th unit of data to the lowest
-possible unit price. \\
-\textbf{Remark:} In a coordinated bid, $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Naturally, the coordinated bid is the
-lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers.
-
-The seller is represented by a similar function, however a seller only has a
-single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
-seller we have a more direct interpretation of revenue.
-We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
-% SELLER REVENUE 
-\begin{equation}\label{sellerinversedemand}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-where $f^j$ maps to the highest possible unit data price.
-Thus we have the following Lemma. 
-{
-\lemma{(User valuation)}\label{uservaluation}
-For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
-\begin{equation}\label{singlevaluation}
-    \theta_i^j \circ e_i^j(a) = \int_0^{e_i^j(a)} f_i(z) \ dz,
-\end{equation}
-it follows that 
-\begin{equation}\label{buyervaluation}
-    \theta_i \circ e_i(a) = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-Similarly, seller $j$'s valuation is,
-\begin{equation}\label{sellervaluation}
-    \theta^j \circ e_i(a) = \displaystyle\sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-}
-\textbf{Proof:} 
-We assume that a buyer wants to minimize the cost of purchasing their data
-requirement, at the same time ensuring they get the full allocation $e_i(a)$,
-and so must minimally meet $j$'s reserve price.
-A seller will try to maximize profit for any given allocation $a$,
-and will try to sell all of its data, and so 
-$d_i^j = e_i(a) \Rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
-\sum_{i\in\mcI} e_i(a)$,
-The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
-(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)
-
-We note that except at points of discontinuity, we have
-$P_i(z) = f_i(z)$. This mechanism generalizes Vickrey
-(``second-price") auctions which are for nondivisible objects.
-
-The sellers' natural utility is the potential
-profit $u^j = \theta^j \circ e_i(a) $, where $\theta^j$ is the
-potential revenue from the sale of data composed with each buyers' opt-out
-value, $e_i(a)$. 
-We have chosen to omit the original cost of the data
-paid to the ISP, as a discussion of mobile data plans is outside the scope of this
-paper.
-
-As $j$'s behavior is restricted by
-the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
-{
-% SELLER CONSTRAINTS
-\lemma{(Seller constraints)}\label{constraints}
-Let $j$ be a seller with total data amount $D^j$.
-First, the seller must satisfy the quantity
-constraint, 
-\begin{equation}\label{quantity}
-    d_i^j \ge e_i^j(a)
-\end{equation}
-and
-\begin{equation}\label{budget}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
-\end{equation}
-which implies, for any $i\in\mcI$,
-\begin{equation}\label{partialallocation}
-    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
-\end{equation}
-In addition, for a rational seller, the reserve price must
-satisfy, $\forall \ i\in \mcI$,
-\begin{equation}\label{reserveprice}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
-\end{equation}
-}\\
-\textbf{Proof:}
-The first statement is obvious, 
-a seller cannot sell more data than indicated in their bid, (\ref{budget}) and
-(\ref{partialallocation}) enforce
-a data constraint for the seller. Finally, (\ref{reserveprice})
-follows from the assumption that $j$ is rational, and so utility-maximization
-acts as revenue maximization; a rational seller will not sell its
-data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)
-
-\subsubsection{Seller Strategy}
-In order to to develop the seller strategy, it is necessary we determine 
-that a seller has an incentive to
-accept fractional (CHANGE TO PARTIAL? PICK ONE) bids (i.e. sell a fraction of
-their data $D^j$). Reasonably,
-there may not exist a buyer such that $D_i = D^j$. \cite{zheng} reasons that the seller does not know the exact amount of
-leftover data available, and so they may only sell enough data to ensure that
-they will not become a buyer while they submit their total data overage to the
-secondary market. Buyers are allowed to
-bid both dynamically and asychronously, and as a seller determines allocations using only bids
-in its local market. Therefore, in order to
-maximize the revenue gained per unit of data the seller must respond to the
-varation of competitive bids in its market (MORE? FUTURE WORK? CITE?).
-
-We describe the sellers' \emph{local} auction strategy for allocating its
-data according to the constraints formed by the buyer strategy. As
-local auction is progressive, and influenced by the $\epsilon$-best replies of
-the buyers, we will need the following Lemma. 
-We now define the local auction, which we describe, when coupled with the buyer
-responses, as a progressive game of strategy with incomplete, but perfect
-information (SAY MORE?).
-(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
-
-% SELLER LOCAL STRATEGY
-{
-\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
-For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
-Define
-$$
-    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
-n}\sum_{i\in{\mcI}'} p_i^j,
-$$
-where,
-\begin{equation}\label{sellercoordinate}
-    n = \min( i \ \vert \ i \in\mcI^j(n) : \displaystyle\sum_{i\in\mcI} d_i^j \ge
-D^j),
-\end{equation} 
-We have, for any fixed $n$ at time $t$, a minimal subset 
-of buyers that maximizes $j$'s revenue, which we will
-denote,
-\begin{equation}\label{buyers}
-    \mcI^j \subset \mcI.
-\end{equation} 
-Define buyer $i^* = n \le I$.
-Then, for time $(t+1)$, set $j$'s reserve price as 
-\begin{equation}\label{newprice}
-    p_i^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon,
-\end{equation}
-Let the winner at time $t$ be determined by,
-\begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i\in I^j} p_i^j,
-\end{equation}
-and update $j$'s total data to reflect the (tentative) allocation,
-\begin{equation}\label{newbudget}
-    D^{j(t+1)} = D^{j(t)} - e_{\bar{i}}^{j(t)}(a),
-\end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
-%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
-market equilibrium. (BLAST I RUINED THE EQ) % from time $t$ to $(t+1) \in \tau$. 
-}\\
-\textbf{Proof:}
-We assume that the seller has enough data to satisfy at least one buyer,
-and that they want to maximize their revenue.
-In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}), where $i^*$ loses by: (1)
-$i^*$ is excluded from $I^j$ or (2) $i^*$s demand is not met, noting as well
-that any $i\ni \mcI^j$ is also a loser. 
-In this case, by (\ref{quantity}) the seller must notify the buyer of a
-fractional allocation.
-
-%As the set of buyers is
-%computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
-%at equilibrium as it is designed so that the data offered by
-%seller $j$ equals the aggregate demand of the buyers \cite{???}
-With this caveat, we have that the aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
-Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that the buyer is bidding truthfully, and so ${\theta_i}' + \epsilon
-=p_i^j + \epsilon$, and as $\mcI^j\subset \mcI$, we
-note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
-(\ref{singlevaluation}), we have, $\forall \ z\ge 0$,
-\begin{align*}
-    \int_0^{e_{i^*}^j(a)} f_{i}(z)\ dz &\le\int_0^{e_i^{j}(a)}
-f^{j}(z) \ dz 
-\end{align*}
-and so,
-$$
-     \theta_i \circ e_{i^*}(a) \le \theta_i \circ e_i(a),
-$$
-which holds $\forall \ j \in \mcI_i$.
-It follows that, using
-%, using (\ref{buyercoordinate}), 
-the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
-for any $\epsilon$-best reply, 
-$$
-    p_i^j \le {\theta_i}'(v_i^j) + \epsilon,
-$$
-$\forall i \in \mcI^j$.
-Therefore the choice of $p_i^j$ does not force any buyers out of the local
-auction. Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
-equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-We note the special case where for winner $\bar{i}$, $\ \exists \ k\in\mcI^j$
-such that $p_{\bar{i}}^j =
-p_i^k$. In this case the seller again notifies the buyers of a fractional
-allocation by changing $d_i^j$ and $d_k^j$ to reflect the proportional
-division. Finally, in the case where winning buyer(s) \emph{opts-out} of the local
-auction, where $j\in\mcI_i$ at time $t$, then at time $(t+1)$ $j\ne \mcI_i \Rightarrow s_i^{j(t+1)} = (0,0) \Rightarrow i \ne
-\mcI^j$, which is mathematically analogous to the definition of opting-out in our
-scenario. The seller may simply return the tentatively allocated data to $D^j$,
-and recompute $\mcI^j$ and $p_{i^*}^j$, 
-$$
-    D^{j(t+1)} = D^{j(t)} + \displaystyle\sum_{i\in\Gamma} d_i^{j(t)}
-$$
-where $\Gamma$ represents the buyers who have opted-out from time $t$ to 
-$(t+1)$, indicated by a zero bid from any buyer $\in \mcI^j$:
-$$
-    \Gamma = \lbrace i\in \mcI^j : s_i^{j(t+1)} = 0\rbrace.
-$$
-
-(NOTE - NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK IN
-FRACTIONAL ALLOCATIONS? SAVE FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
-
-We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. Consequentially, we have the following Lemma.
-
-% USER UNION
-{
-\lemma{(Valuation across local auctions)}\label{userunion}
-For any $i,j\in \mcI$, 
-\begin{equation}\label{jtoi}
-j\in\mcI_i \Leftrightarrow i\in\mcI^j.
-\end{equation}
-Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
-\begin{equation}\label{lambda}
-    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
-\end{equation}
-and for each $i\in\mcI^j$ define,
-\begin{equation}\label{ilambda}
-    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
-\bigg).
-\end{equation}
-(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
-\equiv s_i^j \in \mcI$)
-Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
-\begin{equation}\label{sym}
-    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
-\end{equation}
-(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
-HAPPEN)
-}\\
-\textbf{Proof:}
-A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $p_i^j \ge p_{i^*}^j$.
-Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
-If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
-Proposition \ref{buyerstrategy}, $i^*$
-will add sellers to its pool until its demand is satisfied. Therefore for any
-$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
-holds.
-
-The subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
-coordinated, truthful bid, $\mcI_i\subset \mcI$ 
-will determine the unit price $p_{i}$ in buyer $i$'s bid.
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price, which in turn defines $j$'s reserve price, $p_{i^*}^j$,
-the lowest price that $j$ will accept to perform any allocation.
-Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy},
-we have that for each $i \in \mcI^j$, 
-$p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
-Let $p_*^j=p_{i^*}^j$ denote the reserve
-price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$.
-Now, we have,
-%Fix any buyer $i\in\mcI^j$.
-\begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-and, $\forall \ i \in \mcI^j$, 
-\begin{equation}\label{invrho}
-    f_i \circ e_i^j(a) \ge p_*^j,
-\end{equation}
-and, $\forall \ k \in \mcI_i$, 
-\begin{equation}\label{invrho}
-    p_*^j \ge f^k \circ e_i^k(a) ,
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-
-The sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
-%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
-for any $k\ne j \in \mcI_i$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
-$\forall \ i \in \mcI^j$,
-\begin{equation}\label{feq}
-    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
-\end{equation}
-where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
-Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
-Since,
-$$
-    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
-$$ 
-there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
-we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
-It follows that buyer $i$'s bid price is given by,
-\begin{equation}\label{iprice}
-    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
-\end{equation}
-
-%where $p_i^*$ represents $i$'s coordinated bid price,
-%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
-This holds for any
-$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
-Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
-denote each as $f$ in the remainder of the proof.
-
-Now, using (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
-$i\in\mcI^j$ to be, (HERE)
-(SHOW THAT $\Lambda$ IS DISJOINT!)
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p_*^k) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^k$ is the highest unit price in the feasible set $\mcI_i\cup\mcI_k$.
-Thus we determine the aggregate demand from buyer
-$i\in\mcI^j$ over the set of intersecting markets $\Lambda$ to be, 
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p^*) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^* = \max(p^k), \ \forall \ k \in\Lambda$, and corresponds to the
-highest reserve price over all the sellers. 
-Now, by the continuity of $\theta'$, (AND)
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\mcI_i\cup\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &=\displaystyle\sum_{i\in\mcI^j} \theta_i \circ e_i(a) \\
-     &= \sum_{k\in\mcI_i\cup\mcI^j}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &= \sum_{k\in\mcI_i\cup\mcI^j}\theta^j \circ e_i(a)\\
-     &= (\theta_i \circ \theta^j) \circ e_i(a).
-\end{align*}
-
-\iffalse
-************************
-Proposition \ref{buyerstrategy} defines $e_i^j(a) = D_i/ 2$, and so $0 <
-e_i^j(a)$.
-************************
-\fi
-\iffalse
-Suppose $\exists \ i \in\mcI^j$ such that $\mcI_i = j$, so that $j$ is the only
-seller in $\Lambda$.
-, and $i$'s bid quantity,
-\begin{equation}\label{iquantity}
-    d_i^* = \circ e_i(a) = \frac{a_i^j}{j},
-\end{equation}
-where $j=j^* = \argmin$ for each $i\in\mcI^j$, thus $d_i^*$ represents $i$'s coordinated bid quantity, and we have
-$s_i^j = (p_i^*,d_i^*), \ \forall \ j$ such that $s_i^j > 0$,
-\fi
-\iffalse
-
-*****************************************************************************************************
-From (\ref{jtoi}), $i\in\mcI^j \Rightarrow
-j\in \mcI_i$, so $i\in \mcI^j \cup \mcI^j$, 
-Using (\ref{buyerinversedemand}), we have the valuation of $j\in\mcI_i$,
-%$i\in\bigcap_{i\in\mcI^j}\mcI_i$,
-\begin{align*}
-      \theta^j \circ e = \sum_{k\in\mcI_i\cup\mcI^j}}&\int_0^{e_i^k(a)} f(z) \ dz,
-\end{align*}
-and by (\ref{sellerinversedemand}), we have the valuation of $j$ fixed, 
-\begin{align*}
-      \theta^j \circ e = \sum_{i\in\mcI^j}&\int_0^{e_i^j(a)} f(z) \ dz,
-\end{align*}
-and thus we have the valuation of $\Lambda^j$,
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} \bigg(\sum_{k\in\Lambda}&\int_0^{e_i^k(a)}
-f(z) \ dz\bigg).
-\end{align*}
-\\(FINISH!)\\
-$$
-     \displaystyle\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg).
-$$
-----------------HERE--------------\\
-(HOW TO MAKE SETS THE SAME???)
-Now we consider $\Lambda_i$. For each buyer $i\in\mcI^j$, we have that $p_i^j
-\ge p_i^k$
-
-Now, for $\Lambda_i \cap \Lambda^j$, and by the continuity of $\theta'$,
-\begin{align*}
-     \displaystyle\sum_{i\in\mcI^j} &\bigg(\sum_{k\in\Lambda_i}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-     &= \sum_{k\in\Lambda_i}\bigg(\sum_{i\in\mcI^j}\int_0^{e_i^k(a)}
-f(z) \ dz\bigg)\\
-      &= \sum_{k\in\Lambda^j}\bigg(\sum_{j\in\mcI_i}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg)\\
-      &=\sum_{j\in\mcI_i} \bigg(\sum_{k\in\Lambda^j}\int_0^{e_k^j(a)}
-f(z) \ dz\bigg).
-\end{align*}
-
-(WHAT?)\\
-Therefore, $\Lambda$ is such that $j\ni \mcI_i, \ \forall \ i \ni \mcI^j$. In other words, $\Lambda$ is a
-disjoint set in the global marketplace with respect to $j$.
-****************************************************************************************************
-\fi
-
-For completeness, in the case where the ISP $\kappa$ 
-does not adhere to the market dynamics, so $P^\kappa > p^j +
-\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
-bid fee.
-
-(ADD TIME? INDUCTION GOES HERE? DID NOT SHOW!)
-
-(OWN
-WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
-competing in multiple local auctions hosted by the sellers, the two games are
-inter-dependent, and may be played on the same or on a different scale in
-valuation, time (AND....).
-
-PSP relies on the \emph{relevation prinicple}; the
-PSP mechanism is able to demonstrate equlibrium by showing that PSP is
-incentive-compatible. (MORE?)
-Arrow's paradox is an impossibility theorem stating that when voters have three
-or more distinct alternatives (options), no ranked voting electoral system can
-convert the ranked preferences of individuals into a community-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives.
-
-Thus, (WHAT? FINISH, OWN WORDS)
-The designer of a mechanism generally hopes either to design a mechanism
-y() that "implements" a social choice function to find the
-mechanism y() that maximizes some value criterion (e.g. profit)
-Independence of irrelevant alternatives (IIA)
-The IIA condition has three purposes (or effects)
-
-Normative
-Irrelevant alternatives should not matter.
-Practical
-Use of minimal information.
-Strategic
-Providing the right incentives for the truthful revelation of individual
-preferences.
-
-\subsection{PSP Formulation}
-
-We intend to show that our auction
-is rational and achieves the desired VCG properties, as does the original
-formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
-realistic, theoretic, and notational templates, we define optimal strategies for
-CMHK users, and demonstrate that the development of a set PSP auction mechanisms
-in a data exchange setting is able achieve a network equilibrium for cellular data.
+on the buyers demand, that the strategies of buyers and sellers may differ
+drastically depending on the market.
+
+\section{Related Work}
+
+\section{The Problem Model}
+\subsection{The Secondary Market}
+
+We define the set of users, $\mcI = \lbrace 1, \cdots, I\rbrace$, who purchase or sell
+data from other users. A buyer submits bids directly to sellers, where we
+assume that all users submit bids in order to maximize their
+(private) valuation functions.
+
+(TERRIBLE, FUTURE WORK) public information in the
+secondary market consists of a set of offers that are published by users
+wishing to sell their data overage.
+
+A user's identity $i \in \mcI$ as a subscript indicates that the user
+is a buyer, and a superscript indicates the seller.
+Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
+meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
+a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
+auctions; if a user $i$ does not submit a bid to $j$, we simply set $s_i^j = (0,0)$.
+A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
+quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
+with reserve unit price $p^j = [p_i^j]_{i\in\mcI}$. $D^j = \sum_{i\in\mcI}
+d_i^j$ is the total amount and $D_i = \sum_{j\in\mcI} d_i^j$ is the
+total amount of data required by a buyer $i$. Naturally, we define $P_i$ and
+$P^j$ in the same way.
+We emphasize that we allow for $s_i^j$ to
+stand for a buyer or sellers' bid, determined by whether or not the user is a
+buyer or seller. In other words, a bid $s^j$, the bid is understood as an offer in the secondary
+market; we assume that data is a unary resource belonging to the seller, and
+therefore can identify the data (for sale) with the identity of the user.
+To further clarify our analysis, we will emphasize the separation of buyers and
+sellers by denoting vectors bid as slices of the
+grid, i.e. $s^j = [s_i^j]_{i\in\mcI}$ will denote a sellers' profile, and  $s_i =
+[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
+The notational conventions given by the slices $s_i$
+and $s^j$ will be used indicate if a bid is from a buyer or a seller. However,
+we note that this is a simplification for ease of notation, and considering the
+grid $s$ in a distributed setting, each buyer $i$ will
+have information from each auction in which it is participating, and therefore
+in the limit will have access to the full grid $s$. However, 
+sellers can only gain information about the market grid by observing buyer
+behavior in their local auction.
+In our current formulation, we do not allow a seller to host multiple auctions(FUTURE WORK).
 
 % MECHANISM
-\subsubsection{Data Auction Mechanism}\label{datamechanism}
+\subsection{Data Auction Mechanism}\label{mechanism}
 We now proceed to formally define the PSP auction, which determines the actions 
 buyers and sellers in the secondary market, which we will denote the \emph{data}
-PSP rules. The rules presented here incorporate of the opt-out function with the
-mechanism as in \cite{lazar}, which we note greatly simplifies our
-analysis. 
+PSP rules.
 The market price function (MPF) for a buyer in the secondary market
@@
 \end{align}
-Finally we must have that the cost to the buyer adheres to the second price
+% DATA ALLOCATION RULE
+The resulting data allocation rule is a function of the local market
+interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
+allocation from auction $j$ is,
+% and so for profile $s_i$, for any $i \in \mcI$,
+\begin{align}\label{dataallocation}
+    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
+    &= \min\bigg\lbrace e_i^j\circ D_i,
+    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i\circ D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
+\end{align}
+Finally, we must have that the cost to the buyer adheres to the second price
 rule for each local auction, with total cost to buyer $i$,
@@
 \end{align}
-% DATA ALLOCATION RULE
-The resulting data allocation rule is a function of the local market
-interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
-allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
-    &= \min\bigg\lbrace e_i^j \circ D_i, \\
-    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i \circ
-D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
-\end{align}
-noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool, as in the previous definitions.
-
-\subsubsection{Mechanism Realization}\label{realization}
-
+
+The main contribution of this work 
+is an auction mechanism inspired by the classic PSP throughput problem. In
+order to apply a distributed PSP implementation to CMHK's secondary market,
+we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
+to change their bid strategies, and as each user only has \emph{local}
+information about the bidding environment, it is clear that an unconstrained
+market, even with a finite number of users, could suffer from the communication
+expense from numerous local auctions trading an infinitely divisible resource.
+We will assume that the cost of participatingn in the CMHK secondary market is
+absorbed by the bid fee, which could represent data used in submitting bids, or
+a fee charged per unit of data, or a flat rate charged at the completion of the
+purchase. We perform a simple survey of these bid fee models, we
+provide some idea of the expected revenue of the mobile data ISP (NEED
+STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
+market, additionally, the purchased data expires (does not carry to the next
+service period). Therefore, a simple definition of market equilibrium, where
+supply equals demand, is insufficent to complete a comprehensive analysis of
+the CMHK data-exchange market behavior. We will make an attempt to address why
+our formulation at least partially considers some of these issues (BAD), such
+as the impact of the bid fee on user behavior. (MOVE SOME OF THIS UP)
+Finally, we  .... (WHAT? COMPLETE THE THOUGHT)
+
+We claim that the market is
+able to achieve an equilibrium as the sellers and buyers have an
+incentive for a collaborative exchange, our mechanism provides the functions
+for the effective communication between the connected users. It was shown in
+\cite{lazar} that a $2$-dimensional message space is sufficient for the PSP
+auction. Using a restricted message space is essential for the distributed
+nature of our design (EXPLAIN), however, as a given message can come from many
+possible types, there is no single
+way to do the transformation from the direct revelation mechanism to the
+desired one. This is equivalent to guessing the
+right direct-revelation-to-desired-mechanism transformation and building it
+into the allocation rule from the start. (FINISH!)
+We claim that in
+this secondary market our formulation not only holds the desired VCG qualities,
+but minimizes comminication overhead (and so possibly fees paid to the ISP)
+and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
+with respect to the classic throughput problem.
+
+\section{Distributed PSP Analysis}
+
+\subsection{User Behavior}
+
+We assume that users are selfish, and therefore
+rational. Users prefer to participate in the secondary market as it allows them to purchase
+additional data for a cost less than the overage fee set by the ISP. 
+In general, user preferences are defined by a utility function, which typically
+represents a users' valuation of an allocation minus the price, 
+\begin{align*}
+    u &: S \rightarrow (-\infty, \infty) \\
+          & s \rightarrow u(s).
+\end{align*}
+Absent the cost or revenue from trading data, CMHK users gain utility from consuming
+data. 
+We will assume that the user valuation satisfies the conditions for an
+\emph{elastic demand function}: 
+\definition{\cite{lazar}}
+A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta(0) = 0$,
+    \item $\theta$ is differentiable,
+    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
+     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
+${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
+{\theta}'(\eta)
+- \gamma(z - \eta)$. 
+\end{itemize}
+The user valuation
+
+\subsubsection{Buyer Strategy}
+
+Suppose the total amount of seller $j$'s data on the network at the instance that
+user $i$ joins the auction is $D^j$. 
+A sellers' allocation cannot exceed the total amount they have available,
+i.e. $\sum_{i\in\mcI} a_i^j \le D^j$. This will hold simultaneously for each $i \in
+\mcI$ if and only if 
+\begin{equation}\label{isp}
+    D^j \ge \sum_{i\in\mcI} \ D_i.
+\end{equation}
+We define the only ``seller" to satisfy (\ref{isp}) to be the ISP.
+We will show that in our
+algorithm, sellers are restricted to subset of buyers $\in\mcI$, and provide a
+buyer strategy defining when a rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
+extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
+We assume that buyers and sellers are separated (a seller does not also buy
+data and vice versa).
+
+Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
+is also reasonable to expect that a seller may come close to using their
+entire data cap, and only sell the fractional overage. In this case, we
+determine that buyers must split their bids among multiple sellers. 
+We propose the following strategy, 
+% BUYER STRATEGY
+{
+\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
+Define any auction duration to be $\tau \in [0,\infty)$. 
+Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
+$t\in\tau$. % For any allocation $a$ at time $t$, let
+% OPT-OUT BUYER STRATEGY
+%\begin{equation}\label{opt-out}
+    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
+    %e_i^j(a) \triangleq a_i^j,
+%\end{equation}
+%and define,
+Define the composition,
+$$
+    e_i^j(a) = a_i^j \circ e,
+$$
+and the set,
+% MIN SET
+$$
+    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
+n}\sum_{j\in\mcI'} D^j,
+$$
+where buyer $i$ chooses its seller pool by determining $n$, where
+\begin{equation}\label{buyercoordinate}
+    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
+    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
+    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
+\end{equation} 
+Now let $j^* = n \le I$, and define,
+\begin{equation}\label{opt-minallocation}
+    e_i^j(a) \triangleq e_i^{j^*}(a).
+\end{equation}
+The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
+fixed $n$ we will denote this subset,
+\begin{equation}\label{sellers}
+    \mcI_i \subset \mcI.
+\end{equation}  
+As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
+we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
+}\\
+\textbf{Proof:}
+
+We assume that a buyer wants to fufill their data requirement.
+In the case that there exists a seller who can completely satisfy a buyers'
+demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
+as the set $\ell_i$ is an ordered set, $i$ may discover 
+$j^*$ by computing $\ell_i$. If we suppose that $D_i >
+\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\ell_i = \emptyset$. 
+We model the ISP as a seller $\kappa$ with bid $s^\kappa =(D^\kappa, P^\kappa)$,
+where $D^\kappa > D^j, \
+\forall \ j\in\mcI_i$, and
+$P^k$ represents the overage fee for data set by the ISP, which is also the upper bound of the sellers'
+pricing function, and so again (\ref{buyercoordinate}) holds.
+Now consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
+The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
+between all buyers with the same unit price. 
+It is possible that the resulting partial allocation of data to $i$ and $k$
+would not satisfy some demand. As the two cases $i$ and $k$ are the same, we consider such
+a seller $i$. Suppose seller $j$ updates its
+bid to reflect the new data quantity, so that $d_i^{j(t+1)} < d_i^{j(t)}$ (NOTE:
+IS THE DIRECTION OF THE BID CONFUSING?, i.e. $d_i^j$ from buyer (rhs) or seller
+(lhs) unclear? does it matter?) Then, by the definition of $\ell_i$, we can
+only have that $j \ni \mcI_i$, or that $n$ has been increased, and new seller(s)
+enter the pool. 
+Additionally, we consider that at time $(t+1)$, we can have a 
+new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
+words, a new buyer $k$ may enter the market with a better price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
+$n$ so that
+$$
+    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
+$$
+and the subset $\mcI_i$ is large enough to balance the additional demand from
+$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
+and we determine that the opt-out strategy is optimal.
+
+Finally, we note that $\mcI_i$ is not the only
+possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
+minimal ordered subset where a
+coordinated bid is possible, the reasoning for which we will address in further analysis (Section
+\ref{analysis}).
+
+\subsubsection{Buyer Influence}
+The buyer demand is a key market influence (SILLY SENTENCE), as the buyer
+valuation is elastic, even infintesimal changes in the market dynamics can be
+modeled. $\forall \ y\ge 0$, we determine that the market demand for $D^j$ is given by,
+% BUYER DEMAND 
+\begin{equation}\label{datademand}
+    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
+\end{equation}
+
+Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
+which is distributed across the secondary market via bids in local auctions. 
+Buyer behavior is influenced by opponent bid profiles from multiple auctions.
+The valuation of any user, however, is a function of the entire marketplace.  
+We first define the ``inverse" demand for any buyer $i$,
+% BUYER REVENUE 
+\begin{equation}\label{buyerinversedemand}
+    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
+        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
+\end{equation}
+For a given demand $\rho^j$, $f_i$ maps the $z$-th unit of data to the lowest price at
+which $i$ could still bid in \emph{any} auction $j\in\mcI$.
+Naturally, this is the
+lowest unit cost of the buyer to participate in all auctions, and corresponds to
+the maximum reserve price amongst the sellers.
+
+The seller is represented by a similar function, however a seller only has a
+single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
+seller we have a more direct interpretation of revenue.
+We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
+% SELLER REVENUE 
+\begin{equation}\label{sellerinversedemand}
+    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
+        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
+\end{equation}
+where $f^j$ maps to the highest possible unit data price.
+Thus we have the following Lemma. 
+{
+\lemma{(User valuation)}
+For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
+\begin{equation}\label{singlevaluation}
+    \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
+\end{equation}
+it follows that 
+\begin{equation}\label{buyervaluation}
+    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
+ \int_0^{e_i^j(a)} f_i(z) \ dz.
+\end{equation}
+Similarly, seller $j$'s valuation is,
+\begin{equation}\label{sellervaluation}
+    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
+ \int_0^{e_i^j(a)} f^j(z) \ dz.
+\end{equation}
+}
+\textbf{Proof:} 
+We assume that a buyer wants to minimize the cost of purchasing their data
+requirement, at the same time ensuring they get the full allocation $e_i(a)$,
+and so must minimally meet $j$'s reserve price.
+A seller will try to maximize profit for any given allocation $a$,
+and will try to sell all of its data, and so 
+$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
+\sum_{i\in\mcI} e_i$,
+The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
+(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)
+
+The sellers' natural utility is the potential
+profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
+potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
+We have chosen to omit the original cost of the data
+paid to the ISP, as a discussion of mobile data plans is outside the scope of this
+paper.
+
+As $j$'s behavior is restricted by
+the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
+{
+% SELLER CONSTRAINTS
+\lemma{(Seller constraints)}\label{constraints}
+Let $j$ be a seller with total data amount $D^j$.
+First, the seller must satisfy the quantity
+constraint, 
+\begin{equation}\label{quantity}
+    d_i^j \ge e_i^j(a)
+\end{equation}
+and
+\begin{equation}\label{budget}
+    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
+\end{equation}
+which implies, for any $i\in\mcI$,
+\begin{equation}\label{partialallocation}
+    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
+\end{equation}
+In addition, for a rational seller, the reserve price must
+satisfy, $\forall \ i\in \mcI$,
+\begin{equation}\label{reserveprice}
+   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
+\end{equation}
+}\\
+\textbf{Proof:}
+The first statement is obvious, 
+a seller cannot sell more data than indicated in their bid, (\ref{budget}) and
+(\ref{partialallocation}) enforce
+a data constraint for the seller. Finally, (\ref{reserveprice})
+follows from the assumption that $j$ is rational, and so utility-maximization
+acts as revenue maximization; a rational seller will not sell its
+data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)
+
+\subsubsection{Seller Strategy}
+In order to to develop the seller strategy, it is necessary we determine 
+that a seller has an incentive to
+accept fractional (CHANGE TO PARTIAL? PICK ONE) bids (i.e. sell a fraction of
+their data $D^j$). Reasonably,
+there may not exist a buyer such that $D_i = D^j$. \cite{zheng} reasons that the seller does not know the exact amount of
+leftover data available, and so they may only sell enough data to ensure that
+they will not become a buyer while they submit their total data overage to the
+secondary market. Buyers are allowed to
+bid both dynamically and asychronously, and as a seller determines allocations using only bids
+in its local market. Therefore, in order to
+maximize the revenue gained per unit of data the seller must respond to the
+varation of competitive bids in its market (MORE? FUTURE WORK? CITE?).
+
+We describe the sellers' \emph{local} auction strategy for allocating its
+data according to the constraints formed by the buyer strategy. As
+local auction is progressive, and influenced by the $\epsilon$-best replies of
+the buyers, we will need the following Lemma. 
+We now define the local auction, which we describe, when coupled with the buyer
+responses, as a progressive game of strategy with incomplete, but perfect
+information (SAY MORE?).
+(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
+
+% SELLER LOCAL STRATEGY
+{
+\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
+Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
+For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
+Define
+$$
+    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
+n}\sum_{i\in{\mcI}'} p_i^j,
+$$
+where,
+\begin{equation}\label{sellercoordinate}
+    n = \min( i \ \vert \ i \in\mcI^j(n) : \displaystyle\sum_{i\in\mcI} d_i^j \ge
+D^j),
+\end{equation} 
+We have, for any fixed $n$ at time $t$, a minimal subset 
+of buyers that maximizes $j$'s revenue, which we will
+denote,
+\begin{equation}\label{buyers}
+    \mcI^j \subset \mcI.
+\end{equation} 
+Define buyer $i^* = n \le I$.
+Then, for time $(t+1)$, set $j$'s reserve price as 
+\begin{equation}\label{newprice}
+    p_i^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon,
+\end{equation}
+Let the winner at time $t$ be determined by,
+\begin{equation}\label{winner}
+    \bar{i} = \displaystyle\max_{i\in I^j} p_i^j,
+\end{equation}
+and update $j$'s total data to reflect the (tentative) allocation,
+\begin{equation}\label{newbudget}
+    D^{j(t+1)} = D^{j(t)} - e_{i^*}^{j(t)}(a).
+\end{equation}
+Allowing $t$ to range over $\tau$, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
+%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
+market equilibrium. (BLAST I RUINED THE EQ) % from time $t$ to $(t+1) \in \tau$. 
+}\\
+\textbf{Proof:}
+We assume that the seller has enough data to satisfy at least one buyer,
+and that they want to maximize their revenue.
+In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
+price offer, determined by (\ref{sellercoordinate}), where $i^*$ loses by: (1)
+$i^*$ is excluded from $I^j$ or (2) $i^*$s demand is not met, noting as well
+that any $i\ni \mcI^j$ is also a loser. 
+In this case, by (\ref{quantity}) the seller must notify the buyer of a fractional allocation, so
+$d_{i^*}^j = a_i^j(s) \circ e_i^j$.
+
+%As the set of buyers is
+%computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
+%at equilibrium as it is designed so that the data offered by
+%seller $j$ equals the aggregate demand of the buyers \cite{???}
+With this caveat, we have that the aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
+Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
+that the buyer is bidding truthfully, and so ${\theta_i}' + \epsilon
+=p_i^j + \epsilon$, and as $\mcI^j\subset \mcI$, we
+note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
+(\ref{singlevaluation}), we have, $\forall \ z\ge 0$,
+\begin{align*}
+    \int_0^{e_{i^*}^j(a)} f_{i}(z)\ dz &\le\int_0^{e_i^{j}(a)}
+f^{j}(z) \ dz 
+\end{align*}
+and so,
+$$
+    \theta_i\circ e_{i^*}(a) \le \theta_i\circ e_i(a),
+$$
+which holds $\forall \ j \in \mcI_i$.
+It follows that, using
+%, using (\ref{buyercoordinate}), 
+the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
+for any $\epsilon$-best reply, 
+$$
+    p_i^j \le {\theta_i}'(v_i^j) + \epsilon,
+$$
+$\forall i \in \mcI^j$.
+Therefore the choice of $p_i^j$ does not force any buyers out of the local
+auction. Thus we determine the valuation between seller
+$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
+equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
+We note the special case where for winner $\bar{i}$, $\ \exists \ k\in\mcI^j$
+such that $p_{\bar{i}}^j =
+p_i^k$. In this case the seller again notifies the buyers of a fractional
+allocation by changing $d_i^j$ and $d_k^j$ to reflect the proportional
+division. Finally, in the case where winning buyer(s) \emph{opts-out} of the local
+auction, where $j\in\mcI_i$ at time $t$, then at time $(t+1)$ $j\ne \mcI_i \Rightarrow s_i^{j(t+1)} = (0,0) \Rightarrow i \ne
+\mcI^j$, which is mathematically analogous to the definition of opting-out in our
+scenario. The seller may simply return the tentatively allocated data to $D^j$,
+and recompute $\mcI^j$ and $p_{i^*}^j$, 
+$$
+    D^{j(t+1)} = D^{j(t)} + \displaystyle\sum_{i\in\Gamma} d_i^{j(t)}
+$$
+where $\Gamma$ represents the buyers who have opted-out from time $t$ to 
+$(t+1)$, indicated by a zero bid from any buyer $\in \mcI^j$:
+$$
+    \Gamma = \lbrace i\in \mcI^j : s_i^{j(t+1)} = 0\rbrace.
+$$
+
+(NOTE - NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK IN
+FRACTIONAL ALLOCATIONS? SAVE FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
+
+We conclude this section by examining the relationship between the strategies of buyers and
+sellers in local auctions. As we have shown, the seller
+is a functional extension of the buyer, with rules determined by the buyers'
+behavior. Consequentially, we have the following Lemma.
+
+{
+\lemma{(Valuation in local auctions)}
+For any buyer $i$, $s_i^j > 0 \equiv j\in\mcI_i \Rightarrow i\in\mcI^j$. 
+Define any auction to be the set of users,
+\begin{equation}
+    \mcI_i \cap \mcI^j.
+\end{equation}
+We have that there exists a strategic local market equilibrium.
+}\\
+\textbf{Proof:}
+A local auction $j\in\mcI$, is determined by the collection of buyer bid
+profiles, where if $s_i^j > 0$, so $j\in\mcI_i$, we have that $i\in\mcI^j$. 
+The subset $\mcI^j \subset \mcI$
+determines $j$'s reserve price $p_{i^*}^j$. Similarly, $\mcI_i\subset \mcI$ 
+determines the (coordinated) unit price $p_{i}$ in buyer $i$'s bid.
+ For each $j$,
+(\ref{sellercoordinate}) defines $i^*$ as the first losing buyer in the ordered
+set $\ell^j$, and reserve price, $p_{i^*}^j$, which is by definition the lowest price that $j$
+will accept to perform any allocation. 
+We have that for each $i \in \mcI^j$, (LIPSCHITZ)
+$$
+   f_i(z) = \inf\bigg\lbrace y \ge 0 : \rho_i^j(y) \ge z,\
+\forall \ j\in\mcI_i\bigg\rbrace,
+$$
+and so $y\ge p_{i^*}^j > 0, \ \forall \ j\in\mcI_i$.
+% with $i$'s bid price $[p_i]_{j\in\mcI_i} \equiv [y]_{j\in\mcI_i}$. 
+The buyers determine the reserve prices (and thereby dynamics), of each local
+auction (MORE). 
+It follows that either $i\in\mcI^j$ or $i = i^* \in \ell^j$ in any local market
+where $s_i^j \ne 0$. If $i^* \ni \mcI^j$, then the local auction is at
+equilibrium; we need only consider the latter case. By
+Proposision \ref{buyerstrategy}, $i^*$
+will add sellers to its pool until its demand is satisfied. As this holds true
+for any $i^* \in \mcI$ and some $j\in\mcI$, we must have that every auction
+achieves a local equilibrium. 
+(ADD TIME? INDUCTION GOES HERE?)
+
+For completeness, in the case where, for some buyer $i\in \mcI$, $D^{j^*}\vert
+\mcI_i\vert < D_i$, and the ISP $\kappa$ with bid $s^\kappa =(D^\kappa,
+P^\kappa)$ does not adhere to the market dynamics, so $P^\kappa > p_{i^*}^j +
+\epsilon, \ \forall j \in\mcI$, then we may absorb the overage (difference) as part of the
+bid fee.
+
+(OWN
+WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
+competing in multiple local auctions hosted by the sellers, the two games are
+inter-dependent, and may be played on the same or on a different scale in
+valuation, time (AND....).
+
+PSP relies on the \emph{relevation prinicple}; the
+PSP mechanism is able to demonstrate equlibrium by showing that PSP is
+incentive-compatible. (MORE?)
+Arrow's paradox is an impossibility theorem stating that when voters have three
+or more distinct alternatives (options), no ranked voting electoral system can
+convert the ranked preferences of individuals into a community-wide (complete
+and transitive) ranking while also meeting a specified set of criteria:
+unrestricted domain, non-dictatorship, Pareto efficiency and independence of
+irrelevant alternatives.
+
+Thus, (WHAT? FINISH, OWN WORDS)
+The designer of a mechanism generally hopes either to design a mechanism
+y() that "implements" a social choice function to find the
+mechanism y() that maximizes some value criterion (e.g. profit)
+Independence of irrelevant alternatives (IIA)
+The IIA condition has three purposes (or effects)
+
+Normative
+Irrelevant alternatives should not matter.
+Practical
+Use of minimal information.
+Strategic
+Providing the right incentives for the truthful revelation of individual
+preferences.
+
+\subsection{PSP Formulation}
 Consider a user seeking to prevent
@@
 D^{j(t)}\rbrace$
-\State $ \bar{i} \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
-\State $D^{j(t+1)} \gets D^{j(t)} - e_{\bar{i}}^{j(t)}(a)$
+\State $ i^* \gets \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j$ 
+\State $D^{j(t+1)} \gets D^j - d_{i^*}^{j}$
 %\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
-\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
+\State $p^j \gets p_{i^*}^j+\epsilon/2$ and $d^j \gets D^j$
 \State $s^{j(t+1)} \gets (d^j, p^j)$
@@
 \State $D^{j(t+1)} = D^{j(t)}$
-\State $t \gets t+1$
 \State Go to 4.
 \Else
-\State $\bar{i} \gets e_{\bar{i}}^j(a)$
+\State $i^* \gets \bar e_{i^*}^j(a(s))$
 %\State $\beta^{j(t+1)} \gets \bigg\lbrace i\in\mcI^j: 
 %        d_i \le \bar{b}^j \bigg\rbrace$
-\State $t \gets t+1$
 \State Go to 4.
@@
 \begin{align*}
-    z_i^j &= e_i^{j^*}(a), \\
+    z_i^j &= e_i^j(a), \\
     y_i^j &= \theta_i'(z_i^j).
@@
 \begin{equation}\label{minimaleq}
-    e_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+,
+e_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+,
 \end{equation}
@@
 Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$e_k^{j^*}(a) \ge e_i^{j^*}(a)$ and so $d^j - d_k^j < z_i^{j}$, resulting in a
+$e_k^j(a) \ge e_i^j(a)$ and so $d^j - d_k^j < z_i^{j}$, resulting in a
 partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
@@
 set, (\ref{buyercoordinate}) states that $n$ is such that $e_i^{j*}(a)
-\ge e_k^{j^*}(a)$ for any $k$, therefore such a buyer $k$ cannot exist.
+\ge e_k(a)$ for any $k$, therefore such a buyer $k$ cannot exist.
 \iffalse
@@
 d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= e_i^{j^*}(a)
+    &= z_i^{j}= e_i^j(a)
 \end{align*}
@@
 $$
-From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = e_i^j(a(z_i,y_i))$, 
-and so,
-$$
-    \theta_i\circ e_i^j(a(z_i,y_i)) = \theta_i\circ e_i^j(a),
-$$ 
-which holds $\forall \ j\in\mcI_i$.
+From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = e_i^j(a(z_i,y_i))$, which
+implies that 
+$$
+\theta_i\circ e_i^j(a(z_i,y_i)) = \theta_i\circ e_i^j(a).
+$$ 
 Therefore, by the definition of utility (\ref{buyerutility}),
@@
 \begin{align*}
-    &\theta_i\circ e_i(a(z_i,y_i)) - \theta_i(a)\circ e_i(a) \\
-    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
-    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - z) \ dz.
+    &\theta_i\circ e_i(a(z_i,y_i)) - \theta_i(a)) \\
+    &= u_i(z_i,y_i) - u_i =  c_i^j -c_i^{j}(z_i,y_i)\\
+    &= \displaystyle\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(D_i - z) \ dz.
 \end{align*}
@@
 For any seller $j$, let time $t \in \tau$ be fixed and for any buyer $i\in
-\mcI^j$, let $s_{-i}$ also be fixed. )VALIDATE: FOR ALL j) Define,
+\mcI^j$, let $s_{-i}$ also be fixed. Define,
 \begin{align}
@@
 $$
-    v_i^j = e_i^{j^*}(z) 
+    v_i^j = e_i^j(z) 
 $$
@@
 $$ 
-which implies, as (MORE) $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
-we have $\forall \ j \in \mcI_i$, 
+which implies, as (MORE) $\theta_i'$ is non-increasing and $P_i^j$ is
+non-decreasing $\forall \ j \in \mcI_i$, 
 \begin{align*}
@@
 \end{align*}
-And so, by (\ref{dataallocation}),
+And so, (MORE)
 \begin{align*}
     a_i^j(t_i) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\mcI_i} a_i^j(t_i) &= z.
+    \Rightarrow \displaystyle\sum_{j\in\mcI_i} \bar{a}_i^j(t_i) &= z.
 \end{align*}
@@
 \begin{align*}
-    \displaystyle\sum_{j\in\mcI_i}&\int_0^{v_i^j} P_i^j(x) \ dx =  \int_0^{z}
+    \displaystyle\sum_{j\in\mcI_i}\int_0^{v_i^j} P_i^j(x) \ dx &=  \int_0^{x}
     \bar{P}_i^j(x) \ dx \\
-    &= \sum_{j\in\mcI_i}\int_0^{e_i^j(z)} P_i^j(x) \ dx.
+    &= \sum_{j\in\mcI_i}\int_0^x P_i^j(x) \circ e_i^j \ dx.
 \end{align*}
-Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
-s_{-i}) + \epsilon$. The buyer coordinated strategy, from Propositions
-\ref{coordinationlemma} and
-\ref{buyerstrategy}, gives $s_{i^*} = (e_i\circ a_i(s), \ \theta_i'(z)) =
-(z_i, c_i)$, where
-for each $j\in \mcI$, $a_i^j(s_{i^*}; s_{-i}) = z_i^j$,
-then clearly $u_i(s_{i*}, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
-u_i(s_i;s_{-i}) > \epsilon$. Denoting $z_i^j$ (fixed) as $\zeta$, 
-$$
-    \int_z^{\zeta} {\theta_i}'(x) \ dx- \int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
-$$
-For concave valuation functions, the first-order derivative of $\theta$ at point
-$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
-/ \theta'(0)$ guarantees that new bids will differ by at least
-$\epsilon$, and as such, buyer $i$ will remain in
-any local auction with reserve price determined by (\ref{???}). We therefore
-verify that,
-$$
-    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
-dx \le \epsilon,
-$$
-and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
-$$
-    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
-\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
-$$
-If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
-$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
-\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
-Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
-\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
-exist.
-
-We consider the other term in the minimization; let $z=\chi_i$. We have that
-For any coordinated bid $s_i$ such that $u_i(z_i, c_i) > u_i(t_i)+
-\epsilon$, then $\zeta > z
-\Rightarrow c_i(s_{i}) > b_i$, and so is infeasible. 
-Finally, by Lemma \ref{userunion}, for a single buyer-seller interaction, we
-have that $f_i = f^j \Rightarrow \theta_i \circ e_i^j = \theta^j \circ e_i^j$.
-Therefore $\theta_i' = {\theta^j}'$. We have by Proposision
-\ref{sellerstrategy} and (\ref{???}eqn 30), that $\theta^j = \max_{i\in\mcI^j}
-\theta_i$, and so for any $i\in\mcI^j, \theta^j(z) \ge \theta_i(z)$, and so $j$
-cannot set a higher reserve price, and also cannot sell more data than the buyers'
-bids, so we have that $j$'s bid is both truthful and optimal.
-\\----------------------REF-------------------------\\
-% NEW MARKET PRICE
-\begin{align}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}
-    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
-\end{split}
-\end{align}
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
-    D^j \big] : \\
-    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
-\end{split}
-\end{align}
-% DATA ALLOCATION RULE
-\begin{align}
-    a_i^j(s) \\
-    &= \min\bigg\lbrace e_i^j(D_i),
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
-\end{align}
-% DATA COST
-\begin{align}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-p^j \bigg(ai^j(0; s_{-i}^j)
-    -a_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
-% BUYER DEMAND 
-\begin{equation}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
-\end{equation}
-% BUYER REVENUE 
-\begin{equation}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-% SELLER REVENUE 
-\begin{equation}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-\begin{equation}
-    \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
-\end{equation}
-\begin{equation}
-    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-\begin{equation}
-    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-\begin{equation}
-    d_i^j \ge e_i^j(a)
-\end{equation}
-\begin{equation}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
-\end{equation}
-\begin{equation}
-    e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
-\end{equation}
-\begin{equation}
-   p_i^j \ge \min_{i\in\mcI}\big(p_i^j).
-\end{equation}
-\\----------------------------------------------------\\
+(FINISH!)\\
+Now suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^k(s_i;s_{-i}) > u_i^k(t_i;
+s_{-i}) + \epsilon$. Suppose there is a seller such that $\mu = e_i^k\circ a_i^k(s)$, also $\zeta = e_i^j\circ
+a_i^j$, and $s_{i^*} = (\zeta_i,p_i)$.
+
+Then from
+(\ref{coordination}), $a_i^j(s_{i^*}; s_{-i}) = \zeta_i^j$, therefore
+\begin{align*}
+    &\qquad u_i(s_{i^*};s_{-i}) \\
+    &= \displaystyle\int_0^\xi {\theta_i}'(\eta)\ d\eta -\sum_j\int_0^\xi P_i^j(\eta/\vs_i^j) \ d\eta.
+\end{align*}
+By Lemma \ref{coordinationlemma}, $u_i(s_{i^*}, s_{-i}) > u_i(t_i; s_{-i}) +
+\epsilon$, which is equivalent to 
+$$
+    \int_\epsilon^\xi {\theta_i}'(\eta) \ d\eta - \sum_j\int_0^\xi
+P_i^j(\eta/\vs_i^j) \ d\eta > \epsilon.
+$$
+The rest of the calculation follows as in \cite{semret} with the modified
+framework, i.e. both $\bar\epsilon = \epsilon + \epsilon/{\theta_i}'(0)$ and
+$\xi > \bar\epsilon$ show a contradiction.
 (SELLER FINISH)\\
@@
 restricted to $\epsilon$-best replies from buyers $\in \mcI^j$. Therefore we have that a
-fixed point in the ``truthful" local game is a fixed point for the auction. We
+fixed point in the ``truthful" local game is a fixed point for the auction.
+To see this, We
 further argue that as the set $\mcI^j$ is
@@
 Matthias Roggendorf and Fernando Beltr{\'a}n,
-\textit{Simulation Model for the Dynamic Allocation of Network Resources in a
-Competitive Wireless Scenario}. Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
+\textit{Simulation Model for the Dynamic Allocation of Network Resources in a Competitive Wireless Scenario}.
+Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
 pp. 54 - 64.
 
-\bibitem{diffserve}
-N. Semret, R. R. F. Liao, A. T. Campbell and A. A. Lazar, 
-\textit{Pricing, provisioning and peering: dynamic markets for differentiated Internet services and
-implications for network interconnections}, in IEEE Journal on Selected Areas in
-Communications, vol. 18, no. 12, pp. 2499-2513, Dec. 2000.
-
 \end{thebibliography}

### 2019-08-21 April/paper_wc_save3.tex
On hold.

--- 2018-04-18 paper_wc_save_4.tex
@@
 We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
-Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
+Kong 4G Pro Service Plan customers. Telecommunications providers' revenue is typically
 gained by charging users a fixed fee for a maximum amount
@@
 bids for that element only \cite{lazar}. In this work, the proposed mechanism
-allows the distribution of bids, where there are many ISPs each holding
+allows the distribution of bids, where there are many providers each holding
 thier own local auction; there is no entity that holds a global market knowledge.
@@
 VALUATION.. FUTURE WORK)
-
-The paper is organized as follows...
 
@@
 
+\section{Distributed PSP Analysis}
+
+\subsection{User Behavior}
+
+We assume that users are selfish, and therefore
+rational. Users prefer to participate in the secondary market as it allows them to purchase
+additional data for a cost less than the overage fee set by the ISP. 
+User preferences are defined by a utility function, for any $i\in\mcI$,
+\begin{align*}
+    u_i : &S \rightarrow (-\infty, \infty) \\
+          &s \rightarrow u_i(s).
+\end{align*}
+(TOO GENERAL?)
+
+\subsubsection{Buyer Strategy}
+
+Absent the cost or revenue from trading data, CMHK users gain utility from consuming
+data. 
+We will assume that the buyer valuation satisfies the conditions for an
+\emph{elastic demand function}: 
+\definition{\cite{lazar}}
+A real valued function, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta_i(0) = 0$,
+    \item $\theta_i$ is differentiable,
+    \item ${\theta_i}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
+     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
+${\theta_i}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le
+{\theta_i}'(\eta)
+- \gamma(z - \eta)$. 
+\end{itemize}
+
+% OPT-OUT BUYER
+We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
+function,
+\begin{equation}\label{buyerutility}
+    u_i = \theta_i \circ e_i(a) - c_i,
+\end{equation}
+where $e_i : [0, \infty) \rightarrow [0,\infty)$ is %the expectation 
+a function that maps buyer $i$'s data quantity (requirement) to matching
+seller(s). We note that the opt-out buyers valuation depends only on a scalar $e_i(a)$ which is a function of the
+quantities of all the available data for sale in the secondary market.
+
+Suppose the total amount of seller $j$'s data on the network at the instance that
+user $i$ joins the auction is $b^j$. 
+A sellers' allocation cannot exceed the total amount they have available,
+i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
+\mcI$ if and only if $b^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
+restricted to subset of buyers $\in\mcI$.
+Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
+rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
+extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
+We assume that buyers and sellers are separated (a seller does not also buy
+data and vice versa).
+
+Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
+is also reasonable to expect that a seller may come close to using their
+entire data cap, and only sell the fractional overage. In this case, we
+determine that a buyer must coordinate their bids among multiple sellers. 
+Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
+moderated by the function $e$ which maps its data requirement to the distributed market. 
+We propose the following strategy,
+{
+\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
+Let $i\in\mcI$ be a buyer and define any auction duration
+to be $\tau \in [0,\infty)$, and fix all other buyers' bids $s_{-i}$. 
+For any allocation $a$, let
+% OPT-OUT BUYER STRATEGY
+\begin{equation}\label{opt-out}
+    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
+    e_i^j(a) \triangleq a_i^j,
+\end{equation}
+and define,
+% MIN SET
+$$
+    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
+n}\sum_{j\in\mcI'} d^j.
+$$
+Buyer $i$ chooses its seller pool by determining $n$, where
+\begin{equation}\label{buyercoordinate}
+    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
+    n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
+\ge d_i\rbrace,
+\end{equation} 
+which produces a minimal subset 
+\begin{equation}\label{sellers}
+    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
+\end{equation} 
+Now let $j^* = n \le I$, and define, 
+\begin{equation}\label{opt-minallocation}
+    e_i(a) \triangleq e_i^{j^*}(a).
+\end{equation}
+we address the following special cases:\\
+(Budget limited allocation)
+\begin{equation}\label{partialallocation}
+    d_i^j > b^j - \sum_{k\in\mcI^j, k\ne i} d_k^j.
+\end{equation}
+(Equal price allocation)
+There exists $k,i \in \mcI^j, k\ne i$, such that
+\begin{equation}\label{equalprice}
+    \quad p_i^j = p_k^j.
+\end{equation}
+(Price-dominant allocation)
+There exists $k \ni \mcI^j$, where $\forall \ i\ne k \in \mcI^j$.
+\begin{equation}\label{newbuyer}
+    p_k^j < p_i^j, 
+    %p_i^j < p_k^j \quad \text{and} \quad d_i^j >= b^j, \quad \forall \ k \in \mcI^j.
+\end{equation}
+(Empty allocation)
+\begin{equation}\label{emptyset}
+    n > \vert \mcI\vert \Rightarrow \ell^j = \emptyset.
+\end{equation}
+In any of the above cases, seller $j$'s local auction strategy does not change and
+Proposition \ref{sellerstrategy} holds.
+Then, we have that $e_i$
+is an optimal feasible strategy for buyer $i$.
+}\\
+\textbf{Proof:}
+In the case that there exists a seller who can completely satisfy a buyers'
+demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
+as the set $\ell_i$ is an ordered set, $i$ may discover 
+$j^*$ by computing $\ell_i$. In the case that $d_i >
+\sum_{j\in\mcI}d^j$, then $j^* > I$, we reason that this case is unlikely; our formulation reduces to a
+monopoly, and the user pays the overage fee for data set by the provider which the upper bound of the sellers'
+pricing function, where we consider the provider (AT\&T) as a seller. We also note that $\mcI_i$ is not the only
+possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
+minimal ordered subset where a
+coordinated bid is possible, which we will address in further analysis in Section \ref{analysis}.
+Suppose there exists buyer $k\in \mcI^j$, such that
+$e_k^j(a) \ge e_i^j(a)
+\rightarrow p_k^j > p_i^{j}$ and so $d^j - d_k^j < z_i^{j*}$, resulting in a
+partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
+As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
+set, (\ref{buyercoordinate}) states that $n$ is such that $e_i(a) = e_i^{j*}(a)
+\ge e_k(a)$. We assume that $i$ will faithfully follow the opt-out strategy, and
+so such a buyer $k$ cannot exist. 
+Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$.
+
+% BUYER LOCAL RESPONSE
+{
+\lemma{(Localized buyer response)}\label{buyerresponse}
+As we cannot
+assume that a buyers' bid will remain fixed at time $(t+1)$,
+}\\
+\textbf{Proof:} 
+The first two cases, (\ref{partialallocation}) and (\ref{equalprice}) deal with
+the problem of a buyer receiving a partial allocation:
+In (\ref{partialallocation}), the winner with the lowest unit price $p_i^j$ results in a partial
+allocation. In this case, using (\ref{buyercoordinate}), buyer $i$ will decrease its
+quantity $d_i^j$ by increasing $n$, and will either remain a winner in $j$'s local
+auction, or drop out of $\mcI^j$. (WILL USE LATER, DEVELOP MORE HERE?)
+(\ref{equalprice}) considers that there may exist multiple buyers with the same unit price. The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
+between all buyers with the same unit price. Therefore, again by
+(\ref{buyercoordinate}), the buyers will increase $n$ until their demand is
+met. 
+The third case considers that a new buyer $k$ may enter the market with a better
+price. There cannot be a buyer where $d_k^j > b^j$, as this violates
+(\ref{budget}) imposed by (\ref{buyercoordinate}). When $d_k^j =
+b^j$, the optimal solution at time $t$ is the single allocation, therefore at
+time $(t+1)$, we have $\mcI^j = k$. It follows that in the case $d_k^j < b^j$, buyers $i\in\mcI^j$ will
+lose their position in $\ell^j$ as the auction progresses and the minimal
+subset $\mcI^j$ is computed. 
+(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
+Lastly, to resolve (\ref{emptyset}), $j$ chooses $n=I$, and sets its reserve price to $p_I^j$.
+
+\subsubsection{Buyer Influence}
+To determine a strategy for the sellers, we first perform a general examination
+of seller incentive. The potential revenue for $j$ at unit price $y$ is determined by the
+demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
+% BUYER DEMAND 
+\begin{equation}\label{datademand}
+    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
+\end{equation}
+with ``inverse"
+% SELLER REVENUE 
+\begin{equation}\label{revenue}
+    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
+        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace.
+\end{equation}
+For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
+which it \emph{could} be sold to any buyer $i\in \mcI$ (as in \cite{semret}).
+% SELLER VALUATION
+We may now define the seller valuation (potential). 
+{
+\lemma{(Seller valuation)}\label{sellervaluation}
+For any seller $j\in\mcI$, the contribution from buyer $i$'s valuation may be
+modeled as,
+\begin{equation}\label{singlevaluation}
+    \theta_i^j = \int_0^{e_i^j(a)} f^j(z) \ dz.
+\end{equation}
+it follows that 
+\begin{equation}\label{valuation}
+    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
+ \int_0^{e_i^j(a)} f^j(z) \ dz.
+\end{equation}
+}
+\textbf{Proof:} 
+We assume that a seller will try to maximize profit for any given allocation $a$, and
+as such there is an incentive for $j$ to sell all of its data, and so 
+$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = b^j =
+\sum_{i\in\mcI} e_i$,
+The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
+
+The sellers' natural utility is the potential
+profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
+potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
+This is intuitive as a seller who does not meet the demand of \emph{any} buyer will not
+participate in any auction. We have chosen to omit the original cost of the data
+paid to the ISP, as a discussion of mobile data plans is outside the scope of this
+paper.
+
+As $j$ is restricted by
+the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
+{
+% SELLER CONSTRAINTS
+\lemma{(Seller constraints)}\label{constraints}
+Let $j$ be a seller with budget $b^j$.
+First, the seller must satisfy the quantity
+constraint, 
+\begin{equation}\label{quantity}
+    d^j \ge e_i(a)
+\end{equation}
+and
+\begin{equation}\label{budget}
+    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j.
+\end{equation}
+In addition, for a rational seller, the reserve price must
+satisfy 
+\begin{equation}\label{reserveprice}
+   p^j \ge \min_{i\in\mcI}\big({\theta_i}'(d_i^j)\big).
+\end{equation}
+}\\
+\textbf{Proof:}
+The first statement is an assumption, which we may enforce by (\ref{opt-out}),
+and as a seller cannot sell more data than their bid, (\ref{budget}) enforces
+the budget constraint for the seller. (\ref{reserveprice})
+follows from the assumption that $j$ is rational, and so utility-maximization
+acts as revenue maximization; a rational seller will not sell its
+data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)
+
+\subsubsection{Progressive User Strategy}
+In order to to develop the seller strategy, it is necessary we determine 
+that a seller has an incentive to
+accept fractional bids (i.e. sell a fraction of their data $b^j$). Reasonably,
+there may not exist a buyer such that $d_i = b^j$. In addition, a seller may accept
+fractional bids in order to
+maximize the revenue gained per unit of data by increasing market competition
+\cite{???}.
+Finally, in the case that the seller does not know the exact amount of
+leftover data available, then they may only sell enough data to ensure that
+they will not become a buyer while they submit their total data overage to the
+secondary market. (FUTURE WORK? FROM \cite{zheng})
+
+We describe the sellers' \emph{local} auction strategy for allocating its
+data according to the constraints formed by the buyer strategy. As
+local auction is progressive, and influenced by the $\epsilon$-best replies of
+the buyers, we will need the following Lemma. (SHOULD I COUPLE THESE
+ALGORITHMS? LESS OR MORE CONFUSING?)
+We now define the local auction, which we describe, when coupled with the buyer
+responses, as a progressive game of strategy with incomplete, but perfect
+information (SAY MORE?).
+
+% SELLER LOCAL STRATEGY
+{
+\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
+Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
+For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
+
+let the winner be determined by,
+\begin{equation}\label{winner}
+    \bar{i} = \displaystyle\argmax_{I^j}\sum_{i\in I^j} p_i^j.
+\end{equation}
+Also define
+$$
+    \ell^j =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
+n}\sum_{i\in{\mcI}'} p_i^j,
+$$
+where,
+\begin{equation}\label{sellercoordinate}
+    n = \argmin_{\ell^j}(i \in \ell^j : \displaystyle\sum_{i\in\mcI^j} d_i^j >
+b^j),
+\end{equation} 
+which gives $j$ a minimal subset 
+\begin{equation}\label{buyers}
+    \mcI^j = \lbrace i \in \mcI : i < n\rbrace \subset \mcI
+\end{equation} 
+of buyers that maximizes $j$'s revenue.
+Define buyer $i^* = n \le I$ in the ordered set $\ell^j$.
+Then, for time $(t+1)$, set $j$'s reserve price as 
+\begin{equation}\label{newprice}
+    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
+\end{equation}
+and update $j$'s budget to reflect the (tentative) allocation,
+\begin{equation}\label{newbudget}
+    \bar{b}^{j(t+1)} = b^{j(t)} - d_{i^*}^{j(t)}.
+\end{equation}
+Allowing $t$ to range over $\tau$, with buyer responses given as in Lemma
+\ref{buyerresponse}, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
+%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
+market equilibrium.% from time $t$ to $(t+1) \in \tau$.
+}\\
+\textbf{Proof:}
+We will assume that the seller has enough data to satisfy at least one buyer,
+in the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
+price offer, determined by (\ref{sellercoordinate}). As the set of buyers is
+computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
+at equilibrium as it is designed so that the data offered by
+seller $j$ equals the aggregate demand of the buyers \cite{???}
+Although the buyers' valuation $\theta_i$ is not known to the seller, we assume
+that the buyer is bidding truthfully, and so $p^j = {\theta_i}' + \epsilon
+=p_i^j + \epsilon$, therefore $p^j$ is known, and as $\mcI^j\subset \mcI$, we
+note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
+(\ref{singlevaluation}), we have, $\forall \ z\ge 0$,
+\begin{align*}
+    \int_0^{e_{i^*}^{j}(a)} f^{j}(z)\ dz &\le\int_0^{e_i^{j}(a)}
+f^{j}(z) \ dz 
+\end{align*}
+and so,
+$$
+    \theta^j\circ e_{i^*}(a) \le \theta^j\circ e_i(a),
+$$
+which holds $\forall \ i \in \mcI^j$.
+It follows that, using
+%, using (\ref{buyercoordinate}), 
+the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
+for any $\epsilon$-best reply, 
+$$
+    p^j \le {\theta_i}'(v_i^j) + \epsilon,
+$$
+$\forall i \in \mcI^j$.
+Therefore the choice of $p^j$ does not force any buyers out of the local
+equilibrium. Thus we determine the valuation between seller
+$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
+equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
+(NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK? SAVE
+FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
+
+We conclude this section by reasoning that the user behavior restrictions are
+necessary to formally define (and restrain) the incentives of the users. (OWN
+WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
+competing in multiple local auctions hosted by the sellers, the two games are
+inter-dependent, and may be played on the same or on a different scale in
+valuation, time (AND....). PSP relies on the \emph{relevation prinicple}; the
+PSP mechanism is able to demonstrate equlibrium by showing that PSP is
+incentive-compatible. (MORE?)
+Arrow's paradox is an impossibility theorem stating that when voters have three
+or more distinct alternatives (options), no ranked voting electoral system can
+convert the ranked preferences of individuals into a community-wide (complete
+and transitive) ranking while also meeting a specified set of criteria:
+unrestricted domain, non-dictatorship, Pareto efficiency and independence of
+irrelevant alternatives.
+
+Thus, (WHAT? FINISH, OWN WORDS)
+The designer of a mechanism generally hopes either to design a mechanism
+y() that "implements" a social choice function to find the
+mechanism y() that maximizes some value criterion (e.g. profit)
+Independence of irrelevant alternatives (IIA)
+The IIA condition has three purposes (or effects)
+
+Normative
+Irrelevant alternatives should not matter.
+Practical
+Use of minimal information.
+Strategic
+Providing the right incentives for the truthful revelation of individual
+preferences.
+
 % MECHANISM
 \subsection{Data Auction Mechanism}\label{mechanism}
-We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the secondary market. We will denote the \emph{data} PSP rules
+We may now proceed to formally define the PSP auction as a composition of the
+buyers and sellers in the secondary market. We will denote the data-PSP rules
 by including an overbar, in order to emphasize that they have been changed from
-the original forms described in \cite{lazar}.
+the original forms \cite{lazar}.
 The market price function (MPF) for a buyer in the secondary market
@@
 data amount $z$ given an opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
+the total minimum price for the buyer must be an aggragation of the \emph{individual} prices of the buyers as it is
+possible that $\mcI_i \ne \mcI^j$, and so the reserve prices of the individual sellers
+may vary. 
 %To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
@@
 purchase. We perform a simple survey of these bid fee models, we
-provide some idea of the expected revenue of the mobile data ISP (NEED
+provide some idea of the expected revenue of the mobile data provider (NEED
 STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
@@
 this secondary market our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead (and so possibly fees paid to the ISP)
+but minimizes comminication overhead (and so possibly fees paid to the provider)
 and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
 with respect to the classic throughput problem.
-
-\section{Distributed PSP Analysis}
-
-\subsection{User Behavior}
-
-We assume that users are selfish, and therefore
-rational. Users prefer to participate in the secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
-In general, user preferences are defined by a utility function, for any $i\in\mcI$,
-\begin{align*}
-    u_i : &S \rightarrow (-\infty, \infty) \\
-          &s \rightarrow u_i(s).
-\end{align*}
-
-\subsubsection{Buyer Strategy}
-
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We will assume that the buyer valuation satisfies the conditions for an
-\emph{elastic demand function}: 
-\definition{\cite{lazar}}
-A real valued function, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta_i(0) = 0$,
-    \item $\theta_i$ is differentiable,
-    \item ${\theta_i}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta_i}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le
-{\theta_i}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
-
-% OPT-OUT BUYER
-We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with utility
-function,
-\begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ e_i(a) - c_i,
-\end{equation}
-where $e_i : [0, \infty) \rightarrow [0,\infty)$ is %the expectation 
-a function that maps buyer $i$'s data quantity (requirement) to matching
-seller(s). We note that the opt-out buyers valuation depends only on a scalar $e_i(a)$ which is a function of the
-quantities of all the available data for sale in the secondary market.
-
-Suppose the total amount of seller $j$'s data on the network at the instance that
-user $i$ joins the auction is $b^j$. 
-A sellers' allocation cannot exceed the total amount they have available,
-i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
-\mcI$ if and only if $b^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
-restricted to subset of buyers $\in\mcI$.
-Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
-rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
-extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
-We assume that buyers and sellers are separated (a seller does not also buy
-data and vice versa).
-
-Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
-is also reasonable to expect that a seller may come close to using their
-entire data cap, and only sell the fractional overage. In this case, we
-determine that a buyer must coordinate their bids among multiple sellers. 
-Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-moderated by the function $e_i$ which maps its data requirement to the distributed market. 
-We propose the following strategy, 
-% BUYER STRATEGY
-{
-\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t\in\tau$. For any allocation $a$ at time $t$, let
-% OPT-OUT BUYER STRATEGY
-\begin{equation}\label{opt-out}
-    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
-    e_i^j(a) \triangleq a_i^j,
-\end{equation}
-and define,
-% MIN SET
-$$
-    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
-n}\sum_{j\in\mcI'} d^j.
-$$
-Buyer $i$ chooses its seller pool by determining $n$, where
-\begin{equation}\label{buyercoordinate}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
-    n = \argmin_{j\in \ell_i}(n d^j\ge d_i\rbrace,
-\end{equation} 
-which produces a minimal subset 
-\begin{equation}\label{sellers}
-    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
-\end{equation} 
-Now let $j^* = n \le I$, and define, 
-\begin{equation}\label{opt-minallocation}
-    e_i(a) \triangleq e_i^{j^*}(a).
-\end{equation}
-
-We have that $e_i$ defines an optimal feasible strategy for buyer $i$ for any
-time $t\in\tau$.
-}\\
-\textbf{Proof:}
-We assume that a buyer wants to fufill their data requirement.
-In the case that there exists a seller who can completely satisfy a buyers'
-demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
-as the set $\ell_i$ is an ordered set, $i$ may discover 
-$j^*$ by computing $\ell_i$. If we suppose that $d_i >
-\sum_{j\in\mcI}d^j$, then $j^* > I$ and $\ell_i = \emptyset$, 
-we model the ISP as a seller $k$ with bid $s^k =(d^k, p^k)$, where $d^k > d^j, \
-\forall \ j\in\mcI_i$, an
-$p^k$ is the overage fee for data set by the ISP, which is also the upper bound of the sellers'
-pricing function, and so again (\ref{buyercoordinate}) holds.
-As prices are a bounded set, we consider some $k \ne i \in
-\mcI$ where $p_i^j = p_k^j$. 
-The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
-between all buyers with the same unit price. 
-This would result in a partial allocation of data to $i$ and $k$, and so neither
-buyer would satisfy thier demand as expected. (NOT QUITE SURE
-HOW I WANT TO HANDLE THIS YET ... WANT PROPORTIONAL SPLIT TO WORK WITH PARTIAL
-DATA ALLOCATION FOR BUYERS AND SELLERS)
-Additionally, we consider the transition from time $t$ to time $(t+1)$, and a
-new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other words, a new buyer $k$ may enter the market with a better
-price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
-$n$ so that
-$$
-    e_i^{(t+1)}(a) = e_i^{(t)}(a) - e_k^{(t)}(a),
-$$
-and the subset $\mcI_i$ is large enough to balance the additional demand from
-$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal.
-
-Finally, we note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
-minimal ordered subset where a
-coordinated bid is possible, the reasoning for which we will address in further analysis (Section
-\ref{analysis}).
-
-\subsubsection{Buyer Influence}
-The buyer demand is a key market influence (SILLY SENTENCE), as the buyer
-valuation is elastic, even infintesimal changes in the market dynamics can be
-modeled. $\forall \ y\ge 0$, we determine that the demand for $j$ is given by,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
-\end{equation}
-
-Buyers are influenced by each others' behavior, each buyer has an incentive to
-remain a participant in all of the auctions.
-We define the ``inverse" demand for any buyer $i$,
-% SELLER REVENUE 
-\begin{equation}\label{revenue}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-For a given demand $\rho^j$, $f_i$ maps a unit of data to the lowest price at
-which $i$ \emph{could} buy the unit from \emph{any} seller $j\in\mcI$. This is the
-lowest potential unit cost of the buyer, and corresponds to the maximum reserve
-price amongst the sellers. 
-The revenue for $j$ at unit price $y$ is also determined by the
-demand of the buyers.
-We define the ``inverse" of the buyer demand function for seller $j$:
-% SELLER REVENUE 
-\begin{equation}\label{revenue}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-where $f^j$ maps to the highest possible unit data price.
-Thus we have the following Lemma. 
-{
-\lemma{(User valuation)}\label{uservaluation}
-For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
-\begin{equation}\label{buyerprice}
-    \theta_i^j \circ e_i = \int_0^{e_i^j(a)} f_i(z) \ dz,
-\end{equation}
-it follows that 
-\begin{equation}\label{valuation}
-    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
- \int_0^{e_i^j(a)} f_i(z) \ dz.
-\end{equation}
-Similarly, seller $j$'s valuation is,
-\begin{equation}\label{sellervaluation}
-    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
- \int_0^{e_i^j(a)} f^j(z) \ dz.
-\end{equation}
-}
-\textbf{Proof:} 
-We assume that a buyer wants to minimize the cost of purchasing their data
-requirement, at the same time ensuring they get the full allocation $e_i(a)$,
-and so must minimally meet $j$'s reserve price.
-A seller will try to maximize profit for any given allocation $a$,
-and will try to sell all of its data, and so 
-$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = b^j =
-\sum_{i\in\mcI} e_i$,
-The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
-(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)
-
-The sellers' natural utility is the potential
-profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
-potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
-We have chosen to omit the original cost of the data
-paid to the ISP, as a discussion of mobile data plans is outside the scope of this
-paper.
-
-As $j$'s behavior is restricted by
-the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
-{
-% SELLER CONSTRAINTS
-\lemma{(Seller constraints)}\label{constraints}
-Let $j$ be a seller with budget $b^j$.
-First, the seller must satisfy the quantity
-constraint, 
-\begin{equation}\label{quantity}
-    d^j \ge e_i(a)
-\end{equation}
-and
-\begin{equation}\label{budget}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j,
-\end{equation}
-which implies, for any $i\in\mcI$,
-\begin{equation}\label{partialallocation}
-    e_i^j(a) \le b^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
-\end{equation}
-In addition, for a rational seller, the reserve price must
-satisfy 
-\begin{equation}\label{reserveprice}
-   p^j \ge \min_{i\in\mcI}\big(p_i^j).
-\end{equation}
-}\\
-\textbf{Proof:}
-The first statement is obvious, 
-a seller cannot sell more data than indicated in their bid, (\ref{budget}) and
-(\ref{partialallocation}) enforce
-the budget constraint for the seller. Finally, (\ref{reserveprice})
-follows from the assumption that $j$ is rational, and so utility-maximization
-acts as revenue maximization; a rational seller will not sell its
-data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)
-
-\subsubsection{Seller Strategy}
-In order to to develop the seller strategy, it is necessary we determine 
-that a seller has an incentive to
-accept fractional (CHANGE TO PARTIAL? PICK ONE) bids (i.e. sell a fraction of
-their budget $b^j$). Reasonably,
-there may not exist a buyer such that $d_i = b^j$. \cite{zheng} reasons that the seller does not know the exact amount of
-leftover data available, and so they may only sell enough data to ensure that
-they will not become a buyer while they submit their total data overage to the
-secondary market. Buyers are allowed to
-bid both dynamically and asychronously, and as a seller determines allocations using only bids
-in its local market. Therefore, in order to
-maximize the revenue gained per unit of data the seller must respond to the
-varation of competitive bids in its market (MORE? FUTURE WORK? CITE?).
-
-We describe the sellers' \emph{local} auction strategy for allocating its
-data according to the constraints formed by the buyer strategy. As
-local auction is progressive, and influenced by the $\epsilon$-best replies of
-the buyers, we will need the following Lemma. 
-We now define the local auction, which we describe, when coupled with the buyer
-responses, as a progressive game of strategy with incomplete, but perfect
-information (SAY MORE?).
-(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
-
-% SELLER LOCAL STRATEGY
-{
-\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
-For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
-Let the winner at time $t$ be determined by,
-\begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i}\sum_{i\in I^j} p_i^j,
-\end{equation}
-and define
-$$
-    \ell^j =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
-n}\sum_{i\in{\mcI}'} p_i^j,
-$$
-where,
-\begin{equation}\label{sellercoordinate}
-    n = \argmin_{i\in\ell^j}(\displaystyle\sum_{i\in\mcI} d_i^j >
-b^j),
-\end{equation} 
-which gives $j$ a minimal subset 
-\begin{equation}\label{buyers}
-    \mcI^j = \lbrace i \in \mcI : i < n\rbrace \subset \mcI
-\end{equation} 
-of buyers that maximizes $j$'s revenue.
-Define buyer $i^* = n \le I$ in the ordered set $\ell^j$.
-Then, for time $(t+1)$, set $j$'s reserve price as 
-\begin{equation}\label{newprice}
-    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
-\end{equation}
-and update $j$'s budget to reflect the (tentative) allocation,
-\begin{equation}\label{newbudget}
-    \bar{b}^{j(t+1)} = b^{j(t)} - d_{i^*}^{j(t)}.
-\end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
-%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
-market equilibrium. (BLAST I RUINED THE EQ) % from time $t$ to $(t+1) \in \tau$. 
-}\\
-\textbf{Proof:}
-We assume that the seller has enough data to satisfy at least one buyer,
-and that they want to maximize their revenue.
-In the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}),
-%As the set of buyers is
-%computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
-%at equilibrium as it is designed so that the data offered by
-%seller $j$ equals the aggregate demand of the buyers \cite{???}
-and so we have that the aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
-Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that the buyer is bidding truthfully, and so $p^j = {\theta_i}' + \epsilon
-=p_i^j + \epsilon$, therefore $p^j$ is known, and as $\mcI^j\subset \mcI$, we
-note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
-(\ref{singlevaluation}), we have, $\forall \ z\ge 0$,
-\begin{align*}
-    \int_0^{e_{i^*}^{j}(a)} f^{j}(z)\ dz &\le\int_0^{e_i^{j}(a)}
-f^{j}(z) \ dz 
-\end{align*}
-and so,
-$$
-    \theta^j\circ e_{i^*}(a) \le \theta^j\circ e_i(a),
-$$
-which holds $\forall \ i \in \mcI^j$.
-It follows that, using
-%, using (\ref{buyercoordinate}), 
-the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
-for any $\epsilon$-best reply, 
-$$
-    p^j \le {\theta_i}'(v_i^j) + \epsilon,
-$$
-$\forall i \in \mcI^j$.
-Therefore the choice of $p^j$ does not force any buyers out of the local
-auction. Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
-equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-(NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK? SAVE
-FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
-
-(TRY FRACTIONAL ALLOCATION AS A SEPARATE AUCTION? FOR EXTRAS)
-
-We conclude this section by reasoning that the user behavior restrictions are
-necessary to formally define (and restrain) the incentives of the users. (OWN
-WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
-competing in multiple local auctions hosted by the sellers, the two games are
-inter-dependent, and may be played on the same or on a different scale in
-valuation, time (AND....). PSP relies on the \emph{relevation prinicple}; the
-PSP mechanism is able to demonstrate equlibrium by showing that PSP is
-incentive-compatible. (MORE?)
-Arrow's paradox is an impossibility theorem stating that when voters have three
-or more distinct alternatives (options), no ranked voting electoral system can
-convert the ranked preferences of individuals into a community-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives.
-
-Thus, (WHAT? FINISH, OWN WORDS)
-The designer of a mechanism generally hopes either to design a mechanism
-y() that "implements" a social choice function to find the
-mechanism y() that maximizes some value criterion (e.g. profit)
-Independence of irrelevant alternatives (IIA)
-The IIA condition has three purposes (or effects)
-
-Normative
-Irrelevant alternatives should not matter.
-Practical
-Use of minimal information.
-Strategic
-Providing the right incentives for the truthful revelation of individual
-preferences.
 
@@
 For any profile $s_i = (d_i, p_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
-allocation. For any fixed $s_{-i}$, a better reply for $i$ is $x_i =
-(z_i,y_i)$, where $\forall \ j \in \mcI_i$,
-\begin{align*}
-    z_i^j &= e_i(a), \\
-    y_i^j &= \theta_i(e) \\ &(\text{BETTER NOTATION!})
-\end{align*}
-and furthermore,
+allocation. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
+(z_i,p_i)$, where $\forall \ j \in \mcI_i$,
+$$
+    z_i^j = e_i(a),
+$$
+and,
 \begin{equation}\label{coordination}
-    a_i^j(z_i,y_i) = z_i^{j^*},
+    a_i^j(z_i,p_i) = z_i^{j^*},
 \end{equation}
@@
 $$
-If there exists a seller who can fully satisfy $i$'s demand,
-then $\vert\mcI_i\vert = 1$, and the case is trivial as no
+We address two cases:\\
+1. \emph{There exists a seller who can fully satisfy $i$'s demand.} \\
+In this case, $\vert\mcI_i\vert = 1$, and is trivial as no
 coordination is necessary for a single bid. (SPECIAL CASE OF MONOPOLY? THINK!)\\
-Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
-multiple sellers.
-We will show that $i$ may increase $\vert\mcI_i\vert$, without decreasing $u_i$,
-so that the coordinated bid is optimal as in Proposition \ref{opt-out}. 
+2. \emph{Buyer $i$'s demand can only be satisfied by purchasing data from multiple sellers.} \\
+We will show that $i$ may increase $\vert\mcI_i\vert$, without decreasing $u_i$, so that
+coordinated bid is possible. 
 Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
@@
 \end{equation}
-where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
-\ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
-be accepted. We are looking for the set where, for any $j\in\mcI_i$, $\theta_i'(d_i^j) \ge
-p_{i^*}^j$, and for any $i\in\mcI^j$, $e_i^j \le b^j$.
-
-Now, as any $l \ni \mcI_i$ ... for any
+where $p_{i^*}^j$ is the reserve price of the seller, defined in Proposision
+\ref{sellerstrategy}, and is by definition the minimum price allowing any
+allocations to be made by seller $j$. Now, as any $l \ni \mcI_i$ ... for any
 $j\in\mcI_i$
-(LOOK FOR $i^* = j^*$? I.E. the minimum bid = the max losing price)
+(LOOK FOR $i^* = j^*$?)
 
@@
 z_i^j \le a_i^j \Rightarrow u_i(z_i,p_i) - u_i \ge 0$.
-To illustrate our result, suppose there exists buyer $k\in \mcI^j$, such that
-$e_k^j(a) \ge e_i^j(a)
-\rightarrow p_k^j > p_i^{j}$ and so $d^j - d_k^j < z_i^{j*}$, resulting in a
-partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
-As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $e_i(a) = e_i^{j*}(a)
-\ge e_k(a)$. By (\ref{}), such a buyer $k$ cannot exist. 
-Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$.
 
@@
 NOTES: (today)\\
+1. switch from defined valuation function\\
 2. finish seller incentive compat\\
@@
 4. check reserve price = monopoly price
+
+NOTES: (CMHK)
+FAQ
+Why I am not able to purchase extra data?
+Incorrect input: Please follow the instruction on the failure SMS and try to
+purchase extra data again. You can also call our 24 hours customer service
+hotline at 2945 8888 to purchase extra data.
+If you are still unable to purchase extra data after a few attempts, please call
+our 24 hours customer service hotline for enquiries.
+
+Can the remaining extra data be carried forward to the next bill month?
+Extra data purchased can only be used within the bill month that it was
+purchased. Remaining extra data will be forfeited by the end of that bill month
+and will not be carried forward to the next bill month.
+Can I sell the extra data purchased on 2cm Exchange Platform?
+Extra data purchased cannot be sold on 2cm Exchange Platform.
+Terms and Conditions of Data Top-up:
+When the data entitlement of designated service plan is used up, customers can
+purchase extra data within the bill month based on their needs to continue using
+the data service. Otherwise, the data service will be suspended until the next
+bill month. On the other hand, customers with Data+ VAS or Data+ Package can
+enjoy unlimited local data service with designated maximum access speed limit
+within the contract period after the data entitlement of the bill month is used
+up. Data+ will not support tethering and pee-to-peer (P2P) upload and download,
+including BitTorrent.
+Data Top-up is only applicable to designated service plans, including but not
+limited to “Supreme Global” Service Plan, “Supreme Asia” Service Plan, “Supreme
+Greater China” Service Plan, 4.5G Full Speed Local Service Plan, 4.5G Full Speed
+Share Service Plan,“Smart Care” Service Plan and Tertiary Student 4.5G Full
+Speed Local Service Plan.
+Customers can only purchase extra data again after the purchased extra data is
+used up.
+Extra data fee is subject to change. CMHK will charge to the customers at the
+prevailing fee.
+The purchased extra data is only applicable to the bill month that it was
+purchased. Any remaining data (if applicable) cannot be carried forward.
+The purchased extra data is not applicable to 2cm exchange platform.
+Once the top-up data has been purchased, the related payment will not be
+refunded.
+CMHK reserves the right to modify the above content and amend these terms and
+conditions at any time without prior notice.
+In case of dispute, CMHK reserves the right of final decision.
 

### 2019-08-21 April/paper_wc_save_5.tex
On hold.

--- 2019-08-21 April/paper_wc_recovered.tex
@@
 
-We are not concerned with network
-bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
-we reason that there remains an optimal user strategy. As a user no longer needs
-to bid on a complete (but arbitrary)
-cluster of nodes with minimum bandwidth allocation (defined as a route in
-\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
-utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out
-value}, $e$, as a function that when composed with our user type to describes
-its market behavior. In a general sense, $e$ is %the expectation 
-a function that maps a buyer $i$ to matching seller(s).
-
-We have the transform $e: \mathcal{X} \rightarrow \mathcal{Y}$, where
-$\mathcal{Y} \subset \mathcal{X}$, and any
-composition of the opt-out value $e$ with another function $x \in \mathcal{X}$
-results in the scalar application of $e$ to $x$. In other words, for any
-$x\in\mathcal{X}$, and $\mathcal{Y} \subset \mathcal{X}$,
-$$
-    e\circ x = \begin{cases} e(x), \qquad &x \in \mathcal{Y} \\
-                             0, \qquad &x \ni \mathcal{Y}.
-\end{cases}
-$$
 % OPT-OUT BUYER
-We define a \emph{opt-out buyer} as a user $i\in\mcI$ with quasi-linear utility
+We define a \textbf{opt-out buyer} as a user $i\in\mcI$ with quasi-linear utility
 function, the value of the allocation minus the cost,
@@
 \end{equation}
-where $e(\theta_i) : [0, \infty)_{i\in\mcI} \rightarrow [0,\infty)_{i\in\mcI}$. 
+where $e : [0, \infty)_{i\in\mcI} \rightarrow [0,\infty)_{j\in\mcI}$ is %the expectation 
+a function that maps buyer $i$'s data quantity (requirement) to matching
+seller(s). 
 We extend the P2P rules described
@@
     \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
-    &= \min\bigg\lbrace e_i^j\circ D_i,
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i\circ D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
+    &= \min\bigg\lbrace e_i^j(D_i),
+    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
 \end{align}
@@
 $$
-    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
+    \ell_i =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
 n}\sum_{j\in\mcI'} D^j,
@@
     %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
-    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
-\end{equation} 
-Now let $j^* = n \le I$, and define,
+    n = \min(j\in \ell_i : n D^j\ge D_i),
+\end{equation} 
+which produces a minimal subset 
+\begin{equation}\label{sellers}
+    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
+\end{equation} 
+Now let $j^* = n \le I$, and define, $\forall \ j\in\mcI_i$,
 \begin{equation}\label{opt-minallocation}
@@
 \end{equation}
-The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
-fixed $n$ we will denote this subset,
-\begin{equation}\label{sellers}
-    \mcI_i \subset \mcI.
-\end{equation}  
-As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
-we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
+
+We have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
 }\\
 \textbf{Proof:}
-
 We assume that a buyer wants to fufill their data requirement.
@@
 \end{equation}
-For a given demand $\rho^j$, $f_i$ maps the $z$-th unit of data to the lowest price at
-which $i$ could still bid in \emph{any} auction $j\in\mcI$.
+For a given demand $\rho^j$, $f_i$ maps a unit of data to the lowest price at
+which $i$ \emph{could} buy the unit from \emph{any} seller $j\in\mcI$.
 Naturally, this is the
@@
 For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
-Define
-$$
-    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
-n}\sum_{i\in{\mcI}'} p_i^j,
-$$
-where,
-\begin{equation}\label{sellercoordinate}
-    n = \min( i \ \vert \ i \in\mcI^j(n) : \displaystyle\sum_{i\in\mcI} d_i^j \ge
-D^j),
-\end{equation} 
-We have, for any fixed $n$ at time $t$, a minimal subset 
-of buyers that maximizes $j$'s revenue, which we will
-denote,
-\begin{equation}\label{buyers}
-    \mcI^j \subset \mcI.
-\end{equation} 
-Define buyer $i^* = n \le I$.
-Then, for time $(t+1)$, set $j$'s reserve price as 
-\begin{equation}\label{newprice}
-    p_i^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon,
-\end{equation}
 Let the winner at time $t$ be determined by,
@@
 \end{equation}
-and update $j$'s total data to reflect the (tentative) allocation,
+and define
+$$
+    \ell^j =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
+n}\sum_{i\in{\mcI}'} p_i^j,
+$$
+where,
+\begin{equation}\label{sellercoordinate}
+    n = \min(i\in\ell^j : \displaystyle\sum_{i\in\mcI} d_i^j \ge
+D^j),
+\end{equation} 
+which gives $j$ a minimal subset 
+\begin{equation}\label{buyers}
+    \mcI^j = \lbrace i \in \mcI : i < n\rbrace \subset \mcI
+\end{equation} 
+of buyers that maximizes $j$'s revenue.
+Define buyer $i^* = n \le I$ in the ordered set $\ell^j$.
+Then, for time $(t+1)$, set $j$'s reserve price as 
+\begin{equation}\label{newprice}
+    p_i^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
+\end{equation}
+$\forall i \in \mcI^j$, and update $j$'s total data to reflect the (tentative) allocation,
 \begin{equation}\label{newbudget}
@@
 \mcI^j$, which is mathematically analogous to the definition of opting-out in our
-scenario. The seller may simply return the tentatively allocated data to $D^j$,
-and recompute $\mcI^j$ and $p_{i^*}^j$, 
+scenario. The seller may simply add back in the allocated data,
 $$
@@
 
-We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. Consequentially, we have the following Lemma.
-
-{
-\lemma{(Valuation in local auctions)}
-For any buyer $i$, $s_i^j > 0 \equiv j\in\mcI_i \Rightarrow i\in\mcI^j$. 
-Define any auction to be the set of users,
-\begin{equation}
-    \mcI_i \cap \mcI^j.
-\end{equation}
-We have that there exists a strategic local market equilibrium.
-}\\
-\textbf{Proof:}
-A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where if $s_i^j > 0$, so $j\in\mcI_i$, we have that $i\in\mcI^j$. 
-The subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. Similarly, $\mcI_i\subset \mcI$ 
-determines the (coordinated) unit price $p_{i}$ in buyer $i$'s bid.
- For each $j$,
-(\ref{sellercoordinate}) defines $i^*$ as the first losing buyer in the ordered
-set $\ell^j$, and reserve price, $p_{i^*}^j$, which is by definition the lowest price that $j$
-will accept to perform any allocation. 
-We have that for each $i \in \mcI^j$, (LIPSCHITZ)
-$$
-   f_i(z) = \inf\bigg\lbrace y \ge 0 : \rho_i^j(y) \ge z,\
-\forall \ j\in\mcI_i\bigg\rbrace,
-$$
-and so $y\ge p_{i^*}^j > 0, \ \forall \ j\in\mcI_i$.
-% with $i$'s bid price $[p_i]_{j\in\mcI_i} \equiv [y]_{j\in\mcI_i}$. 
-The buyers determine the reserve prices (and thereby dynamics), of each local
-auction (MORE). 
-It follows that either $i\in\mcI^j$ or $i = i^* \in \ell^j$ in any local market
-where $s_i^j \ne 0$. If $i^* \ni \mcI^j$, then the local auction is at
-equilibrium; we need only consider the latter case. By
-Proposision \ref{buyerstrategy}, $i^*$
-will add sellers to its pool until its demand is satisfied. As this holds true
-for any $i^* \in \mcI$ and some $j\in\mcI$, we must have that every auction
-achieves a local equilibrium. 
-(ADD TIME? INDUCTION GOES HERE?)
-
-For completeness, in the case where, for some buyer $i\in \mcI$, $D^{j^*}\vert
-\mcI_i\vert < D_i$, and the ISP $\kappa$ with bid $s^\kappa =(D^\kappa,
-P^\kappa)$ does not adhere to the market dynamics, so $P^\kappa > p_{i^*}^j +
-\epsilon, \ \forall j \in\mcI$, then we may absorb the overage (difference) as part of the
-bid fee.
+We conclude this section by reasoning that the user behavior restrictions are
+necessary to formally define (and restrain) the incentives of the users.
 
@@
 $$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j^*})\ge D_i^j(p_i^{k}).
+    D_i(y_i^j) \ge D_i(p_i^{j^*})\ge D_i(p_i^{k}).
 $$
@@
 
-Seller $j$'s reserve price is determined by a
-buyer $i \ni \mcI^j$, and therefore, even if this price is zero,
+We proceed to examine the strategy of the users in local auctions. As we have shown, the seller
+is a functional extension of the buyer, with rules determined by the buyers'
+behavior. Seller $j$'s reserve price is determined by a
+buyer $i \in \mcI \setminus \mcI^j$, and therefore, even if this price is zero,
 then $p^j = \epsilon \ge 0$.
-
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
+We argue that if truthfullness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
 \forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
 there exists a local market
-equilibrium (NOTE: NOT GLOBAL! YET). We have the following Proposition. For
-completeness, we use the full notation. (BAD SENTENCE)
+equilibrium (NOTE: NOT GLOBAL! YET). We have the following Proposition.
 
@@
 \begin{align}
-\begin{split}\label{eta}
-    \eta_i &= \sup\bigg\lbrace x\ge 0 : 
- {\theta_i}'(x) > \bar{P}_i^j(x)\bigg\rbrace, 
+\begin{split}
+    z_i &= \sup\bigg\lbrace z\ge 0 : 
+ {\theta_i}'(z) > \bar{P}_i^j(z)\bigg\rbrace, 
 \end{split}\\
-\begin{split}\label{chi}
-    \chi_i &= \sup\bigg\lbrace x\ge 0: 
-\displaystyle\int_0^x 
-    \bar{P}_i(x) \ dx \le \sum_{j\in\mcI_i}b_i^j \bigg\rbrace,
+\begin{split}
+    \chi_i &= \sup\bigg\lbrace z\ge 0: 
+\displaystyle\int_0^z 
+    \bar{P}_i(z) \ dz \le \sum_{j\in\mcI_i} b_i^j \bigg\rbrace,
 \end{split}
 \end{align}
-$z = \min(\eta_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
+$e = \min(z_i, \chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
 \mcI_i$, 
 $$
-    v_i^j = e_i^j(z) 
+    v_i^j = e 
 $$
@@
 $$
-    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
+    w_i^j = \theta_i'(e).
 $$
@@
 %and fix $j$'s reserve price $p^j$ as is defined by (\ref{newprice}). 
-With reserve prices $p^j >0$, there exists a ``truthful" local game embeddeded
-in each local auction, and thus an equilibrium point for the local auction. 
+We have a ``truthful" local game embeddeded in each local auction, and an
+equilibrium point of
+the embedded local game is an equlibrium point for the local auction. 
 }\\
 \textbf{Proof:}
-For the buyer, we show that $t_i$ is an $\epsilon$-best reply. That is,
+For the buyer, we show that $t_i$ is and $\epsilon$-best reply. That is,
 $$
@@
 $$
-Let $z = \eta_i^j$. We have that $i\in\mcI^j$, 
-and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
-max of the reserve prices $p_i^j,\ \forall \ j\in\mcI_i$, therefore
-(\ref{eta}) is such that,
-$$
-    \theta_i'(z) > \bar{P}_i^j(z),
-$$ 
-which implies, as (MORE) $\theta_i'$ is non-increasing and $P_i^j$ is
-non-decreasing $\forall \ j \in \mcI_i$, 
+We have that $p_i^j=p_{i^*}^j \ \forall i\in\mcI^j$ and is the lowest price that $j$
+will accept to perform any allocation. By the definition of ``reserve
+price", $j$ is willing to buy (all) its own data $D^j$ at price $p^j$. For
+each $i \in \mcI^j$, 
+$$
+    y_i^j = \min_{j\in\mcI_i} (p_i^j).
+$$
+Let $e = z_i^j$, since $\theta_i'$ is non-increasing
+and, $P_i^j$ is non-decreasing, and so 
+$$
+    \theta_i'(e) = w_i^j  \ge P_i^j(v_i^j),
+$$ 
+holds for any $j$. Therefore, as $i$'s strategy guarantees that $i\in\mcI^j$, 
+and (\ref{buyerinversedemand}) defines $e$ as being
+max of the reserve price $p^j$ of any $j\in\mcI_i$, 
 \begin{align*}
-    w_i^j &> P_i^j(v_i^j) \\
-    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
+    v_i^j \le D^j - d^j(w_i^l).
 \end{align*}
-And so, (MORE)
-\begin{align*}
-    a_i^j(t_i) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\mcI_i} \bar{a}_i^j(t_i) &= z.
-\end{align*}
-Therefore,
-\begin{align*}
-    \displaystyle\sum_{j\in\mcI_i}\int_0^{v_i^j} P_i^j(x) \ dx &=  \int_0^{x}
-    \bar{P}_i^j(x) \ dx \\
-    &= \sum_{j\in\mcI_i}\int_0^x P_i^j(x) \circ e_i^j \ dx.
-\end{align*}
-(FINISH!)\\
-Now suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^k(s_i;s_{-i}) > u_i^k(t_i;
-s_{-i}) + \epsilon$. Suppose there is a seller such that $\mu = e_i^k\circ a_i^k(s)$, also $\zeta = e_i^j\circ
-a_i^j$, and $s_{i^*} = (\zeta_i,p_i)$.
-
-Then from
+Now suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i(s_i;s_{-i}) > u_i(t_i;
+s_{-i}) + \epsilon$. Let $\xi = \min_k e_i^k\circ a_i^k(s)$, and $\forall \ j,
+\zeta_i^j = \xi/\vs_i^j$ and $s_{i^*} = (\zeta_i,p_i)$. Then from
 (\ref{coordination}), $a_i^j(s_{i^*}; s_{-i}) = \zeta_i^j$, therefore
@@
 $\xi > \bar\epsilon$ show a contradiction.
-(SELLER FINISH)\\
+
 This forms a ``truthful" local game embeddeded within $j$'s auction with strategy space
@@
 
-\bibitem{matt}
-Matthias Roggendorf and Fernando Beltr{\'a}n,
-\textit{Simulation Model for the Dynamic Allocation of Network Resources in a Competitive Wireless Scenario}.
-Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
-pp. 54 - 64.
-
 \end{thebibliography}

### 2019-08-21 PSPorig.tex
On hold.

--- 2018-05-05 paper_wc.tex
@@
-%\documentclass[journal,comsoc]{IEEEtran}
-\documentclass[sigconf, anonymous]{acmart}
-
-%\usepackage[text={6in,8.1in},centering]{geometry}
-
-\usepackage{enumerate}
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage{mathrsfs} % to use mathscr fonts
-
-\usepackage{multicol}
-\usepackage{url}
-
-\usepackage{epstopdf}
-\usepackage{caption,subcaption}
-\usepackage{pstricks}
-\usepackage{pst-solides3d}
-\usepackage{pstricks-add}
-\usepackage{graphicx}
-\usepackage{pst-tree}
-\usepackage{pst-poly}
-\usepackage{calc,ifthen}
-\usepackage{float}\usepackage{multicol}
-\usepackage{multirow}
-\usepackage{array}
-\usepackage{longtable}
-\usepackage{fancyhdr}
-\usepackage{algorithmicx}
-\usepackage[noend]{algpseudocode}
-\usepackage{changepage}
-\usepackage{color}
-\usepackage{listings}
-\usepackage{fancyvrb}
-\usepackage{verbatim,moreverb}
-\usepackage{courier}
-\usepackage{algorithm}
-
-\newcommand{\vs}{\varsigma}
-\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcI}{\mathcal{I}}
-\newcommand{\g}{\sigma}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-\iffalse
-
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{corFollary}{Corollary}[section]
-\newtheorem{sublemma}{Lemma}[lemma]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\headsep25pt\headheight20pt
-\setcounter{secnumdepth}{4}
-\pagestyle{fancyplain}
-\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
-\cfoot{\ \hfill\tiny\sl Draft printed on \today}
-\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
-
-\fi
-
-%---------------ACM CCS---------------------%
-\fancyhf{} % Remove fancy page headers 
-\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
-\fancyfoot[C]{\thepage}
-
-\setcopyright{none} % No copyright notice required for submissions
-\acmConference[?]%Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
-\acmYear{2017}
-
-\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
-%-------------------------------------------%
-
-\begin{document}
-%\begin{multicols}{2}
-\title{Title?}
-
-\begin{abstract}
-We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
-Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
-gained by charging users a fixed fee for a maximum amount
-of data usage in a month, i.e., a monthly data cap \cite{???}. 
-2cm's (2nd exchange market) data exchange platform allows users to submit
-bids to buy and sell data.
-This usage model, is, as far as our knowledge, the first data trading
-platform that allows customers to buy and sell their own data.
-We describe a distributed auction mechanism for data exchange inspired by the
-classic PSP throughput problem,
-and prove that our distributed data exchange mechanism provides incentive
-compatibility (social choice function), and that we have efficiency
-using only partial valuation information of each participant in an exchange market.
-
-In applying a distributed PSP implementation to CMHK market, we
-find that
-the market is able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and design our mechanism tp provide the functions
-for effective communication between the connected users. We claim that in
-this secondary market our formulation holds the desired VCG qualities through the construction of a
-probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
-with respect to the classic throughput problem.
-and provide simulated results on convergence time to support our (FIND
-COMPETITVE RATIO!), and a bound
-on the convergence of our mechanism. We extend the works of cite!cite!
-i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
-market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
-\end{abstract}
-
-\iffalse
-% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002978.10003029.10011703</concept_id>
-<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
-
-\keywords{template; formatting; pickling} % TODO: replace with your keywords
-\fi
-\maketitle
-
-\section{Introduction}
-
-(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
-SENTENCES)
-In this work, we propose \emph{a distributed progressive second price (PSP) auction in
-order to maximize social utility in the CMHK market}. Using the
-distributed PSP mechanism on CMHKs data
-exhange platform, we show that for cellular data allocated between multiple users there
-exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
-demand information is not known centrally, rather, it is distributed in the
-buyers' valuations. The mechanism for an auction is defined
-as \emph{distributed} when the allocations at any element depend only on
-\emph{local} state: the quantity offered by the seller at that element, and the
-bids for that element only \cite{lazar}. In this work, the proposed mechanism
-allows the distribution of bids, where there are many ISPs each holding
-thier own local auction; there is no entity that holds a global market knowledge.
-
-In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
-using its own demand functions). Buyers submit bids cyclically until an
-($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.
-
-(HOW DO WE MODEL ISP REVENUE? FUTURE WORK?)
-
-The form of the auction mechanism presented here is described as a \emph{locally}
-pure-strategy progressive game with incomplete, but perfect information.
-In a distributed setting, local markets have perfect local information, since you know what each move of the opponent is.
-However, since users are not aware of behavior in other auctions, it is a game of incomplete information.
-We complete a comprehensive analysis of market dynamics, and will assume
-complete and perfect information in order to verify properties and validate
-results of the auction mechanism.
-
-(TO ORGANIZE)\\
-The main contribution of this work 
-is an auction mechanism inspired by the classic PSP throughput problem. In
-order to apply a distributed PSP implementation to the CMHK market,
-we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the communication
-expense from numerous local auctions trading an infinitely divisible resource.
-We will assume that the cost of participating in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. It is worth mentioning that CMHK users are not allowed to resell data
-purchased from the CMHK
-market, additionally, the purchased data does not carry to the next
-service period. Therefore, a market equilibrium, where
-supply equals demand, requires that users maintain incentive for truthfullness
-across a distributed setting.
-To the best of our knowledge, this is the first work to provide a truthful
-mechanism in a distributed setting for data-exchange based on market behavior.
-\\
-\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
-restrictions introduced by the CMHK secondary market. We reserve this for
-future work.
-
-We claim that the CMHK market is
-able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and as our mechanism provides incentives
-for optimal, effective communication between the connected users.
-
-Despite the small message space, with many user types, there is no single
-way to do the transformation from the direct revelation mechanism to the
-desired one. Our mechanism is designed by guessing
-right direct-revelation-to-desired-mechanism transformation and building it
-into the allocation rule to be the primary step in the design. This incentive for a user to
-truthfully reveal its type is built into the user strategies. As in classic
-mechanism design, we determine the equilibria as result of incentive
-compatibility in our mechanism design. 
-We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead 
-and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
-with respect to the classic throughput problem.
-
-The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
-construction of the user strategy space results in truthful bids that are optimal for all users,
-i.e. bid prices are to the marginal value as determined by market dynamics. 
-This is the (built-in) transformation from the
-direct-revelation mechanism to the desired message space.
-
-The paper is organized as follows...
-
-\subsection{Distributed Progressive Second Price Auctions}
+%\iffalse
+\section{Distributed Progressive Second Price Auctions}
 
@@
 i.e. $p_i^j = {\theta_i^j}'$.
-
-\subsection{Motivation for Privacy/Security}(NEW SECTION)
-
-A property of PSP is that the user valuations are held private.
-
-1. The seller doesn't update with the ISP, and so does not know the market price
- in the data-exchange market.\\
-2. The auction is distributed, so there is no collusion between sellers and
-ISP.\\
-3. The mechanism is self-contained, and only requires participation. (THINK!)
-4. Better economy, as few users will get data plans with a lot of data, make
-money, allowing others to have cheaper data plans and not pay a lot for
-texting, phone calls (Buzzfeed). Free market capitalism! \\
-(CONCERN HERE ABOUT THROTTLING)
-
-\section{Related Work}
-
-\section{The Problem Model}
-
-\subsection{The CMHK Market}
-
-We construct the model for a PSP data auction for mobile users
-particpating in CMHK's secondary data-sharing market.
-Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
-data from other users. We again define the bidding profile for any user to be 
-$s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
-$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
-set of opponent profiles. We assume that the users are connected.
-A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. We assume
-that users are selfish, and therefore rational. 
-Thus we assume that all users submit bids in order to maximize their
-(private) valuation functions. 
-In general, user preferences are defined by a utility function, $u$, which 
-represents a users' valuation of an allocation minus the price.
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We assume that data is a unary resource belonging to the seller, and
-therefore we identify each local auction with the identity of the seller
-$j\in\mcI$.
-We further show that user valuation satisfies the conditions for an
-\emph{elastic demand function}, as in \cite{lazar}.
-Finally, we assume in the CMHK market that a buyers' budget is always
-sufficient, as the alternative is to pay the overage fee to the ISP.
-
-The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
-the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
-separated (a seller does not also buy data and vice versa). Thus, we may assume
-that this is implied in our notation.
-A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
-belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
-the bid belongs to a \textbf{seller}.
-Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
-meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
-a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
-auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
-(0,0)$. Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
-$j$. We additionally determine that a user who does not submit a bid is holding
-its previous bid, either zero or nonzero. For the purposes of our analysis, we will assume that a zero bid from a
-buyer is equivalent to no bid.
-A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
-with the intent of offering a
-quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
-with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
-stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
-by the user type, whether or not they are  a buyer or a seller. 
-To further clarify our analysis, we will emphasize the separation of buyers and
-sellers using
-$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
-In other words, a bid $s^j =
-[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
-secondary market. The notational conventions of the bid vectors are essentially 
-slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
-[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
-Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
-d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
-d_i^j$ represent the
-total amount of data requested by buyer $i$.
-
-Consider the grid of bid proiles, $s$, representing the distributed PSP auction
-mechanism in the CMHK market, each buyer $i$ will
-have information from each seller $j$, as well as opponent profiles $s_{-i}$
-from each auction in which it is participating, and therefore
-in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
-$i$ gains access to the full grid $s$. However, 
-sellers can only gain information about the market grid by observing buyer
-behavior in their local auction.
-In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
-influence the CMHK market dynamics, with the sellers taking a secondary role
-(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
-
-\subsection{User Valuation}
-
-We assume that the CMHK market does not have network
-bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper. We derive a globally optimal strategy suited for
-users with local information in a distrubuted data-sharing model.
-
-Our mechanism allows a buyer
-to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
-utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
-part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
-will determine its bid quanities by,
-\begin{equation}\label{opt-out}
-    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
-\end{equation}
-In a general sense, this abstraction applies our \emph{user strategy}
-to the PSP rules.
-% OPT-OUT BUYER
-We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
-\begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ (\g_i(a)) - c_i,
-\end{equation}
-where the composition of the elastic valuation function $\theta_i$ with $\g_i$
-distributes a buyers' valuation of allocation $a$ across local markets (and thus
-multiple sellers).
-In this way we extend the PSP rules described
-in \cite{semret} to design equilibria across subsets of local data-exchange markets.
-
-The sellers, $j\in\mcI$ are not associated with an opt-out function, we
-consider their valuation to be a functional extension of the buyers, where
-$\theta^j$ is constructed by buyer demand.
-The sellers strategy can only be to determine the reserve price of their local
-auction, using only information from buyers who have not opted out.
-In our analysis, we demonstrate market dynamics, and further show evidence of symmetry in the strategies of
-buyers and sellers.
-
-\subsubsection{Valuation under Market Dynamics}
-The buyer demand largely motivates the market price function, however, the
-distributed nature of the market prevents any single user from knowing the
-market demand for a quantity of data. All users have knowledge of market
-supply, as this is public information, however only buyers
-are able to determine supply or demand across multiple auctions, and then only from auctions
-in which they participate. \\
-\textbf{Remark:}
-It is possible that a seller would be able to derive information about other
-auctions by examining buyer bids over time, particularly if the seller had knowledge of the
-buyer strategy. (FUTURE WORK?)\\
-
-We interpret the collection of local auctions as collection of congestion games,
-where a buyers' payoff depends on the dynamics of the set of local auctions it
-``chooses".
-In a multi-auction market, each auction a buyer joins has the potential to
-decrease the potential cost of its data. However, increasing the size of the
-auction implies a certain risk, which we may interpret as a potential and
-definite
-liability. Increasing the number of transactions causes additional messaging
-overhead, fees, and increased competition from other buyers. 
-A transaction also causes potential indirect costs, which may be considered work done to find
-sellers, or effort of communication from participation. A seller
-has the potential for greater profit with each new buyer in its auction, taking 
-the same risk.
-%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
-%and the individual. We denote the potential indirect costs of participation of
-%each user as $\varrho$.
-The liability of any user is naturally absorbed into the bid fee $\epsilon$,
-as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
-dependent on the association between two users and their market positions, in
-addition to the underlying network structure. Now, both sellers and buyers must consider
-the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
-OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)
-
-Elastic valuation functions allow for even infinitesimal changes in the market
-dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
-allows for the analysis of constraints imposed by the user strategies. 
-Buyers may directly impact each other in local market intersections.
-Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
-A buyers' valuation of an amount of data represents how much a buyer is willing
-to pay for that amount. 
-This is equivalent to the bid price, given a fixed amount of data,
-satisfying $\theta_i$. We determine the
-buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
-possible unit price. We have,
-% BUYER PRICING 
-\begin{equation}\label{buyerinversedemand}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
-\end{equation}
-where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
-$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
-We determine that the market supply function corresponds to an extreme of
-possible buyer demand, and 
-acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
-% BUYER DEMAND 
-\begin{equation}\label{datasupply}
-    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
-\end{equation}
-We note that $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Therefore, in a coordinated bid, the utility-maximizing bid price is the
-lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers. 
-%We will later show, in Proposition
-%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
-%bids, i.e. using the same bid for all auctions.
-
-A seller only has
-information from buyers in its own auction, and may only be indirectly influenced by
-buyers in other auctions. So from the perspective of the
-seller we have a more direct interpretation of valuation as revenue.
-We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} \g_i^j(a), 
-\end{equation}
-and define the ``inverse" of the buyer demand function for seller $j$ as
-potential revenue at unit price $y$, we have, 
-% SELLER REVENUE 
-\begin{equation}\label{sellerinversedemand}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
-price.
-
-The valuation of any user must be modeled as a function of the entire
-marketplace. 
-Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
-\circ \g_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
-(\ref{datademand}) and (\ref{sellerinversedemand}). We first note that, in
-general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
-$$
-    \theta(x) = \int_0^x f(z) \ dz,
-$$ 
-as in \cite{semret}. Now, we have the following Lemma,
-{
-\lemma{(User valuation)}\label{uservaluation}
-For any buyer $i\in\mcI$, the valuation of a potential
-allocation $a$ is, 
-\begin{equation}\label{buyervaluation}
-    \theta_i \circ \g_i(a) = \displaystyle\sum_{j\in\mcI}
- \int_0^{\g_i^j(a)} f_i(z) \ dz.
-\end{equation}
-Now, we may define seller $j$'s valuation in terms of revenue,
-\begin{equation}\label{sellervaluation}
-    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ \g_i^j(a) = \sum_{i\in\mcI}
- \int_0^{\g_i^j(a)} f^j(z) \ dz.
-\end{equation}
-We have that $\theta_i$ and $\theta^j$ are elastic valuation functions, with
-derivatives
-${\theta_i}$ and ${\theta^j}'$ satisfing the conditions of elastic demand.
-}
-\textbf{Proof:} 
-Let $\xi$
-be a unit of data from buyer bid quantity $\g_i^j(a)$.
-If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
-similarly decrease. The lost potential revenue for seller $j$ is the price of
-the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
-$$
-    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
-$$
-Thus (\ref{sellervaluation}) holds.
-As we may use the same argument for (\ref{buyervaluation}), as such, we will
-denote $f_i=f^j=f$ for the remainder of the proof. We observe that the function
-$f$ is the first
-derivative of the valuation function with respect to
-quantity. Letting $\theta_i=\theta^j=\theta$, the existence of the derivative implies $\theta$ 
-is continuous, and therefore, in this context, $f$ represents
-the marginal valuation of the user, ${\theta}'$. Also, clearly
-$\theta(0)=\theta(\sigma(0)) = 0$. Now, as we consider data to be an infinitely
-divisible resource, we have a continuous interval between allocations $a$ and
-$b$, where $a\le b$. Now, as $\theta$ is continuous, for some $c\in[a,b]$, 
-$$
-\theta'(c) = \lim_{x\to c}\frac{\theta(x) - \theta(c)}{x-c} = f(c),
-$$
-and so $f=\theta'$ is continuous at $c\in[a,b]$, and so as $a\ge 0$, 
-$\theta'\ge 0$. Finally, we have that concavity follows from the demand
-function. Then, as $\theta'$ is
-non-increasing, we may denote its derivative $\gamma \le 0$,
-and taking the derivative of the Taylor approximation, we have, $\theta'(z) \le
-\theta'(\eta) + \gamma(z-\eta)$.
-$\qed$
-
-Utility is defined by their valuation, and is the basis for user behavior. 
-The sellers' natural utility is the potential
-profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
-paid to the ISP, as it is not a component of our mechanism, and as a discussion
-of mobile data plans is outside the scope of this paper.  
-Now, a rational user will try
-to maximize its utility, thus, user incentive manifests as a
-response to market dynamics. A buyer has the choice to
-opt-out of any auction, and as a seller will try to sell the maximum amount of
-data, the highest possible reserve price is conditioned by ``natural" constraints. Utility-maximization 
-acts as revenue maximization for a rational seller, and as cost minimization for a
-rational buyer. Thus, for each user $p_i^j \ge \min\big(p_i^j)$ and $p_i^j \le
-\max\big(p_i^j)$, which holds $\forall \ i, j\in\mcI$ such that $s_i^j>0$.
-Now, rational buyer does not want to purchase extra data, as this would be
-equivalent to overpaying, however $i$ submits positive bids to a set of
-sellers, and a rational seller will attempt to maximize profit, and so will try and sell all of
-its data. Therefore,
-\begin{equation}\label{bidcap}
-    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j \quad\text{and}\quad
-\sum_{j\in\mcI} d^j_i \ge D_i,
-\end{equation}
-which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
-constraint from our formulation.
-Thus, at equilibrium all users are satisfied, and 
-$D^j = D_i$, although we observe that this result
-does \emph{not} imply that $s_i=s^j$.
-
-We further determine that the set of buyers and sellers participating
-in a single equilibrium is bounded by the potential indirect costs of
-participation. We will denote this individual cost to each user as
-$\varrho$. The indirect cost is the portion of the bid fee
-$\epsilon$ that is dependent on the underlying network and the individual.
-Observing that $\varrho$ indirectly effects user utility,
-and therefore acts to establish a natural budget for each user. We give this
-constraint as, 
-\begin{equation}\label{poolbnd}
-    u \le \varrho,
-\end{equation}
-which may be interpreted as the effort a rational user is willing to expend
-on its message space, and serves to limit the size of the buyer/seller pools. 
-Additionally, in congestion games,
-overly-frequent bid updates can result in an auction being
-overloaded, similarly to a DOS (denial-of-service) attack, thus the
-``liability" component of $\epsilon$ attempts to regulate bid flooding.
-
-Finally, it is worth mention that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, in order to derive properties.
-The mechanism itself does not require any knowledge of user demand or
-valuation. 
-\subsection{PSP for Data-Exchange}
-
-% MECHANISM
-\subsubsection{Data Auction Mechanism}\label{datamechanism}
-We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the CMHK market, and which we will denote the \emph{data}
-PSP rules. The rules presented here incorporate of the opt-out function with the
-mechanism as in \cite{lazar}, which we note greatly simplifies our
-analysis. 
-The market price function (MPF) for a buyer in the CMHK market
-can be described as follows:
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
-order to obtain
-data amount $z$ given opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices
-of the individual sellers may vary.\\
-\textbf{Remark:} We further note that except at points of discontinuity, from
-Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
-(THE ABOVE IS GOOD, BUT DOESN'T FIT MY CONSTRUCTION, CHANGE TO BELOW?)
-The market price function (MPF) for a buyer in the CMHK market
-is determined per (\ref{buyerinversedemand}), and is defined as,
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ j\in\mcI \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-and is interpreted as the price that buyer $i$ bids in
-order to obtain
-data amount $z$ given opponent profile $s_{-i}$.
-The sellers pricing function is according to (\ref{sellerinversedemand}), 
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}^j(z, s_{-i}) =\displaystyle\sum_{i\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\sup\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z), \ \forall \ i\in\mcI \bigg\rbrace \bigg).\\
-\end{split}
-\end{align}
-We note that
-the total price cannot be an aggragation of the
-\emph{individual} bid prices as it is possible that the reserve prices
-of the individual sellers may vary, which contradicts
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}).\\
-\textbf{Remark:} We further note that except at points of discontinuity, from
-Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
-%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
-%buyer $i$'s bid quantity. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is: 
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}\label{datacomposed}
-    \bar{D}_i^j(y,s_{-i}^j) &= \g_i^j \circ D_i^j( y,s_{-i}^j)\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
-\end{split}
-\end{align}
-It follows from the upper-semicontinuity of $D_i^j$ that for $s_{-i}^j$ fixed, $\forall \ y,z \ge 0$,
-\begin{equation}\label{dtop}
-    \g_i^j(z) \le \g_i^j \circ D_i^j(y,s_{-i}^j) \Leftrightarrow y \ge \g_i^j
-\circ P_i^j(z,s_{-i}^j).
-\end{equation}
-% DATA ALLOCATION RULE
-The resulting data allocation rule is a function of the local market
-interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
-allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-\begin{split}
-    \bar{a}_i^j(&s) = \g_i^j \circ a_i^j(s) \\
-    &= \min\bigg\lbrace \g_i^j(a), 
-    \frac{\g_i^j(a)}{\displaystyle\sum_{p_k^j= p_i^j}\g_k^j(a)} 
-D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
-\end{split}
-\end{align}
-noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool.
-Finally we must have that the cost to the buyer adheres to the second price
-rule for each local auction, with total cost to buyer $i$,
-% DATA COST
-\begin{align}\label{datacost}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-    p_i^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
-    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
-\textbf{Remark:} The cost to buyer $i$ adds up the willingness
-of all buyers excluded by player $i$ to pay for quantity $\bar{a}_i^j$. i.e.
-$$
-    c_i^j(s) = \displaystyle\int_0^{\bar{a}_i^j} P_i^j(z, s_{-i}) \ dz.
-$$
-This is the ``social opportunity cost" of the PSP pricing rule.
-
-The formulation is inspired to the thinnest allocation route for
-bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
-satisfy $i$'s demand, then
-(\ref{buyerutility}) reduces to the original form, defined in
-\cite{semret} as ``a simple buyer at a single resource element".
-
-(OWN WORDS!)
-The cost function will therefore be a stepwise-linear function, which is
-increasing in slope with each new bidder excluded from the market.
-
-\subsection{User Behavior}
-
-\subsubsection{Buyer Strategy}
-
-Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
-is also reasonable to expect that a seller may come close to using their
-entire data cap, and only sell the fractional overage. In this case, a buyer
-must split its bid among multiple sellers. 
-The buyer strategy bids in auctions with the highest quantities first,
-a natural exploitation of the demand curve. A new seller entering the market
-with a large quantity of data will be in high demand. This behavior contributes to market price
-stability, as seller valuation is determined by buyer demand, the
-buyer strategy tends towards equal valuation of all local markets, and therefore
-similar prices. If a buyers' demand is not satisfied, they will need to bid in
-markets with smaller data quantities, and so will bid on a larger portion of
-the sellers' bid quantity, increasing their unit price. Market equilibrium is achieved when each buyer has equal bids in
-each auction. Our bidding strategy is inspired by \cite{lazar}, and we also
-hold buyers to consistent bids, where buyers sumbit identical bids to a
-subset of sellers with the highest offers. In the remainder of this section, we
-will make the assumption of truthful bids from the buyer, although this
-analysis is left to Section \ref{analysis}.
-Thus, we determine when rational (utility-maximizing) buyers opt-out of a local auction. 
-We propose the following strategy, 
-% BUYER STRATEGY
-{
-\lemma{(Opt-out buyer strategy)}\label{buyerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t>0\in\tau$, and let $a$ be $i$'s desired allocation. 
-% OPT-OUT BUYER STRATEGY
-Define the composition,
-$$
-     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity.
-Also define the set,
-% MIN SET
-$$
-    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
-n}\sum_{j\in\mcI'} D^j,
-$$
-where buyer $i$ chooses its seller pool by determining $n$ as,
-\begin{align}
-\begin{split}\label{buyercoordinate}
-    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
-    %\wedge \sum_{j\in\mcI(n)}&\g_i^j(\varrho) \le \sum_{j\in\mcI(n)} \theta_i^j(\g_i^j(a)) \big\rbrace. 
-    %&\wedge \g_i(\varrho) \le \theta_i(\g_i(a)) \big\rbrace. 
-\end{split}
-\end{align} 
-The buyer strategy produces a minimal subset of sellers $\in \mcI$ 
-able to satisfy buyer $i$'s demand while ensuring that the size of $\mcI^j$
-does not allow the overhead to outweigh the valuation of the data. For 
-fixed $n$ we will denote this subset,
-\begin{equation}\label{sellers}
-    \mcI_i \subset \mcI.
-\end{equation}  
-Now let $j^* = n \le I$ represent the seller with the least amount of data
-$\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$, and define $i$'s bid
-vector $\g_i$ with respect to its strategy, where
-\begin{equation}\label{opt-eq}
-    \g_i^j(a) \triangleq \begin{cases} \g_i^{j^*}(a), \quad j\in\mcI^j,\\
-            0, \quad j\ni\mcI^j.\end{cases}
-\end{equation}
-and define bid price $p_i^j = \theta_i'(\g_i^j(a))$.
-Now, (\ref{opt-eq}) holds $\forall \ j\in\mcI$,
-and we have an optimal strategy for buyer $i$.
-}\\
-\textbf{Proof:}
-We assume that a buyer will try and fill their data requirement.
-In the case that there exists a seller who can completely satisfy a buyers'
-demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
-as the set $\mcI_i$ is ordered by the quantity of the sellers' bids, $i$ may discover 
-$j^*$ by computing $\mcI_i$.
-Suppose that $D_i >
-\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
-We model the ISP at time $t>0$ as a seller $\kappa$ with bid $s^\kappa
-=(d^\kappa, p^\kappa)$,
-where $d^\kappa > D^j, \
-\forall \ j\in\mcI_i$, and
-$p^\kappa$ represents the overage fee for data set by the ISP, which we note is also the upper bound of the sellers'
-pricing function.
-Consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
-The allocation rule (\ref{dataallocation}) determines that the data will be
-split proportionally
-between all buyers with the same unit price. 
-It is possible that the resulting partial allocation of data to $i$ and $k$
-would not satisfy some demand. As the two cases $i$ and $k$ are the same, we
-will only consider one. Suppose seller $j$ updates its
-bid to reflect the new data quantity, where
-$d_i^{j(t+1)} < \g_i^{j(t)}(a)$. First, $i$ sets its bid to $s_i^j = 0$, and
-from the new subset $\mcI_i$, submits bids until
-$\sum_{j\in\mcI_i} \g(a)_i^j \ge D_i$, by (\ref{bidcap}).
-Now, we consider the case where a new buyer $k$ with bid
-price $p_k^j > p_i^j$ for some $j \ \in \mcI_i$, in other
-words, a new buyer $k$ may enter the market with a better price, decreasing the
-value of $i$'s bid for $j\in\mcI_i$. In this case, by (\ref{buyercoordinate}),
-$i$ will choose $\mcI_i$ so that, $\g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a)$,
-and so $\mcI_i$ is large enough to balance the additional demand from
-$k$. Finally, we consider the case where $\vert\mcI^j\vert = I$, where the
-demand of buyer $i$ exceeds the supply, and the case where $\g_i(\varrho) >
-\theta_i(\g_i(a))$, where the overhead exceeds the current valuation of the
-data. Then, by (\ref{buyerinversedemand}), the valuation of the data increases until either
-the demand is satisfied, the debit from the overhead costs are balanced
-(\ref{poolbnd}), or the upper bound of the sellers' reserve price
-$p^\kappa$ is reached. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal.
-$\qed$\\
-\textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
-are complementary. In fact, the buyer strategy is the first term in the
-minimum, the second term being owned by the seller.
-
-Finally, we note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, in fact, by
-restricting the size of the set $\mcI_i$, we would be able to improve the
-computation time of buyer $i$, at the cost of increasing the price.
-
-\subsubsection{Seller Strategy}
-In order to to develop the seller strategy, we examine the incentive of a
-rational seller with only local information in a dynamic market of many
-buyers and sellers. A local auction, examined independently, may appear as
-single market with a single seller and many buyers, but is in fact a subset of the
-larger data-exchange market, and is subject to the trends and dynamics
-therewithin. A seller must determine allocations using only bids in its local market, while the buyers' response is based on the
-allocations and resulting opponent bids from all auctions in its seller pool.
-In addition, buyers are allowed to bid both dynamically and asychronously. 
-In order to
-maximize revenue, the seller must also be able to respond dynamically to
-address the mutation of competitive bids in its market. In order to do this, we
-determine that the seller may modify its reserve price in response to the
-changing market dynamics.
-
-We will show that sellers are able to maximize revenue in restricted subset of
-buyers in $\mcI$, and as such will attempt to facilitate a local market
-equilibrium for this subset. A local auction $j$ converges when all buyer bids
-remain the same over a time step, that is, if $\forall \ i \in\mcI$,
-$s_i^{j(t+1)} = s_i^{j(t)}$, at which point the allocation is stable, the data
-is sold, and the auction ends. In the sellers' local environment, we determine
-that the best course of action is to maximize revenue, and then try to keep its
-buyer pool stable until convergence occurs. Thus, the seller strategy is
-complementary to that of the buyers, and is designed to achieve and maintain a
-local market equilibrium.
-
-We describe a \emph{local} auction strategy for data allocation, where the seller is unaware of the existence of other auctions, and so
-the seller behavior is the same in the case of a single buyer, a small buyer set, and in the
-extreme case, where all buyers $i\in\mcI$ participate. We again note that the
-seller must initialize the strategy with a first iteration, and so the auction
-is defined for time $t>0$.
-In our model, a local auction may be described as a progressive game of strategy with
-incomplete, but perfect information, however in our analysis, as before, we will assume
-complete information. 
-(BUYERS ARRIVE AS A POISSON PROCESS? FUTURE WORK)
-
-% SELLER LOCAL STRATEGY
-{
-\lemma{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t>0\in\tau$.
-Define the set,
-$$
-    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
-n}\sum_{i\in{\mcI}'} p_i^j,
-$$
-where,
-\begin{equation}\label{sellercoordinate}
-    \min\bigg\lbrace n \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(n)}d_i^j
-\ge D^j \bigg\rbrace,
-\end{equation} 
-so that $n$ produces a minimal subset 
-of buyers that maximizes $j$'s revenue at time $t$, which we will
-denote, for fixed $n$, by,
-\begin{equation}\label{buyers}
-    \mcI^j \subset \mcI.
-\end{equation} 
-Define buyer $i^* = n-1 \le I$ as the buyer with the maximum bid price $\ni
-\mcI^j$.
-Then, for time $(t+1)$, set $j$'s reserve price to be, 
-\begin{equation}\label{newprice}
-    p_i^{j(t+1)} = p_{i^*}^{j(t)} + \epsilon,
-\end{equation}
-Let the winner at time $t$ be determined by,
-\begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i\in I^j} p_i^{j(t)},
-\end{equation}
-and update $j$'s total data to reflect the (tentative) allocation,
-\begin{equation}\label{newdata}
-    D^{j(t+1)} = D^{j(t)} - \g_{\bar{i}}^{j(t)}(a),
-\end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{sellercoordinate}) -
-(\ref{newdata}) produces a local market equilibrium. 
-}\\
-\textbf{Proof:}
-We assume that the seller will try to maximize its revenue. In the case where
-$\vert\mcI^j\vert =1$, then if $\g_i^j(a)=D^j$, then $j$'s market is at equilibrium.
-Otherwise, we arrive at the case of multiple buyers, which we note includes the
-case where $\g_i^j(a) < D^j$, which is reflected trivially here.
-
-For auction $j$ with multiple buyers, $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}), 
-Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
-In this case, by (\ref{bidcap}) the seller must notify $i$ of a
-partial allocation by changing the bid vector at index $i$.
-With this caveat, and Proposition \ref{buyerstrategy}, we have that the
-aggragate demand of subset $\mcI^j$ is satisfied by seller $j$, as in Lemma
-\ref{sellerconstraints}.
-Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that buyers are bidding truthfully, and so the new reserve price $p_{i^*}^j +
-\epsilon ={\theta_{i^*}}' + \epsilon$. For clarity, let the reserve price be denoted by
-$p_*^j$.
-Now, by the elasticity of (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}), we have that, $\forall \ z\ge 0$,
-$f_{i^*}(z) < f^j(z) \le f_i(z)$,
-which holds $\forall \ i \in \mcI^j$, and $\forall \ j \in \mcI_i$.
-We claim that the choice of reserve price $p_*^j$ does not force any buyers out
-of the local auction. To show this, we use the assumption of truthful bids, and
-the fact that since the auction begins at time $t>0$, buyers will
-bid at least once. As will be addressed in further analysis, we assume
-that a new bid price differs from the last bid price by at least
-$\epsilon$. Suppose the auction starts at equilibrium, so $\sum_{i\in\mcI^j}
-\g_i^j(a) = D^j$ at time $t=0$. The reserve price $p_*^j$ set at time $t=0$
-begins the auction with the first bid iteration, and so at $t>0$, $\forall \ i \in
-\mcI^j$, we have that $p_i^j - p_*^j \ge \epsilon$.
-Now, in the case where at $t=0$, $\sum_{i\in\mcI^j} \g_i^j(a) > D^j$, by
-(\ref{dataallocation}), the seller notifies (any) buyer $k$ with the lowest bid
-price of a partial allocation by changing
-$d_k^j$ thus by Proposition \ref{buyerstrategy}, $k$ either decreases its
-demand or increases its valuation until
-$\g_i^j(a) \le d_i^j$. Then, as the seller computes the set $\mcI^j$ at each time
-step, a new $i^*$ may be chosen and the buyers bid again.
-Suppose $\exists \ k \in \mcI^j$ such that $\forall \ l \ \in
-\mcI_k, \ i\ni \mcI^l \ \forall \ i\ne k\in\mcI^j$. That is, $k$ is
-disconnected from all other buyers $i\in\mcI^j$, and suppose that $d_k^j$
-is partial allocation at $t>0$, and further suppose that there are many
-$l\in\mcI_k$ where $\vert \mcI^l\vert > \vert\mcI^j\vert$. The more buyers an
-auction has, the more likely that cases will occur that cause buyers to rebid,
-particularly if auctions $l\in\mcI_k$ have overlapping buyers, then $k$ may
-opt-out of auction $j$, i.e. $s_k^{j(t)} \ne s_k^{j(t+1)} =
-0$, then the seller may simply return the tentatively allocated data to $D^j$.
-Finally, we note that if for some $i\in\mcI^j \ \exists \ k\in\mcI^j$
-such that $p_{i}^j = p_k^j$, then the seller again notifies the buyers of a
-partial
-allocation by changing $d_i^j$ and $d_k^j$ by (\ref{dataallocation}).
-Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
-equlibirium created by $j$ is independently stable from time $t$ to $(t+1)$. 
-$\qed$
-
-\subsubsection{Market Dynamics under Strategy}
-
-We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. We model the impact of the dynamics of the
-data-exchange market on a local auction $j$. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. This gives an auction $j$ a natural logical extension into the
-global market through its buyers. We demonstrate that the symmetry between
-buyer and seller behavior, consequently strategies, stretches into a symmetry across subsets of local
-auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. Defining a single iteration of the auction, where a seller updates bid vector
-$s^j$, and the buyers' response $s_i$, to comprise a single time step, and we have the following Lemma,
-% USER UNION
-{
-\proposition{(Valuation across local auctions)}\label{userunion}
-For any $i,j\in \mcI$, 
-\begin{equation}\label{jtoi}
-j\in\mcI_i \Leftrightarrow i\in\mcI^j.
-\end{equation}
-Fix an auction $j\in\mcI$ with duration $\tau$ and define the influence sets of users. 
-The primary influencing set is given as,
-%(ALL THE SELLERS FROM EACH BUYERS POOL)
-\begin{equation}\label{lambda}
-    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
-\end{equation}
-with secondary influencing set,
-%(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
-\begin{equation}\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
-\iffalse
-(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
-\begin{equation}%\label{lambda}
-    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
-\end{equation}
-(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
-POOLS)
-\begin{equation}%\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
-\fi
-Define $\Delta = \Lambda \cup \lambda$.
-Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
-\begin{equation}\label{union-eq}
-    \displaystyle\sum_{j\in\Lambda} \theta_i^j = \sum_{i\in\lambda} \theta_i^j.
-\end{equation}
-}\\
-\textbf{Proof:}
-A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. Using Proposition \ref{sellerstrategy} and (\ref{jtoi}), we have that, 
-\begin{equation}\label{iff}
-    i\in\mcI^j \Leftrightarrow p_i^j > p_{i^*}^j,
-\end{equation}
-where
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price in auction $j$. By (\ref{buyerinversedemand}) $p_i^j \ge
-p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
-shift caused by the underlying dynamics.
-Consider $k\in\mcI^j$ at time $t$ where, for example, some buyer(s) enter the auction, and
-so (\ref{iff}) implies that
-$\sum_{i\in\mcI^j} \g_i^j(a) > D^j$. Now, $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
-$s_k^j>0$ will cause $k$ to initiate a shift. By Proposition \ref{buyerstrategy}, $k$ will set $s_k^j=0$, and begin to add sellers to its pool.
-Suppose that at time $t$, $j$'s market is at equilibrium, i.e.
-$\sum_{i\in\mcI^j} \g_i^j(a) = D^j$, and fixing all other bids, so 
-no buyer $i\in\mcI^j$ rebids. Unless $k$ adds a seller with a higher reserve
-price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
-auction ends. Otherwise, at some time $t\in[t+1,\tau]$, we must have that
-$\g_k^j \le D^j$, and $k$ rejoins auction $j$ or opts-out. Finally, overlooking market shifts and messaging
-overhead, we have that,
-$\forall \ i\in\mcI^j$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and (\ref{jtoi})
-holds.
-\iffalse
-Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
-of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
-s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
-\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
-\fi
-
-Now, the subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
-coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
-determines the unit price $p_{i}$ in buyer $i$'s bid.
-The reserve price (\ref{newprice}) of seller $j$ is determined at each
-shift, and is
-the lowest price that $j$ will accept to perform any allocation.
-Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
-[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
-\ \forall \ k \in\mcI_i$. 
-Using Proposition
-\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
-\ \forall \ k \in\mcI_i$.
-
-\iffalse
-Now, we have,
-\begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-\fi
-
-The incentive of each seller $\in\Lambda$ is to sell all of its data at the
-best possible price. In the simplest case,
-consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
-\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
-$\lambda = \mcI^j$. 
-Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
-clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-In all other cases, the sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
-%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-The set $\lambda$ represents all of the buyers influencing auction $j$, both
-directly and indirectly. 
-The bid price of buyer $i\in\mcI^j$ is determined by,
-\begin{equation}\label{maxbid}
-    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
-\end{equation}
-$\Lambda$ is the set of sellers directly influencing the bids of buyers
-in auction $j$. Now, the reserve price for auction $j$ is such that,
-\begin{equation}\label{resprice}
-    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
-\end{equation}
-from (\ref{newprice}). Now, by Proposition \ref{sellerstrategy}, in the absence
-of external influences caused by multi-auction market dynamics, we have 
-that $j$ maintains a local market equilibrium from time $t$ to $(t+1)$.
-From (\ref{lambda}) and (\ref{llambda}), $\Delta$ is defined by a seller $j\in\mcI$, where each
-user $k\in\Delta$ has some direct or indirect influence on $j$. 
-We may identify $\Delta$ by its dominant seller, and we denote $\Delta^j = \Lambda^j
-\cup \lambda^j$.
-
-Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$, and
-the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
-have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
-where,
-\begin{equation}\label{ordering}
-    p_*^k \le p_l^* < p_*^j \le p_i^*,
-\end{equation} 
-for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
-p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
-which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
-\ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
-(\ref{iff}).
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
-0$, for some $g\in\mcI_i$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
-where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
-p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
-a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
-such that $p_*^g \ge p_*^j$. Thus, we
-determine a direct influence as $l\in\mcI^k
-\cap \Lambda^j$, such that $p_l^* > p_i^*$,
-and an indirect influence as, for any $l\in\mcI^k
-\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
-
-Now, consider the subset $\Lambda^j$, by
-Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
-decreases its bid quantity so that $\sum_{i\in\mcI^j}
-\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
-\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
-p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the
-lowest bid price, the ``lowest clearing player",
-and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
-directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
-buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
-recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
-will attempt to regain equilibrium.
-Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
-then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
-seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
-p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
-\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
-case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
-where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).
-
-In each case we
-have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
-some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
-\begin{equation}\label{jdemand}
-    \int_0^{\g_i^j(a)} f^j(z) \ dz 
-    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
-\end{equation}
-therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-Thus, any bid ouside of
-our construction
-has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$, and therefore cannot cause shifts to occur except through a
-shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
-bids in any auction $q \ni \Lambda^j$,
-we have, $\forall \ k\in\mcI_i$,
-\begin{equation}\label{idemand}
-    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
-f^k(z) \ dz,
-\end{equation}
-which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
-\ref{sellerstrategy}..
-Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
-\begin{align}\label{tieqtk}
-    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
-\end{align}
-and
-\begin{align}\label{tkeqtl}
-    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
-\end{align}
-Thus, with a slight abuse of notation for clarity,
-\begin{equation}\label{funion-eq}
-    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
-\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
-\end{equation}
-where the result follows by construction, and the continuity of $\theta'$.
-$\qed$
-
-For completeness, in the case where the ISP $\kappa$ 
-does not adhere to the market dynamics, so $p^\kappa > p^j +
-\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
-bid fee.
-(NEED TO DO BETTER WITH TIME?)
-
-\subsubsection{Mechanism Realization}
-
-In order to represent the public platform of the secondary market, we model the ISP as
-a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
-in any auctions. At time $t=0$, a seller $k$ entering the market will have
-submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
-seller does not require a priori demand information to enter the market.
-Also, a new sellers' bid, $(D^j, \epsilon)$, is public knowledge. 
-\iffalse
-(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
-IMPLICATIONS?)
-We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. 
-\fi
-A buyer entering the market
-at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER! ALSO DO I REALLY NEED THE I.I.D?) is initialized as 
-an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
-probability $\mathcal{P}$,
-$$
-    \mathcal{P}[\epsilon\le X \le \kappa] =
-\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
-ds,
-$$
-where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
-density function of $X$.
-%may represent by some homogenous function of degree one (EXPAND?). 
-Thus the auction
-begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
-initializing bid prices.
-
-Consider a user seeking to prevent
-data overage charges by purchasing data from a subset of other network users.
-The sellers' auction will function as follows: at each bid iteration all buyers
-submit bids, and the winning bid is the buyer $i$ that has the highest price
-$p_i^j$. The seller allocates
-data to this winner, at which point all other buyers are able to bid again, and
-the winner leaves the auction (with the exception where multiple bidders bid
-the same price, where (\ref{dataallocation}) determines they will not fully
-satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
-sellers' data has been allocated. 
-% SELLER ALGORITHM
-\begin{center}
-\begin{algorithm}[H]
-\caption{(Seller progressive allocation)}
-\begin{algorithmic}[1]
-\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
-\emptyset$, compute
-$\mcI^{j(0)}$
-\State Update $s^j$ 
-\While{$D^j(t) > 0$}
-\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
-\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
-%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
-\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
-\State $s^{j(t+1)} \gets (d^j, p^j)$
-\State Update $s^j$
-\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
-\For{$k \in \bar\mcI$}
-\If{$p_k^j < p_{i*}^j$}
-\State $D^{j(t+1)} = d_k^{j}$
-\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
-\EndIf
-\EndFor
-\State Compute $\mcI^{j(t)}$
-\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
-\State $t \gets t+1$
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-\end{center}
-Each time step, $s^j$ is updated it is shared with all
-participating buyers. At this point buyers have the opportunity to bid again,
-where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$.
-
-% SELLER ALGORITHM
-\begin{center}
-\begin{algorithm}[H]
-\caption{(Buyer response)}
-\begin{algorithmic}[1]
-\State $p_{i(0)} \gets \epsilon$, $s_{i(0)} \gets (p_i, D_i)$, $D_t \gets D_i$, compute
-$\mcI_{i(0)}$
-\State Update $s_i$ 
-\While{$D_i(t) > 0$}
-\State $D_{i(t+1)}^j \gets \sum_{j\in\mcI_i}\g_i^{j(t)}(a)$
-\If{$D_{i(t+1)}^j < D_t$}
-    \State Compute $\mcI_{i(t)}$
-    \State $p_i \gets \theta_i(\g_i(a))$
-\EndIf
-\State $s_{i(t+1)} \gets (\g_i(a), p_i)$
-\State Update $s_i$
-\State $D_{i(t+1)}^j \gets D_{i(t)}^j$
-\State $t \gets t+1$
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-\end{center}
-Finally, we give a simple example of convergence to a local market equilibrium,
-where the buyers are assumed to respond with their truthful,
-$\epsilon$-best replies.
-\begin{center}
-\begin{tabular}{c|c|c}
-Name & Bid total & Unit price\\
-\hline
-A & 50 & 1\\ 
-B & 40 & 1.2\\
-C & 26 & 1.5\\
-D & 20 & 2\\
-E & 14 & 2.2
-\end{tabular}
-\end{center}
-Let $s^{(1)} = [(65,\epsilon)]_{i\in\mcI}$ and
-$s^{(2)}=[(85,\epsilon)]_{i\in\mcI}$. The buyer bids are as follows: 
-\begin{align*}
-    s_A &= [(0,0), (50,1)], \\
-    s_B &= [(0,0), (40,1.2)], \\
-    s_C &= [(0,0),(26,1.5)], \\
-    s_D &= [(0,0),(20,2)], \\
-    s_E &= [(0,0), (14,2.2)]. 
-\end{align*}
-Then at $t=1$, we have 
-bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}),\\ (20,p^{(2)}),
-(14,p^{(2)})]$, and so  $(D^{(2)},p^{(2)}) = (85, 1+\epsilon)$, The buyer response is,
-\begin{align*}
-    s_A &= [(50,1), (0,0)], \\
-    s_B &= [(40,1.2), (0,0)], \\
-    s_C &= [(0,0),(26,p^{(2)})], \\
-    s_D &= [(0,0),(20,p^{(2)})], \\
-    s_E &= [(0,0),(14,p^{(2)})].
-\end{align*}
-At $t=2$, $(D^{(1)},p^{(1)}) = (65,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}),\\ (40,p^{(1)}), (0,0), (0,0),
-(0,0)]$. $(D^{(2)},p^{(2)}) = (25, 1+\epsilon)$. Then,
-\begin{align*}
-    s_A &= [(25,p^{(1)}), (25,p^{(2)})], \\
-    s_B &= [(40,p^{(1)}), (0,0)], \\
-\end{align*}
-where we have removed bids to indicate winner(s) with a tentative allocation.
-At $t=3$, $(D^{(1)},p^{(1)}) = (50,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0), (0,0),
-(0,0)]$. $(D^{(2)},p^{(2)}) = (0, 1+\epsilon)$ and $s^{(2)}=[(25,p^{(1)}),
-(0,0), (26,p^{(2)}), (20,p^{(2)}),\\(14,p^{(2)})]$. Then,
-\begin{align*}
-    s_A &= [(25,p^{(1)}), (0,0))].
-\end{align*}
-At $t=4$ the auction ends.\\
-\textbf{Remark:} In the case where market resources do not satisfy (\ref{bidcap}), however as
-this constraint is not restricted in time, we reason that in the case of
-insufficient data in the market buyers may wait for additional sellers or
-purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, in
-the case of insufficient demand, where we may assume that data is held at time
-$t=0$ by $\kappa$ at bid price $\epsilon$.
-
-% VCG ANALYSIS
-\section{PSP Analysis}\label{analysis}
-
-\subsection{Equilibrium}
-
-We intend to show evidence shared network optima (a
-global optimum). 
-A buyer $i\in\mcI$ will have incentive to change its bid
-quantity if it increases its opt-out value $\g_i$, and therefore its utility (\ref{buyerutility}). 
-We will show that, without loss of utility, buyer $i$ may  
-use a ``consistent" bid strategy within its seller pool, i.e. $d_i^j = d_i^k, \
-\forall \ j,k \in \mcI_i$, and as such,
-Proposition \ref{buyerstrategy} supports an optimal strategy with respect to
-(\ref{buyerutility}). 
-Our result shows that a buyer may select $\mcI_i$ in order to maximize its
-utility while maintaining a coordinated bid strategy. 
-Reasonably, if $j^*< I$, a buyer may increase the size of its seller pool
-$\mcI_i$, thereby lowering its coordinated bid
-quantity while obtaining the same (potential) allocation $a_i$. 
-As buyer $i$ submits identical bids to multiple auctions, the bid price must be
-as high as the highest reserve price $p_i^j \in \mcI_i$.
-Buyer $i$'s bid then has identical bid price $p_i^j \forall \ j \in\mcI_i$. 
-We further note that $i$ optimal strategy does not require reducing its bid price to a
-minimum in each auction, where
-the bid quantity $\g_i^j(a)$ is still fufilled. The pricing rule of the PSP
-auction dictates that a buyer $i$ will pay the cost of excluding other players from
-the auction, and as $i$'s bid price reflects its valuation of it data
-requirement $D_i$ across all local markets, we have identical bid prices in
-each auction where $s_i^j>0$. Obviously, if $j\ni\mcI_i$, then $\theta_i^j = 0$.
-
-% BUYER COORDINATION
-{
-\lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
-Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
-For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be a
-tentative data
-allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
-\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
-\begin{align*}
-    z_i^j &= \g_i^{j}(a), \\
-    y_i^j &= \theta_i'(z_i^j).
-\end{align*}
-Furthermore,
-\begin{equation}\label{allocationcoordination}
-    a_i^j(z_i,y_i) = z_i^{j},
-\end{equation}
-and
-\begin{equation}\label{costcoordination}
-    c_i^j(z_i,y_i) = y_i^{j},
-\end{equation}
-where $i$'s strategy is as in Proposition \ref{buyerstrategy}.
-}\\
-\textbf{Proof:}
-As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
-u_i(s_i;s_{-i})$. In full notation, we intend to show
-$$
-    u_i((d_i,p_i);s) \le u_i((z_i,y_i);s_{-i}).
-$$
-Now, if there exists a seller who can fully satisfy $i$'s demand,
-then $\vert\mcI_i\vert = 1$, and the case is trivial as no
-coordination is necessary for a single bid. %(SPECIAL CASE OF MONOPOLY? THINK!)\\
-Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
-multiple sellers.
-We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
-$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $\sum_{j\in\mcI_i}u_i^j$.
-Buyer $i$ maintains ordered set $\mcI_i$ where the sellers with the
-largest bid quantities are considered first; the index of seller $j^*$ defines
-a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$.
-Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$, $\g_i^k(a) \le z_i^j = \g_i^{j}(a)$,
-and so, using (\ref{union-eq}), 
-\begin{equation}\label{minimaleq}
-    \g_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
-\end{equation}
-Now, the buyer valuation function (\ref{buyervaluation}), guarantees
-that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
-\ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
-be accepted. 
-As $\bar{D}_i^j$ is non-decreasing, $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j})\ge D_i^j(p_i^{k}).
-$$
-\iffalse
-Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$\g_k^{j}(a) \ge \g_i^{j}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
-partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
-As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j}(a)
-\ge \g_k^{j}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
-We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
-$$
-    {\theta_i}'(\g_i^{k}(a)) \ge {\theta_i}'(\g_i^{j}(a)) \ge y_i^j.
-$$
-Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$...
-\fi
-Thus (\ref{minimaleq}) holds and so, by (\ref{dataallocation}),
-\begin{align*}
-     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j, \bigg\lbrack D^{j} - \sum_{p_k^{j}> y_i^{j}}
-d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= \g_i^{j}(a)
-\end{align*}
-where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
-From (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
-0 \ \forall \ y < p_{i^*}^j$, and $\bar{D}_i^j(y, s_{-i}) =0 \le \epsilon
-\Rightarrow \g_i^j(a) = 0 \Rightarrow z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
-\begin{align*}
-    \displaystyle\sum_{j\in\mcI_i} c_i^j(z_i,y_i) =\sum_{j\in\mcI_i}
-c_i^j(z_i,p_i),
-\end{align*}
-thus (\ref{costcoordination}) simply shows that changing the price $p^j_i$ to $y^j_i$ does not exclude any
-additional buyers, as the bid $p^j_i$ was already above the reserve price of any
-seller $j \in \mcI_i$.
-We proceed to show that $x_i$ does not result in a loss of utility for
-buyer $i$, that is,
-$$
-    u_i \le u_i(z_i,y_i).
-$$
-From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = \g_i^j(a(z_i,y_i))$, 
-and so,
-$$
-    \theta_i\circ \g_i^j(a(z_i,y_i)) = \theta_i\circ \g_i^j(a),
-$$ 
-which holds $\forall \ j\in\mcI_i$.
-Therefore, by the definition of utility (\ref{buyerutility}),
-and the buyers' valuation (\ref{buyervaluation}), 
-\begin{align*}
-    &\theta_i\circ \g_i(a(z_i,y_i)) - \theta_i(a)\circ \g_i(a) \\
-    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
-    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - x) \ dx.
-\end{align*}
-Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
-$z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
-$\qed$
-%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
-
-\subsubsection{Incentive Compatibility}
-
-The property of truthfullness is an essential component of equilibrium in
-second-price markets. The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
-construction of the user strategy space results in truthful bids that are optimal for all users,
-i.e. bid prices are to the marginal value as determined by market dynamics. 
-To achieve incentive compatibility, we find that the opt-out buyer must choose
-this subset so that its overall marginal value is greater than its market price.
-We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
-has incentive to change its bid as a result of a market shift or partial
-allocation. We now show the necessary condition of a truthful reply, new bid
-prices must differ from the last by at least $\epsilon$, and prove that the
-resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
-In a truthful reply, the term $\epsilon/\theta_i'(0)$
-ensures that a new bid price differs from the last bid price by at least
-$\epsilon$, thereby ensuring that a buyer does not change its bid without
-correcting the effects of unstable shifts.
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a market equilibrium extending over a subset of connected
-local markets. 
-For a buyer $i$, define the set of possible $\epsilon$-best replies,
-\begin{equation}\label{e-bid}
-    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
-u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
-\end{equation}
-and the set of \emph{truthful} bids, 
-\begin{equation}\label{t-bid}
-    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
-\wedge p_i = \theta_i'(z)\rbrace,
-\end{equation}
-where $\wedge$ denotes the logical ``and" operator. We note that the ``strategic" set $T_i$
-is restricted by Proposition \ref{buyerstrategy}.
-We have the following Proposition,
-
-{
-\proposition{(Incentive compatibility across local auctions)}\label{incentive}
-Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
-$t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
-buyer $i\in \mcI^j$, let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
-\begin{align}
-\begin{split}\label{eta}
-    \chi_i &= \bigg\lbrace x\in [0,D_i] : 
- {\theta_i}'(x) > \max_{j\in\Lambda}P_i^j(x)\bigg\rbrace, 
-\end{split}
-\end{align}
-and $z = \sup(\chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
-\Lambda$, 
-$$
-    v_i^j = \g_i^{j}(z),
-$$
-and 
-$$
-    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
-$$
-Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
-(v_i,w_i) \in T_i\cap S_i^\epsilon(s_{-i})$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
-s_{-i})$.
-With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
-$\in\Delta$. Therefore, a fixed point $\in \Delta$ is a fixed point in
-the multi-auction game. 
-}\\
-\textbf{Proof:}
-We claim that $t_i$ is an $\epsilon$-best reply for buyer $i$. That is,
-$$
-    u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;s_{-i}).
-$$
-As a result of auction initialization, a seller $j$'s valuation defines its
-reserve price to be determined
-by a buyer $i \ni \lambda$, even if this price is zero, we have that $p^j =
-\epsilon \ge 0 \ \forall \ j \in\Lambda$.
-Let $z = \sup(\chi_i^j)$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, and $p_i^*= f_i \circ \g_i^j(a)$ denote the (coordinated) bid price of buyer $i$. 
-We have that $i\in\mcI^j$, 
-and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
-max of the reserve prices $p_*^j,\ \forall \ j\in\mcI_i$, therefore
-(\ref{eta}) is such that,
-$$
-    \theta_i'(z) > \max_{j\in\Lambda}P_i^j(v_i^j),
-$$ 
-which implies, as $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
-we have $\forall \ j \in \mcI_i$, 
-\begin{align*}
-    w_i^j &> P_i^j(v_i^j) \\
-    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
-\end{align*}
-And so, by (\ref{dataallocation}),
-\begin{align*}
-    a_i^j(t_i;s_{-i}) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\Lambda} a_i^j(t_i;s_{-i}) &= z.
-\end{align*}
-Therefore, $\forall \ j\in\Lambda$ and $\forall \ i \in \lambda$ such that
-(\ref{tieqtk}) and (\ref{tkeqtl}) hold,
-\begin{align*}
-    \int_0^{v_i^j} \bar{P}_i(x) \ dx 
-    = \sum_{j\in\Lambda}\int_0^{\g_i^j(z)} P_i^j(x) \ dx.
-\end{align*}
-It follows that,
-$$
-    u_i(t_i;s_{-i}) = \int_0^{z} \theta_i'(x) \ dx -  \g_i \ \circ \int_0^{z} \bar{P}_i(x) \ dx.
-$$
-Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
-s_{-i}) + \epsilon$. Propositions
-\ref{coordinationlemma} and
-\ref{buyerstrategy}, define the coordinated bid, $\nu_i=(\zeta_i, p_i)$,
-% = (\g_i\circ a_i(s), \ \theta_i'(z)) = (z_i, c_i),$
-using (\ref{tieqtk}) and (\ref{tkeqtl}),
-for each $j\in \Lambda$, $\g_i^j(a_i^j(\nu_i; s_{-i})) = \zeta_i^j$,
-then clearly $u_i(\nu_i, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
-u_i(s_i;s_{-i}) > \epsilon$. Denoting $\zeta_i^j$ (fixed) as $\zeta$, 
-$$
-    \int_z^{\zeta} {\theta_i}'(x) \ dx-\int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
-$$
-For concave valuation functions, the first-order derivative of $\theta$ at point
-$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
-/ \theta'(0)$ guarantees that new bids will differ by at least
-$\epsilon$, and as such, buyer $i$ will remain in
-any local auction with reserve price determined by (\ref{newprice}). We therefore
-verify that,
-$$
-    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
-dx \le \epsilon,
-$$
-and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
-$$
-    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
-\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
-$$
-If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
-$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
-\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
-Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
-\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
-exist.
-Finally, as we may consider $\Delta \subset \mcI$ to be a
-multi-auction game, our user strategies form a ``truthful" local game 
-with strategy space restricted to $\epsilon$-best replies from buyers $\in
-\lambda$. Therefore we have that a fixed point in the ``truthful" game is a fixed point for the auction. 
-$\qed$\\
-
-The strategy space of is comprised of a collection of bid, or ``strategy", vectors that
-together, describe the collection of congestion games. A change in buyer $i$'s
-utility, resulting from a change in strategy, equals the change in
-the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
-formulated by mapping the incentives of all users in a local auction to a
-single function. The goal of our analysis is to therefore construct a global potential function that encompasses
-all local markets. Then, we may determine a Nash equilibrium by finding a local
-optima of the potential function. Additionally, as the potential function also
-iterates, it may be used in an analysis of convergence. The
-convergence of a Nash equilibrium results from the progression of
-$\epsilon$-best replies, where each subsequent bid is a unilateral
-improvement, provided that $t_i$ is continuous in opponent profiles.
-From the original proof by \cite{lazar}, we observe that the collection of
-unconstrained truthful bids may be a subset
-of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
-%An essential component of determining the existence of a Nash equilibrium is 
-For this work, it suffices to show the continuity of the set of truthful
-$\epsilon$-best replies in the set of opponent bid profiles.
-In order to address continuity in a global sense, we must demonstrate
-continuity in the construction of our model.
-Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
-and determine the
-existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
-correspondence,
-{
-\definition{(Correspondence)}
-A correspondence is mathematically defined as an ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
-$Y$, i.e. any subset of the Cartesian product $X\times Y$.
-}
-
-In an economic model, a correspondence $(S_i,S_{-i},R)$ defines a map from $S_i$
-to the power set $S_{-i}$, where $R$ is a binary relation, i.e. $R \subset
-S_i\times S_{-i}$. The classic
-example of a correspondence in our model is the buyers' best response
-$B_i^\epsilon$, where, for the multi-auction,
-$S_i$ and $S_{-i}$ are built by repeatedly using the
-cartesian product over bid profiles. The power set 
-$S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
-product of ordered sets. 
-The best response is a reaction correspondence
-defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
-S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
-profiles $S_{-i}$. \\
-\textbf{Remark:} 
-The ease by which the game is constructed is a consequence of the the cartesian
-product on a 2-dimensional message space. \\
-A natural induced topology of this space is the product
-topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.
-
-Motivated by the symmetric nature of supply and demand, we determine the
-game-theoritical argument is complemented by an abstract-theoretical analysis.
-In fact, we may even be philosophically motivated, as the truth value of a bid
-is determined only by how it relates to markets, and whether it provides an
-accurate correspondence. Using a set-theoretical approach to address the sellers
-bids, we derive our result from the symmetry of supply and demand,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
-\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
-\ref{buyercoordinate}, and include the following corollary,
-{
-\corollary{Data-bid correspondence (seller cooperation)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}).
-For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
-$\epsilon$-best reply.
-}\\
-\textbf{Proof:}
-We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
-strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
-We use the the axiom of set equality,
-based on first-order logic with equality, which states that,  
-$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
-\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
-Then, for any allocation $a$, we may define the relation, $i\thicksim
-j$,
-\begin{equation}\label{eqrel}
-        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
-        \big(\g_i^j(a),y)\big).
-\end{equation}
-Formally, the axiom states that a set is \emph{uniquely} determined by its
-members. It follows that $\thicksim$ defines equality of bids using a static
-analysis with respect to equilibrium, where all users who are not changing thier
-bids are considered equal.\\
-\textbf{Remark:} Equality is both an equivalence relation and a partial order,
-and therefore is reflexive, transitive, symmetric and antisymmetric. \\
-Now, we may define the mapping $s \mapsto [s]$,
-\begin{equation}\label{indeqrel}
-         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
-\end{equation}o
-noting that equality in the bid quantity is implicity satisfied and $z =
-\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
-buyer-seller pair. Without loss of generality, let $S = \Pi_{j\in\mcI} \big(
-\Pi_{i\in\mcI} S_i^j$. The indicator function is the canonical mapping,
-$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
-topology is preserved, the set of all indicator
-functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
-S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
-\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
-$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$.
-
-{
-\proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
-$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
-}\\
-\textbf{Proof:}
-Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
-$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
-the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
-We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
-$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
-we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
-\overline{P}]^{\vert \mcI^j\vert})$
-is a product of closed subsets of compact sets. Now, we have that a closed
-subset of a compact set is compact and the resulting product topology gives
-Tychonoff's theorem. every product of a
-compact space is compact, we have $\g_i \circ B_i^\epsilon$
-is compact subset of $B_i^\epsilon$.
- Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
-definition of $\Delta$ and the product, 
-\begin{align*}
-    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
-    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
-[0,\overline{P}]\bigg)
-    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
-[0,\overline{P}]\bigg) \\
-    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
-\times \lambda^j \subset T.
-\end{align*}
-The result follows from the fact that $t_i$ is continuous in $s_i$, as was
-proven in \cite{semret}, and as a finite union of compact sets is a compact set.
-$\qed$
-on any subset $\lbrace
-s_{-i}\in S_i : \ \forall \ z > 0, \overline{P} \ge P_i(z,s_{-i}) \ge
-\underline{P} \rbrace$, where $0<\underline{P}\le \overline{P} < \infty$
-(HERE) The dimension of a linear space is defined as the maximal number of linearly
-independent vectors or, equivalently, as the minimal number of vectors that span
-the space
-
-%We have proven that buyers will submit bids according to their marginal
-%valuations. Now, in the interest of completeness (BAD SENTENCE), 
-We have that all bids represent $\epsilon$-best replies, and, as was proven in
-\cite{lazar}, the sellers' positive reserve price implies that bids are
-truthful. Finally, by properties determined by the construction of a mixed strategy
-symmetric game with a 2-dimensional message space, we may now restrict our
-analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.
-
-{
-\corollary{Hemicontinuity of $\Delta$}
-}
-
-The data-sharing market consists of inter-dependent sets of these
-multi-auction games around possible fixed points.  Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
-between the different subsets $\Delta$ form a sufficiently connected set that
-the heirarchy described in Proposition \ref{userunion} holds. Then,
-there can only be a single primary fixed point, where the sellers' reserve
-price is an equilibrium price in the global market. 
-We first address the analytical approach, and demonstrate properties of
-$\Delta$ as a finite-dimensional linear topological space. We have that the
-reserve price of the sellers, and the bid price of the buyers is constant
-within an interval of length 2$\epsilon$. We have that 
-(HERE) We have the following
-Corollary, (MIGHT NEED TO REDEFINE.. NOT CLEAR IS A SEQUENCE, SHOULD BE
-SEQUENCE OF PRICES INSTEAD OF USERS?) 
-{
-\corollary{(Primary fixed point)}
-Let the set of shared buyers be denoted as,
-$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
-sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
-$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
-\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
-for a fixed time $t$,
-$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
-k\ne j\in\overline{\Lambda}$. 
-}\\
-(CAN PROBABLY USE ALL BUYERS HERE... BECAUSE OF INF)
-\textbf{Proof:}
-We assume a finite number of users, with continuous valuation functions bounded both
-above and below. From the assumption that $\overline{\Lambda}$ is not a
-partition, we have that the limits exist with respect to bid price $p_i^j$, 
-$$
-    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
-$$
-is the primary seller $j$, and we have the market price $p_*^j$ from,
-$$
-    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
-\lambda^k,
-$$
-and the result follows from Lemma \ref{uservaluation}, Proposition
-\ref{userunion} and Proposition \ref{incentive}.
-(NEED TO SHOW THEY ARE EQUAL...)
-%$\qed$\\
-(USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
-
-We show that our bidding strategy is
-part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
-equilibrium, where the sellers reserve prices are fixed.
-{
-\lemma{(Static Nash Equilibrium)} 
-Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
-let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
-sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
-Using the rules of the data auction mechanism applied independently by each
-user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
-}\\
-\textbf{Proof:}
-(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
-As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
-$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
-$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
-represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
-and we may use Brouwer's fixed point theorem, as in \cite{semret},
-
-As a result of user behavior, and subsequent strategies, we determine that the
-data-exchange market behaves in a predictable way. However,
-each auction may be played on the same or on a different scale in
-valuation, time and quantity, and so the rate at which market fluctuations occur is
-impossible to predict (NEED HELP!). 
-Arrow's paradox is an impossibility theorem stating that when buyers have three
-or more distinct alternatives (auctions), no deterministic ranking system can
-convert the ranked preferences of users into a market-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives. It follows that the case where
-$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
-is disjoint.
-
-Nonetheless, we claim that our mechanism is normative, that irrelevant
-alternatives should not matter, it is practical, uses minimal information,
-strategy, and provides the right incentives for the truthful revelation of individual preferences.
-
-The rules of the PSP
-multi-auction drive market mutations that evolve and are regulated by the user
-strategies.
-(HERE)
-
-(DEFINITION.. USE?)
-In the General Symmetric Game, p is an evolutionarily stable mixed strategy if
-there is a (small) positive number y such that when any other mixed strategy q
-invades p at any level x < y, the fitness of an organism playing p is strictly
-greater than the fitness of an organism playing q.
-(EXPAND)
-% DATA NASH EQ
-{
-\theorem{(Dynamic Nash Equilibrium)}
-Using the rules of the data auction mechanism, the CMHK
-\cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
-game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
-equilibrium. 
-}\\
-\textbf{Proof:}
-
-\subsection{Efficiency}
-
-Formally, the
-mechanism is efficient, if, at equilibrium, the allocation maximizes
-$\sum_i\theta_i(a_i)$.
-(NEED OWN WORDS)
-The objective in designing the auction is that, at equilbrium, resources al-
-ways go to those who value them most. Indeed, the PSP mechanism does
-have that property. This can be loosely argued as follows: for each player,
-the marginal valuation is never greater than the bid price of any opponent
-who is getting a non-zero allocation. Thus, whenever there is a player j
-whose marginal valuation is less than player i 's and j is getting a non-zero
-allocation, i can take some away from j , paying a price less than i 's marginal
-valuation, i.e. increasing u i , but also increasing the total value, since i 's
-marginal value is greater. Thus at equilibrium, i.e. when no one can unilat-
-erally increase P their utility, the total value is maximized.
-
-\subsection{Convergence}
-
-%\end{multicols}
-
-\begin{thebibliography}{9}
-
-\bibitem{zheng}
-L. Zheng, C. Joe-Wong, C. W. Tan, S. Ha and M. Chiangs, 
-\textit{Secondary markets for mobile data: Feasibility and benefits of traded
-data plans}, 2015 IEEE
-Conference on Computer Communications (INFOCOM), Kowloon, 2015, pp. 1580-1588.
-
-\bibitem{lazar}
-A. A. Lazar and N. Semret, 
-\textit{“Design and Analysis of the Progressive Second Price Auction for Network
-Bandwidth Sharing,”} Telecommunication Systems, Special Issue on Network Economics, 2000.
-
-\bibitem{semret} 
-N. Semret, 
-\textit{“Market Mechanisms for Network Resource Sharing,”
-Ph.D. thesis}. 
-Columbia University, 1999.
-
-\bibitem{tuffin}
-Bruno Tuffin,
-\textit{Revisited Progressive Second Price Auction for Charging
-Telecommunication Networks}.
-[Research Report] RR-4176, INRIA, 2001.
-
-\bibitem{qpsp}
-Clare W. Qu, Peng Jia, and Peter E. Caines,
-\textit{Analysis of a Class of Decentralized Decision Processes: Quantized
-Progressive Second Price Auctions},
-46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
-779-784.
-
-\bibitem{cmhk}
-\textit{China Mobile Hong Kong Company Limited}.
-\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html}.
-2018
-
-\bibitem{iia}
-Andreu Mas-Colell, Michael Dennis Whinston, and Jerry R. Green, 
-\textit{Microeconomic Theory}. Oxford University Press. 1995. p. 794.
-
-\bibitem{matt}
-Matthias Roggendorf and Fernando Beltr{\'a}n,
-\textit{Simulation Model for the Dynamic Allocation of Network Resources in a
-Competitive Wireless Scenario}. Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
-pp. 54 - 64.
-
-\bibitem{diffserve}
-N. Semret, R. R. F. Liao, A. T. Campbell and A. A. Lazar, 
-\textit{Pricing, provisioning and peering: dynamic markets for differentiated Internet services and
-implications for network interconnections}, in IEEE Journal on Selected Areas in
-Communications, vol. 18, no. 12, pp. 2499-2513, Dec. 2000.
-
-\bibitem{maille}
-Patrick Maillé.
-\textit{Market Clearing Price and Equilibria of the Progressive Second Price
-Mechanism},
-RAIRO - Operations Research, EDP Sciences, 2007, 41 (4), pp.465-478.
-
-\end{thebibliography}
-
-\end{document}
+%\fi

### 2019-08-21 css-submission.tex
On hold.

--- 2019-08-21 April/paper_recovered.tex
@@
-%\documentclass[journal,comsoc]{IEEEtran}
 \documentclass[sigconf, anonymous]{acmart}
 
-%\usepackage[text={6in,8.1in},centering]{geometry}
-
-\usepackage{enumerate}
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage{mathrsfs} % to use mathscr fonts
-
-\usepackage{multicol}
-\usepackage{url}
-
-\usepackage{epstopdf}
-\usepackage{caption,subcaption}
-\usepackage{pstricks}
-\usepackage{pst-solides3d}
-\usepackage{pstricks-add}
-\usepackage{graphicx}
-\usepackage{pst-tree}
-\usepackage{pst-poly}
-\usepackage{calc,ifthen}
-\usepackage{float}\usepackage{multicol}
-\usepackage{multirow}
-\usepackage{array}
-\usepackage{longtable}
-\usepackage{fancyhdr}
-\usepackage{algorithmicx}
-\usepackage[noend]{algpseudocode}
-\usepackage{changepage}
-\usepackage{color}
-\usepackage{listings}
-\usepackage{fancyvrb}
-\usepackage{verbatim,moreverb}
-\usepackage{courier}
-\usepackage{algorithm}
-
-\newcommand{\vs}{\varsigma}
-\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcI}{\mathcal{I}}
-\newcommand{\g}{\sigma}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-\iffalse
-
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{corFollary}{Corollary}[section]
-\newtheorem{sublemma}{Lemma}[lemma]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\headsep25pt\headheight20pt
-\setcounter{secnumdepth}{4}
-\pagestyle{fancyplain}
-\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
-\cfoot{\ \hfill\tiny\sl Draft printed on \today}
-\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
-
-\fi
-
-%---------------ACM CCS---------------------%
 \fancyhf{} % Remove fancy page headers 
-\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
+\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
 \fancyfoot[C]{\thepage}
@@
 \setcopyright{none} % No copyright notice required for submissions
-\acmConference[?]%Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
+\acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
 \acmYear{2017}
@@
 \settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
-%-------------------------------------------%
+
+%%\ccsPaper{9999} % TODO: replace with your paper number once obtained
 
 \begin{document}
-%\begin{multicols}{2}
-\title{Title?}
+\title{Template for ACM CCS 2017} % TODO: replace with your title
 
 \begin{abstract}
-We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
-Kong 4G Pro Service Plan customers. Telecommunications ISPs' revenue is typically
-gained by charging users a fixed fee for a maximum amount
-of data usage in a month, i.e., a monthly data cap \cite{???}. 
-2cm's (2nd exchange market) data exchange platform allows users to submit
-bids to buy and sell data.
-This usage model, is, as far as our knowledge, the first data trading
-platform that allows customers to buy and sell their own data.
-We describe a distributed auction mechanism for data exchange inspired by the
-classic PSP throughput problem,
-and prove that our distributed data exchange mechanism provides incentive
-compatibility (social choice function), and that we have efficiency
-using only partial valuation information of each participant in an exchange market.
-
-In applying a distributed PSP implementation to CMHK market, we
-find that
-the market is able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and design our mechanism tp provide the functions
-for effective communication between the connected users. We claim that in
-this secondary market our formulation holds the desired VCG qualities through the construction of a
-probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
-with respect to the classic throughput problem.
-and provide simulated results on convergence time to support our (FIND
-COMPETITVE RATIO!), and a bound
-on the convergence of our mechanism. We extend the works of cite!cite!
-i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
-market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
+Your abstract should go here. You will also need to upload a plain-text abstract into the web submission form.
 \end{abstract}
 
-\iffalse
 % TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
@@
 \ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
+% -- end of section to replace with generated code
 
 \keywords{template; formatting; pickling} % TODO: replace with your keywords
-\fi
+
 \maketitle
 
-\section{Introduction}
+%\input{ccs-body} % TODO: replace with your brilliant paper!
 
-(NOTE: THE INTRODUCTION IS CURRENTLY A COLLECTION OF NOTES AND PARTIAL
-SENTENCES)
-In this work, we propose \emph{a distributed progressive second price (PSP) auction in
-order to maximize social utility in the CMHK market}. Using the
-distributed PSP mechanism on CMHKs data
-exhange platform, we show that for cellular data allocated between multiple users there
-exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
-demand information is not known centrally, rather, it is distributed in the
-buyers' valuations. The mechanism for an auction is defined
-as \emph{distributed} when the allocations at any element depend only on
-\emph{local} state: the quantity offered by the seller at that element, and the
-bids for that element only \cite{lazar}. In this work, the proposed mechanism
-allows the distribution of bids, where there are many ISPs each holding
-thier own local auction; there is no entity that holds a global market knowledge.
-
-In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
-using its own demand functions). Buyers submit bids cyclically until an
-($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.
-
-(FEE IS FIXED OR
-PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)
-
-The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
-CLAIM 'IS') described as a \emph{locally}
-pure-strategy progressive game with incomplete, but perfect information.
- you have perfect information, since you know what each move of the opponent is.
-However, since you do not know the payoff function of the other player (which
-will affect its behavior even if it does not alter your own victory conditions),
-it is a game of incomplete information.
-In the overall market analysis assumes complete, but perfect information.
-
- (WHAT
-DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
-VALUATION.. FUTURE WORK)
-
-The paper is organized as follows...
-
-(MOVED: TO ORGANIZE)\\
-The main contribution of this work 
-is an auction mechanism inspired by the classic PSP throughput problem. In
-order to apply a distributed PSP implementation to the CMHK market,
-we analize the behavior of users in a dynamical data exchange market. As both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the communication
-expense from numerous local auctions trading an infinitely divisible resource.
-We will assume that the cost of participating in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. It is worth mentioning that CMHK users are not allowed to resell data
-purchased from the CMHK
-market, additionally, the purchased data does not carry to the next
-service period. Therefore, a market equilibrium, where
-supply equals demand, requires that users maintain incentive for truthfullness
-across a distributed setting.
-We complete a comprehensive analysis of market dynamics, (FINISH)
-To the best of our knowledge, this is the first work to provide a truthful
-mechanism in a distributed setting for data-exchange based on market behavior.
-\\
-\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
-restrictions introduced by the CMHK secondary market. We reserve this for
-future work.
-
-We claim that the CMHK market is
-able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and as our mechanism provides
-for effective communication between the connected users.
-
-Despite the small message space, with many user types, there is no single
-way to do the transformation from the direct revelation mechanism to the
-desired one. Our mechanism is designed by guessing
-right direct-revelation-to-desired-mechanism transformation and building it
-into the allocation rule to be the primary step in the design. This incentive for a user to
-truthfully reveal its type is built into the user strategies. As in classic
-mechanism design, we determine the equilibria as result of incentive
-compatibility in our mechanism design. 
-We claim that in the CMHK market our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead 
-and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
-with respect to the classic throughput problem.
-
-This is the (built-in) transformation from the
-direct-revelation mechanism to the desired message space.
-
-\subsection{Distributed Progressive Second Price Auctions}
-
-Progressive second price auctions (PSPs) were proposed
-in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
-scheme to provide consistent services for network bandwith users.
-\cite{diffserve} conducts a game theoretic analysis, deriving
-optimal strategies for buyers and brokers, and further shows the existence
-of networkwide market equilibria based on their game-theoretic
-model. Constructing necessary and sufficient conditions for the stability
-of the game allows the sustainability of any set
-of service level agreement configurations between Internet service
-providers.
-
-We begin with a brief introduction to the distributed PSP auction for bandwith
-sharing, first introduced by Lazar and Semret \cite{lazar}.
-We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ network bandwidth users.
-Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
-seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
-pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents. 
-Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
-bids $s_{-i}$,
-user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
-and is a Nash move
-where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
-budget, and every user has an elastic demand function.
-Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
-an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
-by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
-allocations awarded in auction $j$. 
-An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
-
-% MECHANISM
-\subsubsection{The PSP Mechanism}\label{mechanism}
-The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
-problem of network bandwidth allocation, and is analyzed as a noncooperative
-game where $i\in\mcI$ agents buy the
-fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
-The market price function (MPF) for a buyer-seller pair is,
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
-\end{split}
-\end{align}
-and is the of minimum prices a user bids in
-order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is,
-% NEW INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
-\end{split}
-\end{align}
-where $D^j$ is the total amount of bandwith that user $j$ has to offer.
-% DATA ALLOCATION RULE
-For each $i \in \mcI$, the allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-    a_i^j(s) &= \min\bigg( d_i^j, 
-    D_i^j(p_i^j,s_{-i}^j)\bigg).
-\end{align}
-Finally, we have the cost of the allocation,
-% DATA COST
-\begin{align}\label{datacost}
-    c_i^j(s) = \displaystyle\sum_{k\ne i} 
-p_k^j \big[a_k^j(0; s_{-i}^j)
-    -a_k^j(s_i^j;s_{-i}^j)\big].
-\end{align}
-
-It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
-equilibria for differentiated services
-allocated between multiple agents when all players bid their real marginal valuation
-of the bandwidth resource. In other words, the PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive
-compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
-principle}, user $i$
-pays for its allocation so as to exactly cover the ``social opportunity cost"
-which is given by the declared willingness to pay (bids) of the users who are
-excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
-revenue \cite{lazar}.
-The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
-\definition{\cite{lazar}}
-A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta(0) = 0$,
-    \item $\theta$ is differentiable,
-    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
-{\theta}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
-The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
-function.
-In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
-
-\section{Related Work}
-
-\section{The Problem Model}
-
-\subsection{The CMHK Market}
-
-We construct the model for a PSP data auction for mobile users
-particpating in CMHK's secondary data-sharing market.
-Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
-data from other users. We again define the bidding profile for any user to be 
-$s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
-cellular network. We assume that users are selfish, and therefore
-rational. 
-Users prefer to participate in the CMHK secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
-Thus we assume that all users submit bids in order to maximize their
-(private) valuation functions. 
-In general, user preferences are defined by a utility function, $u$, which 
-represents a users' valuation of an allocation minus the price.
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We assume that data is a unary resource belonging to the seller, and
-therefore we identify each local auction with the identity of the seller
-$j\in\mcI$.
-We further show that user valuation satisfies the conditions for an
-\emph{elastic demand function}, as in \cite{lazar}.
-Finally, we assume in the CMHK market that a buyers' budget is always
-sufficient, as the alternative is to pay the overage fee to the ISP.
-
-The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
-the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
-separated (a seller does not also buy data and vice versa). Thus, we may assume
-that this is implied in our notation.
-A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
-belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
-the bid belongs to a \textbf{seller}.
-Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
-meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
-a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
-auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
-(0,0)$. Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
-$j$. We additionally determine that a user who does not submit a bid is holding
-its previous bid, either zero or nonzero. For the purposes of our analysis, we will assume that a zero bid from a
-buyer is equivalent to no bid.
-A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
-with the intent of offering a
-quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
-with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
-stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
-by the user type, whether or not they are  a buyer or a seller. 
-To further clarify our analysis, we will emphasize the separation of buyers and
-sellers using
-$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
-In other words, a bid $s^j =
-[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
-secondary market. The notational conventions of the bid vectors are essentially 
-slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
-[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
-Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
-d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
-d_i^j$ represent the
-total amount of data requested by buyer $i$.
-
-Consider the grid of bid proiles, $s$, representing the distributed PSP auction
-mechanism in the CMHK market, each buyer $i$ will
-have information from each seller $j$, as well as opponent profiles $s_{-i}$
-from each auction in which it is participating, and therefore
-in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
-$i$ gains access to the full grid $s$. However, 
-sellers can only gain information about the market grid by observing buyer
-behavior in their local auction.
-In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
-influence the CMHK market dynamics, with the sellers taking a secondary role
-(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
-
-\subsection{User Valuation}
-
-We assume that the CMHK market does not have network
-bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, and as
-bandwidth in wireless networks is not the focus of this paper. We
-conduct a comprehensive analysis, deriving a globally optimal strategy suited for
-users with local information in a distrubuted data-sharing model.
-
-Our mechanism allows a buyer
-to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
-utility while minimizing the number of positive bids submitted to the overall
-market. We define an \textbf{opt-out function}, associated with a buyer $i$ as
-part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
-will determine its bid quanities by,
-\begin{equation}\label{opt-out}
-    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
-\end{equation}
-In a general sense, this abstraction applies our \emph{user strategy}
-to the PSP rules.
-% OPT-OUT BUYER
-We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
-\begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ (\g_i(a)) - c_i,
-\end{equation}
-where the composition of the elastic valuation function $\theta_i$ with $e_i$ acts as a distribution function, splitting
-the buyers' valuation of allocation $a$ across local markets (and thus multiple
-sellers), and $\theta_i(\g_i(a)) - \g_i(\varrho)$ represents the buyers'
-corresponding debit.  
-In this way we extend the PSP rules described
-in \cite{semret} to design equilibria across subsets of local data-exchange markets.
-
-The sellers, $j\in\mcI$ are not associated with an opt-out function, we
-consider their valuation to be a functional extension of the buyers, where
-$\theta^j$ is constructed by buyer demand.
-The sellers strategy can only be to determine the reserve price of their local
-auction, using only information from buyers who have not opted out.
-In our analysis, we demonstrate market dynamics, and further show evidence of symmetry in the strategies of
-buyers and sellers.
-
-\subsubsection{Valuation under Market Dynamics}
-The buyer demand largely motivates the market price function, however, the
-distributed nature of the market prevents any single user from knowing the
-market demand for a quantity of data. All users have knowledge of market
-supply, as this is public information, however only buyers
-are able to determine supply or demand across multiple auctions, and then only from auctions
-in which they participate. \\
-\textbf{Remark:}
-It is possible that a seller would be able to derive information about other
-auctions by examining buyer bids over time, particularly if the seller had knowledge of the
-buyer strategy. (FUTURE WORK?)\\
-
-In a multi-auction market, each auction a buyer joins has the potential to
-decrease the potential cost of its data. However, increasing the size of the
-auction implies a certain risk, which we may interpret as a potential and
-definite
-liability. Increasing the number of transactions causes additional messaging
-overhead, fees, and increased competition from other buyers. 
-A transaction also causes potential indirect costs, which may be considered work done to find
-sellers, or effort of communication from participation. A seller
-has the potential for greater profit with each new buyer in its auction, taking 
-the same risk.
-%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
-%and the individual. We denote the potential indirect costs of participation of
-%each user as $\varrho$.
-The liability of any user is naturally absorbed into the bid fee $\epsilon$,
-as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
-dependent on the association between two users and their market positions, in
-addition to the underlying network structure. Now, both sellers and buyers must consider
-the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
-OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)
-
-Elastic valuation functions allow for even infinitesimal changes in the market
-dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
-allows for the analysis of constraints imposed by the user strategies. 
-Buyers may directly impact each other in local market intersections.
-Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
-A buyers' valuation of an amount of data represents how much a buyer is willing
-to pay for that amount. 
-This is equivalent to the bid price, given a fixed amount of data,
-satisfying $\theta_i$. We determine the
-buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
-possible unit price. We have,
-% BUYER PRICING 
-\begin{equation}\label{buyerinversedemand}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
-\end{equation}
-where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
-$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
-We determine that the market supply function is equivalent to buyer demand, and 
-acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
-% BUYER DEMAND 
-\begin{equation}\label{datasupply}
-    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
-\end{equation}
-We note that $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Therefore, in a coordinated bid, the utility-maximizing bid price is the
-lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers. 
-%We will later show, in Proposition
-%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
-%bids, i.e. using the same bid for all auctions.
-
-A seller only has
-information from buyers in its own auction, and may only be indirectly influenced by
-buyers in other auctions. So from the perspective of the
-seller we have a more direct interpretation of valuation as revenue.
-We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} \g_i^j(a), 
-\end{equation}
-and define the ``inverse" of the buyer demand function for seller $j$ as
-potential revenue at unit price $y$, we have, 
-% SELLER REVENUE 
-\begin{equation}\label{sellerinversedemand}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
-price.
-
-The valuation of any user must be modeled as a function of the entire
-marketplace. 
-Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
-\circ \g_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
-(\ref{datademand}) and (\ref{sellerinversedemand}). We first note that, in
-general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
-$$
-    \theta(x) = \int_0^x f(z) \ dz,
-$$ 
-as in \cite{semret}. Now, we have the following Lemma,
-{
-\lemma{(User valuation)}\label{uservaluation}
-For any buyer $i\in\mcI$, the valuation of a potential
-allocation $a$ is, 
-\begin{equation}\label{buyervaluation}
-    \theta_i \circ \g_i(a) = \displaystyle\sum_{j\in\mcI}
- \int_0^{\g_i^j(a)} f_i(z) \ dz.
-\end{equation}
-Now, we may define seller $j$'s valuation in terms of revenue,
-\begin{equation}\label{sellervaluation}
-    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ \g_i^j(a) = \sum_{i\in\mcI}
- \int_0^{\g_i^j(a)} f^j(z) \ dz.
-\end{equation}
-We have that $\theta_i$ and $\theta^j$ are elastic valuation functions, with
-derivatives
-${\theta_i}$ and ${\theta^j}'$ satisfing the conditions of elastic demand.
-}
-\textbf{Proof:} 
-Let $\xi$
-be a unit of data from buyer bid quantity $\g_i^j(a)$.
-If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
-similarly decrease. The lost potential revenue for seller $j$ is the price of
-the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
-$$
-    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
-$$
-Thus (\ref{sellervaluation}) holds.
-As we may use the same argument for (\ref{buyervaluation}), as such, we will
-denote $f_i=f^j=f$ for the remainder of the proof. We observe that the function
-$f$ is the first
-derivative of the valuation function with respect to
-quantity. Letting $\theta_i=\theta^j=\theta$, the existence of the derivative implies $\theta$ 
-is continuous, and therefore, in this context, $f$ represents
-the marginal valuation of the user, ${\theta}'$. Also, clearly
-$\theta(0)=\theta(\sigma(0)) = 0$. Now, as we consider data to be an infinitely
-divisible resource, we have a continuous interval between allocations $a$ and
-$b$, where $a\le b$. Now, as $\theta$ is continuous, for some $c\in[a,b]$, 
-$$
-\theta'(c) = \lim_{x\to c}\frac{\theta(x) - \theta(c)}{x-c} = f(c),
-$$
-and so $f=\theta'$ is continuous at $c\in[a,b]$, and so as $a\ge 0$, 
-$\theta'\ge 0$. Finally, we have that concavity follows from the demand
-function. Then, as $\theta'$ is
-non-increasing, we may denote its derivative $\gamma \le 0$,
-and taking the derivative of the Taylor approximation, we have, $\theta'(z) \le
-\theta'(\eta) + \gamma(z-\eta)$.
-$\qed$
-
-Utility is defined by their valuation, and is the basis for user behavior. 
-The sellers' natural utility is the potential
-profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
-paid to the ISP, as it is not a component of our mechanism, and as a discussion
-of mobile data plans is outside the scope of this paper.  
-Now, a rational user will try
-to maximize its utility, thus, user incentive manifests as a
-response to market dynamics. A buyer has the choice to
-opt-out of any auction, and as a seller will try to sell the maximum amount of
-data, the highest possible reserve price is conditioned by ``natural" constraints. Utility-maximization 
-acts as revenue maximization for a rational seller, and as cost minimization for a
-rational buyer. Thus, for each user $p_i^j \ge \min\big(p_i^j)$ and $p_i^j \le
-\max\big(p_i^j)$, which holds $\forall \ i, j\in\mcI$ such that $s_i^j>0$.
-Now, rational buyer does not want to purchase extra data, as this would be
-equivalent to overpaying, however $i$ submits positive bids to a set of
-sellers, and a rational seller will attempt to maximize profit, and so will try and sell all of
-its data. Therefore,
-\begin{equation}\label{bidcap}
-    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j \quad\text{and}\quad
-\sum_{j\in\mcI} d^j_i \ge D_i,
-\end{equation}
-which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
-constraint from our formulation.
-Thus, at equilibrium all users are satisfied, and 
-$D^j = D_i$, although we observe that this result
-does \emph{not} imply that $s_i=s^j$.
-
-We further determine that the set of buyers and sellers participating
-in a single equilibrium is bounded by the potential indirect costs of
-participation. We will denote this individual cost to each user as
-$\varrho$. The indirect cost is the portion of the bid fee
-$\epsilon$ that is dependent on the underlying network and the individual.
-Observing that $\varrho$ indirectly effects user utility,
-and therefore acts to establish a natural budget for each user. We give this
-constraint as, 
-\begin{equation}\label{poolbnd}
-    u \le \varrho,
-\end{equation}
-which may be interpreted as the effort a rational user is willing to expend
-on its message space, and serves to limit the size of the buyer/seller pools.
-
-Finally, it is worth mentioning that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, in order to derive properties.
-The mechanism itself does not require any knowledge of user demand or
-valuation. 
-\subsection{PSP for Data-Exchange}
-
-% MECHANISM
-\subsubsection{Data Auction Mechanism}\label{datamechanism}
-We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the CMHK market, and which we will denote the \emph{data}
-PSP rules. The rules presented here incorporate of the opt-out function with the
-mechanism as in \cite{lazar}, which we note greatly simplifies our
-analysis. 
-The market price function (MPF) for a buyer in the CMHK market
-can be described as follows:
-% NEW MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI} \ \g_i^j \circ P_i^j(z_i^j,
-s_{-i}^j) \\
-    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {D_i^j}(y,s_{-i}^j) \ge \g_i^j(z) \bigg\rbrace \bigg),\\
-\end{split}
-\end{align}
-and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
-order to obtain
-data amount $z$ given opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices
-of the individual sellers may vary.\\
-\textbf{Remark:} We further note that except at points of discontinuity, from
-Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
-%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
-%buyer $i$'s bid quantity. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is: 
-% NEW ALLOCATION RULE
-\begin{align}
-\begin{split}\label{datacomposed}
-    \bar{D}_i^j(y,s_{-i}^j) &= \g_i^j \circ D_i^j( y,s_{-i}^j)\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
-\end{split}
-\end{align}
-% DATA ALLOCATION RULE
-The resulting data allocation rule is a function of the local market
-interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
-allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-\begin{split}
-    \bar{a}_i^j(&s) = \g_i^j \circ a_i^j(s) \\
-    &= \min\bigg\lbrace \g_i^j(a), 
-    \frac{\g_i^j(a)}{\displaystyle\sum_{p_k^j= p_i^j}\g_k^j(a)} 
-D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace,
-\end{split}
-\end{align}
-noting that for the full allocation from all auctions we may simply aggregate
-over the seller pool.
-Finally we must have that the cost to the buyer adheres to the second price
-rule for each local auction, with total cost to buyer $i$,
-% DATA COST
-\begin{align}\label{datacost}
-\begin{split}
-    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
-    p_i^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
-    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
-\end{split}
-\end{align}
-\textbf{Remark:} The cost to buyer $i$ adds up the willingness
-of all buyers excluded by player $i$ to pay for quantity $\bar{a}_i^j$. i.e.
-$$
-    c_i^j(s) = \displaystyle\int_0^{\bar{a}_i^j} P_i^j(z, s_{-i}) \ dz.
-$$
-This is the ``social opportunity cost" of the PSP pricing rule.
-
-The formulation is inspired to the thinnest allocation route for
-bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
-satisfy $i$'s demand, then
-(\ref{buyerutility}) reduces to the original form, defined in
-\cite{semret} as ``a simple buyer at a single resource element".
-
-(OWN WORDS!)
-The cost function will therefore be a stepwise-linear function, which is
-increasing in slope with each new bidder excluded from the market.
-
-\subsection{User Behavior}
-
-\subsubsection{Buyer Strategy}
-
-Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
-is also reasonable to expect that a seller may come close to using their
-entire data cap, and only sell the fractional overage. In this case, a buyer
-must split its bid among multiple sellers. 
-The buyer strategy bids in auctions with the highest quantities first,
-a natural exploitation of the demand curve. A new seller entering the market
-with a large quantity of data will be in high demand. This behavior contributes to market price
-stability, as seller valuation is determined by buyer demand, the
-buyer strategy tends towards equal valuation of all local markets, and therefore
-similar prices. If a buyers' demand is not satisfied, they will need to bid in
-markets with smaller data quantities, and so will bid on a larger portion of
-the sellers' bid quantity, increasing their unit price. Market equilibrium is achieved when each buyer has equal bids in
-each auction. Our bidding strategy is inspired by \cite{lazar}, and we also
-hold buyers to consistent bids, where buyers sumbit identical bids to a
-subset of sellers with the highest offers. In the remainder of this section, we
-will make the assumption of truthful bids from the buyer, although this
-analysis is left to Section \ref{analysis}.
-Thus, we determine when rational (utility-maximizing) buyers opt-out of a local auction. 
-We propose the following strategy, 
-% BUYER STRATEGY
-{
-\lemma{(Opt-out buyer strategy)}\label{buyerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t>0\in\tau$, and let $a$ be $i$'s desired allocation. 
-% OPT-OUT BUYER STRATEGY
-Define the composition,
-$$
-     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity, and similarly for $\varrho$.
-Also define the set,
-% MIN SET
-$$
-    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
-n}\sum_{j\in\mcI'} D^j,
-$$
-where buyer $i$ chooses its seller pool by determining $n$ as,
-\begin{align}
-\begin{split}\label{buyercoordinate}
-    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
-    %\wedge \sum_{j\in\mcI(n)}&\g_i^j(\varrho) \le \sum_{j\in\mcI(n)} \theta_i^j(\g_i^j(a)) \big\rbrace. 
-    %&\wedge \g_i(\varrho) \le \theta_i(\g_i(a)) \big\rbrace. 
-\end{split}
-\end{align} 
-The buyer strategy produces a minimal subset of sellers $\in \mcI$ 
-able to satisfy buyer $i$'s demand while ensuring that the size of $\mcI^j$
-does not allow the overhead to outweigh the valuation of the data. For 
-fixed $n$ we will denote this subset,
-\begin{equation}\label{sellers}
-    \mcI_i \subset \mcI.
-\end{equation}  
-Now let $j^* = n \le I$ represent the seller with the least amount of data
-$\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$, and define $i$'s bid
-vector $\g_i$ with respect to its strategy, where
-\begin{equation}\label{opt-eq}
-    \g_i^j(a) \triangleq \begin{cases} \g_i^{j^*}(a), \quad j\in\mcI^j,\\
-            0, \quad j\ni\mcI^j.\end{cases}
-\end{equation}
-and define bid price $p_i^j = \theta_i'(\g_i^j(a))$.
-Now, (\ref{opt-eq}) holds $\forall \ j\in\mcI$,
-and we have an optimal strategy for buyer $i$.
-}\\
-\textbf{Proof:}
-We assume that a buyer will try and fill their data requirement.
-In the case that there exists a seller who can completely satisfy a buyers'
-demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
-as the set $\mcI_i$ is ordered by the quantity of the sellers' bids, $i$ may discover 
-$j^*$ by computing $\mcI_i$.
-Suppose that $D_i >
-\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
-We model the ISP at time $t>0$ as a seller $\kappa$ with bid $s^\kappa
-=(d^\kappa, p^\kappa)$,
-where $d^\kappa > D^j, \
-\forall \ j\in\mcI_i$, and
-$p^\kappa$ represents the overage fee for data set by the ISP, which we note is also the upper bound of the sellers'
-pricing function.
-Consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
-The allocation rule (\ref{dataallocation}) determines that the data will be
-split proportionally
-between all buyers with the same unit price. 
-It is possible that the resulting partial allocation of data to $i$ and $k$
-would not satisfy some demand. As the two cases $i$ and $k$ are the same, we
-will only consider one. Suppose seller $j$ updates its
-bid to reflect the new data quantity, where
-$d_i^{j(t+1)} < \g_i^{j(t)}(a)$. First, $i$ sets its bid to $s_i^j = 0$, and
-from the new subset $\mcI_i$, submits bids until
-$\sum_{j\in\mcI_i} \g(a)_i^j \ge D_i$, by (\ref{bidcap}).
-Now, we consider the case where a new buyer $k$ with bid
-price $p_k^j > p_i^j$ for some $j \ \in \mcI_i$, in other
-words, a new buyer $k$ may enter the market with a better price, decreasing the
-value of $i$'s bid for $j\in\mcI_i$. In this case, by (\ref{buyercoordinate}),
-$i$ will choose $\mcI_i$ so that, $\g_i^{j(t+1)}(a) = \g_i^{j(t)}(a) - \g_k^{j(t)}(a)$,
-and so $\mcI_i$ is large enough to balance the additional demand from
-$k$. Finally, we consider the case where $\vert\mcI^j\vert = I$, where the
-demand of buyer $i$ exceeds the supply, and the case where $\g_i(\varrho) >
-\theta_i(\g_i(a))$, where the overhead exceeds the current valuation of the
-data. Then, by (\ref{buyerinversedemand}), the valuation of the data increases until either
-the demand is satisfied, the debit from the overhead costs are balanced
-(\ref{poolbnd}), or the upper bound of the sellers' reserve price
-$p^\kappa$ is reached. Thus, as in each case we have that $i$ is able to satisfy thier demand,
-and we determine that the opt-out strategy is optimal.
-$\qed$\\
-\textbf{Remark:} The bid quantity $\g_i^j(a)$ and the allocation $\bar{a}_i^j$
-are complementary. In fact, the buyer strategy is the first term in the
-minimum, the second term being owned by the seller.
-
-Finally, we note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, in fact, by
-restricting the size of the set $\mcI_i$, we would be able to improve the
-computation time of buyer $i$, at the cost of increasing the price.
-
-\subsubsection{Seller Strategy}
-In order to to develop the seller strategy, we examine the incentive of a
-rational seller with only local information in a dynamic market of many
-buyers and sellers. A local auction, examined independently, may appear as
-single market with a single seller and many buyers, but is in fact a subset of the
-larger data-exchange market, and is subject to the trends and dynamics
-therewithin. A seller must determine allocations using only bids in its local market, while the buyers' response is based on the
-allocations and resulting opponent bids from all auctions in its seller pool.
-In addition, buyers are allowed to bid both dynamically and asychronously. 
-In order to
-maximize revenue, the seller must also be able to respond dynamically to
-address the mutation of competitive bids in its market. In order to do this, we
-determine that the seller may modify its reserve price in response to the
-changing market dynamics.
-
-We will show that sellers are able to maximize revenue in restricted subset of
-buyers in $\mcI$, and as such will attempt to facilitate a local market
-equilibrium for this subset. A local auction $j$ converges when all buyer bids
-remain the same over a time step, that is, if $\forall \ i \in\mcI$,
-$s_i^{j(t+1)} = s_i^{j(t)}$, at which point the allocation is stable, the data
-is sold, and the auction ends. In the sellers' local environment, we determine
-that the best course of action is to maximize revenue, and then try to keep its
-buyer pool stable until convergence occurs. Thus, the seller strategy is
-complementary to that of the buyers, and is designed to achieve and maintain a
-local market equilibrium.
-
-We describe a \emph{local} auction strategy for data allocation, where the seller is unaware of the existence of other auctions, and so
-the seller behavior is the same in the case of a single buyer, a small buyer set, and in the
-extreme case, where all buyers $i\in\mcI$ participate. We again note that the
-seller must initialize the strategy with a first iteration, and so the auction
-is defined for time $t>0$.
-In our model, a local auction may be described as a progressive game of strategy with
-incomplete, but perfect information, however in our analysis, as before, we will assume
-complete information. 
-(BUYERS ARRIVE AS A POISSON PROCESS? FUTURE WORK)
-
-% SELLER LOCAL STRATEGY
-{
-\lemma{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t>0\in\tau$.
-Define the set,
-$$
-    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
-n}\sum_{i\in{\mcI}'} p_i^j,
-$$
-where,
-\begin{equation}\label{sellercoordinate}
-    \min\bigg\lbrace n \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(n)}d_i^j
-\ge D^j \bigg\rbrace,
-\end{equation} 
-so that $n$ produces a minimal subset 
-of buyers that maximizes $j$'s revenue at time $t$, which we will
-denote, for fixed $n$, by,
-\begin{equation}\label{buyers}
-    \mcI^j \subset \mcI.
-\end{equation} 
-Define buyer $i^* = n-1 \le I$ as the buyer with the maximum bid price $\ni
-\mcI^j$.
-Then, for time $(t+1)$, set $j$'s reserve price to be, 
-\begin{equation}\label{newprice}
-    p_i^{j(t+1)} = p_{i^*}^{j(t)} + \epsilon,
-\end{equation}
-Let the winner at time $t$ be determined by,
-\begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i\in I^j} p_i^{j(t)},
-\end{equation}
-and update $j$'s total data to reflect the (tentative) allocation,
-\begin{equation}\label{newdata}
-    D^{j(t+1)} = D^{j(t)} - \g_{\bar{i}}^{j(t)}(a),
-\end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{sellercoordinate}) -
-(\ref{newdata}) produces a local market equilibrium. 
-}\\
-\textbf{Proof:}
-We assume that the seller will try to maximize its revenue. In the case where
-$\vert\mcI^j\vert =1$, then if $\g_i^j(a)=D^j$, then $j$'s market is at equilibrium.
-Otherwise, we arrive at the case of multiple buyers, which we note includes the
-case where $\g_i^j(a) < D^j$, which is reflected trivially here.
-
-For auction $j$ with multiple buyers, $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}), 
-Suppose that for some $i\in\mcI^j$, buyer demand is not met. 
-In this case, by (\ref{bidcap}) the seller must notify $i$ of a
-partial allocation by changing the bid vector at index $i$.
-With this caveat, and Proposition \ref{buyerstrategy}, we have that the
-aggragate demand of subset $\mcI^j$ is satisfied by seller $j$, as in Lemma
-\ref{sellerconstraints}.
-Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
-that buyers are bidding truthfully, and so the new reserve price $p_{i^*}^j +
-\epsilon ={\theta_{i^*}}' + \epsilon$. For clarity, let the reserve price be denoted by
-$p_*^j$.
-Now, by the elasticity of (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}), we have that, $\forall \ z\ge 0$,
-$f_{i^*}(z) < f^j(z) \le f_i(z)$,
-which holds $\forall \ i \in \mcI^j$, and $\forall \ j \in \mcI_i$.
-We claim that the choice of reserve price $p_*^j$ does not force any buyers out
-of the local auction. To show this, we use the assumption of truthful bids, and
-the fact that since the auction begins at time $t>0$, buyers will
-bid at least once. As will be addressed in further analysis, we assume
-that a new bid price differs from the last bid price by at least
-$\epsilon$. Suppose the auction starts at equilibrium, so $\sum_{i\in\mcI^j}
-\g_i^j(a) = D^j$ at time $t=0$. The reserve price $p_*^j$ set at time $t=0$
-begins the auction with the first bid iteration, and so at $t>0$, $\forall \ i \in
-\mcI^j$, we have that $p_i^j - p_*^j \ge \epsilon$.
-Now, in the case where at $t=0$, $\sum_{i\in\mcI^j} \g_i^j(a) > D^j$, by
-(\ref{dataallocation}), the seller notifies (any) buyer $k$ with the lowest bid
-price of a partial allocation by changing
-$d_k^j$ thus by Proposition \ref{buyerstrategy}, $k$ either decreases its
-demand or increases its valuation until
-$\g_i^j(a) \le d_i^j$. Then, as the seller computes the set $\mcI^j$ at each time
-step, a new $i^*$ may be chosen and the buyers bid again.
-Suppose $\exists \ k \in \mcI^j$ such that $\forall \ l \ \in
-\mcI_k, \ i\ni \mcI^l \ \forall \ i\ne k\in\mcI^j$. That is, $k$ is
-disconnected from all other buyers $i\in\mcI^j$, and suppose that $d_k^j$
-is partial allocation at $t>0$, and further suppose that there are many
-$l\in\mcI_k$ where $\vert \mcI^l\vert > \vert\mcI^j\vert$. The more buyers an
-auction has, the more likely that cases will occur that cause buyers to rebid,
-particularly if auctions $l\in\mcI_k$ have overlapping buyers, then $k$ may
-opt-out of auction $j$, i.e. $s_k^{j(t)} \ne s_k^{j(t+1)} =
-0$, then the seller may simply return the tentatively allocated data to $D^j$.
-Finally, we note that if for some $i\in\mcI^j \ \exists \ k\in\mcI^j$
-such that $p_{i}^j = p_k^j$, then the seller again notifies the buyers of a
-partial
-allocation by changing $d_i^j$ and $d_k^j$ by (\ref{dataallocation}).
-Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
-equlibirium created by $j$ is independently stable from time $t$ to $(t+1)$. 
-$\qed$
-
-\subsubsection{Market Dynamics under Strategy}
-
-We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. We model the impact of the dynamics of the
-data-exchange market on a local auction $j$. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. This gives an auction $j$ a natural logical extension into the
-global market through its buyers. We demonstrate that the symmetry between
-buyer and seller behavior, consequently strategies, stretches into a symmetry across subsets of local
-auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. We have the following Lemma,
-% USER UNION
-{
-\proposition{(Valuation across local auctions)}\label{userunion}
-For any $i,j\in \mcI$, 
-\begin{equation}\label{jtoi}
-j\in\mcI_i \Leftrightarrow i\in\mcI^j.
-\end{equation}
-Fix an auction $j\in\mcI$ with duration $\tau$ and define the influence sets of users. 
-The primary influencing set is given as,
-%(ALL THE SELLERS FROM EACH BUYERS POOL)
-\begin{equation}\label{lambda}
-    \Delta = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
-\end{equation}
-with secondary influencing set,
-%(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
-\begin{equation}\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
-\iffalse
-(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
-\begin{equation}%\label{lambda}
-    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
-\end{equation}
-(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
-POOLS)
-\begin{equation}%\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
-\fi
-Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
-\begin{equation}\label{union-eq}
-    \displaystyle\sum_{j\in\Lambda} \theta_i^j = \sum_{i\in\lambda} \theta_i^j.
-\end{equation}
-}\\
-\textbf{Proof:}
-A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$, and we have that $i\in\mcI^j$,
-if and only if $i$'s bid is such that $p_i^j > p_{i^*}^j$, where
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price in auction $j$. By (\ref{buyerinversedemand}) $p_i^j \ge
-p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
-shift, caused by the underlying dynamics.
-Consider $k\in\mcI^j$ where for example, new buyers enter the auction, or increase
-thier bid prices, so that $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
-$s_k^j>0$ at time $t$. 
-By Proposition \ref{buyerstrategy}, $k$ will set its bid $s_i^j=0$, and begin to add sellers to its pool.
-Suppose that at time $t$, $j$'s market is at equilibrium, i.e. $\sum_{i\in\mcI^j} = D^j$, and
-no buyer rebids. Unless $k$ adds a seller with a higher reserve
-price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
-auction will end. Otherwise, at some time $t\in[t+1,\tau]$, we must have that $\g_k^j <
-D^j$, and $k$ opts-out. Finally, overlooking market transitions and messaging
-overhead, we have that,
-$\forall \ i\in\mcI^j$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and (\ref{jtoi})
-holds.
-\iffalse
-Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
-of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
-s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
-\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
-\fi
-
-Now, the subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
-coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
-determines the unit price $p_{i}$ in buyer $i$'s bid.
-The reserve price (\ref{newprice}) of seller $j$ is determined at each
-transition, and is
-the lowest price that $j$ will accept to perform any allocation.
-Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
-[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
-\ \forall \ k \in\mcI_i$. 
-Using Proposition
-\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
-\ \forall \ k \in\mcI_i$.
-
-\iffalse
-Now, we have,
-\begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-\fi
-
-The incentive of each seller $\in\Lambda$ is to sell all of its data at the
-best possible price. In the simplest case,
-consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
-\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
-$\lambda = \mcI^j$. 
-Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
-clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-In all other cases, the sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
-%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-The set $\lambda$ represents all of the buyers influencing auction $j$, both
-directly and indirectly. 
-The bid price of buyer $i\in\mcI^j$ is determined by,
-\begin{equation}\label{maxbid}
-    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
-\end{equation}
-$\Lambda$ is the set of sellers directly influencing the bids of buyers
-in auction $j$. Now, the reserve price for auction $j$ is such that,
-\begin{equation}\label{resprice}
-    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
-\end{equation}
-by Proposition \ref{sellerstrategy}. 
-Also, in the absence of transitions, caused by multi-auction market dynamics, we have 
-that $j$ maintains a local market
-equilibrium from time $t$ to $(t+1)$. Let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the lowest bid price,
-and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand from time $t$ to $t+1$ will
-directly impact buyer $i$. If at time $t+1$ we still have that $i$ is the
-buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and
-thus $j$'s valuation does not change. Otherwise a new buyer with the lowest bid will be chosen upon
-recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}. 
-In each case we
-have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
-some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
-\begin{equation}\label{jdemand}
-    \int_0^{\g_i^j(a)} f^j(z) \ dz 
-    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
-\end{equation}
-therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-
-Consider the set $\lambda$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$, and
-the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$, so,
-$$
-    p_*^k \le p_l^* < p_*^j \le p_i^*,
-$$
-for any buyer $l\in\lambda$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
-p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
-which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
-\ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$. 
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^q =
-0$ for $q\in\mcI_i$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$
-for $q\in\mcI_l$ or $\theta_l^q = 0$ for some $q\in\mcI_i$. Thus, any bid ouside of
-our construction
-has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$, and therefore cannot cause transitions to occur except through a
-shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
-bids in any auction $\mcI^q$, where $q\in \mcI_l \setminus \Lambda$,
-we have, $\forall \ k\in\mcI_i$,
-\begin{equation}\label{idemand}
-    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
-f^k(z) \ dz,
-\end{equation}
-which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
-\ref{sellerstrategy}..
-Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
-\begin{align}\label{tieqtk}
-    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
-\end{align}
-and
-\begin{align}\label{tkeqtl}
-    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
-\end{align}
-Thus, with a slight abuse of notation for clarity,
-\begin{equation}\label{funion-eq}
-    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
-\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
-\end{equation}
-where the result follows by construction, and the continuity of $\theta'$.
-$\qed$
-
-For completeness, in the case where the ISP $\kappa$ 
-does not adhere to the market dynamics, so $p^\kappa > p^j +
-\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
-bid fee.
-(NEED TO DO BETTER WITH TIME?)
-
-\subsubsection{Mechanism Realization}
-
-In order to represent the public platform of the secondary market, we model the ISP as
-a kind of buyer $\kappa$ who remains at time $t=0$, i.e. does not participate
-in any auctions. At time $t=0$, a seller $k$ entering the market will have
-submitted bid $s_\kappa^j =(\epsilon, D^j)$ to the CMHK platform, and so the
-seller does not require a priori demand information to enter the market.
-(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
-IMPLICATIONS?)
-We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. 
-A new sellers' bid, $(D^j, \epsilon)$, as well as updated bids(NOT SURE), is public
-knowledge. 
-\iffalse
-A buyer entering the market
-at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER!) is initialized as 
-an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
-probability $\mathcal{P}$,
-$$
-    \mathcal{P}[\epsilon\le X \le \kappa] =
-\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
-ds,
-$$
-where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
-density function of $X$.
-\fi
-%may represent by some homogenous function of degree one (EXPAND?). 
-Thus the auction
-begins at time $t>0$, and at $t=0$, $j$ will increment through a single iteration,
-initializing bid prices.
-
-Consider a user seeking to prevent
-data overage charges by purchasing data from a subset of other network users.
-The sellers' auction will function as follows: at each bid iteration all buyers
-submit bids, and the winning bid is the buyer $i$ that has the highest price
-$p_i^j$. The seller allocates
-data to this winner, at which point all other buyers are able to bid again, and
-the winner leaves the auction (with the exception where multiple bidders bid
-the same price, where (\ref{dataallocation}) determines they will not fully
-satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
-sellers' data has been allocated. 
-% SELLER ALGORITHM
-\begin{center}
-\begin{algorithm}[H]
-\caption{(Seller progressive allocation)}
-\begin{algorithmic}[1]
-\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
-\emptyset$, compute
-$\mcI^{j(0)}$
-\State Update $s^j$ 
-\While{$D^j(t) > 0$}
-\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
-\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
-%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
-\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
-\State $s^{j(t+1)} \gets (d^j, p^j)$
-\State Update $s^j$
-\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
-\For{$k \in \bar\mcI$}
-\If{$p_k^j < p_{i*}^j$}
-\State $D^{j(t+1)} = d_k^{j}$
-\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
-\EndIf
-\EndFor
-\State Compute $\mcI^{j(t)}$
-\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
-\State $t \gets t+1$
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-\end{center}
-Each time step, $s^j$ is updated it is shared with all
-participating buyers. At this point buyers have the opportunity to bid again,
-where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. We
-define a single iteration of the auction, wher a seller updates bid vector
-$s^j$, and the buyers' response $s_i$, to comprise a single time step.
-
-% SELLER ALGORITHM
-\begin{center}
-\begin{algorithm}[H]
-\caption{(Buyer response)}
-\begin{algorithmic}[1]
-\State $p_{i(0)} \gets \epsilon$, $s_{i(0)} \gets (p_i, D_i)$, $D_t \gets D_i$, compute
-$\mcI_{i(0)}$
-\State Update $s_i$ 
-\While{$D_i(t) > 0$}
-\State $D_{i(t+1)}^j \gets \sum_{j\in\mcI_i}\g_i^{j(t)}(a)$
-\If{$D_{i(t+1)}^j < D_t$}
-    \State Compute $\mcI_{i(t)}$
-    \State $p_i \gets \theta_i(\g_i(a))$
-\EndIf
-\State $s_{i(t+1)} \gets (\g_i(a), p_i)$
-\State Update $s_i$
-\State $D_{i(t+1)}^j \gets D_{i(t)}^j$
-\State $t \gets t+1$
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-\end{center}
-Finally, we give a simple example of convergence to a local market equilibrium, where the buyers are assumed to respond with their
-$\epsilon$-best replies.
-\begin{center}
-\begin{tabular}{c|c|c}
-Name & Bid total & Unit price\\
-\hline
-A & 50 & 1\\ 
-B & 40 & 1.2\\
-C & 26 & 1.5\\
-D & 20 & 2\\
-E & 14 & 2.2
-\end{tabular}
-\end{center}
-Let $s^{(1)} = [(65,\epsilon)]_{i\in\mcI}$ and
-$s^{(2)}=[(85,\epsilon)]_{i\in\mcI}$. The buyer bids are as follows: 
-\begin{align*}
-    s_A &= [(0,0), (50,1)], \\
-    s_B &= [(0,0), (40,1.2)], \\
-    s_C &= [(0,0),(26,1.5)], \\
-    s_D &= [(0,0),(20,2)], \\
-    s_E &= [(0,0), (14,2.2)]. 
-\end{align*}
-Then at $t=1$, we have 
-bid vector $s^{(2)}=[(0,p^{(2)}), (20,p^{(2)}), (26,p^{(2)}),\\ (20,p^{(2)}),
-(14,p^{(2)})]$, and so  $(D^{(2)},p^{(2)}) = (85, 1+\epsilon)$, The buyer response is,
-\begin{align*}
-    s_A &= [(50,1), (0,0)], \\
-    s_B &= [(40,1.2), (0,0)], \\
-    s_C &= [(0,0),(26,p^{(2)})], \\
-    s_D &= [(0,0),(20,p^{(2)})], \\
-    s_E &= [(0,0),(14,p^{(2)})].
-\end{align*}
-At $t=2$, $(D^{(1)},p^{(1)}) = (65,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}),\\ (40,p^{(1)}), (0,0), (0,0),
-(0,0)]$. $(D^{(2)},p^{(2)}) = (25, 1+\epsilon)$. Then,
-\begin{align*}
-    s_A &= [(25,p^{(1)}), (25,p^{(2)})], \\
-    s_B &= [(40,p^{(1)}), (0,0)], \\
-\end{align*}
-where we have removed bids to indicate winner(s) with a tentative allocation.
-At $t=3$, $(D^{(1)},p^{(1)}) = (50,1+\epsilon)$, with
-bid vector $s^{(1)}=[(25,p^{(1)}), (40,p^{(1)}), (0,0), (0,0),
-(0,0)]$. $(D^{(2)},p^{(2)}) = (0, 1+\epsilon)$ and $s^{(2)}=[(25,p^{(1)}),
-(0,0), (26,p^{(2)}), (20,p^{(2)}),\\(14,p^{(2)})]$. Then,
-\begin{align*}
-    s_A &= [(25,p^{(1)}), (0,0))].
-\end{align*}
-At $t=4$ the auction ends.\\
-\textbf{Remark:} In the case where market resources do not satisfy (\ref{bidcap}), however as
-this constraint is not restricted in time, we reason that in the case of
-insufficient data in the market buyers may wait for additional sellers or
-purchase from the ISP, $\kappa$, as a monopoly sale. Similarly, in
-the case of insufficient demand, where we may assume that data is held at time
-$t=0$ by $\kappa$ at bid price $\epsilon$.
-
-% VCG ANALYSIS
-\section{PSP Analysis}\label{analysis}
-
-\subsection{Equilibrium}
-
-We intend to show evidence shared network optima (a
-global optimum). 
-A buyer $i\in\mcI$ will have incentive to change its bid
-quantity if it increases its opt-out value $\g_i$, and therefore its utility (\ref{buyerutility}). 
-We will show that, without loss of utility, buyer $i$ may  
-use a ``consistent" bid strategy within its seller pool, i.e. $d_i^j = d_i^k, \
-\forall \ j,k \in \mcI_i$, and as such,
-Proposition \ref{buyerstrategy} supports an optimal strategy with respect to
-(\ref{buyerutility}). 
-Our result shows that a buyer may select $\mcI_i$ in order to maximize its
-utility while maintaining a coordinated bid strategy. 
-Reasonably, if $j^*< I$, a buyer may increase the size of its seller pool
-$\mcI_i$, thereby lowering its coordinated bid
-quantity while obtaining the same (potential) allocation $a_i$. 
-As buyer $i$ submits identical bids to multiple auctions, the bid price must be
-as high as the highest reserve price $p_i^j \in \mcI_i$.
-Buyer $i$'s bid then has identical bid price $p_i^j \forall \ j \in\mcI_i$. 
-We further note that $i$ optimal strategy does not require reducing its bid price to a
-minimum in each auction, where
-the bid quantity $\g_i^j(a)$ is still fufilled. The pricing rule of the PSP
-auction dictates that a buyer $i$ will pay the cost of excluding other players from
-the auction, and as $i$'s bid price reflects its valuation of it data
-requirement $D_i$ across all local markets, we have identical bid prices in
-each auction where $s_i^j>0$. Obviously, if $j\ni\mcI_i$, then $\theta_i^j = 0$.
-
-% BUYER COORDINATION
-{
-\lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
-Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
-For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be a
-tentative data
-allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
-(z_i,y_i)$, where $\forall \ j \in \mcI_i$,
-\begin{align*}
-    z_i^j &= \g_i^{j^*}(a), \\
-    y_i^j &= \theta_i'(z_i^j).
-\end{align*}
-Furthermore,
-\begin{equation}\label{allocationcoordination}
-    a_i^j(z_i,y_i) = z_i^{j},
-\end{equation}
-and
-\begin{equation}\label{costcoordination}
-    c_i^j(z_i,y_i) = y_i^{j},
-\end{equation}
-where $i$'s strategy is as in Proposition \ref{buyerstrategy}.
-}\\
-\textbf{Proof:}
-As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
-u_i(s_i;s_{-i})$. In full notation, we intend to show
-$$
-    u_i((d_i,p_i);s) \le u_i((z_i,y_i);s_{-i}).
-$$
-Now, if there exists a seller who can fully satisfy $i$'s demand,
-then $\vert\mcI_i\vert = 1$, and the case is trivial as no
-coordination is necessary for a single bid. %(SPECIAL CASE OF MONOPOLY? THINK!)\\
-Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
-multiple sellers.
-We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
-$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $\sum_{j\in\mcI_i}u_i^j$.
-Buyer $i$ maintains ordered set $\mcI_i$ where the sellers with the
-largest bid quantities are considered first; the index of seller $j^*$ defines
-a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$,
-so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$. 
-Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    \g_i^k(a) \le z_i^j = \g_i^{j^*}(a) \le \g_i^{j}(a),
-$$
-and so, using (\ref{union-eq}), 
-\begin{equation}\label{minimaleq}
-    \g_i^{j^*}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
-\end{equation}
-Now, the buyer valuation function (\ref{buyervaluation}), guarantees
-that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
-\ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
-be accepted. 
-As $\bar{D}_i^j$ is non-decreasing, $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j^*})\ge D_i^j(p_i^{k}).
-$$
-\iffalse
-Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$\g_k^{j^*}(a) \ge \g_i^{j^*}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
-partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
-As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j*}(a)
-\ge \g_k^{j^*}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
-We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
-$$
-    {\theta_i}'(e_i^{k}(a)) \ge {\theta_i}'(e_i^{j^*}(a)) \ge y_i^j.
-$$
-Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$...
-\fi
-Thus (\ref{minimaleq}) holds and so, by (\ref{dataallocation}),
-\begin{align*}
-     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j, \bigg\lbrack D^{j} - \sum_{p_k^{j}> y_i^{j}}
-d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= e_i^{j^*}(a)
-\end{align*}
-where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
-From (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
-0 \ \forall \ y < p_{i^*}^j$, and $\bar{D}_i^j(y, s_{-i}) =0 \le \epsilon
-\Rightarrow \g_i^j(a) = 0 \Rightarrow z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
-\begin{align*}
-    \displaystyle\sum_{j\in\mcI_i} c_i^j(z_i,y_i) =\sum_{j\in\mcI_i}
-c_i^j(z_i,p_i),
-\end{align*}
-thus (\ref{costcoordination}) simply shows that changing the price $p^j_i$ to $y^j_i$ does not exclude any
-additional buyers, as the bid $p^j_i$ was already above the reserve price of any
-seller $j \in \mcI_i$.
-We proceed to show that $x_i$ does not result in a loss of utility for
-buyer $i$, that is,
-$$
-    u_i \le u_i(z_i,y_i).
-$$
-From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = \g_i^j(a(z_i,y_i))$, 
-and so,
-$$
-    \theta_i\circ \g_i^j(a(z_i,y_i)) = \theta_i\circ \g_i^j(a),
-$$ 
-which holds $\forall \ j\in\mcI_i$.
-Therefore, by the definition of utility (\ref{buyerutility}),
-and the buyers' valuation (\ref{buyervaluation}), 
-\begin{align*}
-    &\theta_i\circ \g_i(a(z_i,y_i)) - \theta_i(a)\circ \g_i(a) \\
-    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
-    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - x) \ dx.
-\end{align*}
-Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
-$z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
-$\qed$
-%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
-
-\subsubsection{Incentive Compatibility}
-
-The property of truthfullness is an essential component of equilibrium in
-second-price markets. The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, and due to our
-construction, we intend to show that truthful bids are optimal for all users,
-i.e. bid prices are to the marginal value as determined by market dynamics. 
-To achieve incentive compatibility, we find that the opt-out buyer must choose
-this subset so that its overall marginal value is greater than its market price.
-We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
-has incentive to change its bid as a result of a market shift or partial
-allocation. We now show the necessary condition of a truthful reply, new bid
-prices must differ from the last by at least $\epsilon$, and prove that the
-resulting bid is an $\epsilon$-best response, supporting our strategic analysis.
-In a truthful reply, the term $\epsilon/\theta_i'(0)$
-ensures that a new bid price differs from the last bid price by at least
-$\epsilon$, thereby ensuring that a buyer does not change its bid without
-correcting the effects of unstable transitions.
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a local market equilibrium extending over a subset of connected
-local markets. We have the following Proposition. 
-(DO I NEED TO PROVE CONTINUITY TOO?)
-
-{
-\proposition{(Incentive compatibility across local auctions)}
-Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
-$t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
-buyer $i\in \mcI^j$, (DO I WANT LAMBDA? SO MANY CASES) let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
-\begin{align}
-\begin{split}\label{eta}
-    \chi_i &= \bigg\lbrace x\in [0,D_i] : 
- {\theta_i}'(x) > \max_{j\in\Lambda}P_i^j(x)\bigg\rbrace, 
-\end{split}
-\end{align}
-and $z = \sup(\chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
-\Lambda$, 
-$$
-    v_i^j = \g_i^{j}(z),
-$$
-and 
-$$
-    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
-$$
-Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
-(v_i,w_i)$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
-s_{-i})$.
-With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
-in the global market, and thus denoting $\Gamma= \Lambda \cup \lambda$, we have
-an equilibrium point in $\Gamma$. 
-}\\
-\textbf{Proof:}
-We claim that $t_i$ is an $\epsilon$-best reply for buyer $i$. That is,
-$$
-    u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;s_{-i}).
-$$
-As a result of auction initialization, a seller $j$'s valuation defines its
-reserve price to be determined
-by a buyer $i \ni \lambda$, even if this price is zero, we have that $p^j =
-\epsilon \ge 0 \ \forall \ j \in\Lambda$.
-Let $z = \sup(\chi_i^j)$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, and $p_i^*= f_i \circ \g_i^j(a)$ denote the (coordinated) bid price of buyer $i$. 
-We have that $i\in\mcI^j$, 
-and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
-max of the reserve prices $p_*^j,\ \forall \ j\in\mcI_i$, therefore
-(\ref{eta}) is such that,
-$$
-    \theta_i'(z) > \max_{j\in\Lambda}P_i^j(v_i^j),
-$$ 
-which implies, as $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
-we have $\forall \ j \in \mcI_i$, 
-\begin{align*}
-    w_i^j &> P_i^j(v_i^j) \\
-    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
-\end{align*}
-And so, by (\ref{dataallocation}),
-\begin{align*}
-    a_i^j(t_i;s_{-i}) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\Lambda} a_i^j(t_i;s_{-i}) &= z.
-\end{align*}
-Therefore, $\forall \ j\in\Lambda$ and $\forall \ i \in \lambda$ such that
-(\ref{tieqtk}) and (\ref{tkeqtl}) hold,
-\begin{align*}
-    \int_0^{v_i^j} \bar{P}_i(x) \ dx 
-    = \sum_{j\in\Lambda}\int_0^{\g_i^j(z)} P_i^j(x) \ dx.
-\end{align*}
-It follows that,
-$$
-    u_i(t_i;s_{-i}) = \int_0^{z} \theta_i'(x) \ dx -  \g_i \ \circ \int_0^{z} \bar{P}_i(x) \ dx.
-$$
-Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
-s_{-i}) + \epsilon$. Propositions
-\ref{coordinationlemma} and
-\ref{buyerstrategy}, define the coordinated bid, $\nu_i=(\zeta_i, p_i)$,
-% = (\g_i\circ a_i(s), \ \theta_i'(z)) = (z_i, c_i),$
-using (\ref{tieqtk}) and (\ref{tkeqtl}),
-for each $j\in \Lambda$, $\g_i^j(a_i^j(\nu_i; s_{-i})) = \zeta_i^j$,
-then clearly $u_i(\nu_i, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
-u_i(s_i;s_{-i}) > \epsilon$. Denoting $\zeta_i^j$ (fixed) as $\zeta$, 
-$$
-    \int_z^{\zeta} {\theta_i}'(x) \ dx-\int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
-$$
-For concave valuation functions, the first-order derivative of $\theta$ at point
-$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
-/ \theta'(0)$ guarantees that new bids will differ by at least
-$\epsilon$, and as such, buyer $i$ will remain in
-any local auction with reserve price determined by (\ref{newprice}). We therefore
-verify that,
-$$
-    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
-dx \le \epsilon,
-$$
-and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
-$$
-    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
-\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
-$$
-If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
-$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
-\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
-Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
-\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
-exist.
-Finally, as we may consider $\Delta \subset \mcI$ to be a
-multi-auction game, our user strategies form a ``truthful" local game 
-with strategy space restricted to $\epsilon$-best replies from buyers $\in
-\lambda$. Therefore we have that a fixed point in the ``truthful" game is a fixed point for the auction. 
-$\qed$\\
-For completeness, we address the sellers bids, and include the following corollary to support our result.
-{
-\corollary{Seller cooperation.}
-We claim that $s^j$ is both truthful and optimal.
-}\\
-\textbf{Proof:}
-For a single buyer-seller interaction, (\ref{jtoi}) gives that $\theta_i =
-\theta^j \Rightarrow \theta_i' = {\theta^j}'$. Thus, we have by symmetry, as the buyers' bids are
-truthful, and by (\ref{newprice}), $j\in\Lambda$ cannot set a higher reserve price, 
-and cannot sell more data than the buyers' aggragated bid quantities.
-The result follows by Lemma \ref{userunion} and Lemma \ref{buyercoordinate}.\\
-
-The data-sharing market consists of a inter-dependent sets of these
-multi-auction games around fixed points. We have that $\Delta$ is defined by a seller $j\in\mcI$, where each
-user $k\in\Delta$ has some direct or indirect influence on $j$. 
-We may identify $\Delta$ by its dominant seller. Let $\Delta^j$ denote $j$'s
-influencing sets. Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. Consider two subsets, $\Delta^j$
-and $\Delta^k$, at equilibrium, and a shared
-buyer $i\in (\lambda^j \cup \lambda^k)$, where
-$\lambda^j\subset\Delta^j$, and  $\lambda^k\subset \Delta^k$.  By Lemma
-\ref{userunion}, a transition is induced in $\Delta^k$ by $\Delta^j$ if and only if
-$\exists \ l \in \Lambda^j$ such that $p_*^{l} > p_*^{q}$, for some
-$q\in\Lambda^k$. We claim that the shared buyers
-between the different subsets $\Delta$ form a heirarchical structure, and that
-there can only be a single primary fixed point, and this seller determines
-the equilibrium price in the global market. Consider a subset $\Delta^j$. Clearly, if $i^*$, from Proposition
-\ref{sellerstrategy}, increases its valuation,
-then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider a
-seller $k^*\in\mcI_{i^*}$. Since $p_{i^*}^j <
-p_*^j$, we have that $k^*\ni\Lambda\subset \Delta^j\Rightarrow \mcI^{k^*} \ni
-\lambda$. Now, suppose at the end of some time step, $p_*^{k^*} > p_*^j$, and
-consider a buyer $l^*\in\mcI^{k^*}$. Clearly, if $l^*\in\mcI^j$, then $j$'s
-valuation wil increase. Suppose $l^*\ni\mcI^j$, from Proposition \ref{userunion}, if $l^*\in\mcI^k\subset
-\Delta^j$, for some $k\in\mcI_i$, where $i\in\Delta^j$, then either
-$k^*\ni\mcI_i$ or $\exists \ q\in\mcI_i$ such that $p_*^q \ge p_*^{k^*}$. In
-the former case, the valuation of $k\in\mcI_i$ and $j$ will increase.
-In the latter case, $p_*^q \ge p_*^{k^*}$ for some
-$q\in\mcI_i$, and then only the valuation of $j$ will increase. We have that $j$ is
-directly influenced by our choice of seller $k^*$, and observe that
-$i\in\mcI^j$ is free to increase its valuation within $\Delta^j$. 
-Now, consider the set of sellers across all $\Delta$,
-$\bigcup_{j\in\mcI}\Lambda^j$.
-
-%Consider
-%again $q\in\mcI_i$, and the subset $\Delta^q$, where $p_*^q \ge p_*^j$, and
-%a buyer $l\in\lambda\subset\Delta^q$ chosen in the same way as $l^*$.
-
-A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
-profile $s$,
-from which no player has a unilateral incentive to deviate (Johari, 2004)
-(EXPAND)
-We first show the existence of a \emph{static} Nash equilibrium, where buyers have fixed reserve
-prices.
-
-{
-\lemma{(Static Nash Equilibrium)} 
-}
-
-As a result of user behavior, and subsequent strategies, we determine that the
-global data-exchange market behaves in a predictable way. However, as
-each auction may be played on the same or on a different scale in
-valuation, time and quantity, the rate at which market fluctuations occur is
-impossible to predict (NEED HELP!). 
-Arrow's paradox is an impossibility theorem stating that when buyers have three
-or more distinct alternatives (auctions), no deterministic ranking system can
-convert the ranked preferences of users into a market-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives. It follows that the case where
-$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
-is disjoint.
-
-Nonetheless, we claim that our mechanism is normative, that irrelevant
-alternatives should not matter, it is practical, uses minimal information,
-strategy, and provides the right incentives for the truthful revelation of individual preferences. 
-(EXPAND)
-% DATA NASH EQ
-{
-\theorem{(Nash Equilibrium)}
-Using the rules of the data auction mechanism, the CMHK
-\cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
-game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
-equilibrium. 
-}\\
-\textbf{Proof:}
-
-\subsection{Efficiency}
-
-Formally, the
-mechanism is equilbriumcient if at equilibrium, the allocation maximizes
-$\sum_i\theta_i(a_i)$.
-(NEED OWN WORDS)
-The objective in designing the auction is that, at equilbrium, resources al-
-ways go to those who value them most. Indeed, the PSP mechanism does
-have that property. This can be loosely argued as follows: for each player,
-the marginal valuation is never greater than the bid price of any opponent
-who is getting a non-zero allocation. Thus, whenever there is a player j
-whose marginal valuation is less than player i 's and j is getting a non-zero
-allocation, i can take some away from j , paying a price less than i 's marginal
-valuation, i.e. increasing u i , but also increasing the total value, since i 's
-marginal value is greater. Thus at equilibrium, i.e. when no one can unilat-
-erally increase P their utility, the total value is maximized.
-
-\subsection{Convergence}
-
-%\end{multicols}
-
-\begin{thebibliography}{9}
-
-\bibitem{zheng}
-L. Zheng, C. Joe-Wong, C. W. Tan, S. Ha and M. Chiangs, 
-\textit{Secondary markets for mobile data: Feasibility and benefits of traded
-data plans}, 2015 IEEE
-Conference on Computer Communications (INFOCOM), Kowloon, 2015, pp. 1580-1588.
-
-\bibitem{lazar}
-A. A. Lazar and N. Semret, 
-\textit{“Design and Analysis of the Progressive Second Price Auction for Network
-Bandwidth Sharing,”} Telecommunication Systems, Special Issue on Network Economics, 2000.
-
-\bibitem{semret} 
-N. Semret, 
-\textit{“Market Mechanisms for Network Resource Sharing,”
-Ph.D. thesis}. 
-Columbia University, 1999.
-
-\bibitem{tuffin}
-Bruno Tuffin,
-\textit{Revisited Progressive Second Price Auction for Charging
-Telecommunication Networks}.
-[Research Report] RR-4176, INRIA, 2001.
-
-\bibitem{qpsp}
-Clare W. Qu, Peng Jia, and Peter E. Caines,
-\textit{Analysis of a Class of Decentralized Decision Processes: Quantized
-Progressive Second Price Auctions},
-46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
-779-784.
-
-\bibitem{cmhk}
-\textit{China Mobile Hong Kong Company Limited}.
-\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html}.
-2018
-
-\bibitem{iia}
-Andreu Mas-Colell, Michael Dennis Whinston, and Jerry R. Green, 
-\textit{Microeconomic Theory}. Oxford University Press. 1995. p. 794.
-
-\bibitem{matt}
-Matthias Roggendorf and Fernando Beltr{\'a}n,
-\textit{Simulation Model for the Dynamic Allocation of Network Resources in a
-Competitive Wireless Scenario}. Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
-pp. 54 - 64.
-
-\bibitem{diffserve}
-N. Semret, R. R. F. Liao, A. T. Campbell and A. A. Lazar, 
-\textit{Pricing, provisioning and peering: dynamic markets for differentiated Internet services and
-implications for network interconnections}, in IEEE Journal on Selected Areas in
-Communications, vol. 18, no. 12, pp. 2499-2513, Dec. 2000.
-
-\end{thebibliography}
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{ccs-sample}
 

### 2019-08-21 paper_acm.tex
On hold.

%\documentclass[journal,comsoc]{IEEEtran}
\documentclass[sigconf, anonymous]{acmart}
%\documentclass[12pt]{article}

\usepackage{algorithmicx}
\usepackage{algorithm,algpseudocode}
\usepackage[english]{babel}

\newcommand{\vs}{\varsigma}
\newcommand{\mcL}{\mathcal{L}}
\newcommand{\mcI}{\mathcal{I}}
\newcommand{\g}{\sigma}
\newcommand{\s}{\nu}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\iffalse

\newtheorem{proposition}{Proposition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{sublemma}{Lemma}[lemma]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\headsep25pt\headheight20pt
\setcounter{secnumdepth}{4}
\pagestyle{fancyplain}
\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
\cfoot{\ \hfill\tiny\sl Draft printed on \today}
\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables

\fi
 %\iffalse
%---------------ACM CCS---------------------%
\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#837 to ACM CCS 2018} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer
and Communications Security}{Due 8 May 2018}{Dallas, Texas}
\acmYear{2018}

\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
%-------------------------------------------%
%\fi

\begin{document}
%\begin{multicols}{2}
\title{A Trusted Mechanism for the Fair Allocation of Mobile Data}

\begin{abstract}

%Verizon and At\&T, two major Internet service providers (ISPs), are offering
%shared data plans, where multiple users may purchase and share a single pool of
%data. 
We propose a distributed, privacy-preserving auction-based approach to
allocation in a secondary market for wireless data exchange.
The secondary market is modeled as a fully connected, pure ``point of sale"
market, with initial public platform provided by its parent wireless internet service
provider (ISP). 
The progressive second price (PSP) auction rules provide our underlying auction
structure, allowing for a single degree of freedom, the reserve
price. We suggest that data exchange markets allow for greater flexibility in
mechanism design.
We propose new, natural degrees of freedom, and derive modifiers
to represent the deformation of the strategy space.

Wireless users are modeled as a fixed type with dynamic incentives. Using a game
theoretic analysis, we derive strategy profiles for wireless users
based on their typed response to market dynamics, resulting in self-contained, self-balancing pricing system. 
We examine mutations in the strategy space resulting from the new modifiers, and
prove that the desired PSP properties hold. 
Convergence is determined by set theory; we prove that the symmetry of our
strategy space provides built-in conditions for convergence and stability, finally arriving at a network Nash equilibrium.

Trust and privacy issues in secondary markets have yet to be addressed.
As rational users will not publicly reveal valuations, out users form coalitions to establish trust with local auctioneers.
In a centrally moderated secondary market, an unregulated,
rational ISP will prevent its secondary market from acting as a competitor.
Competition is desired as it provides incentive for the ISP to protect
and care for its end users.
The distributed nature of PSP extends individual privacy to the secondary market,
allowing for it to compete with its parent ISP. 
\end{abstract}

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10002986.10002987</concept_id>
<concept_desc>Security and privacy~Trust frameworks</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10002978.10003006.10003013</concept_id>
<concept_desc>Security and privacy~Distributed systems security</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10002978.10003014.10003017</concept_id>
<concept_desc>Security and privacy~Mobile and wireless security</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Security and privacy~Trust frameworks}
\ccsdesc[300]{Security and privacy~Distributed systems security}
\ccsdesc[100]{Security and privacy~Mobile and wireless security}

\keywords{game theory, second price auctions, mobile share, software-defined networks} 
\maketitle

\input{body_acm}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper_acm}

\end{document}

### 2019-08-21 save.tex
On hold.

--- 2018-05-07 paper_wc.tex
@@
 \documentclass[sigconf, anonymous]{acmart}
+%\documentclass[12pt]{article}
 
@@
 
-\usepackage{enumerate}
-\usepackage{amsmath,amsthm,amssymb}
-\usepackage{mathrsfs} % to use mathscr fonts
-
-\usepackage{multicol}
-\usepackage{url}
-
-\usepackage{epstopdf}
-\usepackage{caption,subcaption}
-\usepackage{pstricks}
-\usepackage{pst-solides3d}
-\usepackage{pstricks-add}
-\usepackage{graphicx}
-\usepackage{pst-tree}
-\usepackage{pst-poly}
-\usepackage{calc,ifthen}
-\usepackage{float}\usepackage{multicol}
-\usepackage{multirow}
-\usepackage{array}
-\usepackage{longtable}
-\usepackage{fancyhdr}
+%\usepackage{enumerate}
+%\usepackage{amsmath,amsthm,amssymb}
+%\usepackage{mathrsfs} % to use mathscr fonts
+
+%\usepackage{multicol}
+%\usepackage{url}
+
+%\usepackage{epstopdf}
+%\usepackage{caption,subcaption}
+%\usepackage{graphicx}
+%\usepackage{float}\usepackage{multicol}
+%\usepackage{multirow}
+%\usepackage{array}
 \usepackage{algorithmicx}
 \usepackage[noend]{algpseudocode}
-\usepackage{changepage}
-\usepackage{color}
-\usepackage{listings}
-\usepackage{fancyvrb}
-\usepackage{verbatim,moreverb}
-\usepackage{courier}
+%\usepackage{changepage}
+%\usepackage{color}
+%\usepackage{listings}
+%\usepackage{fancyvrb}
+%\usepackage{verbatim,moreverb}
+%\usepackage{courier}
 \usepackage{algorithm}
@@
 \newcommand{\g}{\sigma}
+\newcommand{\s}{\nu}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 \newtheorem{lemma}{Lemma}[section]
-\newtheorem{corFollary}{Corollary}[section]
+\newtheorem{corollary}{Corollary}[section]
 \newtheorem{sublemma}{Lemma}[lemma]
@@
 \fi
-
+ %\iffalse
 %---------------ACM CCS---------------------%
@@
 \setcopyright{none} % No copyright notice required for submissions
-\acmConference[?]%Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
-\acmYear{2017}
+\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer
+and Communications Security}{Due 8 May 2018}{Dallas, Texas}
+\acmYear{2018}
 
@@
 %-------------------------------------------%
+%\fi
 
@@
 %data. 
-We investigate data-exchange platforms for wireless users. The
-2cm (2nd exchange market) creates a secondary market where users can buy and sell data from each other.
-The ISP owns and moderates 2cm, which prevents the secondary market from
-acting as a competitor, and provides the ISP with free market research.
-Competition is desired, as it provides incentive for the ISP to protect
+We propose a distributed, privacy-preserving auction-based approach to
+allocation in a secondary market for wireless data exchange.
+The secondary market is modeled as a fully connected, pure ``point of sale"
+market, with inital public platform provided by its parent wireless internet service
+provider (WISP). 
+The progressive second price (PSP) auction rules provide our underlying auction
+structure, allowing for a single degree of freedom, the reserve
+price. We suggest that data exchange markets allow for greater flexibility in
+mechanism design.
+We propose new, natural degrees of freedom, and derive modifiers
+to represent the deformation of the strategy space.
+
+Wireless users are modeled as a fixed type with dynamic incentives. Using a game
+theoretic analyis, we derive strategy profiles for wireless users
+based on their typed response to market dynamics, resulting in self-contained, self-balancing pricing system. 
+We examine mutations in the strategy space resulting from the new modifiers, and
+prove that the desired PSP properties hold. 
+Convergence is determined by set theory; we prove that the symmetry of our
+strategy space provides built-in conditions for convergence and stablility, finally arriving at a network Nash equlibirium.
+
+Trust and privacy issues in secondary markets have yet to be addressed.
+As rational users will not publicly reveal valuations, out users form coalitions to establish trust with local auctioneers.
+In a centrally moderated secondary market, an unregulated,
+rational ISP will prevent its secondary market from acting as a competitor.
+Competition is desired as it provides incentive for the ISP to protect
 and care for its end users.
-In this work, we design a strategy space, and a distributed Progressive Second Price (PSP) mechanism
-that extends individual privacy to the global space, allowing a secondary market to compete with its parent ISP. 
-The PSP auction has a single degree of freedom, the reserve price. We suggest
-that data exchange markets allow for greater flexibility in mechanism
-design due to the connectedness of the wireless network, and the fact that data
-exchange is a pure ``point of sale" market.
-We propose additional degrees of freedom, and derive modifiers
-to represent the deformation of the strategy space. 
-Using a game theoretic analysis, we derive a new strategic
-framework, removing restrictions that are dependent only on bandwidth. We
-model user valuation as a strategic response to market dynamics, and propose
-the resulting self-contained, self-balancing pricing system. 
-We examine mutations in market dynamics resulting from the new modifiers, and
-using set theory, we prove that the symmetry of our strategy space provides built-in
-conditions for convergence, and upholds the properties of truthfulness, efficiency and
-incentive compatibility, arriving at a Nash equlibirium.
+The distributed nature of PSP extends individual privacy to the secondary market,
+allowing for it to compete with its parent ISP. 
 \end{abstract}
-
-\iffalse
-We further provide bounds on the auction duration, 
-with respect to the classic throughput problem.
-and provide simulated results on convergence time to support our (FIND
-COMPETITVE RATIO!), and a bound
-on the convergence of our mechanism. We extend the works of cite!cite!
-i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
-market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
-\fi
 
@@
 
-In this work, we propose a PSP auction mechanism for a secondary data
-market's valuations to be hidden from its parent ISP.
-A quality of the PSP auction is that
-demand information is not known centrally, rather, it is distributed in the
-buyers' valuations. The mechanism for an auction is defined
-as \emph{distributed} when the allocations at any element depend only on
-\emph{local} state, no single entity holds a global market knowledge. We consider the multi-auction, where there are many auctioneers, each holding
-thier own local auction. The auction mechanism may be described as
-pure-strategy progressive game with incomplete, but perfect information.
+An evolving consumer culture is has led wireless internet service providers
+(ISPs) to rethink their service plans. Mobile data usage is quickly outpacing voice and SMS in
+wireless network, and the trend is only expected to increase with
+multi-device ownership. Declining revenue has caused ISPs search for sources
+of new revenue in the changing market. Thus the introduction of the shared data plan \cite{att}. Using an account
+service, users are able to keep track of data usage in real time across all
+their devices. 
+The shared data service plan requires that users hold an \emph{a priori}
+knowledge of demand.
+We address several topics: data as a product in the real-monetary market, and
+data a network resource in a wireless topology.
+
+Many new services are found exclusively on mobile devices; older softwares
+are moving from (wired) grid-based to node-based communication. Software-defined
+networking (SDN) addresses the new environment of wireless communication
+devices, allowing for a programmable network architecture. 
+The account services that manage wireless shared data plans decentralize
+network management, and mobility becomes a factor in SDN design.
+Individual mobile devices provide flexibility, and may make decisions regarding
+local network infrastructure. There is a clear need for algorithms designed for
+optimization in this space. In many cases, the direct communication between
+mobile devices allows for a simple mutation of classic optimization models.
+Auctions are key in SDN for the fair allocation of resources. For this work, we
+focus on mobile data, an infinitely divisible and distributable quantity.
+Mobile data represents online data accessed using the WISP network, and as
+representation of future network usage, we are able remove restrictions imposed
+by the physical layer.
+
+We focus on Vickery-Clark-Groves (VCG) type 
+auction mechanisms that are (1) easily distributed, and (2) allocate an infinitely
+divisible resource.
+In \cite{lazar}, Lazar and Semret introduce the Distributed Progressive Second Price (PSP)
+Mechanisms for bandwidth allocation. An auction mechanism is defined
+as distributed when the allocations at any element depend only on
+local state, no single entity holds a global market knowledge. We consider the
+multi-auction, where there are many auctioneers, each holding thier own local auction.
+
+The model for data exchange was recently adopted by China Mobile Hong Kong
+(CMHK), who released a platform, 2cm (2nd exchange market) creating a secondary
+market where users can buy and sell data from each other.
+CMHK owns and moderates 2cm, centrally computing allocations of mobile data
+based on bids submitted to the platform.
+Flexible data-sharing
+plans are similar to the CMHK market, where a limited number of devices may
+share a single data plan. A shared-data plan, however limited, offers better economy
+by creating primary users with a service package with cellular, and a lot of data, and
+limited number of secondary users that are using only data \cite{att}.
+The secondary market allows for primary and secondary users to freely correspond,
+without the restriction of a static primary-secondary user association.
+
+Users on the shared data plan given by \cite{att} do not ``buy" or ``sell"
+data, however, we may easily augment the model to include a price function,
+which may be virtual, creating a secondary market.
+In order to demonstrate potential of expanding to other $\emph{a priori}$ use
+models, we give a simple example. Consider Alice and Bob, who met through an online service connecting neighborly
+individuals closest to each other, in fact, close enough to be within wireless
+range. Alice is going on vacation, and offers to transfer her wireless signal to
+Bob. As they have the same provider, Bob agrees, and is able to use Alice's
+bandwidth, which he finds is useful during peak network
+hours. He pays a discounted rate. We note that the additional bandwith may be
+used by another device, or even a 5G-capable mobile device.
+
+The secondary market provides a unique opportunity for social equilibrium, as it
+allows users to share data without sharing the same data plan, a restriction in
+most ISPs, such as \cite{att}. We reason that a secondary market effectively creates a competitive secondary market, and contributes to the
+dynamics of a free-market economy. Market competition is a desirable quality in
+free markets, and is encouraged, particularly in wireless and data services. In
+fact, California Legistature has recently passed laws promoting
+competition and enforcing fair practice of ISPs \cite{cabill}.
+Laws such as \cite{fedbill} exist to
+regulate ISPs as they have historically come close to monopolizing regional
+markets, leading to consumer abuse.
+The global view of privacy has not been addressed, as the data exchange model is still
+in its experimental phase.
+Within the secondary market, bid privacy is a concern for two reasons: (1) Buyers are reluctant to
+reveal their true valuations, as sellers may use these values to discriminate
+against specific buyers. (2) Buyers doubt an auction's outcome, as they do
+not pay what they bid, e.g. the auctioneer might create a fake
+second highest bid slightly below the highest bid in order to increase his revenue
+In general, the buyer does not trust the auctioneer, and the economy does not
+trust the ISP.
+
+We therefore determine that our mechanism must be (3) globally and locally privacy-preserving.
 
@@
 ($\epsilon$-Nash) equilibrium is reached. 
-
-In the distributed setting, we assume users have a binary type, either seller,
-i.e. auctioneer, or buyer, and so user strategy changes according to the user
-type.
-
-We use game theory to show that the PSP mechanism, when applied to a
-pure ``point-of-sale" market, results in a primary
-$\epsilon$-Nash market equilibrium that is the dominant strategy in the
-multi-auction system.
-To the best of our knowledge, this is the first work to provide a comprehensive
-derivation of a truthful mechanism that is self-contained within a dynamic market
-topology. The market
+Our mechanism
+takes advantage of the opportunity for adaptation provided by the
+secondary market.
+
+The secondary market applies the PSP auction rules over a wireless network. The
+wireless users' data incentives create a pure ``point-of-sale" market. We prove
+that there exists a primary $\epsilon$-Nash market equilibrium that is
+the dominant strategy in the multi-auction system.
+
+The market
 topology and the user strategy are organically determined by the impact of user
@@
 representing user valuation globally, and so fufills an additional property of
-economy over time and space. We further model the ISP as a deaf and blind
-user, who nonetheless holds the power to create a monopoly, thereby providing a free
-market space in which the market may operate, and real-world implications.
-
-The market strategy is based on providing users with an incentive framework, and
-so rational users choose a collaborative exchage. 
-%\textbf{Remark:} It is certainly possible to extend the mechanism, alleviating the
-%restrictions introduced by the CMHK secondary market. We reserve this for
-%future work.
+economy over time and space. To the best of our knowledge, this is the first
+work to provide a comprehensive derivation of a truthful mechanism that is self-contained within a dynamic market
+topology.
+To the best of our knowledge, this is the first work to provide a comprehensive
+derivation of a truthful mechanism that is self-contained within a dynamic market
+topology.
+
 In classic mechanism design, with multiple user types, there is no single
@@
 local equilibria follow as a result of incentive
-compatibility characterizing best strategy moves. \\ 
-\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
-from mechanism design and game theory, respectively.\\
-\iffalse
-We claim that our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead 
-and auction duration, resulting in a convergence time (FIND COMPETITIVE RATIO?)
-with respect to the classic throughput problem. 
-\fi
-
+compatibility characterizing best strategy moves.
+We claim that our formulation holds the desired PSP qualities,
+converging at a rate of $\mathcal{O}(\sum_{i\in\mcI}(\sum_{j\in\mcI}) \theta_i /
+\epsilon I!)$.
+We note that the convergence time is dependent on the ratio of
+supply and demand, or the ratio of buyers to sellers.
+
+We focus on providing users with an incentive framework, and
+so rational users choose a collaborative exchage. 
 The user strategies are organic in that they are natural, or
@@
 This is the (built-in) transformation from the
-direct-revelation mechanism to the desired message space, (OWN WORDS) where each user
-message defines a strategic point, which we may interpret as a move to a better
-market position. Then, in the limit of the data-model, a user reveals its
-valuation of a quantitiy of data-resource over the whole range of possible demands.
-
-The secondary market applies the PSP auction rules over a wireless network. The
-wireless users' data incentives create a pure ``point-of-sale" market. We prove
-that there exists a primary $\epsilon$-Nash market equilibrium that is
-the dominant strategy in the multi-auction system.
-To the best of our knowledge, this is the first work to provide a comprehensive
-derivation of a truthful mechanism that is self-contained within a dynamic market
-topology. The market topology and the user strategy are organically determined by the impact of user
-behavior on market dynamics. We determine a globally optimal objective, and a
-strategy that satisfies the desires properties of competition, and
-economy over time and space.
-
-We address several topics under discussion in the real-monetary market of virtual
-data ownership. The proliferation of services that are moving from grid-based to node-based communication
-calls for algorithms designed for optimization in this space. Direct and
-network-based communication between mobille devices allows for a simple
-mutation of classic optimization models.
-
-The secondary market provides a unique opportunity for social equilibrium, as it
-allows users to share data without sharing the same data plan, a restriction in
-most ISPs, such as \cite{att}. We reason that a secondary market
-approximates local, free-market economy. Laws such as \cite{fedbill} exist to regulate ISPs
-as they have historically come close to monopolizing regional markets, leading
-to consumer abuse. Our mechanism
-takes advantage of the opportunity for full generalization provided by CMHK.
-Our secondary market is adapted from the idea behind 2cm, the goal of allowing
-users to buy and sell data. We claim that it is simple
-to adapt our mechanism to the data share
-plans published by any major ISP, for example AT\&T's data share plan \cite{att}.
-We argue that data-sharing plans in general may be
-biased against the end-user. Adding devices to a shared-data plan includes a
-base fee for other services that have relatively small demand in comparison to
-the demand for data. Effectively, users must pay for services that go unused in
-order to increase the amount of data for a shared plan. Flexible data-sharing
-plans are similar to the CMHK market, where a limited number of devices may
-share a single data plan. A shared-data plan, however limited, offers better economy
-by creating primary users with a service package with a lot of data, and
-limited number of secondary users that are only using data \cite{att}.
-The CMHK model allows for primary and secondary users to freely correspond,
-without the restriction of a static primary-secondary user association.
-This effectively creates a competitive secondary market, and contributes to the
-dynamics of a free-market economy. Market competition is a desirable quality in
-free markets, and is encouraged, particularly in wireless and data services. In
-fact, California Legistature has recently passed laws promoting
-competition and enforcing fair practice of ISPs \cite{cabill}.
+direct-revelation mechanism to the desired message space, Then, in the limit of
+the data-model, a user reveals its valuation of a quantitiy of data-resource over the whole range of possible demands.
+
+We describe our auction mechanism as a
+pure-strategy progressive game with incomplete, but perfect information.
+
 The paper is organized as follows... (TODO)
@@
 
-%\iffalse
-\section{Distributed Progressive Second Price Auctions}
-
-Progressive second price auctions (PSPs) were proposed
-in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
-scheme to provide consistent services for network bandwith users.
-\cite{diffserve} conducts a game theoretic analysis, deriving
-optimal strategies for buyers and brokers, and further shows the existence
-of networkwide market equilibria based on their game-theoretic
-model. Constructing necessary and sufficient conditions for the stability
-of the game allows the sustainability of any set
-of service level agreement configurations between Internet service
-providers.
-
-We begin with a brief introduction to the distributed PSP auction for bandwith
-sharing, first introduced by Lazar and Semret \cite{lazar}.
-We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ network bandwidth users.
-Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
-seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
-pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents. 
-Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
-bids $s_{-i}$,
-user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
-and is a Nash move
-where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
-budget, and every user has an elastic demand function.
-Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
-an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
-by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
-allocations awarded in auction $j$. 
-An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
-
-% MECHANISM
-\subsubsection{The PSP Mechanism}\label{mechanism}
-The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
-problem of network bandwidth allocation, and is analyzed as a noncooperative
-game where $i\in\mcI$ agents buy the
-fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
-The market price function (MPF) for a buyer-seller pair is,
-% MARKET PRICE
-\begin{align}\label{dataprice}
-\begin{split}
-    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : D_i^j(y, s_{-i}) \ge z \bigg\rbrace,\\
-\end{split}
-\end{align}
-and is the of minimum prices a user bids in
-order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
-The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is,
-% INVERSE DEMAND
-\begin{align}\label{datapriceinverse}
-\begin{split}
-    D_i^j(y, s_{-i}) &= \bigg[ D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg]^+,
-\end{split}
-\end{align}
-where $D^j$ is the total amount of bandwith that user $j$ has to offer.
-% DATA ALLOCATION RULE
-For each $i \in \mcI$, the allocation from auction $j$ is,
-% and so for profile $s_i$, for any $i \in \mcI$,
-\begin{align}\label{dataallocation}
-    a_i^j(s) &= \min\bigg( d_i^j, 
-    D_i^j(p_i^j,s_{-i}^j)\bigg).
-\end{align}
-Finally, we have the cost of the allocation,
-% DATA COST
-\begin{align}\label{datacost}
-    c_i^j(s) = \displaystyle\sum_{k\ne i} 
-p_k^j \big[a_k^j(0; s_{-i}^j)
-    -a_k^j(s_i^j;s_{-i}^j)\big].
-\end{align}
-
-It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
-equilibria for differentiated services
-allocated between multiple agents when all players bid their real marginal valuation
-of the bandwidth resource. In other words, the PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive
-compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
-principle}, user $i$
-pays for its allocation so as to exactly cover the ``social opportunity cost"
-which is given by the declared willingness to pay (bids) of the users who are
-excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
-revenue \cite{lazar}.
-{
-\definition{(Nash Equilibrium)}
-A Nash equilibrium is defined as a strategy vector, or, in terms of PSP, a bid
-profile $s$,
-from which no player has a unilateral incentive to deviate (Johari, 2004)
-(EXPAND?)
-}\\
-
-The PSP rules assume that an agent's valuation is represented by an elastic valuation function.
-\definition{\cite{lazar}}
-A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta(0) = 0$,
-    \item $\theta$ is differentiable,
-    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
-{\theta}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
-The function $\theta'(\cdot)$ on $[0, D]$ is called an (elastic) demand
-function.
-In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
-%\fi
-
 \section{The Problem Model}
 
-\subsection{The CMHK Market}
+\subsection{The Secondary Market}
 
 We construct the model for a PSP data auction for mobile users
-particpating in CMHK's secondary data-sharing market.
-Define the index set $\mcI = \lbrace 1, \cdots, I\rbrace$ to represent the set of users who purchase or sell
-data from other users. We again define the bidding profile for any user to be 
+particpating in secondary mobile data exchange market.
+Let the set of all wireless users to be labeled by
+the index set $\mcI = \lbrace 1, \cdots, I\rbrace$. In our current formulation, we do not allow a seller to host multiple
+auctions, thus we may assume that data is a unary resource belonging to the seller, and
+identify each local auction with the index of the seller
+$j\in\mcI$. The bid profiles of the users are given as,
 $s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
+[s_i^j] \in \mcI \times \mcI$,  
+We have the strategy space for buyer $i$ as all possible bids at all auctions:
+$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \big( \Pi_{k\ne
+i\in\mcI} S_k^j\big)$ as the
+associated opponent profiles. 
+\iffalse
+(HERE)
+Additionally, we assume that a user's budget is 
+sufficient, as the alternative is to pay the overage fee to the ISP, but as we
+assume a rational user.
+\fi
+
+The grid of bid profiles, $s$, represents the state of distributed PSP auction
+mechanism in the secondary market. 
+We emphasize that we allow the grid $s$ to represent the bids of all buyers and
+sellers. In general, we will not reference the full grid. In order to emphasize
+that a bid belongs to a seller, we use the notation $\s_i^j$. We
+will also empasize the \emph{context} of the bid to indicate the user type.
+To further clarify our analysis, we adopt the notational conventions: a
+seller's profile is denoted by $\s^j = [s_i^j]_{i\in\mcI}$, and $s_i =
+[s_i^j]_{j\in\mcI}$ denotes a buyer's profile, where $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
 , s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents.
-Our strategy space is the vector space of all buyer $i$'s \emph{possible} bids,
-$S_i=\Pi_{j\in\mcI} S_i^j$, and $S_{-i} =\Pi_{j\in\mcI} \Pi_{k\ne i\in\mcI} S_i^j$ the
-set of opponent profiles. We assume that the users are connected.
-A buyer submits bids directly to sellers. Users prefer to participate in the CMHK secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. We assume
-that users are selfish, and therefore rational. 
-Thus we assume that all users submit bids in order to maximize their
-(private) valuation functions. 
-In general, user preferences are defined by a utility function, $u$, which 
-represents a users' valuation of an allocation minus the price.
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We assume that data is a unary resource belonging to the seller, and
-therefore we identify each local auction with the identity of the seller
+Furthermore, noting that this is a simplification for ease of notation, we let
+$D^j = \sum_{i\in\mcI} d_i^j$ be the total amount of data $j$ has to sell, and
+$D_i = \sum_{j\in\mcI} d_i^j$ represent the total amount of data desired by buyer $i$.
+
+We assume a public platform, published by the ISP, that allows sellers to advertise their
+auctions, and that buyers may submit bids directly to sellers over the wireless
+network. 
+The ISP is included
+by introducing a mutation of user type, and represent
+the ISP as a blind, deaf user $\kappa$, who does not participate
+in any auctions, but nonetheless holds the power to create a monopoly. At time
+$t=0$, a seller $j$ entering the market will
+submit bid $\s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
+platform, and so the initial bid $\s_\kappa^j$, is public knowledge.
+
+We assume that buyers and sellers are
+separated (a seller does not also buy data and vice versa). 
+In general, we denote a buyer's identity $i \in \mcI$, and a seller as
 $j\in\mcI$.
-We further show that user valuation satisfies the conditions for an
-elastic demand function.
-\iffalse:
-\definition{(Elastic demand) \cite{lazar}}
-A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta(0) = 0$,
-    \item $\theta$ is differentiable,
-    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
-{\theta}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
-\fi
-In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
-Finally, we assume in the CMHK market that a buyers' budget is always
-sufficient, as the alternative is to pay the overage fee to the ISP.
-
-The CMHK market does not allow for brokers \cite{cmhk}, we thereby determine that
-the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation. In other words, we assume that buyers and sellers are
-separated (a seller does not also buy data and vice versa). Thus, we may assume
-that this is implied in our notation.
-A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
-belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
-the bid belongs to a \textbf{seller}.
 Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
 meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
-a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
-auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
-(0,0)$. Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$. Obviously, a buyer that does not submit a bid will not recieve opponent profiles from seller
+a unit price $p^j_i$. 
+Seller $j$'s local auction begins at time $t>0$. The seller takes reponsibility
+to send opponent bid profiles $s_{-i}$ to each buyer that joins the auction,
+those buyers where $s_i^j > 0 \in s$, as well its own bid, $\s_i^j = (d_i^j,
+p_i^j)$, offfering quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$, 
+with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$. 
+Naturally, in a live auction, if a buyer does
+not submit a bid to a seller, then this implies $s_i^j=\s_i^j = 0$. A buyer that does not submit a bid will not recieve opponent profiles from seller
 $j$. We additionally determine that a user who does not submit a bid is holding
-its previous bid, either zero or nonzero. For the purposes of our analysis, we will assume that a zero bid from a
-buyer is equivalent to no bid.
-A seller $j$ submits a bid $s_i^j = (d_i^j, p_i^j)$ to the secondary market,
-with the intent of offering a
-quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
-with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
-stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
-by the user type, whether or not they are  a buyer or a seller. 
-To further clarify our analysis, we will emphasize the separation of buyers and
-sellers using
-$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
-In other words, a bid $s^j =
-[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
-secondary market. The notational conventions of the bid vectors are essentially 
-slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
-[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
-Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
-d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
-d_i^j$ represent the
-total amount of data requested by buyer $i$.
-
-Consider the grid of bid proiles, $s$, representing the distributed PSP auction
-mechanism in the CMHK market, each buyer $i$ will
-have information from each seller $j$, as well as opponent profiles $s_{-i}$
-from each auction in which it is participating, and therefore
-in the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
-$i$ gains access to the full grid $s$. However, 
+to the previous bid, either zero or nonzero. We note that buyers are
+consistently referenced using the index $i$ as a subscript, and sellers using
+the index $j$ as a superscript, as in \cite{semret}.
+
+We will examine the role of buyers, who are able to directly
+influence global market dynamics, and assume that the sellers take a reactionary role.
+Each buyer $i$ will have information from each seller $j$, as well as opponent
+profiles $s_{-i}$, from each auction in which it is participating.
+In the extreme case, where $i$ submits bids to all auctions $j\in\mcI$, buyer
+$i$ gains access all buyer profiles, $[s_1, \cdots, s_I]$. However, 
 sellers can only gain information about the market grid by observing buyer
 behavior in their local auction.
-In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, the buyers are able to directly and globally
-influence global market dynamics, with the sellers taking a secondary role
-(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
+Finally, we define the seller pool for buyer $i\in\mcI$: 
+% MIN SET
+$$
+    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
+n}\sum_{j\in\mcI'} D^j,
+$$
+and similarly, for a seller $j\in\mcI$, we define the set of participating buyers:
+$$
+    \mcI^j(m) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
+m}\sum_{i\in{\mcI}'} p_i^j,
+$$
+where $m, n\in\mcI$.
 
@@
 
-We determine the need for privacy in the data-sharing market. In \cite{zheng},
+We aim to design a distributed PSP auction, operating within a strategic framework that
+determines the bidding behavior of users in a wireless network.
+The auction design must must meet a certain set of known
+criteria: (1) \emph{truthfulness}, (2) \emph{individual rationality/
+selfishness}, (3) \emph{social welfare maximization}, and (4)\emph{the winning
+bid is private}. For the secondary data exchange
+market, we determine that the
+strategy space must meet additional criteria: (5) \emph{privacy and
+independence from the ISP}, (6) \emph{locally fair division}, and (7)
+\emph{minimize crossover in buyer/ seller pools}.
+Thus, we propose a design to replace centralized data exchange
+markets, e.g. 2cm..
+
+There is a clear need for privacy in the secondary data exchange market. In \cite{zheng},
 it is assumed that the ISP interferes in 2cm (market) dynamics, and will maximize the
@@
 
-We aim to design a distributed PSP auction, and a strategic framework that
-determines the bidding behavior of users in a wireless network.
-The auction design must must meet a certain set of known
-criteria: 1) \emph{truthfulness}, 2) \emph{individual rationality/
-selfishness}, 3) \emph{social welfare maximization}. For the secondary data exchange
-market, we determine that the
-strategy space must meet additional criteria: 4) \emph{privacy and
-independence from the ISP}, 5) \emph{locally fair division}, and vg)
-\emph{minimize crossover in buyer/ seller pools}.
-Thus, we propose a strategic framework to replace centralized data exchange
-markets, e.g. 2cm. The framework will act as a host for our distributed PSP
-mechanism, defining the strategy space and directing user correspondance.
-
 We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
@@
 
+\subsubsection{Buyers are anonymous}
+We have that any local auction is anonymous by definition, as a permutation of
+the valuations resutls in a permutation of allocations and prices, equivalently,
+exchanging the bids of two losing buyers does not change the auction's result.
+Formally,
+\definition{(Anonymous auction)} \cite{???}
+Given an auction $j$ and buyers $i\in\mcI$, a protocol for computing
+$\max\lbrace i \in\mcI : p_i^j \ge p_k^j \ \forall \ k\in\mcI\rbrace$ if for
+all coalitions $T\subset \mcI$, any pair of inputs $x = [s_1^j, \cdots,
+s_I^j], \xi$, so that $\xi$ is a permutation of $x$, $\forall \ i \in T : x_i =
+\xi_i$, and $\max( )$, and any choice of random inputs $\lbrace
+r_i\rbrace_{i\in T}$. Let $\bar{T} =   T \times \mcI \setminus T$, 
+$$
+    Pr\big([x, \lbrace r_i\rbrace_{i\in T}]_{x\in}
+    \big\vert
+    \lbrace r_i\rbrace_{i\in T}\big) = Pr\big([\xi, \lbrace r_i\rbrace_{i\in T}]_{\xi\in T
+    \times \mcI \setminus T}\big\vert
+    \lbrace r_i\rbrace_{i\in T}\big)),
+$$
+which states that any two inputs, the messages seen by coalition $T$
+are indentically distributed.
+
+\subsubsection{The winning bid is private.}
+We claim that a buyer's trust in a local auction is fufilled when the outcome of
+the auction is guaranteed to be correct, and if the buyers' identity is secret.
+We define a value to be private if any coalition is incapable of learning any information
+besides what can be inferred from the shared computation and the coalition’s
+inputs \cite{felix}. For each local auction, we define a coalition of the
+participating buyers. The winning bidder is \emph{privately} chosen by
+distributing the computation of the winner to the local coalition.
+
+We follow the process given in \cite{felix}. In general, a distributed private
+computation is as follows: Denoting $m_{-i} = [(s_i^*, r_i), m_1, \cdots, m_n]_{k\ne i\in \mcI}$, buyer sends a
+message to each of its opponents, where $s_i^*$ is $i$'s bid, $r_i$
+is an independent random value, and $m_1, \cdots, m_n$ the messages $i$ has
+received so far.
+Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$.
+
 \subsubsection{Privacy and independence from the ISP.}
- In
-our model, free-market exchange is protected as privacy is integrated into the
-mechanism. Our design enforces privacy by a mutation of user type, where
-the ISP is represented by the blind, deaf user $\kappa$, who does not participate
-in any auctions, but nonetheless holds the power to create a monopoly. At time $t=0$, a seller $j$ entering the market will have
-submitted bid $s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
-platform, and so the initial bid $s_\kappa^j$, is public knowledge. 
-The, the auction
+In our model, free-market exchange is protected as privacy is integrated into the
+mechanism. Our design enforces privacy by a (HERE) The, the auction
 begins at time $t>0$, and at $t=0$, $j$ will,
@@
 \subsubsection{Locally fair division.}
+We claim that the allocation $a$ by seller $j$ for a local auction at
+equilibrium is an equitable division, where each buyer equally values their
+portion of the allocation. We have,
+$$
+    \displaystyle\int_0^{\g_i^j(a)} f_i(z) \ dz = \int_0^{\g_k^j(a)} f_k(z) \ dz,
+$$
+which follows from Proposition \ref{userunion}.
+
+Let $i,k$ be buyers in auction $j$, and let $\vert\mcI^j\vert = 2$. Suppose $j$
+is at equilbrium, i.e. $\g(a)_i^j + \g(a)_k^j = D^j$. From the buyer valuations,
+$\theta_i$ and $\theta_k$ over $[0, D^j]$, we have bid quantities $z_i, z_k$
+representing a $50-50$ division. We follow the surplus procedure \cite{???}.
+Let $z_i < z_k$ and let $z_{ik}$ be the point in $[z_i, z_k]$ such that
+
+we have that $\theta_i(g_i^j(a)) =
+\theta_k(\g_k^j(a)$. Each buyer recieves an allocation based on their valuation.
+
+In the case where a buyer $i\in\mcI^j$ changes strategy such that
+$\theta_i - \theta_k < \epsilon$ for some $k\in\mcI^j$, it follows that
 
 \subsubsection{Minimize crossover in buyer/ seller pools.}
-%A mutation characterized by a new variable cost, absorbed into the bid fee,
-%represents the fact that CMHK users are denied resale and carryover of shared
-%data, effectively creating a form of liability with each transaction. 
-We determine that the set of buyers and sellers participating
+Buyer $i$'s seller pool is determined by minimizing $n$, and is the smallest set of sellers that
+allows for a coordinated bid, and the aggragate bids satisfy its demand, $D_i$.
+\begin{align}
+\begin{split}\label{buyercoordinate}
+    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
+\end{split}
+\end{align}
+Similarly, seller $j$ determines the minimal set of buyers that maximizes revenue and
+sells all of its data, $D^j$.
+\begin{equation}\label{sellercoordinate}
+    \min\bigg\lbrace n \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(n)}d_i^j
+\ge D^j \bigg\rbrace,
+\end{equation} 
+We further determine that the set of buyers and sellers participating
 in a single equilibrium is bounded by the potential indirect costs of
@@
 We define a move to a better market position to be synonymous with a
-strategic bid.
+strategic bid. \\ 
+\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
+from auction design and game theory, respectively.\\
 
@@
 sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
-\circ \g_i$ as the valuation of the buyers. We further model the valuation of the sellers, based on
-(\ref{datademand}) and (\ref{sellerinversedemand}). We first note that, in
+\circ \g_i$ as the valuation of the buyers.
+We further show that user valuation satisfies the conditions for an
+elastic demand function, with valuations based on
+(\ref{datademand}) and (\ref{sellerinversedemand}). 
+\definition{(Elastic demand) \cite{lazar}}
+A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta(0) = 0$,
+    \item $\theta$ is differentiable,
+    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
+     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
+${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
+{\theta}'(\eta)
+- \gamma(z - \eta)$. 
+\end{itemize}
+We first note that, in
 general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
@@
 
-Also define the set,
-% MIN SET
-$$
-    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
-n}\sum_{j\in\mcI'} D^j,
-$$
-where buyer $i$ chooses its seller pool by determining $n$ as,
-\begin{align}
-\begin{split}\label{buyercoordinate}
-    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
-    %\wedge \sum_{j\in\mcI(n)}&\g_i^j(\varrho) \le \sum_{j\in\mcI(n)} \theta_i^j(\g_i^j(a)) \big\rbrace. 
-    %&\wedge \g_i(\varrho) \le \theta_i(\g_i(a)) \big\rbrace. 
-\end{split}
-\end{align} 
-The buyer strategy produces a minimal subset of sellers $\in \mcI$ 
-able to satisfy buyer $i$'s demand while ensuring that the size of $\mcI^j$
-does not allow the overhead to outweigh the valuation of the data. For 
-fixed $n$ we will denote this subset,
-\begin{equation}\label{sellers}
-    \mcI_i \subset \mcI.
-\end{equation}  
 Now let $j^* = n \le I$ represent the seller with the least amount of data
@@
 For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t>0\in\tau$.
-Define the set,
-$$
-    \mcI^j(n) =\argmax_{{\mcI}' \subset \mcI, \vert{\mcI}'\vert =
-n}\sum_{i\in{\mcI}'} p_i^j,
-$$
-where,
-\begin{equation}\label{sellercoordinate}
-    \min\bigg\lbrace n \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(n)}d_i^j
-\ge D^j \bigg\rbrace,
-\end{equation} 
-so that $n$ produces a minimal subset 
-of buyers that maximizes $j$'s revenue at time $t$, which we will
-denote, for fixed $n$, by,
-\begin{equation}\label{buyers}
-    \mcI^j \subset \mcI.
-\end{equation} 
 Define buyer $i^* = n-1 \le I$ as the buyer with the maximum bid price $\ni
@@
 
+%\bibliographystyle{acm}
+%\bibliography{paper.bib}
+
+%\iffalse
 \begin{thebibliography}{9}
@@
 \bibitem{fedbill}
-\textit{No Rate Regulation of Broadband Internet Access Act},H.R. 2666, 114th
+\textit{No Rate Regulation of Broadband Internet Access Act}, H.R. 2666, 114th
 Cong. (2016).
@@
 
+\bibitem{felix}
+Felix Brandt and Tuomas Sandholm.
+\textit{On the Existence of Unconditionally Privacy-Preserving Auction
+Protocols}, ACM Trans. Inf. Sys. Secur. 11, 2, Article 10 (May 2008).
+
 \end{thebibliography}
+%\fi
 

### 2019-09-26 Old/April/paper_alphafair.tex
Work

--- 2019-08-21 April/paper_wc_save3.tex
@@
 \usepackage{multicol}
-\usepackage{url}
 
@@
 
-\section{Abstract}
-
-We investigate the 2cm app, a data-exchange platform published for China Mobile Hong
-Kong 4G Pro Service Plan customers. Telecommunications providers' revenue is typically
-gained by charging users a fixed fee for a maximum amount
-of data usage in a month, i.e., a monthly data cap \cite{???}. 
-2cm's (2nd exchange market) data exchange platform allows users to submit
-bids to buy and sell data.
-This usage model, is, as far as our knowledge, the first data trading
-platform that allows customers to buy and sell their own data.
-We describe a distributed auction mechanism for data exchange inspired by the
-classic PSP throughput problem,
-and prove that our distributed data exchange mechanism provides incentive
-compatibility (social choice function), and that we have efficiency
-using only partial valuation information of each participant in an exchange market.
-
-In applying a distributed PSP implementation to CMHK's secondary market, we
-find that
-the market is able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, and design our mechanism tp provide the functions
-for effective communication between the connected users. We claim that in
-this secondary market our formulation holds the desired VCG qualities through the construction of a
-probable equilibrium \cite{???}. We further provide bounds on the auction duration, 
-with respect to the classic throughput problem.
-and provide simulated results on convergence time to support our (FIND
-COMPETITVE RATIO!), and a bound
-on the convergence of our mechanism. We extend the works of cite!cite!
-i.e. (market influence/EQ,social EQ,payment/allocation models) OR (bandwidth, data bundles, distributed
-market algorithms) and show the existence of a dynamic global market equilibrium, allowing for a unique set of market dynamics.
-
 \section{Introduction}
-
-In this work, we propose \emph{a distributed progressive second price (PSP) auction in
-order to maximize social utility in this secondary market}. Using the
-distributed PSP mechanism on CMHKs data
-exhange platform, we show that for cellular data allocated between multiple users there
-exists an $\epsilon$-Nash market equilibria. A quality of the PSP auction is that
+China Mobile Hong Kong (CMHK) recently introduced such a secondary market.
+CMHK’s 2cm (2nd exchange market) data exchange platform allows users to submit
+bids to buy and sell data, with CMHK acting as a middleman both to match buyers
+and sellers and to ensure that the sellers’ trading revenue and buyers’
+purchased data are reflected on customers’ monthly bills. \cite{zheng}
+
+In this work, we propose a distributed progressive second price (PSP) auction in
+order to maximize social utility in this secondary data-sharing market. We show that for cellular data allocated between multiple users there
+exists an $\epsilon$-Nash market equilibria when all users bid their real marginal
+valuation of the mobile data offered in the secondary market described in
+\cite{zheng}. A quality of the PSP auction is that
 demand information is not known centrally, rather, it is distributed in the
@@
 \emph{local} state: the quantity offered by the seller at that element, and the
-bids for that element only \cite{lazar}. In this work, the proposed mechanism
-allows the distribution of bids, where there are many providers each holding
-thier own local auction; there is no entity that holds a global market knowledge.
-
-In a PSP mechanism, bids consist of (i) an available (required) quantity and (ii) a unit-price (calculated
+bids for that element only. In this work, the proposed mechanism allows sellers submit bids to buyers
+directly; there is no entity that holds a global market knowledge.
+
+We suppose that each seller (resp. buyer) can submit a bid to the secondary
+market consisting of (i) an available (required) quantity and (ii) a unit-price (calculated
 using its own demand functions). Buyers submit bids cyclically until an
-($\epsilon$-Nash) equilibrium is reached and a local auction is concluded.
-
-(FEE IS FIXED OR
-PER-UNIT?)(HOW DO WE MODEL ISP REVENUE? IMMEDIATE FUTURE)
+($\epsilon$-Nash) equilibrium is reached where $\epsilon$ corresponds to a bid
+fee to be paid to the ISP on completion of the transaction. (FEE IS FIXED OR
+PER-UNIT?)(DO WE MODEL ISP PROFIT? FUTURE WORK)
 
@@
 
-\subsubsection{Allocation using PSP}
-
-We begin with a brief introduction to the generalized distributed PSP auction, first introduced by Lazar and Semret \cite{lazar}.
-We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users.
-
-Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
-seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
-pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i−1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents.
-
-Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
-bids $s_{-i}$,
+\subsubsection{Bandwidth Allocation using PSP}
+
+We begin with a brief introduction to the distributed PSP auction for the
+bandwidth allocation problem, first introduced by Lazar and Semret \cite{lazar}.
+The distributed PSP auction from \cite{lazar} forms a part of the
+overall market based allocation model. They consider a noncooperative game
+where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
+amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$.
+
+Suppose each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
+seller of resource $l$,
+where $p_i^l$ is the unit-price the user is willing to pay and $d_i^l$ is the
+quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
+[s_i^l] \in \mcI \times \mcI$ (BAD NOTATION?
+SEEMS OK)  and $s_{−i}^l \equiv [s_1^l , \cdots , s_{i−1}^l , s_{i+1}^l , \cdots
+, s_I^l]_{l\in\mcI}$ is
+the profile of user $i$’s opponents. In addition, the user type now includes a
+\emph{routing variable}, $r_i\in\lbrace 0, 1\rbrace^L$ to manage throughput in
+an arbitrary collection of nodes where $r_i^l >0$ if and only if $l(i)$ is on
+$i$'s path, i.e. $l(i) \in \lbrace l\in \mcI : r_i^l >0\rbrace$. 
+The market now shares $L$ resources, with allocation:
+$$
+    \hat{D_i^l}(y,s_{-i}^l) = \bigg\lbrack D^l -
+\displaystyle\sum_{p_k^l > y, k\ne i} d_k^l\bigg\rbrack^+.
+$$
+The market price function (MPF) of user $i$ is defined as:
+% MARKET PRICE 
+\begin{align*}
+    \tilde{P_i}(z, s_{-i}) &= \displaystyle\sum_{l\in\mcI}P_i^l(z_i^l,
+s_{-i}^l)r_i^l \\
+    = \displaystyle\sum_{l\in\mcI}&\bigg(\inf\bigg\lbrace y\ge 0 :
+\hat{D_i^l}(y,s_{-i}^l)\bigg\rbrace r_i^l\bigg),
+\end{align*}
+which is interpreted as the aggragate minimum price a user bids over its route in order to obtain the
+resource $z$ given the opponents’ profile $s_{−i}$. Its inverse function
+$\tilde{D_i}$ is defined as follows:
+% INVERSE PRICE (ALLOCATION)
+\begin{align*}
+    \tilde{D}_i(y, s_{-i}) &= \sup\bigg\lbrace z\in \bigg( 0,
+\min_l\hat{D}_i^l/r_i^l\bigg) : \\
+    &\tilde{P_i}(z,s_{-i}^l) < y\bigg\rbrace,
+\end{align*}
+which means the maximum available quantity at a bid price of $y$ given
+$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin},
+\cite{qpsp} is defined
+as:
+% ALLOCATION RULE
+\begin{align*}
+    \tilde{a_i}(s) &= \min\big\lbrace d_i^{l(i)}, \\
+ &\frac{d_i^{l(i)}}{\sum_{k:p_k^{l(k)}=p_i^{l(i)}}d_k^{l(k)}} \tilde{D_i}(p_i^{l(i)},
+s_{-i}^l)\big\rbrace,
+\end{align*}
+\begin{align*}
+    \tilde{c_i}(s) &= \displaystyle\sum_{j\ne i}\bigg\lbrack\sum_{l\in\mcI}
+p_j^{l(j)} \bigg(\tilde{a_j}(0; s_{-i}^l)\\
+    &-\tilde{a_j}(s_i^l;s_{-i}^l)\bigg) r_i^l\bigg\rbrack,
+\end{align*}
+ $a_i^{l(i)}$ denotes the quantity user $i$ obtains by a bid price
+$p_i^{l(i)}$ (when the
+opponents bid $s_{−i}^l$) and the charge to user $i$ by the seller is denoted
+$c_i^{l(i)}$. $\sum_{l\in\mcI} c_i^{l(i)}$ is interpreted to be the total cost incurred in the system if
+user $i$ is removed from the auction. Note that the allocation rule is modified
+from \cite{lazar} according to \cite{tuffin}, so that buyers with identical unit-price
+$p_i$ are not rejected.
+%%%%%%%%%%%%
+\iffalse
+An allocation rule is feasible \cite{lazar} if $\forall \ s$,
+$$
+    \displaystyle\sum_{i\in\mcI} a_i(s) \le Q
+$$
+and $\forall \ i\in\mcI$,
+\begin{align*}
+    a_i(s) &\le d_i \\
+    c_i(s) &\le p_id_i.
+\end{align*}
+\fi
+%%%%%%%%%%%%%%%%%%
+
+Using this classic PSP mechanism, \cite{lazar} shows that given the opponents bids $s_{-i}$,
 user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
+(where $s_i$ is chosen to maximize $i$'s utility with $s_{-i}$ held constant), is
+given by:
+\begin{align}
+\begin{split}
+    v_i &= \sup\bigg\lbrace d \ge 0 : \theta '(d) > P_i(d), \\ 
+&\displaystyle\int_0^d P_i(\eta) \ d\eta \le b_i\bigg\rbrace -
+\frac{\epsilon}{\theta_i'(0)} \\
+&\qquad\qquad \text{(best quantity reply)} \\
+\end{split}\\
+    w_i &= \theta_i'(v_i) \quad \text{(best unit-price reply)},
+\end{align}
 where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
@@
 
-Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, there exists
-an allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to
-each user $i\in\mcI$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
-allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
-
-We intend to show that our auction
+\subsubsection{Data Allocation using PSP}
+
+The main contribution of this work is to show that the rules of PSP auctions are applicable to the
+secondary market described in \cite{zheng}. We find that the auction of data effects the
+strategies of the users (buyers and sellers) and results in a (somewhat) different
+auction from the original bandwidth problem. We intend to show that our auction
 is rational and achieves the desired VCG properties, as does the original
 formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
-realistic, theoretic, and notational templates, we define optimal strategies for
-CMHK users, and demonstrate that the development of a set PSP auction mechanisms
-in a data exchange setting is able achieve a network equilibrium for cellular data.
-
+both a theoretic and notational template (BAD SENTENCE), we define optimal strategies for
+buyers and sellers which allows for the development of a PSP auction mechanism
+to achieve a network equilibrium for cellular data. (EXPAND)
+
+We will introduce a user type called an \emph{opt-out buyer} in order to perform our analysis. The
+opt-out buyer restricts its pool of sellers by only submitting bids to sellers
+who are able to meet their requirements.
 We intend to show that our PSP constraints are
@@
 principle}, and is a valid progressive second price auction to the extent that buyer $i$
-pays for its allocation so as to exactly cover the ``social opportunity cost"
-which is given by the declared willingness to pay (bids) of the users who are
-excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
+pays for its allocation so as to exactly cover the ``social opportunity cost" which is given by the declared willingness to pay (bids) of the users who are excluded by $i$'s
+presence, and thus also compensates the seller for the maximum lost potential
 revenue \cite{lazar}.
 
-We will introduce a user type called an \emph{opt-out buyer} in order to perform our analysis. The
-opt-out buyer restricts its pool of sellers. We extend the P2P rules described
-in \cite{semret} to account for a set of \emph{local} data-exchange markets.
-Our reserve price function is determined by the subset of nodes participating in the
+We extend the P2P rules described in \cite{semret} to include a \emph{local} market
+price function as determined by the subset of nodes participating in the
 auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
@@
 dynamically influenced by the market via the $\epsilon$-best replies from the
-buyers. We demonstrate that as the valuation function of seller $j$ is dependent
-on the buyers demand, that the strategies of buyers and sellers may differ
-drastically depending on the market.
+buyers: the
+valuation function of seller $j$ is dependent on the buyers demand, and is
+modeled as a function of their potential revenue \cite{semret}.
+
+%%%%%%%%%%%%%%%%%%%
+\iffalse 
+We use the $\alpha$-fair utility functions \cite{zheng} to model the
+valuation from consuming $d$ amount of data:
+% BUYER VALUATION
+\begin{equation}\label{buyervaluation}
+    \theta(d) = \frac{\sigma d^{1-\alpha}}{1-\alpha}
+\end{equation}
+(AUGH! NEED X TO BE SO BIG COMPARED TO ALPHA! can we assume a minimum ask?)
+where $\sigma$ is a positive constant representing (the scale) of the usage
+utility and we take $\alpha \in [0, 1)$.
+We verify that the user valuation above satisfies the conditions for an
+\emph{elastic demand function}: (NOTE: this part seems in the wrong place)
+
+\definition{\cite{lazar}}
+A real valued function $\theta(\cdot)$ is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta(0) = 0$; \\
+        \emph{Verification:} (obvious)
+    \item $\theta$ is differentiable; \\
+        \emph{Verification:} The derivative, $\sigma d^{-\alpha}$, is positive assuming non-negative
+data requirements.
+    \item $\theta ' \ge 0$, and $\theta '$ is non-increasing and continuous; \\
+        \emph{Verification:} $U$ is differentiable for all $d$, and therefore
+continuous. Its derivative is a negative exponential, and so is non-increasing.
+    \item There exists $\gamma > 0$, such that for all $z \in [0,D]$, $\theta
+'(z) > 0$ implies that for all $\eta \in [0, z), \theta '(z) \le \theta '(\eta)
+- \gamma(z - \eta)$. \\
+        \emph{Verification:} Without loss of generality, we may set the scaling
+constant $\sigma=1$, and compute the curvature $\gamma(\xi)$, where by definition,
+$$
+    \gamma = \frac{\theta''}{(1+\theta')^{3/2}} = \frac{-\alpha
+\xi^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}.
+$$
+Using a Taylor theorem approximation,
+\begin{align*}
+    z^{-\alpha} &\le \eta^{-\alpha} + \frac{-\alpha
+d^{-\alpha-1}}{(1+\xi^{-2\alpha)^{3/2}}}(z-\eta) \\
+    & \le \eta^{-\alpha} +
+\frac{\alpha}{2\sqrt{2} \xi}(z-\eta)  \\
+    &\le \eta^{-\alpha} +
+\frac{\alpha}{\xi}(z-\eta).
+\end{align*}
+Now, using Taylor repeatedly, simplifying and taking the limit as $\eta \rightarrow z$,
+\begin{align*}
+    z^{-\alpha} - \eta^{-\alpha} &\le -\alpha\eta^{-\alpha-1}(z-\eta) \\
+    & \le \frac{-\alpha}{\xi}(z-\eta).
+\end{align*}
+And so, since $\xi \le \eta^{\alpha+1}$,
+we may set
+$$
+    \gamma \ge
+\frac{-\alpha\eta^{-(\alpha+1)^2}}{\big(1+(\eta^{-2\alpha(\alpha+1)})^{3/2}},
+$$
+which holds in the case that $z > 1$, and so assuming that there must be at least one
+unit of data required for a user to have
+a valuation,  we have that the concavity of $\theta'$ is shown by Squeeze theorem.
+\end{itemize}
+\fi
+%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-We define the set of users, $\mcI = \lbrace 1, \cdots, I\rbrace$, who purchase or sell
-data from other users. A buyer submits bids directly to sellers, where we
-assume that all users submit bids in order to maximize their
-(private) valuation functions.
-
-(TERRIBLE, FUTURE WORK) public information in the
+We consider the set of $\mcI = \lbrace 1, \cdots, I\rbrace$ users who purchase or sell
+data from other users. A buyer submits bids directly to sellers who enough leftover data
+to satisfy their demand, and will submit bids in order to maximize their
+(private) valuation. We assume (SUPPOSE?) that the public information in the
 secondary market consists of a set of offers that are published by users
 wishing to sell their data overage. 
-
 A user's identity $i \in \mcI$ as a subscript indicates that the user
@@
 the user has the exact amout of data they require, or that seller $j$ does not have
-enough data to satisfy the buyers demand, and we simply set $s_i^j = (0, 0)$.
+enough data to satisfy the buyers' demand, and we simply set $s_i^j = (0, 0)$.
 A seller $j$ places an ask $s^j = (d^j, p^j)$, meaning $j$ is offering a
@@
 
+Based on the profile of bids $s^j = (s^j_1, \cdots s^j_I)$, seller $j$ computes
+an allocation $(a^j, c^j) = A^j(s^j)$, where $a^j_i$ is the quantity given to
+user $i$ and $c^j_i$ is the total cost charged to user $i$. $A^j$ is the
+allocation rule of seller $j$. It is feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.
+
 \section{Distributed PSP Analysis}
-
 \subsection{User Behavior}
 
-We assume that users are selfish, and therefore
-rational. Users prefer to participate in the secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
-User preferences are defined by a utility function, for any $i\in\mcI$,
-\begin{align*}
-    u_i : &S \rightarrow (-\infty, \infty) \\
-          &s \rightarrow u_i(s).
-\end{align*}
-(TOO GENERAL?)
-
 \subsubsection{Buyer Strategy}
-
 Absent the cost or revenue from trading data, CMHK users gain utility from consuming
@@
 \definition{\cite{lazar}}
-A real valued function, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
+A real valued function for buyer $i$, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
+function} on $[0, b_i]$ if 
 \begin{itemize}
@@
      \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta_i}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le
-{\theta_i}'(\eta)
+${\theta_i}
+'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le {\theta_i}'(\eta)
 - \gamma(z - \eta)$. 
 \end{itemize}
-
 % OPT-OUT BUYER
@@
 function,
-\begin{equation}\label{buyerutility}
+\begin{equation}\label{opt-utility}
     u_i = \theta_i \circ e_i(a) - c_i,
@@
 a function that maps buyer $i$'s data quantity (requirement) to matching
-seller(s). We note that the opt-out buyers valuation depends only on a scalar $e_i(a)$ which is a function of the
+seller(s). We note that the opt-out buyers' valuation depends only on a scalar $e_i(a)$ which is a function of the
 quantities of all the available data for sale in the secondary market.
@@
 user $i$ joins the auction is $b^j$. 
-A sellers' allocation cannot exceed the total amount they have available,
+The data transfer from each seller cannot exceed the total amount they have available,
 i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
@@
 Note that with our formulation, if a seller $j$ does not meet a buyer $i$'s data requirements, a
-rational (utility-maximizing) buyer will set $s_i^j = 0$. The seller, in our analysis, is a functional
-extension of the buyer, with valuation $\theta^j$ constructed by buyer demand.
-We assume that buyers and sellers are separated (a seller does not also buy
-data and vice versa).
+rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
+place a bid, as in \cite{zheng}. The seller, in our analysis, is a functional
+extension of the buyer, its valuation $\theta^j$ is dependent on the buyers. We will assume that buyers and sellers
+are separated (a seller does not also buy data and vice versa).
 
 Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
-is also reasonable to expect that a seller may come close to using their
+is also reasonable to expect that many sellers will come close to using their
 entire data cap, and only sell the fractional overage. In this case, we
-determine that a buyer must coordinate their bids among multiple sellers. 
-Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-moderated by the function $e$ which maps its data requirement to the distributed market. 
-We propose the following strategy,
+determine that a buyer must coordinate their bids among multiple sellers. (SAY
+MORE?) Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
+moderated
+by a function of quantities desired from the distributed market. 
+We define, in addition to the valuation $\theta_i$ and budget $b_i$, a generic
+\textbf{data-provisioning vector} $\vs_i$, held by buyer $i$ as part of its type. We propose the
+following strategy,
 {
 \proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
-Let $i\in\mcI$ be a buyer and define any auction duration
-to be $\tau \in [0,\infty)$, and fix all other buyers' bids $s_{-i}$. 
-For any allocation $a$, let
+Define, for any allocation $a$,
 % OPT-OUT BUYER STRATEGY
 \begin{equation}\label{opt-out}
-    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
-    e_i^j(a) \triangleq a_i^j,
+    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} + a_j^i,
+    e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j},
 \end{equation}
@@
 \begin{equation}\label{buyercoordinate}
-    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
-    n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
-\ge d_i\rbrace,
-\end{equation} 
-which produces a minimal subset 
+    n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i} = d_i\rbrace,
+\end{equation} 
+which produces the minimal subset 
 \begin{equation}\label{sellers}
-    \mcI_i = \lbrace j \in \mcI : j \le n\rbrace \subset \mcI.
-\end{equation} 
-Now let $j^* = n \le I$, and define, 
-\begin{equation}\label{opt-minallocation}
+    \mcI_i = \lbrace j \in \mcI : j < n\rbrace \subset \mcI.
+\end{equation} 
+Now let $j^* = n < I$, and define, 
+\begin{equation}\label{opt-quantity}
     e_i(a) \triangleq e_i^{j^*}(a).
 \end{equation}
-we address the following special cases:\\
-(Budget limited allocation)
-\begin{equation}\label{partialallocation}
-    d_i^j > b^j - \sum_{k\in\mcI^j, k\ne i} d_k^j.
-\end{equation}
-(Equal price allocation)
-There exists $k,i \in \mcI^j, k\ne i$, such that
-\begin{equation}\label{equalprice}
-    \quad p_i^j = p_k^j.
-\end{equation}
-(Price-dominant allocation)
-There exists $k \ni \mcI^j$, where $\forall \ i\ne k \in \mcI^j$.
-\begin{equation}\label{newbuyer}
-    p_k^j < p_i^j, 
-    %p_i^j < p_k^j \quad \text{and} \quad d_i^j >= b^j, \quad \forall \ k \in \mcI^j.
-\end{equation}
-(Empty allocation)
-\begin{equation}\label{emptyset}
-    n > \vert \mcI\vert \Rightarrow \ell^j = \emptyset.
-\end{equation}
-In any of the above cases, seller $j$'s local auction strategy does not change and
-Proposition \ref{sellerstrategy} holds.
 Then, we have that $e_i$
@@
 $j^*$ by computing $\ell_i$. In the case that $d_i >
-\sum_{j\in\mcI}d^j$, then $j^* > I$, we reason that this case is unlikely; our formulation reduces to a
-monopoly, and the user pays the overage fee for data set by the provider which the upper bound of the sellers'
-pricing function, where we consider the provider (AT\&T) as a seller. We also note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the
-minimal ordered subset where a
-coordinated bid is possible, which we will address in further analysis in Section \ref{analysis}.
-Suppose there exists buyer $k\in \mcI^j$, such that
-$e_k^j(a) \ge e_i^j(a)
-\rightarrow p_k^j > p_i^{j}$ and so $d^j - d_k^j < z_i^{j*}$, resulting in a
-partial allocation. Bid $s_k \in S_i$, and so is considered in buyer $i$'s strategy. 
-As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $e_i(a) = e_i^{j*}(a)
-\ge e_k(a)$. We assume that $i$ will faithfully follow the opt-out strategy, and
-so such a buyer $k$ cannot exist. 
-Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$.
-
-% BUYER LOCAL RESPONSE
-{
-\lemma{(Localized buyer response)}\label{buyerresponse}
-As we cannot
-assume that a buyers' bid will remain fixed at time $(t+1)$,
-}\\
-\textbf{Proof:} 
-The first two cases, (\ref{partialallocation}) and (\ref{equalprice}) deal with
-the problem of a buyer receiving a partial allocation:
-In (\ref{partialallocation}), the winner with the lowest unit price $p_i^j$ results in a partial
-allocation. In this case, using (\ref{buyercoordinate}), buyer $i$ will decrease its
-quantity $d_i^j$ by increasing $n$, and will either remain a winner in $j$'s local
-auction, or drop out of $\mcI^j$. (WILL USE LATER, DEVELOP MORE HERE?)
-(\ref{equalprice}) considers that there may exist multiple buyers with the same unit price. The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
-between all buyers with the same unit price. Therefore, again by
-(\ref{buyercoordinate}), the buyers will increase $n$ until their demand is
-met. 
-The third case considers that a new buyer $k$ may enter the market with a better
-price. There cannot be a buyer where $d_k^j > b^j$, as this violates
-(\ref{budget}) imposed by (\ref{buyercoordinate}). When $d_k^j =
-b^j$, the optimal solution at time $t$ is the single allocation, therefore at
-time $(t+1)$, we have $\mcI^j = k$. It follows that in the case $d_k^j < b^j$, buyers $i\in\mcI^j$ will
-lose their position in $\ell^j$ as the auction progresses and the minimal
-subset $\mcI^j$ is computed. 
-(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
-Lastly, to resolve (\ref{emptyset}), $j$ chooses $n=I$, and sets its reserve price to $p_I^j$.
+\sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
+infeasible (CAN DO BETTER!). 
+We also note that $\mcI_i$ is not the only
+possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, it is the minimal subset where a
+coordinated bid is possible. We will show optimality through the
+analysis in Section \ref{analysis}.
 
 \subsubsection{Buyer Influence}
-To determine a strategy for the sellers, we first perform a general examination
-of seller incentive. The potential revenue for $j$ at unit price $y$ is determined by the
+To determine a strategy for the sellers, we examine seller incentive. The potential revenue for $j$ at unit price $y$ is determined by the
 demand of the buyers. $\forall \ y\ge 0$, we determine that the demand is given by,
@@
     f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace.
+        \rho_i^j(y) \ge z \ \forall \ i \in \mcI\big\rbrace.
 \end{equation}
 For a given demand $\rho^j$, $f^j$ maps a unit of data to the highest price at
-which it \emph{could} be sold to any buyer $i\in \mcI$ (as in \cite{semret}).
+which it \emph{could} be sold to any buyer $i\in \mcI$ (as in \cite{semret}). However, $j$ is restricted by
+the bid strategy of the buyers, as well as some natural constraints, and so we have the following Lemma.
+
+{
+% SELLER CONSTRAINTS
+\lemma{(Seller constraints)}\label{constraints}
+Let $j$ be a seller with budget $b^j$.
+Formalizing the quantity threshold, the seller must satisfy the quantity
+constraint, 
+\begin{equation}\label{quantity}
+    d^j \ge e_i(a)
+\end{equation}
+and
+\begin{equation}\label{budget}
+    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j.
+\end{equation}
+In addition, for a seller who does not sell at a loss, the reserve price must
+satisfy 
+\begin{equation}\label{reserveprice}
+   p^j \ge \min_{i\in\mcI}\big({\theta_i}'(d_i^j)\big).
+\end{equation}
+Finally, we must have,
+\begin{equation}\label{sumallocation}
+    \displaystyle\sum_{k\in \mcI, k\ne i} e_k^j(a) \le a_i^j.
+\end{equation}
+}\\
+\textbf{Proof:}
+The first statement is an assumption, which we may enforce by (\ref{opt-out}),
+and as a seller cannot sell more data than their bid, (\ref{budget}) enforces
+the budget constraint for the seller. (\ref{reserveprice})
+follows from the assumption that $j$ does not sell at a loss, and finally, (\ref{sumallocation})
+follows from Proposition \ref{buyerstrategy}.
+
 % SELLER VALUATION
-We may now define the seller valuation (potential). 
+We may now define the seller $j$'s valuation (potential). 
 {
 \lemma{(Seller valuation)}\label{sellervaluation}
-For any seller $j\in\mcI$, the contribution from buyer $i$'s valuation may be
-modeled as,
+For any $i\in\mcI$, 
 \begin{equation}\label{singlevaluation}
@@
 We assume that a seller will try to maximize profit for any given allocation $a$, and
-as such there is an incentive for $j$ to sell all of its data, and so 
-$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = b^j =
+as such there is an incentive for $j$ to sell all of its data, and so from Lemma
+\ref{sellervaluation},  $\sum_{i\in{\mcI}} d_i^j = 
 \sum_{i\in\mcI} e_i$,
-The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
+The remainder of the proof follows as in \cite{semret}.
 
@@
 paper.
-
-As $j$ is restricted by
-the bid strategy of the buyers, in addition to natural constraints, and we have the following Lemma.
-{
-% SELLER CONSTRAINTS
-\lemma{(Seller constraints)}\label{constraints}
-Let $j$ be a seller with budget $b^j$.
-First, the seller must satisfy the quantity
-constraint, 
-\begin{equation}\label{quantity}
-    d^j \ge e_i(a)
-\end{equation}
-and
-\begin{equation}\label{budget}
-    \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le b^j.
-\end{equation}
-In addition, for a rational seller, the reserve price must
-satisfy 
-\begin{equation}\label{reserveprice}
-   p^j \ge \min_{i\in\mcI}\big({\theta_i}'(d_i^j)\big).
-\end{equation}
-}\\
-\textbf{Proof:}
-The first statement is an assumption, which we may enforce by (\ref{opt-out}),
-and as a seller cannot sell more data than their bid, (\ref{budget}) enforces
-the budget constraint for the seller. (\ref{reserveprice})
-follows from the assumption that $j$ is rational, and so utility-maximization
-acts as revenue maximization; a rational seller will not sell its
-data at a price less than the lowest offer. (ASSUMPTIONS MADE HERE)
 
@@
 ALGORITHMS? LESS OR MORE CONFUSING?)
+
+% BUYER LOCAL RESPONSE
+{
+\lemma{(Buyer response)}\label{buyerresponse}
+Define any auction duration to be $\tau \in [0,\infty)$. 
+Fix any seller $j$, and fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$. Let the
+winner be determined and $s^j$ updated as in the seller strategy. As we cannot
+assume that a buyers' bid will remain fixed at time $(t+1)$,
+we address the following special cases:\\
+(Budget limited allocation)
+\begin{equation}\label{partialallocation}
+    d_i^j > b^j - \sum_{k\in\mcI^j, k\ne i} d_k^j.
+\end{equation}
+(Equal price allocation)
+There exists $k,i \in \mcI^j$ where $k\ne i$, such that
+\begin{equation}\label{equalprice}
+    \quad p_i^j = p_k^j.
+\end{equation}
+(Price-dominant allocation)
+There exists $i \in \mcI^j$, $k \ni \mcI^j$, where
+\begin{equation}\label{newbuyer}
+    p_k^j < p_i^j \qquad \forall \ i \in \mcI^j.
+    %p_i^j < p_k^j \quad \text{and} \quad d_i^j >= b^j, \quad \forall \ k \in \mcI^j.
+\end{equation}
+(Empty allocation)
+\begin{equation}\label{emptyset}
+    n > \vert \mcI\vert \Rightarrow \ell^j = \emptyset.
+\end{equation}
+In any of the above cases, seller $j$'s local auction strategy does not change and
+Proposition \ref{sellerstrategy} holds.
+}
+\textbf{Proof:} \\
+The first two cases, (\ref{partialallocation}) and (\ref{equalprice}) deal with
+the problem of a buyer receiving a partial allocation:
+In (\ref{partialallocation}), the winner with the lowest unit price $p_i^j$ results in a partial
+allocation. In this case, using (\ref{buyercoordinate}), buyer $i$ will decrease its
+quantity $d_i^j$ by increasing $n$, and will either remain a winner in $j$'s local
+auction, or drop out of $\mcI^j$. (WILL USE LATER, DEVELOP MORE HERE?)
+(\ref{equalprice}) considers that there may exist multiple buyers with the same unit price. The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
+between all buyers with the same unit price. Therefore, again by
+(\ref{buyercoordinate}), the buyers will increase $n$ until their demand is
+met. (SHOULD I ALLOW FOR SPECIALIZED SPLIT BIDS FROM THE BUYERS? WILL IT WORK
+WITH COORDINATED BIDS? MORE WORK NEEDED HERE...)\\
+The third case considers that a new buyer $k$ may enter the market with a better
+price. There cannot be a buyer where $d_k^j > b^j$, as this violates
+(\ref{budget}) imposed by (\ref{buyercoordinate}). When $d_k^j =
+b^j$, the optimal solution at time $t$ is the single allocation, therefore at
+time $(t+1)$, we have $\mcI^j = k$. It follows that in the case $d_k^j < b^j$, buyers $i\in\mcI^j$ will
+lose their position in $\ell^j$ as the auction progresses and the minimal
+subset $\mcI^j$ is computed. 
+(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
+Lastly, to resolve (\ref{emptyset}), $j$ chooses $n=I$, and sets its reserve price to $p_I^j$.
+
 We now define the local auction, which we describe, when coupled with the buyer
@@
 information (SAY MORE?).
-
 % SELLER LOCAL STRATEGY
@@
 \end{equation} 
-which gives $j$ a minimal subset 
+which gives $j$ the minimal subset 
 \begin{equation}\label{buyers}
@@
 equilibrium. Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
+$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and that the local
 equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
@@
 
-We conclude this section by reasoning that the user behavior restrictions are
-necessary to formally define (and restrain) the incentives of the users. (OWN
-WORDS) Since the sellers are driven by the buyers' demands, and the buyers are
-competing in multiple local auctions hosted by the sellers, the two games are
-inter-dependent, and may be played on the same or on a different scale in
-valuation, time (AND....). PSP relies on the \emph{relevation prinicple}; the
-PSP mechanism is able to demonstrate equlibrium by showing that PSP is
-incentive-compatible. (MORE?)
-Arrow's paradox is an impossibility theorem stating that when voters have three
-or more distinct alternatives (options), no ranked voting electoral system can
-convert the ranked preferences of individuals into a community-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives.
-
-Thus, (WHAT? FINISH, OWN WORDS)
-The designer of a mechanism generally hopes either to design a mechanism
-y() that "implements" a social choice function to find the
-mechanism y() that maximizes some value criterion (e.g. profit)
-Independence of irrelevant alternatives (IIA)
-The IIA condition has three purposes (or effects)
-
-Normative
-Irrelevant alternatives should not matter.
-Practical
-Use of minimal information.
-Strategic
-Providing the right incentives for the truthful revelation of individual
-preferences.
-
 % MECHANISM
@@
 We may now proceed to formally define the PSP auction as a composition of the
-buyers and sellers in the secondary market. We will denote the data-PSP rules
-by including an overbar, in order to emphasize that they have been changed from
-the original forms \cite{lazar}.
+buyers and sellers in the secondary market. 
 The market price function (MPF) for a buyer in the secondary market
@@
     &= \sum_{j\in\mcI_i}\bigg(\inf\bigg\lbrace y\ge 0 : 
-    {\bar{D}_i^j}(y,s_{-i}^j) \ge z\bigg\rbrace \bigg),\\
+    {\bar{D}_i^j}(y,s_{-i}^j)\bigg\rbrace \bigg),\\
 \end{split}
 \end{align}
-and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
-order to obtain
-data amount $z$ given an opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the \emph{individual} prices of the buyers as it is
-possible that $\mcI_i \ne \mcI^j$, and so the reserve prices of the individual sellers
-may vary. 
-%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
-%buyer $i$'s bid quantity. 
-The maximum available quantity of data from seller
-$j$ at price $y$ given $s_{-i}$ is: 
+where
 % NEW ALLOCATION RULE
@@
     \bar{D}_i^j(y,s_{-i}^j) &= D_i^j(y,s_{-i}^j)\ \circ\ e_i\\
-    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
+    &= \bigg\lbrack d^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+/\vs_i^j,
 \end{split}
 \end{align}
-and we have the inverse price function as an aggragate over all local auctions
-$j\in \mcI_i$,
+and is interpreted as the aggragate of minimum bid prices of buyer $i$ for bids
+over $\mcI_i$ given an opponent profile $s_{-i}$. In this expression, we note that
+the price is an aggragation of the \emph{individual} prices of the buyers as it is
+possible that $\mcI_i \ne \mcI^j$, and so the reserve prices of the individual sellers
+may vary. 
+The inverse function
 % NEW INVERSE DEMAND
+$\bar{D}_i$ is defined as
 \begin{align}\label{datapriceinverse}
@@
 \end{align}
+We may interpret $\bar{D}_i(y, s_i)$ as the maximum quantity provided by the subset
+$\mcI_i$ at a bid price of $y$ given $s_{-i}$. 
 % DATA ALLOCATION RULE
-The data allocation rule is given as in \cite{semret}, however with the
-influence of the opt-out buyer strategy, the resulting allocation is a function of the total amount of data
-required by buyer $i$ composed with its opt-out value and the allocation relies
-on the incentives of the seller, so that $\forall \ i \in \mcI^j$,
-% and so for profile $s_i$, for any $i \in \mcI$,
+The data allocation rule is given as,
 \begin{align}\label{dataallocation}
@@
     \bar{a}_i(s) &= a_i(s) \circ e_i =
-\displaystyle\sum_{j\in\mcI_i}\bigg(\min\bigg\lbrace d_i^j,
+\displaystyle\sum_{j\in\mcI_i}\bigg(\min\bigg\lbrace d_i^j/\vs_i^j,
 \\
@@
 p_i^j}d_k^j}
-\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace\bigg).
+\bar{D}_i^j(p_i^j,s_{-i}^j)\bigg\rbrace\bigg)
 \end{split}
 \end{align}
-Finally, we must have that the cost to the buyer adheres to the second price rule for each local auction:
+with cost to the buyer,
 % DATA COST
@@
 
-The main contribution of this work 
-is an auction mechanism inspired by the classic PSP throughput problem. In
-order to apply a distributed PSP implementation to CMHK's secondary market,
-we utilize our opt-out buyer and seller strategies in order to analize the
-behavior of the resulting dynamical market. As both buyers and sellers are able
-to change their bid strategies, and as each user only has \emph{local}
-information about the bidding environment, it is clear that an unconstrained
-market, even with a finite number of users, could suffer from the communication
-expense from numerous local auctions trading an infinitely divisible resource.
-We will assume that the cost of participatingn in the CMHK secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. We perform a simple survey of these bid fee models, we
-provide some idea of the expected revenue of the mobile data provider (NEED
-STATS!). It is worth mentioning that CMHK users are not allowed to resell data purchased from the secondary
-market, additionally, the purchased data expires (does not carry to the next
-service period). Therefore, a simple definition of market equilibrium, where
-supply equals demand, is insufficent to complete a comprehensive analysis of
-the CMHK data-exchange market behavior. We will make an attempt to address why
-our formulation at least partially considers some of these issues (BAD), such
-as the impact of the bid fee on user behavior. (MOVE SOME OF THIS UP)
-Finally, we  .... (WHAT? COMPLETE THE THOUGHT)
-
-We claim that the market is
-able to achieve an equilibrium as the sellers and buyers have an
-incentive for a collaborative exchange, our mechanism provides the functions
-for the effective communication between the connected users. It was shown in
-\cite{lazar} that a $2$-dimensional message space is sufficient for the PSP
-auction. Using a restricted message space is essential for the distributed
-nature of our design (EXPLAIN), however, as a given message can come from many
-possible types, there is no single
-way to do the transformation from the direct revelation mechanism to the
-desired one. This is equivalent to guessing the
-right direct-revelation-to-desired-mechanism transformation and building it
-into the allocation rule from the start. (FINISH!)
-We claim that in
-this secondary market our formulation not only holds the desired VCG qualities,
-but minimizes comminication overhead (and so possibly fees paid to the provider)
-and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
+The main contribution of this work is comprised by the modified PSP rules
+along with the user strategies, which we use to
+describe an auction mechanism inspired by the classic PSP throughput problem. In order to apply PSP to the data-sharing secondary market described in
+\cite{zheng} the idea of a ``route" is repurposed, and by the use of the
+opt-out buyer, we are abel to achieve a market equilibrium. We claim that in
+the secondary market our
+formulation not only holds the desired VCG qualities, but minimizes the message
+space and auction duration, resulting in a convergence time (FIND COMPETITVE RATIO?)
 with respect to the classic throughput problem.
 
-\subsection{PSP Formulation}
+\subsection{VCG Formulation}
 Consider a user seeking to prevent
@@
 satisfy $i$'s demand, then
-(\ref{buyerutility}) reduces to the original form, defined in
+(\ref{opt-utility}) reduces to the original form, defined in
 \cite{semret} as ``a simple buyer at a single resource element".
@@
 algorithm makes use of the fact that the sellers' valuation is determined by
-the buyers' market and upholds the PSP mechanism. (CHECK) (ALSO $j$ NEEDS TO
-UPDATE FOR NEW BUYERS, $j$'S CONTROL)
+the buyers' market and upholds the PSP mechanism. (CHECK)
 
@@
 % VCG ANALYSIS
-\section{PSP Analysis}\label{analysis}
+\section{VCG Analysis}\label{analysis}
 \subsection{Equilibrium}
 
-Consider an opt-out buyer $i\in\mcI$. A PSP auction
-allows for a buyer to react to opponents bids, and so its incentive is based on
-the opponent profile.
-
-Due to (\ref{buyerutility}), $i$ only has an incentive to change its bid
-quantity if it increases its opt-out value $e_i$, and therefore its utility. 
-We will show that $i$ can coordinate its
-bids over $\mcI_i$ so that the opt-out value $e_i$ is the same for each
-$j \in\mcI_i$, and therefore, without loss of utility, $i$ may choose a seller pool 
-using a ``consistent" strategy, where for any $j\in \mcI_i$, $d_i^j = d_i^k, \
-\forall \ k \in \mcI_i$, and still have feasible best replies. 
-Our result shows that a buyer may select $\mcI_i$ in order to maximize its
-utility while maintaining a coordinated bid strategy. 
-It is intuitive that, if $j^*
-< I$, a buyer may increase the size of $\mcI_i$, thereby lowering its bid
-quantity while obtaining the same (potential) allocation $a_i$. 
-(OWN WORDS!)
-One important question to ask is why a bidder should bid with identical unit
-prices on (j) all auctions and not reduce the unit price to a level where he still wins the
-amount q i . The reason for this can be found in the pricing rule of the PSP auction. Since a
-player is only charged with the cost of excluding other players from the market, the
-unit price does not influence the final charges. Since this unit price reflects the
-valuation of the total resources gained from the multi-auction market a player uses this price on all
-auctions
+Consider an opt-out buyer $i\in\mcI$. 
+(I THINK WE NEED PRICE TO COME IN SOON... MODIFIED ALLOCATION RULE!)
+Due to (\ref{opt-utility}), $i$ only has an incentive to change its bid
+quantity if it increases its opt-out value $e_i$. 
+We show that, without loss of utility, $i$ can coordinate its
+bid quantities $d_i$ to the level where the opt-out value $e_i$ 
+ is the same for each qualifying seller $j \in\mcI_i$. We argue
+that without loss of utility, $i$ may choose a seller pool where a minimal subset
+of sellers guaranteed (CHECK) to satisfy demand where $i$ is able to play a
+``consistent" strategy and still have feasible best replies, and buyer
+coordination holds in the secondary data market under our assumptions.
 
@@
 \lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
-Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
+Let $i\in\mcI$ be a opt-out buyer.
 For any profile $s_i = (d_i, p_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be the resulting data
-allocation. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
-(z_i,p_i)$, where $\forall \ j \in \mcI_i$,
-$$
-    z_i^j = e_i(a),
-$$
-and,
+tranfer. For a fixed $s_{-i}$, a better reply for $i$ is $x_i =
+(z_i,p_i)$, where $\mcI_i$ is computed as in the buyer strategy,
+$$
+    z_i^j = e_i(a)
+$$
+and
 \begin{equation}\label{coordination}
@@
 \end{equation}
-where $i$'s strategy is as in Proposition \ref{buyerstrategy}.
 }\\
@@
 As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
-u_i(s_i;s_{-i})$. In full notation, we intend to show
-$$
-    u_i((d_i,p_i);s) \le u_i((z_i,p_i);s_{-i}).
+u_i(s_i;s_{-i})$. 
+We have, by (\ref{opt-out}) and (\ref{datacomposed}), $\forall \ j\in\mcI_i$,
+\begin{align*}
+    z_i^{j^*} &= z_i^j = e_i(a) = e_i^{j^*}(a) \\
+    &\le \bigg\lbrack d^{j^*} - \sum_{p_k^j> y}
+d_k^{j^*}\bigg\rbrack^+/\vs_i^{j^*},
+\end{align*}
+and so
+$$
+     a_i^j(z_i,p_i) = a_i^{j^*}(z_i,p_i) = z_i^{j^*}= e_i(a).
+$$
+In order to determine that $i$ has no loss of utility, we will show that
+$$
+    u_i(d_i,p_i) \le u_i(z_i,p_i).
 $$
@@
 1. \emph{There exists a seller who can fully satisfy $i$'s demand.} \\
-In this case, $\vert\mcI_i\vert = 1$, and is trivial as no
-coordination is necessary for a single bid. (SPECIAL CASE OF MONOPOLY? THINK!)\\
-2. \emph{Buyer $i$'s demand can only be satisfied by purchasing data from multiple sellers.} \\
-We will show that $i$ may increase $\vert\mcI_i\vert$, without decreasing $u_i$, so that
+In this case, $\vert\mcI_i\vert = 1$, and the case is trivial as no
+coordination is necessary for a single bid.\\
+2. \emph{Buyer $i$'s demand can only be satisfied by a minimal subset of sellers.} \\
+Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
+largest bid are considered first, the seller $j^*$ defines the minimal subset $\mcI_i$ where a
 coordinated bid is possible. 
-Buyer $i$ maintains ordered set $\ell_i$ where the sellers with the
-largest bid quantities are considered first; the index of seller $j^*$ defines
-a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity offered by any $j\in \mcI_i$,
-so $d_i^{j^*} \le d_i^j, \ \forall \ j \in \mcI_i$ and also defines the
-maximum quantity bid of any $k \ni \mcI_i$.
-Thus by (\ref{opt-out}) and (\ref{opt-minallocation}), $\forall \ j\in \mcI_i$,
-$$
-    z_i^j = e_i(a) = e_i^{j^*}(a)  \le e_i^{j}(a),
-$$
-and for any $j\in\mcI_i$, we have $\forall \ l \ni \mcI_i$,
-\begin{equation}\label{minimaleq}
-e_i^{l}(a) 
-     \le \bigg\lbrack d^{j} - \sum_{p_k^{l}> p_{i^*}^{j}} d_k^{l}\bigg\rbrack^+,
-\end{equation}
-where $p_{i^*}^j$ is the reserve price of the seller, defined in Proposision
-\ref{sellerstrategy}, and is by definition the minimum price allowing any
-allocations to be made by seller $j$. Now, as any $l \ni \mcI_i$ ... for any
-$j\in\mcI_i$
-(LOOK FOR $i^* = j^*$?)
-
-1. buyers have same d but diff p
-2. " same p but diff d i.e. d1 < d2
-
-The inequality follows from
-(\ref{dataallocation}) and that $P_i^j$ is non-decreasing, so $p_i^j \le p_i^{j^*} \ \forall \ j \ni \mcI_i$.
-Now, by (\ref{dataallocation}),
-\begin{align*}
-     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j{^*}, \bigg\lbrack d^{j} - \sum_{p_k^{j}> p_i^{j^*}}
-d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j^*}= e_i(a)
-\end{align*}
-by definition, and (\ref{minimaleq}) is proven.
-%we have that buyers will submit equal bids to a minimum subset of sellers $\mcI_i$.
-We proceed to demonstrate that $x_i$ does not result in a loss of utility for
-buyer $i$; we will show that
-$$
-    u_i \le u_i(z_i,p_i).
-$$
-From (\ref{minimaleq}), we have $a_i^{j}(z_i,p_i) = z_i^{j^*} = e_i(a(z_i,p_i))$, which
+From (\ref{dataallocation}) and (\ref{coordination}), we have that, $\forall \ j\in \mcI_i$,
+\begin{align*}
+    e_i^j(z_i,p_i) &= \bigg\lbrack d^j - \sum_{p_k^j> y}
+d_k^j\bigg\rbrack^+/\vs_i^j 
+\end{align*}
+We have $e_i^j(a(z_i,p_i)) = a_i^{j^*}(z_i,p_i)/\vs_i^{j^*} = e_i(a)$, which
 implies that 
@@
 Therefore, by the definition of utility (\ref{buyerutility}),
-and the sellers' valuation (\ref{singlevaluation}), 
-\begin{align*}
-    &\theta_i\circ e_i(a(z_i,p_i)) - \theta_i(a)) \\
-    &= u_i(z_i,p_i) - u_i =  c_i^j -c_i^{j^*}(z_i,p_i)\\
-    &= \displaystyle\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d^j - z) \ dz.
-\end{align*}
-Then, noting that $\theta_i\ge 0$, $\forall \ j\in\mcI_i$, $a_i(z_i,p_i) \le
-z_i^j \le a_i^j \Rightarrow u_i(z_i,p_i) - u_i \ge 0$.
-
-Finally, since (\ref{opt-out}) does
-not increase the demand of seller $i$, $\sum_j c_i^j(s) \le b_i$, and so $x_i$ is feasible.
-
+\begin{align*}
+    \theta_i\circ& e_i(a(z_i,p_i)) - \theta_i(a)) \\
+    &=  c_i^j(s) -c_i^{j^*}(z_i,p_i).
+\end{align*}
+Now using the definition of
+the buyers' valuation (\ref{buyervaluation}), we have $\forall \ i \in\mcI$,
+\begin{align*}
+    u_i(z_i,p_i) &- u_i \\
+    &=\displaystyle\sum_{\mcI_j}\bigg(\theta_i(a_i^j)-
+\theta_i(a_i^{j^*}(z_i,p_i))\bigg) 
+\end{align*}
+Now, from (\ref{dataallocation}), $\forall \ j\in\mcI_i$, $a_i(z_i,p_i) \le
+z_i^j \le a_i^j$ and $\theta_i\ge 0 \Rightarrow u_i(z_i,p_i) - u_i \ge 0,
+\ \forall \ i\in \mcI$, as is shown by the definition of the buyers' utility,
+(CAN USE THIS! VERY STRONG)
+$$
+     \sum_{\mcI_j}\bigg(\frac{\sigma (a_i^j)^{1-\alpha}}{1-\alpha}
+-\frac{\sigma (a_i^j(z_i,p_i))^{1-\alpha}}{1-\alpha}\bigg)
+     \ge 0.
+$$
+
+Additionally, since (\ref{opt-out}) does
+not increase the demand of seller $i$, $\sum_j c_i^j(s) \le b_i$, i.e. $x_i$ is feasible.
 In effect, we are using the buyer demand
@@
 gives $\bar{D}_i(0,s_{-i}) =0$. 
-By the assumptions made in the definition of $i$'s valuation function $\theta_i$,
-$$
-w_i = {\theta_i}'(v_i) > {\theta_i}'(z_i) = y_i,
-$$
-and as $D_i^j$ is non-decreasing, $D_i^j(y_i,s_{-i}) \ge z_i \ge v_i$.
+By choice of $i$'s valuation function $\theta$,
+$$
+w_i = {\theta_i}'(v_i) =\sigma v_i^{-\alpha} >  \sigma
+z_i^{-\alpha} = {\theta_i}'(z_i) = y_i,
+$$
+and since $D_i^j$ is non-decreasing, $D_i^j(y_i,s_{-i}) \ge z_i \ge v_i$.
 Thus, by (\ref{dataallocation}) and (\ref{figureout}),
@@
 {
-\lemma{(Static Data Nash Equilibrium)} 
+\lemma{(Continuity of $\epsilon$-best reply)} (NEED A LEMMA?)
 }
@@
 \cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
-game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
+game with the data-PSP rules applied independently by each user, and all users applying
+their respective strategies, the secondary market converges to an $\epsilon$-Nash
 equilibrium. 
@@
 \textbf{Proof:}
+1. selling off data piecewise over time (MAYBE?), \\
 2. using the min price of sellers in the auction i.e. ${\theta_i}'(d_{i^*}^j) =
@@
 
-NOTES: (CMHK)
-FAQ
-Why I am not able to purchase extra data?
-Incorrect input: Please follow the instruction on the failure SMS and try to
-purchase extra data again. You can also call our 24 hours customer service
-hotline at 2945 8888 to purchase extra data.
-If you are still unable to purchase extra data after a few attempts, please call
-our 24 hours customer service hotline for enquiries.
-
-Can the remaining extra data be carried forward to the next bill month?
-Extra data purchased can only be used within the bill month that it was
-purchased. Remaining extra data will be forfeited by the end of that bill month
-and will not be carried forward to the next bill month.
-Can I sell the extra data purchased on 2cm Exchange Platform?
-Extra data purchased cannot be sold on 2cm Exchange Platform.
-Terms and Conditions of Data Top-up:
-When the data entitlement of designated service plan is used up, customers can
-purchase extra data within the bill month based on their needs to continue using
-the data service. Otherwise, the data service will be suspended until the next
-bill month. On the other hand, customers with Data+ VAS or Data+ Package can
-enjoy unlimited local data service with designated maximum access speed limit
-within the contract period after the data entitlement of the bill month is used
-up. Data+ will not support tethering and pee-to-peer (P2P) upload and download,
-including BitTorrent.
-Data Top-up is only applicable to designated service plans, including but not
-limited to “Supreme Global” Service Plan, “Supreme Asia” Service Plan, “Supreme
-Greater China” Service Plan, 4.5G Full Speed Local Service Plan, 4.5G Full Speed
-Share Service Plan,“Smart Care” Service Plan and Tertiary Student 4.5G Full
-Speed Local Service Plan.
-Customers can only purchase extra data again after the purchased extra data is
-used up.
-Extra data fee is subject to change. CMHK will charge to the customers at the
-prevailing fee.
-The purchased extra data is only applicable to the bill month that it was
-purchased. Any remaining data (if applicable) cannot be carried forward.
-The purchased extra data is not applicable to 2cm exchange platform.
-Once the top-up data has been purchased, the related payment will not be
-refunded.
-CMHK reserves the right to modify the above content and amend these terms and
-conditions at any time without prior notice.
-In case of dispute, CMHK reserves the right of final decision.
-
 \subsection{Efficiency}
@@
 
-\bibitem{cmhk}
-\textit{China Mobile Hong Kong Company Limited}.
-\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html} 
-2018
-
-\bibitem{iia}
-Andreu Mas-Colell, Michael Dennis Whinston, and Jerry R. Green, 
-\textit{Microeconomic Theory}. Oxford University Press. 1995. p. 794.
-
 \end{thebibliography}

### 2019-09-26 Old/April/paper_clean.tex
Work

--- 2019-09-26 Old/April/paper_alphafair.tex
@@
 In this work, we propose a distributed progressive second price (PSP) auction in
-order to maximize social utility in this secondary data-sharing market. We show that for cellular data allocated between multiple users there
+order to maximize social utility. We show that for cellular data allocated between multiple users there
 exists an $\epsilon$-Nash market equilibria when all users bid their real marginal
 valuation of the mobile data offered in the secondary market described in
-\cite{zheng}. A quality of the PSP auction is that
-demand information is not known centrally, rather, it is distributed in the
+\cite{zheng}. The PSP auction's (as in all auctions),
+demand information is not known centrally, rather it is distributed in the
 buyers' valuations. The mechanism for an auction is defined
@@
 fee to be paid to the ISP on completion of the transaction. (FEE IS FIXED OR
-PER-UNIT?)(DO WE MODEL ISP PROFIT? FUTURE WORK)
-
-The form of the auction mechanism presented here is (CAN BE? NEED TO SHOW TO
-CLAIM 'IS') described as a
-pure-strategy progressive game with incomplete, but perfect information. (WHAT
-DOES NASH SAY ABOUT THIS?) (TRY MIXED? CAN ONLY HAVE MIXED WITH A DISTRIBUTED
-VALUATION.. FUTURE WORK)
+PER-UNIT? (will change market incentives slightly))
+(DO WE MODEL ISP PROFIT? FUTURE WORK)
 
@@
 
-\subsubsection{Bandwidth Allocation using PSP}
-
-We begin with a brief introduction to the distributed PSP auction for the
-bandwidth allocation problem, first introduced by Lazar and Semret \cite{lazar}.
-The distributed PSP auction from \cite{lazar} forms a part of the
-overall market based allocation model. They consider a noncooperative game
+The distributed PSP auction first introduced in \cite{lazar} forms a part of the
+overall market based allocation model. Consider a noncooperative game
 where a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users buy a fixed
-amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$.
-
-Suppose each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
+amount of resource $D_i$ from a set of resources $\mcI = \lbrace 1,\cdots,L\rbrace$. Suppose
+each user $i \in \mcI$ makes a bid $s_i^l = (p_i^l, d_i^l)$ to the
 seller of resource $l$,
@@
 which means the maximum available quantity at a bid price of $y$ given
-$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin},
-\cite{qpsp} is defined
+$s_{−i}^j$. With this notation, the modified PSP allocation rule \cite{tuffin} is defined
 as:
@@
 $p_i$ are not rejected.
-%%%%%%%%%%%%
-\iffalse
+
 An allocation rule is feasible \cite{lazar} if $\forall \ s$,
@@
 \end{align*}
-\fi
-%%%%%%%%%%%%%%%%%%
-
-Using this classic PSP mechanism, \cite{lazar} shows that given the opponents bids $s_{-i}$,
-user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
-(where $s_i$ is chosen to maximize $i$'s utility with $s_{-i}$ held constant), is
-given by:
-\begin{align}
-\begin{split}
-    v_i &= \sup\bigg\lbrace d \ge 0 : \theta '(d) > P_i(d), \\ 
-&\displaystyle\int_0^d P_i(\eta) \ d\eta \le b_i\bigg\rbrace -
-\frac{\epsilon}{\theta_i'(0)} \\
-&\qquad\qquad \text{(best quantity reply)} \\
-\end{split}\\
-    w_i &= \theta_i'(v_i) \quad \text{(best unit-price reply)},
-\end{align}
-where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
-has an elastic demand function.
-
-\subsubsection{Data Allocation using PSP}
-
-The main contribution of this work is to show that the rules of PSP auctions are applicable to the
-secondary market described in \cite{zheng}. We find that the auction of data effects the
-strategies of the users (buyers and sellers) and results in a (somewhat) different
-auction from the original bandwidth problem. We intend to show that our auction
-is rational and achieves the desired VCG properties, as does the original
-formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
-both a theoretic and notational template (BAD SENTENCE), we define optimal strategies for
-buyers and sellers which allows for the development of a PSP auction mechanism
-to achieve a network equilibrium for cellular data. (EXPAND)
 
@@
 opt-out buyer restricts its pool of sellers by only submitting bids to sellers
-who are able to meet their requirements.
-We intend to show that our PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive compatibility. We
-reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
+who have sufficient data to meet their requirement.
+(NOTE: TAKE MAX ONLY OR NEED TO INTRODUCE
+A GAP VARIABLE?), similar to \cite{zheng}. 
+In addition, we define a generic
+\textbf{data-provisioning vector} $\vs$, held the user as part of its type
+along with its valuation and budget, . 
+We intend to show that the pricing model (\ref{dataprice}) is sufficient to attain the desirable
+property of truthfullness through incentive compatibility. (MOVE THIS? NEED OWN
+WORDS?) We
+reason that our formulation upholds the \emph{exclusion-compensation
 principle}, and is a valid progressive second price auction to the extent that buyer $i$
@@
 
-We extend the P2P rules described in \cite{semret} to include a \emph{local} market
+(NOTE: move this?)
+We extend the P2P rules as in \cite{semret} to include a \emph{local} market
 price function as determined by the subset of nodes participating in the
-auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
+auction, where the user is the auctioneer. Therefore the influence of the greater market on the individual
 auctions will be influenced only by the submission of bids from buyers to
 sellers. As a buyer may have access to multiple auctions, the sellers will be
-dynamically influenced by the market via the $\epsilon$-best replies from the
-buyers: the
+dynamically influenced by the $\epsilon$-best replies from the buyers. The
 valuation function of seller $j$ is dependent on the buyers demand, and is
@@
 
-%%%%%%%%%%%%%%%%%%%
-\iffalse 
-We use the $\alpha$-fair utility functions \cite{zheng} to model the
+Absent the cost or revenue from trading data, users gain utility from consuming
+data. We use the $\alpha$-fair utility functions \cite{zheng} to model the
 valuation from consuming $d$ amount of data:
@@
 \end{itemize}
-\fi
-%%%%%%%%%%%%%%%%%%%%%%
+
+% USER UTILITY (7)
+In the remainder of this paper we omit the bar in the data allocation rule for
+simplicity of notation, so $\bar{a}_i = a_i$. We may now define the user's utitlity function as
+\begin{equation}\label{buyerutility}
+    u_i = \theta_i(a_i(s)) - c_i(s).
+\end{equation}
+
+Under the PSP rule, \cite{lazar} shows that given the opponents bids $s_{-i}$,
+user $i$'s $\epsilon$-best response $s_i = (w_i, v_i)$ as a Nash move
+(where $s_i$ is chosen to maximize $i$'s utility with $s_{-i}$ held constant), is
+given by:
+\begin{align}
+\begin{split}
+    v_i &= \sup\bigg\lbrace d \ge 0 : \theta '(d) > P_i(d), \\ 
+&\displaystyle\int_0^d P_i(\eta) \ d\eta \le b_i\bigg\rbrace -
+\frac{\epsilon}{\theta_i'(0)} \\
+&\qquad\qquad \text{(best quantity reply)} \\
+\end{split}\\
+    w_i &= \theta_i'(v_i) \quad \text{(best unit-price reply)},
+\end{align}
+where $\epsilon > 0$ is the bid fee, $b_i$ is user $i$'s budget, and every user
+has an elastic demand function.
+
+In the Secondary Market \cite{zheng}, we intend to show optimal strategies for
+buyers and sellers which allows the use a PSP auction to achieve a global
+network equilibrium.
 
@@
 meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
-a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
+a unit price $p^j_i$. (STILL TRUE?) Without loss of generality, we assume that all users bid in all
 auctions; if a user $i$ does not submit a bid to $j$, then this means that
@@
 
-\subsubsection{Buyer Strategy}
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We will assume that the buyer valuation satisfies the conditions for an
-\emph{elastic demand function}: 
-\definition{\cite{lazar}}
-A real valued function for buyer $i$, $\theta(\cdot)_i$, is an \emph{(elastic) valuation
-function} on $[0, b_i]$ if 
-\begin{itemize}
-    \item $\theta_i(0) = 0$,
-    \item $\theta_i$ is differentiable,
-    \item ${\theta_i}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta_i}
-'(z) > 0$ implies that for all $\eta \in [0, z), {\theta_i}'(z) \le {\theta_i}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
 % OPT-OUT BUYER
@@
 \end{equation}
-where $e_i : [0, \infty) \rightarrow [0,\infty)$ is %the expectation 
-a function that maps buyer $i$'s data quantity (requirement) to matching
-seller(s). We note that the opt-out buyers' valuation depends only on a scalar $e_i(a)$ which is a function of the
+where $e_i : [0, \infty) \rightarrow [0,\infty)$ is the expectation 
+(EXPECTATION??? BAD) that user
+$i$ finds matching seller(s). An opt-out buyers' valuation
+depends only on a scalar $e_i(a)$ which is a function of the
 quantities of all the available data for sale in the secondary market.
@@
 Suppose the total amount of seller $j$'s data on the network at the instance that
-user $i$ joins the auction is $b^j$. 
+user $i$ joins the auction is $\bar{b}^j$. 
 The data transfer from each seller cannot exceed the total amount they have available,
-i.e. $a_i^j \le b^j$. This will hold simultaneously for each $i \in
-\mcI$ if and only if $b^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
+i.e. $a_i^j \le \bar{b}^j$. This will hold simultaneously for each $i \in
+\mcI$ if and only if $\bar{b}^j \ge \max_i \ a_i^j$. Therefore a seller $j$ is
 restricted to subset of buyers $\in\mcI$.
@@
 rational (utility-maximizing) buyer will set $s_i^j = 0$, i.e. they will not
-place a bid, as in \cite{zheng}. The seller, in our analysis, is a functional
-extension of the buyer, its valuation $\theta^j$ is dependent on the buyers. We will assume that buyers and sellers
+place a bid, as in \cite{zheng}. The seller, in our analysis, is an extension of the buyer, where the valuation
+$\theta^j$ is dependent on the buyers, we will assume that buyers and sellers
 are separated (a seller does not also buy data and vice versa).
@@
 determine that a buyer must coordinate their bids among multiple sellers. (SAY
-MORE?) Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
-moderated
-by a function of quantities desired from the distributed market. 
+MORE?) Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$, given as
+the $\alpha$-fair utility in (\ref{buyervaluation}), scaled
+by a function of quantity desired from the market. 
 We define, in addition to the valuation $\theta_i$ and budget $b_i$, a generic
@@
 which produces the minimal subset 
-\begin{equation}\label{sellers}
+\begin{equation}\label{buyers}
     \mcI_i = \lbrace j \in \mcI : j < n\rbrace \subset \mcI.
@@
 \sum_{j\in\mcI}d^j/d_i$, then $j^* > I$ and we consider the buyers' demand
-infeasible (CAN DO BETTER!). 
+infeasible. 
 We also note that $\mcI_i$ is not the only
@@
 
-\subsubsection{Buyer Influence}
 To determine a strategy for the sellers, we examine seller incentive. The potential revenue for $j$ at unit price $y$ is determined by the
@@
 \textbf{Proof:} 
-We assume that a seller will try to maximize profit for any given allocation $a$, and
-as such there is an incentive for $j$ to sell all of its data, and so from Lemma
+We assume that a seller will try to maximize profit, and
+so there is an incentive to sell all of its data, and so from Lemma
 \ref{sellervaluation},  $\sum_{i\in{\mcI}} d_i^j = 
@@
 
-\subsubsection{Progressive User Strategy}
-In order to to develop the seller strategy, it is necessary we determine 
+In order to to implement a PSP auction, it is necessary that we determine 
 that a seller has an incentive to
-accept fractional bids (i.e. sell a fraction of their data $b^j$). Reasonably,
-there may not exist a buyer such that $d_i = b^j$. In addition, a seller may accept
+accept fractional bids (i.e. sell fraction of their data $d^j$). Reasonably,
+there may not exist a buyer such that $d_i = d^j$, in addition, a seller may accept
 fractional bids in order to
@@
 they will not become a buyer while they submit their total data overage to the
-secondary market. (FUTURE WORK? FROM \cite{zheng})
-
-We describe the sellers' \emph{local} auction strategy for allocating its
-data according to the constraints formed by the buyer strategy. As
-local auction is progressive, and influenced by the $\epsilon$-best replies of
-the buyers, we will need the following Lemma. (SHOULD I COUPLE THESE
-ALGORITHMS? LESS OR MORE CONFUSING?)
-
-% BUYER LOCAL RESPONSE
+secondary market. (FUTURE WORK?)
+
+% SELLER STRATEGY
 {
-\lemma{(Buyer response)}\label{buyerresponse}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-Fix any seller $j$, and fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$. Let the
-winner be determined and $s^j$ updated as in the seller strategy. As we cannot
-assume that a buyers' bid will remain fixed at time $(t+1)$,
-we address the following special cases:\\
-(Budget limited allocation)
-\begin{equation}\label{partialallocation}
-    d_i^j > b^j - \sum_{k\in\mcI^j, k\ne i} d_k^j.
-\end{equation}
-(Equal price allocation)
-There exists $k,i \in \mcI^j$ where $k\ne i$, such that
-\begin{equation}\label{equalprice}
-    \quad p_i^j = p_k^j.
-\end{equation}
-(Price-dominant allocation)
-There exists $i \in \mcI^j$, $k \ni \mcI^j$, where
-\begin{equation}\label{newbuyer}
-    p_k^j < p_i^j \qquad \forall \ i \in \mcI^j.
-    %p_i^j < p_k^j \quad \text{and} \quad d_i^j >= b^j, \quad \forall \ k \in \mcI^j.
-\end{equation}
-(Empty allocation)
-\begin{equation}\label{emptyset}
-    n > \vert \mcI\vert \Rightarrow \ell^j = \emptyset.
-\end{equation}
-In any of the above cases, seller $j$'s local auction strategy does not change and
-Proposition \ref{sellerstrategy} holds.
-}
-\textbf{Proof:} \\
-The first two cases, (\ref{partialallocation}) and (\ref{equalprice}) deal with
-the problem of a buyer receiving a partial allocation:
-In (\ref{partialallocation}), the winner with the lowest unit price $p_i^j$ results in a partial
-allocation. In this case, using (\ref{buyercoordinate}), buyer $i$ will decrease its
-quantity $d_i^j$ by increasing $n$, and will either remain a winner in $j$'s local
-auction, or drop out of $\mcI^j$. (WILL USE LATER, DEVELOP MORE HERE?)
-(\ref{equalprice}) considers that there may exist multiple buyers with the same unit price. The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
-between all buyers with the same unit price. Therefore, again by
-(\ref{buyercoordinate}), the buyers will increase $n$ until their demand is
-met. (SHOULD I ALLOW FOR SPECIALIZED SPLIT BIDS FROM THE BUYERS? WILL IT WORK
-WITH COORDINATED BIDS? MORE WORK NEEDED HERE...)\\
-The third case considers that a new buyer $k$ may enter the market with a better
-price. There cannot be a buyer where $d_k^j > b^j$, as this violates
-(\ref{budget}) imposed by (\ref{buyercoordinate}). When $d_k^j =
-b^j$, the optimal solution at time $t$ is the single allocation, therefore at
-time $(t+1)$, we have $\mcI^j = k$. It follows that in the case $d_k^j < b^j$, buyers $i\in\mcI^j$ will
-lose their position in $\ell^j$ as the auction progresses and the minimal
-subset $\mcI^j$ is computed. 
-(BUYERS ARRIVE AS A POISSOIN PROCESS? FUTURE WORK)
-Lastly, to resolve (\ref{emptyset}), $j$ chooses $n=I$, and sets its reserve price to $p_I^j$.
-
-We now define the local auction, which we describe, when coupled with the buyer
-responses, as a progressive game of strategy with incomplete, but perfect
-information (SAY MORE?).
-% SELLER LOCAL STRATEGY
-{
-\proposition{(Localized seller strategy (i.e. fractional allocation))}\label{sellerstrategy}
+\proposition{(Localized seller strategy)}\label{sellerstrategy}
 Define any auction duration to be $\tau \in [0,\infty)$. For any seller $j$,
-For any seller $j$, fix all buyers bids $s_i^j=(d_i^j,p_i^j)$ at time $t\in\tau$.
-
-let the winner be determined by,
+fix bid $s^j=(d^j,p^j)$ at time $t\in\tau$.
+Let the winner be determined by,
 \begin{equation}\label{winner}
@@
 \begin{equation}\label{newprice}
-    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon.
-\end{equation}
-and update $j$'s budget to reflect the (tentative) allocation,
+    p^j = \theta_{i^*}'(d_{i^*}^j) + \epsilon/2,
+\end{equation}
+and update $j$'s budget,
 \begin{equation}\label{newbudget}
@@
 \end{equation}
-Allowing $t$ to range over $\tau$, with buyer responses given as in Lemma
-\ref{buyerresponse}, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
-%Assuming that no new buyers enter the market, we have that (\ref{winner}) - (\ref{newprice}) produces a local
-market equilibrium.% from time $t$ to $(t+1) \in \tau$.
+Allowing $t$ to range over $\tau$, we have that (\ref{winner}) - (\ref{newbudget}) produces a local
+market equilibrium.
 }\\
 \textbf{Proof:}
-We will assume that the seller has enough data to satisfy at least one buyer,
-in the case of multiple buyers $i^*$ is the \emph{losing} buyer with the highest unit
-price offer, determined by (\ref{sellercoordinate}). As the set of buyers is
-computed at each iteration, we are guaranteed a subset $\mcI^j \subset \mcI$ that is 
+We assume that the seller has enough data to satisfy at least one buyer. As the
+set of buyers is computed at each iteration, we are guaranteed a
+a subset $\mcI^j \subset \mcI$ that is 
 at equilibrium as it is designed so that the data offered by
-seller $j$ equals the aggregate demand of the buyers \cite{???}
+seller $j$ equals the aggregate demand of the buyers (CITE! KNOWN?).
 Although the buyers' valuation $\theta_i$ is not known to the seller, we assume
-that the buyer is bidding truthfully, and so $p^j = {\theta_i}' + \epsilon
-=p_i^j + \epsilon$, therefore $p^j$ is known, and as $\mcI^j\subset \mcI$, we
+that the buyer is bidding truthfully, and so $p^j = {\theta_i}' + \epsilon/2
+=p_i^j + \epsilon/2$, therefore $p^j$ is known, and as $\mcI^j\subset \mcI$, we
 note that (\ref{budget}) and (\ref{reserveprice}) hold. Now, using
@@
 which holds $\forall \ i \in \mcI^j$.
-It follows that, using
-%, using (\ref{buyercoordinate}), 
-the definition of an $\epsilon$-best reply $s_i^j = (v_i^j, w_i^j)$,  
-for any $\epsilon$-best reply, 
-$$
-    p^j \le {\theta_i}'(v_i^j) + \epsilon,
-$$
-$\forall i \in \mcI^j$.
+From (\ref{sellercoordinate}), $i^* \ni \mcI^j$, and by definition of an
+$\epsilon$-best reply and (\ref{newprice}), 
 Therefore the choice of $p^j$ does not force any buyers out of the local
-equilibrium. Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and that the local
-equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-(NEED TO SAY MORE HERE... INDUCTION? HOW DOES THE TENTATIVE AWARD WORK? SAVE
-FOR NASH EQ PROOF? KEEP WITH t TO t+1?)
+equilibrium.
+Thus we determine the valuation of the transaction between seller $j$ and buyer $i$ is well-posed,
+and the reserve price (\ref{newprice}) is justified, and that the seller does
+not force a change to the local market equilibrium from time $t$ to $(t+1)$.
+(NEED TO SAY MORE HERE... INDUCTION?)
 
@@
 data overage by purchasing enough data from a subset of other network users.
-This user $i$ can be modeled as a opt-out buyer where, as in \cite{semret},
-$\vs_i^j$ corresponds to a fraction of user $j$'s data aquired by user $i$. In order to form the
+This user $i$ can be modeled as a opt-out buyer where, as in \cite{semret}, $\vs_i^j$ denotes the
+fraction of user $j$'s data aquired by user $i$. In order to form the
 distributed auction, we set $1$ if seller $j$ has enough data to
@@
 \State $p^{j(0)} \gets \min_{i\in\mcI^j} p_i^j$
-\State $s^{j(0)} \gets (p^j, b^j)$
-\While{$b^j > 0$}
+\State $s^{j(0)} \gets (p^j, d^j)$
+\While{$d^j > 0$}
 \State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \lbrace i \in \mcI^{j(t)}: d_i^j >
@@
 buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$. As we will show in our analysis, the buyers are bidding truthfully; the
-algorithm makes use of the fact that the sellers' valuation is determined by
-the buyers' market and upholds the PSP mechanism. (CHECK)
-
-(BUYER ALGORITHM? WHY NOT..., CLEANER)
+algorithm makes use of the fact that the sellers' valuation is determined by the
+market and upholds the PSP mechanism. (CHECK)
 
@@
 of sellers guaranteed (CHECK) to satisfy demand where $i$ is able to play a
-``consistent" strategy and still have feasible best replies, and buyer
+``consistent" 
+strategy and still have feasible best replies, and buyer
 coordination holds in the secondary data market under our assumptions.
@@
 to partition the auction space, thereby 
-controlling (optimizing?) the message space (EXPLAIN) for the
+optimizing the message space (EXPLAIN) for the
 ISP, and providing an optimal market space to host the buyers and sellers based
@@
 
-\subsubsection{Incentive Compatibility}
-
 We proceed to claim that the optimality of truth-telling holds in our
 formulation, where the market functions as a hybrid of \cite{semret} and
-\cite{zheng}. The opt-out buyers' market is comprised of the minimal subset of
-sellers with the largest budgets, described in the buyer strategy as $\mcI_i$.
-To achieve incentive compatibility, we find that the opt-out buyer must choose this subset so that
-its overall marginal value is greater than its market price.
-The buyers' market price is calculated as the sum of reserve prices
-of the sellers in the opt-out buyers' pool.
-the market prices at the %different auctions, weighted by the data provisioning vector values.
-The actual bids are
-obtained from the opt-out buyers' strategy. The quantity to bid is given
-by the auction mechanism, i.e. (\ref{dataprice}) and (\ref{datacomposed}), as
-the maximim possible quantity of data that a buyer $i$ can bid over its seller
-pool while maintaining a marginal valuation greater than the aggragate of
-minimum prices maintained by the sellers in $i$'s pool.
-As with a single resource, \cite{semret} and
-\cite{lazar}, we show that truth-telling is optimal for the buyer, i.e. in each auction, the buyer sets
+\cite{zheng}. The seller
+finds the optimal opt-out buyer $i$ , which is the buyer with the largest demand such that the marginal value is greater than the market price.
+The role of the market price is played by the sum of the market prices at the
+different auctions, weighted by the data provisioning vector values. The actual bids are
+obtained by transforming the opt-out buyers' strategy back into the
+corresponding quantities to bid. As with a single resource,
+truth-telling is optimal for the buyer, i.e. in each auction, the buyer sets
 the bid price to the marginal value.
@@
 
-We proceed to examine the strategy of the seller. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. As we have shown, the buyers are bidding truthfully, according to the
-rule of incentive compatibility. Seller $j$'s reserve price is determined by a
-buyer $i \in \mcI \setminus \mcI^j$, and therefore, even if this price is zero,
-then $p^j = \epsilon \ge 0$.
-We argue that if truthfullness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then there exists a market
-equilibrium. We have the following Lemma.
-
-{
-\lemma{(Incentive compatibility in local auctions)}
-For any seller $j$, let time $t \in \tau$ be fixed, as well as bids from $j$'s
-seller pool, so that $s_i$ is fixed $\forall \ i \in\mcI^j$. The
-``$\epsilon$-best" reply for seller $j$ is,
-$$
-    s^j = (b^j, p^j),
-$$
-defined by Proposition \ref{sellerstrategy}.
-%and fix $j$'s reserve price $p^j$ as is defined by (\ref{newprice}). 
-The sellers' ``truthful" strategy, combined with Proposition
-\ref{buyerincentivecompatibility}, forms a
-``truthful" local game embeddeded within $j$'s auction, and an equilibrium of
-the embedded game is an equlibrium point for the local auction. 
-}\\
-\textbf{Proof:}
-We have that $p^j$ is the lowest price that $j$
-will accept to perform any allocation. By the definition of ``reserve
-price", $j$ is willing to buy its own budget $b^j$ at price $p^j$. This forms a
-``truthful" local game embeddeded within $j$'s auction with strategy space
-restricted to $\epsilon$-best replies from buyers $\in \mcI^j$. Therefore we have that a
-fixed point in the ``truthful" local game is a fixed point for the auction.
-To see this, we observe that from (\ref{datacomposed}), $\forall \ i \in \mcI^j$, $\bar{D}_i^j(y, s_{-i}) =
-0 \ \forall \ y < p^j$, and so $y=0 \le \epsilon \Rightarrow e_i^j(a) = 0$. We
-further argue that by Lemma \ref{buyerresponse}, and as the set $\mcI^j$ is
-computed at each bid iteration, that our result holds for time $(t+1) \in \tau$.
-(NEED MORE? EACH CASE IN 4.3?)
-
-{
-\lemma{(Continuity of $\epsilon$-best reply)} (NEED A LEMMA?)
-}
+We proceed to examine the strategy of the seller. We argue that if
+truthfullness holds for both buyers and sellers, i.e. $p_i ={\theta_i}' \
+\forall j$ and $p^j = {\theta^j}' \ \forall i$, then there exists a market
+equilibrium.
 
@@
 Using the rules of the data auction mechanism, the secondary market described in
-\cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
-game with the data-PSP rules applied independently by each user, and all users applying
-their respective strategies, the secondary market converges to an $\epsilon$-Nash
+\cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auctin
+game with the PSP rule applied independently by each buyer, with fixed $s^j$
+and reserve prices $p^j>0$, for all sellers $j\in\mcI$, and all buyers applying
+the opt-out strategy. Then the secondary market wil converge to an $\epsilon$-Nash
 equilibrium.
@@
 \textbf{Proof:}
-1. selling off data piecewise over time (MAYBE?), \\
-2. using the min price of sellers in the auction i.e. ${\theta_i}'(d_{i^*}^j) =
+We will prove the theorem by asserting that our formulation upholds the VGC
+mechanism that is given in the properties of modern PSP. Namely,
+\begin{itemize}
+    \item Incentive compatibility
+    \item Efficiency 
+    \item Convergence
+\end{itemize}
+(WANT TO SHOW ALGORITHM DOES NOT RUIN VCG : \\
+1. selling off data piecewise over time, \\
+2.
+using the min price of sellers in the auction i.e. ${\theta_i}'(d_{i^*}^j) =
 p^j$ is OK, \\
@@
 4. the algorithm achieves global economic equilibrium)\\
-\textbf{NEED TO COVER:}\\
-1. Change in buyer valuation \\
-2. New buyers\\
-3. Not enough buyers \\
-4. Not enough data\\
 \textbf{TRY:}\\
@@
 valuation of the sellers is derived by the demand of the buyers, who are
-bidding equivalent bids over a minimum subset of buyers, we claim that the seller
+bidding equivalent bids over a minimum subset of buyers, then the seller
 strategy, along with the seller constraint (\ref{??}) results in a global
 market equilibrium.
-We have shown that the local
-equlibirium created by $j$ is stable from time $t$ to $(t+1)$. 
-Now, suppose that buyer $i^*$ computes its best response $s_i^j = (v_i^j, w_i^j)$
-Finally, suppose that
-a buyer $k$ enters the market such that for some buyer $l\in\mcI^j$,
-$$
-    \displaystyle\sum_{i\in\mcI^j} p_i^je_i^j(a) + p_k^je_k^j(a) \ge
-\sum_{i\in\mcI^j} p_i^je_i^j(a) - p_l^je_l^j(a),
-$$
-that is,
-
-NOTES: (today)\\
-1. switch from defined valuation function\\
-2. finish seller incentive compat\\
-3. work on progression\\
-4. check reserve price = monopoly price
 
 \subsection{Efficiency}
-(NEED OWN WORDS)
-The objective in designing the auction is that, at equilbrium, resources al-
-ways go to those who value them most. Indeed, the PSP mechanism does
-have that property. This can be loosely argued as follows: for each player,
-the marginal valuation is never greater than the bid price of any opponent
-who is getting a non-zero allocation. Thus, whenever there is a player j
-whose marginal valuation is less than player i 's and j is getting a non-zero
-allocation, i can take some away from j , paying a price less than i 's marginal
-valuation, i.e. increasing u i , but also increasing the total value, since i 's
-marginal value is greater. Thus at equilibrium, i.e. when no one can unilat-
-erally increase P their utility, the total value is maximized.
 

### 2019-09-26 Old/April/paper_wc_hold.tex
Work

--- 2018-04-18 paper_wc_4-12.tex
@@
 budget, and every user has an elastic demand function.
+
 Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
@@
 
+We intend to show that our auction
+is rational and achieves the desired VCG properties, as does the original
+formulation. Using \cite{zheng} as a basis for our model, and \cite{lazar} as
+realistic, theoretic, and notational templates, we define optimal strategies for
+CMHK users, and demonstrate that the development of a set PSP auction mechanisms
+in a data exchange setting is able achieve a network equilibrium for cellular data.
+
 % MECHANISM
-\subsubsection{The Mechanism}\label{mechanism}
-The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
-problem of network bandwidth allocation, and is analyzed as a noncooperative
-game where $i\in\mcI$ agents buy the
-fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
-The market price function (MPF) for a buyer-seller pair is,
+\subsection{Data Auction Mechanism}\label{mechanism}
+We now proceed to formally define the PSP auction, which determines the actions 
+buyers and sellers in the secondary market, which we will denote the \emph{data}
+PSP rules.
+The market price function (MPF) for a buyer in the secondary market
+can be described as follows:
 % NEW MARKET PRICE
@@
 \begin{split}
-    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
-    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
+    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z,
+s_{-i}^j)\\
+    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
+    {D_i^j}(y,s_{-i}^j) \ge z \bigg\rbrace \bigg),\\
 \end{split}
 \end{align}
-and is the of minimum prices a user bids in
-order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
+and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
+order to obtain
+data amount $z$ given opponent profile $s_{-i}$. We note that
+the total minimum price for the buyer must be an aggragation of the
+\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
+%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
+%buyer $i$'s bid quantity. 
 The maximum available quantity of data in auction
-$j$ at unit price $y$ given $s_{-i}^j$ is,
+$j$ at unit price $y$ given $s_{-i}^j$ is: 
+% NEW ALLOCATION RULE
+\begin{align}
+\begin{split}\label{datacomposed}
+    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
+\end{split}
+\end{align}
+it follows that the inverse price function is aggregated over all local auctions
+$j\in \mcI$,
 % NEW INVERSE DEMAND
@@
 \begin{split}
-    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
+    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
+    D^j \big] : \\
+    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
 \end{split}
 \end{align}
-where $D^j$ is the total amount of bandwith that user $j$ has to offer.
 % DATA ALLOCATION RULE
-For each $i \in \mcI$, the allocation from auction $j$ is,
+The resulting data allocation rule is a function of the local market
+interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
+allocation from auction $j$ is,
 % and so for profile $s_i$, for any $i \in \mcI$,
 \begin{align}\label{dataallocation}
-    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
-    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
+    a_i^j(s) &= \min\bigg\lbrace D_i, \\
+    &\frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
 \end{align}
-Finally, we have the cost of the allocation,
+Finally, we must have that the cost to the buyer adheres to the second price
+rule for each local auction, with total cost to buyer $i$,
 % DATA COST
 \begin{align}\label{datacost}
-    c_i^j(s) = \displaystyle\sum_{k\ne i} 
-p_k^j \big[a_k^j(0; s_{-i}^j)
-    -a_k^j(s_i^j;s_{-i}^j)\big].
+\begin{split}
+    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
+p^j \bigg(a_i^j(0; s_{-i}^j)
+    -a_i^j(s_i^j;s_{-i}^j)\bigg).
+\end{split}
 \end{align}
 
-It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
-equilibria for differentiated services
-allocated between multiple agents when all players bid their real marginal valuation
-of the bandwidth resource. In other words, the PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive
-compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
-principle}, user $i$
+We intend to show that the PSP constraints are
+sufficient to attain the desirable property of truthfullness through incentive compatibility. We
+reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
+principle}, and is a valid progressive second price auction to the extent that buyer $i$
 pays for its allocation so as to exactly cover the ``social opportunity cost"
@@
 revenue \cite{lazar}.
-We have the definition of an elastic valuation function. In the PSP market, a
-user is considered truthful if their bid price equals their marginal valuation,
-i.e. $p_i^j = {\theta_i^j}'$.
+
+\section{Related Work}
+
+\section{The Problem Model}
+\subsection{The Secondary Market}
+
+We define the set of users, $\mcI = \lbrace 1, \cdots, I\rbrace$, who purchase or sell
+data from other users. A buyer submits bids directly to sellers, where we
+assume that all users submit bids in order to maximize their
+(private) valuation functions. 
+We assume that users are selfish, and therefore
+rational. Users prefer to participate in the secondary market as it allows them to purchase
+additional data for a cost less than the overage fee set by the ISP. 
+In general, user preferences are defined by a utility function, which typically
+represents a users' valuation of an allocation minus the price, 
+\begin{align*}
+    u &: S \rightarrow (-\infty, \infty) \\
+          & s \rightarrow u(s).
+\end{align*}
+
+Absent the cost or revenue from trading data, CMHK users gain utility from consuming
+data. 
+We will assume that the user valuation satisfies the conditions for an
+\emph{elastic demand function}, as in \cite{lazar}: 
 \definition{\cite{lazar}}
@@
 \end{itemize}
-
-\section{Related Work}
-
-\section{The Problem Model}
-\subsection{The CMHK Market}
-
-We begin to construct the model for a PSP data auction for  mobile users
-particpating in CMHK's secondary data-sharing market.
-Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
-data from other users. We again define the bidding profile for any user to be 
-$s \equiv
-[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
-, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
-As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
-cellular network. We assume that users are selfish, and therefore
-rational. 
- Users prefer to participate in the secondary market as it allows them to purchase
-additional data for a cost less than the overage fee set by the ISP. 
-Thus we assume that all users submit bids in order to maximize their
-(private) valuation functions. 
-In general, user preferences are defined by a utility function, $u$, which typically
-represents a users' valuation of an allocation minus the price.
-Absent the cost or revenue from trading data, CMHK users gain utility from consuming
-data. 
-We will assume that the user valuation satisfies the conditions for an
-\emph{elastic demand function}, as in \cite{lazar}. 
-As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
-the bid profiles must adhere to some additional restrictions, which we will
-imply using the PSP bid profile notation.
-A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
-belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
-the bid belongs to a \textbf{seller}.
-Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
-meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
+A user's identity $i \in \mcI$ as a subscript indicates that the user
+is a buyer, and a superscript indicates the seller.
+Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$, from
+buyer $i$
+means $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
 a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
-auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
-(0,0)$. Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
-and seller $j$.
+auctions; if a user $i$ does not submit a bid to $j$, we simply set $s_i^j = (0,0)$.
 A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
 quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
-with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
-stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
-by the user type, whether or not they are  a buyer or a seller. 
+with reserve unit price $p^j = [p_i^j]_{i\in\mcI}$. $D^j = \sum_{i\in\mcI}
+d_i^j$ is the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI} d_i^j$ is the
+total amount of data required by a buyer $i$. 
+We emphasize that we allow for $s_i^j$ to
+stand for a buyer or sellers' bid, determined by whether or not the user is a
+buyer or seller. In other words, a bid $s^j$, the bid is understood as an offer in the secondary
+market; we assume that data is a unary resource belonging to the seller, and
+therefore can identify the data (for sale) with the identity of the user.
 To further clarify our analysis, we will emphasize the separation of buyers and
-sellers using
-$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
-In other words, a bid $s^j =
-[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
-secondary market. The notational conventions of the bid vectors are essentially 
-slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
+sellers by denoting bid vectors as slices of the
+grid, i.e. $s^j = [s_i^j]_{i\in\mcI}$ will denote a sellers' profile, and  $s_i =
 [s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
-Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
-d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
-d_i^j$ represent the
-total amount of data requested by buyer $i$. 
-Finally, we assume that data is a unary resource belonging to the seller, and
-therefore can identify each local auction
-with the identity of the seller $j\in\mcI$.
-
-Consider the grid of bid proiles, $s$, representing the distributed PSP auction
-mechanism in the CMHK market, each buyer $i$ will
-have information from each seller $j$, as well as opponent profiles $s_{-i}$
-from each auction in which it is participating, and therefore
-in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
-$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
-(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
+The notational conventions given by the slices $s_i$
+and $s^j$ will be used indicate if a bid is from a buyer or a seller. However,
+we note that this is a simplification for ease of notation, and considering the
+grid $s$ in a distributed setting, each buyer $i$ will
+have information from each auction in which it is participating, and therefore
+in the limit will have access to the full grid $s$, i.e. the buyer will
+participate in all auctions. However, 
 sellers can only gain information about the market grid by observing buyer
 behavior in their local auction.
-In our current formulation, we do not allow a seller to host multiple
-auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
-influence the CMHK market dynamics, with the sellers taking a secondary role
-(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).
+In our current formulation, we do not allow a seller to host multiple auctions(FUTURE WORK).
 
@@
     f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
-\end{equation}
-For a given demand $\rho^j$, $f_i$ maps the $z$th unit of data to the lowest
-possible unit price. \\
-\textbf{Remark:} In a coordinated bid, $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Naturally, the coordinated bid is the
+        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
+\end{equation}
+For a given demand $\rho^j$, $f_i$ maps the $z$-th unit of data to the lowest price at
+which $i$ could still bid in \emph{any} auction $j\in\mcI$.
+Naturally, this is the
 lowest unit cost of the buyer to participate in all auctions, and corresponds to
@@
     f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
+        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
 \end{equation}
@@
 (THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)
-
-We note that except at points of discontinuity, we have
-$P_i(z) = f_i(z)$. This mechanism generalizes Vickrey
-(``second-price") auctions which are for nondivisible objects.
 
@@
 \lemma{(Valuation across local auctions)}\label{userunion}
-For any $i,j\in \mcI$, 
+For any buyer $i$, let $s_i^j > 0$.
+Then, 
 \begin{equation}\label{jtoi}
@@
 \end{equation}
-Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
+Define the set of users $\Lambda$, where
+\iffalse
 \begin{equation}\label{lambda}
-    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
+    \Lambda_i = \bigg(\displaystyle\bigcap_{j\in\mcI_i} \mcI^j \bigg) \cup \mcI_i,
+\end{equation}
+$$
+     \mcI_i \cup (\mcI^j \cap \mcI^k) = (\mcI_i \cup \mcI^j) \cap (\mcI_i \cup
+\mcI^k)
+$$
+$$
+     \mcI^j \cup (\mcI_i \cap \mcI_k) = (\mcI_i \cup \mcI^j) \cap (\mcI_k \cup
+\mcI^j)
+$$
+and
+\fi
 \begin{equation}\label{lambda}
-    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
-\end{equation}
-and for each $i\in\mcI^j$ define,
-\begin{equation}\label{ilambda}
-    \Lambda_i = \mcI^j \cap \bigg(\displaystyle\bigcap_{k\in\mcI_i} \mcI^k
-\bigg).
-\end{equation}
-(WANT TO SAY $s_i^j > 0$ iff $i,j \in\Lambda \Rightarrow s_i^j \in \Lambda
-\equiv s_i^j \in \mcI$)
-Fixing all bids $s_i^j \in \mcI$, and time $t\in\tau$,
-\begin{equation}\label{sym}
-    (\theta_i \circ \theta^j) = (\theta^j \circ \theta_i).
-\end{equation}
-(ONLY HAVE ONE HALF OF THE SYMMETRY SO FAR! REALLY WANT TO MAKE $s_i = s^j$
-HAPPEN)
+    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
+\end{equation}
+and fix all bids $s_i^j \in \Lambda$.
+(BETTER RESULT!)
 }\\
@@
 if and only if $p_i^j \ge p_{i^*}^j$.
-Suppose $p_i^j < p_{i^*}^j$. By Proposition \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
+Suppose $p_i^j < p_{i^*}^j$. By Proposision \ref{sellerstrategy}, $i^*$ is either included or excluded from $\mcI^j$. 
 If $i^* \ni \mcI^j$, then (\ref{jtoi}) holds; in the latter case, by
@@
 will add sellers to its pool until its demand is satisfied. Therefore for any
-$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and so (\ref{jtoi})
+$j\in\mcI_i$, $\not\exists \ s_i^j > 0$ where $i \ni \mcI^j$, and (\ref{jtoi})
 holds.
-
-The subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. Assuming the buyer submits a
-coordinated, truthful bid, $\mcI_i\subset \mcI$ 
-will determine the unit price $p_{i}$ in buyer $i$'s bid.
+Now, the subset $\mcI^j \subset \mcI$
+determines $j$'s reserve price $p_{i^*}^j$. Similarly, $\mcI_i\subset \mcI$ 
+will determine the (coordinated) unit price $p_{i}$ in buyer $i$'s (truthful) bid.
 (\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
@@
 the lowest price that $j$ will accept to perform any allocation.
-Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy},
+Using (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}),
 we have that for each $i \in \mcI^j$, 
 $p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
-Let $p_*^j=p_{i^*}^j$ denote the reserve
-price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
-[p_i^j]_{i\ni\mcI^j}$.
-Now, we have,
-%Fix any buyer $i\in\mcI^j$.
+Now, fix any buyer $i\in\mcI^j$, and denote $p_{i^*}^j = p^j$ as the reserve
+price for auction $j\in \mcI_i$,
+(\ref{datademand}) implies,
 \begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-and, $\forall \ i \in \mcI^j$, 
-\begin{equation}\label{invrho}
-    f_i \circ e_i^j(a) \ge p_*^j,
-\end{equation}
-and, $\forall \ k \in \mcI_i$, 
-\begin{equation}\label{invrho}
-    p_*^j \ge f^k \circ e_i^k(a) ,
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-
+    \rho^j(p^j) = \displaystyle\sum_{i\in\mcI^j} e_i(a),
+\end{equation}
+and again using (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}), we have that 
+\begin{equation}\label{pj}
+p^j = f_i\circ e_i(a) = f^j\circ e_i(a).
+\end{equation}
+%The buyers valuation is distributed across multiple auctions. 
 The sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
-%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-Consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0$
-for any $k\ne j \in \mcI_i$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
-$\forall \ i \in \mcI^j$,
-\begin{equation}\label{feq}
-    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
-\end{equation}
-where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
-Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
-Since,
-$$
-    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
-$$ 
-there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
-we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
-It follows that buyer $i$'s bid price is given by,
-\begin{equation}\label{iprice}
-    p_i^j = \max_{j\in\Lambda}(f^j) \circ e_i(a)= \max_{j\in\Lambda}(p_*^j),
-\end{equation}
-
-%where $p_i^*$ represents $i$'s coordinated bid price,
-%i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
-This holds for any
-$i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
-Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
-denote each as $f$ in the remainder of the proof.
-
-Now, using (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
-$i\in\mcI^j$ to be, (HERE)
-(SHOW THAT $\Lambda$ IS DISJOINT!)
-\begin{equation}\label{sumrho}
-    \displaystyle\sum_{k\in\mcI_i\cup\mcI^j}\rho^k(p_*^k) =
-\sum_{k\in\mcI_i\cup\mcI^j}
-e_i^k(a),
-\end{equation}
-where $p^k$ is the highest unit price in the feasible set $\mcI_i\cup\mcI_k$.
-Thus we determine the aggregate demand from buyer
+their respective resources. By construction, we have that $j\in \mcI_i \
+\forall \ i\in \mcI^j$. 
+For any $k\in \bigcap_{i\in\mcI^j}\mcI_i$, let $\mcI^j \cup \mcI_k$ be a
+feasible subset, that is, $s_i^j > 0 \in \mcI^j \cup \mcI_k$ and $e_i^j(a) \le
+e \circ \min(D^j, D_i)$. From (\ref{jtoi}), $k\in\mcI_i \Rightarrow
+i\in \mcI^k$, so $i\in \mcI^k \cap \mcI^j$, and we have from Proposition
+\ref{buyerstrategy} that $i$ will
+bid so that $e_i^j(a) = e_i^k(a) \Rightarrow
+f_i(e_i^k(a)) = f_i(e_i^j(a))$, therefore $s_i^j\ge s_i^k > 0$, which holds $\forall \ i\in
+\mcI^j$.
+
+We now consider reserve prices among sellers $\in\Lambda$. Fix some $i \ \in\mcI^j$, and suppose
+$\exists \ k \ \in\mcI_{i}$ such that $p_{i}^k > p_{i}^j$. As we assume that
+buyers are bidding their valuation, $p^k = f_i(e_i^k(a)) = f^k(e_i^k(a))$. 
+We have by construction that $j\in\mcI_i, \ \forall \ i\in\mcI^j$, and so for
+any $k \in\mcI_k \cup \mcI_i$ we have that $p^k = p^j$. This holds for any $i\in\mcI^j$ and similarly if $p_i^k <
+p_i^j$. 
+We have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, for simplicity we
+denote each as $f$.
+Now, from (\ref{rho}), and intersection of subspaces, we determine the aggregate demand from buyer
 $i\in\mcI^j$ over the set of intersecting markets $\Lambda$ to be, 
@@
 \iffalse
-************************
-Proposition \ref{buyerstrategy} defines $e_i^j(a) = D_i/ 2$, and so $0 <
-e_i^j(a)$.
-************************
-\fi
-\iffalse
-Suppose $\exists \ i \in\mcI^j$ such that $\mcI_i = j$, so that $j$ is the only
-seller in $\Lambda$.
-, and $i$'s bid quantity,
-\begin{equation}\label{iquantity}
-    d_i^* = \circ e_i(a) = \frac{a_i^j}{j},
-\end{equation}
-where $j=j^* = \argmin$ for each $i\in\mcI^j$, thus $d_i^*$ represents $i$'s coordinated bid quantity, and we have
-$s_i^j = (p_i^*,d_i^*), \ \forall \ j$ such that $s_i^j > 0$,
-\fi
-\iffalse
-
 *****************************************************************************************************
@@
 % NEW MARKET PRICE
-\begin{align}
+\begin{align}\label{dataprice}
 \begin{split}
@@
 \begin{align}
-\begin{split}
+\begin{split}\label{datacomposed}
     D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
@@
 % DATA ALLOCATION RULE
-\begin{align}
+\begin{align}\label{dataallocation}
     a_i^j(s) \\
@@
 % DATA COST
-\begin{align}
+\begin{align}\label{datacost}
 \begin{split}
@@
 % BUYER DEMAND 
-\begin{equation}
+\begin{equation}\label{datademand}
     \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} d_i^j, 
@@
 % BUYER REVENUE 
-\begin{equation}
+\begin{equation}\label{buyerinversedemand}
     f_i(z) \triangleq \inf\big\lbrace y\ge 0:
@@
 % SELLER REVENUE 
-\begin{equation}
+\begin{equation}\label{sellerinversedemand}
     f^j(z) \triangleq \sup\big\lbrace y\ge 0:
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{singlevaluation}
     \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
 \end{equation}
-\begin{equation}
+\begin{equation}\label{buyervaluation}
     \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{sellervaluation}
     \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
@@
 \end{equation}
-\begin{equation}
+\begin{equation}\label{quantity}
     d_i^j \ge e_i^j(a)
 \end{equation}
-\begin{equation}
+\begin{equation}\label{budget}
     \displaystyle\sum_{i\in\mcI} e_i^j(a) \le \sum_{i\in\mcI} d^j_i \le D^j,
 \end{equation}
-\begin{equation}
+\begin{equation}\label{partialallocation}
     e_i^j(a) \le D^j - \sum_{k\in\mcI, k\ne i} e_k^j(a).
 \end{equation}
-\begin{equation}
+\begin{equation}\label{reserveprice}
    p_i^j \ge \min_{i\in\mcI}\big(p_i^j).

### 2019-09-26 Old/body_acm.tex
Work

--- 2019-08-21 save.tex
@@
-%\documentclass[journal,comsoc]{IEEEtran}
-\documentclass[sigconf, anonymous]{acmart}
-%\documentclass[12pt]{article}
-
-%\usepackage[text={6in,8.1in},centering]{geometry}
-
-%\usepackage{enumerate}
-%\usepackage{amsmath,amsthm,amssymb}
-%\usepackage{mathrsfs} % to use mathscr fonts
-
-%\usepackage{multicol}
-%\usepackage{url}
-
-%\usepackage{epstopdf}
-%\usepackage{caption,subcaption}
-%\usepackage{graphicx}
-%\usepackage{float}\usepackage{multicol}
-%\usepackage{multirow}
-%\usepackage{array}
-\usepackage{algorithmicx}
-\usepackage[noend]{algpseudocode}
-%\usepackage{changepage}
-%\usepackage{color}
-%\usepackage{listings}
-%\usepackage{fancyvrb}
-%\usepackage{verbatim,moreverb}
-%\usepackage{courier}
-\usepackage{algorithm}
-
-\newcommand{\vs}{\varsigma}
-\newcommand{\mcL}{\mathcal{L}}
-\newcommand{\mcI}{\mathcal{I}}
-\newcommand{\g}{\sigma}
-\newcommand{\s}{\nu}
-\DeclareMathOperator*{\argmax}{arg\,max}
-\DeclareMathOperator*{\argmin}{arg\,min}
-
-\iffalse
-
-\newtheorem{proposition}{Proposition}[section]
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{corollary}{Corollary}[section]
-\newtheorem{sublemma}{Lemma}[lemma]
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\headsep25pt\headheight20pt
-\setcounter{secnumdepth}{4}
-\pagestyle{fancyplain}
-\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
-\cfoot{\ \hfill\tiny\sl Draft printed on \today}
-\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
-
-\fi
- %\iffalse
-%---------------ACM CCS---------------------%
-\fancyhf{} % Remove fancy page headers 
-\fancyhead[C]{Jordan Blocher}% to ACM CCS 2017} % TODO: replace 9999 with your paper number
-\fancyfoot[C]{\thepage}
-
-\setcopyright{none} % No copyright notice required for submissions
-\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer
-and Communications Security}{Due 8 May 2018}{Dallas, Texas}
-\acmYear{2018}
-
-\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
-%-------------------------------------------%
-%\fi
-
-\begin{document}
-%\begin{multicols}{2}
-\title{Title?}
-
-\begin{abstract}
-
-%Verizon and At\&T, two major Internet service providers (ISPs), are offering
-%shared data plans, where multiple users may purchase and share a single pool of
-%data. 
-We propose a distributed, privacy-preserving auction-based approach to
-allocation in a secondary market for wireless data exchange.
-The secondary market is modeled as a fully connected, pure ``point of sale"
-market, with inital public platform provided by its parent wireless internet service
-provider (WISP). 
-The progressive second price (PSP) auction rules provide our underlying auction
-structure, allowing for a single degree of freedom, the reserve
-price. We suggest that data exchange markets allow for greater flexibility in
-mechanism design.
-We propose new, natural degrees of freedom, and derive modifiers
-to represent the deformation of the strategy space.
-
-Wireless users are modeled as a fixed type with dynamic incentives. Using a game
-theoretic analyis, we derive strategy profiles for wireless users
-based on their typed response to market dynamics, resulting in self-contained, self-balancing pricing system. 
-We examine mutations in the strategy space resulting from the new modifiers, and
-prove that the desired PSP properties hold. 
-Convergence is determined by set theory; we prove that the symmetry of our
-strategy space provides built-in conditions for convergence and stablility, finally arriving at a network Nash equlibirium.
-
-Trust and privacy issues in secondary markets have yet to be addressed.
-As rational users will not publicly reveal valuations, out users form coalitions to establish trust with local auctioneers.
-In a centrally moderated secondary market, an unregulated,
-rational ISP will prevent its secondary market from acting as a competitor.
-Competition is desired as it provides incentive for the ISP to protect
-and care for its end users.
-The distributed nature of PSP extends individual privacy to the secondary market,
-allowing for it to compete with its parent ISP. 
-\end{abstract}
-
-\iffalse
-% TODO: replace this section with code generated by the tool at https://dl.acm.org/ccs.cfm
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10002978.10003029.10011703</concept_id>
-<concept_desc>Security and privacy~Usability in security and privacy</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc{Security and privacy~Use https://dl.acm.org/ccs.cfm to generate actual concepts section for your paper}
-
-\keywords{template; formatting; pickling} % TODO: replace with your keywords
-\fi
-\maketitle
-
 \section{Introduction}
@@
 by the physical layer. 
-
-We focus on Vickery-Clark-Groves (VCG) type 
+In \cite{lazar}, Lazar and Semret introduced the Distributed Progressive Second Price (PSP)
+Mechanism for bandwidth allocation.
 auction mechanisms that are (1) easily distributed, and (2) allocate an infinitely
 divisible resource.
-In \cite{lazar}, Lazar and Semret introduce the Distributed Progressive Second Price (PSP)
-Mechanisms for bandwidth allocation. An auction mechanism is defined
+An auction mechanism is defined
 as distributed when the allocations at any element depend only on
 local state, no single entity holds a global market knowledge. We consider the
-multi-auction, where there are many auctioneers, each holding thier own local auction.
+multi-auction; each auctioneer is a user selling data to its peers.
 
@@
 Flexible data-sharing
-plans are similar to the CMHK market, where a limited number of devices may
+plans are similar to the CMHK market, a limited number of devices may
 share a single data plan. A shared-data plan, however limited, offers better economy
-by creating primary users with a service package with cellular, and a lot of data, and
+by creating primary users with a service package with cellular and a lot of data, and
 limited number of secondary users that are using only data \cite{att}.
@@
 trust the ISP.
-
 We therefore determine that our mechanism must be (3) globally and locally privacy-preserving.
-
-In a PSP mechanism, bids consist of (1) a quantity and
-(2) a unit-price. Buyers submit bids until an
-($\epsilon$-Nash) equilibrium is reached. 
-Our mechanism
-takes advantage of the opportunity for adaptation provided by the
-secondary market.
-
-The secondary market applies the PSP auction rules over a wireless network. The
-wireless users' data incentives create a pure ``point-of-sale" market. We prove
-that there exists a primary $\epsilon$-Nash market equilibrium that is
-the dominant strategy in the multi-auction system.
 
@@
 We claim that our formulation holds the desired PSP qualities,
-converging at a rate of $\mathcal{O}(\sum_{i\in\mcI}(\sum_{j\in\mcI}) \theta_i /
-\epsilon I!)$.
-We note that the convergence time is dependent on the ratio of
+%converging at a rate of $\mathcal{O}(\sum_{i\in\mcI}(\sum_{j\in\mcI}) \theta_i /
+%\epsilon I!)$.
+%We note that the convergence time is 
+and that our strategy profiles are natural; they depend on the ratio of
 supply and demand, or the ratio of buyers to sellers.
@@
 
-The paper is organized as follows... (TODO)
-
 \section{Related Work}
 
-Progressive second price auctions (PSPs) were proposed
-in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
-scheme to provide consistent services for network bandwith users.
-\cite{diffserve} conducts a game theoretic analysis, deriving
+Progressive second price auctions are used for optimal allocation in a
+variety of scenarios, and for different reasons. Different definitions of social
+welfare define different strategies. Typical goals of optimization are the
+maximization of revenue, and optimal allocation. Other papers' focus, taken from
+auction theory, optimize sellers' reserve price, or market price. Results derived from game theory
+focus on player strategy, as in this work. In \cite{qpsp}, user strategy gives a ``quantized"
+version of PSP, improving the rate of convergence of the game. Modifications to
+the mechanism that result in improved convergence also appear in \cite{burst},
+which relies on a global approximation function of demand.
+Another mechanism derived from game theory \cite{diffserve}, derives
 optimal strategies for buyers and brokers, and further shows the existence
-of networkwide market equilibria based on their game-theoretic
-model. Constructing necessary and sufficient conditions for the stability
-of the game allows the sustainability of any set
-of service level agreement configurations between Internet service
-providers.
-It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
-equilibria for differentiated services
-allocated between multiple agents when all players bid their real marginal valuation
-of the bandwidth resource. In other words, the PSP constraints are
-sufficient to attain the desirable property of truthfullness through incentive
-compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
-principle}, user $i$
-pays for its allocation so as to exactly cover the ``social opportunity cost"
-which is given by the declared willingness to pay (bids) of the users who are
-excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
-revenue \cite{lazar}.
-
-In \cite{zheng}, the ISP matches buyers and
-sellers to each other, and determines the amount
-of data that users can buy or sell. A buyer always pays her
-bid price for any data bought, and similarly a seller always
-receives his bid price, with any differences between the amounts
-paid and received acts as revenue for the ISP.
-%Then, the ISP will match buyers and sellers so as to optimize its revenue.
-
-Most previously studied data auctions aim to mitigate net-
-work congestion. For example, \cite{pubacs} considers a scheme in
-which users place bids on each transmitted data packet and the
-ISP admits packets in order of decreasing bids.
+of networkwide market equilibria by provisioning a dynamical system. The stability
+of the game may be implied by various equilibria in distributed systems.
+
+Allowing a user preference to, loosely, represent a policy, we may interpret
+a user preference from the data exchange market as a meta-policy. Then,  plans allow users to set their own policies, and rely existing
+framework for to implement their preferences. Several studies address the
+security of policy-based network management.
+Trusted management systems based on the
+Common Informtion Model (CIM) focus on policy-based management, namely,
+the ``Policy-Maker" toolkit. 
+In general, the translation of policy-based management systems to SDN focuses on combining
+the simplicity of policy-based implementation with the flexibility of SDN, as in the
+meta-policy system, CIM-SDN \cite{meta}.
+
+In the general context of distributed and decentralized allocation of
+resources, a variety of equilibria exist for heterogeous and homogenous services
+with the similar condition of truthfulness. In all cases, the PSP constraints are
+sufficient to attain the desirable property of truthfulness through incentive
+compatibility, as the pricing mechanism upholds the exclusion-compensation
+principle.
 
@@
 associated opponent profiles.
-\iffalse
-(HERE)
-Additionally, we assume that a user's budget is 
-sufficient, as the alternative is to pay the overage fee to the ISP, but as we
-assume a rational user.
-\fi
 
@@
 the ISP as a blind, deaf user $\kappa$, who does not participate
-in any auctions, but nonetheless holds the power to create a monopoly. At time
-$t=0$, a seller $j$ entering the market will
-submit bid $\s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
-platform, and so the initial bid $\s_\kappa^j$, is public knowledge.
-
+in any auctions, but nonetheless holds the power to create a monopoly
+.
 We assume that buyers and sellers are
@@
 $j\in\mcI$.
-Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
+Suppose $i$ is buying from $j$. We assume that a user's budget is 
+sufficient, as the alternative would be to pay a higher price to the ISP. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
 meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
@@
 selfishness}, (3) \emph{social welfare maximization}, and (4)\emph{the winning
-bid is private}. For the secondary data exchange
+bid is persistent private information}. For the secondary data exchange
 market, we determine that the
@@
 \emph{minimize crossover in buyer/ seller pools}.
-Thus, we propose a design to replace centralized data exchange
-markets, e.g. 2cm..
-
-There is a clear need for privacy in the secondary data exchange market. In \cite{zheng},
+Thus, we propose a mechanism that promotes social welfare. 
+Thus our motivation to adapt the PSP auction. The PSP auction given in
+\cite{lazar} is comprised of a set of simple and symmetric rules that closely
+follow market theory, and as it is distributed we can require privacy.
+
+We first address the clear need for privacy in the secondary data exchange market. In \cite{zheng},
 it is assumed that the ISP interferes in 2cm (market) dynamics, and will maximize the
@@
 revenue. We notice that this market behavior is suspiciously monopolistic, as a
-single entity holds the global market power. It is further claimed in
+single entity, the ISP, holds a global market power. It is further claimed in
 \cite{zheng} that user bids are truthful as they are guaranteed to receive
@@
 Thus, in the interest of social good, we aim to provide a method to arrest
-anti-competitive conduct by ISPs. Thus our motivation to adapt the PSP auction,
-as it is easily distributed, and further has the property that user valuation
-functions are private. We propose an alternative to the centralized data
-exchange market that will prevent the exploitation of wireless users by their ISPs.
-
-We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
-part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
-will determine its bid quanities by,
-\begin{equation}\label{opt-out}
-    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
-\end{equation}
-In a general sense, $\g_i$ applies our user strategy to the PSP rules.
-
-\subsubsection{Truthfulness.}
-We prove that the dominant strategy for buyers is to submit coordinated bids,
-where all bids the buyer submits are equal. Our motivation for coordinated bids
-comes from the idea of potential games \cite{shapely}. In potential games, the
-incentive of all users to change strategy can be expressed as a single global
-function. We map the incentive of a buyer over all auctions $j\in\mcI$ to a
-single potential function. This is a standard method that is used often, as it
-simplfies the analysis of both strategy and auction design. 
-We define the composition,
-$$
-     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity. We will prove that for each
-buyer $i\in\mcI$ that $g_i^j(a)$ is equal $\forall \ j$. Finally, we prove the necessary condition of an $\epsilon$-best
-reply: a new bid price must differ from the last by at least $\epsilon$.
-Thus, our strategic bid is an $\epsilon$-best response.
-
-\subsubsection{Individual rationality.}
-We prove that a buyer cannot have a negative utility. Our
-strategic framework creates an incentive for the seller to maintain a local
-equilibrium, where supply equals demand. 
-We define the reserve price for seller $j$ as,
-\begin{equation}\label{newprice}
-    p_*^{j} = p_{i^*}^{j} + \epsilon,
-\end{equation}
-where $i^*$ is the highest losing bidder with respect to bid price.
-We claim that the choice of reserve price $p_*^j$ does not force any buyers out
-of the local auction. 
-A truthful bid implies that the new bid price differs from the last bid price by at least
-$\epsilon$. As a seller must distribute bid vectors to all
-buyers in its auction, we reason that the seller may employ a strategic caveat.
-The seller will notify a buyer who is subject to a market shift by changing its
-bid at the appropate index, and provide a proof by cases.
-
-\subsubsection{Social welfare maximization.}
-We claim that this is a natural consequence of PSP. Additionally,
-the mechanism is self-contained, and as prices are derived from market dynamics, there cannot be any nefarious or
-criminal entity negatively influencing the market.
-
-In the original bandwidth-sharing model, the allocation role defines the active edges in a network for a particular bidder. 
-The flexibily of correspondance, and
-the ability for instantaneous communication in the distributed wireless network, allows for a more general, and
-thus adaptive strategy. We therefore introduce additional restrictions on
-defining properties of PSP multi-auctions, and claim they are normal.
+anti-competitive conduct by ISPs. Then, we may trust the ISP. Naturally,
+rational users will only purchase data if the rewards outweigh the risk, it follows that
+the secondary auction should be trusted as well. 
+We argue that as the mechanism is also privacy-preserving, that both the users and the ISP benefit.
+An ISP that is trusted will end up with a loyal customer base, taking profit
+from to one that is revenue maximizing, assuming that competion laws will
+prevent a monopoly.
+
+We define a value to be private if any coalition is incapable of learning any information
+besides what can be inferred from the shared computation and the coalition’s
+inputs. We describe the process as given in \cite{felix}. In general, a distributed private
+computation, where buyer $i$ is part of a coalition comprising auction $j$, is as follows:
+
+Denoting $m_{-i} = [(s_i^j, r_i), m_1, \cdots, m_n]_{k\ne i\in \mcI}$, buyer sends a
+message to each of its opponents, where $s_i^j$ is $i$'s bid, $r_i$
+is an independent random value, and $m_1, \cdots, m_n$ the messages $i$ has
+received so far.
+Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$.
+
+The
+private computation process requires that buyers connect with each other, and
+so reveal their identities to the coalition. It was proven in \cite{felix} that full privacy is not possible in a second
+price auction, even if we allow partial relevation and weak coalitions. Yet, we
+claim that our mechanism is trustworthy:
 
 \subsubsection{Buyers are anonymous}
-We have that any local auction is anonymous by definition, as a permutation of
+In our secondary market, we have that any local auction is anonymous by definition, as a permutation of
 the valuations resutls in a permutation of allocations and prices, equivalently,
@@
 Formally,
-\definition{(Anonymous auction)} \cite{???}
+\definition{(Anonymous auction)} \cite{felix}
 Given an auction $j$ and buyers $i\in\mcI$, a protocol for computing
@@
 
-\subsubsection{The winning bid is private.}
+\subsubsection{The winning bid is persistent private information.}
 We claim that a buyer's trust in a local auction is fufilled when the outcome of
-the auction is guaranteed to be correct, and if the buyers' identity is secret.
-We define a value to be private if any coalition is incapable of learning any information
-besides what can be inferred from the shared computation and the coalition’s
-inputs \cite{felix}. For each local auction, we define a coalition of the
+the auction is guaranteed to be correct, and if the winner's identity is secret.
+For each local auction, we define a coalition of the
 participating buyers. The winning bidder is \emph{privately} chosen by
-distributing the computation of the winner to the local coalition.
-
-We follow the process given in \cite{felix}. In general, a distributed private
-computation is as follows: Denoting $m_{-i} = [(s_i^*, r_i), m_1, \cdots, m_n]_{k\ne i\in \mcI}$, buyer sends a
-message to each of its opponents, where $s_i^*$ is $i$'s bid, $r_i$
-is an independent random value, and $m_1, \cdots, m_n$ the messages $i$ has
-received so far.
-Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$.
+distributing the computation of the winner to the local coalition. The
+computation is based on the homomorphicity of secret sharing. We present the
+Lemma in its general form,
+{
+\lemma{(Benaloh 1987)}\label{modp} \ 
+    $f(x_1, x_2, \cdots, x_n) = \sum_{i=1}^n x_i \mod p$ is privately
+    computable.
+}
+Thus, it is possible to privately compute,
+\begin{equation}\label{winner}
+    \omega = \max([p_i^j]_{i\in\mcI^j}) = (p_1^j, p_2^j, \cdots, p_n^j, \argmax(p^j).
+\end{equation}
+We have the following procedure determining the winner of auction $j$ for
+some fixed time in the bid progression, where $D^j > 0$.
+% PRIVACY
+\begin{center}
+\begin{algorithm}
+\caption{(Max bid private computation)}
+\begin{algorithmic}[1]\label{maxbidcomp}
+\State $\omega\gets 1, e\gets 0$
+\While{$e \le 1$}
+\For{$i \in \mcI^j$}
+\If{$p_i^j \le \omega$}
+\State $p_i^j \gets 1 $
+\Else
+\State $p_i^j \gets 0$
+\EndIf
+\EndFor
+\State $e = \sum_{i\in\mcI^j} p_i^j \mod (n+1)\quad$ (Lemma \ref{modp})
+\For{$i \in \mcI^j$}
+\If{$p_i^j \ge e$}
+\Return $i \ (winner)$
+\EndIf
+\EndFor
+\EndWhile\\
+\end{algorithmic}
+\end{algorithm}
+\end{center}
+
+The winning buyer then leaves the auction, and so we have that the privacy of
+the winning bid is persistent. We note that it is possible for a winner to
+anonymously rejoin an auction, however this does not alter our result.
 
 \subsubsection{Privacy and independence from the ISP.}
-In our model, free-market exchange is protected as privacy is integrated into the
-mechanism. Our design enforces privacy by a (HERE) The, the auction
-begins at time $t>0$, and at $t=0$, $j$ will,
-initializing its reserve price by holding a single bid iteration.
+In our model, privacy is integrated into the mechanism. Our design enforces
+privacy by hiding the reserve price of the sellers. At time
+$t=0$, a seller $j$ entering the market will
+submit bid $\s_\kappa^j =(D^j, \epsilon)$ to the public data exchange
+platform, and so the initial bid $\s_\kappa^j$, is public knowledge. 
+The auction
+begins at time $t>0$, and at $t=0$, $j$ will
+initializing its reserve price by executing a single bid iteration.
 Sellers do not update pricing information with the ISP, thereby hiding
@@
 
-\subsubsection{Locally fair division.}
-We claim that the allocation $a$ by seller $j$ for a local auction at
-equilibrium is an equitable division, where each buyer equally values their
-portion of the allocation. We have,
-$$
-    \displaystyle\int_0^{\g_i^j(a)} f_i(z) \ dz = \int_0^{\g_k^j(a)} f_k(z) \ dz,
-$$
-which follows from Proposition \ref{userunion}.
-
-Let $i,k$ be buyers in auction $j$, and let $\vert\mcI^j\vert = 2$. Suppose $j$
-is at equilbrium, i.e. $\g(a)_i^j + \g(a)_k^j = D^j$. From the buyer valuations,
-$\theta_i$ and $\theta_k$ over $[0, D^j]$, we have bid quantities $z_i, z_k$
-representing a $50-50$ division. We follow the surplus procedure \cite{???}.
-Let $z_i < z_k$ and let $z_{ik}$ be the point in $[z_i, z_k]$ such that
-
-we have that $\theta_i(g_i^j(a)) =
-\theta_k(\g_k^j(a)$. Each buyer recieves an allocation based on their valuation.
-
-In the case where a buyer $i\in\mcI^j$ changes strategy such that
-$\theta_i - \theta_k < \epsilon$ for some $k\in\mcI^j$, it follows that
-
-\subsubsection{Minimize crossover in buyer/ seller pools.}
-Buyer $i$'s seller pool is determined by minimizing $n$, and is the smallest set of sellers that
-allows for a coordinated bid, and the aggragate bids satisfy its demand, $D_i$.
-\begin{align}
-\begin{split}\label{buyercoordinate}
-    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
-\end{split}
-\end{align}
-Similarly, seller $j$ determines the minimal set of buyers that maximizes revenue and
-sells all of its data, $D^j$.
-\begin{equation}\label{sellercoordinate}
-    \min\bigg\lbrace n \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(n)}d_i^j
-\ge D^j \bigg\rbrace,
-\end{equation} 
-We further determine that the set of buyers and sellers participating
-in a single equilibrium is bounded by the potential indirect costs of
-participation. We will denote this individual cost to each user as
-$\varrho$. The indirect cost is the portion of the bid fee
-$\epsilon$ that is dependent on the underlying network and the individual.
-Observing that $\varrho$ indirectly effects user utility,
-and therefore acts to establish a natural budget for each user. We give this
-constraint as, 
-\begin{equation}\label{poolbnd}
-    u \le \varrho,
-\end{equation}
-which may be interpreted as the effort a rational user is willing to expend
-on its message space, and serves to limit the size of the buyer/seller pools. 
-This information may be collected from a specific
-device's configuration, i.e. enabled roaming, daily data restrictions.
-It is clear that an unconstrained
-market, even with a finite number of users, could suffer from the
-expense of many local auctions trading an infinitely divisible resource, thus
-$\varrho$ is interpreted as
-the ``liability" component of $\epsilon$ attempts to regulate network congestion.
-
-In order derive a distributed PSP implementation that arrives at an optimal
-objective,
-we analyze the behavior of users in a dynamical data exchange market. 
-Buyers and sellers are able
-to change their bid strategies asychronously and serially, using local information to determine their strategy. 
-A users' local strategy space is therefore nondeterministic, and the prefererences of users
-are subject to change, i.e. binary dependence.
-Then, from \emph{Arrow's Theorem}, we have that no deterministic strategy can
-provide a mapping of the preferences of users into a market-wide (complete
-and transitive) strategy. As individual bids cannot map to a general objective, a better market
-position can only be determined by an adaptive strategy.
-We define a move to a better market position to be synonymous with a
-strategic bid. \\ 
-\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
-from auction design and game theory, respectively.\\
-
-\section{Strategic Framework}
-
-\subsection{User Valuation}
-
-We address the market risks and securities in our secondary data exchange market. 
-We provide a game-theoretic model of a real market progression, which we use to
-derive, then define, adaptive variables. 
-Assuming equal bandwidth for all users, and derive a globally optimal strategy suited for
-users with local information in a distrubuted data-sharing model.
-
-Our mechanism allows a buyer
-to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
-utility while minimizing the number of positive bids submitted to the overall
-market. 
-% OPT-OUT BUYER
-We define each buyer as a user $i\in\mcI$ with quasi-linear utility
-function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
-\begin{equation}\label{buyerutility}
-    u_i = \theta_i \circ (\g_i(a)) - c_i,
-\end{equation}
-where the composition of the elastic valuation function $\theta_i$ with $\g_i$
-distributes a buyers' valuation of allocation $a$ across local markets (and thus
-multiple sellers).
-In this way we extend the PSP rules described
-in \cite{semret} to design equilibria across subsets of local data-exchange markets.
-
-The sellers, $j\in\mcI$ are not associated with an opt-out function, we
-consider their valuation to be a functional extension of the buyers, where
-$\theta^j$ is constructed by buyer demand.
-The sellers strategy can only be to determine the reserve price of their local
-auction, using only information from buyers who have not opted out.
-In our analysis, we demonstrate market dynamics, and further show evidence of symmetry in the strategies of
-buyers and sellers.
-
-\subsubsection{Valuation under Market Dynamics}
-The buyer demand largely motivates the market price function, however, the
-distributed nature of the market prevents any single user from knowing the
-market demand for a quantity of data. All users have knowledge of market
-supply, as this is public information, however only buyers
-are able to determine supply or demand across multiple auctions, and then only from auctions
-in which they participate. \\
-\textbf{Remark:}
-It is possible that a seller would be able to derive information about other
-auctions by examining buyer bids over time, particularly if the seller had
-knowledge of the buyer strategy. In this work, we assume sellers are unable to derive opponent information from buyer bids. \\
-
-We interpret the collection of local auctions as collection of strategic games
-of incomplete but perfect information,
-where a buyers' payoff depends on the dynamics of the set of local auctions it
-``chooses".
-In a multi-auction market, each auction a buyer joins has the potential to
-decrease the potential cost of its data. However, increasing the size of the
-auction implies a certain risk, which we may interpret as a potential and
-definite
-liability. Increasing the number of transactions causes additional messaging
-overhead, fees, and increased competition from other buyers. 
-A transaction also causes potential indirect costs, which may be considered work done to find
-sellers, or effort of communication from participation. A seller
-has the potential for greater profit with each new buyer in its auction, taking 
-the same risk.
-%We define this cost to be separate from the bid fee $\epsilon$, as it is dependent on the underlying network
-%and the individual. We denote the potential indirect costs of participation of
-%each user as $\varrho$.
-The liability of any user is naturally absorbed into the bid fee $\epsilon$,
-as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
-dependent on the association between two users and their market positions, in
-addition to the underlying network structure. Now, both sellers and buyers must consider
-the cost of adding additional users to their subsequent pools. (MODEL SEPARATE,
-OR DYNAMIC, TO OPTIMIZE SIZE OF SUBSETS?)
-
-Elastic valuation functions allow for even infinitesimal changes in the market
-dynamics to be modeled. This, and the homogenous nature of data in the CMHK market, 
-allows for the analysis of constraints imposed by the user strategies. 
-Buyers may directly impact each other in local market intersections.
-Thus our motivation to begin our analysis with buyer valuation $\theta_i$.
-A buyers' valuation of an amount of data represents how much a buyer is willing
-to pay for that amount. 
-This is equivalent to the bid price, given a fixed amount of data,
-satisfying $\theta_i$. We determine the
-buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
-possible unit price. We have,
-% BUYER PRICING 
-\begin{equation}\label{buyerinversedemand}
-    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
-        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
-\end{equation}
-where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
-$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
-We determine that the market supply function corresponds to an extreme of
-possible buyer demand, and 
-acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
-% BUYER DEMAND 
-\begin{equation}\label{datasupply}
-    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
-\end{equation}
-We note that $f_i$ is such that
-$i$ could still bid in \emph{any} auction $j\in\mcI$.
-Therefore, in a coordinated bid, the utility-maximizing bid price is the
-lowest unit cost of the buyer to participate in all auctions, and corresponds to
-the maximum reserve price amongst the sellers. 
-%We will later show, in Proposition
-%\ref{buyercoordinate}, that a buyer does not lose utility from coordinating its
-%bids, i.e. using the same bid for all auctions.
-
-A seller only has
-information from buyers in its own auction, and may only be indirectly influenced by
-buyers in other auctions. So from the perspective of the
-seller we have a more direct interpretation of valuation as revenue.
-We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
-% BUYER DEMAND 
-\begin{equation}\label{datademand}
-    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} \g_i^j(a), 
-\end{equation}
-and define the ``inverse" of the buyer demand function for seller $j$ as
-potential revenue at unit price $y$, we have, 
-% SELLER REVENUE 
-\begin{equation}\label{sellerinversedemand}
-    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
-        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
-\end{equation}
-and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
-price.
-
-The valuation of any user must be modeled as a function of the entire
-marketplace. 
-Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
-\circ \g_i$ as the valuation of the buyers.
-We further show that user valuation satisfies the conditions for an
-elastic demand function, with valuations based on
-(\ref{datademand}) and (\ref{sellerinversedemand}). 
-\definition{(Elastic demand) \cite{lazar}}
-A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
-function} on $[0, D]$ if 
-\begin{itemize}
-    \item $\theta(0) = 0$,
-    \item $\theta$ is differentiable,
-    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
-     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
-${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
-{\theta}'(\eta)
-- \gamma(z - \eta)$. 
-\end{itemize}
-We first note that, in
-general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
-$$
-    \theta(x) = \int_0^x f(z) \ dz,
-$$ 
-as in \cite{semret}. Now, we have the following Lemma,
-{
-\lemma{(User valuation)}\label{uservaluation}
-For any buyer $i\in\mcI$, the valuation of a potential
-allocation $a$ is, 
-\begin{equation}\label{buyervaluation}
-    \theta_i \circ \g_i(a) = \displaystyle\sum_{j\in\mcI}
- \int_0^{\g_i^j(a)} f_i(z) \ dz.
-\end{equation}
-Now, we may define seller $j$'s valuation in terms of revenue,
-\begin{equation}\label{sellervaluation}
-    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ \g_i^j(a) = \sum_{i\in\mcI}
- \int_0^{\g_i^j(a)} f^j(z) \ dz.
-\end{equation}
-We have that $\theta_i$ and $\theta^j$ are elastic valuation functions, with
-derivatives
-${\theta_i}$ and ${\theta^j}'$ satisfing the conditions of elastic demand.
-}
-\textbf{Proof:} 
-Let $\xi$
-be a unit of data from buyer bid quantity $\g_i^j(a)$.
-If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
-similarly decrease. The lost potential revenue for seller $j$ is the price of
-the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
-$$
-    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
-$$
-Thus (\ref{sellervaluation}) holds.
-As we may use the same argument for (\ref{buyervaluation}), as such, we will
-denote $f_i=f^j=f$ for the remainder of the proof. We observe that the function
-$f$ is the first
-derivative of the valuation function with respect to
-quantity. Letting $\theta_i=\theta^j=\theta$, the existence of the derivative implies $\theta$ 
-is continuous, and therefore, in this context, $f$ represents
-the marginal valuation of the user, ${\theta}'$. Also, clearly
-$\theta(0)=\theta(\sigma(0)) = 0$. Now, as we consider data to be an infinitely
-divisible resource, we have a continuous interval between allocations $a$ and
-$b$, where $a\le b$. Now, as $\theta$ is continuous, for some $c\in[a,b]$, 
-$$
-\theta'(c) = \lim_{x\to c}\frac{\theta(x) - \theta(c)}{x-c} = f(c),
-$$
-and so $f=\theta'$ is continuous at $c\in[a,b]$, and so as $a\ge 0$, 
-$\theta'\ge 0$. Finally, we have that concavity follows from the demand
-function. Then, as $\theta'$ is
-non-increasing, we may denote its derivative $\gamma \le 0$,
-and taking the derivative of the Taylor approximation, we have, $\theta'(z) \le
-\theta'(\eta) + \gamma(z-\eta)$.
-$\qed$
-
-Utility is defined by their valuation, and is the basis for user behavior. 
-The sellers' natural utility is the potential
-profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
-paid to the ISP, as it is not a component of our mechanism, and as a discussion
-of mobile data plans is outside the scope of this paper.  
-Now, a rational user will try
-to maximize its utility, thus, user incentive manifests as a
-response to market dynamics. A buyer has the choice to
-opt-out of any auction, and as a seller will try to sell the maximum amount of
-data, the highest possible reserve price is conditioned by ``natural" constraints. Utility-maximization 
-acts as revenue maximization for a rational seller, and as cost minimization for a
-rational buyer. Thus, for each user $p_i^j \ge \min\big(p_i^j)$ and $p_i^j \le
-\max\big(p_i^j)$, which holds $\forall \ i, j\in\mcI$ such that $s_i^j>0$.
-Now, rational buyer does not want to purchase extra data, as this would be
-equivalent to overpaying, however $i$ submits positive bids to a set of
-sellers, and a rational seller will attempt to maximize profit, and so will try and sell all of
-its data. Therefore,
-\begin{equation}\label{bidcap}
-    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j \quad\text{and}\quad
-\sum_{j\in\mcI} d^j_i \ge D_i,
-\end{equation}
-which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
-constraint from our formulation.
-Thus, at equilibrium all users are satisfied, and 
-$D^j = D_i$, although we observe that this result
-does \emph{not} imply that $s_i=s^j$.
-
-Finally, it is worth mention that the \emph{analysis} of the auction as
-a game assumes some forms of demand and supply, in order to derive properties.
-The mechanism itself does not require any knowledge of user demand or
-valuation. 
-\subsection{PSP for Data-Exchange}
-
+We now proceed to formally define the PSP auction, which determines the actions 
+buyers and sellers in the secondary market, and which we will denote the \emph{data}
+PSP rules. 
+We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
+part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
+will determine its bid quanities by,
+\begin{equation}\label{opt-out}
+    \g_i(a) = [\g_i^j(a)]_{j\in\mcI}.
+\end{equation}
+In a general sense, $\g_i$ applies our user strategy to the PSP rules.
+
+%\subsection{PSP for Data-Exchange}
 % MECHANISM
-\subsubsection{Data Auction Mechanism}\label{datamechanism}
-We now proceed to formally define the PSP auction, which determines the actions 
-buyers and sellers in the CMHK market, and which we will denote the \emph{data}
-PSP rules. The rules presented here incorporate of the opt-out function with the
+\subsubsection{The Mechanism}\label{datamechanism}
+The rules presented here incorporate of the opt-out function with the
 mechanism as in \cite{lazar}, which we note greatly simplifies our
 analysis. 
-The market price function (MPF) for a buyer in the CMHK market
+The market price function (MPF) for a buyer in the secondary market
 can be described as follows:
@@
 order to obtain
-data amount $z$ given opponent profile $s_{-i}$. We note that
-the total minimum price for the buyer must be an aggragation of the
-\emph{individual} prices of the buyers as it is possible that the reserve prices
-of the individual sellers may vary.\\
+data amount $z$ given opponent profile $s_{-i}$. We note that in the following
+analysis
+the total minimum price for the buyer cannot be an aggragation of the
+\emph{individual} prices of the buyers, as it is possible that the reserve prices
+of the sellers may vary.\\
 \textbf{Remark:} We further note that except at points of discontinuity, from
 Lemma \ref{uservaluation} we have that $P_i^j(z) = f_i(z)$. \\
+\iffalse
 (THE ABOVE IS GOOD, BUT DOESN'T FIT MY CONSTRUCTION, CHANGE TO BELOW?)
-The market price function (MPF) for a buyer in the CMHK market
+The market price function (MPF) for a buyer in the secondary market
 is determined per (\ref{buyerinversedemand}), and is defined as,
@@
 %buyer $i$'s bid quantity. 
+\fi
 The maximum available quantity of data in auction
@@
 \begin{split}\label{datacomposed}
-    \bar{D}_i^j(y,s_{-i}^j) &= \g_i^j \circ D_i^j( y,s_{-i}^j)\\
-    &= \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
+    \bar{D}_i^j(y,s_{-i}^j) = \g_i^j \circ D_i^j( y,s_{-i}^j)
+    = \bigg\lbrack D^j - \sum_{p_k^j> y} \g_k^j(a)\bigg\rbrack^+.
 \end{split}
@@
 
-The formulation is inspired to the thinnest allocation route for
-bandwidth given in \cite{lazar}. We note that if a single seller $j$ can
-satisfy $i$'s demand, then
-(\ref{buyerutility}) reduces to the original form, defined in
-\cite{semret} as ``a simple buyer at a single resource element".
-
-(OWN WORDS!)
-The cost function will therefore be a stepwise-linear function, which is
-increasing in slope with each new bidder excluded from the market.
+%The formulation is inspired to the thinnest allocation route for
+%bandwidth given in \cite{lazar}. 
+%We note that if a single seller $j$ can
+%satisfy $i$'s demand, then
+%(\ref{buyerutility}) reduces to the original form, defined in
+%\cite{semret} as ``a simple buyer at a single resource element".
+
+\subsubsection{Truthfulness.}
+We will prove that the dominant strategy for buyers is to submit coordinated bids,
+where all bids the buyer submits are equal. Our motivation for coordinated bids
+comes from the idea of potential games. In potential games, the
+incentive of all users to change strategy can be expressed as a single global
+function. We map the incentive of a buyer over all auctions $j\in\mcI$ to a
+single potential function. This is a standard method that is used often, as it
+simplfies the analysis of both strategy and auction design. We will prove the necessary condition of an $\epsilon$-best
+reply: a new bid price must differ from the last by at least $\epsilon$.
+Thus, our strategic bid is an $\epsilon$-best response.
+
+%\section{Strategic Framework}
+\subsection{User Valuation (Strategic Incentive)}
+
+We define a move to a better market position to be synonymous with a
+strategic bid. \\ 
+\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
+from auction design and game theory, respectively.\\
+Our mechanism allows a buyer
+to \emph{opt-out} of auctions by submitting zero bids. This strategy maximizes
+utility while minimizing the number of positive bids submitted to the overall
+market. 
+% OPT-OUT BUYER
+We define each buyer as a user $i\in\mcI$ with quasi-linear utility
+function $u_i = [u_i^j]_{j\in\mcI}$, a buyers' utility function is of the form,
+\begin{equation}\label{buyerutility}
+    u_i = \theta_i \circ \g_i(a) - c_i,
+\end{equation}
+where the composition of the elastic valuation function $\theta_i$ with $\g_i$
+distributes a buyers' valuation of allocation $a$ across local markets (and thus
+multiple sellers).
+In this way we extend the PSP rules described
+in \cite{semret} to design equilibria across subsets of local data-exchange markets.
+
+The sellers, $j\in\mcI$ are not associated with an opt-out function. We
+consider their valuation to be a functional extension of the buyers, where
+$\theta^j$ is constructed from buyer demand.
+The sellers' strategy can only be to determine the reserve price of their local
+auction, using only information from buyers who have not opted out.
+\\
+\textbf{Remark:}
+It is possible that a seller would be able to derive information about other
+auctions by examining buyer bids over time, particularly if the seller had
+knowledge of the buyer strategy. In this work, we assume sellers are unable to
+derive opponent information from buyer bids. \\
+
+Elastic valuation functions allow for even infinitesimal changes in the market
+dynamics to be modeled. We give the definition for an elastic valuation
+function as in \cite{lazar}.
+\definition{(Elastic demand) \cite{lazar}}
+A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
+function} on $[0, D]$ if 
+\begin{itemize}
+    \item $\theta(0) = 0$,
+    \item $\theta$ is differentiable,
+    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
+     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
+${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
+{\theta}'(\eta)
+- \gamma(z - \eta)$. 
+\end{itemize}
+
+The elastic valuation of users and homogenous nature of data in the secondary market, 
+allows for continuity of constraints imposed by the user strategies. 
+We begin our analysis with buyer valuation $\theta_i$.
+A buyers' valuation of an amount of data represents how much a buyer is willing
+to pay for that amount. 
+This is equivalent to the bid price, given a fixed amount of data,
+satisfying $\theta_i$. We determine the
+buyers' utility-maximizing bid given quantity $z\ge0$ to be a mapping to the lowest
+possible unit price. We have,
+% BUYER PRICING 
+\begin{equation}\label{buyerinversedemand}
+    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
+        \rho_i(y) \ge z, \ \forall \ j \in \mcI\big\rbrace,
+\end{equation}
+where $\rho_i(y)$ represents the demand function of buyer $i$ at bid price
+$y\ge 0$, and gives the quantity that buyer $i$ would buy at a given price.
+We determine that the market supply function corresponds to an extreme of
+possible buyer demand, and 
+acts as an ``inverse" function of $f_i$. We have, for bid price $y\ge 0$,
+% BUYER DEMAND 
+\begin{equation}\label{datasupply}
+    \rho_i(y) = \sum_{j\in\mcI : p_i^j\ge y} D^j.
+\end{equation}
+We note that $f_i$ is such that
+$i$ could still bid in \emph{any} auction $j\in\mcI$.
+Therefore, the utility-maximizing bid price is the
+lowest unit cost of the buyer to participate in all auctions, and corresponds to
+the maximum reserve price amongst the sellers.
+
+From the perspective of the
+seller we have a more direct interpretation of valuation as revenue.
+We determine the demand function of seller $j$ at reserve price $y\ge 0$ to be,
+% BUYER DEMAND 
+\begin{equation}\label{datademand}
+    \rho^j(y) = \sum_{i\in\mcI : p_i^j\ge y} \g_i^j(a), 
+\end{equation}
+and define the ``inverse" of the buyer demand function for seller $j$ as
+potential revenue at unit price $y$, we have, 
+% SELLER REVENUE 
+\begin{equation}\label{sellerinversedemand}
+    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
+        \rho^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
+\end{equation}
+and, unsurprisingly, $f^j$ maps quantity $z$ to the highest possible unit data
+price.
+
+The valuation of any user must be modeled as a function of the entire
+marketplace. 
+Naturally, a buyers' valuation is aggragated over local markets, and the
+sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
+\circ \g_i$ as the valuation of the buyers.
+We further show that user valuation satisfies the conditions for an
+elastic demand function, with valuations based on
+(\ref{datademand}) and (\ref{sellerinversedemand}). 
+We first note that, in
+general (and so we omit the subscript/superscript notation), the valuation of data quantity $x\ge 0$ is given by,
+$$
+    \theta(x) = \int_0^x f(z) \ dz,
+$$ 
+as in \cite{semret}. Now, we have the following Lemma,
+{
+\lemma{(User valuation)}\label{uservaluation}
+For any buyer $i\in\mcI$, the valuation of a potential
+allocation $a$ is, 
+\begin{equation}\label{buyervaluation}
+    \theta_i \circ \g_i(a) = \displaystyle\sum_{j\in\mcI}
+ \int_0^{\g_i^j(a)} f_i(z) \ dz.
+\end{equation}
+Now, we may define seller $j$'s valuation in terms of revenue,
+\begin{equation}\label{sellervaluation}
+    \theta^j= \displaystyle\sum_{i\in\mcI} \theta^j \circ \g_i^j(a) = \sum_{i\in\mcI}
+ \int_0^{\g_i^j(a)} f^j(z) \ dz.
+\end{equation}
+We have that $\theta_i$ and $\theta^j$ are elastic valuation functions, with
+derivatives
+${\theta_i}$ and ${\theta^j}'$ satisfing the conditions of elastic demand.
+}
+\proof{
+Let $\xi$
+be a unit of data from buyer bid quantity $\g_i^j(a)$.
+If $\xi$ decreases by incremental amount $x$, then seller bid $d_i^j$ must
+similarly decrease. The lost potential revenue for seller $j$ is the price of
+the unit times the quantity decreased, by definition, $f^j(\xi)x$, and so,
+$$
+    \theta^j(\xi) - \theta^j(\xi-x) = f^j(\xi)x.
+$$
+Thus (\ref{sellervaluation}) holds.
+As we may use the same argument for (\ref{buyervaluation}), as such, we will
+denote $f_i=f^j=f$ for the remainder of the proof. We observe that the function
+$f$ is the first
+derivative of the valuation function with respect to
+quantity. Letting $\theta_i=\theta^j=\theta$, the existence of the derivative implies $\theta$ 
+is continuous, and therefore, in this context, $f$ represents
+the marginal valuation of the user, ${\theta}'$. Also, clearly
+$\theta(0)=\theta(\sigma(0)) = 0$. Now, as we consider data to be an infinitely
+divisible resource, we have a continuous interval between allocations $a$ and
+$b$, where $a\le b$. Now, as $\theta$ is continuous, for some $c\in[a,b]$, 
+$$
+\theta'(c) = \lim_{x\to c}\frac{\theta(x) - \theta(c)}{x-c} = f(c),
+$$
+and so $f=\theta'$ is continuous at $c\in[a,b]$, and so as $a\ge 0$, 
+$\theta'\ge 0$. Finally, we have that concavity follows from the demand
+function. Then, as $\theta'$ is
+non-increasing, we may denote its derivative $\gamma \le 0$,
+and taking the derivative of the Taylor approximation, we have, $\theta'(z) \le
+\theta'(\eta) + \gamma(z-\eta)$.
+$\qed$}
+
+The sellers' natural utility is the potential
+profit, or simply $u^j = \theta^j$, where we have chosen to omit the original cost of the data
+paid to the ISP, as it is not a component of our mechanism, and as a discussion
+of mobile data plans is outside the scope of this paper.  
+Now, a rational user will try
+to maximize its utility, thus, user incentive manifests as a
+response to market dynamics. A buyer has the choice to
+opt-out of any auction, and as a seller will try to sell the maximum amount of
+data, the highest possible reserve price is conditioned by ``natural" constraints. Utility-maximization 
+acts as revenue maximization for a rational seller, and as cost minimization for a
+rational buyer. Thus, for each user $p_i^j \ge \min\big(p_i^j)$ and $p_i^j \le
+\max\big(p_i^j)$, which holds $\forall \ i, j\in\mcI$ such that $s_i^j>0$.
+Now, rational buyer does not want to purchase extra data, as this would be
+equivalent to overpaying, however $i$ submits positive bids to a set of
+sellers, and a rational seller will attempt to maximize profit, and so will try and sell all of
+its data. Therefore,
+\begin{equation}\label{bidcap}
+    \displaystyle\sum_{i\in\mcI} \g_i^j(a) \ge D^j \quad\text{and}\quad
+\sum_{j\in\mcI} d^j_i \ge D_i,
+\end{equation}
+which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
+constraint from our formulation.
+Thus, at equilibrium all users are satisfied, and 
+$D^j = D_i$, although we observe that this result
+does \emph{not} imply that $s_i=\nu^j$.
+
+Finally, it is worth mention that the analysis of the auction as
+a game assumes some forms of demand and supply, in order to derive properties.
+The mechanism itself does not require any knowledge of user demand or
+valuation.
 
 \subsection{User Behavior}
+
+Buyers and sellers are able
+to change their bid strategies asynchronously and serially.
+A users' local strategy space is therefore nondeterministic, and the prefererences of users
+are subject to change, i.e. binary dependence.
+Then, from \emph{Arrow's Theorem}, we have that no deterministic strategy can
+provide a mapping of the preferences of users into a market-wide (complete
+and transitive) strategy. As individual bids cannot map to a general objective, a better market
+position can only be determined by an adaptive strategy.
+We address the market risks and securities in our secondary data exchange market. 
+We provide a game-theoretic model of a real market progression, which we use to
+derive, then define, adaptive variables.
+
+Assuming equal bandwidth for all users, we derive a globally optimal strategy suited for
+users with local information in a distrubuted data-sharing model. 
+In a multi-auction market, each auction a buyer joins has the potential to
+decrease the potential cost of its data. However, increasing the size of the
+auction implies a certain risk, which we may interpret as a potential and
+definite
+liability. Increasing the number of transactions causes additional messaging
+overhead, fees, and increased competition from other buyers. 
+A transaction also causes potential indirect costs, which may be considered work done to find
+sellers, or effort of communication from participation. A seller
+has the potential for greater profit with each new buyer in its auction, taking 
+the same risk.
+The liability of any user is naturally absorbed into the bid fee $\epsilon$,
+as described in \cite{semret}. Therefore, according to our interpretation, the bid fee is
+dependent on the association between two users and their market positions, in
+addition to the underlying network structure. Now, both sellers and buyers must consider
+the cost of adding additional users to their subsequent pools.
+
+\subsubsection{Minimize crossover in buyer/ seller pools.}
+Buyer $i$'s seller pool is determined by minimizing $n$, and is the smallest set of sellers that
+allows for a coordinated bid, and the aggragate bids satisfy its demand, $D_i$.
+\begin{align}
+\begin{split}\label{buyercoordinate}
+    \min\big\lbrace n \in \mcI \ &\vert \ n D^n\ge D_i \big\rbrace. 
+\end{split}
+\end{align}
+Similarly, seller $j$ determines the minimal set of buyers that maximizes revenue and
+sells all of its data, $D^j$.
+\begin{equation}\label{sellercoordinate}
+    \min\bigg\lbrace m \in\mcI \ \bigg\vert\displaystyle\sum_{i\in\mcI^j(m)}d_i^j
+\ge D^j \bigg\rbrace,
+\end{equation} 
+We further determine that the set of buyers and sellers participating
+in a single equilibrium is bounded by the potential indirect costs of
+participation. We will denote this individual cost to each user as
+$\varrho$. The indirect cost is the portion of the bid fee
+$\epsilon$ that is dependent on the underlying network and the individual.
+Observing that $\varrho$ indirectly effects user utility,
+and therefore acts to establish a natural budget for each user. We define this
+constraint as, 
+\begin{equation}\label{poolbnd}
+    u \le \varrho,
+\end{equation}
+which may be interpreted as the effort a rational user is willing to expend
+on its message space, and serves to limit the size of the buyer/seller pools. 
+This information may be collected from a specific
+device's configuration, i.e. enabled roaming, daily data restrictions.
+It is clear that an unconstrained
+market, even with a finite number of users, could suffer from the
+expense of many local auctions trading an infinitely divisible resource, thus
+$\varrho$ is interpreted as
+the ``liability" component of $\epsilon$ attempts to regulate network congestion.
 
@@
 markets with smaller data quantities, and so will bid on a larger portion of
-the sellers' bid quantity, increasing their unit price. Market equilibrium is achieved when each buyer has equal bids in
-each auction. Our bidding strategy is inspired by \cite{lazar}, and we also
-hold buyers to consistent bids, where buyers sumbit identical bids to a
-subset of sellers with the highest offers. In the remainder of this section, we
-will make the assumption of truthful bids from the buyer, although this
-analysis is left to Section \ref{analysis}.
-Thus, we determine when rational (utility-maximizing) buyers opt-out of a local auction. 
-We propose the following strategy, 
+the sellers' bid quantity, increasing their unit price. 
+We define $j^* = n \le I$ represent the seller with the least amount of data
+$\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$.
+We define the composition,
+$$
+     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
+$$
+to be the buyer strategy with respect to quantity.
+We propose the following strategy. We include the proof in Appendix $A$.
 % BUYER STRATEGY
@@
 \lemma{(Opt-out buyer strategy)}\label{buyerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
 Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
-$t>0\in\tau$, and let $a$ be $i$'s desired allocation. 
+$t>0$, and let $a$ be $i$'s desired allocation. 
 % OPT-OUT BUYER STRATEGY
-
-Now let $j^* = n \le I$ represent the seller with the least amount of data
-$\in\mcI_i$, i.e. $D^{j^*} \le D^j, \ \forall\ j \in\mcI^j$, and define $i$'s bid
-vector $\g_i$ with respect to its strategy, where
+Define,
 \begin{equation}\label{opt-eq}
     \g_i^j(a) \triangleq \begin{cases} \g_i^{j^*}(a), \quad j\in\mcI^j,\\
-            0, \quad j\ni\mcI^j.\end{cases}
-\end{equation}
-and define bid price $p_i^j = \theta_i'(\g_i^j(a))$.
-Now, (\ref{opt-eq}) holds $\forall \ j\in\mcI$,
-and we have an optimal strategy for buyer $i$.
+            0, \quad\qquad j\ni\mcI^j.\end{cases}
+\end{equation}
+and bid price $p_i^j = \theta_i'(\g_i^j(a))$.
+Now, (\ref{opt-eq}) holds $\forall \ j\in\mcI$.
 }\\
-\textbf{Proof:}
+Each time step, $\s^j$ is updated it is shared with all
+participating buyers. At this point buyers have the opportunity to bid again,
+where a buyer that does not bid again is assumed to hold the same bid, since a
+buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$.
+
+% BUYER ALGORITHM
+\begin{center}
+\begin{algorithm}[H]
+\caption{(Buyer response)}
+\begin{algorithmic}[1]
+\State $p_{i(0)} \gets \epsilon$, $s_{i(0)} \gets (p_i, D_i)$, $D_t \gets D_i$, compute
+$\mcI_{i(0)}$
+\State Update $s_i$ 
+\While{$D_i(t) > 0$}
+\State $D_{i(t+1)}^j \gets \sum_{j\in\mcI_i}\g_i^{j(t)}(a)$
+\If{$D_{i(t+1)}^j < D_t$}
+    \State Compute $\mcI_{i(t)}$
+    \State $p_i \gets \theta_i(\g_i(a))$
+\EndIf
+\State $s_{i(t+1)} \gets (\g_i(a), p_i)$
+\State Update $s_i$
+\State $D_{i(t+1)}^j \gets D_{i(t)}^j$
+\State $t \gets t+1$
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+\end{center}
+
+Finally, we note that $\mcI_i$ is not the only
+possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, in fact, by
+restricting the size of the set $\mcI_i$, we would be able to improve the
+computation time of buyer $i$, at the cost of increasing the price.
+
+\subsubsection{Individual rationality.}
+We prove that a buyer cannot have a negative utility. Our
+strategic framework creates an incentive for the seller to maintain a local
+equilibrium, where supply equals demand. 
+We define the reserve price for seller $j$ as,
+\begin{equation}\label{newprice}
+    p_*^{j} = p_{i^*}^{j} + \epsilon,
+\end{equation}
+where $i^*$ is the highest losing bidder with respect to bid price.
+We claim that the choice of reserve price $p_*^j$ does not force any buyers out
+of the local auction. 
+A truthful bid implies that the new bid price differs from the last bid price by at least
+$\epsilon$. As a seller must distribute bid vectors to all
+buyers in its auction, we reason that the seller may employ a strategic caveat.
+The seller will notify a buyer who is subject to a market shift by changing its
+bid at the appropate index.
+
+\subsubsection{Seller Strategy}
+In order to
+maximize revenue, the seller must also be able to respond dynamically to
+strategic bids. In order to do this, we
+determine that the seller may modify its reserve price in response to the
+changing market dynamics.
+
+Define any auction duration to be $\tau \in [0,\infty)$. 
+We will show that sellers are able to maximize revenue in restricted subset of
+buyers in $\mcI$, and as such will attempt to facilitate a local market
+equilibrium for this subset. A local auction $j$ converges when $\forall \ i \in\mcI$,
+$s_i^{j(t+1)} = s_i^{j(t)}$, at which point the allocation is stable, the data
+is sold, and the auction ends. In the sellers' local environment, we determine
+that the best course of action is to maximize revenue, and then try to keep its
+buyer pool stable until convergence occurs. The exhaustive proof is included in
+Appendix $B$.
+
+% SELLER LOCAL STRATEGY
+{
+\lemma{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
+For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t>0\in\tau$.
+For each $t\in\tau$, let $\omega(t)$ be given by (\ref{winner}), and perform
+the update,
+\begin{equation}\label{newdata}
+    D^{j(t+1)} = D^{j(t)} - \g_{\omega(t)}^{j(t)}(a).
+\end{equation}
+Allowing $t$ to range over $\tau$, we have that $D^j=0$, and a local market equilibrium. 
+}
+
+Consider a user purchasing data from a subset of other network users.
+The sellers' auction will function as follows: at each bid iteration all buyers
+submit bids, and the winning bid is the buyer $i$ that has the highest price
+$p_i^j$. The seller allocates
+data to this winner, at which point all other buyers are able to bid again, and
+the winner leaves the auction (with the exception where multiple bidders bid
+the same price, where (\ref{dataallocation}) determines they will not fully
+satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
+sellers' data has been allocated. 
+% SELLER ALGORITHM
+\begin{center}
+\begin{algorithm}[H]
+\caption{(Seller progressive allocation)}
+\begin{algorithmic}[1]
+\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
+\emptyset$, compute
+$\mcI^{j(0)}$
+\State Update $s^j$ 
+\While{$D^j(t) > 0$}
+\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
+\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
+%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
+\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
+\State $s^{j(t+1)} \gets (d^j, p^j)$
+\State Update $s^j$
+\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
+\For{$k \in \bar\mcI$}
+\If{$p_k^j < p_{i*}^j$}
+\State $D^{j(t+1)} = d_k^{j}$
+\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
+\EndIf
+\EndFor
+\State Compute $\mcI^{j(t)}$
+\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
+\State $t \gets t+1$
+\EndWhile
+\end{algorithmic}
+\end{algorithm}
+\end{center}
+
+\subsubsection{Market Dynamics under Strategy}
+
+We conclude this section by examining the relationship between the strategies of buyers and
+sellers in local auctions. We model the impact of the dynamics of the
+data-exchange market on a local auction $j$. As we have shown, the seller
+is a functional extension of the buyer, with rules determined by the buyers'
+behavior. This gives an auction $j$ a natural logical extension into the
+global market through its buyers. We demonstrate that the symmetry between
+buyer and seller behavior, consequently strategies, stretches into a symmetry across subsets of local
+auctions. Additionally, we identify a clear bound restricting the influence of
+local auctions on each other. Defining a single iteration of the auction, where a seller updates bid vector
+$s^j$, and the buyers' response $s_i$, to comprise a single time step, and we
+have the following Proposition,
+% USER UNION
+{
+\proposition{(Valuation across local auctions)}\label{userunion}
+For any $i,j\in \mcI$, 
+\begin{equation}\label{jtoi}
+j\in\mcI_i \Leftrightarrow i\in\mcI^j.
+\end{equation}
+Fix an auction $j\in\mcI$ with duration $\tau$ and define the influence sets of users. 
+The primary influencing set is given as,
+%(ALL THE SELLERS FROM EACH BUYERS POOL)
+\begin{equation}\label{lambda}
+    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
+\end{equation}
+with secondary influencing set,
+%(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
+\begin{equation}\label{llambda}
+    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
+\end{equation}
+\iffalse
+(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
+\begin{equation}%\label{lambda}
+    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
+\end{equation}
+(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
+POOLS)
+\begin{equation}%\label{llambda}
+    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
+\end{equation}
+\fi
+Define $\Delta = \Lambda \cup \lambda$.
+Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
+\begin{equation}\label{union-eq}
+    \displaystyle\sum_{j\in\Lambda} \theta_i^j = \sum_{i\in\lambda} \theta_i^j.
+\end{equation}
+}\\
+\proof{
+A local auction $j\in\mcI$, is determined by the collection of buyer bid
+profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. Using Proposition \ref{sellerstrategy} and (\ref{jtoi}), we have that, 
+\begin{equation}\label{iff}
+    i\in\mcI^j \Leftrightarrow p_i^j > p_{i^*}^j,
+\end{equation}
+where
+(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
+price in auction $j$. By (\ref{buyerinversedemand}) $p_i^j \ge
+p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
+shift caused by the underlying dynamics.
+Consider $k\in\mcI^j$ at time $t$ where, for example, some buyer(s) enter the auction, and
+so (\ref{iff}) implies that
+$\sum_{i\in\mcI^j} \g_i^j(a) > D^j$. Now, $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
+$s_k^j>0$ will cause $k$ to initiate a shift. By Proposition \ref{buyerstrategy}, $k$ will set $s_k^j=0$, and begin to add sellers to its pool.
+Suppose that at time $t$, $j$'s market is at equilibrium, i.e.
+$\sum_{i\in\mcI^j} \g_i^j(a) = D^j$, and fixing all other bids, so 
+no buyer $i\in\mcI^j$ rebids. Unless $k$ adds a seller with a higher reserve
+price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
+auction ends. Otherwise, at some time $t\in[t+1,\tau]$, we must have that
+$\g_k^j \le D^j$, and $k$ rejoins auction $j$ or opts-out. Finally, overlooking market shifts and messaging
+overhead, we have that,
+    $\forall \ i\in\mcI^j$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and (\ref{jtoi})
+holds.
+\iffalse
+Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
+of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
+s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
+\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
+\fi
+
+Now, the subset $\mcI^j \subset \mcI$
+determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
+coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
+determines the unit price $p_{i}$ in buyer $i$'s bid.
+The reserve price (\ref{newprice}) of seller $j$ is determined at each
+shift, and is
+the lowest price that $j$ will accept to perform any allocation.
+Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
+price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
+[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
+\ \forall \ k \in\mcI_i$. 
+Using Proposition
+\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
+\ \forall \ k \in\mcI_i$.
+
+\iffalse
+Now, we have,
+\begin{equation}\label{rho}
+    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
+\end{equation}
+from (\ref{datademand}), (\ref{buyerinversedemand}),
+(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
+[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
+\fi
+
+The incentive of each seller $\in\Lambda$ is to sell all of its data at the
+best possible price. In the simplest case,
+consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
+\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
+$\lambda = \mcI^j$. 
+Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
+clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+In all other cases, the sellers $\in\Lambda$ are competing to sell
+their respective resources to buyers whose valuations are distributed across multiple auctions. 
+%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
+The set $\lambda$ represents all of the buyers influencing auction $j$, both
+directly and indirectly. 
+The bid price of buyer $i\in\mcI^j$ is determined by,
+\begin{equation}\label{maxbid}
+    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
+\end{equation}
+$\Lambda$ is the set of sellers directly influencing the bids of buyers
+in auction $j$. Now, the reserve price for auction $j$ is such that,
+\begin{equation}\label{resprice}
+    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
+\end{equation}
+from (\ref{newprice}). Now, by Proposition \ref{sellerstrategy}, in the absence
+of external influences caused by multi-auction market dynamics, we have 
+that $j$ maintains a local market equilibrium from time $t$ to $(t+1)$.
+From (\ref{lambda}) and (\ref{llambda}), $\Delta$ is defined by a seller $j\in\mcI$, where each
+user $k\in\Delta$ has some direct or indirect influence on $j$. 
+We may identify $\Delta$ by its dominant seller, and we denote $\Delta^j = \Lambda^j
+\cup \lambda^j$.
+
+Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
+some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
+p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
+Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
+that $p_l^* < p_*^j$, and
+the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
+have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
+where,
+\begin{equation}\label{ordering}
+    p_*^k \le p_l^* < p_*^j \le p_i^*,
+\end{equation} 
+for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
+p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
+$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
+which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
+\ni\mcI^q \Rightarrow p_*^q >
+p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
+buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
+(\ref{iff}).
+Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
+0$, for some $g\in\mcI_i$.
+We have that for any $l\in\mcI^k$ such that $l\ni
+\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
+where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
+p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
+a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
+such that $p_*^g \ge p_*^j$. Thus, we
+determine a direct influence as $l\in\mcI^k
+\cap \Lambda^j$, such that $p_l^* > p_i^*$,
+and an indirect influence as, for any $l\in\mcI^k
+\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
+
+Now, consider the subset $\Lambda^j$, by
+Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
+decreases its bid quantity so that $\sum_{i\in\mcI^j}
+\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
+\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
+p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the
+lowest bid price, the ``lowest clearing player",
+and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
+that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
+directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
+buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
+recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
+will attempt to regain equilibrium.
+Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
+then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
+seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
+p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
+\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
+case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
+where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).
+
+In each case we
+have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
+some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
+\begin{equation}\label{jdemand}
+    \int_0^{\g_i^j(a)} f^j(z) \ dz 
+    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
+\end{equation}
+therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
+Thus, any bid ouside of
+our construction
+has a zero valuation, with respect to buyers $\in\lambda$ and sellers
+$\in\Lambda$, and therefore cannot cause shifts to occur except through a
+shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
+(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
+bids in any auction $q \ni \Lambda^j$,
+we have, $\forall \ k\in\mcI_i$,
+\begin{equation}\label{idemand}
+    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
+f^k(z) \ dz,
+\end{equation}
+which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
+\ref{sellerstrategy}..
+Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
+\begin{align}\label{tieqtk}
+    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
+\end{align}
+and
+\begin{align}\label{tkeqtl}
+    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
+\end{align}
+Thus, with a slight abuse of notation for clarity,
+\begin{equation}\label{funion-eq}
+    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
+\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
+\end{equation}
+where the result follows by construction, and the continuity of $\theta'$.
+$\qed$}
+
+For completeness, in the case where the ISP $\kappa$ 
+does not adhere to the market dynamics, so $p^\kappa > p^j +
+\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
+bid fee.
+
+The topology of the bids in $\delta$ is key to our result. We immediately have:
+
+\subsubsection{Locally fair division.}
+We claim that the allocation $a$ by seller $j$ for a local auction at
+equilibrium is an \emph{equitable division}, a fair division where each buyer
+equally values their valuation. We have that equitable division holds from
+(\ref{tieqtk}) Proposition \ref{userunion}.
+
+\subsubsection{Social welfare maximization.}
+We define an optimal state of social welfare to be when valuations are equal
+across a subset of local auctions. Then, $\Delta\subset \mcI$ to be a subset of
+users where an optimal social welfare is achieved.
+
+From these two properties, and Proposition \ref{userunion}, we have the
+following Corollary, 
+{
+\corollary{($\Delta$-Pareto efficiency)}
+    The subset $\Delta\subset \mcI$ is Pareto efficient, in that no user can
+    make a strategic move without making any other user worse off.
+}
+\proof{Follows directly from the result of Proposision \ref{userunion}.}
+
+% VCG ANALYSIS
+\section{PSP Analysis}\label{analysis}
+
+\subsection{Equilibrium}
+
+We intend to show evidence shared network optima (a
+global optimum). 
+A buyer $i\in\mcI$ will have incentive to change its bid
+quantity if it increases its opt-out value $\g_i$, and therefore its utility (\ref{buyerutility}). 
+We will show that, without loss of utility, buyer $i$ may  
+use a ``consistent" bid strategy within its seller pool, i.e. $d_i^j = d_i^k, \
+\forall \ j,k \in \mcI_i$, and as such,
+Proposition \ref{buyerstrategy} supports an optimal strategy with respect to
+(\ref{buyerutility}). 
+Our result shows that a buyer may select $\mcI_i$ in order to maximize its
+utility while maintaining a coordinated bid strategy. 
+Reasonably, if $j^*< I$, a buyer may increase the size of its seller pool
+$\mcI_i$, thereby lowering its coordinated bid
+quantity while obtaining the same (potential) allocation $a_i$. 
+As buyer $i$ submits identical bids to multiple auctions, the bid price must be
+as high as the highest reserve price $p_i^j \in \mcI_i$.
+Buyer $i$'s bid then has identical bid price $p_i^j \forall \ j \in\mcI_i$. 
+We further note that $i$ optimal strategy does not require reducing its bid price to a
+minimum in each auction, where
+the bid quantity $\g_i^j(a)$ is still fufilled. The pricing rule of the PSP
+auction dictates that a buyer $i$ will pay the cost of excluding other players from
+the auction, and as $i$'s bid price reflects its valuation of it data
+requirement $D_i$ across all local markets, we have identical bid prices in
+each auction where $s_i^j>0$. Obviously, if $j\ni\mcI_i$, then $\theta_i^j = 0$.
+
+% BUYER COORDINATION
+{
+\lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
+Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
+For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be a
+tentative data
+allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
+\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
+\begin{align*}
+    z_i^j &= \g_i^{j}(a), \\
+    y_i^j &= \theta_i'(z_i^j).
+\end{align*}
+Furthermore,
+\begin{equation}\label{allocationcoordination}
+    a_i^j(z_i,y_i) = z_i^{j},
+\end{equation}
+and
+\begin{equation}\label{costcoordination}
+    c_i^j(z_i,y_i) = y_i^{j},
+\end{equation}
+where $i$'s strategy is as in Proposition \ref{buyerstrategy}.
+}\\
+The proof is left to the Appendix, as it follows closely the work in
+\cite{semret}.
+
+\subsubsection{Incentive Compatibility}
+
+The property of truthfulness is an essential component of equilibrium in
+second-price markets. The strategies described in this paper have removed the
+necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
+construction of the user strategy space results in truthful bids that are optimal for all users,
+i.e. bid prices are to the marginal value as determined by market dynamics. 
+To achieve incentive compatibility, we find that the opt-out buyer must choose
+this subset so that its overall marginal value is greater than its market price.
+We have so far only made the assumption of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
+has incentive to change its bid as a result of a market shift or partial
+allocation. In a truthful reply, the term $\epsilon/\theta_i'(0)$
+ensures that a new bid price differs from the last bid price by at least
+$\epsilon$, thereby ensuring that a buyer does not change its bid without
+correcting the effects of unstable shifts.
+For a buyer $i$, define the set of possible $\epsilon$-best replies,
+\begin{equation}\label{e-bid}
+    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
+u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
+\end{equation}
+and the set of \emph{truthful} bids, 
+\begin{equation}\label{t-bid}
+    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
+\wedge p_i = \theta_i'(z)\rbrace,
+\end{equation}
+where $\wedge$ denotes the logical ``and" operator. We note that the ``strategic" set $T_i$
+is restricted by Proposition \ref{buyerstrategy}.
+We have the following Proposition,
+
+{
+\proposition{(Incentive compatibility across local auctions)}\label{incentive}
+Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
+$t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
+buyer $i\in \mcI^j$, let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
+\begin{align}
+\begin{split}\label{eta}
+    \chi_i &= \bigg\lbrace x\in [0,D_i] : 
+ {\theta_i}'(x) > \max_{j\in\Lambda}P_i^j(x)\bigg\rbrace, 
+\end{split}
+\end{align}
+and $z = \sup(\chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
+\Lambda$, 
+$$
+    v_i^j = \g_i^{j}(z),
+$$
+and 
+$$
+    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
+$$
+Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
+(v_i,w_i) \in T_i\cap S_i^\epsilon(s_{-i})$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
+s_{-i})$.
+With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
+$\in\Delta$. Therefore, a fixed point $\in \Delta$ is a fixed point in
+the multi-auction game. 
+}\\
+As in Lemma \ref{coordinationlemma}, we leave the proof to the Appendix.
+
+The strategy space is comprised of a collection of bid, or ``strategy", vectors that
+together, may be represented as a collection of potential functions, where change in buyer $i$'s
+utility, resulting from a change in strategy, equals the change in
+the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
+formulated by mapping the incentives of all users in a local auction to a
+single function. The goal of our analysis is to therefore construct a global potential function that encompasses
+all local markets. Then, we may determine a Nash equilibrium by finding a local
+optima of the potential function. Additionally, as the potential function also
+iterates, it may be used in an analysis of convergence. The
+convergence of a Nash equilibrium results from the progression of
+$\epsilon$-best replies, where each subsequent bid is a unilateral
+improvement, provided that $t_i$ is continuous in opponent profiles.
+From the original proof by \cite{lazar}, we observe that the collection of
+unconstrained truthful bids may be a subset
+of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
+%An essential component of determining the existence of a Nash equilibrium is 
+For this work, it suffices to show the continuity of the set of truthful
+$\epsilon$-best replies in the set of opponent bid profiles.
+In order to address continuity in a global sense, we must demonstrate
+continuity in the construction of our model.
+Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
+a.nd determine the
+existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
+correspondence,
+{
+\definition{(Correspondence)}
+A correspondence is mathematically defined as an ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
+$Y$, i.e. any subset of the Cartesian product $X\times Y$.
+}
+
+In an economic model, a correspondence $(S_i,S_{-i},R)$ defines a map from $S_i$
+to the power set $S_{-i}$, where $R$ is a binary relation, i.e. $R \subset
+S_i\times S_{-i}$. The classic
+example of a correspondence in our model is the buyers' best response
+$B_i^\epsilon$, where, for the multi-auction,
+$S_i$ and $S_{-i}$ are built by repeatedly using the
+cartesian product over bid profiles. The power set 
+$S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
+product of ordered sets. 
+The best response is a reaction correspondence
+defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
+S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
+profiles $S_{-i}$. \\
+\textbf{Remark:} 
+The ease by which the game is constructed is a consequence of the the cartesian
+product on a 2-dimensional message space. \\
+A natural induced topology of this space is the product\footnote{This is known
+as the Correspondence theory of truth}
+topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.
+
+Motivated by the symmetric nature of supply and demand, we determine the
+game-theoritical argument is complemented by an abstract-theoretical analysis.
+In fact, we may even be philosophically motivated, as the truth value of a bid
+is determined only by how it relates to markets, and whether it provides an
+accurate correspondence\footnote{This is known as the Correspondence theory of
+truth}. Using a set-theoretical approach to address the sellers
+bids, we derive our result from the symmetry of supply and demand,
+(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
+\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
+\ref{buyercoordinate}, and include the following corollary,
+{
+\corollary{Data-bid correspondence (seller cooperation)}
+Let $\Delta$ be defined as in Lemma (\ref{userunion}).
+For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
+$\epsilon$-best reply.
+}\\
+\proof{
+We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
+strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
+We use the the axiom of set equality,
+based on first-order logic with equality, which states that,  
+$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
+\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
+Then, for any allocation $a$, we may define the relation, $i\thicksim
+j$,
+\begin{equation}\label{eqrel}
+        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
+        \big(\g_i^j(a),y)\big).
+\end{equation}
+Formally, the axiom states that a set is \emph{uniquely} determined by its
+members. It follows that $\thicksim$ defines equality of bids using a static
+analysis with respect to equilibrium, where all users who are not changing thier
+bids are considered equal.\\
+\textbf{Remark:} Equality is both an equivalence relation and a partial order,
+and therefore is reflexive, transitive, symmetric and antisymmetric. \\
+Now, we may define the mapping $s \mapsto [s]$,
+\begin{equation}\label{indeqrel}
+         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
+\end{equation}o
+noting that equality in the bid quantity is implicity satisfied and $z =
+\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
+buyer-seller pair. Let $S = \Pi_{j\in\mcI} \big(
+\Pi_{i\in\mcI} S_i^j \big)$. The indicator function is the canonical mapping,
+$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
+topology is preserved, the set of all indicator
+functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
+S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
+\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
+$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$. } Therefore each seller
+$j\in\mcI$ is equivalent buyer(s) $i\in\mcI$. That is, buyers and
+sellers with an equality relation (\ref{eqrel}) belong to the same local
+auction equilbrium. Therefore, sellers' bids represent $\epsilon$-best replies
+in the strategy space. $\qed$ (DONE? REALLY?)
+
+{
+\proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
+Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
+$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
+}\\
+\proof{
+Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
+$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
+the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
+We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
+$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
+we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
+\overline{P}]^{\vert \mcI^j\vert})$
+is a product of closed subsets of compact sets. Now, we have that a closed
+subset of a compact set is compact and the resulting product topology gives
+Tychonoff's theorem. every product of a
+compact space is compact, we have $\g_i \circ B_i^\epsilon$
+is compact subset of $B_i^\epsilon$.
+ Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
+definition of $\Delta$ and the product, 
+\begin{align*}
+    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
+    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
+[0,\overline{P}]\bigg)
+    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
+[0,\overline{P}]\bigg) \\
+    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
+\times \lambda^j \subset T.
+\end{align*}
+The result follows from the fact that $t_i$ is continuous in $s_i$, as was
+proven in \cite{semret}, and as a finite union of compact sets is a compact set.
+$\qed$}
+
+As a result of user behavior, and subsequent strategies, we determine that the
+data-exchange market behaves in a predictable way. However,
+each auction may be played on the same or on a different scale in
+valuation, time and quantity, and so the rate at which market fluctuations occur is
+impossible to predict. 
+We show that our bidding strategy results in (at least one), static Nash
+equilibrium, where the sellers reserve prices are fixed. This result is
+logically derived, and as our final result, we address the audience and note
+that it is a mere step in the right direction.
+{
+\lemma{(Local Static Nash Equilibrium)} 
+Let $\Delta$ be defined as in Lemma (\ref{userunion}), and suppose that auction
+$j\in\Delta$ is at equilibrium. Fix all $s_i^j$. 
+Using the rules of the data auction mechanism, along with type-based strategic
+moves, $j$ converges to an $\epsilon$-Nash equilibrium. 
+The proof follows closely that of \cite{semret}.
+}\\
+\proof{
+As auction $j$ is at equilibrium, and 
+since $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
+$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
+$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
+represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
+and we may use Brouwer's fixed point theorem, as in \cite{semret},
+}
+
+We have proven that buyers will submit bids according to their marginal
+valuations. Now, in the interest of completeness (BAD SENTENCE), 
+We have that all bids represent $\epsilon$-best replies, and, as was proven in
+\cite{lazar}, the sellers' positive reserve price implies that bids are
+truthful. Finally, by properties determined by the construction of a mixed strategy
+symmetric game with a 2-dimensional message space, we may now restrict our
+analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.
+
+{
+\corollary{Hemicontinuity of $\Delta$}
+}
+
+The data-sharing market consists of inter-dependent sets of these
+multi-auction games around possible fixed points.  Clearly, the union of all possible
+sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
+between the different subsets $\Delta$ form a sufficiently connected set that
+the heirarchy described in Proposition \ref{userunion} holds. Then,
+there can only be a single primary fixed point, where the sellers' reserve
+price is an equilibrium price in the global market. 
+We first address the analytical approach, and demonstrate properties of
+$\Delta$ as a finite-dimensional linear topological space. We have that the
+reserve price of the sellers, and the bid price of the buyers is constant
+within an interval of length 2$\epsilon$. We have that 
+(HERE) We have the following
+Corollary, (MIGHT NEED TO REDEFINE.. NOT CLEAR IS A SEQUENCE, SHOULD BE
+SEQUENCE OF PRICES INSTEAD OF USERS?) 
+{
+\corollary{(Primary fixed point)}
+Let the set of shared buyers be denoted as,
+$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
+sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
+$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
+\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
+for a fixed time $t$,
+$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
+k\ne j\in\overline{\Lambda}$. 
+}\\
+(CAN PROBABLY USE ALL BUYERS HERE... BECAUSE OF INF)
+\proof{
+We assume a finite number of users, with continuous valuation functions bounded both
+above and below. From the assumption that $\overline{\Lambda}$ is not a
+partition, we have that the limits exist with respect to bid price $p_i^j$, 
+$$
+    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
+$$
+is the primary seller $j$, and we have the market price $p_*^j$ from,
+$$
+    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
+\lambda^k,
+$$
+and the result follows from Lemma \ref{uservaluation}, Proposition
+\ref{userunion} and Proposition \ref{incentive}.}
+(NEED TO SHOW THEY ARE EQUAL...)
+%$\qed$\\
+(USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
+
+We show that our bidding strategy is
+part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
+equilibrium, where the sellers reserve prices are fixed.
+{
+\lemma{(Static Nash Equilibrium)} 
+Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
+let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
+sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
+Using the rules of the data auction mechanism applied independently by each
+user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
+}\\
+\proof{
+(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
+As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
+$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
+$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
+represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
+and we may use Brouwer's fixed point theorem, as in \cite{semret},
+}
+
+As a result of user behavior, and subsequent strategies, we determine that the
+data-exchange market behaves in a predictable way. However,
+each auction may be played on the same or on a different scale in
+valuation, time and quantity, and so the rate at which market fluctuations occur is
+impossible to predict (NEED HELP!). 
+Arrow's paradox is an impossibility theorem stating that when buyers have three
+or more distinct alternatives (auctions), no deterministic ranking system can
+convert the ranked preferences of users into a market-wide (complete
+and transitive) ranking while also meeting a specified set of criteria:
+unrestricted domain, non-dictatorship, Pareto efficiency and independence of
+irrelevant alternatives. It follows that the case where
+$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
+is disjoint.
+
+Nonetheless, we claim that our mechanism is normative, that irrelevant
+alternatives should not matter, it is practical, uses minimal information,
+strategy, and provides the right incentives for the truthful revelation of individual preferences.
+
+The rules of the PSP
+multi-auction drive market mutations that evolve and are regulated by the user
+strategies.
+(HERE)
+
+(DEFINITION.. USE?)
+In the General Symmetric Game, p is an evolutionarily stable mixed strategy if
+there is a (small) positive number y such that when any other mixed strategy q
+invades p at any level x < y, the fitness of an organism playing p is strictly
+greater than the fitness of an organism playing q.
+(EXPAND)
+% DATA NASH EQ
+{
+\theorem{(Dynamic Nash Equilibrium)}
+Using the rules of the data auction mechanism, the secondary market
+converges to a $\epsilon$-Nash equilibrium. In the network auction
+game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
+equilibrium. 
+}\\
+
+\subsection{Efficiency}
+
+Formally, the
+mechanism is efficient, if, at equilibrium, the allocation maximizes
+$\sum_i\theta_i(a_i)$.
+(NEED OWN WORDS)
+The objective in designing the auction is that, at equilbrium, resources al-
+ways go to those who value them most. Indeed, the PSP mechanism does
+have that property. This can be loosely argued as follows: for each player,
+the marginal valuation is never greater than the bid price of any opponent
+who is getting a non-zero allocation. Thus, whenever there is a player j
+whose marginal valuation is less than player i 's and j is getting a non-zero
+allocation, i can take some away from j , paying a price less than i 's marginal
+valuation, i.e. increasing u i , but also increasing the total value, since i 's
+marginal value is greater. Thus at equilibrium, i.e. when no one can unilat-
+erally increase P their utility, the total value is maximized.
+
+\subsection{Convergence}
+
+% CONCLUSION AND FUTURE WORK
+\section{Conclusion and Future Work}
+
+We point out the need for better management of data on the consumer
+level. It is obvious that there is profit to be made by
+supplying data to the data-driven consumer. However, consumers must be given a
+choice. Consider Bob, a mobile wireless network user. Marketing firms have already realized that an incentive
+for Bob to interact with their ads is to provide them at no cost to his mobile
+    data. Inevitebly, ISPs will find a way to supply the growing demand. We
+    have demonstrated the trend towards a Monopoly of knowledge\footnote{John
+    Watson (2006), suggests that monopolies of knowledge gradually suppress new ways
+    of thinking.}, and suggest
+    that trust, and policy be decentralized, for the greater good.
+
+Mathematically, we have shown that if truthfulness holds locally for both buyers and sellers, i.e.
+$p_i ={\theta_i}', \ \forall \ j \in \mcI_i$ and $p^j = {\theta^j}', \ \forall \
+i \in\mcI^j$, then, in the absence of market shifts,
+there exists an $\epsilon$-Nash equilibrium extending over a subset of connected
+local markets. Observing the symmetric, natural topology of the strategy space,
+we conjecture that a unique subspace limit exists for connected $\Delta$. A
+study of this metric is the direction of our future work.
+
+Finally, we note the harmonious relationship of users, data, and mathematics.
+The exchange of data in the secondary market must mimic the topology of the
+strategy space. Thus, although we assume that the message space of PSP auctions
+is too small, we conjecture that this relationship is the backbone of an
+evolutionary system, naturally derived from the continuity of demand and
+shifting market equilibria.
+
+\appendix
+
+\section{Strategy}
+\subsection{Proof of Lemma 3.5}
+\proof{
 We assume that a buyer will try and fill their data requirement.
@@
 \forall \ j\in\mcI_i$, and
-$p^\kappa$ represents the overage fee for data set by the ISP, which we note is also the upper bound of the sellers'
-pricing function.
+$p^\kappa$ represents the price for data set by the ISP, which we note is also
+the upper bound of the sellers' pricing function. We note that in \cite{zheng}
+this cost is the data overage fee.
 Consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
@@
 and we determine that the opt-out strategy is optimal.
-$\qed$
-
-Finally, we note that $\mcI_i$ is not the only
-possible minimum subset $\in\mcI$ able to satisfy $i$'s demand, in fact, by
-restricting the size of the set $\mcI_i$, we would be able to improve the
-computation time of buyer $i$, at the cost of increasing the price.
-
-\subsubsection{Seller Strategy}
-In order to to develop the seller strategy, we examine the incentive of a
-rational seller with only local information in a dynamic market of many
-buyers and sellers. A local auction, examined independently, may appear as
-single market with a single seller and many buyers, but is in fact a subset of the
-larger data-exchange market, and is subject to the trends and dynamics
-therewithin. A seller must determine allocations using only bids in its local market, while the buyers' response is based on the
-allocations and resulting opponent bids from all auctions in its seller pool.
-In addition, buyers are allowed to bid both dynamically and asychronously. 
-In order to
-maximize revenue, the seller must also be able to respond dynamically to
-address the mutation of competitive bids in its market. In order to do this, we
-determine that the seller may modify its reserve price in response to the
-changing market dynamics.
-
-We will show that sellers are able to maximize revenue in restricted subset of
-buyers in $\mcI$, and as such will attempt to facilitate a local market
-equilibrium for this subset. A local auction $j$ converges when all buyer bids
-remain the same over a time step, that is, if $\forall \ i \in\mcI$,
-$s_i^{j(t+1)} = s_i^{j(t)}$, at which point the allocation is stable, the data
-is sold, and the auction ends. In the sellers' local environment, we determine
-that the best course of action is to maximize revenue, and then try to keep its
-buyer pool stable until convergence occurs. Thus, the seller strategy is
-complementary to that of the buyers, and is designed to achieve and maintain a
-local market equilibrium.
-
-We describe a \emph{local} auction strategy for data allocation, where the seller is unaware of the existence of other auctions, and so
-the seller behavior is the same in the case of a single buyer, a small buyer set, and in the
-extreme case, where all buyers $i\in\mcI$ participate. We again note that the
-seller must initialize the strategy with a first iteration, and so the auction
-is defined for time $t>0$.
-In our model, a local auction may be described as a progressive game of strategy with
-incomplete, but perfect information, however in our analysis, as before, we will assume
-complete information. 
-(BUYERS ARRIVE AS A POISSON PROCESS? FUTURE WORK)
-
-% SELLER LOCAL STRATEGY
-{
-\lemma{(Localized seller strategy (i.e. progressive allocation))}\label{sellerstrategy}
-Define any auction duration to be $\tau \in [0,\infty)$. 
-For any seller $j$, fix all other bids $[s_i^k]_{i,k\ne j \in\mcI}$ at time $t>0\in\tau$.
-Define buyer $i^* = n-1 \le I$ as the buyer with the maximum bid price $\ni
-\mcI^j$.
-Let the winner at time $t$ be determined by,
-\begin{equation}\label{winner}
-    \bar{i} = \displaystyle\max_{i\in I^j} p_i^{j(t)},
-\end{equation}
-and update $j$'s total data to reflect the (tentative) allocation,
-\begin{equation}\label{newdata}
-    D^{j(t+1)} = D^{j(t)} - \g_{\bar{i}}^{j(t)}(a),
-\end{equation}
-Allowing $t$ to range over $\tau$, we have that (\ref{sellercoordinate}) -
-(\ref{newdata}) produces a local market equilibrium. 
-}\\
-\textbf{Proof:}
+$\qed$}
+
+\subsection{Proof of Lemma 3.6}
+\proof{
 We assume that the seller will try to maximize its revenue. In the case where
@@
 Thus we determine the valuation between seller
-$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is justified, and the local
-equlibirium created by $j$ is independently stable from time $t$ to $(t+1)$. 
-$\qed$
-
-\subsubsection{Market Dynamics under Strategy}
-
-We conclude this section by examining the relationship between the strategies of buyers and
-sellers in local auctions. We model the impact of the dynamics of the
-data-exchange market on a local auction $j$. As we have shown, the seller
-is a functional extension of the buyer, with rules determined by the buyers'
-behavior. This gives an auction $j$ a natural logical extension into the
-global market through its buyers. We demonstrate that the symmetry between
-buyer and seller behavior, consequently strategies, stretches into a symmetry across subsets of local
-auctions. Additionally, we identify a clear bound restricting the influence of
-local auctions on each other. Defining a single iteration of the auction, where a seller updates bid vector
-$s^j$, and the buyers' response $s_i$, to comprise a single time step, and we have the following Lemma,
-% USER UNION
-{
-\proposition{(Valuation across local auctions)}\label{userunion}
-For any $i,j\in \mcI$, 
-\begin{equation}\label{jtoi}
-j\in\mcI_i \Leftrightarrow i\in\mcI^j.
-\end{equation}
-Fix an auction $j\in\mcI$ with duration $\tau$ and define the influence sets of users. 
-The primary influencing set is given as,
-%(ALL THE SELLERS FROM EACH BUYERS POOL)
-\begin{equation}\label{lambda}
-    \Lambda = \displaystyle\bigcup_{i\in\mcI^j} \mcI_i,
-\end{equation}
-with secondary influencing set,
-%(ALL THE BUYERS FROM EACH SELLER $i$ IN $j$'s BUYER POOL)
-\begin{equation}\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcup_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
+$j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is
+justified, and we have a local equlibirium at time $\tau$.
+$\qed$}
+
+\section{Equilibrium}
+\subsection{Proof of Lemma 4.1}
+\proof{
+As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
+u_i(s_i;s_{-i})$. In full notation, we intend to show
+$$
+    u_i((d_i,p_i);s) \le u_i((z_i,y_i);s_{-i}).
+$$
+Now, if there exists a seller who can fully satisfy $i$'s demand,
+then $\vert\mcI_i\vert = 1$, and the case is trivial as no
+coordination is necessary for a single bid. %(SPECIAL CASE OF MONOPOLY? THINK!)\\
+Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
+multiple sellers.
+We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
+$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $\sum_{j\in\mcI_i}u_i^j$.
+Buyer $i$ maintains ordered set $\mcI_i$ where the sellers with the
+largest bid quantities are considered first; the index of seller $j^*$ defines
+a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
+$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$.
+Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
+$k\ni\mcI_i$, $\g_i^k(a) \le z_i^j = \g_i^{j}(a)$,
+and so, using (\ref{union-eq}), 
+\begin{equation}\label{minimaleq}
+    \g_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
+\end{equation}
+Now, the buyer valuation function (\ref{buyervaluation}), guarantees
+that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
+\ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
+be accepted. 
+As $\bar{D}_i^j$ is non-decreasing, $\forall \ j\in \mcI_i$,
+$k\ni\mcI_i$,
+$$
+    D_i^j(y_i^j) \ge D_i^j(p_i^{j})\ge D_i^j(p_i^{k}).
+$$
 \iffalse
-(THE SELLERS ALL THE BUYERS IN $j$ HAVE IN COMMON! i.e. $j$ AND...)
-\begin{equation}%\label{lambda}
-    \Lambda = \displaystyle\bigcap_{i\in\mcI^j} \mcI_i,
-\end{equation}
-(THE COLLECTION OF BUYERS FROM EACH $i$ THAT ARE COMMON ACROSS ALL THE $i$'s SELLER
-POOLS)
-\begin{equation}%\label{llambda}
-    \lambda = \bigcup_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg)
-\end{equation}
+Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
+$\g_k^{j}(a) \ge \g_i^{j}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
+partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
+As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
+set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j}(a)
+\ge \g_k^{j}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
+We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
+$$
+    {\theta_i}'(\g_i^{k}(a)) \ge {\theta_i}'(\g_i^{j}(a)) \ge y_i^j.
+$$
+Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$...
 \fi
-Define $\Delta = \Lambda \cup \lambda$.
-Fixing all other bids $s_i^j \in \mcI$, and time $t>0\in\tau$, we have that,
-\begin{equation}\label{union-eq}
-    \displaystyle\sum_{j\in\Lambda} \theta_i^j = \sum_{i\in\lambda} \theta_i^j.
-\end{equation}
-}\\
-\textbf{Proof:}
-A local auction $j\in\mcI$, is determined by the collection of buyer bid
-profiles, where buyer bid $s_i^j > 0 \Rightarrow j\in\mcI_i$. Using Proposition \ref{sellerstrategy} and (\ref{jtoi}), we have that, 
-\begin{equation}\label{iff}
-    i\in\mcI^j \Leftrightarrow p_i^j > p_{i^*}^j,
-\end{equation}
-where
-(\ref{sellercoordinate}) defines $i^*$ as the losing buyer with the highest bid
-price in auction $j$. By (\ref{buyerinversedemand}) $p_i^j \ge
-p_{i^*}^j+\epsilon$, thus $p_i^j < p_{i^*}^j$ can only happen during a market
-shift caused by the underlying dynamics.
-Consider $k\in\mcI^j$ at time $t$ where, for example, some buyer(s) enter the auction, and
-so (\ref{iff}) implies that
-$\sum_{i\in\mcI^j} \g_i^j(a) > D^j$. Now, $p_i^j < p_{i^*}^j\Rightarrow k\ni\mcI^j$ and
-$s_k^j>0$ will cause $k$ to initiate a shift. By Proposition \ref{buyerstrategy}, $k$ will set $s_k^j=0$, and begin to add sellers to its pool.
-Suppose that at time $t$, $j$'s market is at equilibrium, i.e.
-$\sum_{i\in\mcI^j} \g_i^j(a) = D^j$, and fixing all other bids, so 
-no buyer $i\in\mcI^j$ rebids. Unless $k$ adds a seller with a higher reserve
-price within $\vert\mcI^j\vert$ time steps, by (\ref{newdata}), $D^j=0$ and the
-auction ends. Otherwise, at some time $t\in[t+1,\tau]$, we must have that
-$\g_k^j \le D^j$, and $k$ rejoins auction $j$ or opts-out. Finally, overlooking market shifts and messaging
-overhead, we have that,
-$\forall \ i\in\mcI^j$, $\nexists \ s_i^j > 0$ where $i \ni \mcI^j$, and (\ref{jtoi})
-holds.
-\iffalse
-Furthermore, we note that $\lambda \subset \mcI$ is a complete and disjoint set
-of bid vectors with respect to auction $j$. That is, $\forall \ i \in \mcI^j,
-s_i^k > 0 \in \lambda$ if and only if $s_i^k>0 \in\mcI$, and so $s_i \in \lambda
-\equiv s_i \in \mcI$. (NEED TO ADD TO LEMMA AND PROVE?)
-\fi
-
-Now, the subset $\mcI^j \subset \mcI$
-determines $j$'s reserve price $p_{i^*}^j$. We will assume the buyer submits a
-coordinated, truthful bid. Now, $\mcI_i\subset \mcI$ 
-determines the unit price $p_{i}$ in buyer $i$'s bid.
-The reserve price (\ref{newprice}) of seller $j$ is determined at each
-shift, and is
-the lowest price that $j$ will accept to perform any allocation.
-Let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, noting that $s_i^j=0, \ \forall \ i \in
-[s_i^j]_{i\ni\mcI^j}$, and let $p_i^*= f_i \circ \g_i^j(a)$ denote the bid price of buyer $i$, i.e. $p_i^k = p_i^*,
-\ \forall \ k \in\mcI_i$. 
-Using Proposition
-\ref{sellerstrategy}, for each $i \in \mcI^j$, we have from (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), that $p_i^* \ge p_*^k,
-\ \forall \ k \in\mcI_i$.
-
-\iffalse
-Now, we have,
-\begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
-\fi
-
-The incentive of each seller $\in\Lambda$ is to sell all of its data at the
-best possible price. In the simplest case,
-consider a disjoint local market $j$, where $\forall \ i\in\mcI^j$, $s_i^k = 0,
-\ \forall \ k\ne j \in \mcI_i \Rightarrow \Lambda = \lbrace j \rbrace$ and
-$\lambda = \mcI^j$. 
-Again using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), it is
-clear that $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-In all other cases, the sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
-%By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
-The set $\lambda$ represents all of the buyers influencing auction $j$, both
-directly and indirectly. 
-The bid price of buyer $i\in\mcI^j$ is determined by,
-\begin{equation}\label{maxbid}
-    p_i^* = \max_{k\in\mcI_i}\big(f^k \circ \g_i(a)\big)= \max_{k\in\mcI_i}(p_*^k).
-\end{equation}
-$\Lambda$ is the set of sellers directly influencing the bids of buyers
-in auction $j$. Now, the reserve price for auction $j$ is such that,
-\begin{equation}\label{resprice}
-    p_*^j \le \min_{i\in\mcI^j}(p_i^*) - \epsilon,
-\end{equation}
-from (\ref{newprice}). Now, by Proposition \ref{sellerstrategy}, in the absence
-of external influences caused by multi-auction market dynamics, we have 
-that $j$ maintains a local market equilibrium from time $t$ to $(t+1)$.
-From (\ref{lambda}) and (\ref{llambda}), $\Delta$ is defined by a seller $j\in\mcI$, where each
-user $k\in\Delta$ has some direct or indirect influence on $j$. 
-We may identify $\Delta$ by its dominant seller, and we denote $\Delta^j = \Lambda^j
-\cup \lambda^j$.
-
-Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$, and
-the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
-have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
-where,
-\begin{equation}\label{ordering}
-    p_*^k \le p_l^* < p_*^j \le p_i^*,
-\end{equation} 
-for any buyer $l\in\lambda^j$ such that $l\ni \mcI^j$. Now, suppose $\exists \ l\in\mcI^k$ such that $l\in\mcI^j \Rightarrow p_l^* \ge
-p_*^j$. In the case where $p_l^* > p_i^*$, we must have that 
-$\exists \ q \in \mcI_l$ such that $p_*^q > p_*^k$, % \Rightarrow \theta_l^q > \theta_l^k$. 
-which implies, again by (\ref{maxbid}), $q\ni\mcI_i \Leftrightarrow i
-\ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
-(\ref{iff}).
-Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
-0$, for some $g\in\mcI_i$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
-where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
-p_*^j \le p_l^* < p_i^*$, we examine $\mcI^k$ using (\ref{iff}),
-a shift in $\mcI^k$ causes a shift in $\mcI_i$, so that $\exists \ g\in\mcI_i$
-such that $p_*^g \ge p_*^j$. Thus, we
-determine a direct influence as $l\in\mcI^k
-\cap \Lambda^j$, such that $p_l^* > p_i^*$,
-and an indirect influence as, for any $l\in\mcI^k
-\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
-
-Now, consider the subset $\Lambda^j$, by
-Proposition \ref{userunion}, a shift occurs in 2 cases. (1) If $i\in\mcI^j$
-decreases its bid quantity so that $\sum_{i\in\mcI^j}
-\g_i^j(a) < D^j$, and (2) if buyer $i^*$, defined in Proposition
-\ref{sellerstrategy}, increases its valuation so that $p_{i^*}^j <
-p_*^j$. First, let buyer $i\in\mcI^j$ be the buyer in auction $j$ with the
-lowest bid price, the ``lowest clearing player",
-and further suppose $p_i^* > p_*^j + \epsilon$. That is, $\exists \ q \in \mcI_i$ such
-that $p_*^q > p_*^j$. Fixing all other bids, a decrease in $q$'s demand will
-directly impact buyer $i$. If at the end of the bid iteration, we still have that $i$ is the
-buyer with the lowest bid price, then (\ref{sellerinversedemand}) holds and $j$'s valuation does not change. Otherwise a new $i^*$ will be chosen upon
-recomputing $\mcI^j$, as in Proposition \ref{buyerstrategy}, and the market
-will attempt to regain equilibrium.
-Clearly, if $i^*$ in case (1) or resulting from case (2) increases in valuation,
-then $p_*^j$ will similarly increase, by (\ref{uservaluation}). Consider the 
-seller $k^*\in\mcI_{i^*}$ at time $t$, and suppose that $p_*^{k^*} \ge p_*^j$, however, we have that $p_{i^*}^j <
-p_*^j \Rightarrow i^* \ni \mcI^j \Rightarrow k^*\ni\Lambda^j\Rightarrow \mcI^{k^*} \ni
-\lambda^j$. Now, consider a buyer $l^*\in\mcI^{k^*}$. We need only consider the
-case where $\exists \ k \in\Lambda^j$ such that $l^*\in\mcI^k\subset \lambda^j$
-where we determine the influence of $\Delta^{k^*}$ on $\Delta^j$ by (\ref{iff}).
-
-In each case we
-have that (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold for
-some fixed time $t$, and so, $\forall \ i \in\mcI^j$,
-\begin{equation}\label{jdemand}
-    \int_0^{\g_i^j(a)} f^j(z) \ dz 
-    = \int_0^{\g_i^j(a)} f_i(z) \ dz,
-\end{equation}
-therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-Thus, any bid ouside of
-our construction
-has a zero valuation, with respect to buyers $\in\lambda$ and sellers
-$\in\Lambda$, and therefore cannot cause shifts to occur except through a
-shared buyer, e.g. some $l\in\mcI^k$. Thus, in all cases,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}) hold. Fixing all
-bids in any auction $q \ni \Lambda^j$,
-we have, $\forall \ k\in\mcI_i$,
-\begin{equation}\label{idemand}
-    \displaystyle\int_0^{D^k} f^k(z) \ dz = \sum_{i\in\mcI^k}\int_0^{\g_i^k(a)}
-f^k(z) \ dz,
-\end{equation}
-which holds $\forall \ k\in\mcI_i$, by (\ref{jtoi}) and Proposition
-\ref{sellerstrategy}..
-Finally, using (\ref{jdemand}), (\ref{idemand}), $\forall \ i\in\mcI^j, \forall \ k\in\mcI_i,\forall \ l\in\mcI^k$,
-\begin{align}\label{tieqtk}
-    \int_0^{\g_i^k(a)} f_i(z) \ dz &= \int_0^{\g_i^k(a)} f^k(z) \ dz,
-\end{align}
-and
-\begin{align}\label{tkeqtl}
-    \int_0^{\g_l^k(a)} f^k(z) \ dz &= \int_0^{\g_l^k(a)} f_l(z) \ dz.
-\end{align}
-Thus, with a slight abuse of notation for clarity,
-\begin{equation}\label{funion-eq}
-    \sum_{\lambda}\int_0^{\g(a)} f^\Lambda(z) \ dz =
-\sum_{\Lambda}\int_0^{\g(a)} f_\lambda(z) \ dz,
-\end{equation}
-where the result follows by construction, and the continuity of $\theta'$.
-$\qed$
-
-For completeness, in the case where the ISP $\kappa$ 
-does not adhere to the market dynamics, so $p^\kappa > p^j +
-\epsilon, \ \forall \ j \in\mcI$, then we may absorb the overage (difference) as part of the
-bid fee.
-(NEED TO DO BETTER WITH TIME?)
-
-\subsubsection{Mechanism Realization}
-
-\iffalse
-(DO I WANT UPDATES? MORE OR LESS FAIR? NEED EITHER UPDATE QUANTITY OR BOTH,
-IMPLICATIONS?)
-We assume that sellers update their bids with the ISP, which is modeled as a
-``buyer" $\kappa$. 
-\fi
-A buyer entering the market
-at $t=0$ is assumed to have an initial nonzero bid price, which we may assume
-(SAY BETTER! ALSO DO I REALLY NEED THE I.I.D?) is initialized as 
-an independently and identically distributed (i.i.d.) random variable $p_i^j=X$ with
-probability $\mathcal{P}$,
-$$
-    \mathcal{P}[\epsilon\le X \le \kappa] =
-\displaystyle\int_\epsilon^{p^\kappa} \mathfrak{f}(x) \
-ds,
-$$
-where $p^\kappa$ is the overage charge of the ISP, and $\mathfrak{f}$ the probability
-density function of $X$.
-%may represent by some homogenous function of degree one (EXPAND?).
-
-Consider a user seeking to prevent
-data overage charges by purchasing data from a subset of other network users.
-The sellers' auction will function as follows: at each bid iteration all buyers
-submit bids, and the winning bid is the buyer $i$ that has the highest price
-$p_i^j$. The seller allocates
-data to this winner, at which point all other buyers are able to bid again, and
-the winner leaves the auction (with the exception where multiple bidders bid
-the same price, where (\ref{dataallocation}) determines they will not fully
-satisfy their demand, and so we will assume they remain in the auction). The auction progresses as such until all the
-sellers' data has been allocated. 
-% SELLER ALGORITHM
-\begin{center}
-\begin{algorithm}[H]
-\caption{(Seller progressive allocation)}
-\begin{algorithmic}[1]
-\State $p^{j(0)} \gets \epsilon$, $s^{j(0)} \gets (p^j, D^j)$, $\bar\mcI =
-\emptyset$, compute
-$\mcI^{j(0)}$
-\State Update $s^j$ 
-\While{$D^j(t) > 0$}
-\State $\bar{i} \gets \displaystyle\max_{i\in I^j}\sum_{i\in I^j} p_i^j$ 
-\State $D^{j(t+1)} \gets D^{j(t)} - \g_{\bar{i}}^{j(t)}(a)$
-%\State $p^j \gets \theta_{i^*}'(d_{i^*}^j)\circ e_i$
-\State $p^j \gets p_{i^*}^j+\epsilon$ and $d^j \gets D^{j(t+1)}$
-\State $s^{j(t+1)} \gets (d^j, p^j)$
-\State Update $s^j$
-\State $\bar\mcI \gets \bar\mcI \cup \bar{i}$
-\For{$k \in \bar\mcI$}
-\If{$p_k^j < p_{i*}^j$}
-\State $D^{j(t+1)} = d_k^{j}$
-\State $\bar\mcI \gets \bar\mcI \setminus \lbrace k \rbrace$
-\EndIf
-\EndFor
-\State Compute $\mcI^{j(t)}$
-\State $\mcI^{j(t+1)} = \mcI^{j(t)}\setminus \bar\mcI$
-\State $t \gets t+1$
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-\end{center}
-Each time step, $s^j$ is updated it is shared with all
-participating buyers. At this point buyers have the opportunity to bid again,
-where a buyer that does not bid again is assumed to hold the same bid, since a
-buyer dropping out of the auction will set their bid to $s_i^j=(0,0)$.
-
-% SELLER ALGORITHM
-\begin{center}
-\begin{algorithm}[H]
-\caption{(Buyer response)}
-\begin{algorithmic}[1]
-\State $p_{i(0)} \gets \epsilon$, $s_{i(0)} \gets (p_i, D_i)$, $D_t \gets D_i$, compute
-$\mcI_{i(0)}$
-\State Update $s_i$ 
-\While{$D_i(t) > 0$}
-\State $D_{i(t+1)}^j \gets \sum_{j\in\mcI_i}\g_i^{j(t)}(a)$
-\If{$D_{i(t+1)}^j < D_t$}
-    \State Compute $\mcI_{i(t)}$
-    \State $p_i \gets \theta_i(\g_i(a))$
-\EndIf
-\State $s_{i(t+1)} \gets (\g_i(a), p_i)$
-\State Update $s_i$
-\State $D_{i(t+1)}^j \gets D_{i(t)}^j$
-\State $t \gets t+1$
-\EndWhile
-\end{algorithmic}
-\end{algorithm}
-\end{center}
+Thus (\ref{minimaleq}) holds and so, by (\ref{dataallocation}),
+\begin{align*}
+     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j, \bigg\lbrack D^{j} - \sum_{p_k^{j}> y_i^{j}}
+d_k^{j}\bigg\rbrack^+\bigg) \\
+    &= z_i^{j}= \g_i^{j}(a)
+\end{align*}
+where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
+From (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
+0 \ \forall \ y < p_{i^*}^j$, and $\bar{D}_i^j(y, s_{-i}) =0 \le \epsilon
+\Rightarrow \g_i^j(a) = 0 \Rightarrow z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
+\begin{align*}
+    \displaystyle\sum_{j\in\mcI_i} c_i^j(z_i,y_i) =\sum_{j\in\mcI_i}
+c_i^j(z_i,p_i),
+\end{align*}
+thus (\ref{costcoordination}) simply shows that changing the price $p^j_i$ to $y^j_i$ does not exclude any
+additional buyers, as the bid $p^j_i$ was already above the reserve price of any
+seller $j \in \mcI_i$.
+We proceed to show that $x_i$ does not result in a loss of utility for
+buyer $i$, that is,
+$$
+    u_i \le u_i(z_i,y_i).
+$$
+From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = \g_i^j(a(z_i,y_i))$, 
+and so,
+$$
+    \theta_i\circ \g_i^j(a(z_i,y_i)) = \theta_i\circ \g_i^j(a),
+$$ 
+which holds $\forall \ j\in\mcI_i$.
+Therefore, by the definition of utility (\ref{buyerutility}),
+and the buyers' valuation (\ref{buyervaluation}), 
+\begin{align*}
+    &\theta_i\circ \g_i(a(z_i,y_i)) - \theta_i(a)\circ \g_i(a) \\
+    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
+    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - x) \ dx.
+\end{align*}
+Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
+$z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
+$\qed$}
+%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
+
+\subsection{Proof of Proposition 4.2}
+\proof{
+We claim that $t_i$ is an $\epsilon$-best reply for buyer $i$. That is,
+$$
+    u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;s_{-i}).
+$$
+As a result of auction initialization, a seller $j$'s valuation defines its
+reserve price to be determined
+by a buyer $i \ni \lambda$, even if this price is zero, we have that $p^j =
+\epsilon \ge 0 \ \forall \ j \in\Lambda$.
+Let $z = \sup(\chi_i^j)$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
+price of auction $j$, and $p_i^*= f_i \circ \g_i^j(a)$ denote the (coordinated) bid price of buyer $i$. 
+We have that $i\in\mcI^j$, 
+and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
+max of the reserve prices $p_*^j,\ \forall \ j\in\mcI_i$, therefore
+(\ref{eta}) is such that,
+$$
+    \theta_i'(z) > \max_{j\in\Lambda}P_i^j(v_i^j),
+$$ 
+which implies, as $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
+we have $\forall \ j \in \mcI_i$, 
+\begin{align*}
+    w_i^j &> P_i^j(v_i^j) \\
+    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
+\end{align*}
+And so, by (\ref{dataallocation}),
+\begin{align*}
+    a_i^j(t_i;s_{-i}) &= v_i^j \\
+    \Rightarrow \displaystyle\sum_{j\in\Lambda} a_i^j(t_i;s_{-i}) &= z.
+\end{align*}
+Therefore, $\forall \ j\in\Lambda$ and $\forall \ i \in \lambda$ such that
+(\ref{tieqtk}) and (\ref{tkeqtl}) hold,
+\begin{align*}
+    \int_0^{v_i^j} \bar{P}_i(x) \ dx 
+    = \sum_{j\in\Lambda}\int_0^{\g_i^j(z)} P_i^j(x) \ dx.
+\end{align*}
+It follows that,
+$$
+    u_i(t_i;s_{-i}) = \int_0^{z} \theta_i'(x) \ dx -  \g_i \ \circ \int_0^{z} \bar{P}_i(x) \ dx.
+$$
+Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
+s_{-i}) + \epsilon$. Propositions
+\ref{coordinationlemma} and
+\ref{buyerstrategy}, define the coordinated bid, $\nu_i=(\zeta_i, p_i)$,
+% = (\g_i\circ a_i(s), \ \theta_i'(z)) = (z_i, c_i),$
+using (\ref{tieqtk}) and (\ref{tkeqtl}),
+for each $j\in \Lambda$, $\g_i^j(a_i^j(\nu_i; s_{-i})) = \zeta_i^j$,
+then clearly $u_i(\nu_i, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
+u_i(s_i;s_{-i}) > \epsilon$. Denoting $\zeta_i^j$ (fixed) as $\zeta$, 
+$$
+    \int_z^{\zeta} {\theta_i}'(x) \ dx-\int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
+$$
+For concave valuation functions, the first-order derivative of $\theta$ at point
+$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
+/ \theta'(0)$ guarantees that new bids will differ by at least
+$\epsilon$, and as such, buyer $i$ will remain in
+any local auction with reserve price determined by (\ref{newprice}). We therefore
+verify that,
+$$
+    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
+dx \le \epsilon,
+$$
+and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
+$$
+    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
+\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
+$$
+If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
+$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
+\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
+Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
+\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
+exist.
+Finally, as we may consider $\Delta \subset \mcI$ to be a
+multi-auction game, our user strategies form a ``truthful" local game 
+with strategy space restricted to $\epsilon$-best replies from buyers $\in
+\lambda$. Therefore we have that a fixed point in the ``truthful" game is a fixed point for the auction. 
+$\qed$}
+
+\section{A Simple Example}
+\example
 Finally, we give a simple example of convergence to a local market equilibrium,
@@
 $\epsilon$-best replies.
+
 \begin{center}
@@
 
-% VCG ANALYSIS
-\section{PSP Analysis}\label{analysis}
-
-\subsection{Equilibrium}
-
-We intend to show evidence shared network optima (a
-global optimum). 
-A buyer $i\in\mcI$ will have incentive to change its bid
-quantity if it increases its opt-out value $\g_i$, and therefore its utility (\ref{buyerutility}). 
-We will show that, without loss of utility, buyer $i$ may  
-use a ``consistent" bid strategy within its seller pool, i.e. $d_i^j = d_i^k, \
-\forall \ j,k \in \mcI_i$, and as such,
-Proposition \ref{buyerstrategy} supports an optimal strategy with respect to
-(\ref{buyerutility}). 
-Our result shows that a buyer may select $\mcI_i$ in order to maximize its
-utility while maintaining a coordinated bid strategy. 
-Reasonably, if $j^*< I$, a buyer may increase the size of its seller pool
-$\mcI_i$, thereby lowering its coordinated bid
-quantity while obtaining the same (potential) allocation $a_i$. 
-As buyer $i$ submits identical bids to multiple auctions, the bid price must be
-as high as the highest reserve price $p_i^j \in \mcI_i$.
-Buyer $i$'s bid then has identical bid price $p_i^j \forall \ j \in\mcI_i$. 
-We further note that $i$ optimal strategy does not require reducing its bid price to a
-minimum in each auction, where
-the bid quantity $\g_i^j(a)$ is still fufilled. The pricing rule of the PSP
-auction dictates that a buyer $i$ will pay the cost of excluding other players from
-the auction, and as $i$'s bid price reflects its valuation of it data
-requirement $D_i$ across all local markets, we have identical bid prices in
-each auction where $s_i^j>0$. Obviously, if $j\ni\mcI_i$, then $\theta_i^j = 0$.
-
-% BUYER COORDINATION
-{
-\lemma{(Opt-out buyer coordination)}\label{coordinationlemma} 
-Let $i\in\mcI$ be a opt-out buyer and fix all sellers' profiles $s^j$.
-For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be a
-tentative data
-allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
-\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
-\begin{align*}
-    z_i^j &= \g_i^{j}(a), \\
-    y_i^j &= \theta_i'(z_i^j).
-\end{align*}
-Furthermore,
-\begin{equation}\label{allocationcoordination}
-    a_i^j(z_i,y_i) = z_i^{j},
-\end{equation}
-and
-\begin{equation}\label{costcoordination}
-    c_i^j(z_i,y_i) = y_i^{j},
-\end{equation}
-where $i$'s strategy is as in Proposition \ref{buyerstrategy}.
-}\\
-\textbf{Proof:}
-As $s_{-i}$ is fixed, we omit it, in addition, we will use $u\equiv u_i \equiv u_i(s_i) \equiv
-u_i(s_i;s_{-i})$. In full notation, we intend to show
-$$
-    u_i((d_i,p_i);s) \le u_i((z_i,y_i);s_{-i}).
-$$
-Now, if there exists a seller who can fully satisfy $i$'s demand,
-then $\vert\mcI_i\vert = 1$, and the case is trivial as no
-coordination is necessary for a single bid. %(SPECIAL CASE OF MONOPOLY? THINK!)\\
-Otherwise, buyer $i$'s demand can only be satisfied by purchasing data from
-multiple sellers.
-We will show that $i$ may increase $\vert\mcI_i\vert$, and so decreasing
-$d_i^j, \ \forall \ j\in\mcI_i$, without decreasing $\sum_{j\in\mcI_i}u_i^j$.
-Buyer $i$ maintains ordered set $\mcI_i$ where the sellers with the
-largest bid quantities are considered first; the index of seller $j^*$ defines
-a minimal subset $\mcI_i$, satisfying (\ref{buyercoordinate}). By construction, 
-$d_i^{j^*}$ is the minimum quantity bid offered by any $j\in \mcI_i$.
-Thus by (\ref{buyercoordinate}) and (\ref{opt-eq}), $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$, $\g_i^k(a) \le z_i^j = \g_i^{j}(a)$,
-and so, using (\ref{union-eq}), 
-\begin{equation}\label{minimaleq}
-    \g_i^{j}(a)  \le \bigg\lbrack D^{j} - \sum_{k\in \mcI^j : p_k^{j}> y_{i}^{j}} d_k^{j}\bigg\rbrack^+.
-\end{equation}
-Now, the buyer valuation function (\ref{buyervaluation}), guarantees
-that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
-\ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
-be accepted. 
-As $\bar{D}_i^j$ is non-decreasing, $\forall \ j\in \mcI_i$,
-$k\ni\mcI_i$,
-$$
-    D_i^j(y_i^j) \ge D_i^j(p_i^{j})\ge D_i^j(p_i^{k}).
-$$
-\iffalse
-Furthermore, suppose there exists buyer $k\in \mcI^j$, such that
-$\g_k^{j}(a) \ge \g_i^{j}(a)$ and $D^j - \sum_{k\in\mcI^j,k\ne i}d_k^j < z_i^{j}$, resulting in a
-partial allocation. Bid $s_k^j \in s_{-i}$, and so is considered in buyer $i$'s strategy. 
-As buyer $i$ is allowed to choose subset $\mcI_i$, and $\mcI_i$ is a minimal
-set, (\ref{buyercoordinate}) states that $n$ is such that $\g_i^{j}(a)
-\ge \g_k^{j}(a)$ for any $k\in\mcI$, therefore such a buyer $k$ cannot exist.
-We have, $\forall \ j\in \mcI_i$, $k\ni\mcI_i$,
-$$
-    {\theta_i}'(\g_i^{k}(a)) \ge {\theta_i}'(\g_i^{j}(a)) \ge y_i^j.
-$$
-Now, suppose that $p_k^j = p_i^j$, however $d_k^j > d_i^j$...
-\fi
-Thus (\ref{minimaleq}) holds and so, by (\ref{dataallocation}),
-\begin{align*}
-     a_i^j(z_i,p_i) &=\min_{i\in\mcI^j}\bigg(z_i^j, \bigg\lbrack D^{j} - \sum_{p_k^{j}> y_i^{j}}
-d_k^{j}\bigg\rbrack^+\bigg) \\
-    &= z_i^{j}= \g_i^{j}(a)
-\end{align*}
-where the last equality is by definition, and so (\ref{allocationcoordination}) is proven.
-From (\ref{datacomposed}), $\bar{D}_i^j(y, s_{-i}) =
-0 \ \forall \ y < p_{i^*}^j$, and $\bar{D}_i^j(y, s_{-i}) =0 \le \epsilon
-\Rightarrow \g_i^j(a) = 0 \Rightarrow z_i^k = 0, \ \forall \ k \ni \mcI_i$, and therefore,
-\begin{align*}
-    \displaystyle\sum_{j\in\mcI_i} c_i^j(z_i,y_i) =\sum_{j\in\mcI_i}
-c_i^j(z_i,p_i),
-\end{align*}
-thus (\ref{costcoordination}) simply shows that changing the price $p^j_i$ to $y^j_i$ does not exclude any
-additional buyers, as the bid $p^j_i$ was already above the reserve price of any
-seller $j \in \mcI_i$.
-We proceed to show that $x_i$ does not result in a loss of utility for
-buyer $i$, that is,
-$$
-    u_i \le u_i(z_i,y_i).
-$$
-From (\ref{allocationcoordination}), we have $a_i^{j}(z_i,y_i) = z_i^{j} = \g_i^j(a(z_i,y_i))$, 
-and so,
-$$
-    \theta_i\circ \g_i^j(a(z_i,y_i)) = \theta_i\circ \g_i^j(a),
-$$ 
-which holds $\forall \ j\in\mcI_i$.
-Therefore, by the definition of utility (\ref{buyerutility}),
-and the buyers' valuation (\ref{buyervaluation}), 
-\begin{align*}
-    &\theta_i\circ \g_i(a(z_i,y_i)) - \theta_i(a)\circ \g_i(a) \\
-    &= u_i(z_i,y_i) - u_i =  \displaystyle\sum_{j\in\mcI_i} c_i^j -c_i^{j}(z_i,y_i)\\
-    &= \sum_{j\in\mcI_i}\int_{a_i^j(z_i,p_i)}^{a_i^j} f_i(d_i^j - x) \ dx.
-\end{align*}
-Then, as $a_i(z_i,p_i) \le z_i^j \le a_i^j $, and noting that
-$z_i^j>0\Rightarrow \theta_i\ge 0\Rightarrow f_i\ge 0$, we have $u_i(z_i,y_i) - u_i \ge 0$, $\forall \ j\in\mcI_i$.
-$\qed$
-%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
-
-\subsubsection{Incentive Compatibility}
-
-The property of truthfullness is an essential component of equilibrium in
-second-price markets. The strategies described in this paper have removed the
-necessity for a user to determine its own valuation function, we intend to show that the market dynamics resulting from the
-construction of the user strategy space results in truthful bids that are optimal for all users,
-i.e. bid prices are to the marginal value as determined by market dynamics. 
-To achieve incentive compatibility, we find that the opt-out buyer must choose
-this subset so that its overall marginal value is greater than its market price.
-We have so far only made the \emph{assumption} of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
-has incentive to change its bid as a result of a market shift or partial
-allocation. In a truthful reply, the term $\epsilon/\theta_i'(0)$
-ensures that a new bid price differs from the last bid price by at least
-$\epsilon$, thereby ensuring that a buyer does not change its bid without
-correcting the effects of unstable shifts.
-We argue that if truthfulness holds \emph{locally} for both buyers and sellers, i.e. $p_i ={\theta_i}' \
-\forall \ j \in \mcI_i$ and $p^j = {\theta^j}' \ \forall \ i \in\mcI^j$, then
-there exists a market equilibrium extending over a subset of connected
-local markets. 
-For a buyer $i$, define the set of possible $\epsilon$-best replies,
-\begin{equation}\label{e-bid}
-    S^\epsilon(s) = \lbrace s_i\in S_i(s_{-i}) : u(s_i;s_{-i}) \ge
-u_i(s_i';s_{-i}) -\epsilon, \ \forall \ s_i'\in S_i(s_{-i})\rbrace,
-\end{equation}
-and the set of \emph{truthful} bids, 
-\begin{equation}\label{t-bid}
-    T_i = \lbrace s_i\in S_i(s_i) : z=\displaystyle\sum_{j\in\mcI_i} \g_i^j(a)
-\wedge p_i = \theta_i'(z)\rbrace,
-\end{equation}
-where $\wedge$ denotes the logical ``and" operator. We note that the ``strategic" set $T_i$
-is restricted by Proposition \ref{buyerstrategy}.
-We have the following Proposition,
-
-{
-\proposition{(Incentive compatibility across local auctions)}\label{incentive}
-Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
-$t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
-buyer $i\in \mcI^j$, let $s_l$ also be fixed $\forall \ l\ni i \in \lambda$. Define,
-\begin{align}
-\begin{split}\label{eta}
-    \chi_i &= \bigg\lbrace x\in [0,D_i] : 
- {\theta_i}'(x) > \max_{j\in\Lambda}P_i^j(x)\bigg\rbrace, 
-\end{split}
-\end{align}
-and $z = \sup(\chi_i - \epsilon / \theta_i'(0))^+$, and for each $j \in
-\Lambda$, 
-$$
-    v_i^j = \g_i^{j}(z),
-$$
-and 
-$$
-    w_i^j = \theta_i'(z).% \circ e = \theta_i'(v_i^j).
-$$
-Then a (coordinated) $\epsilon$-best reply for the opt-out buyer is $t_i =
-(v_i,w_i) \in T_i\cap S_i^\epsilon(s_{-i})$, i.e., $\forall \ s_i, u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;
-s_{-i})$.
-With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
-$\in\Delta$. Therefore, a fixed point $\in \Delta$ is a fixed point in
-the multi-auction game. 
-}\\
-\textbf{Proof:}
-We claim that $t_i$ is an $\epsilon$-best reply for buyer $i$. That is,
-$$
-    u_i(t_i;s_{-i}) + \epsilon \ge u_i(s_i;s_{-i}).
-$$
-As a result of auction initialization, a seller $j$'s valuation defines its
-reserve price to be determined
-by a buyer $i \ni \lambda$, even if this price is zero, we have that $p^j =
-\epsilon \ge 0 \ \forall \ j \in\Lambda$.
-Let $z = \sup(\chi_i^j)$, and again let $p_*^j = f^j \circ \g_i^j(a) $ denote the reserve
-price of auction $j$, and $p_i^*= f_i \circ \g_i^j(a)$ denote the (coordinated) bid price of buyer $i$. 
-We have that $i\in\mcI^j$, 
-and (\ref{buyerinversedemand}) defines $\theta_i'(z)$ as being
-max of the reserve prices $p_*^j,\ \forall \ j\in\mcI_i$, therefore
-(\ref{eta}) is such that,
-$$
-    \theta_i'(z) > \max_{j\in\Lambda}P_i^j(v_i^j),
-$$ 
-which implies, as $\theta_i'$ is non-increasing and $P_i^j \ge 0$,
-we have $\forall \ j \in \mcI_i$, 
-\begin{align*}
-    w_i^j &> P_i^j(v_i^j) \\
-    \Rightarrow v_i^j &\le D_i^j(w_i^j) = D^j - \rho^j(w_i^j).
-\end{align*}
-And so, by (\ref{dataallocation}),
-\begin{align*}
-    a_i^j(t_i;s_{-i}) &= v_i^j \\
-    \Rightarrow \displaystyle\sum_{j\in\Lambda} a_i^j(t_i;s_{-i}) &= z.
-\end{align*}
-Therefore, $\forall \ j\in\Lambda$ and $\forall \ i \in \lambda$ such that
-(\ref{tieqtk}) and (\ref{tkeqtl}) hold,
-\begin{align*}
-    \int_0^{v_i^j} \bar{P}_i(x) \ dx 
-    = \sum_{j\in\Lambda}\int_0^{\g_i^j(z)} P_i^j(x) \ dx.
-\end{align*}
-It follows that,
-$$
-    u_i(t_i;s_{-i}) = \int_0^{z} \theta_i'(x) \ dx -  \g_i \ \circ \int_0^{z} \bar{P}_i(x) \ dx.
-$$
-Suppose $\exists \ s_i = (d_i, p_i)$ such that $u_i^j(s_i;s_{-i}) > u_i^j(t_i;
-s_{-i}) + \epsilon$. Propositions
-\ref{coordinationlemma} and
-\ref{buyerstrategy}, define the coordinated bid, $\nu_i=(\zeta_i, p_i)$,
-% = (\g_i\circ a_i(s), \ \theta_i'(z)) = (z_i, c_i),$
-using (\ref{tieqtk}) and (\ref{tkeqtl}),
-for each $j\in \Lambda$, $\g_i^j(a_i^j(\nu_i; s_{-i})) = \zeta_i^j$,
-then clearly $u_i(\nu_i, s_{-i}) \ge u_i(s_i, s_{-i}) \Rightarrow u_i(t_i;s_{-i}) -
-u_i(s_i;s_{-i}) > \epsilon$. Denoting $\zeta_i^j$ (fixed) as $\zeta$, 
-$$
-    \int_z^{\zeta} {\theta_i}'(x) \ dx-\int_z^{\zeta} \bar{P}_i(x) \ dx > \epsilon.
-$$
-For concave valuation functions, the first-order derivative of $\theta$ at point
-$0$ gives the maximum slope of the valuation function, and so the factor $\epsilon
-/ \theta'(0)$ guarantees that new bids will differ by at least
-$\epsilon$, and as such, buyer $i$ will remain in
-any local auction with reserve price determined by (\ref{newprice}). We therefore
-verify that,
-$$
-    \displaystyle\int_{z}^{z +\epsilon / \theta_i'(0)} \theta_i'(x) \
-dx \le \epsilon,
-$$
-and as $P_i^j \ge 0$, we have that, from the construction of $\zeta$,
-$$
-    \displaystyle\int_{z+\epsilon / \theta_i'(0)}^\zeta \theta_i'(x) \ dx -
-\int_{z+\epsilon / \theta_i'(0)}^\zeta \bar{P}_i(x) \ dx > 0.
-$$
-If $\zeta > z + \epsilon / \theta_i'(0)$, then for some $\delta >0$,
-$\theta_i(z+\epsilon / \theta_i'(0)+\delta) > P_i^j(z+\epsilon /
-\theta_i'(0)+\delta)$, contradicting (\ref{eta}).
-Now, if $\zeta \le z$, then $\theta_i'(z+\epsilon / \theta_i'(0)) < P_i^j(z+\epsilon /
-\theta_i'(0))$, also a contradiction of (\ref{eta}), and so buyer $s_i$ cannot
-exist.
-Finally, as we may consider $\Delta \subset \mcI$ to be a
-multi-auction game, our user strategies form a ``truthful" local game 
-with strategy space restricted to $\epsilon$-best replies from buyers $\in
-\lambda$. Therefore we have that a fixed point in the ``truthful" game is a fixed point for the auction. 
-$\qed$\\
-
-The strategy space is comprised of a collection of bid, or ``strategy", vectors that
-together, may be represented as a collection of potential functions, where change in buyer $i$'s
-utility, resulting from a change in strategy, equals the change in
-the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
-formulated by mapping the incentives of all users in a local auction to a
-single function. The goal of our analysis is to therefore construct a global potential function that encompasses
-all local markets. Then, we may determine a Nash equilibrium by finding a local
-optima of the potential function. Additionally, as the potential function also
-iterates, it may be used in an analysis of convergence. The
-convergence of a Nash equilibrium results from the progression of
-$\epsilon$-best replies, where each subsequent bid is a unilateral
-improvement, provided that $t_i$ is continuous in opponent profiles.
-From the original proof by \cite{lazar}, we observe that the collection of
-unconstrained truthful bids may be a subset
-of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
-%An essential component of determining the existence of a Nash equilibrium is 
-For this work, it suffices to show the continuity of the set of truthful
-$\epsilon$-best replies in the set of opponent bid profiles.
-In order to address continuity in a global sense, we must demonstrate
-continuity in the construction of our model.
-Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
-and determine the
-existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
-correspondence,
-{
-\definition{(Correspondence)}
-A correspondence is mathematically defined as an ordered triple $(X,Y,R)$, where $R$ is a relation from $X$ to
-$Y$, i.e. any subset of the Cartesian product $X\times Y$.
-}
-
-In an economic model, a correspondence $(S_i,S_{-i},R)$ defines a map from $S_i$
-to the power set $S_{-i}$, where $R$ is a binary relation, i.e. $R \subset
-S_i\times S_{-i}$. The classic
-example of a correspondence in our model is the buyers' best response
-$B_i^\epsilon$, where, for the multi-auction,
-$S_i$ and $S_{-i}$ are built by repeatedly using the
-cartesian product over bid profiles. The power set 
-$S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
-product of ordered sets. 
-The best response is a reaction correspondence
-defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
-S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
-profiles $S_{-i}$. \\
-\textbf{Remark:} 
-The ease by which the game is constructed is a consequence of the the cartesian
-product on a 2-dimensional message space. \\
-A natural induced topology of this space is the product
-topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.
-
-Motivated by the symmetric nature of supply and demand, we determine the
-game-theoritical argument is complemented by an abstract-theoretical analysis.
-In fact, we may even be philosophically motivated, as the truth value of a bid
-is determined only by how it relates to markets, and whether it provides an
-accurate correspondence. Using a set-theoretical approach to address the sellers
-bids, we derive our result from the symmetry of supply and demand,
-(\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
-\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
-\ref{buyercoordinate}, and include the following corollary,
-{
-\corollary{Data-bid correspondence (seller cooperation)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}).
-For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
-$\epsilon$-best reply.
-}\\
-\textbf{Proof:}
-We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
-strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
-We use the the axiom of set equality,
-based on first-order logic with equality, which states that,  
-$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
-\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
-Then, for any allocation $a$, we may define the relation, $i\thicksim
-j$,
-\begin{equation}\label{eqrel}
-        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
-        \big(\g_i^j(a),y)\big).
-\end{equation}
-Formally, the axiom states that a set is \emph{uniquely} determined by its
-members. It follows that $\thicksim$ defines equality of bids using a static
-analysis with respect to equilibrium, where all users who are not changing thier
-bids are considered equal.\\
-\textbf{Remark:} Equality is both an equivalence relation and a partial order,
-and therefore is reflexive, transitive, symmetric and antisymmetric. \\
-Now, we may define the mapping $s \mapsto [s]$,
-\begin{equation}\label{indeqrel}
-         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
-\end{equation}o
-noting that equality in the bid quantity is implicity satisfied and $z =
-\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
-buyer-seller pair. Without loss of generality, let $S = \Pi_{j\in\mcI} \big(
-\Pi_{i\in\mcI} S_i^j$. The indicator function is the canonical mapping,
-$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
-topology is preserved, the set of all indicator
-functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
-S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
-\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
-$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$.
-
-{
-\proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
-$i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
-}\\
-\textbf{Proof:}
-Define $\g_i \circ \overline{P} = \max_{i\in\mcI^j} \theta_i'(0)$, and
-$\bar{P}_i(z, s_{i}) = \underline{P} = \epsilon -\varrho$, where $\epsilon$ is
-the bid fee, and $\varrho$ is $i$'s liability estimate for auction $j\in\mcI$. 
-We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
-$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
-we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
-\overline{P}]^{\vert \mcI^j\vert})$
-is a product of closed subsets of compact sets. Now, we have that a closed
-subset of a compact set is compact and the resulting product topology gives
-Tychonoff's theorem. every product of a
-compact space is compact, we have $\g_i \circ B_i^\epsilon$
-is compact subset of $B_i^\epsilon$.
- Now, letting $\overline{P} = \max_{i\in\lambda^j} \theta_i'(0)$, and we have by
-definition of $\Delta$ and the product, 
-\begin{align*}
-    \g_i \circ& S_i(s_{-i}) \equiv g_i\vert_{\Lambda^j} : S_i \mapsto S_i \\
-    &\Rightarrow\bigg(\bigcup_{i\in\mcI^j} [0,D^k]_{k\in\mcI_i},
-[0,\overline{P}]\bigg)
-    = \bigcup_{i\in\mcI^j}\bigg([0,D^k]_{k\in\mcI_i} \times
-[0,\overline{P}]\bigg) \\
-    &=  ([0,D^k]_{k\in\Lambda^j}, [0,\overline{P}]) \in \Lambda^j
-\times \lambda^j \subset T.
-\end{align*}
-The result follows from the fact that $t_i$ is continuous in $s_i$, as was
-proven in \cite{semret}, and as a finite union of compact sets is a compact set.
-$\qed$
-on any subset $\lbrace
-s_{-i}\in S_i : \ \forall \ z > 0, \overline{P} \ge P_i(z,s_{-i}) \ge
-\underline{P} \rbrace$, where $0<\underline{P}\le \overline{P} < \infty$
-(HERE) The dimension of a linear space is defined as the maximal number of linearly
-independent vectors or, equivalently, as the minimal number of vectors that span
-the space
-
-%We have proven that buyers will submit bids according to their marginal
-%valuations. Now, in the interest of completeness (BAD SENTENCE), 
-We have that all bids represent $\epsilon$-best replies, and, as was proven in
-\cite{lazar}, the sellers' positive reserve price implies that bids are
-truthful. Finally, by properties determined by the construction of a mixed strategy
-symmetric game with a 2-dimensional message space, we may now restrict our
-analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.
-
-{
-\corollary{Hemicontinuity of $\Delta$}
-}
-
-The data-sharing market consists of inter-dependent sets of these
-multi-auction games around possible fixed points.  Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
-between the different subsets $\Delta$ form a sufficiently connected set that
-the heirarchy described in Proposition \ref{userunion} holds. Then,
-there can only be a single primary fixed point, where the sellers' reserve
-price is an equilibrium price in the global market. 
-We first address the analytical approach, and demonstrate properties of
-$\Delta$ as a finite-dimensional linear topological space. We have that the
-reserve price of the sellers, and the bid price of the buyers is constant
-within an interval of length 2$\epsilon$. We have that 
-(HERE) We have the following
-Corollary, (MIGHT NEED TO REDEFINE.. NOT CLEAR IS A SEQUENCE, SHOULD BE
-SEQUENCE OF PRICES INSTEAD OF USERS?) 
-{
-\corollary{(Primary fixed point)}
-Let the set of shared buyers be denoted as,
-$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
-sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
-$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
-\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
-for a fixed time $t$,
-$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
-k\ne j\in\overline{\Lambda}$. 
-}\\
-(CAN PROBABLY USE ALL BUYERS HERE... BECAUSE OF INF)
-\textbf{Proof:}
-We assume a finite number of users, with continuous valuation functions bounded both
-above and below. From the assumption that $\overline{\Lambda}$ is not a
-partition, we have that the limits exist with respect to bid price $p_i^j$, 
-$$
-    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
-$$
-is the primary seller $j$, and we have the market price $p_*^j$ from,
-$$
-    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
-\lambda^k,
-$$
-and the result follows from Lemma \ref{uservaluation}, Proposition
-\ref{userunion} and Proposition \ref{incentive}.
-(NEED TO SHOW THEY ARE EQUAL...)
-%$\qed$\\
-(USE BOREL-CANTELLI WITH I.I.D? FUTURE WORK?)
-
-We show that our bidding strategy is
-part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
-equilibrium, where the sellers reserve prices are fixed.
-{
-\lemma{(Static Nash Equilibrium)} 
-Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
-let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
-sellers reserve prices at $t\in(0,\tau), \ \forall \ j\in\mcI$.
-Using the rules of the data auction mechanism applied independently by each
-user, where users are acting according to their respective strategies, the multi-auction game converges to an $\epsilon$-Nash equilibrium. 
-}\\
-\textbf{Proof:}
-(CAN'T DO THIS, NOT THE SAME TYPE OF GAME?)
-As $\theta_i'$ is continuous, as was shown in Lemma \ref{uservaluation}, and
-$t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
-$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
-represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
-and we may use Brouwer's fixed point theorem, as in \cite{semret},
-
-As a result of user behavior, and subsequent strategies, we determine that the
-data-exchange market behaves in a predictable way. However,
-each auction may be played on the same or on a different scale in
-valuation, time and quantity, and so the rate at which market fluctuations occur is
-impossible to predict (NEED HELP!). 
-Arrow's paradox is an impossibility theorem stating that when buyers have three
-or more distinct alternatives (auctions), no deterministic ranking system can
-convert the ranked preferences of users into a market-wide (complete
-and transitive) ranking while also meeting a specified set of criteria:
-unrestricted domain, non-dictatorship, Pareto efficiency and independence of
-irrelevant alternatives. It follows that the case where
-$\theta_i = \theta^j$ as in (\ref{buyerinversedemand}) and
-(\ref{sellerinversedemand}) will only occur if each set $\Lambda \cup \lambda$
-is disjoint.
-
-Nonetheless, we claim that our mechanism is normative, that irrelevant
-alternatives should not matter, it is practical, uses minimal information,
-strategy, and provides the right incentives for the truthful revelation of individual preferences.
-
-The rules of the PSP
-multi-auction drive market mutations that evolve and are regulated by the user
-strategies.
-(HERE)
-
-(DEFINITION.. USE?)
-In the General Symmetric Game, p is an evolutionarily stable mixed strategy if
-there is a (small) positive number y such that when any other mixed strategy q
-invades p at any level x < y, the fitness of an organism playing p is strictly
-greater than the fitness of an organism playing q.
-(EXPAND)
-% DATA NASH EQ
-{
-\theorem{(Dynamic Nash Equilibrium)}
-Using the rules of the data auction mechanism, the CMHK
-\cite{zheng} converges to a $\epsilon$-Nash equilibrium. In the network auction
-game with the data-PSP rules applied independently by each user according to their respective strategies, the secondary market converges to an $\epsilon$-Nash
-equilibrium. 
-}\\
-\textbf{Proof:}
-
-\subsection{Efficiency}
-
-Formally, the
-mechanism is efficient, if, at equilibrium, the allocation maximizes
-$\sum_i\theta_i(a_i)$.
-(NEED OWN WORDS)
-The objective in designing the auction is that, at equilbrium, resources al-
-ways go to those who value them most. Indeed, the PSP mechanism does
-have that property. This can be loosely argued as follows: for each player,
-the marginal valuation is never greater than the bid price of any opponent
-who is getting a non-zero allocation. Thus, whenever there is a player j
-whose marginal valuation is less than player i 's and j is getting a non-zero
-allocation, i can take some away from j , paying a price less than i 's marginal
-valuation, i.e. increasing u i , but also increasing the total value, since i 's
-marginal value is greater. Thus at equilibrium, i.e. when no one can unilat-
-erally increase P their utility, the total value is maximized.
-
-\subsection{Convergence}
-
 %\end{multicols}
-
-%\bibliographystyle{acm}
-%\bibliography{paper.bib}
-
-%\iffalse
-\begin{thebibliography}{9}
-
-\bibitem{zheng}
-L. Zheng, C. Joe-Wong, C. W. Tan, S. Ha and M. Chiangs, 
-\textit{Secondary markets for mobile data: Feasibility and benefits of traded
-data plans}, 2015 IEEE
-Conference on Computer Communications (INFOCOM), Kowloon, 2015, pp. 1580-1588.
-
-\bibitem{lazar}
-A. A. Lazar and N. Semret, 
-\textit{“Design and Analysis of the Progressive Second Price Auction for Network
-Bandwidth Sharing,”} Telecommunication Systems, Special Issue on Network Economics, 2000.
-
-\bibitem{semret} 
-N. Semret, 
-\textit{“Market Mechanisms for Network Resource Sharing,”
-Ph.D. thesis}. 
-Columbia University, 1999.
-
-\bibitem{tuffin}
-Bruno Tuffin,
-\textit{Revisited Progressive Second Price Auction for Charging
-Telecommunication Networks}.
-[Research Report] RR-4176, INRIA, 2001.
-
-\bibitem{qpsp}
-Clare W. Qu, Peng Jia, and Peter E. Caines,
-\textit{Analysis of a Class of Decentralized Decision Processes: Quantized
-Progressive Second Price Auctions},
-46th IEEE Conference on Decision and Control, New Orleans, LA, 2007, pp.
-779-784.
-
-\bibitem{cmhk}
-\textit{China Mobile Hong Kong Company Limited}.
-\url{https://www.hk.chinamobile.com/en/corporate_information/Data_N_VAS/DataTopup/index.html}.
-2018
-
-\bibitem{iia}
-Andreu Mas-Colell, Michael Dennis Whinston, and Jerry R. Green, 
-\textit{Microeconomic Theory}. Oxford University Press. 1995. p. 794.
-
-\bibitem{matt}
-Matthias Roggendorf and Fernando Beltr{\'a}n,
-\textit{Simulation Model for the Dynamic Allocation of Network Resources in a
-Competitive Wireless Scenario}. Mobility Aware Technologies and Applications, Springer Berlin Heidelberg. 2005.
-pp. 54 - 64.
-
-\bibitem{diffserve}
-N. Semret, R. R. F. Liao, A. T. Campbell and A. A. Lazar, 
-\textit{Pricing, provisioning and peering: dynamic markets for differentiated Internet services and
-implications for network interconnections}, in IEEE Journal on Selected Areas in
-Communications, vol. 18, no. 12, pp. 2499-2513, Dec. 2000.
-
-\bibitem{maille}
-Patrick Maillé.
-\textit{Market Clearing Price and Equilibria of the Progressive Second Price
-Mechanism},
-RAIRO - Operations Research, EDP Sciences, 2007, 41 (4), pp.465-478.
-
-\bibitem{att}
-\textit{AT\&T Mobile Share Flex Plans}
-\url{https://www.att.com/plans/wireless/mobile-share-flex.html}
-2018
-
-\bibitem{cabill}
-\textit{Communications: broadband Internet access service}, S.B. 822. Reg. Sess.
-2017-2018. (2018).
-
-\bibitem{fedbill}
-\textit{No Rate Regulation of Broadband Internet Access Act}, H.R. 2666, 114th
-Cong. (2016).
-
-\bibitem{shapley}
-Dov Monderer and Loyd Shapley. 
-\textit{Potential Games}, Games and Economic Behavior. 14: 124–143. (1996).
-
-\bibitem{felix}
-Felix Brandt and Tuomas Sandholm.
-\textit{On the Existence of Unconditionally Privacy-Preserving Auction
-Protocols}, ACM Trans. Inf. Sys. Secur. 11, 2, Article 10 (May 2008).
-
-\end{thebibliography}
-%\fi
-
-\end{document}

### 2019-09-26 Old/temp.tex
Work

--- 2018-04-18 paper_wc_4-12.tex
@@
 \end{equation}
-Fix an auction $j\in\mcI$ and define the set of users $\Lambda$, where
+Fix $j\in\mcI$ and define the set of users $\Lambda$, where
 \begin{equation}\label{lambda}
-    \lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \bigcap_{i\in\mcI^j} \bigg(\bigcap_{k\in\mcI_i} \mcI^k \bigg),
-\end{equation}
-\begin{equation}\label{lambda}
-    \Lambda = \mcI^j \cap \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg),
+    \Lambda = \bigg(\displaystyle\bigcap_{i\in\mcI^j} \mcI_i \bigg) \cup \mcI^j,
 \end{equation}
@@
 the lowest price that $j$ will accept to perform any allocation.
-Using (\ref{buyerinversedemand}), (\ref{sellerinversedemand}), and Proposition
-\ref{sellerstrategy},
+Using (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}),
 we have that for each $i \in \mcI^j$, 
 $p_{i}^j \ge p_{i^*}^j \ge p_i^k > 0$, which holds $\forall \ k \in\mcI_i$.
-Let $p_*^j=p_{i^*}^j$ denote the reserve
+
+Therefore $p_i^j \ge p_{i^*}^j, \ \forall \ i \in
+[p_i^j]_{i\in\mcI^j}$. Let $p_*^j=p_{i^*}^j$ denote the reserve
 price of auction $j$, noting that $p_i^j=0, \ \forall \ i \in
@@
 \begin{equation}\label{rho}
-    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)),
-\end{equation}
-and, $\forall \ i \in \mcI^j$, 
-\begin{equation}\label{invrho}
-    f_i \circ e_i^j(a) \ge p_*^j,
-\end{equation}
-and, $\forall \ k \in \mcI_i$, 
-\begin{equation}\label{invrho}
-    p_*^j \ge f^k \circ e_i^k(a) ,
-\end{equation}
-from (\ref{datademand}), (\ref{buyerinversedemand}),
-(\ref{sellerinversedemand}), and so $p_i^j \ge p_{*}^j \ge p_i^k, \ \forall \ i \in
-[p_i^j]_{i\in\mcI^j}$ and $\forall \ k \in [p_i^k]_{k\in\mcI_i}$
+    \rho^j(p_*^j) \le \displaystyle\sum_{i\in\mcI^j} e_i(a(s_i^j)).
+\end{equation}
+using (\ref{datademand}), (\ref{buyerinversedemand}),
+(\ref{sellerinversedemand}).
 
 The sellers $\in\Lambda$ are competing to sell
-their respective resources to buyers whose valuations are distributed across multiple auctions. 
+their respective resources to buyers whose valuations that are distributed across multiple auctions. 
 %By (\ref{jtoi}), $j\in \mcI_i, \ \forall \ i\in \mcI^j$. 
@@
 for any $k\ne j \in \mcI_i$. 
-Using (\ref{buyerinversedemand}) and  (\ref{sellerinversedemand}), we have
-$\forall \ i \in \mcI^j$,
+Using (\ref{buyerinversedemand}) and
+(\ref{sellerinversedemand}), 
 \begin{equation}\label{feq}
-    p_*^j = f^j \circ e_i(a) = f_i\circ e_i(a) = p_i^*,
-\end{equation}
-where we denote $p_i^*$ as the coordinated bid price of buyer $i$.
-Now, suppose $\exists \ i\in\mcI^j$ such that $p_i^* \ge p_*^j$.
-Since,
-$$
-    p_i^* = \max_{k\in\Lambda_i}(f^k) \circ e_i(a)= \max_{k\in\Lambda_i}(p_*^k),
-$$ 
-there must be some $k \ \in\mcI_{i}$, where $p_i^k > p_*^j$, and so, 
-we have that $ \Rightarrow p_i^k > p_*^j$. Also, $\not\exists$(HERE) 
+    p_*^j = f_i\circ e_i(a) = f^j\circ e_i(a).
+\end{equation}
+Suppose for some $i\in\mcI^j \ \exists \ k \ \in\mcI_{i}$ such that $p_{i}^k > p_{*}^j$. 
+%For any $k \in\Lambda_i$ we have that $p_i^k = p_i^j$. 
+We have that $p_i^j = p_i^k = \max(f^k,f^j) \circ e_i(a)= \max(p_*^k, p_*^j)$.
+It follows $p_i^j = p_i^k, \ \forall \ i \in \Lambda_i$,
+which, for any $i\in\mcI^j$, holds $\forall \ k\in\mcI_i$.
 It follows that buyer $i$'s bid price is given by,
@@
 \end{equation}
-
 %where $p_i^*$ represents $i$'s coordinated bid price,
 %i.e., $p_i^j = p_i^*, \ \forall \ j$ such that $s_i^j > 0$.
+and so $p_i^j = p_i^k > 0, \ \forall \ k \in \mcI_i$.
+
 This holds for any
 $i\in\mcI^j$ and similarly if $p_i^k < p_i^j$. 
-Now, from (\ref{feq}), we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
+Now we have that $f_i=f^k=f^j, \ \forall \ i,j,k \in \Lambda$, as such, we may
 denote each as $f$ in the remainder of the proof.

### 2019-09-26 main.tex
Work

%\documentclass[master,tocprelim]{Latex/Classes/PhDthesisPSnPDF}
%\documentclass[letterpaper,12pt]{cls/thesis}
%\documentclass[master,final,tocprelim]{unrthesis}
\documentclass[master,tocprelim,12pt]{unrthesis}
%\documentclass[master,tocprelim,12pt]{thesis}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{float}
%\usepackage{wrapfig}
%\usepackage{showkeys}
\usepackage{algorithm2e}
\usepackage{plain}
\usepackage{pdfpages}

\usepackage{listings}

\graphicspath{{./graphics/}}

\lstset{ %
language=C,               
basicstyle=\footnotesize,
showspaces=false,               
showstringspaces=false,         
numbers=left,                   % where to put the line-numbers
numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
numbersep=10pt,     
showtabs=false,                 
columns=fullflexible,
frame=single,          
tabsize=2,          
captionpos=b,       
extendedchars=true,
frame=single,
breaklines=true,       
breakatwhitespace=false, 
escapeinside={\%*}{*)}       
}
\def\verbatimtabsize{4\relax}
\def\listingoffset{1em}
\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{property}{Property}[chapter]

\title{Dynamical Systems: Chaotic Attractors and \\{~}
    Synchronization using Time-Averaged Partial \\{~}\\
\vskip-12pt
Observations of the Phase Space}
\author{
Jordan Fleming Blocher 
}

%\date{\today}

\newcommand{\cF}{{\mathcal F}}
\newcommand{\cO}{{\mathcal O}}
\newcommand{\cA}{{\mathcal A}}
\newcommand{\cB}{{\mathcal B}}
\newcommand{\cV}{{\mathcal V}}
%\newcommand{\R}{\textbf{R}}
\newcommand{\R}{{\bf R}}
\newcommand{\B}{{\cal B}}
\newcommand{\C}{\textbf{C}}
\newcommand{\del}{\delta}
\newcommand{\cL}{{\mathcal L}}
\newcommand{\mydelta}{{h}}
\newcommand{\yourdelta}{{\Delta}}
\def\words#1{\quad\hbox{#1}\quad}
\def\wwords#1{\qquad\hbox{#1}\qquad}
\renewcommand{\emptyset}{\O}
\numberwithin{equation}{chapter}
\begin{document}

\maketitle

\includepdf{ms-committee-page.pdf}

\begin{abstract}

We study the synchronization of chaotic systems when the coupling
between them contains both time averages and stochastic noise.
Our model dynamics are given by the Lorenz equations
which are a system of three ordinary differential
equations in the variables $X$, $Y$ and $Z$.
Our theoretical results show that coupling two copies of the
Lorenz equations using a feedback control which consists
of time averages of the $X$ variable
leads to exact synchronization provided the
time-averaging window is known and sufficiently small.
In the presence of noise the convergence is to within a
factor of the variance of the noise.
The novelty of our investigation hinges on the
analysis of the time averages.
We also consider the case when the time-averaging window
is not known and show that it is possible to tune the
feedback control to recover the size of the
time-averaging window.
Further numerical computations
show that synchronization is more accurate and occurs
under much less stringent conditions than our theory requires.

\end{abstract}

\begin{acknowledgements}
I would like to acknowledge my thesis advisor, Eric Olson.
I would like to thank my committee members:
Bruce Blackadar, Paul Hurtado and Fred Harris.
I would also like to thank my friends, family and UNR.
This research is supported in part by NSF grant DMS-1418928.
\end{acknowledgements}

\contentspage
\tablelistpage
\figurelistpage

\begin{manuscript}
\chapter{Introduction}\label{Intro}

We produce synchronization results when coupling is applied on 
two chaotic systems when the coupling
between them contains both time averages and stochastic noise.
Our model dynamics are given by the Lorenz equations
which are a system of three ordinary differential
equations in the variables $X$, $Y$ and $Z$.
We build off of investigations of the Lorenz model in 
\cite{Hayden11, Stuart14}, where 
space and continuous time observations \cite{Olson14} by use of a control
theory perspective similar to that which arises from the derivation of
continuous time limits of discrete time filters \cite{ Bloemker14}. 
We seek to determine relationships between the underlying
dynamical system and the observation operator
to ensure that synchronization can be obtained.
For a coupled pair of chaotic dynamical systems,
where the driven system's initialization is not known precisely, the extent 
of the use of observed data over time is a topic of interest in 
meteorology, weather forecasting and any attempt to predict the 
future using incomplete information about the current state of a
dynamical model.

In this thesis, we extend the approach of \cite{Olson14}
to use time-averaged continuous-in-time partial observations of 
the phase space. We examine
both the noise-free case and the case where the observations include
stochastic noise. We are able to show that the use of time-averaged
observations results in synchronization.
The techniques investigated here are applicable to different
dissipative dynamical systems, and
provide many points of continued study, which
are detailed in a chapter dedicated to future work.

The outline of the thesis is as follows. In Chapter 1 we introduce the concept
of synchronization on the global attractor. We also provide a
detailed description of our model problem, a simplified model of atmospheric
convection, the Lorenz system, and present an analytical bound on the
trajectories which is used throughout the thesis. We also introduce the coupling
method that is is the focus of the thesis and introduce the notation that will
be used to describe our experiments.
In Chapter 2 we present a proof of the
existence and uniqueness of our solution. In addition, we present a generalized
Gronwall integration proof that will be used throughout the thesis and is
applicable to the convergence of our model. 
In chapter three we study the convergence of the approximating solution in a noise-free 
setting, ending with an investigation into the sensitivity of the time-averaging
window. Chapter 4 presents an analysis when the observations contain stochastic noise. 
Chapters 5 and 6 present our numerical methods and conclusions. Finally, Chapter
7 provides points of future work.

\section{Synchronization}\label{Synchro}

Synchronization means that the difference between two solution
trajectories converge to zero as time tends to infinity.  The sensitivity
to initial conditions of dynamical systems means that two identical
systems with even a slight perturbation of initial conditions quickly
become uncorrelated even though they are bounded and converging to the
same attractor.  
On the theoretical side, we would like to determine 
when coupling between two identical copies of a dynamical system
leads to synchronization and to study the effects that
realistic conditions, such as a moving time-averages and 
noisy observations, have on the synchronization.
On the computational
side, we would like to simulate the same things and test the
sharpness of our theory.

Consider a dynamical system given by the ordinary differential equations
\begin{equation}\label{freeODE}
    \frac{dU}{dt} = \cF(U) 
\end{equation}
where $U(0) = U_0\in{\bf R}^n$ and ${\cal F}\colon{\bf R}^n\to{\bf R}^n$.
We use partial information about $U$ to drive a second solution $u$
as follows:
\begin{equation}\label{noerra}
    \frac{du}{dt} = \cF(u) + \mu\big(\widetilde{\cal R}(U) - {\cal R}(u)\big)
\end{equation}
with arbitrary initial condition $u(0) = u_0$.
Here $\widetilde{\cal R}(U)$ denotes an interpolation of
partial observations of $U$ back into the phase space ${\bf R}^n$
that may contain noise as well moving time averages, and
${\cal R}(u)$ denotes a feedback control used to nudge $u$
towards $U$ over time.
Note that the relaxation parameter $\mu > 0$ 
determines the rate
at which $u$ is nudged towards $U$ as it evolves forward in time 
and represents a tunable parameter in the system.

Note, we assume the forcing function ${\cal F}$ is known 
exactly and leads to a well posed dynamical system that governs
the freely evolving solution.
More realistically, ${\cal F}$ might only be known up to an
approximation $\widetilde {\cal F}$.  Ideas for work along these 
lines is discussed in Section \ref{whatissigma} in the
chapter on future work.  
We assume the dynamics given by ${\cal F}$ are dissipative.
However, our analysis relies not just on dissipativity, but
on a squeezing property with respect to the observable
part of the phase space.

If $\widetilde{\cal R}={\cal R}$ and $u_0=U_0$, then
$\mu\big((\widetilde{\cal R}(U_0) - {\cal R}(u_0)\big)= 0$.
It follows that both $u$ and $U$ evolve according to the same
dynamics, which in turn implies $u(t)=U(t)$ for all $t\ge 0$.
When $u_0\ne U_0$ it may still happen
%provided $\widetilde{\cal R}={\cal R}$ 
that $\|u(t)-U(t)\|\to 0$ as $t\to\infty$.
When this happens we say that $u$ synchronizes with $U$.
Note, however, when $\widetilde{\cal R}\ne{\cal R}$ it
may happen that
$\mu(\big(\widetilde{\cal R}(U_0) - {\cal R}(u_0)\big)\ne 0$
even if $U_0=u_0$.
It immediately follows that $U(t)\ne u(t)$ for $t>0$.
In this case, we look for bounds on $\|U-u\|$ that depend
on the quality of the approximation $\widetilde{\cal R}\approx{\cal R}$.

If the observations $\widetilde{\cal R}$ have been 
contaminated using a moving time average with a known window size,
then ${\cal R}$ can also include an identical moving time average
so that $\widetilde{\cal R}={\cal R}$.  However, if the size of
the averaging window is unknown, then we can only guess its size.
In this case ${\cal R}$ is only an approximation of $\widetilde{\cal R}$.
Similarly, if the observations $\widetilde{\cal R}$ contain a 
unknown noise term, this this noise can not be included in the 
feedback term and again ${\cal R}$ will differ from 
$\widetilde{\cal R}$, this time by the noise.
The main result of this thesis are theoretical and numerical
bounds on the expected value of $\|U-u\|^2$ in the case 
when $\widetilde{\cal R}$
contains noisy observations that have been averaged with
respect to an unknown window size.

\section{Global Attractors}

For general continuous time dynamical systems the number of degrees of freedom
is often associated with the number of first order ordinary differential
equations (ODEs) in the model.  If
$$ 
\displaystyle\sum_{i=1}^n{\partial \cF_i \over \partial U_i }< 0,
$$
then the system is said to be
\emph{dissipative} system.
This indicates that volumes transported by the dynamics of
the system are contracting.
In this case, there exists a compact set to which all bounded 
sets converge as they are transported by the flow.
In particular, all trajectories eventually converge that set.
Moreover, if this set is invariant, that is, if every point on
the attractor is the image under the flow of the
dynamics over a fixed period of time of another point on the attractor, 
then the set is unique and called the global attractor.
Since the attractor is bounded and invariant, then any trajectory 
on the attractor is bounded backwards in time.
This leads to another characterization of the attractor
as the set of all solutions which are bounded backwards
in time.  
Note that the set of fixed points such that 
$\big\{\, x : {\cal F}(x)=0 \,\big\}$ are included in the attractor,
as is the unstable manifold of the fixed point.
This observation can be used to find lower bounds on the
size of the attractor.

Due to the presence of an attractor, the sum of the Lyapunov
exponents is expected to be negative; an indication that the 
system is dissipative. 
The Lyapunov exponents control the exponential growth or
contraction of volume elements in phase space \cite{Doering95a}.
They 
quantify the exponential divergence of infinitesimally close 
state-space trajectories 
and estimate the amount of chaos in a system. 
A positive exponent is consistent with diagnosing chaos and represents
local instability in a particular direction.

The Lyapunov spectrum is represented geometrically as a small $n$-dimensional 
sphere of initial conditions.
%, where $n$ is the degrees of freedom in the system.
In a chaotic attractor, the sphere evolves into an ellipsoid whose
principal axes expand (or contract) at rates given by the Lyapunov
exponents.
Calculating the largest Lyapunov exponent can yield an estimate 
of the ``level of chaos" using the slope of the divergence
as was calculated by Rosenstein and Collins \cite{Rosenstein93}.
This determines how two trajectories with nearby initial conditions 
diverge over time.
In fact, we expect that two randomly chosen initial 
conditions in arbitrary phase space will diverge exponentially at 
the rate given by the largest Lyapunov exponent. 
In the context of the synchronization studies in this thesis, 
it is this tendency for the
trajectories to diverge that needs to be overcome by the
feedback controller represented by $\mu\big(\tilde{\cal R}(U)-{\cal R}(u)\big)$
in equation~(\ref{noerra}).

\section{The Lorenz '63 Model}

The Lorenz '63 Model is a system of three ordinary differential equations that
represent a simplified model of atmospheric convection \cite{Lorenz63}. 
The model is dissipative with a quadratic energy-conserving nonlinearity.
This system of three coupled non-linear ordinary differential
equations satisfies equation~(\ref{freeODE}) where
$U=(X,Y,Z)$ and
\begin{align}\label{freeLorenz}
    \cF(U)=\begin{bmatrix}\sigma(Y-X)\\
    -\sigma X-Y-XZ\\ -bZ+XY-b(r+\sigma)\end{bmatrix}.
\end{align}
Here $\sigma$ is
the Prandtl number, $r$ is the Rayleigh number, 
and $b$ is a geometric factor. 
Note that we have employed a coordinate system where 
the center is shifted to the point $(0, 0, 0)$.
We will use the standard parameter values 
$\sigma=10$, $b=8/3$ and $r=28$
in our study.  
At these values, the system is known to 
have a chaotic global attractor $\cA$, Tucker \cite{Tucker1999}.

Note that
$$
\displaystyle\sum_{i=1}^3{\partial \cF_i \over \partial U_i }
	=-\sigma-1-b
$$	
which shows the system is dissipative.
Moreover, linearization about the
fixed point $$(\sqrt{b(r-1)},\sqrt{b(r-1)},-\sigma-1)$$
gives the matrix
$$
\begin{bmatrix}
    -\sigma & \sigma & 0\\
    1 & -1 & -\sqrt{b(r-1)}\\
    \sqrt{b(r-1)} & \sqrt{b(r-1)} & -b
\end{bmatrix}.
$$
which has eigenvalues
\begin{align*}
	\lambda_1&\approx -13.85457791\\
\quad
	\lambda_2&\approx 0.093955624 - 10.19450522i\\
\quad
	\lambda_3&\approx 0.093955624 + 10.19450522i.
\end{align*}
Since the real parts of two of these eigenvalues is positive,
nearby solutions will
spiral away onto a two-dimensional unstable manifold. 
We conclude that the unstable manifold at the fixed point
is two dimensional.
Therefore, the global attractor contains a two dimensional
set and is itself at least two dimensional.

The Lorenz attractor has been shown to be a global 
attractor contained in a
volume bounded by a sphere, a cylinder, the volume between two parabolic sheets,
an ellipsoid and a cone \cite{Doering95a}, see
also \cite{Doering95b}.
A smaller sphere which also contains the attractor was 
discovered while attempting to improve estimates used in
the proof of Proposition~\ref{UKNLTAprop}.
While we did not make use of that bound in this thesis,
it has been included as Appendix~A because it is of independent
interest and may be useful in future work, see Section~\ref{fractalbound}.
Throughout this thesis we assume that
the free running solution lies on the global attractor.
Thus, $U$ reflects the long term behavior of the
Lorenz systems and obeys the {\it a priori\/} bounds discussed
above.
Of those bounds we make exclusive use of the spherical bound given 
as Theorem~\ref{Ktheorem} stated below.

The following proof
is essentially the same as the one given in \cite{Doering95a};
however, it is simpler because
we have already translated the $Z$ variable in the formulation 
of the Lorenz system.

\begin{theorem}
\label{Ktheorem} 
Let $U$ be a trajectory with 
$U_0\in \mathcal{A}$ and assume that $b\ge 2$ and $\sigma$ $r>0$. 
Then $|U(t)|^2 \leq K$ for all $t\in\textbf{R}$ where
\begin{equation}\label{Keqn}
    K = \frac{b^2(r+\sigma)^2}{4(b-1)}
\approx 1540.27.
\end{equation}
\end{theorem}
\begin{proof}
We define a Lyapunov function as
\begin{equation}\label{boundsEqn}
    K = \{(X,Y,Z) \ \vert \ X^2 + Y^2 + Z^2 \le R^2\}
\end{equation}
and consider the evolution of the sphere as determined by the Lorenz equations:
$$
{1\over 2} {dK\over dt} = \sigma X^2 + Y^2 + bZ^2 -b(r+\sigma)Z.\\
$$
$K$ is a decreasing function in time, and so trajectories will move closer to
the point $(0,0,0)$. Solving the constrained maximization problem 
$$
K = \max\{K(X,Y,Z)\ \vert \ \sigma X^2 + Y^2 + bZ^2 -b(r+\sigma)Z \ge 0\}
$$
by using the Lagrange multiplier method with
$$
    f(X,Y,Z,\lambda) = X^2 + Y^2 + Z^2 + \lambda(\sigma X^2 + Y^2 + bZ^2
    +b(r+\sigma)Z)
$$
we may bound the radius of a sphere into which all solutions flow as $t\to
\infty$ where $K_{max} = R^2$.
\end{proof}

\section{The Coupling Method}

%We are interested in a dynamical system formed by two near identical
%subsystems:  one subsystem evolves freely and
%drives the evolution of the other. 
In \cite{Olson14} Azouani, Olson, Titi 
introduced equation~(\ref{noerra}) as a simple
data-assimilation method that constructs an
approximating solution $u$ from partial observations
of an exact solution $U$ over time.
A numerical study of this algorithm was performed by
Gesho \cite{GeshoThesis}, see also Gesho, Olson and Titi \cite{Gesho16}.
The effects of noisy measurements were treated by
Bessaih, Olson and Titi in \cite{Bessaih15}, which led
to a stochastic version of equation~(\ref{noerra}) that
included a $Q$-Brownian motion on the right hand side
to represent measurement errors.
In those works the model problem was the two-dimensional
incompressible Navier--Stokes equations and ${\cal R}(U)$
represented nodal 
measurements of an Eulerian velocity field as might be taken 
by an array of idealized weathervane anemometers that can
measure the exact velocity at a discrete set of points in 
space at any point in time.

Synchronization of coupled copies of the Lorenz system
was first observed by Pecora and Carroll in \cite{Pecora90}.
The Lorenz system was considered in the context of data assimilation 
by Hayden \cite{HaydenThesis} and by Hayden, Olson and Titi 
\cite{Hayden11} and to understand the effects noise
in the observational measurements by Law, Shukla and Stuart 
in \cite{Stuart14}.
This thesis explores the case in which the
available information about the true state of $U$ is 
further contaminated
by a moving time average with an averaging window 
of size $\delta$.
This type of moving average is physically relevant to 
real-world scientific instrumentation that approximates,
for example, the measurement of velocity at any instant
in time by
an average velocity taken over a very small time interval.

Another physically relevant property of most instrumentation is 
that measurements are produced at a sequence of discrete moments 
in time rather than continuously in time.
Sequences of discrete-in-time observations for the Lorenz system
have been considered by Hayden \cite{HaydenThesis},
by Hayden, Olson and Titi in \cite{Hayden11} and 
by Cecilia, Jolly, Foias and Titi in \cite{Cecilia}.
In order to focus on time averages we do not treat
discrete-in-time data in the present thesis.

We now describe the observational measurements of $U$
denoted by $\widetilde{\cal R}(U)$.
Coupling through either the $X$ or $Y$ variable can lead to 
synchronization in the Lorenz system, see \cite{HaydenThesis}.
In this thesis the coupling is on $X$ because the analysis is 
easier and more closely 
represents the analysis used when treating the synchronization
of dynamics given by partial differential equations.
Let 
$\widetilde {\cal R}\colon \R^3\to \R^3$ in equation~(\ref{noerra}) be given 
by one of
$$
R=\cL\circ \cO,\quad
\widetilde R=\cL\circ \widetilde \cO
,\quad
R_{\hat\delta}=\cL\circ \cO_{\hat\delta}
\words{or}
\widetilde R_{\hat\delta}=\cL\circ \widetilde \cO_{\hat\delta},
$$ 
where $\cO$, $\widetilde\cO$, $\cO_{\hat\delta}$ and 
$\widetilde\cO_{\hat\delta}$
represent 
observations with and without noise/time-averages
and
$\cL$
represents an interpolation of the observations 
back into the phase space.
Note that $\hat\delta$ is the size of the averaging window
present in the observational measurements of $U$.
Specifically, we take $\cO\colon \R^3 \rightarrow \R$
and $\cL\colon\R\to\R^3$ 
to be given by 
\begin{equation}\label{Lobserve}
\cO(X,Y,Z)=X\wwords{and} \cL(X)=(X,0,0)
\end{equation}
throughout our study.
Thus, $\cL(U)$ represents exact observations 
of $U$ obtained instantaneously at the time $t$ 
and $\widetilde\cO(U)$ a noisy version of $\cO(U)$ 
which, following \cite{Bessaih15}, satisfies
\begin{equation}\label{tildecO}
\widetilde\cO(U)dt
	=\cO(U)dt+\epsilon dW_t
\end{equation}
where $W_t$ is a standard one-dimensional Brownian motion
with underlying probability space $\Omega$.
The corresponding noise-free and noisy moving time averages
are then given 
by 
\begin{equation}\label{cOdelta}\cO_{\hat\delta}(U)
	={1\over\hat\delta}\int_{t-\hat\delta}^t \cO(U(s))\,ds
\end{equation}
and
\begin{equation}\label{tildecOdelta}
\widetilde\cO_{\hat\delta}(U)
	={1\over\hat\delta}\int_{t-\hat\delta}^t \widetilde\cO(U(s))\,ds.
\end{equation}
%Note that $\delta>0$ above represents the size of the
%averaging window.
For notational convenience we define 
$\cO_0=\cO$ and $R_0=R$ so that $\hat\delta=0$ indicates measurements 
for which the averaging is zero.

As the noise is unknown, the possible choices for ${\cal R}$
used in the feedback control ${\cal R}(u)$ can not include
noise.
This ensures the evolution of the driven solution is given
only in terms of things which are observable.
It may also happen that the size of the averaging present in 
the observations is also unknown. 
In this case, we let $\delta$ represent the time 
averaging in the feedback control.
Thus,
the possible choices for ${\cal R}$ are given given by 
one of $R$ or $R_{\delta}$ where $\delta$ is an approximation
of $\hat\delta$.

When the observations
%are given by $\cO_\delta$ they
are noise-free and $\delta=\hat\delta$ we obtain conditions 
under which $\|U-u\|\to 0$ as $t\to\infty$.
When the observations 
%are given by $\widetilde \cO_\delta$ they
are noisy
$u$ becomes a stochastic process.
In particular, $u$ solves a stochastic differential equation 
when $\hat\delta=0$ and a 
random differential equation when $\hat\delta>0$.
In this case we obtain
bounds of the form
\begin{equation}\label{B1bound}
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big]< B_1.
\end{equation}
Chebyshev's inequality applied to the bound (\ref{B1bound}) implies 
there exists $T>0$ such that
\begin{equation}\label{cheby}
	{\bf P}\big\{ \|U-u\|^2\le B_2\varepsilon^2\big\} \ge 1-B_1/B_2
\end{equation}
for every $B_2>B_1$ and $t>T$.
Thus, the error has a 90 
percent chance of being bounded by $B_2=10B_1$ at any fixed
point in time.

We also consider the general case when 
$\delta\ne\hat\delta$, that is, when the time averaging present 
in the observations is unknown.  
In this case, the equation for $u$ becomes
\begin{equation}\label{NLTAUnkSoln}
    \frac{du}{dt} = \cF(u) -
    \mu \big(\widetilde R_{\hat\delta}(U)
    - {R}_{\delta}
    (u)\big),
\end{equation}
In the absence of noise $\varepsilon=0$ and we 
obtain as Proposition \ref{UKNLTAprop}
conditions and a bound
$B_3$ such that
\begin{equation}\label{lessdeltadelta}
	\limsup_{t\to\infty} \|U-u\|^2 < B_3 (\hat\delta-\delta)^2.
\end{equation}
This analysis suggests it may is possible to recover 
$\hat\delta$ using successively better guesses.
When there is noise we obtain our final
result Proposition~\ref{UKNTAprop} which provides
bounds $B_4$ and $B_5$ such that
\begin{equation}\label{noisydeltadelta}
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] 
		< B_4 (\hat\delta-\delta)^2 + B_5\varepsilon^2.
\end{equation}
In this case, $\delta$ can be tuned to 
match $\hat\delta$ only up to the point 
where the second term starts to dominate the bound.

\chapter{Preliminaries}

In this chapter we prove a local existence theorem 
which will be used later to show our data assimilation 
equations are globally well posed as well as an
integro-Gronwall inequality which will be used to
estimate the accuracy of the synchronization.

We now turn our attention to proving existence and
uniqueness of solutions for the integro-differential equations
which define the driven system as a result of the time averages
present in the observational measurements.
Let
$$
	f\colon [0,\infty)\times\R^n\to\R^n \
	\text{ and }\
 g\colon [0,\infty)\times\R^n\to\R^n$$
be continuous in the first variable and
uniformly Lipschitz in the second.
Consider the integro-differential equation
\begin{equation}\label{intdiff}
     V'=\begin{cases}
{\smallskip}
f\big(t, V\big) & \text { for } t<\delta\\\\
        f\big(t, V\big)
    +\displaystyle {1\over\delta}\int_{t-\delta}^t g\big(s, V(s)\big)\,ds &
    \text{ for } t>\delta\end{cases}
\end{equation}
where $ V\in\R^n$ is a continuous function.
Note that $ V'$ may not be defined at time $t=\delta$, 
unless
$$
	\int_0^\delta g(s,y(s))\,ds\ne 0.
$$
As this is not in general true, then we consider as solutions
to equations (\ref{intdiff}) continuous functions which are piecewise
differentiable.
This equation, similar to the
Volterra equations studied by Levin in \cite{Levin64},
is locally well posed as shown by 
\begin{lemma}\label{localexist}
Suppose $ V\colon [0,T]\to \R^n$ satisfies equations (\ref{intdiff}),
then there exists $\Delta t>0$ such that $ V$ can be uniquely extended to a function
on $[0,T+\Delta t]$ which also satisfies equations (\ref{intdiff}).
\end{lemma}

\begin{proof}
If $T<\delta$, standard existence and uniqueness results
for ordinary differential equations show there exists $\Delta t>0$ 
such that the solution $ V$ can be extended to the interval $[0,T+\Delta t)$.
If $T\ge\delta$, the result follows from a straight-forward 
fixed point argument which we include here for completeness.

Define 
$$D=\max\big\{\, \| V(t)\| : t\in[0,T]\,\big\}+1$$
and
$$M_f=\max\big\{\, \|f(t,v)\| : t\in[0,T+1]\hbox{ and }\|v\|\le D\,\big\}.$$
Let $\gamma_f$ be the Lipschitz constant such that
$$
	\big\|f(t,v_1)-f(t,v_2)\big\|\le \gamma_f \|v_1-v_2\|
\words{for} \|v_1\|,\|v_2\|\le D.
$$
Corresponding to the function $g$
similarly define $M_g$ and $\gamma_g$.
Let
\begin{equation}\label{sizeofh}
	\Delta t=\min\bigg(1,{1\over M_f+M_g},{1\over 2(\gamma_f+\gamma_g)}\bigg).
\end{equation}
and define
\begin{align}
    {\cal X}=\Bigg\{
        v\in {\cal C}([0,T+\Delta t],\R^n):
        \begin{matrix}v(t)=V(t)\hbox{ for }t\le T,\hbox{ and }\hfill\\
        \|v(t)\| \le D\hbox{ for }t\in[T,T+\Delta t]\end{matrix}\,\Bigg\}.
\end{align}
Consider the mapping ${\cal J}\colon{\cal X}\to {\cal C}([0,T+\Delta t],\R^n)$ 
given when $t\le T$ by ${\cal J}(v)(t)= V(t)$ and when $t> T$ by
$$
	{\cal J}(v)(t)= V(T)+\int_T^t f\big(\tau,v(\tau)\big)\,d\tau
		+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau g(s,v(s))\,ds\,d\tau.
$$
We claim that ${\cal J}\colon{\cal X}\to{\cal X}$ and
that ${\cal J}$ is a contraction.
Estimate
\begin{align*}
	\|{\cal J}(v)(t)\|
	&
	\le \| V(T)\|+
	\int_T^t \|f\big(\tau,v(\tau)\big)\|\,d\tau\\
	&\phantom{{}\le \| V(T)\|}
		+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau 
			\|g(s,v(s))\|\,ds\,d\tau\\
	&\le (D-1) + \Delta t M_f +\Delta t M_g \le D.
        \end{align*}
Therefore, ${\cal J}\colon{\cal X}\to{\cal X}$.  Moreover,
\begin{align*}
	\|{\cal J}(v_1)(t)&-{\cal J}(v_2)(t)\|
		\le
	\int_T^t \|f\big(\tau,v_1(\tau)\big)-f(\tau,v_2(\tau)\|\,d\tau\\
		&
\phantom{{}-{\cal J}(v_2)(t)\|}
+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau 
			\|g(s,v_1(s))-g(s,v_2(s))\|\,ds\,d\tau\\
	&\le \Delta t(\gamma_f+\gamma_g) \max \{\,\|v_1(s)-v_2(s)\|: s\in [T,T+\Delta t]\,\}\\
	&\le (1/2) \max \{\,\|v_1(s)-v_2(s)\|: s\in [T,T+\Delta t]\,\}
        \end{align*}
shows that ${\cal J}$ is a contraction.
Now, by the contraction mapping theorem, there is a unique fixed point
$v\in {\cal X}$ such that ${\cal J}(v)=v$.  
Since this fixed point clearly satisfies equations (\ref{intdiff}),
the lemma is proved.
\end{proof}

We now prove the following integro-differential Gronwall inequality.

\begin{lemma}\label{intGronwallerror}
Suppose
\begin{equation}\label{idineq}
    {d\cV(t)\over dt} +  \cV(t) 
	\leq A \mydelta \int_{t-\mydelta}^t  \cV(s) \ ds + B
\end{equation}
where $A>0$, $B>0$ and
%$$ 0<\mydelta < \min \Big\{ 1, \sqrt{1-e^{-1}\over 2A}\Big\}.$$
$$ 0<\mydelta < \min\bigg\{\sqrt{1-e^{-1}\over 2A},1\bigg\}.$$
Then $\limsup_{t\to\infty} \cV(t)< eB.$
\end{lemma}
\begin{proof}
By hypothesis 
%Since %$$\delta< \sqrt{1-e^{-1}\over 2A}$$
there exists $\gamma\in (0,1)$ such that
$$\mydelta< \sqrt{e^{-\gamma}-e^{-1}\over 2A}.$$
Therefore
\begin{equation}\label{est4R}
	e^{-(1-\gamma)}+2A\mydelta^2e^{\gamma\mydelta}
	< e^{-(1-\gamma)}+2A {e^{-\gamma}-e^{-1}\over 2A}e^{\gamma}
	=1
\end{equation}
and
\begin{equation}\label{est4B}
	2e^{-1}+2A\mydelta^2(1-e^{-1})-e^{-2}
		<e^{-1}+e^{-\gamma}(1-e^{-1}) = \beta<1.
\end{equation}
Moreover,
\begin{equation}\label{betaest}
	\beta+(e^{-1}-e^{-2})(\beta^{-1}-1)\le 1.
\end{equation}
Inequality (\ref{betaest}) follows by
taking $\phi(\beta)= \beta+(e^{-1}-e^{-2})(\beta^{-1}-1)$ and
differentiating to get
$\phi'(\beta)=1-(e^{-1}-e^{-2})\beta^{-2}$.
Therefore $\phi$ is increasing when
$\beta>\sqrt{e^{-1}-e^{-2}}$.
Since $\gamma\in(0,1)$ implies 
$\beta\ge 2e^{-1}-e^{-2}>\sqrt{e^{-1}-e^{-2}}$ then
$\phi(\beta)\nearrow 1$ as $\beta\nearrow 1$.

Let $m$ be the smallest integer such that $1+h\le m$
and $\B=e\beta B$.
Since $ \cV$ is continuous there is $R$ such that
$ \cV(s)\le Re^{-\gamma s}+\B$ for all $s\in [0,m]$.
For induction, suppose 
$ \cV(s)\le Re^{-\gamma s}+\B$ for all $s\in [0,n]$.
Claim 
$ \cV(s)<2(Re^{-\gamma s}+\B)$ for all $s\in [n,n+1]$.
If not, then there is some $t\in(n,n+1]$ such that
$ \cV(t)\ge 2(Re^{-\gamma t}+\B)$ and
$ \cV(s)\le 2(Re^{-\gamma s}+\B)$ for $s\in [n,t]$.
Multiplying inequality (\ref{idineq}) by $e^t$
and integrating from $t-1$ to $t$ we obtain
\begin{plain}$$\eqalign{
	 \cV(t)
		&\le\cV(t-1)e^{-1}+e^{-t}A\mydelta\int_{t-1}^t
		e^{\rho}\int_{\rho-\mydelta}^\rho\cV(s)\,ds\,d\rho
		+(1-e^{-1}) B.
}$$\end{plain}%
Since
\begin{plain}$$\eqalign{
		\int_{t-1}^t
		e^{\rho}\int_{\rho-\mydelta}^\rho\cV(s)\,ds\,d\rho
	&\le
		\int_{t-1}^t
		e^{\rho}\int_{\rho-\mydelta}^\rho  2(Re^{-\gamma s} +\B) \,ds\,d\rho\cr
	&\le
		2\mydelta \int_{t-1}^t
		e^{\rho} (Re^{-\gamma (\rho-\mydelta)} +\B) \,d\rho\cr
	&\le
		2 R\mydelta e^{\gamma\mydelta} \int_{t-1}^t
		e^{(1-\gamma) \rho} \,d\rho
		+2 \B\mydelta\int_{t-1}^t e^{\rho}\,d\rho\cr
	&\le
		2 R\mydelta e^{\gamma\mydelta} 
		e^{(1-\gamma) t} 
		+2 \B\mydelta (e^t-e^{t-1}),\cr
}$$\end{plain}%
then using estimates (\ref{est4R}) and (\ref{betaest}) we obtain
\begin{plain}
\begin{equation}\label{Rineqerr}
\eqalign{
	 \cV(t)
		&\le (Re^{-\gamma(t-1)}+\B)e^{-1}\cr
		&\qquad+ A\mydelta \big(2 R\mydelta e^{\gamma\mydelta}
        e^{-\gamma t} +2\B\mydelta (1-e^{-1})\big)
		+(1-e^{-1})B\cr
		&= Re^{-\gamma t} \big(e^{-(1-\gamma)}
			+2A\mydelta^2 e^{\gamma\mydelta}\big)\cr
		&\qquad+\B\big(
			2 e^{-1}+2Ah^2(1-e^{-1})-e^{-2}\big)\cr
			&\qquad+\B\big((e^{-1}-e^{-2})(\beta^{-1}-1)
			\big)\cr
		&\le Re^{-\gamma t} + \B\big(
			\beta
			+(e^{-1}-e^{-2})(\beta^{-1}-1)
			\big).\cr
%		&\qquad+\B\big(
%			\beta
%			+(e^{-1}-e^{-2})(\beta^{-1}-1)
%			\big)\cr
%		&\qquad+\B\big(
%			2e^{-1}+2A\mydelta^2(1-e^{-1})-e^{-2}
%			+(e^{-1}-e^{-2})(\beta^{-1}-1)
%			\big)\cr
		&\le R e^{-\gamma t} + \B.
}\end{equation}\end{plain}%
which contradicts $\cV(t)\ge 2(Re^{-\gamma t} +\B)$.
Therefore $\cV(s)\le 2(Re^{-\gamma s}+\B)$ for $s\in[n,n+1]$ and
it immediately follows from equation~(\ref{Rineqerr}) and induction
that $\cV(t)\le Re^{-\gamma t}+\B$ for $t>0$.
Consequently $\limsup_{t\to\infty}\cV(t)\le \B<eB$.
\end{proof}

We remark that the proof of Lemma~\ref{intGronwallerror} is still valid
when $B=0$ except for the strict inequality in the last step.  
Consequently we also obtain
\begin{corollary}
\label{intGronwallerror0}
Suppose the hypothesis of Lemma~\ref{intGronwallerror}
are satisfied except that $B=0$.
Then $\cV(t)\to 0$ as $t\to\infty$.
\end{corollary}

Combining Lemma~\ref{localexist} with Lemma~\ref{intGronwallerror} 
leads to a proof of
global existence of the driven solution $u$ for all time
when the $h$ appearing in Lemma~\ref{intGronwallerror} is small enough.
The main issue is showing that the size of the $\Delta t$ from
Lemma~\ref{localexist} is uniformly bounded below at any point in time.
Since the size of $\Delta t$ given in (\ref{sizeofh}) is constrained 
by $M_f$ and $M_g$, it is enough to show that these two
constants don't grow without bound over time.

We assume, 
as is the case for the Lorenz system 
focused on in this thesis, 
that
$$
	L_f=\sup\{ f(t,0) : t>0 \}
\wwords{and}
	L_g=\sup\{ g(t,0) : t>0 \}
$$
are finite.  In particular, when there is no noise, the
$f$ and $g$ which correspond to the Lorenz system are time
independent.  When there is noise we obtain 
probabilistic bounds on $f$ and $g$ which are uniform in
time because the variance of the noise process is stationary.
Since
$$
	\| f(t,v)\| \le \|f(t,v)-f(t,0)\|+\|f(t,0)\|
		\le \gamma_f \|v\|+ L_f
$$
then
$$
	M_f\le \gamma_f D + L_f
\wwords{and similarly}
	M_g\le \gamma_g D + L_g.
$$
Consequently, the only requirement to prevent $\Delta t$ from shrinking
is that $\|u\|$ stays below $D$.

Now, if $h$ is small enough
then taking ${\cal V}=\|U-u\|^2$ in Lemma~\ref{intGronwallerror}
(or in the case of noise taking
${\cal V}={\bf E}\big[\|U-u\|^2\big]$) implies that
$$
	\|U-u\|^2\le eB.
$$
Therefore taking $D=\sqrt{eB}+ \sqrt{K}$ yields
$$
	\|u\|\le \|U-u\|+\|U\|\le D
\wwords{for} t\in [0,T+\delta t].
$$
We conclude that $\|u\|$ remains uniformly bounded 
and therefore exists globally in time.
In the case where there is noise, the same result follows almost
everywhere after an application of the Borel-Cantelli lemma.

\chapter{Coupling without Noise}

When there is no noise in the coupling we 
show that the difference between the freely evolving system
and the driven system converges to zero over time.

Section~\ref{NLICoupling} treats the case 
%when ${\cal R}=R$, that is, 
when the coupling involves the $X$ variable measured 
exactly at each moment in time.
We include a complete analysis of this simple case as a frame
of reference.
Section~\ref{NLTACoupling} treats the case 
%when ${\cal R}=R_\delta$, that is, 
when the coupling involves a
simple moving time-average of the $X$ variable.
Provided the averaging window is small enough we again show
that exact synchronization occurs.
Section~\ref{UNTCoupling} treats the case when the size of the averaging
window is known only approximately.  In this case we obtain
an upper bound on the accuracy of the synchronization that
depends on $|\hat\delta-\delta|$ where $\hat\delta$ is the exact, but
unknown, size of the averaging window use to form the 
moving average of $X$ and $\delta$ is an the size of the
averaging window used on $x$ in the feedback control.

\section{Noiseless Instantaneous-in-Time Coupling}\label{NLICoupling}

This chapter treats the simplest case of synchronization for
the Lorenz system in which there are no time averages present
in the observational measurements.  Thus, $\hat\delta=0$, $\delta=0$
and $\varepsilon=0$ in equation~(\ref{NLTAUnkSoln}).

Substituting ${\cal R}={\cal L}\circ{\cal O}$ into equation~(\ref{noerra})
where ${\cal L}$ and ${\cal O}$ are given by equations (\ref{Lobserve})
yields the driven system
\begin{align}
\label{drivenX}
    \dot{x} &= -\sigma(y-x)+\mu(X-x)\\
\label{drivenY}
    \dot{y} &= -\sigma x-y-xz\\
\label{drivenZ}
    \dot{z} &= -bz+xy-b(r+\sigma)
\end{align}
We now show for $\mu$ sufficiently large
that
the approximating solution $(x,y,z)$
converges to the
free-running solution  $(X,Y,Z)$
as $t$ tends to infinity.

\begin{proposition}\label{NLIprop} 
Suppose $\delta=0$, $\hat\delta=0$ and $\varepsilon=0$.
Let $\mu>{K/4}-\sigma$, then 
$||U-u|| \to 0$ as $t\to \infty$.
In particular, synchronization is obtained 
by equation~(\ref{freeODE}).
\end{proposition}

\begin{proof}
Define $V=\yourdelta X^2+\yourdelta Y^2+\yourdelta Z^2$ 
where $\yourdelta X=X-x$, $\yourdelta Y=Y-y$ and
$\yourdelta Z=Z-z$.
Since
\begin{align}
\label{NLIddotx}
    \yourdelta\dot{X} &= -(\sigma + \mu)\yourdelta X + \sigma\yourdelta Y\\
\label{NLIddoty}
    \yourdelta\dot{Y} &= -\sigma\yourdelta X - \yourdelta Y - \yourdelta XZ - x\yourdelta Z\\
\label{NLIddotz}
    \yourdelta\dot{Z} &= -b\yourdelta Z + \yourdelta X Y + x\yourdelta Y
\end{align}
we have
$$
{1\over 2}\dot{V} + (\sigma + \mu)\yourdelta X^2 + \yourdelta Y^2 + b\yourdelta Z^2 =
-\yourdelta X\yourdelta Y Z +\yourdelta X Y \yourdelta Z.
$$
Since $\mu+\sigma>K/4$ then there exists $\alpha\in (0,2)$
such that 
\begin{equation}\label{alphadef}
	\sigma + \mu = {\alpha\over 2}+{K\over 2(2-\alpha)}.
\end{equation}
Using Young's inequality we have 
$$
	-\yourdelta X\yourdelta Y Z\le
    \frac{Z^2\yourdelta X^2}{2}\Big({1\over 2-\alpha}\Big) 
		+  {\yourdelta Y^2\over 2} (2-\alpha)
$$
and
$$
	\yourdelta XY\yourdelta Z\le
    \frac{Y^2\yourdelta X^2}{2}\Big({1\over 2b-\alpha}\Big)
		+ {\yourdelta Z^2\over 2} (2b-\alpha).
$$
Therefore
$$
{1 \over 2}\dot{V} + \Big(\sigma + \mu 
	-{Y^2\over 2(2b-\alpha)}
	-{Z^2\over 2(2-\alpha)} 
\Big)\yourdelta X^2 + {\alpha\over 2}\yourdelta Y^2 + 
	{\alpha\over 2}\yourdelta Z^2 \le
    0.
$$
Since our working assumption is that $U$ lies on the global attractor,
then Theorem~\ref{Ktheorem} and the fact that $b\ge 1$ implies that
$$
{Y^2\over 2(2b-\alpha)}
+{Z^2\over 2(2-\alpha)}
	\le {K\over 2(2-\alpha)} = 
		\sigma+\mu-{\alpha\over 2}
$$
Hence 
$$
	{1 \over 2}\dot{V} + {\alpha\over 2}
		\yourdelta X^2 + {\alpha\over 2}\yourdelta Y^2 +
    {\alpha\over 2}\yourdelta Z^2 \le
    0.
$$
and consequently $\sigma+\mu\ge 1$ implies that
$\dot{V} + \alpha V \le 0$.
Integrating over the interval $[0,t]$ yields
$V(t) \leq  V(0)e^{-\alpha t} $.
\end{proof}

\section{Noiseless Time-averaged Coupling}\label{NLTACoupling}

We now examine convergence of the trajectories using the 
time-averaged observation operator when $\hat\delta$
is known without noise.  Taking $\delta=\hat\delta$
and substituting ${\cal R}_\delta=\cL\circ\cO_\delta$ into
equation~(\ref{noerra}) yields the driven system given by
$$
    \dot{x} = -\sigma(y-x)+\mu (\bar X-\bar x)
$$
where
$$
	\bar X =
{1\over\delta}\int_{t-\delta}^t X(s)\, ds
\wwords{and}
	\bar x =
{1\over\delta}\int_{t-\delta}^t x(s)\, ds
$$
with $\dot y$ and $\dot z$ given as before by equations (\ref{drivenY})
and (\ref{drivenZ}).
Thus equations (\ref{NLIddoty}) and (\ref{NLIddotx}) remain the same but
the evolution of the $\Delta X$ given by equation~(\ref{NLIddotx}) now becomes
\begin{plain}\begin{equation}\label{NLTAdxo}\eqalign{
    \yourdelta\dot{X} &= -\sigma \yourdelta X + \sigma\yourdelta Y 
		- \mu \yourdelta\bar{X}
}\end{equation}\end{plain}%
where $\yourdelta\bar X=\bar X-\bar x$.
We show for $\mu$ sufficiently large and $\delta$ small that 
the approximating solution
converges to the
reference solution as $t$ tends to infinity.

Before proving the main result in this chapter, we first turn our
attention to an estimate that compares time-averaged
and instantaneous-in-time feedback terms.

\begin{lemma}\label{tadiffit} 
%Given $\yourdelta X$ as defined in Section ?? and $\yourdelta\bar{X} 
%= \frac{1}{\delta}\displaystyle\int_{t-\delta}^t X(s) \,ds$. 
Let $\yourdelta\bar X=\bar X-\bar x$.
We have
$$| \yourdelta X - \yourdelta\bar{X}|^2 \leq 4\delta(\sigma 
+ \mu)^2\displaystyle\int_{t-2\delta}^t\big\{
	|\yourdelta X|^2 + |\yourdelta Y|^2\big\}.$$ 
\end{lemma}
\begin{proof} By definition
\begin{align*}
    | \yourdelta X - \yourdelta\bar{X}| &
%\big|\yourdelta X(t) 
%    - \displaystyle\int_{t-\delta}^t\yourdelta X(s)\,ds\big| =
	= \frac{1}{\delta}\bigg|\int_{t-\delta}^t
		\big\{\yourdelta X(t)-\yourdelta X(s)\big\}\,ds \bigg| \\
%   & = \frac{1}{\delta}\bigg|\int_{t-\delta}^t\int_s^t 
%		\yourdelta\dot{X}(\rho)\,d\rho \,ds \bigg| \\
    &\leq \frac{1}{\delta}\int_{t-\del}^t\int_s^t 
		|\yourdelta\dot{X}(\rho)|\,d\rho \,ds
    \leq \int_{t-\del}^t
		|\yourdelta\dot{X}(\rho)|\,d\rho \\
    &= \int_{t-\delta}^t|-\sigma\yourdelta X(\rho) 
	    + \sigma\yourdelta Y(\rho) - \mu\yourdelta\bar{X}(\rho)| \,d\rho \\
    &\leq \sigma \int_{t-\delta}^t|\yourdelta X| 
		+ \sigma \int_{t-\delta}^t|\yourdelta Y| 
	    + \frac{\mu}{\delta}\int_{t-\delta}^t
		\int_{\rho-\delta}^{\rho} |\yourdelta X(\xi)|
		\,d\xi \,d\rho \\
    &\leq \sigma \int_{t-\delta}^t|\yourdelta X| 
	    + \sigma \int_{t-\delta}^t|\yourdelta Y| 
		+ \mu\int_{t-2\delta}^t |\yourdelta X(\xi) | \,d\xi \\
    &\leq (\sigma + \mu)\displaystyle\int_{t-2\delta}^t|\yourdelta X| 
    + \sigma\int_{t-\delta}^t|\yourdelta Y|.
\end{align*}
Therefore,
\begin{align*}
    | \yourdelta X - \yourdelta\bar{X}|^2 &\leq 2(\sigma 
    + \mu)^2\bigg(\displaystyle\int_{t-2\delta}^t|\yourdelta X|\bigg)^2 
    + 2\sigma^2\bigg(\int_{t-\delta}^t|\yourdelta Y|\bigg)^2\\
    &\leq 4\delta(\sigma + \mu)^2\int_{t-2\delta}^t 
		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\},
\end{align*}
which finishes the proof.
\end{proof}

We are now ready to show the convergence of the driven solution
to the free running solution.

\begin{proposition}\label{NLTAprop} 
Suppose $\delta=\hat\delta$ and $\varepsilon=0$.
Let $\alpha\in (0,2)$,
$\mu \ge {K/(2-\alpha)^2}-\sigma$ and 
$$	\delta<
	\sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 16\mu(\sigma+\mu)^2}}.$$
Then $||U-u|| \to 0$ as $t\to \infty$.
\end{proposition}

\begin{proof}
The proof proceeds as the proof 
of Proposition~\ref{NLIprop}.
After multiplying by $\yourdelta X$ the only difference is the additional 
term on the right hand side that
which we estimate using Lemma~\ref{tadiffit} as
\begin{align*}
    \mu(\yourdelta X - \yourdelta\bar{X})\yourdelta X
		&\le
    {\mu\over 2\alpha}|\yourdelta X - \yourdelta\bar{X}|^2 +
		{\alpha\mu\over 2}|\yourdelta X|^2\\
    &
		\leq {2\delta\mu (\sigma + \mu)^2\over \alpha}
		\int_{t-2\delta}^t 
		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}
		+{\alpha\mu\over 2}|\yourdelta X|^2.
\end{align*}
Therefore
\begin{plain}$$\eqalign{
{1 \over 2}\dot{V} + 
	\Big(\sigma + \mu
		-{\alpha\mu\over 2}
		-{Y^2\over 2(2b-\alpha)}
		&-{Z^2\over 2(2-\alpha)} 
	\Big)
\yourdelta X^2 + {\alpha\over 2}\yourdelta Y^2 + 
	{\alpha\over 2}\yourdelta Z^2 \cr
	&\le
		 {2\delta\mu (\sigma + \mu)^2\over \alpha}
		\int_{t-2\delta}^t 
		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}.
}$$\end{plain}%
By hypothesis
$$
	{\alpha\mu \over 2} + {K\over 2(2-\alpha)} 
	\le \mu+\sigma\Big(1-{\alpha\over 2}\Big).
$$
Therefore
\begin{align*}
    \dot V 
+ \alpha V
	\leq 
	    {4\delta\mu (\sigma + \mu)^2\over \alpha}
		\int_{t-2\delta}^t V(s)\,ds.
\end{align*}
Define $\cV(\tau)= V(\tau / \alpha)$. 
%$\dot V=\alpha \cV'(\tau)$.  
It follows that
$$
	{d\cV(\tau)\over d\tau}
		+\cV(\tau)\le {4\delta\mu(\sigma+\mu)^2\over \alpha^3}
		\int_{\tau-2\alpha\delta}^\tau \cV(s)\,ds.
$$
By hypothesis $\delta$ is small enough that we may apply
Corollary~\ref{intGronwallerror0} with 
$$A=4\mu(\sigma+\mu)^2/\alpha^3,\qquad B=0\wwords{and}h=2\alpha\delta
$$
to conclude that $V\to 0$ as $t\to\infty$.
\end{proof}

Note that by taking $\alpha$ small we obtain synchronization
for values of $\mu$ close to the limiting value $K/4-\sigma$
given in Proposition~$\ref{NLIprop}$.
However, as $\alpha$ vanishes the length $\delta$ of the
time averaging window also vanishes.
On the other hand, as $\alpha$ approaches 2, then
$\mu$ approaches infinity and
since $\delta$ depends inversely on $\mu^{3/2}$
then again $\delta$ vanishes.
Thus, there is some value $\alpha\in(0,2)$ for which
our analytic bound on $\delta$ is maximal.  Simple
calculus yields this optimal value to be
$$
  \alpha^*=-\rho\cos(\phi)+{22\over 15}+\rho\sqrt3\sin\phi
      \approx 0.28413
$$
where
$$
  \rho={4\sqrt{25370}\over 75}
\wwords{and}
  \phi={1\over 3}\arctan\Big({19\sqrt{1731443695}\over167665}\Big).
$$
For $\alpha=\alpha^*$ it follows that we may take
$$
  \mu\approx 513.153\wwords{and}\delta\approx 0.0000063216.
$$

\section{Unknown Noiseless Time-averaged Coupling}\label{UNTCoupling}

In the previous chapter we assumed the time averaging
window of the observations was known exactly.
We then used this same averaging window in the 
feedback control of the driven system to obtain exact 
synchronization.
In this chapter we examine the case when the time averaging 
in the observations of the free running solution is unknown.
%and the driven system is given by (\ref{NLTAUnkSoln}).
Specifically, we have
$$
    \dot{x} = -\sigma(y-x)+\mu 
		\Big(
		{1\over\hat\delta}\int_{t-\hat\delta}^t X(s)ds
		-{1\over\delta}\int_{t-\delta}^t x(s)ds
	\Big)
$$
with $\dot y$ and $\dot z$ given as before by equations (\ref{drivenY})
and (\ref{drivenZ}).
Recall that $\hat\delta$ is the unknown size of 
the averaging window in the observations of the free running 
solution and $\delta$ be the averaging
used in the feedback control of the driven system.
%\[\frac{du}{dt} = \cF(u) +
%    \mu\big(R_{\hat\delta}(U) 
%-R_{\delta}(u) \big). \]
Recall that $\hat\delta$ is the unknown size of 
the averaging window in the observations of the free running 
solution and $\delta$ is the averaging
used in the feedback control of the driven system.
In this case
\begin{plain}\begin{equation}
	\eqalign{\label{NLTAdxhat}
    {\yourdelta \dot X} =& -\sigma\yourdelta X + \sigma\yourdelta Y 
        - {\mu\over\hat\delta}\displaystyle\int_{t-\hat\delta}^{t} X
        +{\mu\over\delta}\displaystyle\int_{t-\delta}^{t} x  \cr
    =& -(\sigma+\mu)\yourdelta X + \sigma\yourdelta Y 
       + \mu(\yourdelta X-\yourdelta\bar{X})
		+ \mu{\cal E}_1 +\mu {\cal E}_2
}\end{equation}\end{plain}%
where
$$
       {\cal E}_1=
		{1\over\hat\delta}\int_{t-\delta}^{t-\hat\delta} X
\words{and}
       {\cal E}_2=
		\Big({1\over\delta}-{1\over\hat\delta}\Big)
			\int_{t-\delta}^t X
$$
represents the errors resulting from the unknown time 
averaging window.
Note that when $\delta=\hat\delta$ this is exactly the coupling
method treated in Proposition~\ref{NLTAprop}.  When
$\delta\ne\hat\delta$ exact synchronization does not occur;
however, the error between $u$ and $U$ can be bounded by
a constant which tends to zero as $\delta$ approaches $\hat\delta$.

We begin with a slightly modified version of Lemma~\ref{tadiffit}
that reflects the fact that $\hat\delta\ne\delta$.
\begin{lemma}\label{tadiffithat}
We have
\begin{align*}
	|\Delta X-\Delta \bar X|^2
	\le
		4\delta(\sigma+\mu)^2
		\int_{t-2\delta}^t\big\{|\Delta X|^2&+|\Delta Y|^2\big\}
		+8 \mu^2\delta^2 K \Big({\delta-\hat\delta\over\hat\delta}\Big)^2.
\end{align*}
\end{lemma}
\begin{proof}
The proof proceeds as in Lemma~\ref{tadiffit}.  Thus
\begin{plain}$$
\eqalign{
	|\Delta X-\Delta\bar X| 
	&\le \int_{t-\delta}^t |\Delta\dot X(\rho)|d\rho
	\le I_1+I_2+I_3
}$$\end{plain}%
where
\begin{plain}$$\eqalignno{
    I_1&=(\sigma+\mu)\int_{t-2\delta}^t |\Delta X|,\qquad
	I_2=\sigma\int_{t-\delta}^t |\Delta Y|\cr
\noalign{\noindent and}
	I_3&=
		\mu\int_{t-\delta}^t{1\over\hat\delta}
			\int_{\rho-\delta}^{\rho+\hat\delta} X(\xi)d\xi d\rho
		+\mu\int_{t-\delta}^t
			\Big({1\over\delta}-{1\over\hat\delta}\Big)
			\int_{\rho-\delta}^{\rho} X(\xi)d\xi d\rho
		\cr
		&\le \mu\bigg|\int_{t-\delta}^t {1\over\hat\delta}
			\int_{\rho-\delta}^{\rho+\hat\delta} \sqrt K\,d\xi d\rho\bigg|
		+\mu\bigg|\int_{t-\delta}^t
			\Big({1\over\delta}-{1\over\hat\delta}\Big)
			\int_{\rho-\delta}^{\rho} \sqrt K \,d\xi d\rho\bigg|\cr
		&= 2\mu \sqrt K \delta \Big|{\delta-\hat\delta\over\hat\delta}\Big|
}$$\end{plain}%
Squaring the results as
$$
	|\Delta X-\Delta\bar X|^2
		\le (I_1+I_2+I_3)^2
		\le 2 I_1^2+4 I_2^2 + 4 I_3^2
$$
yields the desired result.
\end{proof}

\begin{proposition}\label{UKNLTAprop}
Given $\alpha\in(0,2)$,
let 
$$\mu \ge JK/(2-\alpha)^2-\sigma
\words{where}
		J={\sigma(1+\sqrt 2)}
        \Big({\hat\delta\over 2} +\delta\Big)+1.
$$ 
and 
\begin{equation}\label{deltabound32}
\delta<
    \sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 16\mu(\sigma+\mu)^2}}.
\end{equation}
Then $$\limsup_{t\to\infty}||U-u||^2
< 
	{5e(2-\alpha)\mu^2\over\alpha}
%e {2-\alpha\over\alpha}
%	\cdot \Big(
%	{1\over 2} +
%		{4\mu^2}     \Big)
\Big({\hat\delta-\delta\over\hat\delta}\Big)^2.
      $$
\end{proposition}

\begin{proof}
The proof proceeds as before.
Upon multiplying equation~(\ref{NLTAdxhat}) by $\yourdelta X$ we estimate 
the additional terms as
$$
	\mu {\cal E}_i\yourdelta X\le
		{\mu \eta \over 2}
		{\cal E}_i^2\yourdelta X^2
		+
		{\mu \over 2\eta}
\words{for} i=1,2.
$$
%Therefore
%\begin{plain}$$\eqalign{
%{1 \over 2}\dot{V} &+
%    \Big(\sigma + \mu
%        -{\alpha\mu\over 2}
%		-{\mu\eta\over 2}\big({\cal E}_1^2+{\cal E}_2^2\big)
%        -{Y^2\over 2(2b-\alpha)}
%        -{Z^2\over 2(2-\alpha)
%}
%    \Big)
%\yourdelta X^2 \cr
%	&+ {\alpha\over 2}\yourdelta Y^2 +
%    {\alpha\over 2}\yourdelta Z^2
%    \le
%         {2\delta\mu (\sigma + \mu)^2\over \alpha}
%        \int_{t-2\delta}^t
%        \big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}+{\mu\over\eta}.
%}$$\end{plain}%
Since
$$
{Y^2\over 2(2b-\alpha)}
        +{Z^2\over 2(2-\alpha)}
	\le {1\over 2(2-\alpha)}\big(K-X^2\big)
$$
we obtain
\begin{plain}$$\eqalign{
{1 \over 2}\dot{V} &+
    \Big(\sigma + \mu
        -{\alpha\mu\over 2}
        +{X^2\over 2(2-\alpha)}
		-{\mu\eta\over 2}\big({\cal E}_1^2+{\cal E}_2^2\big)
        -{K\over 2(2-\alpha)}
    \Big)
\yourdelta X^2 \cr
	&+ {\alpha\over 2}\yourdelta Y^2 +
    {\alpha\over 2}\yourdelta Z^2
    \le
         {2\delta\mu (\sigma + \mu)^2\over \alpha}
        \int_{t-2\delta}^t
        \big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}\cr
		&\qquad\qquad\qquad\qquad\qquad\quad
		+{4\mu^2\delta^2K\over\alpha}
			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
		+{\mu\over\eta}.
}$$\end{plain}%
Now, by the Cauchy--Schwartz inequality
$$
	{\mu\eta}{\cal E}_1^2
\le
{\mu\eta\over\hat\delta^2} |\hat\delta-\delta|
		\bigg|
		\int_{t-\delta}^{t-\hat\delta} X^2
		\bigg|
\quad\hbox{and}\quad
	{\mu\eta}{\cal E}_2^2
\le
{\mu\eta\over\hat\delta^2} |\hat\delta-\delta|^2
		\bigg|
		{1\over \delta}
		\int_{t-\delta}^t X^2
		\bigg|.
$$
Upon taking
$$
	\eta={1\over 2(2-\alpha)}\cdot{\hat\delta^2\over(\hat\delta-\delta)^2}
		\cdot {1\over \mu}
$$
we obtain
\begin{plain}$$\eqalign{
	{X^2\over 2(2-\alpha)}-\mu\eta
		{\cal E}_1^2
	\ge
	{-1\over 2(2-\alpha)}
		\bigg|
			{1\over \hat\delta-\delta}
			\int_{t-\delta}^{t-\hat\delta}
				\big(X(t)^2-X(s)^2\big)ds\bigg|
}$$\end{plain}%
and
\begin{plain}$$\eqalign{
	{X^2\over 2(2-\alpha)}-\mu\eta{\cal E}_2^2
	\ge
	{-1\over 2(2-\alpha)}
		\bigg| {1\over \delta}
			\int_{t-\delta}^t
				\big(X(t)^2-X(s)^2\big)ds\bigg|.
}$$\end{plain}%
Since 
\begin{align*}
	|X(t)^2&-X(s)^2|=\Big|2\int_s^t X\dot X\Big|
	\le 2\sigma \int_s^t (X^2+ |XY|)\\
	&
	\le \sigma (1+\sqrt 2)\int_s^t \big(X^2+ Y^2\big)
	\le \sigma (1+\sqrt 2)(t-s)K
\end{align*}
then
$$
	{X^2\over 2-\alpha}-\mu\eta
        \big({\cal E}_1^2+{\cal E}_2^2\big)
	\ge{-\sigma(1+\sqrt 2)\over 2(2-\alpha)}
    \Big({\hat\delta+\delta\over 2}+{\delta\over 2}\Big)K
	={1-J\over 2(2-\alpha)}K.
$$
Consequently
\begin{align*}
{1 \over 2}\dot{V} &+
    \Big(\sigma + \mu
        -{\alpha\mu\over 2}
	-
        {JK\over 2(2-\alpha)}
    \Big)
	\yourdelta X^2 
	+ {\alpha\over 2}\yourdelta Y^2 +
    {\alpha\over 2}\yourdelta Z^2\\
    &\le
         {2\delta\mu (\sigma + \mu)^2\over \alpha}
        \int_{t-2\delta}^t
        \big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}
		+{4\mu^2\delta^2K\over\alpha}
			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
+{\mu\over\eta}.
\end{align*}
By hypothesis
$$
	{\alpha\mu\over 2}
    +
        {JK\over 2(2-\alpha)}
	\le
		\mu+\sigma \Big(1-{\alpha\over 2}\Big).
$$
Therefore
\begin{align*}
    \dot V
+ \alpha V
    \leq
        {4\delta\mu (\sigma + \mu)^2\over \alpha}
        \int_{t-2\delta}^t V(s)\,ds
		+{8\mu^2\delta^2K\over\alpha}
			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
+{2\mu\over\eta}.
\end{align*}
We apply Lemma~\ref{intGronwallerror} as in the proof
of Proposition~\ref{NLTAprop} except this time 
taking 
$$B=
		{8\mu^2\delta^2K\over\alpha^2}
			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
+{2\mu\over \alpha\eta}
.$$  The result follows.
\end{proof}

\section{Numeric Results for Noiseless Coupling}\label{NoiselessComp}

In all our numerical experiments the free-running solution 
$U$ was obtained by taking 
$$U_0=(-5.5751, -3.24345, -11.0728).$$
As this value of $U_0$ lies very close to the global attractor,
the resulting trajectory
satisfies the conditions of Theorem~\ref{Ktheorem}
to within a certain numerical error and therefore 
we suppose the bound (\ref{numbound}) holds.
A sharper bound may be obtained {\it a posteriori\/} 
as the maximum value of the actual numerical solution.  
In particular, the trajectory for $U$
considered here satisfies
\begin{equation}\label{numbound}
	\|U(t)\|^2\le 1247.0911\qquad\hbox{for}\qquad t\in [0,500]
\end{equation}
which is about 20 percent smaller than the theoretical 
bound.

%Computationally, our free-running solution satisfies
%$$K=(18.2818, 24.6582, 8.4834)$$
%and
%$$k=(-18.8543,-25.7439,-34.55988).$$

\begin{figure}[ht]\label{measd}
    \centerline{\begin{minipage}[t]{0.9\textwidth}
    \caption{\label{d025meas}%
	Illustration of time-averaged exact measurements of $U$
	for different values of $\delta$.}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{d025meas.eps}}
\end{figure}

We compute $u$ using equations (\ref{noerra})
with $\widetilde{\cal R}={\cal R}=R_\delta$ 
and $u_0=(0,0,0)$ for different values 
of $\delta$ with $\mu=30$.  
This value of $\mu$ is comparable
to the value $\mu=K/40\approx 38.5$ used for Figure 5 
of \cite{Stuart14}. 
Figure~$\ref{measd}$ illustrates the 
phase shift that occurs for $\delta >0$ which delays the measurements of $U$ in time.

\begin{figure}[ht]\label{avgd}
    \centerline{\begin{minipage}[t]{0.9\textwidth}
    \caption{\label{e0assim}%
	Results when coupling time-averaged exact measurements
	with an averaging window of size $\delta$ when $\delta=\hat\delta$.}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{e0assim.eps}}
\end{figure}

In particular, Figure~\ref{e0assim} shows the evolution of 
the error $\|U-u\|^2$ when coupling the free-running solution to the
driven solution using noise-free time averaged measurements of $X$
with $\mu=30$ when $\hat\delta=\delta$ for $\delta\in \{ 0, 0.25, 0.375 \}$.
For $\delta=0$ and $\delta=0.25$ the error converges 
to zero within the limits of the floating point arithmetic
used for the computations.
We point out, however, that the rate of convergence
appears slightly slower when $\delta=0.25$.
On the other hand the error remains large for $\delta=0.375$.

\begin{figure}[ht]
    \centerline{\begin{minipage}[t]{0.9\textwidth}
    \caption{\label{avgdup}%
	Results when coupling time-averaged exact measurements
	with an averaging window of size $\delta$ near
$\delta_c$ for $T<2000$ when $\hat\delta=\delta$.}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{e0assimupper.eps}}
\end{figure}

Further computations show that the conditions for convergence
are intractable when $\delta \approx 0.33$. 
Intuitively, we suspect there is a value $\delta_c$ such that
for $\delta < \delta_c$ the rate of convergence is very slow, but
synchronization is eventually achieved and the error decays to zero,
and for $\delta > \delta_c$ the systems fail to synchronize.
Our calculations suggest $\delta_c\in [0.31,0.33]$, provided such
a critical value exists.
What we do know, is that numerically for values $\delta>0.33$ there
is no sign of synchronization, and for values $\delta<0.31$ the
two solutions synchronize to within the limits of the rounding error
of the double precision arithmetic used for our calculations.
Figure~\ref{avgdup} shows instability of the synchronization
for $\delta = 0.318$, where the error $\|U-u\|^2$ 
oscillates over time through $20$ decimal orders of magnitude.

\begin{figure}[ht]
    \centerline{\begin{minipage}[t]{0.9\textwidth}
    \caption{\label{avgdiffmu}
	Results when coupling time-averaged exact measurements
	with an averaging window of size $\delta = 0.334$ using
    increasing values of $\mu$ where $T<600$ when $\hat\delta=\delta$.}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{e0diffmu.eps}}
\end{figure}

While the theory requires $\mu$ to be greater than $375.07$,
a slightly less restrictive bound on $\mu$ may be obtained 
by using the value for $K$ suggested by the bound (\ref{numbound}).
Either bound, however, is significantly more restrictive 
than the value chosen here which 
works when the size of the averaging window is sufficiently small.
In this case where $\delta > 0.33$, there are no 
values of $\mu$ for which the error converges to zero, illustrated in
Figure~\ref{avgdiffmu}.

By further varying the value of $\delta$ it appears that
$\delta\le 0.31$ is sufficient to ensure
$\|U-u\|\to 0$ numerically as $t\to\infty$.
We further compare the theoretical size of $\delta$ to 
this numerically determined value.
To find the largest value of $\delta$ that Proposition~\ref{NLTAprop} 
guarantees will lead to synchronization
we maximize the upper bound in 
(\ref{deltabound32}) with respect to $\alpha$.
Note that as $\alpha$ vanishes in the bound (\ref{deltabound32}) 
the length $\delta$ of the time averaging window also 
vanishes.  Moreover, $\delta$ also vanishes as 
$\alpha$ approaches 2,
because $\delta$ depends inversely on $\mu^{3/2}$ and
$\mu$ approaches infinity as $\alpha$ approaches $2$.
Simple
calculus now yields the optimal value of $\alpha$ to be
$$
  \alpha^*=-\rho\cos(\phi)+{22\over 15}+\rho\sqrt3\sin\phi
      \approx 0.28413
$$
where
$$
  \rho={4\sqrt{25370}\over 75}
\wwords{and}
  \phi={1\over 3}\arctan\Big({19\sqrt{1731443695}\over167665}\Big).
$$
For $\alpha=\alpha^*$ it follows that we may take
$$
  \mu\approx 513.153\wwords{and}\delta\approx 0.0000063216.
$$
Using the value for $K$ suggested by the bound 
(\ref{numbound}) leads to a 30 percent larger value for $\delta$;
however, in either case the analytic bounds are more than $10\,000$
times stricter than what works numerically.

In summary our numeric results show
measurements of $X$ averaged with respect to a small
averaging window are just as effective for synchronizing the
driven solution to the free-running solution as exact
measurements taken instantaneously in time.  However, if
the averaging window is too large, then the information is
blurred too much for $u$ to synchronize with $U$.
This is consistent with the theoretical results of
Proposition~\ref{NLTAprop} which proves the
convergence of the driven solution to the free-running
solution only when $\delta$ is sufficiently small and $\mu$
sufficiently large.
We emphasize that our analytic bounds on $\mu$ and $\delta$
are much more restrictive than what works numerically.

\begin{figure}[ht]
    \centerline{\begin{minipage}[t]{0.9\textwidth}
    \caption{\label{avgddhat}%
	Results when coupling time-averaged exact measurements with
    window size $\hat\delta=0.25$ using a feedback term with
	averaging window size $\delta\ne\hat\delta$.  Note that
	$\Delta\delta=\delta-\hat\delta$.
	}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{mix3a.eps}}
    \centerline{\includegraphics[height=0.5\textwidth]{mix3b.eps}}
\end{figure}

Now consider the case treated by Proposition~\ref{UKNLTAprop} 
where the exact size of the time averaging 
window present in the observational measurements is unknown.
Figure~\ref{avgddhat} describes the evolution of $\|U-u\|^2$ 
when $\hat\delta=0.25$ and $\delta$ is smaller but near 
$\hat\delta$.
Note that $\delta$ greater than
$\hat\delta$ results in a nearly identical graph.
The asymptotic error
%$$\limsup_{t\to\infty} \|U-u\|^2$$
may be approximated numerically as a function of 
$\Delta\delta=\delta-\hat\delta$ by
$$
%	\limsup_{t\to\infty} \|U-u\|^2
%		\approx 
	E(\Delta\delta)=
	\max \big\{\, \|U-u\|^2 : t\in [50,100]\,\big\}.
$$
From Figure~$\ref{avgddhat}$, there is a decrease in the error $\|U-u\|^2$ as
$\Delta\delta$ decreases before reaching $\Delta\delta=0$. 
Table~\ref{tableddhat} illustrates the the convergence of the driven solution, where
the limit supremum is taken over the error for all $t>T$.
As expected, the error levels 
decrease as $\delta$ gets closer to $\hat\delta$.
It is reasonable to determine that there exists a function that will 
allow us to predict
the largest value $|\delta -\hat{\delta}|$ that results in convergence.
We now consider the functional dependency how 
$E(\Delta\delta)$ depends on $\Delta\delta$.

    \begin{table}[h!]\label{tableddhat}
    \centerline{\begin{minipage}[t]{0.9\textwidth}
    \caption{\label{limsupexact}%
	Limsup of $\| U - u\|^2$ for different values of $\Delta\delta$.
    }
    \end{minipage}}
    \medskip
    \centering
    \begin{tabular}{  r | r }
    \hline\hline
\vphantom{\raise8pt\hbox{H}}%
	$\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
    \hline
\vphantom{\raise8pt\hbox{H}}%
$-2^{-2}$&$1267.31$ \\
$-2^{-5}$&$194.081$ \\
$-2^{-8}$&$5.61624$ \\
$-2^{-11}$&$0.0906275$ \\
$-2^{-14}$&$0.00140762$ \\
$-2^{-17}$&$2.19772\times 10^{-05}$ \\
$-2^{-20}$&$3.43361\times 10^{-07}$ \\
$-2^{-23}$&$5.36495\times 10^{-09}$ \\
$-2^{-26}$&$8.38272\times 10^{-11}$ \\
$-2^{-29}$&$1.30979\times 10^{-12}$ \\
$-2^{-32}$&$2.04656\times 10^{-14}$ \\
$-2^{-35}$&$3.19773\times 10^{-16}$ \\
$0.0$&$2.67042\times 10^{-25}$ \\
[1ex]
\hline
\end{tabular}\qquad\qquad
    \begin{tabular}{  r | r }
    \hline\hline
\vphantom{\raise8pt\hbox{H}}%
	$\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
    \hline
\vphantom{\raise8pt\hbox{H}}%
$2^{-2}$&$2663.41$ \\
$2^{-5}$&$249.552$ \\
$2^{-8}$&$5.86352$ \\
$2^{-11}$&$0.0911086$ \\
$2^{-14}$&$0.00143265$ \\
$2^{-17}$&$2.24025\times 10^{-05}$ \\
$2^{-20}$&$3.50073\times 10^{-07}$ \\
$2^{-23}$&$5.46996\times 10^{-09}$ \\
$2^{-26}$&$8.54684\times 10^{-11}$ \\
$2^{-29}$&$1.33543\times 10^{-12}$ \\
$2^{-32}$&$2.08664\times 10^{-14}$ \\
$2^{-35}$&$3.26052\times 10^{-16}$ \\
$0.0$&$2.67042\times 10^{-25}$ \\
[1ex]
\hline
\end{tabular}
\label{regress}
\end{table}

%Empirical evidence allows us to infer that there is an exponential function that will fit the rate of
%convergence in terms of $\Delta\delta$. We find that the numerical data 
%supports our results and provides greater
%detail to the exact coefficients necessary for convergence.
The theoretical bounds given by 
Proposition~\ref{UKNLTAprop} suggest that
$E(\Delta\delta)$ is proportional to 
the square of $\Delta\delta$.
In order to test this hypothesis we performed 
a least squares fit to find $m$ and $s$ such that
$$
	\log E(\Delta\delta) \approx \log m + s \log(\Delta\delta).
$$
Figure~\ref{ftmix} shows that the least squares fit
agrees with $E(\Delta\delta)$ to remarkable precision
over a range of ten decimal orders of magnitude.
Since the fitted value $s=1.99964$ 
is so close to $2$, we presume that the $\Delta\delta$ 
dependency given by our analytic bound is physical
even though the values for $\mu$ and $\delta$
are much more restrictive than numerically needed.

\begin{figure}[ht]
    \centerline{\begin{minipage}[b]{0.9\textwidth}
    \caption{\label{ftmix}%
	The numerical data from Table~\ref{limsupexact}
	when plotted with the least squares fit
	of $m(\Delta\delta)^s$
	given by $m=378647$ and $s=1.99964$.}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{ftmix.eps}}
\end{figure}

It is worth remarking that the theoretical bound in
Proposition~\ref{UKNLTAprop} actually depends on the 
relative error $\Delta\delta/\hat\delta$ which,
as we have held $\hat\delta=0.25$ constant, is
proportional to the absolute error $\Delta\delta$
in the above computations.
Computations using different values for $\hat\delta$
are a direction for future work described in
Section~\ref{futurehatdelta}.  
Preliminary calculations suggest that a better fit
is obtained for bounds of the form
$$
	E(\Delta\delta) \approx m 
			\Big({\delta-\hat\delta\over
			\delta_c-\hat\delta}\Big)^2
$$
where $\delta_c\approx 0.33$ is the critical 
value of $\delta$ for which synchronization fails detailed
in Figure~\ref{avgdup}.
The numerical dependence of the bound on $\hat\delta$ is 
a point of future work.

\chapter{Coupling with Noise}

In this chapter we examine the synchronization of the free running and driven
solutions with the addition of a time-averaged Brownian motion. By
synchronization we mean that the system driven by noisy observations will converge
to the true solution within a tolerance determined by the level of observational noise.
The expected value $\bf E$ of the convergence is examined as we are only able to
bound the error of the system with some probability for a finite
amount of time, preventing us from forming a generalized proof for pathwise convergence.
In particular, we bound the expected value of the error 
and then use Chebyshev's inequality to find probabilistic 
bounds on the paths.

\section{Noisy Instantaneous-in-Time Coupling}

Consider when the observations of $U$
are noisy and satisfy equation~(\ref{tildecO})
%$$\tilde {\cal O}(U)dt = Xdt + \varepsilon dW_t$$
where $W_t$ is a one-dimensional 
standard Brownian motion.
Thus, the noise present in the observational measurements 
satisfies ${\bf Var}(\varepsilon W_t)= t\varepsilon^2$.
In this case, equation~(\ref{drivenX}) becomes
\begin{equation}\label{dxnoise}
    dx = -\sigma(y-x)dt+\mu(X-x)dt + \varepsilon \mu dW_t.
\end{equation}
Note that the noise present in the observations appears
in equation~(\ref{dxnoise}) multiplied by the factor $\mu$.
Therefore, increasing $\mu$ to strengthen the coupling 
between $U$ and $u$
also amplifies the noise.

The techniques employed are almost identical to those in \cite{Olson14} 
but have been detailed here to provide a concrete point of reference
for comparing our main results which involve time-averaged measurements.
The results in this section, though slightly sharper,
are similar to those which appear in \cite{Stuart14}. 
As in Section~\ref{NLICoupling}, carefully examining the case 
without time-averages first provides a concrete point of reference 
for comparing our results which involve time-averaged measurements.
\begin{proposition}\label{NIprop} 
Suppose $\delta=0$, $\hat\delta=0$ and $\varepsilon>0$.
Let $\mu>K/4-\sigma$, then
$$\limsup_{t\to\infty}{\bf E}\big[||U-u||^2\big] 
	\le
{\mu^2\varepsilon^2\over 
		\sigma+\mu+1-\sqrt{(\sigma+\mu-1)^2+K}
}$$
\end{proposition}

\begin{proof}
With the addition of the noise, equation~(\ref{NLIddotx})
becomes the stochastic differential equation
$$
d(\yourdelta X) = -(\sigma + \mu)\yourdelta X dt + \sigma\yourdelta Y dt
 - \mu
{\varepsilon} dW_t.
$$
Using Ito's formula and the same estimates as in 
Proposition~\ref{NLIprop} we obtain
$$d{V} + \alpha V dt \le 
    2\mu\varepsilon \yourdelta X d W_t +\mu^2\varepsilon^2 dt.$$
Integrating over the interval $[0,t]$ yields
$$
	V(t)e^{\alpha t}-V(0)\le 
		2\mu\varepsilon\delta \int_0^t e^{\alpha s}\yourdelta X(s) d W_s
		+{\mu^2\varepsilon^2 \over \alpha}\big( e^{\alpha t} -1 \big).
$$
Now, taking expected values obtains
$$
	{\bf E}\big[V(t)\big]\le e^{-\alpha t}{\bf E}\big[V(0)\big]
		+{\mu^2\varepsilon^2 \over \alpha}\big( 1-e^{-\alpha t} \big).
$$
Consequently
$$
	\limsup_{t\to\infty} {\bf E}[V] \le {\mu^2\varepsilon^2\over\alpha}.
$$
Solving for $\alpha$ in equation~(\ref{alphadef}) finishes the proof.
\end{proof}

\section{Noisy Time-averaged Coupling}\label{NTACsec}

In this section we consider the case when
the noisy observations
of $X$ have been averaged in time over a known window of 
size $\hat\delta$.  Thus we take $\delta=\hat\delta$ and
%${\cal R}=\widetilde R_\delta$ 
in equation~(\ref{NLTAUnkSoln}) and
equation~(\ref{drivenX}) becomes
$$
	\dot x = -\sigma(y-x) +\mu(\bar X-\bar x)+\mu\xi
\words{where} \xi(t)={\varepsilon\over\delta}\big(W_t-W_{t-\delta}\big).
$$
Thus
$$
	\yourdelta\dot X 
	=-(\sigma+\mu)\yourdelta X+\sigma\yourdelta Y +
		\mu(\yourdelta X-\yourdelta\bar X)+\mu\xi.
$$
Theoretically the presence of a small time average in the measurements 
does not substantially affect the results of the instantaneous in
time case.
Our results show that measurements averaged over
small time windows lead to bounds that are similar to those given 
by Proposition~\ref{NIprop} when there are no time averages.
The expected value of the difference 
between the driven solution and the free running solution in
both cases is bounded by a constant factor of the variance of the noise.
In particular, we have

\begin{proposition}\label{NTAprop} 
Let $\alpha\in(0,2)$ and $\mu\ge K/(2-\alpha)^2-\sigma$.  If
$$	\delta<
	\sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 32\mu(\sigma+\mu)^2}}.
$$
Then
$$
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] <
	e\Big({8\mu^3\over\alpha^2}+{2\mu\over \alpha^2\delta}\Big)
		\varepsilon^2.
$$
\end{proposition}

\begin{proof} 
The proof proceeds as the proof of Proposition~\ref{NTAprop}, where the
only difference is an additional noise term.
Similar estimates as in the proofs of Lemma~\ref{tadiffit}
and Lemma~\ref{tadiffithat} yield that
$$
	|\Delta X-\Delta\bar X|^2
		\le
		4\delta(\sigma+\mu)^2
		\int_{t-2\delta}^t \big\{|\Delta X|^2+|\Delta Y|^2\big\}
		+4\mu^2\delta\int_{t-\delta}^t\xi^2.
$$
Following similar estimates as before, multiply 
by $\yourdelta X$ and use Young's inequality as
\begin{plain}$$\eqalign{
    \mu(\yourdelta X - \yourdelta\bar{X})\yourdelta X
		&\le
    	{4\delta\mu (\sigma + \mu)^2\over \alpha}
		\int_{t-2\delta}^t 
		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}\cr
		&\qquad
		+{4\mu^3\delta\over \alpha}\int_{t-\delta}^t\xi^2
+{\alpha\mu\over 4}|\yourdelta X|^2
}$$\end{plain}%
and
\begin{plain}$$\eqalign{
\mu\xi \yourdelta X
&\le 
 {\mu\xi^2 \over
    \alpha}+
{\alpha\mu \over 4} |\yourdelta X|^2 .
}$$\end{plain}
to obtain
$$
    \dot{V} + \alpha V
    \le {8\delta\mu(\sigma + \mu)^2 \over \alpha}
	\displaystyle\int_{t-2\delta}^t(\yourdelta X^2 +
    \yourdelta Y^2) 
	+{8\mu^3\delta\over\alpha} \int_{t-\delta}^t \xi^2
	+{2\mu\xi^2 \over \alpha}.
$$
Since ${\bf E}[\xi^2]=\varepsilon^2/\delta$ for any time $t$, 
then setting
$\cV(\tau)={\bf E}[V(\tau/\alpha)]$ yields
$$
{d{\cV}(\tau)\over d\tau} + \cV(\tau) \leq 
	{8\delta\mu(\sigma + \mu)^2\over \alpha^3}
		\int_{t-2\alpha\delta}^t \cV(s)\,ds
+\Big({8\mu^3\over\alpha^2}+{2\mu \over \alpha^2\delta}\Big)\varepsilon^2.
$$
We apply Lemma~\ref{intGronwallerror} 
taking 
$$A=
	{8\delta\mu(\sigma + \mu)^2\over \alpha^3},\qquad
B=
\Big({8\mu^3\over\alpha^2}+{2\mu \over \alpha^2\delta}\Big)\varepsilon^2
\qquad\hbox{and}\qquad h=2\alpha\delta.$$
The result follows.
\end{proof}

\section{Unknown Noisy Time-averaged Coupling}\label{UNTACsec}

In this section we examine the case when there is noise in
the measurements and the length of the time averaging window 
is unknown.  
Our main result is a version of Proposition~\ref{UKNLTAprop}
that also allows noise in the observations.
As before let $\hat\delta$ be the length of the unknown averaging
window in the observations of the free running solution and
$\delta$ be an approximation of $\hat\delta$ that will be used 
in the feedback control of the driven system.
In this case the equation governing the evolution $x$ in the driven system
becomes
$$
    \dot{x} = -\sigma(y-x)+\mu
        \Big(
        {1\over\hat\delta}\int_{t-\hat\delta}^t X(s)ds
        -{1\over\delta}\int_{t-\delta}^t x(s)ds
    \Big) + \mu\xi
$$
where $\xi$ is as in Section~\ref{NTACsec}.
Since there is now noise in the observations, exact synchronization does 
not occur when $\delta=\hat\delta$.  Thus, our theoretical bounds
on $\|U-u\|^2$ take the form given by equation~(\ref{noisydeltadelta}) consisting
of two terms, one which vanishes as $\delta\to\hat\delta$ and
the other which vanishes as $\varepsilon\to 0$.
In particular, we obtain

\begin{proposition}\label{UKNTAprop}
Suppose $\delta\ne\hat\delta$ and $\varepsilon>0$.
Given $\alpha\in(0,2)$,
let 
$$\mu \ge JK/(2-\alpha)^2-\sigma
\words{where}
		J={\sigma(1+\sqrt 2)}
        \Big({\hat\delta\over 2} +\delta\Big)+1.
$$ 
and 
$$  \delta<
    \sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 32\mu(\sigma+\mu)^2}}.$$
Then $$\limsup_{t\to\infty}{\bf E}\big[\|U-u\|^2 \big]
< {5e(2-\alpha)\mu^2\over \alpha}\cdot
{(\hat\delta-\delta)^2\over\hat{\delta}^2}
	+
    e\Big({16\mu^3\over\alpha^2} +{2\mu\over\alpha^2\hat\delta}\Big)\varepsilon^2.
$$
\end{proposition}

\begin{proof}
Modifying the proof of Lemma~\ref{tadiffithat}
we add the term for measurement error, which yields
\begin{align*}
	|\Delta X-\Delta\bar X|^2
		&\le
		4\delta(\sigma+\mu)^2
		\int_{t-2\delta}^t \big\{|\Delta X|^2+|\Delta Y|^2\big\}\\
		&+16 \mu^2\delta^2 K \Big({\delta-\hat\delta\over\hat\delta}\Big)^2
		+8\mu^2\delta\int_{t-\delta}^t\xi^2.
\end{align*}
Now, modifying the proof of Proposition~\ref{UKNLTAprop} as was done
for the proof of Proposition~\ref{NTAprop} to add the term which
represents measurement error yields 
\begin{align*}
    {d\cV(\tau)\over d\tau}
+ \cV(\tau)
    &\leq
        {8\delta\mu (\sigma + \mu)^2\over \alpha^3}
        \int_{\tau-2\alpha\delta}^\tau \cV(s)\,ds\\
		&+16 \mu^2\delta^2 K \Big({\delta-\hat\delta\over\hat\delta}\Big)^2
			+{2\mu\over\alpha\eta} 
            +{16\mu^3 \over \alpha^2}
	+ {2\mu\varepsilon^2\over \alpha^2\delta}.
\end{align*}
Applying Lemma~\ref{intGronwallerror} 
finishes the proof.
\end{proof}

\section{Numeric Results for Noisy Coupling}\label{NoisyComp}

The first set computations in this section treat the case 
where no time averaging is present in the observational measurements.
Under this hypothesis Proposition~\ref{NIprop} 
shows that the expected value of the difference between 
the approximating solution and the exact solution
is bounded by a factor of the variance of the noise.
A similar bound was obtained 
%by Law, Shukla and Stuart 
as Theorem 4.1 
in \cite{Stuart14} which, using the notation here, may be written as
\begin{equation}\label{stubound}
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] \le 
	{\mu^2\varepsilon^2\over 2-K/(2\mu)}
\qquad\hbox{for}\qquad \mu>K/4.
\end{equation}
Optimizing the bound in the bound (\ref{stubound}) with respect to $\mu$ and 
using the value of $K$ given by Theorem~\ref{Ktheorem}
we obtain that 
$$
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] \le 
	{27K^2\varepsilon^2\over 128}\le (5.005\times 10^5)\varepsilon^2.
$$
Alternatively, 
optimizing the bound in Proposition~\ref{NIprop} yields
$$
	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] \le 
	(4.838\times 10^5) {\varepsilon^2}
$$
which is about 3 percent smaller.  
Moreover, since
$$
{\mu^2\varepsilon^2\over 
		\sigma+\mu+1-\sqrt{(\sigma+\mu-1)^2+K}}
<{\mu^2\varepsilon^2\over 2-K/(2\mu)}
$$
provided $\mu>K/4$, the bound given in the bound (\ref{stubound}) is
strict.  Therefore, there exists $T>0$ such that
by Chebyshev's inequality 
$$
	{\bf P}\Big\{\,\omega\in\Omega : \|U-u\|^2\le 
{10\mu^2\varepsilon^2\over 2-K/(2\mu)}
\,\Big\}
		\ge 0.9.
$$
Computations in \cite{Stuart14} demonstrate
numerical bounds on $\|U-u\|$ which are proportional to 
$\varepsilon$ and therefore consistent with
the theoretical bounds described above.
In the present thesis we fix the noise level at 
$\varepsilon=0.01$ and focus on the effects of the 
time averaging.

\begin{figure}[ht]
    \centerline{\begin{minipage}[b]{0.9\textwidth}
    \caption{\label{e001paths}%
	Results when coupling noisy instantaneous-in-time measurements
	with $\mu=30$ and $\varepsilon=0.01$. The expected value was 
	computed using 500 independent realizations of Brownian motion
	and $L(t)$ is a computed bound on $90$ percent of the paths at 
	each point in time.
	The gray region represents the 500 pathwise solutions, one of which
    has been plotted in a darker shade for illustration.}
	\medskip
    \end{minipage}}
    \centerline{\includegraphics[height=0.5\textwidth]{e001paths.eps}}
\end{figure}

For a frame of reference, first consider 500 independent
realizations of Brownian motion corresponding to 
$\omega_i\in\Omega$ such that $i=1,2,\ldots,500$ and 
compute the corresponding pathwise solutions $u_i$ using 
equation~(\ref{noerra}) with the coupling 
term ${\cal R}=\widetilde R$.
The exact algorithm used to compute $u$ shall 
be described later in Section~\ref{numerics}.
Approximate the expected value of $\|U-u\|^2$ by
$$
	{\bf E}\big[\|U-u\|^2\big]\approx
		{1\over 500} \sum_{i=1}^{500} \|U-u_i\|^2
$$
and let $L(t)$ be the value such that
$$
	{\rm card}\big\{\, i\in \{1,2,\ldots,500\} 
		: \|U-u_i\|^2\le L(t)\,\big\} = 450.
$$
Thus, $L(t)$ bounds $90$ percent of the
paths at each point in time.
In particular, assuming $500$ samples is statistically large enough, 
we have
$$
	{\bf P}\big\{\,\omega\in\Omega : \|U-u\|^2\le L(t)
		\,\big\} \approx 0.9.
$$
Figure~\ref{e001paths} describes
the results of this first computation.  Note that the
expected value of 
$\|U-u\|^2$ oscillates around $0.01$ and
that $L(t)$ is about 5 times greater.
Thus, $L(t)$ is about 2 times smaller than the bound
given by Chebyshev's inequality (\ref{cheby}).
Moreover, at each point in time a small percentage 
of trajectories are significantly more accurate than
expected and a few satisfy $\|U-u_i\|^2\le\varepsilon^2$.

The computation described in Figure~\ref{e001paths} may
be directly compared to Figure 5 in \cite{Stuart14}.
Similar values of $\mu$ and $\varepsilon$ were employed
in both computations and result in similar looking
pathwise solutions.  The difference is that our
expected values have been computed by averaging
over the pathwise solutions $u_i$ which result from 
independent Brownian motions and approximate
the time-dependent expected values which appear in 
the analysis,
whereas~\cite{Stuart14} computes expected values that 
do not change over time and appear to have been computed 
by taking a long-time average over a single pathwise solution.
We now consider how the presence of time averaging in the
observational measurements affects the degree to which 
$u$ synchronizes with~$U$.

\begin{figure}[ht]
    \centerline{\begin{minipage}[b]{0.9\textwidth}
    \caption{\label{e001meas}%
	Time-averaged noisy measurements 
	for different values of $\delta$ corresponding to a 
	representative Brownian path
    with $\varepsilon=0.01$.}
	\medskip
    \end{minipage}}
    \centerline{\includegraphics[height=0.5\textwidth]{e001mtalk.eps}}
\end{figure}

Figure~\ref{e001meas} depicts the time evolution of a typical 
set of noisy observational measurements with and without time 
averaging.
Note that when $\hat\delta=0$ there is no time
averaging and resulting observations show
oscillation of the trajectory,
As we are dealing with a chaotic system, we can expect that these oscillations
will perturb the system enough so that synchronization is only possible within
a tolerance of the measure of the noise.
When $\hat\delta>0$
the noise has been smoothed out at the expense of a phase
shift that delays the measurements in time.  We now perform
a number of calculations of $u$ using measurements of
the kind depicted in Figure~\ref{e001meas}.

Figure~\ref{e001exp} depicts the evolution of the expected
value of $\|U-u\|^2$ over time for $\mu=30$,
$\varepsilon=0.01$ and $\delta\in \{ 0, 0.25, 0.375 \}$.
As in the noise-free case, the difference between $u$ and $U$ 
remains large when $\delta=0.375$.
However, the difference between $\delta=0.25$ and $\delta=0$
appears greater than in the noise-free case.
Intuitively, the presence of moving time averages seems to 
result in decreased efficiency of the feedback control 
that nudges the driven solution towards the free running solution.
Without noise, only enough nudging to overcome the tendency for 
nearby trajectories of the Lorenz equation to diverge is needed.
As the nudging must also overcome the noise in the present case,
which in turn may account for the expected error levels being 
slightly greater when $\delta=0.25$.
Further support for this intuition may also be inferred from 
the already mentioned slower rate of convergence in the absence of noise 
$\delta=0.25$ compared to $\delta=0$.

\begin{figure}[ht]
    \centerline{\begin{minipage}[b]{0.9\textwidth}
    \caption{\label{e001exp}%
	Results when coupling time-averaged 
	noisy measurements with an
	averaging window of size $\delta$ and
a noise level $\varepsilon=0.01$.
	The expected values were computed using 500 independent
	realizations of Brownian motion.}
    \end{minipage}}
	\medskip
    \centerline{\includegraphics[height=0.5\textwidth]{e001exp.eps}}
\end{figure}

\begin{figure}[ht]\label{mixassim}\label{mix3ae001}
    \centerline{\begin{minipage}[b]{0.9\textwidth}
    \caption{\label{mix3a}%
    Results when coupling time-averaged noisy measurements with
	$\varepsilon=0.01$ and
    window size $\hat\delta=0.25$ using a feedback term with
    averaging window size $\delta\ne\hat\delta$.  Note that
    $\mu=30$ and $\Delta\delta=\delta-\hat\delta$.
    }
    \end{minipage}}
    \medskip
    \centerline{\includegraphics[height=0.5\textwidth]{mix3ae001.eps}}
    \centerline{\includegraphics[height=0.5\textwidth]{mix3be001.eps}}
\end{figure}

Figure~\ref{e001exp} depicts the evolution over time of
the expected value of $\|U-u\|^2$ for $\mu=30$,
$\varepsilon=0.01$ and $\delta\in \{ 0, 0.25, 0.375 \}$ with
respect to
500 independent realizations of noisy measurements of the kind
depicted in Figure~\ref{e001meas}.
As in the noiseless case, the difference between $u$ and $U$
remains large when $\delta=0.375$.
Similarly, for $\delta=0.25$ and $\delta=0$ the error decreases
over time; however, unlike the noiseless case
the asymptotic error level for $\delta=0.25$ is
noticeably larger than for $\delta=0$.  In particular,
\vfill\eject
\begin{plain}$$
\max\big\{\,{\bf E}\big[\|U-u\|\big]:t\in[50,100]\,\big\}\approx
\cases{
    0.0089 & for $\delta=0$\cr
    0.49 & for $\delta=0.25$.
}
$$\end{plain}%

Intuitively, the presence of moving time averages seems to
result in a decreased efficiency of the feedback control
that nudges the driven solution towards the free running solution.
Without noise, this decrease in efficiency doesn't matter
because the difference between the free running and driven
solutions tends to zero over time anyway, only perhaps
with a slightly decreased rate of convergence.
In the presence of noise, however, the nudging must also
overcome the noise.
This leads to a higher error level in the difference
between $U$ and $u$ over time.

The last set of computations treats the case in
Proposition~\ref{UKNTAprop} when the length of
the averaging window used for the observations is unknown.
Figure~\ref{mix3ae001} depicts the evolution
of the expected value of $\|U-u\|^2$ when
$\hat\delta=0.25$ and $\delta$ is smaller but near $\hat\delta$.
The error level decreases as
$\delta$ gets closer to $\hat\delta$, but unlike the noiseless
case, there is very little difference between
$\Delta\delta=0$ and $\Delta\delta=-2^{-11}$.
Bounds on the expected error may be approximated
numerically as
$$
    \widetilde E(\Delta\delta)
    =\max\big\{\, {\bf E}\big[\|U-u\|^2\big] :
        t\in[50,100]\,\big\}.
$$
A summary of our computations are presented in
Table~\ref{limsupe001}.
These numeric results show, as do our theoretical bounds,
that $\delta$ can be tuned to match $\hat\delta$ only up to
the point where the noise term dominates.
Specifically,
when $\hat\delta=0.25$ and $\epsilon=0.01$
%our computations suggest
it is possible
to tune $\delta$ so that $|\delta-\hat\delta|< 2^{-8}$.

As seen in Figure~\ref{e001meas} typical values of $X$
range from $-10$ to $10$.  Moreover, the free running
solution used in our experiments satisfies
$$
    \Big({1\over 100}\int_0^{100} X(s)^2ds\Big)^{1/2}
        \approx 7.92731.
$$
We finish by noting that $\varepsilon=0.01$ is $1.3$
percent the root-mean-squared value of $X$ and that
$2^{-8}$ is $1.6$ percent the value of $\hat\delta$.
The exact relationship between the value of $\varepsilon$
and the degree to which $\delta$ can and needs to be tuned
would be an interesting direction for future study.

\begin{table}[ht]
    \centerline{\begin{minipage}[b]{0.9\textwidth}
    \caption{\label{limsupe001}%
    Values of
    $\widetilde E(\Delta\delta)=
    \max \big\{\, {\bf E}\big[\|U-u\|^2\big] : t\in [50,100]\,\big\}$
    as a function of $\Delta\delta=\delta-\hat\delta$.
    Here $\hat\delta$ represents
    the unknown size of the averaging present in the observational
    measurements and
    $\delta$ an approximation of $\hat\delta$ used in the feedback
    control.}
    \end{minipage}}
    \bigskip
    \centering
    \begin{tabular}{  r | r }
    \hline\hline
\vphantom{\raise8pt\hbox{H}}%
%   $\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
    $\Delta\delta$ & $\widetilde E(\Delta\delta)$ \\ [0.5ex]
    \hline
\vphantom{\raise8pt\hbox{H}}%
$-2^{-2}$&$1.60729\times 10^{6}$ \\
$-2^{-5}$&$38419.5$ \\
$-2^{-8}$&$44.133$ \\
$-2^{-11}$&$0.693591$ \\
$0$&$0.491966$ \\
[1ex]
\hline
\end{tabular}\qquad\qquad
    \begin{tabular}{  r | r }
    \hline\hline
\vphantom{\raise8pt\hbox{H}}%
%   $\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
    $\Delta\delta$ & $\widetilde E(\Delta\delta)$ \\ [0.5ex]
    \hline
\vphantom{\raise8pt\hbox{H}}%
$2^{-2}$&$6.09399\times 10^{6}$ \\
$2^{-5}$&$62104.1$ \\
$2^{-8}$&$38.5955$ \\
$2^{-11}$&$0.56483$ \\
$0$&$0.491966$ \\
[1ex]
\hline
\end{tabular}
\end{table}

\chapter{Numerical Methods}\label{numerics}

This section described the numerical methods used to obtain the 
results in Section~\ref{NoiselessComp} and Section~\ref{NoisyComp}.
We compute both the free running solution and the driven solution
using Euler's explicit method
\begin{plain}$$\eqalign{
	U^{n+1}&=U^{n}+h{\cal F}(U^n)\cr
	u^{n+1}&=u^{n}+h{\cal F}(u^n)+
		h\mu\big(R_{\hat\delta}(U^n)-R_\delta(u^n)\big)
		+h\mu\hat\xi^n
.\cr
}$$\end{plain}%
in double-precision floating-point arithmetic
with step size $h=1/2048$. 
Here $\hat\delta=m_0h$ for some $m_0\in{\bf N}$
but $\delta$ may be any positive floating-point number.
Upon writing $U^n=(X_n,Y_n,Z_n)$ and $u^n=(x_n,y_n,z_n)$, it 
follows that $R_\delta={\cal L}\circ{\cal O}_{\delta}$ where
$$
	{\cal O}_{\hat\delta}(U^n)={1\over m_0}\sum_{k=0}^{m_0-1} X_{n-k}
$$
and 
by interpolation 
setting $m_3=\lfloor\delta/h\rfloor$ that
$$
	{\cal O}_{\delta}(u^n)=
	{h\over\delta}\Big\{
		\Big({\delta\over h}-m_3\Big)
		x_{n-m_3}+
			\sum_{k=0}^{m_3-1} x_{n-k}
		\Big\}.
$$

%\chapter{Standard Brownian Motion}

The noise term $\hat\xi^n=\hat\xi(nh)$ is given as in Section~\ref{UNTACsec}
by
$$
	\hat\xi(t)={\varepsilon\over\hat\delta}\big(W(t)-W(t-\hat\delta)\big)
$$
where $W(t)$ is a standard Brownian motion,
one of the simplest of the continuous-time stochastic 
processes.
Numerically we use the construction of Brownian
motion as developed by L\'evy and Ciesielski.
By L\'evy and Ciesielski, there is a probability space $\Omega$ and a sequence
of independently distributed standard normal random variables $(G_n)_{n\ge 0}$
such that for $\omega\in\Omega$ and $t\in[0,1]$
$$
W(\omega, t)= \lim_{n\to\infty} W_n(\omega,t)
\wwords{where}
	W_n(\omega,t)=\displaystyle\sum_{k=0}^n G_k(\omega)S_k(t)
$$
is a Brownian motion, where $S_n(t)$ is from the family of Schauder functions.
The Schauder functions $S_{2^j+k}$ are tent-functions with support $[k2^{-j},
(k+1)2^{-j}]$ and a maximal value $\textstyle{1\over 2}2^{-j/2}$ at the tip of the
tent.
Using an application of Minkowski's inequality, monotone convergence theorem,
and by the completeness of the space of continuous functions, there is a
subsequence of $(W_{2^j}(t, \omega))_{j\ge 1}$ which converges uniformly in
$t\in[0,1]$ for a subset $\Omega_0\subset \Omega$.
Defining $W(t, \omega)$ as a limiting function, we see that it
indeed inherits the continuity of $W_{2^j}(t, \omega)$. We conclude that there
exists a restriction of $W(t, \omega)$ that is a Brownian motion defined on
$\Omega$.

The algorithm for the construction of Brownian motion is an adaptation based on
L\'evy's original interpolation argument.
Let $t_0<t<t_1$ and let $W(t)$ be a Brownian motion. Then,
$$ 
G' = W(t) - W(t_0) \wwords{and} G'' = W(t_1) - W(t)
$$ 
are Gaussian random variables with mean zero and variances $t-t_0$ and $t_1-t$
respectively. Let $\Gamma$ be a further $N(0,1)$ random variable which is
independent of $W(t_0)$ and $W(t_1) - W(t_0)$. 
If $t$ is the midpoint of $[t_0,
t_1]$, then $\Gamma$ is a random variable with the same distribution as
$W(t)$ and is a one-dimensional Brownian motion. 
\begin{theorem}\label{levy}(Levy 1940)
    The series 
    $$
    W(t, \omega) = \displaystyle\sum_{n=0}^\infty \big(W_{2^{n+1}}(t,\omega) -
    W_{2^{n}}(t, \omega)\big) + W_1(t,\omega), \qquad t\in[0,1]
    $$
    converges a.s. uniformly. In particular, $\big(W(t)\big)_{t\in[0,1]}$ is a
    Brownian motion.
\end{theorem}
$W(t)$ is almost surely continuous and can be constructed
iteratively using independent increments.
This algorithm is based on L\'evy's construction of Brownian motion
by means of a limit as $n\to\infty$ of piecewise linear functions 
taken on subsequently finer and finer refinements of a dyadic grid
of size $1/2^n$.
Numerically, continuous time processes are sampled 
on a finite grid as we can only generate finitely many values in
finite time.
Assuming we have already constructed $W(k2^{-j})$ for some fixed $j\ge 1$ and all $k \in [0,2^j]$, 
then
$$
    W(l2^{-j-1}) = \begin{cases}
                        W(k2^{-j}) \qquad &l = 2k\\
                        \textstyle{1\over 2}(W(k2^{-j}) +
                        W((k+1)2^{-j})) + \Gamma_{2^j +k} \qquad &l = 2k+1\\
                   \end{cases}
$$
so $W_{2^j}(t)$ is therefore a piecewise linear interpolation of the Brownian path
$W(t)$.
We take the size of the time steps used in our
numerical simulations equal to $h=1/2^n$ so that no further 
processing is needed to compute $W(t)$ at the values needed
for our numerical simulations.
This results in a numerical approximation of Brownian motion,
where any refinement of the discretization yields a refinement of the
same simulated path.  The points on the discrete time grid are simulated
linearly, which is possible as Brownian motion has continuous paths.

The seed of the random generator provides a unique random
variable $\omega$ in the Gaussian space $\Omega$ used to create a unique Brownian motion.
The refinement of an already simulated path
is an interpolation in $[t_0, t_1]$
taken as dyadic points $t= k2^{-j}$ the expansion of $W(t, \omega)$ is finite and
we are able to calculate the value of
$W(t, \omega)$, by successive approximations $t \to W(t, \omega)$.
Set $W(0,\omega)$ to zero and let $W(1,\omega)$ be an $N(0,1)$ 
distributed random variable.
The initialization of $\omega \in \Omega$ as an $N(0,1)$ distributed random
variable is implemented using 1024-bit Marsaglia pseudo-random 
number generators \cite{Marsaglia2003}.
The random numbers generator may take a fixed seed as an input, and as such,
the same Brownian 
path can be sampled at any resolution on the dyadic grid. In this way we were able
to change the time-scale of the simulation without changing the results from
previous experiments.
We initialize the L\'evy-Ciesielski algorithm with an initial refinement, then refine
as needed to support our averaging scheme. The algorithm as described in
the chapter on simulation by Bj\"orn B\"ottcher in
Schilling and Partzsch \cite{Schilling2012},
can be described as follows,

\begin{algorithm}[ht]
 \textbf{Algorithm:} (L\'evy-Ciesielski)\\
Let $J\ge1$ we the order of refinement.\\
Initialize $w_0 := 0$\\
Generate $w_1 \sim N(0,1)$\\
 \For{$j=0$ to $J-1$}{
    \For{$l= 0$ to $2^j - 1$}{
    1. Generate $y \sim N(0,1)$\\
    2. Set $w_{(2l+1)/2^{j+1}} = \textstyle{1\over 2}(w_{l/2^j} + w_{(l+1)/2^j}) 
    + 2^{-(\textstyle{j\over 2} + 1)}y$\\
    }
 }
\textbf{Then} $(w_0, w_{1/2^J}, w_{2/2^J},\cdots , w_1) \sim (W_0, W_{1/2^J}, W_{2/2^J},\cdots , W_1)$
\end{algorithm}

Note that taking $\hat\delta=h$ reduces $\hat\xi^n$
to exactly the term used in the Euler-Maruyama method
for the simulation of the stochastic differential
equation given by equation~(\ref{dxnoise}).  
Thus, taking $\hat\delta=h$ in our computations corresponds 
to noisy in\-stan\-tan\-eous-in-time coupling in our analysis.
Although the sample paths of our Brownian motions 
do not depend on $h$, 
the sensitive dependence of the 
Lorenz system on initial conditions and the 
resulting deterministic chaos exhibited implies that the 
free running solution $U$ strongly depends on $h$.
Therefore, we have fixed $h=1/2048$ to ensure that the same 
reference solution $U$ is considered in all our simulations.

Theoretically, if $\delta=\hat\delta$, $u_0=U_0$ and $\varepsilon=0$, 
then $u(t)=U(t)$ for all $t\ge 0$ and any value of $\mu$.  
This property is preserved at the discrete level in our numerics.
In particular, when $\delta=\hat\delta$ and $\varepsilon=0$
exact synchronization of $u^n$ with $U^n$ is possible and was 
observed in certain simulations.
Exact bit-for-bit synchronization of $u^n$ with $U^n$ seems to
result from a lucky coincidence in the rounding of the floating 
point arithmetic, whereas, in general synchronization is
only good up to the least significant bits.
Note when $\delta\ne\hat\delta$ or $\varepsilon>0$ that
exact synchronization is neither theoretically possible nor 
was numerically observed.

\chapter{Conclusions}

This thesis considers coupling two systems of equations using
noisy partial observations of the phase space that have been
blurred in time by means of a moving time average.
The inclusion of blur using time averages in the observational 
measurements is both realistic from a physical point of view
as well as tractable in our mathematical and numerical frameworks.
The major contributions of our study are four new theorems 
that cover time averages and numeric simulations that show
the coupling works even better than what is guaranteed by
the analysis.  Namely, the original work in this thesis
centers on the statements and proofs of Propositions \ref{NLTAprop},
\ref{UKNLTAprop}, \ref{NTAprop} and \ref{UKNTAprop} and the
corresponding numeric simulations.

In the context the model system, the Lorenz equations, we have shown that the 
data-assimilation method introduced in \cite{Olson14} is well-posed
when the observational data is contaminated by a moving average
with sufficiently short averaging window. In the noiseless case,
analysis and numeric simulation shows that synchronization
of the driven solution to the free-running solution occurs when
the time averaging window is known and small enough.
Moreover, when the time averaging window is unknown, the bound on 
the error is proportional to $(\Delta\delta)^2$ where $\Delta\delta$ 
is the difference between the size of the actual averaging window 
and the guess for the size of the window used in the feedback
control.

In the presence of noise, time averaging smooths out the noise
in the observational measurements at the expense of a phase
shift that delays the measurements in time.
Although averaging gives no improvement in the analytic and numerical
bounds on $\|U-u\|$, there is also no significant deterioration 
in those bounds provided the averaging window is small enough.
In fact, this is the punch line of this thesis:  {\it short time
averages can be compensated for in the feedback term and as a
result have minimal effect on the quality of the synchronization 
between the free-running solution and the driven solution.}
Note, however, that time averaging appear to slightly weaken the
coupling between the driven and the free-running solution
which, in turn, yields a slight increase in the expected error levels.

\chapter{Future Work}

\section{Improved Bound on Fractal Dimension of Attractor}
	\label{fractalbound}
Using the improved ellipsoid described in Appendix~A, we conjecture that
an improved analytic bound on the fractal dimension of the global
attractor ${\cal A}$ of the Lorenz equations may be found using the
techniques in Doering and Gibbon \cite{Doering95a}.

\section{Numerically Determined Upper Bound}

In the case where the size of the averaging window is unknown, we conjecture
that an improvement to the analytical bound given in

Noting that in Figure~\ref{mixassim} the difference between ${\bf E}[\| U - u\|^2]$ and $L(t)$ is less than a factor of $2$, it may be possible to compute a bound numerically that will improve the bound obtained analytically using the Chebyshev inequality.
By using a non-linear least squares we postulate that an upper bound on $\| U - u\|$ can be determined in the case where the averaging window of $U$ is unknown.

\section{Adapting $\mu$ by Computing Local Lyapunov Exponents}

We postulate that an improvement on convergence can be achieved through the use
of an adaptive filter that tunes the $\mu$ parameter as the system evolves by
testing the rate of convergence at time $t$.

We conjecture that an adaptive filter may be constructed by computing local
Lyapunov numbers. By determining the rate of divergence of the trajectories, we can allow 
for larger values of $\mu$ when the system is 'well-behaved', 
In the noiseless case, we can achieve synchronization for unstable values of
$\delta$ such as $\delta = 0.318$ as shown in Figure~\ref{avgdup}.
In the noisy case, the noise in the observations can be made
to be smooth enough that convergence below the level of observational noise can be achieved.

\section{Reconstructing Attractor Dynamics}

Takens' \cite{Takens81} proved that the time-delayed 
versions 
$$
[y(t),y(t-\tau),y(t-2\tau),\cdots,y(t-2n\tau)]
$$ 
of one generic signal would suffice 
to embed the $n$-dimensional manifold. 
This may be compared to the topological result
by Whitney \cite{Whitney36} in which a single observation
in $2n+1$ dimensions can be replaced by $2n+1$ observations
of one dimension.  Namely, Taken's proved

\begin{theorem} Let $M$ be a compact manifold of dimension $d$. 
For pairs $(\phi, h)$,
where $\phi : M \to M$ is a smooth (at least $C^2$) diffeomorphism and 
$h : M \to R$ a smooth
function, it is a generic property that the $(2d +1)$-fold observation map
$H_k[\phi, h] : M \to \R^{2d+1}$
defined by
$$
x \to (h(x), h(\phi(x)), \ldots, h(\phi^{2d} (x)))
$$
is an immersion (i.e. $H_k$ is one-to-one between $M$ and its image with both 
$H_k$ and $H^{-1}_k$ differentiable).
\end{theorem}
The theorem can be applied to time series by taking $\phi$ to be the time $T$ map of
the underlying
(continuous time) dynamical system, i.e. $\phi_j (x_0) = x(jT)$, 
where $x(t·)$ is the
trajectory starting
at $x_0$. 
Since $H_k$ is a diffeomorphism 
its inverse is differentiable) this reconstruction
preserves the
dimension of any invariant set and the Lyapunov exponents of the flow.
\begin{figure}[ht]\label{reconst}
\begin{center}
\caption{Lorenz attractor reconstructed in $X$ with time delay $T = 1$.}
\includegraphics[width=10cm]{lorenz_reconst.eps}
\end{center}\end{figure}

We can see from Figure~$\ref{reconst}$ that the reconstruction of the Lyapunov
attractor results in similar, but not identical geometry in the phase space. 
However, according to Takens' Theorem, the Lyapunov spectrum and the correlation
dimension are preserved by the embedding. It is therefore reasonable to assume
that a system constructed by averages where $\delta < \delta_c$ will also
preserve these properties. In this case he phase space of $U$ will be exactly
the sets of observational data. It will be difficult to compute $H^{-1}$
directly or exactly. Therefore we may be able to compute $H^{-1}$ by
approximating its determining form as defined in \cite{Jolly15}.

\section{Unknown Dynamics of Free Running Solution}
\label{whatissigma}
It is realistic to suppose that only an approximation $\widetilde{\cal F}$
is known of the exact dynamics ${\cal F}$ of the free running solution.
A simple example for the Lorenz systems is when
the exact parameters values $\hat\sigma$, $\hat r$ and $\hat b$ are 
unknown.
In this case we write
\begin{align*}
	{\cal F}(U)=
    \begin{bmatrix}\hat\sigma(Y-X)\\
    -\hat\sigma X-Y-XZ\\ -\hat bZ+XY-\hat b(\hat r+\hat\sigma)\end{bmatrix},
\quad
	\widetilde {\cal F}(U)=
    \begin{bmatrix}\sigma(Y-X)\\
    -\sigma X-Y-XZ\\ -bZ+XY-b(r+\sigma)\end{bmatrix}.
\end{align*}
where $\sigma$, $r$ and $b$ are guesses for the
true values of the parameters.  Just as we obtained bounds on
$\|U-u\|$ when $\Delta\delta=\delta-\hat\delta\ne 0$ that vanished when 
$\Delta\delta\to 0$, we expect similar bounds in terms of
$\Delta\sigma$, $\Delta r$ and $\Delta b$

\section{Existence of $\delta_c$}

Our calculations suggest that $\delta_c$, if it exists, must
lie somewhere between $0.31$ and $0.33$.  The fact that $\|U-u\|^2$
oscillates through $20$ decimal orders of magnitude by hitting
the noise floor due to rounding error when $\delta=0.318$ implies
that extended precision arithmetic is needed to further characterize
$\delta_c$.  One could use the GMP Gnu multiprecision library
to more accurately determine $\delta_c$.  Similar techniques were
used by Hayden \cite{HaydenThesis} to more accurately characterize 
the critical sampling interval for discrete in time observations.

\section{Correcting Phase Shift when $\hat\delta\ne\delta$}

In the case where $\hat\delta > \delta_c$, then taking $\delta =
\hat\delta$ does not lead to synchronization. 
However, taking $\delta < \delta_c$ may lead to usable
bounds on $\|U-u\|$.
We may improve these bounds by time-advancing the measurements by
$$
    \hat\delta - \delta \over 2
$$
so that the phase shift caused by averaging is the same in both 
systems even though $\hat\delta \ne \delta$.

\section{Statistical Test Whether $U-u$ is Gaussian}

While $u$ is driven by a Gaussian process, the dynamics of the Lorenz
equation is highly non-linear.  Figure~\ref{e001paths} indicates 
that the expected
value of $\|U-u\|^2$ is quite near the top of the gray region, however,
this is not unexpected as it is the square of a vector in ${\bf R}^3$.
The question is, therefore, at any fixed point in time to what extent 
are probability distributions of $X-x$, $Y-y$ and $Z-z$ distributed
as Gaussian.  Numerically, this could be tested by plotting a
histogram of $X-x$, fitting it to a Gaussian, checking the goodness
of fit and calculating the probability that it arose from a Gaussian
distribution.

\section{Nonlinear Least Squares Fit of $M$}
\label{futurehatdelta}
We consider performing a nonlinear fit
%
%$$
%	\log E \approx \log M +\ 2\log (\delta-\hat\delta) - 
%		\gamma \log (\delta_c-\hat\delta)
%$$
to obtain constants $M$, $\gamma$ and $\delta_c$ such that
$$
	E \approx  M (\delta-\hat\delta)^2 / (\delta_c-\hat\delta)^\gamma
$$
Here $\delta_c$ represents the largest value for which 
$\delta=\hat\delta$ leads to convergence.  In particular, 
for values of $\hat\delta$ too large, there is no good bound 
on $E$ even when $\delta\approx\hat\delta$.
Note that $M$ has the same units as $E$ multiplied by
units of time to the power $\gamma-2$.  Therefore taking $\gamma=2$ 
yields a constant $M$ which is invariant with respect to a change of 
scales in time.

\section{Tuning $\delta$ Using Only the Observations}

Our results suggest it is possible to determine the size 
$\hat\delta$ of the unknown averaging window by 
varying $\delta$ is a way that minimizes the resulting error.
In the context of data assimilation, the only 
information actually available concerning $U$ are the time 
averaged measurements of $X$.  Therefore, it is
more relevant to check whether
$$
	{\cal E}=\|R_{\hat\delta}(U)-R_\delta(u)\|^2
        =\bigg|{1\over\hat\delta}\int_{t-\hat\delta}^t X(s)ds
        -{1\over\delta}\int_{t-\delta}^t x(s)ds\bigg|^2
$$
can be used to numerically determine $\delta$.

\section{Extension of Results to Other Dissipative Systems}

The techniques used in our analysis also apply to other model
problems such as the two-dimensional Navier--Stokes equations and
the surface quasi-geostrophic equations.
In those cases, the resulting integro-differential inequality is 
non-linear.
Delayed time averages in the noiseless case for 
is treated by Jolly, Martinez, Olson and Titi for the surface 
quasi-geostrophic equations in \cite{Jolly16}.
In the noisy case, the resulting non-linearity makes estimating 
the expected values of $\|U-u\|^2$ difficult.
It is possible that a slightly modified coupling algorithm which
filters statistical outliers from the observational measurements 
could be used to treat this case.

\section{Same Bounds as Stochastic Case} 
When $\delta$ tends to zero the differential equations with averages
tend to the stochastic case covered by Proposition~\ref{NIprop}.
However, the bounds obtained in Proposition~\ref{NTAprop} blow up
as $\delta$ vanishes.  It is possible to obtain a version of 
Proposition~\ref{NTAprop} such that the bounds remain bounded
when $\delta$ vanishes and are consistent with those which
cover the $\delta=0$ case of Proposition~\ref{NIprop}.  Namely,
we write the noise term as
$$
	\mu\xi(t)\Delta X(t) =
	\mu\xi(t)\big(\Delta X(t)-\Delta X(t-\delta)\big) +
	\mu\xi(t)\Delta X(t-\delta)
$$
and then estimate as in Lemma~\ref{tadiffit} to obtain
\begin{align*}
	|\Delta X(t)-\Delta X(t-\delta)|^2
		&\le \Big(\int_{t-\delta}^t |\Delta \dot X(s)|ds\Big)^2\\
		&\le 4\delta(\sigma +\mu)^2\int_{t-2\delta}^t V
			+ 4\mu^2\delta\int_{t-\delta}^t \xi^2.
\end{align*}
Since $\xi(t)$ is independent of $\Delta X(t-\delta)$ then
$$
	{\bf E}\big[\mu\xi(t)\Delta X(t-\delta)\big]
	=\mu {\bf E}\big[\xi(t)]\cdot {\bf E}[\Delta X(t-\delta)\big]=0.
$$
This implies
\begin{align*}
	{\bf E}\big[\mu\xi(t)\Delta X(t)\big] 
		&\le
	{\bf E}\big[\delta\mu^2\xi^2\big]
		+{1\over 4\delta}
		\Big(
4\delta(\sigma +\mu)^2\int_{t-2\delta}^t V
            + 4\mu^2\delta\int_{t-\delta}^t 
				{\bf E}\big[\xi^2 \big] \Big) \\
		&= 
(\sigma +\mu)^2\int_{t-2\delta}^t V
+2\mu^2\varepsilon^2.
\end{align*}
To finish the proof requires a modified version of the
integro-differential Gronwall inequality to handle the case
when
$$
	{d{\cal V}(t)\over dt}
		+{\cal V}(t)
	\le (A_0+hA_1)\int_{t-h}^t {\cal V}(s)\,ds + B.
$$
We hypothesis that the result is likely to place greater restriction
on the maximum size of $\delta$---likely of the order $\sqrt \mu$
smaller.

\chapter*{Appendix A}

We now describe a spherical bound on the Lorenz trajectories that is
better than existing bounds from Doering and Gibbon \cite{Doering95a}.
Our bound is based on an additional tuning parameter $\eta$ 
and is given by
\begin{equation}\label{Mbound}
    X^2 + Y^2 + (Z-\eta)^2 
    {b^2(r + \sigma - \eta)^2 \over \delta(2b - \delta)}
\end{equation}
where
$\delta = 2(b-1)-2 + \epsilon \eta$ and
$$
    \epsilon = {-\sigma + 1 + \sqrt{\sigma^2 - 2\sigma + 1 + \eta^2} \over
    \eta}. 
$$
Now, differentiating with respect to $\eta$ gives 
the optimal value of $\eta \approx 1.8882316669$.
Substituting this value back into inequality (\ref{Mbound})
we arrive at
$$
    X^2 + Y^2 + (Z-1.8882316669)^2 \le 1456.461665,
$$
which is about $5$ percent smaller than previous bounds.

\chapter*{Appendix B}

This section contains C-language source code used in this thesis. There
are two files:  the first is a pseudo-random number generator 
and the second is the main routine used to produce our simulations.

\section{Pseudo-random Number Generator}

The random number generator is based on the 
public domain implementation by Sebastiano Vigna of the
1024-bit Marsaglia Xorshift algorithm \cite{Marsaglia2003}.
\bigskip

\lstinputlisting{xonorm.c}

The above source contains modifications to 
include a routine that generates normally distributed random numbers
that will be used to create the Brownian paths
representing the noise terms in the observational measurements
in this thesis.
These changes begin on line 44 with the 
routine{\tt\ xonorm }which returns
normally distributed random numbers 
obtained by a polar coordinate transformation.

\section{Main Routine}

The main routine consists of the ODE solver, averaging functions
and implementation of the L\'evy-Ciesielski algorithm used to
create our Brownian motions.
This code was used to perform all our simulations.  
Prior to compilation the following
preprocessor definitions need to be made:
\begin{itemize}
\item {\rm BETA} --- The value of $\beta=8/3$ in the Lorenz system.
\item {\rm SIGMA} --- The value of $\sigma=10$ from the Lorenz system.
\item {\rm RHO} --- The value of $r=10$ from the Lorenz system.
\item {\rm M0} --- The value $\hat\delta={\rm M0}/{\rm N}$ for observation blur.
\item {\rm M3} --- The value $\delta={\rm M3}/{\rm N}$ for the feedback.
\item {\rm N} --- The timestep $h=1/{\rm N}$ where ${\rm N}=2048$ 
		for the ODE solver.
\item {\rm EPSILON} --- The amplitude $\varepsilon$ of the noise term.
\item {\rm MU} --- The relaxation parameter $\mu$ in the feedback term.
\item {\rm M} --- The time of integration $T={\rm M}$.
\item {\rm PMOD} --- Output data every ${\rm PMOD}$ time steps.
\item {\rm L} --- Size ${\rm L}=5$ of the cache for the Brownian paths.
\end{itemize}
The exact code used for the simulations in this thesis follows:
\bigskip

\lstinputlisting{main.c}

Note the averaging routine{\tt\ avg }takes values of 
${\rm M0}$ and ${\rm M3}$ 
that need not be integral and performs an interpolation in 
line 40 to handle decimal part.
The L\'evy-Ciesielsky algorithm called through
the function{\tt\ getb }includes a least recently used
cache as an optimization because the noise term
$$
	\xi^n={\varepsilon \over\delta}\big(
		W(t_n)-W(t_n-\hat\delta)\big)
$$
repeatedly samples the Brownian motion at two different points
in time separated by the distance $\hat\delta$.  
This routine is seeded by the number given in line 159 by
default.  If a parameter is supplied on the command line,
this is used for the seed instead.  The
program was run 500 times with different seeds on the
command line to 500 output files which were then
averaged together to compute the expected values
${\bf E}[\|U-u\|^2]$.

Lines 152--153 treat the case $\hat\delta=0$ as ${\rm M0}=1$
and $\delta=0$ as ${\rm M3}=1$, which reduces to the
Euler--Maruyama method from simulating stochastic differential 
equations.
Line 184 computes a numerical bound $K$ on the free running
solution such that $X^2+Y^2+Z^2\le K$.
Data was output every 64 timesteps.
The condition in lines 199 and 201 turn on the coupling only
after $t>\max\{\delta,\hat\delta\}$ as described in 
(\ref{intdiff}).
Line 201 assumes ${\rm M0}$ is an integer when 
running simulations with noise.  This condition was satisfied
in our simulations where the values of $\hat\delta$
considered $\hat\delta=.25$ obtained when ${\rm M0}=512$
and $\hat\delta=0$ which corresponds to ${\rm M0}=1$.

\end{manuscript}

\nocite{*}
\bibliography{thesis}

% Figures

\end{document}

### 2019-09-26 input.c

@@ -1,0 +1,34 @@
+
+int main(int argc,char *argv[]){
+    int opt;
+    while((opt=getopt(argc,argv,"e:o:t:T:s")) != -1) {
+        switch (opt) {
+case 'e':
+			epsilon=atof(optarg);
+			break;
+case 'o':
+			data=optarg;
+			break;
+case 't':
+            t=atoi(optarg);
+            break;
+case 'T':
+            T=atoi(optarg);
+            break;
+case 's':
+			sflag=1;
+			break;
+default:
+            fprintf(stderr,
+"Usage: %s [options]\n"
+"Options:\n"
+"    -e x    Set noise level to x.\n"
+"    -o s    Set output directory to s.\n"
+"    -T n    Approximate supremum by taking t less than n.\n"
+"    -s      Skip the compile and the generation of data.\n"
+"    -t n    Approximate supremum by taking t greater than n.\n",
+                argv[0]);
+            exit(1);
+        }
+    }
+}

### 2019-09-26 main.c

@@ -1,0 +1,209 @@
+/*  
+    This program uses the original form of the Lorenz equations
+    as stated in 
+
+    Lorenz, Deterministic Nonperiodic Flow, Journal of the Atmospheric
+    Sciences, Volume 20, 1963.
+
+    X' = -sigma X + sigma Y
+    Y' = -XZ + rX - Y
+    Z' = XY - bZ
+
+    The change of variables zeta = Z - r - sigma yields
+
+    X' = -sigma X + sigma Y
+    Y' = -sigma X - Y - X zeta
+    zeta' = - b zeta + XY - b(r+sigma)
+
+    We know theoretically that if (X,Y,zeta) is on the attractor, then
+
+    X^2+Y^2+zeta^2 <= K = b^2(r+sigma)^2/4/(b-1) = 1540.27
+*/
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <math.h>
+#include <float.h>
+#include "xonorm.h"
+
+#define BETA (8.0/3)
+#define SIGMA 10.0
+#define RHO 28.0
+
+#ifndef M0
+#define M0 512.0
+#endif
+#ifndef M3
+#define M3 512.0
+#endif
+#ifndef N
+#define N 2048
+#endif
+#ifndef EPSILON
+#define EPSILON 0.0
+#endif
+#ifndef MU
+#define MU 30
+#endif
+#ifndef M
+#define M 50
+#endif
+#ifndef PMOD
+#define PMOD (N/64)
+#endif
+
+double beta=BETA, sigma=SIGMA, rho=RHO, mu=MU, epsilon=EPSILON;
+double x[6]={ -5.5751, -3.24345, 26.9272, 0,0,0 }, f[6];
+double xmax[6] = { FLT_MIN, FLT_MIN, FLT_MIN, FLT_MIN, FLT_MIN, FLT_MIN };
+double xmin[6] = { FLT_MAX, FLT_MAX, FLT_MAX, FLT_MAX, FLT_MAX, FLT_MAX };
+double vmax = 0;
+double myeta = - SIGMA - RHO;
+double Umax = 0;
+double MM0=M0, MM3=M3;
+
+// Cache of Brownian motion paths
+#define L 5
+static struct {
+    int j,q;
+    double b[N+1];
+} p[L];
+static double e[M+1];
+static uint64_t s[M];
+
+// Return normal N(mu,sigma) distributed random variable
[…]

### 2019-09-26 xonorm.c

@@ -1,0 +1,56 @@
+#include "xonorm.h"
+#include <math.h>
+
+/*  Written in 2014 by Sebastiano Vigna (vigna@acm.org)
+
+To the extent possible under law, the author has dedicated all copyright
+and related and neighboring rights to this software to the public domain
+worldwide. This software is distributed without any warranty.
+
+Modified 2015 to produce normally distributed random numbers for use in
+coupling simulations with noisy observations.  */
+
+static uint64_t x=12455480610190296555ULL;
+static uint64_t s[16] = {
+    9899521803441930453ULL, 4037224574094532358ULL,
+    13192621976843192702ULL, 10923948763034344365ULL,
+    3888343346591572214ULL, 7485323648124204777ULL,
+    8981086447562432722ULL, 1561717205308781184ULL,
+    2780386954292984643ULL, 3863312353808779985ULL,
+    12109031751610640964ULL, 11534438648781303991ULL,
+    9340076221226405573ULL, 219462499049377941ULL,
+    16106326203448552520ULL, 7245732521397473901ULL };
+static int p,flag;
+
+uint64_t xorand64(){
+    x^=x>>12; x^=x<<25; x^=x>>27;
+    return x*2685821657736338717ULL;
+}
+
+uint64_t xorand1024(){
+    uint64_t s0=s[p];
+    uint64_t s1=s[p=(p+1)&15];
+    s1^=s1<<31; s1^=s1>>11; s0^=s0>>30;
+    return (s[p]=s0^s1)*1181783497276652981ULL;
+}
+
+void xoseed(uint64_t seed){
+    x=seed;
+    for(int i=0;i<64;i++) xorand64();
+    for(int i=0;i<16;i++) s[i]=xorand64();
+    p=flag=0;
+}
+
+double xonorm(){
+    static double x2;
+    if(flag) {
+        flag=0;
+        return x2;
+    }
+    flag=1;
+    double u1=(xorand1024()+1.0)/18446744073709551616.0;
+    double u2=(xorand1024()+1.0)/18446744073709551616.0;
+    double r=sqrt(-2*log(u1)), v=2*M_PI*u2;
+    x2=r*sin(v);
+    return r*cos(v);
+}

### 2019-10-02 body_acm.tex
Ty!

--- 2019-09-26 Old/body_acm.tex
@@
 bandwidth, which he finds is useful during peak network
-hours. He pays a discounted rate. We note that the additional bandwith may be
-used by another device, or even a 5G-capable mobile device.
+hours. He pays a discounted rate.
 
@@
 free markets, and is encouraged, particularly in wireless and data services. In
-fact, California Legistature has recently passed laws promoting
+fact, California Legislature has recently passed laws promoting
 competition and enforcing fair practice of ISPs \cite{cabill}.
@@
 behavior on market dynamics, and so determines a minimally optimal objective
-representing user valuation globally, and so fufills an additional property of
+representing user valuation globally, and so fulfills an additional property of
 economy over time and space. To the best of our knowledge, this is the first
@@
 order to mutate the strategy space, following dynamic user
-correspendence. As in \cite{lazar}, we take the direct
+correspondence. As in \cite{lazar}, we take the direct
 approach by guessing the right modifier, and context, such that we have the
@@
 We focus on providing users with an incentive framework, and
-so rational users choose a collaborative exchage. 
+so rational users choose a collaborative exchange. 
 The user strategies are organic in that they are natural, or
@@
 direct-revelation mechanism to the desired message space, Then, in the limit of
-the data-model, a user reveals its valuation of a quantitiy of data-resource over the whole range of possible demands.
+the data-model, a user reveals its valuation of a quantity of data-resource over the whole range of possible demands.
 
@@
 optimal strategies for buyers and brokers, and further shows the existence
-of networkwide market equilibria by provisioning a dynamical system. The stability
+of network-wide market equilibria by provisioning a dynamical system. The stability
 of the game may be implied by various equilibria in distributed systems.
@@
 Trusted management systems based on the
-Common Informtion Model (CIM) focus on policy-based management, namely,
+Common Information Model (CIM) focus on policy-based management, namely,
 the ``Policy-Maker" toolkit. 
@@
 In the general context of distributed and decentralized allocation of
-resources, a variety of equilibria exist for heterogeous and homogenous services
+resources, a variety of equilibria exist for heterogeneous and homogeneous services
 with the similar condition of truthfulness. In all cases, the PSP constraints are
@@
 We construct the model for a PSP data auction for mobile users
-particpating in secondary mobile data exchange market.
+participating in secondary mobile data exchange market.
 Let the set of all wireless users to be labeled by
@@
 that a bid belongs to a seller, we use the notation $\s_i^j$. We
-will also empasize the \emph{context} of the bid to indicate the user type.
+will also emphasize the \emph{context} of the bid to indicate the user type.
 To further clarify our analysis, we adopt the notational conventions: a
@@
 a unit price $p^j_i$. 
-Seller $j$'s local auction begins at time $t>0$. The seller takes reponsibility
+Seller $j$'s local auction begins at time $t>0$. The seller takes responsibility
 to send opponent bid profiles $s_{-i}$ to each buyer that joins the auction,
 those buyers where $s_i^j > 0 \in s$, as well its own bid, $\s_i^j = (d_i^j,
-p_i^j)$, offfering quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$, 
+p_i^j)$, offering quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$, 
 with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$. 
 Naturally, in a live auction, if a buyer does
-not submit a bid to a seller, then this implies $s_i^j=\s_i^j = 0$. A buyer that does not submit a bid will not recieve opponent profiles from seller
+not submit a bid to a seller, then this implies $s_i^j=\s_i^j = 0$. A buyer that does not submit a bid will not receive opponent profiles from seller
 $j$. We additionally determine that a user who does not submit a bid is holding
@@
 selfishness}, (3) \emph{social welfare maximization}, and (4)\emph{the winning
-bid is persistent private information}. For the secondary data exchange
+bid is anonymous}. For the secondary data exchange
 market, we determine that the
@@
 \emph{minimize crossover in buyer/ seller pools}.
-Thus, we propose a mechanism that promotes social welfare. 
 Thus our motivation to adapt the PSP auction. The PSP auction given in
 \cite{lazar} is comprised of a set of simple and symmetric rules that closely
-follow market theory, and as it is distributed we can require privacy.
-
-We first address the clear need for privacy in the secondary data exchange market. In \cite{zheng},
-it is assumed that the ISP interferes in 2cm (market) dynamics, and will maximize the
-gap between supply and demand in each transaction, exacting the difference as
-revenue. We notice that this market behavior is suspiciously monopolistic, as a
-single entity, the ISP, holds a global market power. It is further claimed in
-\cite{zheng} that user bids are truthful as they are guaranteed to receive
-their bid. We argue that this model represents an ``unwitting" buyer and an
-equally uninformed seller, as they have no intution of fair market value.
-Thus, in the interest of social good, we aim to provide a method to arrest
-anti-competitive conduct by ISPs. Then, we may trust the ISP. Naturally,
-rational users will only purchase data if the rewards outweigh the risk, it follows that
-the secondary auction should be trusted as well. 
-We argue that as the mechanism is also privacy-preserving, that both the users and the ISP benefit.
-An ISP that is trusted will end up with a loyal customer base, taking profit
-from to one that is revenue maximizing, assuming that competion laws will
-prevent a monopoly.
-
-We define a value to be private if any coalition is incapable of learning any information
-besides what can be inferred from the shared computation and the coalition’s
-inputs. We describe the process as given in \cite{felix}. In general, a distributed private
+follow market theory, and as it is distributed we can require privacy. We describe the process as given in \cite{felix}. In general, a distributed
 computation, where buyer $i$ is part of a coalition comprising auction $j$, is as follows:
@@
 is an independent random value, and $m_1, \cdots, m_n$ the messages $i$ has
-received so far.
-Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$.
-
-The
-private computation process requires that buyers connect with each other, and
-so reveal their identities to the coalition. It was proven in \cite{felix} that full privacy is not possible in a second
-price auction, even if we allow partial relevation and weak coalitions. Yet, we
-claim that our mechanism is trustworthy:
+received so far. Then, all buyers are able to confirm the winning bid $s_{\bar{i}}^*$. 
+It was proven in \cite{felix} that full privacy is not possible in a second price auction, even if we allow partial revelation and weak coalitions. We propose anonymity, in the winning bid only.
 
@@
 In our secondary market, we have that any local auction is anonymous by definition, as a permutation of
-the valuations resutls in a permutation of allocations and prices, equivalently,
+the valuations results in a permutation of allocations and prices, equivalently,
 exchanging the bids of two losing buyers does not change the auction's result.
@@
 which states that any two inputs, the messages seen by coalition $T$
-are indentically distributed.
-
-\subsubsection{The winning bid is persistent private information.}
-We claim that a buyer's trust in a local auction is fufilled when the outcome of
-the auction is guaranteed to be correct, and if the winner's identity is secret.
-For each local auction, we define a coalition of the
-participating buyers. The winning bidder is \emph{privately} chosen by
-distributing the computation of the winner to the local coalition. The
-computation is based on the homomorphicity of secret sharing. We present the
-Lemma in its general form,
+are identically distributed.
+
+\subsubsection{The winning bid is trusted (anonymous) information.}
+We claim that a buyer's trust in a local auction is fulfilled when the outcome of
+the auction is guaranteed to be correct, and if the winner's identity remains private information. For each local auction, we define a coalition to be the
+participating buyers. The winning bidder is chosen by
+distributed computation via homomorphic encryption. We present the Lemma in its general form,
 {
@@
 }
-Thus, it is possible to privately compute,
+Thus, it is possible to anonymously compute,
 \begin{equation}\label{winner}
@@
 The winning buyer then leaves the auction, and so we have that the privacy of
-the winning bid is persistent. We note that it is possible for a winner to
-anonymously rejoin an auction, however this does not alter our result.
-
-\subsubsection{Privacy and independence from the ISP.}
-In our model, privacy is integrated into the mechanism. Our design enforces
-privacy by hiding the reserve price of the sellers. At time
+the winning buyer is persistent. We note that it is possible for a winner to
+anonymously rejoin an auction, however this does not alter our result. At time
 $t=0$, a seller $j$ entering the market will
@@
 platform, and so the initial bid $\s_\kappa^j$, is public knowledge. 
-The auction
-begins at time $t>0$, and at $t=0$, $j$ will
+The auction begins at time $t>0$, and at $t=0$, $j$ will
 initializing its reserve price by executing a single bid iteration.
-Sellers do not update pricing information with the ISP, thereby hiding
-its local market price in the data-exchange market. As the ISP has limited
-information from its ``competitor", it is unable to sabatoge prices derived
-from fair market competition.
-Thus, we claim that our model supports and protects the secondary market, allowing it
-to be in direct competition with its parent ISP, and so contributes to the
-regulation of ISPs \cite{fedbill} and supports a regional free-market economy
-with respect to wireless data \cite{cabill}.
-We will assume that the cost of participating in the secondary market is
-absorbed by the bid fee, which could represent data used in submitting bids, or
-a fee charged per unit of data, or a flat rate charged at the completion of the
-purchase. We do not model ISP revenue, but assume it may be extracted from the
-bid fee at $t=0$.
+
+%We will assume that the cost of participating in the secondary market is
+%absorbed by the bid fee, which could represent data used in submitting bids, or
+%a fee charged per unit of data, or a flat rate charged at the completion of the
+%purchase. We do not model ISP revenue, but assume it may be extracted from the bid fee at $t=0$.
 
@@
 We define an \textbf{opt-out function}, $\g_i$, associated with a buyer $i$ as
-part of its type. Buyer $i$, when determining how to aquire a possible allocation $a$,
-will determine its bid quanities by,
+part of its type. Buyer $i$, when determining how to acquire a possible allocation $a$,
+will determine its bid quantities by,
 \begin{equation}\label{opt-out}
@@
 \end{align}
-and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
+and is interpreted as the aggregate of minimum prices that buyer $i$ bids in
 order to obtain
@@
 analysis
-the total minimum price for the buyer cannot be an aggragation of the
+the total minimum price for the buyer cannot be an aggregation of the
 \emph{individual} prices of the buyers, as it is possible that the reserve prices
@@
 We note that
-the total price cannot be an aggragation of the
+the total price cannot be an aggregation of the
 \emph{individual} bid prices as it is possible that the reserve prices
@@
 single potential function. This is a standard method that is used often, as it
-simplfies the analysis of both strategy and auction design. We will prove the necessary condition of an $\epsilon$-best
+simplifies the analysis of both strategy and auction design. We will prove the necessary condition of an $\epsilon$-best
 reply: a new bid price must differ from the last by at least $\epsilon$.
@@
 
+In any market, a buyer or seller would like to obtain the maximum amount of utility 
+possible while staying within budget. The buyer's utility maximizes the amount of 
+data allocated by the seller, while the seller's utility maximizes the cost of the 
+data sold.
+We may illustrate the resulting product space for the buyer,
+\vspace{-0.3in}
+{
+\begin{center}\begin{figure}[H]\caption{Product / Quotient Space}
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
+  {
+     a & p \\
+     d &  \\};
+  \path[-stealth]
+    (m-1-1) edge node [left] {projection} (m-2-1)
+            edge node [above] {level} (m-1-2)
+    (m-1-2) edge [dashed,-] (m-2-1);
+\end{tikzpicture}
+\end{figure}\end{center}
+}
+\vspace{-0.3in}
+The `level', or price associated with the buyer's bid may be projected onto a line. As we 
+will show, holds when buyers use the same bid price for all nonzero bids. The `projection',
+or the amount of data requested, is a plane, since buyers may bid in more than
+one auction. Clearly, the allocation is the product of the price and the data request.
+There is, however, another logical representation, that the buyer has found an allocation that
+satisfies its demand AND price constraints.
 We define a move to a better market position to be synonymous with a
 strategic bid. \\ 
-\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangable,
+\textbf{Remark:} The terms ``bid" and ``strategy" are often interchangeable,
 from auction design and game theory, respectively.\\
@@
 distributes a buyers' valuation of allocation $a$ across local markets (and thus
-multiple sellers).
-In this way we extend the PSP rules described
+multiple sellers). Thus, the composition map (the codomain of $\theta_i(\g_i)$ is the
+same as the domain of $\g_i(a)$) performs the function of restricting
+the buyer's domain to minimize $d^j p^j - c_i$, i.e., maximize $u_i$.
+Using this intuition, we formally extend the PSP rules described
 in \cite{semret} to design equilibria across subsets of local data-exchange markets.
@@
 
-The elastic valuation of users and homogenous nature of data in the secondary market, 
+The elastic valuation of users and homogeneous nature of data in the secondary market, 
 allows for continuity of constraints imposed by the user strategies. 
@@
 marketplace. 
-Naturally, a buyers' valuation is aggragated over local markets, and the
-sellers' valuation is aggragated over its own auction. We have already introduced the composition $\theta_i
+Naturally, a buyers' valuation is aggregated over local markets, and the
+sellers' valuation is aggregated over its own auction. We have already introduced the composition $\theta_i
 \circ \g_i$ as the valuation of the buyers.
@@
 derivatives
-${\theta_i}$ and ${\theta^j}'$ satisfing the conditions of elastic demand.
+${\theta_i}$ and ${\theta^j}'$ satisfying the conditions of elastic demand.
 }
@@
 \end{equation}
-which holds $\forall \ i,j\in\mcI$. We will assume that buyers and sellers do not overbid, and so omit this
-constraint from our formulation.
-Thus, at equilibrium all users are satisfied, and 
-$D^j = D_i$, although we observe that this result
-does \emph{not} imply that $s_i=\nu^j$.
+which holds $\forall \ i,j\in\mcI$.
+We will assume that buyers and sellers do not overbid, and so omit this constraint from our formulation.
+Thus, at equilibrium all users are satisfied, and $D^j = D_i$, although we observe that this result does \emph{not} imply that $s_i=\nu^j$.
 
@@
 to change their bid strategies asynchronously and serially.
-A users' local strategy space is therefore nondeterministic, and the prefererences of users
+A users' local strategy space is therefore non-deterministic, and the preferences of users
 are subject to change, i.e. binary dependence.
-Then, from \emph{Arrow's Theorem}, we have that no deterministic strategy can
+Then, from Arrow's Theorem, which states that no deterministic strategy can
 provide a mapping of the preferences of users into a market-wide (complete
@@
 Assuming equal bandwidth for all users, we derive a globally optimal strategy suited for
-users with local information in a distrubuted data-sharing model. 
+users with local information in a distributed data-sharing model. 
 In a multi-auction market, each auction a buyer joins has the potential to
@@
 Buyer $i$'s seller pool is determined by minimizing $n$, and is the smallest set of sellers that
-allows for a coordinated bid, and the aggragate bids satisfy its demand, $D_i$.
+allows for a coordinated bid, and the aggregate bids satisfy its demand, $D_i$.
 \begin{align}
@@
 $\varrho$ is interpreted as
-the ``liability" component of $\epsilon$ attempts to regulate network congestion.
+the ``liability" component of $\epsilon$, and attempts to regulate network congestion.
 
@@
 $$
-     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{j},
-$$
-to be the buyer strategy with respect to quantity.
+     \g_i^j \circ a = \g_i^j(a) = \frac{a_i^j}{\vert \mcI_i \vert},
+$$
+to be the buyer strategy with respect to quantity for all sellers $j\in\mcI_i$.
 We propose the following strategy. We include the proof in Appendix $A$.
@@
 }\\
-Each time step, $\s^j$ is updated it is shared with all
+Each time step, $s^j$, the vector of bids held by auction $j$, is updated it is shared with all
 participating buyers. At this point buyers have the opportunity to bid again,
@@
 The seller will notify a buyer who is subject to a market shift by changing its
-bid at the appropate index.
+bid at the appropriate index.
 
@@
 Consider the set $\lambda^j$. For some buyer $i\in\mcI^j$, and then for
-some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$. By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*,
-p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
-Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so
-that $p_l^* < p_*^j$, and
+some seller $k \in \mcI_i$, we have a buyer $l \in \mcI^k$.
+By (\ref{jtoi}), $i,l \in \mcI^k$, and so the reserve price $p_*^k \le \min(p_l^*, p_i^*)$, and $k, j\in \mcI_i\Rightarrow p_i^* \ge \max(p_*^k, p_*^j)$.
+(NEED ALICE AND BOB) Suppose that $l \ni \mcI^j\Leftrightarrow j \ni \mcI_l$, so that $p_l^* < p_*^j$, and
 the valuation of buyer $l$ does not impact auction $j$ and vice versa, i.e. $\theta_l^j = 0$. Since $l\in\mcI^k$, $p_l^* \ge p_*^k\Rightarrow
-p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$. Therefore, we
-have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) hold,
+p_*^k < p_*^j$, and $i\in\mcI^j \Rightarrow p_i^* \ge p_*^j$ (AGAIN ALICE AND BOB). Therefore, we
+have that the ordering implied by (\ref{lambda}) and (\ref{llambda}) holds,
 where,
@@
 \ni\mcI^q \Rightarrow p_*^q >
-p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of
-buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using
-(\ref{iff}).
+p_i^*$, therefore $\theta_i^q = 0$, and the reserve price of auction $q$ does not effect the valuation of buyer $i$, and as $p_*^k < p_*^j \le p_i^* < p_l^*$, we examine $\mcI^j$ using (\ref{iff}).
 Lastly, in the case where $p_i^* > p_l^*$, by the same reasoning, $\theta_l^g =
 0$, for some $g\in\mcI_i$.
-We have that for any $l\in\mcI^k$ such that $l\ni
-\mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
+We have that for any $l\in\mcI^k$ such that $l\ni \mcI^j$, $\theta_l^j =0$, and when $l\in \mcI^j$, then either $\theta_i^q =0$,
 where $q\in\mcI_l$, or $\theta_l^g = 0$, where $g\in\mcI_i$, and as $p_*^k <
@@
 \cap \Lambda^j$, such that $p_l^* > p_i^*$,
-and an indirect influence as, for any $l\in\mcI^k
-\setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
+and an indirect influence as, for any $l\in\mcI^k \setminus \Lambda^j$, where $p_l^* > p_i^*$ results in $i^*\in\mcI^j$ initiating a shift.
+(REALLY NEED A DIAGRAM <- USE (RATIONAL) PYTHAGOREAN THEOREM)
 
@@
 therefore $\theta_i = \theta^j, \ \forall \ i \in \mcI^j$.
-Thus, any bid ouside of
+Thus, any bid outside of
 our construction
@@
 
-The topology of the bids in $\delta$ is key to our result. We immediately have:
-
 \subsubsection{Locally fair division.}
@@
 }
-\proof{Follows directly from the result of Proposision \ref{userunion}.}
+\proof{Follows directly from the result of Proposition \ref{userunion}.}
 
@@
 minimum in each auction, where
-the bid quantity $\g_i^j(a)$ is still fufilled. The pricing rule of the PSP
+the bid quantity $\g_i^j(a)$ is still fulfilled. The pricing rule of the PSP
 auction dictates that a buyer $i$ will pay the cost of excluding other players from
@@
 For any profile $S_i = (D_i, P_i)$, let $a_i \equiv \sum_j a_i^j(s)$ be a
-tentative data
-allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i =
-\g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
+tentative data allocation. For any fixed $S_{-i}$, a better reply for $i$ in any auction is $x_i = \g_i \circ (z_i,y_i)$, where $\forall \ j \in \mcI_i$,
 \begin{align*}
@@
 To achieve incentive compatibility, we find that the opt-out buyer must choose
-this subset so that its overall marginal value is greater than its market price.
-We have so far only made the assumption of truthful bids throughout our analysis. As was shown in Lemma \ref{userunion}, a buyer only
+We have so far only made the assumption of truthful bids throughout our analysis. As was shown in Proposition \ref{userunion}, a buyer only
 has incentive to change its bid as a result of a market shift or partial
@@
 \proposition{(Incentive compatibility across local auctions)}\label{incentive}
-Let $\Lambda$, $\lambda$ be defined as in Lemma (\ref{userunion}), and fix time
+Let $\Lambda$, $\lambda$ be defined as in Proposition (\ref{userunion}), and fix time
 $t>0 \in \tau$, and fix $s^j, \ \forall \ j\in\Lambda$, and for some
@@
 s_{-i})$.
-With reserve prices $p^j >0$, there exists a ``truthful" strategy game embeddeded
+With reserve prices $p^j >0$, there exists a ``truthful" strategy game embedded
 $\in\Delta$. Therefore, a fixed point $\in \Delta$ is a fixed point in
@@
 utility, resulting from a change in strategy, equals the change in
-the local market objective of each seller $j\in\mcI_i$. These local objectives are known as potential functions, and are
-formulated by mapping the incentives of all users in a local auction to a
-single function. The goal of our analysis is to therefore construct a global potential function that encompasses
-all local markets. Then, we may determine a Nash equilibrium by finding a local
-optima of the potential function. Additionally, as the potential function also
-iterates, it may be used in an analysis of convergence. The
+the local market objective of each seller $j\in\mcI_i$.
+These local objectives are known as potential functions, and are formulated by mapping the incentives of all users in a local auction to a single function.
+The goal of our analysis is to therefore construct a global potential function that encompasses all local markets.
+Then, we may determine a Nash equilibrium by finding a local optima of the potential function.
+Additionally, as the potential function also iterates, it may be used in an analysis of convergence.
+The
 convergence of a Nash equilibrium results from the progression of
@@
 From the original proof by \cite{lazar}, we observe that the collection of
-unconstrained truthful bids may be a subset
-of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
+unconstrained truthful bids may be a subset of the collection of $\epsilon$-best replies, i.e. $T_i\subset S_i^\epsilon$.         
 %An essential component of determining the existence of a Nash equilibrium is 
@@
 continuity in the construction of our model.
-Thus, we extend our analyis to be all-inclusive, %The game-theoritical basis of our argument is complemented by an abstract-theoretical analysis.
-a.nd determine the
-existence and ``uniqueness" of a global market objective by rigor of mathematical construction. Thus, we begin with the definition of
-correspondence,
+Thus, we construct an extension %to be all-inclusive, The game-theoretical basis of our argument is complemented by an abstract-theoretical analysis.
+and determine the existence and uniqueness of a global market objective by mathematical correspondence. We begin with the definition of correspondence,
 {
@@
 $S_i$ and $S_{-i}$ are built by repeatedly using the
-cartesian product over bid profiles. The power set 
+Cartesian product over bid profiles. The power set 
 $S_{-i} =\Pi_j \big(\Pi_{k\ne i} S_i^j)$ arises naturally from the
@@
 The best response is a reaction correspondence
-defined by the mixed-strategy game. Denoting  $B_i^\epsilon = T_i\cap
-S_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
+defined by the mixed-strategy game. Denoting  $T_i^\epsilon = T_i\cap
+B_i^\epsilon$, is the set of truthful $\epsilon$-best replies in opponent bid
 profiles $S_{-i}$. \\
 \textbf{Remark:} 
-The ease by which the game is constructed is a consequence of the the cartesian
+The ease by which the game is constructed is a consequence of the the Cartesian
 product on a 2-dimensional message space. \\
-A natural induced topology of this space is the product\footnote{This is known
-as the Correspondence theory of truth}
-topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S_i$.
+A natural induced topology of this space is the product
+topology, e.g. the canonical map $S_i \rightarrow \Pi_{j\in\mcI} S^j$.
 
 Motivated by the symmetric nature of supply and demand, we determine the
-game-theoritical argument is complemented by an abstract-theoretical analysis.
+game-theoretical argument is complemented by an abstract-theoretical analysis.
 In fact, we may even be philosophically motivated, as the truth value of a bid
 is determined only by how it relates to markets, and whether it provides an
-accurate correspondence\footnote{This is known as the Correspondence theory of
-truth}. Using a set-theoretical approach to address the sellers
-bids, we derive our result from the symmetry of supply and demand,
+accurate correspondence.
+We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the strategy space, and is both an equivalence relation and a partial order,
+and therefore is reflexive, transitive, symmetric and anti-symmetric.
+Using a set-theoretical approach to address the sellers bids, we derive our result from the symmetry of supply and demand,
 (\ref{buyerinversedemand}) and (\ref{sellerinversedemand}), Proposition
-\ref{incentive}, (\ref{newprice}), Lemma \ref{userunion} and Lemma
-\ref{buyercoordinate}, and include the following corollary,
+\ref{incentive}, (\ref{newprice}), Proposition \ref{userunion}, Lemma
+\ref{buyercoordinate}, and include the following Corollary.
 {
 \corollary{Data-bid correspondence (seller cooperation)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}).
-For a fixed time $t\in (0,\tau]$, seller bid $s^j$ is consistent with a truthful
-$\epsilon$-best reply.
+Let $\Delta$ be defined as in Proposition (\ref{userunion}) and fix the price $y$ for all sellers $j\in\Lambda$.
+For a fixed time $t\in (0,\tau]$, for any seller $j\in \Lambda$, the bid $s^j$ is consistent with a truthful
+$\epsilon$-best reply, i.e., $s^j \in T^\epsilon$.
 }\\
+% Sorry, didn't check this one, wow need it to work, ref https://math.stackexchange.com/questions/2264090/in-brouwers-theorem-how-does-the-absence-of-fixed-points-imply-certain-retract
 \proof{
-We claim there exists a binary equality relation $i\thicksim j$ that naturally evolves in the
-strategy space. For a seller $j$, let $y=\theta_i'(\g_i^j(a))$ for a buyer $i$.
-We use the the axiom of set equality,
-based on first-order logic with equality, which states that,  
-$\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i)
-\Rightarrow i \thicksim j$, and is a logical consequence of (\ref{jtoi}).
-Then, for any allocation $a$, we may define the relation, $i\thicksim
-j$,
+For a seller-buyer pair, which we will denote $(i,j)$, let $y=\theta_i'(\g_*^j(a))$.
+We use the the axiom of set equality based on first-order logic,
+which states that, $\forall \ i\in\mcI, \ \forall \ j\in\mcI, (i\in \mcI^j \Leftrightarrow j\in\mcI_i) \Rightarrow i \thicksim j$, and follows from (\ref{jtoi}).
+Then, for any allocation $a$, we may define the relation, $i\thicksim j$ as,
+ % dual?
 \begin{equation}\label{eqrel}
-        \big(\bar{D}_i^j(y), {\theta^j}'(\g_i^j(a))\big) =
-        \big(\g_i^j(a),y)\big).
-\end{equation}
-Formally, the axiom states that a set is \emph{uniquely} determined by its
-members. It follows that $\thicksim$ defines equality of bids using a static
-analysis with respect to equilibrium, where all users who are not changing thier
-bids are considered equal.\\
-\textbf{Remark:} Equality is both an equivalence relation and a partial order,
-and therefore is reflexive, transitive, symmetric and antisymmetric. \\
-Now, we may define the mapping $s \mapsto [s]$,
+        d_i^*(y) = \g_*^j(a) \qquad \text{AND} \qquad f^j \circ \g_i^*(a) = y,
+\end{equation}
+ where $f$ is defined as in (\ref{sellerinversedemand}).
+\vspace{-0.3in}
+{
+\begin{center}\begin{figure}[H]\caption{Buyer-seller pair}
+{
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
+  {
+     F_t(x) & F(x) \\
+     A_t & A \\};
+  \path[-stealth]
+    (m-1-1) edge node [left] {$\mathcal{B}_X$} (m-2-1)
+            edge [double] node [below] {$\mathcal{B}_t$} (m-1-2)
+    (m-2-1.east|-m-2-2) edge node [below] {$\mathcal{B}_T$}
+            node [above] {$\exists$} (m-2-2)
+    (m-1-2) edge node [right] {$\mathcal{B}_T$} (m-2-2)
+            edge [dashed,-] (m-2-1);
+\end{tikzpicture}
+}
+\end{figure}\end{center}
+}
+\vspace{-0.3in}
+We have that $f_i=f^j$, from (\ref{uservaluation}), i.e., for any $z\in D_i$, $x\in D^j$, 
+\begin{equation}\label{zerodiff}
+    \big[\theta_i(x) -\theta_i(x-\xi)\big] \quad \text{AND} \quad \big[\theta^j(z) - \theta^j(z-\zeta)\big].
+\end{equation}
+So, 
+$$
+    \big(\theta_i(x)\theta^j(z) - \theta_i(\xi)\theta^j(\zeta)\big)^2 = 4\theta_i(x)\theta^j(z).
+$$
+Since from (\ref{zerodiff}), $\theta_i\theta^j = $
+Formally, the set of users in an auction is uniquely determined by its members. We note that $\thicksim$ defines equality of bids using a \emph{static}
+analysis, meaning that sellers have fixed market prices; all users who are not changing their bids are considered equal.
+Define the mapping $s \mapsto t$ such that, for any $z$,
 \begin{equation}\label{indeqrel}
-         1_\vartheta \equiv \theta_i'(z) - {\theta^j}'(z) > \epsilon,
-\end{equation}o
-noting that equality in the bid quantity is implicity satisfied and $z =
-\bar{D}_i^j(y)\ge 0$. We have that $\vartheta$ is a price relation for a
-buyer-seller pair. Let $S = \Pi_{j\in\mcI} \big(
-\Pi_{i\in\mcI} S_i^j \big)$. The indicator function is the canonical mapping,
-$1_\vartheta : S \rightarrow \lbrace{0,1\rbrace}$. Then, as the product
-topology is preserved, the set of all indicator
-functions on $S$ naturally forms the power set $\mathcal{P}(S) = S_i\times
-S_{-i}$. Additionally, the set of all equivalence classes defines the quotient space, $S /
-\thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
-$P = \big\lbrace [s] : s\in S\big\rbrace$ of $S$. } Therefore each seller
-$j\in\mcI$ is equivalent buyer(s) $i\in\mcI$. That is, buyers and
-sellers with an equality relation (\ref{eqrel}) belong to the same local
-auction equilbrium. Therefore, sellers' bids represent $\epsilon$-best replies
-in the strategy space. $\qed$ (DONE? REALLY?)
-
+         \theta_i'(z) - {\theta^j}'(z) \le \epsilon/2.
+\end{equation}
+and so,
+\begin{equation}\label{indeqrel}
+         1_\lambda : \theta_i'(z) \mapsto {\theta^j}'(z),
+\end{equation}
+Noting that the constraint $z\ge 0$ in the bid is implicitly satisfied and so $z =
+\bar{D}_i^j(y)\ge 0$.\\
+Let $S = \Pi_{j\in\mcI} \big(\Pi_{i\in\mcI} S_i^j \big)$. Now, given any set of buyers $\mcI_i \in \Lambda$ where we have an allocation from some $j \in \lambda_i$,
+% Given a subset B of a set A, the injection f:B->A defined by f(b)=b for all b in B is called the inclusion map.
+$\gamma(S_i, S_{-i}) : \lambda \rightarrow \Lambda \in \lbrace{0,1\rbrace}$, and so the indicator function is a canonical mapping as well as an inclusion map.
+As the product topology of the strategy space is preserved (WHY?), and as the set of all indicator functions on $S$ forms the power set $\mathcal{P}(S) = S_i\times S_{-i}$, we have that $\Delta \subset \mathcal{P}(S)$ is the result of the mapping $\gamma$ (ACK).
+$$
+    \lambda \rightarrow^\gamma \lambda (FINISH, MAPS TO THEMSELVES, i.e. in the same queue)
+$$
+Now, the set of all equivalence classes (DEFINE % need https://math.stackexchange.com/questions/2264090/in-brouwers-theorem-how-does-the-absence-of-fixed-points-imply-certain-retract
+) on $S$ defines a quotient space (WHY?), $S / \thicksim \ \equiv \big\lbrace [k] : k\in\mcI \big\rbrace$, forming a partition
+$[s] = \big\lbrace s^j\in S : s^j  \thicksim s_i \big\rbrace$ of $S$. $\qed$} \\
+Therefore each seller
+$j\in\mcI$ is equivalent to some buyer $i\in\mcI$.
+That is, buyer $i$'s utility constraint is satisfied in auction $j$ if and only if seller $j$'s utility constraint is also satisfied.
+Sellers with equality relation (\ref{eqrel}) belong to the same local auction equilibrium as the buyers.
+Each seller's bid price represents an $\epsilon$-best reply with respect to its (local) strategy space.
+Now, in order to find a fixed point in the mixed strategy space, we must have a continuous mapping between posets, i.e.
+$\Lambda^j \iff \lambda_i, \forall \ i, j \in \Delta$.
+We have the following Proposition.
 {
 \proposition{(Continuity of $\epsilon$-best reply on $\Delta$)}
-Let $\Delta$ be defined as in Lemma (\ref{userunion}). For any buyer
+Let $\Delta$ be defined as in Proposition (\ref{userunion}). For any buyer
 $i\in\lambda^j$, the collection of bids $B_i$ is continuous in $S_{-i}$
-}\\
+}
 \proof{
@@
 We observe that $\g_i \circ B_i^\epsilon$ is simply $B_i^\epsilon$ restricted to seller pool
-$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . Thus,
-we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
+$\mcI_i$, i.e. $\g_i \circ B_i^\epsilon \equiv B_i^\epsilon\vert_{\mcI_i}$ . % Why did I use size here? ... don't remember
+Thus, we have $\g_i \circ T_i = ([0,D^k]_{k\in\mcI^j}\times [0,\g_i \circ
 \overline{P}]^{\vert \mcI^j\vert})$
@@
 subset of a compact set is compact and the resulting product topology gives
-Tychonoff's theorem. every product of a
-compact space is compact, we have $\g_i \circ B_i^\epsilon$
+Tychonoff's theorem, i.e. every product of a compact space is compact, we have $\g_i \circ B_i^\epsilon$
 is compact subset of $B_i^\epsilon$.
@@
 definition of $\Delta$ and the product, 
+% DID I USE 'g' ANYWHERE ELSE?
 \begin{align*}
@@
 
-As a result of user behavior, and subsequent strategies, we determine that the
-data-exchange market behaves in a predictable way. However,
+As a result of user behavior, and subsequent strategies, we determine that the data-exchange market behaves in a predictable way. However,
 each auction may be played on the same or on a different scale in
-valuation, time and quantity, and so the rate at which market fluctuations occur is
-impossible to predict. 
-We show that our bidding strategy results in (at least one), static Nash
-equilibrium, where the sellers reserve prices are fixed. This result is
-logically derived, and as our final result, we address the audience and note
-that it is a mere step in the right direction.
-{
-\lemma{(Local Static Nash Equilibrium)} 
-Let $\Delta$ be defined as in Lemma (\ref{userunion}), and suppose that auction
-$j\in\Delta$ is at equilibrium. Fix all $s_i^j$. 
-Using the rules of the data auction mechanism, along with type-based strategic
-moves, $j$ converges to an $\epsilon$-Nash equilibrium. 
+valuation, time and quantity, and so the rate at which market fluctuations occur is impossible to predict. 
+We show that our bidding strategy results in (at least one), Nash equilibrium, where the sellers reserve prices are fixed. 
+{
+\lemma{(Local Nash Equilibrium)} 
+Let $\Delta$ be defined as in Proposition (\ref{userunion}), and suppose that auction $j\in\Delta$ is not in a transient state, e.g.
+$t = \tau^j$.
+Fix all $s_i^k, k\ne j$.
+Using the rules of the data auction mechanism, along with type-based strategic moves, $j$ converges to an $\epsilon$-Nash equilibrium.
 The proof follows closely that of \cite{semret}.
-}\\
+}
 \proof{
@@
 $t=[t_i^j] \in \lambda^j \times \Lambda^j$ is continuous in $s$ on
-$T_k=\Pi_{k\in\Lambda^j} T_k^j$. Now, $t$
-represents a continuous mapping of $[0,\sum_{k\in\Lambda^j} D^k]_{i\in\lambda^j}$ onto itself,
-and we may use Brouwer's fixed point theorem, as in \cite{semret},
+$T_k=\Pi_{k\in\lambda^j} T_k^j$. Now, $t$
+represents a continuous mapping of $[0,\sum_{k\in\lambda^j} D^k]_{i\in\Lambda^j}$ onto itself and we may use Brouwer's fixed point theorem, as in \cite{semret}, which states that the continuous mapping of a convex compact set into itself has at least one fixed point.
+Therefore, $\exists \ z^* = \sigma^*(z) \in [0,D_i]_{i\in\Lambda^j}$.
+So, given that $s^* = (z^*, \theta'(z^*))$, we have that $s^* = t(s^*)\in T$.
+%We have that $\forall s \in T$, $\forall z >0$, we have $z>0 = \sum_{i\in \Lambda^j} D_i(p_{i}^j/2,s_{-i})$, so using ($\ref{dataprice}$), $ \sum_{i\in\lambda^j}P_{i^*}^j(z,s_{-i}) \ge p_*^j$ and truthful bid $t_i = (v_i, \theta'(z)) \forall i \in \lambda^j$
+$\qed$
+}\\
+
+We have proven that buyers will submit bids according to their marginal valuations. We have that all bids represent $\epsilon$-best replies, and, as was proven in
+\cite{lazar}.
+The sellers' positive reserve price implies that bids are truthful.
+Finally, by properties determined by the construction of a mixed strategy symmetric game with a 2-dimensional message space, we may now restrict our analysis to the set of continuous, truthful, $\epsilon$-best replies, $T^\epsilon$.
+In mathematics, the notion of the continuity of functions is not immediately extensible to multivalued mappings; we show the correspondences between the two sets $\lambda$ and $\Lambda$.
+Specifically, we show that the joint set $\Delta^epsilon$ is hemicontinuous.
+Thus, we must show that the correspondence is continuous, and so gives the set $\Delta^{\epsilon} \equiv \Delta\vert_{T^\epsilon}$ the necessary functional property, leading to point-wise convergence.
+In this setting, convergence of a sequence of $\epsilon$-best replies is defined by the confluence, meaning that if buyer $i$ and seller $j$ both satisfy their utility functions, and arrive at an allocation $a$, then the $a$ is independent of the specific sequence of $\epsilon$-best replies used to complete the auction.\\
+%in an analogy to the property of the same name for functions?
+The data-sharing market consists of inter-dependent sets of these multi-auction games around possible fixed points.
+Clearly, the union of all possible sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$.
+We claim that the shared buyers between the different subsets $\Delta$ form a sufficiently connected set that the hierarchy described in Proposition \ref{userunion} holds.
+Then, there can only be a finite set of fixed points, where the sellers' reserve price is an equilibrium price in the global market.
+We first address the analytical approach, and derive the projective properties of $\Delta$ as a finite-dimensional linear space.
+We have that the reserve price of the sellers, and the bid price of the buyers is constant within an interval of length 2$\epsilon$.
+We proceed to define the boundary, using a closed graph approach to define our correspondence.\\
+In order to form our cover, we must have:
+\begin{enumerate}
+    \item\label{co1} A convergent sequence of points in the domain, mapping to a sequence of points in the range.
+    \item\label{co2} If there exists another convergent sequence in the domain, then the image of the limiting point must contain the limit of that sequence in the range.
+\end{enumerate}                                                                                                                                                                               The result is sufficient to infer that a sequential solution exists as a result of the correspondence relationship.
+The $\epsilon$-best reply of the seller or the buyer may be determined by backwards induction.
+Once a single fixed point has been found, then we may apply the rules of the mechanism, continuing backward until the best action for every pair has been determined.
+Effectively, we are determining the fixed points as functors on the larger function space, working backwards from an equilibrium.
+The correspondence between $i$ and $j$ forms the (ensemble) set $\lambda \sim \Lambda$. We note that due to the binary relation, the set of all possible $\epsilon$-best replies,
+$$
+    \Delta^\epsilon = \lbrace (i, j) \in \lambda \times \Lambda : j \in \lambda_i\rbrace,
+$$
+is well-posed by Hadamard [1923], definition (4.3) and Corollary (4.4) (PROVE?). %isomorphic?
+We define the set of functors as the cover of the space $\Delta$ as the graph $\Gamma(\Delta^{\epsilon})$; a directed, fully connected graph $\forall \ i \in \lambda^j$ and $\forall i\in\Lambda^k$, for some $k\in\mcI$.
+Therefore, we are able to define the upper hemicontinuity of the space $\Delta^{\epsilon}$ as the closure of its graph, which we will denote $\Gamma$, and we have the following Corollary,
+{
+\corollary{Hemicontinuity of $\Delta^\epsilon$}\\
+For any $j\in\Lambda$, define an ordered triple, $(\Lambda^j, \lambda^j, R)$, where $R$ is the relation from $\Lambda^j$ to $\lambda^j$, as in Proposition (3.7), and define,
+$$
+    \Gamma(\Delta^\epsilon) = \big\lbrace (z^*, \theta_i'(z^*)\ge (z^*, \theta_*^j'(z^*) \in \Lambda^j \times \lambda^j : i\in \Delta \big\rbrace.
+$$
+Then for any $j$ such that $t=\tau^j$, i.e. the market is not in a transition state, then the utility function $u^j$ is satisfied. 
 }
-
-We have proven that buyers will submit bids according to their marginal
-valuations. Now, in the interest of completeness (BAD SENTENCE), 
-We have that all bids represent $\epsilon$-best replies, and, as was proven in
-\cite{lazar}, the sellers' positive reserve price implies that bids are
-truthful. Finally, by properties determined by the construction of a mixed strategy
-symmetric game with a 2-dimensional message space, we may now restrict our
-analysis to the set of continuous, truthful, $\epsilon$-best replies, $B^\epsilon$.
-
-{
-\corollary{Hemicontinuity of $\Delta$}
-}
-
-The data-sharing market consists of inter-dependent sets of these
-multi-auction games around possible fixed points.  Clearly, the union of all possible
-sets $\bigcup_{j\in\mcI} \Delta^j$ covers $\mcI$. We claim that the shared buyers
-between the different subsets $\Delta$ form a sufficiently connected set that
-the heirarchy described in Proposition \ref{userunion} holds. Then,
-there can only be a single primary fixed point, where the sellers' reserve
-price is an equilibrium price in the global market. 
-We first address the analytical approach, and demonstrate properties of
-$\Delta$ as a finite-dimensional linear topological space. We have that the
-reserve price of the sellers, and the bid price of the buyers is constant
-within an interval of length 2$\epsilon$. We have that 
-(HERE) We have the following
-Corollary, (MIGHT NEED TO REDEFINE.. NOT CLEAR IS A SEQUENCE, SHOULD BE
-SEQUENCE OF PRICES INSTEAD OF USERS?) 
+\proof{We have that for any $i$, $\forall \ y_i \ne \theta'(z*)$
+$$
+    u_*^j \ge u^j(z^*,y_i) - \epsilon/2 - \varrho,
+$$
+and so we have that $[s] \mapsto t \in T^{\epsilon}$ is defined by $\Gamma: \Lambda \mapsto \lambda$ $\forall \ i \in \lambda$.
+This is the coassociative, cocommunicative property, where for some pair $(i,j) \in \Delta, u_*^j = u_i^* = u_i^j$.
+The amount of data offered by a seller $j$ at price $p^*$ is met by a buyer $i$ at price $p_*$; we have that there must be some buyer-seller pair $(i,j)$ at some $t\in\tau_i\times \tau^j$ such that $p^* \ge p_*^j \ge p_i^* \ge p_*^$, and $u_* \simeq u^*$.
+Our cover is formed by the duality of \ref{buyervaluation} and \ref{sellervaluation}, and so we have hemicontinuity by the relation $R \equiv \theta_i \propto \theta^j$ for any $(i,j)\in\Delta^\epsilon$, and we assume the existence of a non-transient, global state, which may or may not be the termination of all auctions.\\ % which several non-degenerate maps may be chosen from to satisfy all constraints
+\textbf{Remark:} We note that $\tau_i$ does not need to equal $\tau^j$ in order for equivalence to hold, as at some point there will be at least one pair, $(i,j)$, which satisfy the constraints.
+In the simplest case, there are N buyers and N sellers, and if a stable matching exists, then (\ref{co1}) $\iff$ (\ref{co2}).}\\
+
+We have shown that our bidding strategy results in at least one \emph{local} Nash equilibrium.
+Now, we must prove that each bidding process converges to a unique auction, i.e., no buyer is assigned data that was not bid on, and no seller receives any false bids, which we have by assumption.
+We first show the existence of a \emph{static} Nash equilibrium, where the sellers reserve prices are fixed.
 {
 \corollary{(Primary fixed point)}
-Let the set of shared buyers be denoted as,
-$\underline{\lambda} = \bigcap_{j\in\mcI} \lambda^j$, and the set of all
-sellers as, $\overline{\Lambda} = \bigcup_{j\in\mcI}\Lambda^j$. If
-$\overline{\Lambda}$ is not a partition, i.e. $\nexists \ j,k
-\in\overline{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
-for a fixed time $t$,
-$\exists \ j \in\overline{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
-k\ne j\in\overline{\Lambda}$. 
+Let $\Lambda, \lambda$ be defined as in \ref{userunion}. If
+${\Lambda}$ is not a partition, i.e. $\nexists \ j,k
+\in{\Lambda}$ such that $\Lambda^j \cap \Lambda^k = \emptyset$, then,
+for fixed $t$,
+$\exists \ j \in{\Lambda}$ such that $p_*^j \ge p_*^k, \ \forall \
+k\ne j\in{\Lambda}$. 
 }\\
@@
 We assume a finite number of users, with continuous valuation functions bounded both
-above and below. From the assumption that $\overline{\Lambda}$ is not a
+above and below. From the assumption that ${\Lambda}$ is not a
 partition, we have that the limits exist with respect to bid price $p_i^j$, 
 $$
-    \limsup\limits_{j\to I} \overline{\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
+    \limsup\limits_{j\to I} {\Lambda} =  \bigcap_{j\ge 1}\bigcup_{k\ge j} \Lambda^k,
 $$
@@
 $$
-    \liminf\limits_{i\to I} \overline{\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
+    \liminf\limits_{i\to I} {\lambda} = \bigcup_{i\ge 1}\bigcap{k\ge i}
 \lambda^k,
@@
 
-We show that our bidding strategy is
-part of a Nash equilibrium. We first show the existence of a \emph{static} Nash
-equilibrium, where the sellers reserve prices are fixed.
-{
-\lemma{(Static Nash Equilibrium)} 
-Let $\Delta$ be defined as in Lemma (\ref{userunion}), and
+{
+\lemma{(Nash Equilibrium)} 
+Let $\Delta$ be defined as in Proposition (\ref{userunion}), and
 let the duration of auction $j$ be $\tau \in (0,\infty)$, and fix the
@@
 (DEFINITION.. USE?)
-In the General Symmetric Game, p is an evolutionarily stable mixed strategy if
+In the General Symmetric Game, p is an evolutionary stable mixed strategy if
 there is a (small) positive number y such that when any other mixed strategy q
@@
 choice. Consider Bob, a mobile wireless network user. Marketing firms have already realized that an incentive
-for Bob to interact with their ads is to provide them at no cost to his mobile
-    data. Inevitebly, ISPs will find a way to supply the growing demand. We
-    have demonstrated the trend towards a Monopoly of knowledge\footnote{John
-    Watson (2006), suggests that monopolies of knowledge gradually suppress new ways
-    of thinking.}, and suggest
-    that trust, and policy be decentralized, for the greater good.
-
+for Bob to interact with their ads is to provide them at no cost to his mobile data. 
 Mathematically, we have shown that if truthfulness holds locally for both buyers and sellers, i.e.
@@
 (\ref{poolbnd}), or the upper bound of the sellers' reserve price
-$p^\kappa$ is reached. Thus, as in each case we have that $i$ is able to satisfy thier demand,
+$p^\kappa$ is reached. Thus, as in each case we have that $i$ is able to satisfy their demand,
 and we determine that the opt-out strategy is optimal.
@@
 With this caveat, and Proposition \ref{buyerstrategy}, we have that the
-aggragate demand of subset $\mcI^j$ is satisfied by seller $j$.
+aggregate demand of subset $\mcI^j$ is satisfied by seller $j$.
 Although the buyers' valuation $\theta_i$ is not known to the seller, we will assume
@@
 $j$ and buyer $i$ is well-posed, the reserve price (\ref{newprice}) is
-justified, and we have a local equlibirium at time $\tau$.
+justified, and we have a local equilibrium at time $\tau$.
 $\qed$}
@@
 Now, the buyer valuation function (\ref{buyervaluation}), guarantees
-that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposision
+that $\forall \ j\in\mcI_i$, $y_i^j \ge p_{i^*}^j$, where $p_{i^*}^j$ is the reserve price of seller $j$, defined in Proposition
 \ref{sellerstrategy}, and is by definition the minimum price for a buyer bid to
@@
 $\qed$}
-%Finally, we note that $z_i^j$ does not increase the aggragate demand of the buyer.
+%Finally, we note that $z_i^j$ does not increase the aggregate demand of the buyer.
 

### 2019-10-02 main.tex
Ty!

@@
-%\documentclass[master,tocprelim]{Latex/Classes/PhDthesisPSnPDF}
-%\documentclass[letterpaper,12pt]{cls/thesis}
-%\documentclass[master,final,tocprelim]{unrthesis}
-\documentclass[master,tocprelim,12pt]{unrthesis}
-%\documentclass[master,tocprelim,12pt]{thesis}
+%\documentclass[journal,comsoc]{IEEEtran}
+\documentclass[sigconf, anonymous]{acmart}
+%\documentclass[12pt]{article}
 
+\usepackage{algorithmicx}
+\usepackage{algorithm,algpseudocode}
+\usepackage[english]{babel}
 \usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{graphicx}
-%\usepackage{float}
-%\usepackage{wrapfig}
-%\usepackage{showkeys}
-\usepackage{algorithm2e}
-\usepackage{plain}
-\usepackage{pdfpages}
 
-\usepackage{listings}
+\usepackage{tikz}
+\usetikzlibrary{matrix}
+\usetikzlibrary{arrows,shapes}
 
-\graphicspath{{./graphics/}}
+\newcommand{\vs}{\varsigma}
+\newcommand{\mcL}{\mathcal{L}}
+\newcommand{\mcI}{\mathcal{I}}
+\newcommand{\g}{\sigma}
+\newcommand{\s}{\nu}
+\DeclareMathOperator*{\argmax}{arg\,max}
+\DeclareMathOperator*{\argmin}{arg\,min}
 
-\lstset{ %
-language=C,               
-basicstyle=\footnotesize,
-showspaces=false,               
-showstringspaces=false,         
-numbers=left,                   % where to put the line-numbers
-numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
-stepnumber=1,                   % the step between two line-numbers. If it is 1 each line will be numbered
-numbersep=10pt,     
-showtabs=false,                 
-columns=fullflexible,
-frame=single,          
-tabsize=2,          
-captionpos=b,       
-extendedchars=true,
-frame=single,
-breaklines=true,       
-breakatwhitespace=false, 
-escapeinside={\%*}{*)}       
-}
-\def\verbatimtabsize{4\relax}
-\def\listingoffset{1em}
-\def\listinglabel#1{\llap{\tiny\it\the#1}\hskip\listingoffset\relax}
-\def\mylisting#1{{\fontsize{10}{11}\selectfont \listinginput[1]{1}{#1}}}
-\def\myoutput#1{{\fontsize{9}{9.2}\selectfont\verbatimtabinput{#1}}}
+\iffalse
 
-\newtheorem{proposition}{Proposition}[chapter]
-\newtheorem{theorem}{Theorem}[chapter]
-\newtheorem{lemma}{Lemma}[chapter]
-\newtheorem{corollary}{Corollary}[chapter]
+\newtheorem{proposition}{Proposition}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}{Lemma}[section]
+\newtheorem{corollary}{Corollary}[section]
+\newtheorem{sublemma}{Lemma}[lemma]
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[chapter]
-\newtheorem{property}{Property}[chapter]
+\newtheorem{definition}{Definition}[section]
 
-\title{Dynamical Systems: Chaotic Attractors and \\{~}
-    Synchronization using Time-Averaged Partial \\{~}\\
-\vskip-12pt
-Observations of the Phase Space}
-\author{
-Jordan Fleming Blocher 
-}
+\headsep25pt\headheight20pt
+\setcounter{secnumdepth}{4}
+\pagestyle{fancyplain}
+\rhead{\fancyplain{}{\small\bfseries Blocher, Jordan}}
+\cfoot{\ \hfill\tiny\sl Draft printed on \today}
+\setlength{\extrarowheight}{2.5pt} % defines the extra space in tables
 
-%\date{\today}
+\fi
+ %\iffalse
+%---------------ACM CCS---------------------%
+\fancyhf{} % Remove fancy page headers 
+\fancyhead[C]{}
+%\fancyhead[C]{Anonymous submission \#837 to ACM CCS 2018} % TODO: replace 9999 with your paper number
+\fancyfoot[C]{\thepage}
 
-\newcommand{\cF}{{\mathcal F}}
-\newcommand{\cO}{{\mathcal O}}
-\newcommand{\cA}{{\mathcal A}}
-\newcommand{\cB}{{\mathcal B}}
-\newcommand{\cV}{{\mathcal V}}
-%\newcommand{\R}{\textbf{R}}
-\newcommand{\R}{{\bf R}}
-\newcommand{\B}{{\cal B}}
-\newcommand{\C}{\textbf{C}}
-\newcommand{\del}{\delta}
-\newcommand{\cL}{{\mathcal L}}
-\newcommand{\mydelta}{{h}}
-\newcommand{\yourdelta}{{\Delta}}
-\def\words#1{\quad\hbox{#1}\quad}
-\def\wwords#1{\qquad\hbox{#1}\qquad}
-\renewcommand{\emptyset}{\O}
-\numberwithin{equation}{chapter}
+\setcopyright{none} % No copyright notice required for submissions
+\acmConference[]
+%\acmConference[Anonymous Submission to ACM CCS 2018]{ACM Conference on Computer
+%and Communications Security}{Due 8 May 2018}{Dallas, Texas}
+\acmYear{2019}
+
+\settopmatter{printacmref=false, printccs=true, printfolios=true} % We want page numbers on submissions
+%-------------------------------------------%
+%\fi
+
 \begin{document}
-
-\maketitle
-
-\includepdf{ms-committee-page.pdf}
+%\begin{multicols}{2}
+\title{Progressive Second Price Auction Mechanism for Data-Exchange Models}
 
@@
 
-We study the synchronization of chaotic systems when the coupling
-between them contains both time averages and stochastic noise.
-Our model dynamics are given by the Lorenz equations
-which are a system of three ordinary differential
-equations in the variables $X$, $Y$ and $Z$.
-Our theoretical results show that coupling two copies of the
-Lorenz equations using a feedback control which consists
-of time averages of the $X$ variable
-leads to exact synchronization provided the
-time-averaging window is known and sufficiently small.
-In the presence of noise the convergence is to within a
-factor of the variance of the noise.
-The novelty of our investigation hinges on the
-analysis of the time averages.
-We also consider the case when the time-averaging window
-is not known and show that it is possible to tune the
-feedback control to recover the size of the
-time-averaging window.
-Further numerical computations
-show that synchronization is more accurate and occurs
-under much less stringent conditions than our theory requires.
+%Verizon and At\&T, two major Internet service providers (ISPs), are offering
+%shared data plans, where multiple users may purchase and share a single pool of
+%data. 
+We propose a distributed, privacy-preserving auction-based approach to
+allocation in a secondary market for wireless data exchange.
+The secondary market is modeled as a fully connected, pure ``point of sale"
+market, with initial public platform provided by its parent wireless internet service
+provider (ISP). 
+The progressive second price (PSP) auction rules provide our underlying auction
+structure, allowing for a single degree of freedom, the reserve
+price. We suggest that data exchange markets allow for greater flexibility in
+mechanism design.
+We propose new, natural degrees of freedom, and derive modifiers
+to represent the deformation of the strategy space.
 
+Wireless users are modeled as a fixed type with dynamic incentives. Using a game
+theoretic analysis, we derive strategy profiles for wireless users
+based on their typed response to market dynamics, resulting in self-contained, self-balancing pricing system. 
+We examine mutations in the strategy space resulting from the new modifiers, and
+prove that the desired PSP properties hold. 
+Convergence is determined by set theory; we prove that the symmetry of our
+strategy space provides built-in conditions for convergence and stability, finally arriving at a network Nash equilibrium.
+
+Trust and privacy issues in secondary markets have yet to be addressed.
+As rational users will not publicly reveal valuations, out users form coalitions to establish trust with local auctioneers.
+In a centrally moderated secondary market, an unregulated,
+rational ISP will prevent its secondary market from acting as a competitor.
+Competition is desired as it provides incentive for the ISP to protect
+and care for its end users.
+The distributed nature of PSP extends individual privacy to the secondary market,
+allowing for it to compete with its parent ISP. 
 \end{abstract}
 
-\begin{acknowledgements}
-I would like to acknowledge my thesis advisor, Eric Olson.
-I would like to thank my committee members:
-Bruce Blackadar, Paul Hurtado and Fred Harris.
-I would also like to thank my friends, family and UNR.
-This research is supported in part by NSF grant DMS-1418928.
-\end{acknowledgements}
+\begin{CCSXML}
+<ccs2012>
+<concept>
+<concept_id>10002978.10002986.10002987</concept_id>
+<concept_desc>Security and privacy~Trust frameworks</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10002978.10003006.10003013</concept_id>
+<concept_desc>Security and privacy~Distributed systems security</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10002978.10003014.10003017</concept_id>
+<concept_desc>Security and privacy~Mobile and wireless security</concept_desc>
+<concept_significance>100</concept_significance>
+</concept>
+</ccs2012>
+\end{CCSXML}
 
-\contentspage
-\tablelistpage
-\figurelistpage
+%\ccsdesc[500]{Security and privacy~Trust frameworks}
+%\ccsdesc[300]{Security and privacy~Distributed systems security}
+%\ccsdesc[100]{Security and privacy~Mobile and wireless security}
 
-\begin{manuscript}
-\chapter{Introduction}\label{Intro}
+\keywords{game theory, second price auctions, mobile share, software-defined networks} 
+\maketitle
 
-We produce synchronization results when coupling is applied on 
-two chaotic systems when the coupling
-between them contains both time averages and stochastic noise.
-Our model dynamics are given by the Lorenz equations
-which are a system of three ordinary differential
-equations in the variables $X$, $Y$ and $Z$.
-We build off of investigations of the Lorenz model in 
-\cite{Hayden11, Stuart14}, where 
-space and continuous time observations \cite{Olson14} by use of a control
-theory perspective similar to that which arises from the derivation of
-continuous time limits of discrete time filters \cite{ Bloemker14}. 
-We seek to determine relationships between the underlying
-dynamical system and the observation operator
-to ensure that synchronization can be obtained.
-For a coupled pair of chaotic dynamical systems,
-where the driven system's initialization is not known precisely, the extent 
-of the use of observed data over time is a topic of interest in 
-meteorology, weather forecasting and any attempt to predict the 
-future using incomplete information about the current state of a
-dynamical model.
+\input{body_acm}
 
-In this thesis, we extend the approach of \cite{Olson14}
-to use time-averaged continuous-in-time partial observations of 
-the phase space. We examine
-both the noise-free case and the case where the observations include
-stochastic noise. We are able to show that the use of time-averaged
-observations results in synchronization.
-The techniques investigated here are applicable to different
-dissipative dynamical systems, and
-provide many points of continued study, which
-are detailed in a chapter dedicated to future work.
-
-The outline of the thesis is as follows. In Chapter 1 we introduce the concept
-of synchronization on the global attractor. We also provide a
-detailed description of our model problem, a simplified model of atmospheric
-convection, the Lorenz system, and present an analytical bound on the
-trajectories which is used throughout the thesis. We also introduce the coupling
-method that is is the focus of the thesis and introduce the notation that will
-be used to describe our experiments.
-In Chapter 2 we present a proof of the
-existence and uniqueness of our solution. In addition, we present a generalized
-Gronwall integration proof that will be used throughout the thesis and is
-applicable to the convergence of our model. 
-In chapter three we study the convergence of the approximating solution in a noise-free 
-setting, ending with an investigation into the sensitivity of the time-averaging
-window. Chapter 4 presents an analysis when the observations contain stochastic noise. 
-Chapters 5 and 6 present our numerical methods and conclusions. Finally, Chapter
-7 provides points of future work.
-
-\section{Synchronization}\label{Synchro}
-
-Synchronization means that the difference between two solution
-trajectories converge to zero as time tends to infinity.  The sensitivity
-to initial conditions of dynamical systems means that two identical
-systems with even a slight perturbation of initial conditions quickly
-become uncorrelated even though they are bounded and converging to the
-same attractor.  
-On the theoretical side, we would like to determine 
-when coupling between two identical copies of a dynamical system
-leads to synchronization and to study the effects that
-realistic conditions, such as a moving time-averages and 
-noisy observations, have on the synchronization.
-On the computational
-side, we would like to simulate the same things and test the
-sharpness of our theory.
-
-Consider a dynamical system given by the ordinary differential equations
-\begin{equation}\label{freeODE}
-    \frac{dU}{dt} = \cF(U) 
-\end{equation}
-where $U(0) = U_0\in{\bf R}^n$ and ${\cal F}\colon{\bf R}^n\to{\bf R}^n$.
-We use partial information about $U$ to drive a second solution $u$
-as follows:
-\begin{equation}\label{noerra}
-    \frac{du}{dt} = \cF(u) + \mu\big(\widetilde{\cal R}(U) - {\cal R}(u)\big)
-\end{equation}
-with arbitrary initial condition $u(0) = u_0$.
-Here $\widetilde{\cal R}(U)$ denotes an interpolation of
-partial observations of $U$ back into the phase space ${\bf R}^n$
-that may contain noise as well moving time averages, and
-${\cal R}(u)$ denotes a feedback control used to nudge $u$
-towards $U$ over time.
-Note that the relaxation parameter $\mu > 0$ 
-determines the rate
-at which $u$ is nudged towards $U$ as it evolves forward in time 
-and represents a tunable parameter in the system.
-
-Note, we assume the forcing function ${\cal F}$ is known 
-exactly and leads to a well posed dynamical system that governs
-the freely evolving solution.
-More realistically, ${\cal F}$ might only be known up to an
-approximation $\widetilde {\cal F}$.  Ideas for work along these 
-lines is discussed in Section \ref{whatissigma} in the
-chapter on future work.  
-We assume the dynamics given by ${\cal F}$ are dissipative.
-However, our analysis relies not just on dissipativity, but
-on a squeezing property with respect to the observable
-part of the phase space.
-
-If $\widetilde{\cal R}={\cal R}$ and $u_0=U_0$, then
-$\mu\big((\widetilde{\cal R}(U_0) - {\cal R}(u_0)\big)= 0$.
-It follows that both $u$ and $U$ evolve according to the same
-dynamics, which in turn implies $u(t)=U(t)$ for all $t\ge 0$.
-When $u_0\ne U_0$ it may still happen
-%provided $\widetilde{\cal R}={\cal R}$ 
-that $\|u(t)-U(t)\|\to 0$ as $t\to\infty$.
-When this happens we say that $u$ synchronizes with $U$.
-Note, however, when $\widetilde{\cal R}\ne{\cal R}$ it
-may happen that
-$\mu(\big(\widetilde{\cal R}(U_0) - {\cal R}(u_0)\big)\ne 0$
-even if $U_0=u_0$.
-It immediately follows that $U(t)\ne u(t)$ for $t>0$.
-In this case, we look for bounds on $\|U-u\|$ that depend
-on the quality of the approximation $\widetilde{\cal R}\approx{\cal R}$.
-
-If the observations $\widetilde{\cal R}$ have been 
-contaminated using a moving time average with a known window size,
-then ${\cal R}$ can also include an identical moving time average
-so that $\widetilde{\cal R}={\cal R}$.  However, if the size of
-the averaging window is unknown, then we can only guess its size.
-In this case ${\cal R}$ is only an approximation of $\widetilde{\cal R}$.
-Similarly, if the observations $\widetilde{\cal R}$ contain a 
-unknown noise term, this this noise can not be included in the 
-feedback term and again ${\cal R}$ will differ from 
-$\widetilde{\cal R}$, this time by the noise.
-The main result of this thesis are theoretical and numerical
-bounds on the expected value of $\|U-u\|^2$ in the case 
-when $\widetilde{\cal R}$
-contains noisy observations that have been averaged with
-respect to an unknown window size.
-
-\section{Global Attractors}
-
-For general continuous time dynamical systems the number of degrees of freedom
-is often associated with the number of first order ordinary differential
-equations (ODEs) in the model.  If
-$$ 
-\displaystyle\sum_{i=1}^n{\partial \cF_i \over \partial U_i }< 0,
-$$
-then the system is said to be
-\emph{dissipative} system.
-This indicates that volumes transported by the dynamics of
-the system are contracting.
-In this case, there exists a compact set to which all bounded 
-sets converge as they are transported by the flow.
-In particular, all trajectories eventually converge that set.
-Moreover, if this set is invariant, that is, if every point on
-the attractor is the image under the flow of the
-dynamics over a fixed period of time of another point on the attractor, 
-then the set is unique and called the global attractor.
-Since the attractor is bounded and invariant, then any trajectory 
-on the attractor is bounded backwards in time.
-This leads to another characterization of the attractor
-as the set of all solutions which are bounded backwards
-in time.  
-Note that the set of fixed points such that 
-$\big\{\, x : {\cal F}(x)=0 \,\big\}$ are included in the attractor,
-as is the unstable manifold of the fixed point.
-This observation can be used to find lower bounds on the
-size of the attractor.
-
-Due to the presence of an attractor, the sum of the Lyapunov
-exponents is expected to be negative; an indication that the 
-system is dissipative. 
-The Lyapunov exponents control the exponential growth or
-contraction of volume elements in phase space \cite{Doering95a}.
-They 
-quantify the exponential divergence of infinitesimally close 
-state-space trajectories 
-and estimate the amount of chaos in a system. 
-A positive exponent is consistent with diagnosing chaos and represents
-local instability in a particular direction.
-
-The Lyapunov spectrum is represented geometrically as a small $n$-dimensional 
-sphere of initial conditions.
-%, where $n$ is the degrees of freedom in the system.
-In a chaotic attractor, the sphere evolves into an ellipsoid whose
-principal axes expand (or contract) at rates given by the Lyapunov
-exponents.
-Calculating the largest Lyapunov exponent can yield an estimate 
-of the ``level of chaos" using the slope of the divergence
-as was calculated by Rosenstein and Collins \cite{Rosenstein93}.
-This determines how two trajectories with nearby initial conditions 
-diverge over time.
-In fact, we expect that two randomly chosen initial 
-conditions in arbitrary phase space will diverge exponentially at 
-the rate given by the largest Lyapunov exponent. 
-In the context of the synchronization studies in this thesis, 
-it is this tendency for the
-trajectories to diverge that needs to be overcome by the
-feedback controller represented by $\mu\big(\tilde{\cal R}(U)-{\cal R}(u)\big)$
-in equation~(\ref{noerra}).
-
-\section{The Lorenz '63 Model}
-
-The Lorenz '63 Model is a system of three ordinary differential equations that
-represent a simplified model of atmospheric convection \cite{Lorenz63}. 
-The model is dissipative with a quadratic energy-conserving nonlinearity.
-This system of three coupled non-linear ordinary differential
-equations satisfies equation~(\ref{freeODE}) where
-$U=(X,Y,Z)$ and
-\begin{align}\label{freeLorenz}
-    \cF(U)=\begin{bmatrix}\sigma(Y-X)\\
-    -\sigma X-Y-XZ\\ -bZ+XY-b(r+\sigma)\end{bmatrix}.
-\end{align}
-Here $\sigma$ is
-the Prandtl number, $r$ is the Rayleigh number, 
-and $b$ is a geometric factor. 
-Note that we have employed a coordinate system where 
-the center is shifted to the point $(0, 0, 0)$.
-We will use the standard parameter values 
-$\sigma=10$, $b=8/3$ and $r=28$
-in our study.  
-At these values, the system is known to 
-have a chaotic global attractor $\cA$, Tucker \cite{Tucker1999}.
-
-Note that
-$$
-\displaystyle\sum_{i=1}^3{\partial \cF_i \over \partial U_i }
-	=-\sigma-1-b
-$$	
-which shows the system is dissipative.
-Moreover, linearization about the
-fixed point $$(\sqrt{b(r-1)},\sqrt{b(r-1)},-\sigma-1)$$
-gives the matrix
-$$
-\begin{bmatrix}
-    -\sigma & \sigma & 0\\
-    1 & -1 & -\sqrt{b(r-1)}\\
-    \sqrt{b(r-1)} & \sqrt{b(r-1)} & -b
-\end{bmatrix}.
-$$
-which has eigenvalues
-\begin{align*}
-	\lambda_1&\approx -13.85457791\\
-\quad
-	\lambda_2&\approx 0.093955624 - 10.19450522i\\
-\quad
-	\lambda_3&\approx 0.093955624 + 10.19450522i.
-\end{align*}
-Since the real parts of two of these eigenvalues is positive,
-nearby solutions will
-spiral away onto a two-dimensional unstable manifold. 
-We conclude that the unstable manifold at the fixed point
-is two dimensional.
-Therefore, the global attractor contains a two dimensional
-set and is itself at least two dimensional.
-
-The Lorenz attractor has been shown to be a global 
-attractor contained in a
-volume bounded by a sphere, a cylinder, the volume between two parabolic sheets,
-an ellipsoid and a cone \cite{Doering95a}, see
-also \cite{Doering95b}.
-A smaller sphere which also contains the attractor was 
-discovered while attempting to improve estimates used in
-the proof of Proposition~\ref{UKNLTAprop}.
-While we did not make use of that bound in this thesis,
-it has been included as Appendix~A because it is of independent
-interest and may be useful in future work, see Section~\ref{fractalbound}.
-Throughout this thesis we assume that
-the free running solution lies on the global attractor.
-Thus, $U$ reflects the long term behavior of the
-Lorenz systems and obeys the {\it a priori\/} bounds discussed
-above.
-Of those bounds we make exclusive use of the spherical bound given 
-as Theorem~\ref{Ktheorem} stated below.
-
-The following proof
-is essentially the same as the one given in \cite{Doering95a};
-however, it is simpler because
-we have already translated the $Z$ variable in the formulation 
-of the Lorenz system.
-
-\begin{theorem}
-\label{Ktheorem} 
-Let $U$ be a trajectory with 
-$U_0\in \mathcal{A}$ and assume that $b\ge 2$ and $\sigma$ $r>0$. 
-Then $|U(t)|^2 \leq K$ for all $t\in\textbf{R}$ where
-\begin{equation}\label{Keqn}
-    K = \frac{b^2(r+\sigma)^2}{4(b-1)}
-\approx 1540.27.
-\end{equation}
-\end{theorem}
-\begin{proof}
-We define a Lyapunov function as
-\begin{equation}\label{boundsEqn}
-    K = \{(X,Y,Z) \ \vert \ X^2 + Y^2 + Z^2 \le R^2\}
-\end{equation}
-and consider the evolution of the sphere as determined by the Lorenz equations:
-$$
-{1\over 2} {dK\over dt} = \sigma X^2 + Y^2 + bZ^2 -b(r+\sigma)Z.\\
-$$
-$K$ is a decreasing function in time, and so trajectories will move closer to
-the point $(0,0,0)$. Solving the constrained maximization problem 
-$$
-K = \max\{K(X,Y,Z)\ \vert \ \sigma X^2 + Y^2 + bZ^2 -b(r+\sigma)Z \ge 0\}
-$$
-by using the Lagrange multiplier method with
-$$
-    f(X,Y,Z,\lambda) = X^2 + Y^2 + Z^2 + \lambda(\sigma X^2 + Y^2 + bZ^2
-    +b(r+\sigma)Z)
-$$
-we may bound the radius of a sphere into which all solutions flow as $t\to
-\infty$ where $K_{max} = R^2$.
-\end{proof}
-
-\section{The Coupling Method}
-
-%We are interested in a dynamical system formed by two near identical
-%subsystems:  one subsystem evolves freely and
-%drives the evolution of the other. 
-In \cite{Olson14} Azouani, Olson, Titi 
-introduced equation~(\ref{noerra}) as a simple
-data-assimilation method that constructs an
-approximating solution $u$ from partial observations
-of an exact solution $U$ over time.
-A numerical study of this algorithm was performed by
-Gesho \cite{GeshoThesis}, see also Gesho, Olson and Titi \cite{Gesho16}.
-The effects of noisy measurements were treated by
-Bessaih, Olson and Titi in \cite{Bessaih15}, which led
-to a stochastic version of equation~(\ref{noerra}) that
-included a $Q$-Brownian motion on the right hand side
-to represent measurement errors.
-In those works the model problem was the two-dimensional
-incompressible Navier--Stokes equations and ${\cal R}(U)$
-represented nodal 
-measurements of an Eulerian velocity field as might be taken 
-by an array of idealized weathervane anemometers that can
-measure the exact velocity at a discrete set of points in 
-space at any point in time.
-
-Synchronization of coupled copies of the Lorenz system
-was first observed by Pecora and Carroll in \cite{Pecora90}.
-The Lorenz system was considered in the context of data assimilation 
-by Hayden \cite{HaydenThesis} and by Hayden, Olson and Titi 
-\cite{Hayden11} and to understand the effects noise
-in the observational measurements by Law, Shukla and Stuart 
-in \cite{Stuart14}.
-This thesis explores the case in which the
-available information about the true state of $U$ is 
-further contaminated
-by a moving time average with an averaging window 
-of size $\delta$.
-This type of moving average is physically relevant to 
-real-world scientific instrumentation that approximates,
-for example, the measurement of velocity at any instant
-in time by
-an average velocity taken over a very small time interval.
-
-Another physically relevant property of most instrumentation is 
-that measurements are produced at a sequence of discrete moments 
-in time rather than continuously in time.
-Sequences of discrete-in-time observations for the Lorenz system
-have been considered by Hayden \cite{HaydenThesis},
-by Hayden, Olson and Titi in \cite{Hayden11} and 
-by Cecilia, Jolly, Foias and Titi in \cite{Cecilia}.
-In order to focus on time averages we do not treat
-discrete-in-time data in the present thesis.
-
-We now describe the observational measurements of $U$
-denoted by $\widetilde{\cal R}(U)$.
-Coupling through either the $X$ or $Y$ variable can lead to 
-synchronization in the Lorenz system, see \cite{HaydenThesis}.
-In this thesis the coupling is on $X$ because the analysis is 
-easier and more closely 
-represents the analysis used when treating the synchronization
-of dynamics given by partial differential equations.
-Let 
-$\widetilde {\cal R}\colon \R^3\to \R^3$ in equation~(\ref{noerra}) be given 
-by one of
-$$
-R=\cL\circ \cO,\quad
-\widetilde R=\cL\circ \widetilde \cO
-,\quad
-R_{\hat\delta}=\cL\circ \cO_{\hat\delta}
-\words{or}
-\widetilde R_{\hat\delta}=\cL\circ \widetilde \cO_{\hat\delta},
-$$ 
-where $\cO$, $\widetilde\cO$, $\cO_{\hat\delta}$ and 
-$\widetilde\cO_{\hat\delta}$
-represent 
-observations with and without noise/time-averages
-and
-$\cL$
-represents an interpolation of the observations 
-back into the phase space.
-Note that $\hat\delta$ is the size of the averaging window
-present in the observational measurements of $U$.
-Specifically, we take $\cO\colon \R^3 \rightarrow \R$
-and $\cL\colon\R\to\R^3$ 
-to be given by 
-\begin{equation}\label{Lobserve}
-\cO(X,Y,Z)=X\wwords{and} \cL(X)=(X,0,0)
-\end{equation}
-throughout our study.
-Thus, $\cL(U)$ represents exact observations 
-of $U$ obtained instantaneously at the time $t$ 
-and $\widetilde\cO(U)$ a noisy version of $\cO(U)$ 
-which, following \cite{Bessaih15}, satisfies
-\begin{equation}\label{tildecO}
-\widetilde\cO(U)dt
-	=\cO(U)dt+\epsilon dW_t
-\end{equation}
-where $W_t$ is a standard one-dimensional Brownian motion
-with underlying probability space $\Omega$.
-The corresponding noise-free and noisy moving time averages
-are then given 
-by 
-\begin{equation}\label{cOdelta}\cO_{\hat\delta}(U)
-	={1\over\hat\delta}\int_{t-\hat\delta}^t \cO(U(s))\,ds
-\end{equation}
-and
-\begin{equation}\label{tildecOdelta}
-\widetilde\cO_{\hat\delta}(U)
-	={1\over\hat\delta}\int_{t-\hat\delta}^t \widetilde\cO(U(s))\,ds.
-\end{equation}
-%Note that $\delta>0$ above represents the size of the
-%averaging window.
-For notational convenience we define 
-$\cO_0=\cO$ and $R_0=R$ so that $\hat\delta=0$ indicates measurements 
-for which the averaging is zero.
-
-As the noise is unknown, the possible choices for ${\cal R}$
-used in the feedback control ${\cal R}(u)$ can not include
-noise.
-This ensures the evolution of the driven solution is given
-only in terms of things which are observable.
-It may also happen that the size of the averaging present in 
-the observations is also unknown. 
-In this case, we let $\delta$ represent the time 
-averaging in the feedback control.
-Thus,
-the possible choices for ${\cal R}$ are given given by 
-one of $R$ or $R_{\delta}$ where $\delta$ is an approximation
-of $\hat\delta$.
-
-When the observations
-%are given by $\cO_\delta$ they
-are noise-free and $\delta=\hat\delta$ we obtain conditions 
-under which $\|U-u\|\to 0$ as $t\to\infty$.
-When the observations 
-%are given by $\widetilde \cO_\delta$ they
-are noisy
-$u$ becomes a stochastic process.
-In particular, $u$ solves a stochastic differential equation 
-when $\hat\delta=0$ and a 
-random differential equation when $\hat\delta>0$.
-In this case we obtain
-bounds of the form
-\begin{equation}\label{B1bound}
-	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big]< B_1.
-\end{equation}
-Chebyshev's inequality applied to the bound (\ref{B1bound}) implies 
-there exists $T>0$ such that
-\begin{equation}\label{cheby}
-	{\bf P}\big\{ \|U-u\|^2\le B_2\varepsilon^2\big\} \ge 1-B_1/B_2
-\end{equation}
-for every $B_2>B_1$ and $t>T$.
-Thus, the error has a 90 
-percent chance of being bounded by $B_2=10B_1$ at any fixed
-point in time.
-
-We also consider the general case when 
-$\delta\ne\hat\delta$, that is, when the time averaging present 
-in the observations is unknown.  
-In this case, the equation for $u$ becomes
-\begin{equation}\label{NLTAUnkSoln}
-    \frac{du}{dt} = \cF(u) -
-    \mu \big(\widetilde R_{\hat\delta}(U)
-    - {R}_{\delta}
-    (u)\big),
-\end{equation}
-In the absence of noise $\varepsilon=0$ and we 
-obtain as Proposition \ref{UKNLTAprop}
-conditions and a bound
-$B_3$ such that
-\begin{equation}\label{lessdeltadelta}
-	\limsup_{t\to\infty} \|U-u\|^2 < B_3 (\hat\delta-\delta)^2.
-\end{equation}
-This analysis suggests it may is possible to recover 
-$\hat\delta$ using successively better guesses.
-When there is noise we obtain our final
-result Proposition~\ref{UKNTAprop} which provides
-bounds $B_4$ and $B_5$ such that
-\begin{equation}\label{noisydeltadelta}
-	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] 
-		< B_4 (\hat\delta-\delta)^2 + B_5\varepsilon^2.
-\end{equation}
-In this case, $\delta$ can be tuned to 
-match $\hat\delta$ only up to the point 
-where the second term starts to dominate the bound.
-
-\chapter{Preliminaries}
-
-In this chapter we prove a local existence theorem 
-which will be used later to show our data assimilation 
-equations are globally well posed as well as an
-integro-Gronwall inequality which will be used to
-estimate the accuracy of the synchronization.
-
-We now turn our attention to proving existence and
-uniqueness of solutions for the integro-differential equations
-which define the driven system as a result of the time averages
-present in the observational measurements.
-Let
-$$
-	f\colon [0,\infty)\times\R^n\to\R^n \
-	\text{ and }\
- g\colon [0,\infty)\times\R^n\to\R^n$$
-be continuous in the first variable and
-uniformly Lipschitz in the second.
-Consider the integro-differential equation
-\begin{equation}\label{intdiff}
-     V'=\begin{cases}
-{\smallskip}
-f\big(t, V\big) & \text { for } t<\delta\\\\
-        f\big(t, V\big)
-    +\displaystyle {1\over\delta}\int_{t-\delta}^t g\big(s, V(s)\big)\,ds &
-    \text{ for } t>\delta\end{cases}
-\end{equation}
-where $ V\in\R^n$ is a continuous function.
-Note that $ V'$ may not be defined at time $t=\delta$, 
-unless
-$$
-	\int_0^\delta g(s,y(s))\,ds\ne 0.
-$$
-As this is not in general true, then we consider as solutions
-to equations (\ref{intdiff}) continuous functions which are piecewise
-differentiable.
-This equation, similar to the
-Volterra equations studied by Levin in \cite{Levin64},
-is locally well posed as shown by 
-\begin{lemma}\label{localexist}
-Suppose $ V\colon [0,T]\to \R^n$ satisfies equations (\ref{intdiff}),
-then there exists $\Delta t>0$ such that $ V$ can be uniquely extended to a function
-on $[0,T+\Delta t]$ which also satisfies equations (\ref{intdiff}).
-\end{lemma}
-
-\begin{proof}
-If $T<\delta$, standard existence and uniqueness results
-for ordinary differential equations show there exists $\Delta t>0$ 
-such that the solution $ V$ can be extended to the interval $[0,T+\Delta t)$.
-If $T\ge\delta$, the result follows from a straight-forward 
-fixed point argument which we include here for completeness.
-
-Define 
-$$D=\max\big\{\, \| V(t)\| : t\in[0,T]\,\big\}+1$$
-and
-$$M_f=\max\big\{\, \|f(t,v)\| : t\in[0,T+1]\hbox{ and }\|v\|\le D\,\big\}.$$
-Let $\gamma_f$ be the Lipschitz constant such that
-$$
-	\big\|f(t,v_1)-f(t,v_2)\big\|\le \gamma_f \|v_1-v_2\|
-\words{for} \|v_1\|,\|v_2\|\le D.
-$$
-Corresponding to the function $g$
-similarly define $M_g$ and $\gamma_g$.
-Let
-\begin{equation}\label{sizeofh}
-	\Delta t=\min\bigg(1,{1\over M_f+M_g},{1\over 2(\gamma_f+\gamma_g)}\bigg).
-\end{equation}
-and define
-\begin{align}
-    {\cal X}=\Bigg\{
-        v\in {\cal C}([0,T+\Delta t],\R^n):
-        \begin{matrix}v(t)=V(t)\hbox{ for }t\le T,\hbox{ and }\hfill\\
-        \|v(t)\| \le D\hbox{ for }t\in[T,T+\Delta t]\end{matrix}\,\Bigg\}.
-\end{align}
-Consider the mapping ${\cal J}\colon{\cal X}\to {\cal C}([0,T+\Delta t],\R^n)$ 
-given when $t\le T$ by ${\cal J}(v)(t)= V(t)$ and when $t> T$ by
-$$
-	{\cal J}(v)(t)= V(T)+\int_T^t f\big(\tau,v(\tau)\big)\,d\tau
-		+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau g(s,v(s))\,ds\,d\tau.
-$$
-We claim that ${\cal J}\colon{\cal X}\to{\cal X}$ and
-that ${\cal J}$ is a contraction.
-Estimate
-\begin{align*}
-	\|{\cal J}(v)(t)\|
-	&
-	\le \| V(T)\|+
-	\int_T^t \|f\big(\tau,v(\tau)\big)\|\,d\tau\\
-	&\phantom{{}\le \| V(T)\|}
-		+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau 
-			\|g(s,v(s))\|\,ds\,d\tau\\
-	&\le (D-1) + \Delta t M_f +\Delta t M_g \le D.
-        \end{align*}
-Therefore, ${\cal J}\colon{\cal X}\to{\cal X}$.  Moreover,
-\begin{align*}
-	\|{\cal J}(v_1)(t)&-{\cal J}(v_2)(t)\|
-		\le
-	\int_T^t \|f\big(\tau,v_1(\tau)\big)-f(\tau,v_2(\tau)\|\,d\tau\\
-		&
-\phantom{{}-{\cal J}(v_2)(t)\|}
-+ \int_T^t{1\over\delta}\int_{\tau-\delta}^\tau 
-			\|g(s,v_1(s))-g(s,v_2(s))\|\,ds\,d\tau\\
-	&\le \Delta t(\gamma_f+\gamma_g) \max \{\,\|v_1(s)-v_2(s)\|: s\in [T,T+\Delta t]\,\}\\
-	&\le (1/2) \max \{\,\|v_1(s)-v_2(s)\|: s\in [T,T+\Delta t]\,\}
-        \end{align*}
-shows that ${\cal J}$ is a contraction.
-Now, by the contraction mapping theorem, there is a unique fixed point
-$v\in {\cal X}$ such that ${\cal J}(v)=v$.  
-Since this fixed point clearly satisfies equations (\ref{intdiff}),
-the lemma is proved.
-\end{proof}
-
-We now prove the following integro-differential Gronwall inequality.
-
-\begin{lemma}\label{intGronwallerror}
-Suppose
-\begin{equation}\label{idineq}
-    {d\cV(t)\over dt} +  \cV(t) 
-	\leq A \mydelta \int_{t-\mydelta}^t  \cV(s) \ ds + B
-\end{equation}
-where $A>0$, $B>0$ and
-%$$ 0<\mydelta < \min \Big\{ 1, \sqrt{1-e^{-1}\over 2A}\Big\}.$$
-$$ 0<\mydelta < \min\bigg\{\sqrt{1-e^{-1}\over 2A},1\bigg\}.$$
-Then $\limsup_{t\to\infty} \cV(t)< eB.$
-\end{lemma}
-\begin{proof}
-By hypothesis 
-%Since %$$\delta< \sqrt{1-e^{-1}\over 2A}$$
-there exists $\gamma\in (0,1)$ such that
-$$\mydelta< \sqrt{e^{-\gamma}-e^{-1}\over 2A}.$$
-Therefore
-\begin{equation}\label{est4R}
-	e^{-(1-\gamma)}+2A\mydelta^2e^{\gamma\mydelta}
-	< e^{-(1-\gamma)}+2A {e^{-\gamma}-e^{-1}\over 2A}e^{\gamma}
-	=1
-\end{equation}
-and
-\begin{equation}\label{est4B}
-	2e^{-1}+2A\mydelta^2(1-e^{-1})-e^{-2}
-		<e^{-1}+e^{-\gamma}(1-e^{-1}) = \beta<1.
-\end{equation}
-Moreover,
-\begin{equation}\label{betaest}
-	\beta+(e^{-1}-e^{-2})(\beta^{-1}-1)\le 1.
-\end{equation}
-Inequality (\ref{betaest}) follows by
-taking $\phi(\beta)= \beta+(e^{-1}-e^{-2})(\beta^{-1}-1)$ and
-differentiating to get
-$\phi'(\beta)=1-(e^{-1}-e^{-2})\beta^{-2}$.
-Therefore $\phi$ is increasing when
-$\beta>\sqrt{e^{-1}-e^{-2}}$.
-Since $\gamma\in(0,1)$ implies 
-$\beta\ge 2e^{-1}-e^{-2}>\sqrt{e^{-1}-e^{-2}}$ then
-$\phi(\beta)\nearrow 1$ as $\beta\nearrow 1$.
-
-Let $m$ be the smallest integer such that $1+h\le m$
-and $\B=e\beta B$.
-Since $ \cV$ is continuous there is $R$ such that
-$ \cV(s)\le Re^{-\gamma s}+\B$ for all $s\in [0,m]$.
-For induction, suppose 
-$ \cV(s)\le Re^{-\gamma s}+\B$ for all $s\in [0,n]$.
-Claim 
-$ \cV(s)<2(Re^{-\gamma s}+\B)$ for all $s\in [n,n+1]$.
-If not, then there is some $t\in(n,n+1]$ such that
-$ \cV(t)\ge 2(Re^{-\gamma t}+\B)$ and
-$ \cV(s)\le 2(Re^{-\gamma s}+\B)$ for $s\in [n,t]$.
-Multiplying inequality (\ref{idineq}) by $e^t$
-and integrating from $t-1$ to $t$ we obtain
-\begin{plain}$$\eqalign{
-	 \cV(t)
-		&\le\cV(t-1)e^{-1}+e^{-t}A\mydelta\int_{t-1}^t
-		e^{\rho}\int_{\rho-\mydelta}^\rho\cV(s)\,ds\,d\rho
-		+(1-e^{-1}) B.
-}$$\end{plain}%
-Since
-\begin{plain}$$\eqalign{
-		\int_{t-1}^t
-		e^{\rho}\int_{\rho-\mydelta}^\rho\cV(s)\,ds\,d\rho
-	&\le
-		\int_{t-1}^t
-		e^{\rho}\int_{\rho-\mydelta}^\rho  2(Re^{-\gamma s} +\B) \,ds\,d\rho\cr
-	&\le
-		2\mydelta \int_{t-1}^t
-		e^{\rho} (Re^{-\gamma (\rho-\mydelta)} +\B) \,d\rho\cr
-	&\le
-		2 R\mydelta e^{\gamma\mydelta} \int_{t-1}^t
-		e^{(1-\gamma) \rho} \,d\rho
-		+2 \B\mydelta\int_{t-1}^t e^{\rho}\,d\rho\cr
-	&\le
-		2 R\mydelta e^{\gamma\mydelta} 
-		e^{(1-\gamma) t} 
-		+2 \B\mydelta (e^t-e^{t-1}),\cr
-}$$\end{plain}%
-then using estimates (\ref{est4R}) and (\ref{betaest}) we obtain
-\begin{plain}
-\begin{equation}\label{Rineqerr}
-\eqalign{
-	 \cV(t)
-		&\le (Re^{-\gamma(t-1)}+\B)e^{-1}\cr
-		&\qquad+ A\mydelta \big(2 R\mydelta e^{\gamma\mydelta}
-        e^{-\gamma t} +2\B\mydelta (1-e^{-1})\big)
-		+(1-e^{-1})B\cr
-		&= Re^{-\gamma t} \big(e^{-(1-\gamma)}
-			+2A\mydelta^2 e^{\gamma\mydelta}\big)\cr
-		&\qquad+\B\big(
-			2 e^{-1}+2Ah^2(1-e^{-1})-e^{-2}\big)\cr
-			&\qquad+\B\big((e^{-1}-e^{-2})(\beta^{-1}-1)
-			\big)\cr
-		&\le Re^{-\gamma t} + \B\big(
-			\beta
-			+(e^{-1}-e^{-2})(\beta^{-1}-1)
-			\big).\cr
-%		&\qquad+\B\big(
-%			\beta
-%			+(e^{-1}-e^{-2})(\beta^{-1}-1)
-%			\big)\cr
-%		&\qquad+\B\big(
-%			2e^{-1}+2A\mydelta^2(1-e^{-1})-e^{-2}
-%			+(e^{-1}-e^{-2})(\beta^{-1}-1)
-%			\big)\cr
-		&\le R e^{-\gamma t} + \B.
-}\end{equation}\end{plain}%
-which contradicts $\cV(t)\ge 2(Re^{-\gamma t} +\B)$.
-Therefore $\cV(s)\le 2(Re^{-\gamma s}+\B)$ for $s\in[n,n+1]$ and
-it immediately follows from equation~(\ref{Rineqerr}) and induction
-that $\cV(t)\le Re^{-\gamma t}+\B$ for $t>0$.
-Consequently $\limsup_{t\to\infty}\cV(t)\le \B<eB$.
-\end{proof}
-
-We remark that the proof of Lemma~\ref{intGronwallerror} is still valid
-when $B=0$ except for the strict inequality in the last step.  
-Consequently we also obtain
-\begin{corollary}
-\label{intGronwallerror0}
-Suppose the hypothesis of Lemma~\ref{intGronwallerror}
-are satisfied except that $B=0$.
-Then $\cV(t)\to 0$ as $t\to\infty$.
-\end{corollary}
-
-Combining Lemma~\ref{localexist} with Lemma~\ref{intGronwallerror} 
-leads to a proof of
-global existence of the driven solution $u$ for all time
-when the $h$ appearing in Lemma~\ref{intGronwallerror} is small enough.
-The main issue is showing that the size of the $\Delta t$ from
-Lemma~\ref{localexist} is uniformly bounded below at any point in time.
-Since the size of $\Delta t$ given in (\ref{sizeofh}) is constrained 
-by $M_f$ and $M_g$, it is enough to show that these two
-constants don't grow without bound over time.
-
-We assume, 
-as is the case for the Lorenz system 
-focused on in this thesis, 
-that
-$$
-	L_f=\sup\{ f(t,0) : t>0 \}
-\wwords{and}
-	L_g=\sup\{ g(t,0) : t>0 \}
-$$
-are finite.  In particular, when there is no noise, the
-$f$ and $g$ which correspond to the Lorenz system are time
-independent.  When there is noise we obtain 
-probabilistic bounds on $f$ and $g$ which are uniform in
-time because the variance of the noise process is stationary.
-Since
-$$
-	\| f(t,v)\| \le \|f(t,v)-f(t,0)\|+\|f(t,0)\|
-		\le \gamma_f \|v\|+ L_f
-$$
-then
-$$
-	M_f\le \gamma_f D + L_f
-\wwords{and similarly}
-	M_g\le \gamma_g D + L_g.
-$$
-Consequently, the only requirement to prevent $\Delta t$ from shrinking
-is that $\|u\|$ stays below $D$.
-
-Now, if $h$ is small enough
-then taking ${\cal V}=\|U-u\|^2$ in Lemma~\ref{intGronwallerror}
-(or in the case of noise taking
-${\cal V}={\bf E}\big[\|U-u\|^2\big]$) implies that
-$$
-	\|U-u\|^2\le eB.
-$$
-Therefore taking $D=\sqrt{eB}+ \sqrt{K}$ yields
-$$
-	\|u\|\le \|U-u\|+\|U\|\le D
-\wwords{for} t\in [0,T+\delta t].
-$$
-We conclude that $\|u\|$ remains uniformly bounded 
-and therefore exists globally in time.
-In the case where there is noise, the same result follows almost
-everywhere after an application of the Borel-Cantelli lemma.
-
-\chapter{Coupling without Noise}
-
-When there is no noise in the coupling we 
-show that the difference between the freely evolving system
-and the driven system converges to zero over time.
-
-Section~\ref{NLICoupling} treats the case 
-%when ${\cal R}=R$, that is, 
-when the coupling involves the $X$ variable measured 
-exactly at each moment in time.
-We include a complete analysis of this simple case as a frame
-of reference.
-Section~\ref{NLTACoupling} treats the case 
-%when ${\cal R}=R_\delta$, that is, 
-when the coupling involves a
-simple moving time-average of the $X$ variable.
-Provided the averaging window is small enough we again show
-that exact synchronization occurs.
-Section~\ref{UNTCoupling} treats the case when the size of the averaging
-window is known only approximately.  In this case we obtain
-an upper bound on the accuracy of the synchronization that
-depends on $|\hat\delta-\delta|$ where $\hat\delta$ is the exact, but
-unknown, size of the averaging window use to form the 
-moving average of $X$ and $\delta$ is an the size of the
-averaging window used on $x$ in the feedback control.
-
-\section{Noiseless Instantaneous-in-Time Coupling}\label{NLICoupling}
-
-This chapter treats the simplest case of synchronization for
-the Lorenz system in which there are no time averages present
-in the observational measurements.  Thus, $\hat\delta=0$, $\delta=0$
-and $\varepsilon=0$ in equation~(\ref{NLTAUnkSoln}).
-
-Substituting ${\cal R}={\cal L}\circ{\cal O}$ into equation~(\ref{noerra})
-where ${\cal L}$ and ${\cal O}$ are given by equations (\ref{Lobserve})
-yields the driven system
-\begin{align}
-\label{drivenX}
-    \dot{x} &= -\sigma(y-x)+\mu(X-x)\\
-\label{drivenY}
-    \dot{y} &= -\sigma x-y-xz\\
-\label{drivenZ}
-    \dot{z} &= -bz+xy-b(r+\sigma)
-\end{align}
-We now show for $\mu$ sufficiently large
-that
-the approximating solution $(x,y,z)$
-converges to the
-free-running solution  $(X,Y,Z)$
-as $t$ tends to infinity.
-
-\begin{proposition}\label{NLIprop} 
-Suppose $\delta=0$, $\hat\delta=0$ and $\varepsilon=0$.
-Let $\mu>{K/4}-\sigma$, then 
-$||U-u|| \to 0$ as $t\to \infty$.
-In particular, synchronization is obtained 
-by equation~(\ref{freeODE}).
-\end{proposition}
-
-\begin{proof}
-Define $V=\yourdelta X^2+\yourdelta Y^2+\yourdelta Z^2$ 
-where $\yourdelta X=X-x$, $\yourdelta Y=Y-y$ and
-$\yourdelta Z=Z-z$.
-Since
-\begin{align}
-\label{NLIddotx}
-    \yourdelta\dot{X} &= -(\sigma + \mu)\yourdelta X + \sigma\yourdelta Y\\
-\label{NLIddoty}
-    \yourdelta\dot{Y} &= -\sigma\yourdelta X - \yourdelta Y - \yourdelta XZ - x\yourdelta Z\\
-\label{NLIddotz}
-    \yourdelta\dot{Z} &= -b\yourdelta Z + \yourdelta X Y + x\yourdelta Y
-\end{align}
-we have
-$$
-{1\over 2}\dot{V} + (\sigma + \mu)\yourdelta X^2 + \yourdelta Y^2 + b\yourdelta Z^2 =
--\yourdelta X\yourdelta Y Z +\yourdelta X Y \yourdelta Z.
-$$
-Since $\mu+\sigma>K/4$ then there exists $\alpha\in (0,2)$
-such that 
-\begin{equation}\label{alphadef}
-	\sigma + \mu = {\alpha\over 2}+{K\over 2(2-\alpha)}.
-\end{equation}
-Using Young's inequality we have 
-$$
-	-\yourdelta X\yourdelta Y Z\le
-    \frac{Z^2\yourdelta X^2}{2}\Big({1\over 2-\alpha}\Big) 
-		+  {\yourdelta Y^2\over 2} (2-\alpha)
-$$
-and
-$$
-	\yourdelta XY\yourdelta Z\le
-    \frac{Y^2\yourdelta X^2}{2}\Big({1\over 2b-\alpha}\Big)
-		+ {\yourdelta Z^2\over 2} (2b-\alpha).
-$$
-Therefore
-$$
-{1 \over 2}\dot{V} + \Big(\sigma + \mu 
-	-{Y^2\over 2(2b-\alpha)}
-	-{Z^2\over 2(2-\alpha)} 
-\Big)\yourdelta X^2 + {\alpha\over 2}\yourdelta Y^2 + 
-	{\alpha\over 2}\yourdelta Z^2 \le
-    0.
-$$
-Since our working assumption is that $U$ lies on the global attractor,
-then Theorem~\ref{Ktheorem} and the fact that $b\ge 1$ implies that
-$$
-{Y^2\over 2(2b-\alpha)}
-+{Z^2\over 2(2-\alpha)}
-	\le {K\over 2(2-\alpha)} = 
-		\sigma+\mu-{\alpha\over 2}
-$$
-Hence 
-$$
-	{1 \over 2}\dot{V} + {\alpha\over 2}
-		\yourdelta X^2 + {\alpha\over 2}\yourdelta Y^2 +
-    {\alpha\over 2}\yourdelta Z^2 \le
-    0.
-$$
-and consequently $\sigma+\mu\ge 1$ implies that
-$\dot{V} + \alpha V \le 0$.
-Integrating over the interval $[0,t]$ yields
-$V(t) \leq  V(0)e^{-\alpha t} $.
-\end{proof}
-
-\section{Noiseless Time-averaged Coupling}\label{NLTACoupling}
-
-We now examine convergence of the trajectories using the 
-time-averaged observation operator when $\hat\delta$
-is known without noise.  Taking $\delta=\hat\delta$
-and substituting ${\cal R}_\delta=\cL\circ\cO_\delta$ into
-equation~(\ref{noerra}) yields the driven system given by
-$$
-    \dot{x} = -\sigma(y-x)+\mu (\bar X-\bar x)
-$$
-where
-$$
-	\bar X =
-{1\over\delta}\int_{t-\delta}^t X(s)\, ds
-\wwords{and}
-	\bar x =
-{1\over\delta}\int_{t-\delta}^t x(s)\, ds
-$$
-with $\dot y$ and $\dot z$ given as before by equations (\ref{drivenY})
-and (\ref{drivenZ}).
-Thus equations (\ref{NLIddoty}) and (\ref{NLIddotx}) remain the same but
-the evolution of the $\Delta X$ given by equation~(\ref{NLIddotx}) now becomes
-\begin{plain}\begin{equation}\label{NLTAdxo}\eqalign{
-    \yourdelta\dot{X} &= -\sigma \yourdelta X + \sigma\yourdelta Y 
-		- \mu \yourdelta\bar{X}
-}\end{equation}\end{plain}%
-where $\yourdelta\bar X=\bar X-\bar x$.
-We show for $\mu$ sufficiently large and $\delta$ small that 
-the approximating solution
-converges to the
-reference solution as $t$ tends to infinity.
-
-Before proving the main result in this chapter, we first turn our
-attention to an estimate that compares time-averaged
-and instantaneous-in-time feedback terms.
-
-\begin{lemma}\label{tadiffit} 
-%Given $\yourdelta X$ as defined in Section ?? and $\yourdelta\bar{X} 
-%= \frac{1}{\delta}\displaystyle\int_{t-\delta}^t X(s) \,ds$. 
-Let $\yourdelta\bar X=\bar X-\bar x$.
-We have
-$$| \yourdelta X - \yourdelta\bar{X}|^2 \leq 4\delta(\sigma 
-+ \mu)^2\displaystyle\int_{t-2\delta}^t\big\{
-	|\yourdelta X|^2 + |\yourdelta Y|^2\big\}.$$ 
-\end{lemma}
-\begin{proof} By definition
-\begin{align*}
-    | \yourdelta X - \yourdelta\bar{X}| &
-%\big|\yourdelta X(t) 
-%    - \displaystyle\int_{t-\delta}^t\yourdelta X(s)\,ds\big| =
-	= \frac{1}{\delta}\bigg|\int_{t-\delta}^t
-		\big\{\yourdelta X(t)-\yourdelta X(s)\big\}\,ds \bigg| \\
-%   & = \frac{1}{\delta}\bigg|\int_{t-\delta}^t\int_s^t 
-%		\yourdelta\dot{X}(\rho)\,d\rho \,ds \bigg| \\
-    &\leq \frac{1}{\delta}\int_{t-\del}^t\int_s^t 
-		|\yourdelta\dot{X}(\rho)|\,d\rho \,ds
-    \leq \int_{t-\del}^t
-		|\yourdelta\dot{X}(\rho)|\,d\rho \\
-    &= \int_{t-\delta}^t|-\sigma\yourdelta X(\rho) 
-	    + \sigma\yourdelta Y(\rho) - \mu\yourdelta\bar{X}(\rho)| \,d\rho \\
-    &\leq \sigma \int_{t-\delta}^t|\yourdelta X| 
-		+ \sigma \int_{t-\delta}^t|\yourdelta Y| 
-	    + \frac{\mu}{\delta}\int_{t-\delta}^t
-		\int_{\rho-\delta}^{\rho} |\yourdelta X(\xi)|
-		\,d\xi \,d\rho \\
-    &\leq \sigma \int_{t-\delta}^t|\yourdelta X| 
-	    + \sigma \int_{t-\delta}^t|\yourdelta Y| 
-		+ \mu\int_{t-2\delta}^t |\yourdelta X(\xi) | \,d\xi \\
-    &\leq (\sigma + \mu)\displaystyle\int_{t-2\delta}^t|\yourdelta X| 
-    + \sigma\int_{t-\delta}^t|\yourdelta Y|.
-\end{align*}
-Therefore,
-\begin{align*}
-    | \yourdelta X - \yourdelta\bar{X}|^2 &\leq 2(\sigma 
-    + \mu)^2\bigg(\displaystyle\int_{t-2\delta}^t|\yourdelta X|\bigg)^2 
-    + 2\sigma^2\bigg(\int_{t-\delta}^t|\yourdelta Y|\bigg)^2\\
-    &\leq 4\delta(\sigma + \mu)^2\int_{t-2\delta}^t 
-		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\},
-\end{align*}
-which finishes the proof.
-\end{proof}
-
-We are now ready to show the convergence of the driven solution
-to the free running solution.
-
-\begin{proposition}\label{NLTAprop} 
-Suppose $\delta=\hat\delta$ and $\varepsilon=0$.
-Let $\alpha\in (0,2)$,
-$\mu \ge {K/(2-\alpha)^2}-\sigma$ and 
-$$	\delta<
-	\sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 16\mu(\sigma+\mu)^2}}.$$
-Then $||U-u|| \to 0$ as $t\to \infty$.
-\end{proposition}
-
-\begin{proof}
-The proof proceeds as the proof 
-of Proposition~\ref{NLIprop}.
-After multiplying by $\yourdelta X$ the only difference is the additional 
-term on the right hand side that
-which we estimate using Lemma~\ref{tadiffit} as
-\begin{align*}
-    \mu(\yourdelta X - \yourdelta\bar{X})\yourdelta X
-		&\le
-    {\mu\over 2\alpha}|\yourdelta X - \yourdelta\bar{X}|^2 +
-		{\alpha\mu\over 2}|\yourdelta X|^2\\
-    &
-		\leq {2\delta\mu (\sigma + \mu)^2\over \alpha}
-		\int_{t-2\delta}^t 
-		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}
-		+{\alpha\mu\over 2}|\yourdelta X|^2.
-\end{align*}
-Therefore
-\begin{plain}$$\eqalign{
-{1 \over 2}\dot{V} + 
-	\Big(\sigma + \mu
-		-{\alpha\mu\over 2}
-		-{Y^2\over 2(2b-\alpha)}
-		&-{Z^2\over 2(2-\alpha)} 
-	\Big)
-\yourdelta X^2 + {\alpha\over 2}\yourdelta Y^2 + 
-	{\alpha\over 2}\yourdelta Z^2 \cr
-	&\le
-		 {2\delta\mu (\sigma + \mu)^2\over \alpha}
-		\int_{t-2\delta}^t 
-		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}.
-}$$\end{plain}%
-By hypothesis
-$$
-	{\alpha\mu \over 2} + {K\over 2(2-\alpha)} 
-	\le \mu+\sigma\Big(1-{\alpha\over 2}\Big).
-$$
-Therefore
-\begin{align*}
-    \dot V 
-+ \alpha V
-	\leq 
-	    {4\delta\mu (\sigma + \mu)^2\over \alpha}
-		\int_{t-2\delta}^t V(s)\,ds.
-\end{align*}
-Define $\cV(\tau)= V(\tau / \alpha)$. 
-%$\dot V=\alpha \cV'(\tau)$.  
-It follows that
-$$
-	{d\cV(\tau)\over d\tau}
-		+\cV(\tau)\le {4\delta\mu(\sigma+\mu)^2\over \alpha^3}
-		\int_{\tau-2\alpha\delta}^\tau \cV(s)\,ds.
-$$
-By hypothesis $\delta$ is small enough that we may apply
-Corollary~\ref{intGronwallerror0} with 
-$$A=4\mu(\sigma+\mu)^2/\alpha^3,\qquad B=0\wwords{and}h=2\alpha\delta
-$$
-to conclude that $V\to 0$ as $t\to\infty$.
-\end{proof}
-
-Note that by taking $\alpha$ small we obtain synchronization
-for values of $\mu$ close to the limiting value $K/4-\sigma$
-given in Proposition~$\ref{NLIprop}$.
-However, as $\alpha$ vanishes the length $\delta$ of the
-time averaging window also vanishes.
-On the other hand, as $\alpha$ approaches 2, then
-$\mu$ approaches infinity and
-since $\delta$ depends inversely on $\mu^{3/2}$
-then again $\delta$ vanishes.
-Thus, there is some value $\alpha\in(0,2)$ for which
-our analytic bound on $\delta$ is maximal.  Simple
-calculus yields this optimal value to be
-$$
-  \alpha^*=-\rho\cos(\phi)+{22\over 15}+\rho\sqrt3\sin\phi
-      \approx 0.28413
-$$
-where
-$$
-  \rho={4\sqrt{25370}\over 75}
-\wwords{and}
-  \phi={1\over 3}\arctan\Big({19\sqrt{1731443695}\over167665}\Big).
-$$
-For $\alpha=\alpha^*$ it follows that we may take
-$$
-  \mu\approx 513.153\wwords{and}\delta\approx 0.0000063216.
-$$
-
-\section{Unknown Noiseless Time-averaged Coupling}\label{UNTCoupling}
-
-In the previous chapter we assumed the time averaging
-window of the observations was known exactly.
-We then used this same averaging window in the 
-feedback control of the driven system to obtain exact 
-synchronization.
-In this chapter we examine the case when the time averaging 
-in the observations of the free running solution is unknown.
-%and the driven system is given by (\ref{NLTAUnkSoln}).
-Specifically, we have
-$$
-    \dot{x} = -\sigma(y-x)+\mu 
-		\Big(
-		{1\over\hat\delta}\int_{t-\hat\delta}^t X(s)ds
-		-{1\over\delta}\int_{t-\delta}^t x(s)ds
-	\Big)
-$$
-with $\dot y$ and $\dot z$ given as before by equations (\ref{drivenY})
-and (\ref{drivenZ}).
-Recall that $\hat\delta$ is the unknown size of 
-the averaging window in the observations of the free running 
-solution and $\delta$ be the averaging
-used in the feedback control of the driven system.
-%\[\frac{du}{dt} = \cF(u) +
-%    \mu\big(R_{\hat\delta}(U) 
-%-R_{\delta}(u) \big). \]
-Recall that $\hat\delta$ is the unknown size of 
-the averaging window in the observations of the free running 
-solution and $\delta$ is the averaging
-used in the feedback control of the driven system.
-In this case
-\begin{plain}\begin{equation}
-	\eqalign{\label{NLTAdxhat}
-    {\yourdelta \dot X} =& -\sigma\yourdelta X + \sigma\yourdelta Y 
-        - {\mu\over\hat\delta}\displaystyle\int_{t-\hat\delta}^{t} X
-        +{\mu\over\delta}\displaystyle\int_{t-\delta}^{t} x  \cr
-    =& -(\sigma+\mu)\yourdelta X + \sigma\yourdelta Y 
-       + \mu(\yourdelta X-\yourdelta\bar{X})
-		+ \mu{\cal E}_1 +\mu {\cal E}_2
-}\end{equation}\end{plain}%
-where
-$$
-       {\cal E}_1=
-		{1\over\hat\delta}\int_{t-\delta}^{t-\hat\delta} X
-\words{and}
-       {\cal E}_2=
-		\Big({1\over\delta}-{1\over\hat\delta}\Big)
-			\int_{t-\delta}^t X
-$$
-represents the errors resulting from the unknown time 
-averaging window.
-Note that when $\delta=\hat\delta$ this is exactly the coupling
-method treated in Proposition~\ref{NLTAprop}.  When
-$\delta\ne\hat\delta$ exact synchronization does not occur;
-however, the error between $u$ and $U$ can be bounded by
-a constant which tends to zero as $\delta$ approaches $\hat\delta$.
-
-We begin with a slightly modified version of Lemma~\ref{tadiffit}
-that reflects the fact that $\hat\delta\ne\delta$.
-\begin{lemma}\label{tadiffithat}
-We have
-\begin{align*}
-	|\Delta X-\Delta \bar X|^2
-	\le
-		4\delta(\sigma+\mu)^2
-		\int_{t-2\delta}^t\big\{|\Delta X|^2&+|\Delta Y|^2\big\}
-		+8 \mu^2\delta^2 K \Big({\delta-\hat\delta\over\hat\delta}\Big)^2.
-\end{align*}
-\end{lemma}
-\begin{proof}
-The proof proceeds as in Lemma~\ref{tadiffit}.  Thus
-\begin{plain}$$
-\eqalign{
-	|\Delta X-\Delta\bar X| 
-	&\le \int_{t-\delta}^t |\Delta\dot X(\rho)|d\rho
-	\le I_1+I_2+I_3
-}$$\end{plain}%
-where
-\begin{plain}$$\eqalignno{
-    I_1&=(\sigma+\mu)\int_{t-2\delta}^t |\Delta X|,\qquad
-	I_2=\sigma\int_{t-\delta}^t |\Delta Y|\cr
-\noalign{\noindent and}
-	I_3&=
-		\mu\int_{t-\delta}^t{1\over\hat\delta}
-			\int_{\rho-\delta}^{\rho+\hat\delta} X(\xi)d\xi d\rho
-		+\mu\int_{t-\delta}^t
-			\Big({1\over\delta}-{1\over\hat\delta}\Big)
-			\int_{\rho-\delta}^{\rho} X(\xi)d\xi d\rho
-		\cr
-		&\le \mu\bigg|\int_{t-\delta}^t {1\over\hat\delta}
-			\int_{\rho-\delta}^{\rho+\hat\delta} \sqrt K\,d\xi d\rho\bigg|
-		+\mu\bigg|\int_{t-\delta}^t
-			\Big({1\over\delta}-{1\over\hat\delta}\Big)
-			\int_{\rho-\delta}^{\rho} \sqrt K \,d\xi d\rho\bigg|\cr
-		&= 2\mu \sqrt K \delta \Big|{\delta-\hat\delta\over\hat\delta}\Big|
-}$$\end{plain}%
-Squaring the results as
-$$
-	|\Delta X-\Delta\bar X|^2
-		\le (I_1+I_2+I_3)^2
-		\le 2 I_1^2+4 I_2^2 + 4 I_3^2
-$$
-yields the desired result.
-\end{proof}
-
-\begin{proposition}\label{UKNLTAprop}
-Given $\alpha\in(0,2)$,
-let 
-$$\mu \ge JK/(2-\alpha)^2-\sigma
-\words{where}
-		J={\sigma(1+\sqrt 2)}
-        \Big({\hat\delta\over 2} +\delta\Big)+1.
-$$ 
-and 
-\begin{equation}\label{deltabound32}
-\delta<
-    \sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 16\mu(\sigma+\mu)^2}}.
-\end{equation}
-Then $$\limsup_{t\to\infty}||U-u||^2
-< 
-	{5e(2-\alpha)\mu^2\over\alpha}
-%e {2-\alpha\over\alpha}
-%	\cdot \Big(
-%	{1\over 2} +
-%		{4\mu^2}     \Big)
-\Big({\hat\delta-\delta\over\hat\delta}\Big)^2.
-      $$
-\end{proposition}
-
-\begin{proof}
-The proof proceeds as before.
-Upon multiplying equation~(\ref{NLTAdxhat}) by $\yourdelta X$ we estimate 
-the additional terms as
-$$
-	\mu {\cal E}_i\yourdelta X\le
-		{\mu \eta \over 2}
-		{\cal E}_i^2\yourdelta X^2
-		+
-		{\mu \over 2\eta}
-\words{for} i=1,2.
-$$
-%Therefore
-%\begin{plain}$$\eqalign{
-%{1 \over 2}\dot{V} &+
-%    \Big(\sigma + \mu
-%        -{\alpha\mu\over 2}
-%		-{\mu\eta\over 2}\big({\cal E}_1^2+{\cal E}_2^2\big)
-%        -{Y^2\over 2(2b-\alpha)}
-%        -{Z^2\over 2(2-\alpha)
-%}
-%    \Big)
-%\yourdelta X^2 \cr
-%	&+ {\alpha\over 2}\yourdelta Y^2 +
-%    {\alpha\over 2}\yourdelta Z^2
-%    \le
-%         {2\delta\mu (\sigma + \mu)^2\over \alpha}
-%        \int_{t-2\delta}^t
-%        \big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}+{\mu\over\eta}.
-%}$$\end{plain}%
-Since
-$$
-{Y^2\over 2(2b-\alpha)}
-        +{Z^2\over 2(2-\alpha)}
-	\le {1\over 2(2-\alpha)}\big(K-X^2\big)
-$$
-we obtain
-\begin{plain}$$\eqalign{
-{1 \over 2}\dot{V} &+
-    \Big(\sigma + \mu
-        -{\alpha\mu\over 2}
-        +{X^2\over 2(2-\alpha)}
-		-{\mu\eta\over 2}\big({\cal E}_1^2+{\cal E}_2^2\big)
-        -{K\over 2(2-\alpha)}
-    \Big)
-\yourdelta X^2 \cr
-	&+ {\alpha\over 2}\yourdelta Y^2 +
-    {\alpha\over 2}\yourdelta Z^2
-    \le
-         {2\delta\mu (\sigma + \mu)^2\over \alpha}
-        \int_{t-2\delta}^t
-        \big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}\cr
-		&\qquad\qquad\qquad\qquad\qquad\quad
-		+{4\mu^2\delta^2K\over\alpha}
-			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
-		+{\mu\over\eta}.
-}$$\end{plain}%
-Now, by the Cauchy--Schwartz inequality
-$$
-	{\mu\eta}{\cal E}_1^2
-\le
-{\mu\eta\over\hat\delta^2} |\hat\delta-\delta|
-		\bigg|
-		\int_{t-\delta}^{t-\hat\delta} X^2
-		\bigg|
-\quad\hbox{and}\quad
-	{\mu\eta}{\cal E}_2^2
-\le
-{\mu\eta\over\hat\delta^2} |\hat\delta-\delta|^2
-		\bigg|
-		{1\over \delta}
-		\int_{t-\delta}^t X^2
-		\bigg|.
-$$
-Upon taking
-$$
-	\eta={1\over 2(2-\alpha)}\cdot{\hat\delta^2\over(\hat\delta-\delta)^2}
-		\cdot {1\over \mu}
-$$
-we obtain
-\begin{plain}$$\eqalign{
-	{X^2\over 2(2-\alpha)}-\mu\eta
-		{\cal E}_1^2
-	\ge
-	{-1\over 2(2-\alpha)}
-		\bigg|
-			{1\over \hat\delta-\delta}
-			\int_{t-\delta}^{t-\hat\delta}
-				\big(X(t)^2-X(s)^2\big)ds\bigg|
-}$$\end{plain}%
-and
-\begin{plain}$$\eqalign{
-	{X^2\over 2(2-\alpha)}-\mu\eta{\cal E}_2^2
-	\ge
-	{-1\over 2(2-\alpha)}
-		\bigg| {1\over \delta}
-			\int_{t-\delta}^t
-				\big(X(t)^2-X(s)^2\big)ds\bigg|.
-}$$\end{plain}%
-Since 
-\begin{align*}
-	|X(t)^2&-X(s)^2|=\Big|2\int_s^t X\dot X\Big|
-	\le 2\sigma \int_s^t (X^2+ |XY|)\\
-	&
-	\le \sigma (1+\sqrt 2)\int_s^t \big(X^2+ Y^2\big)
-	\le \sigma (1+\sqrt 2)(t-s)K
-\end{align*}
-then
-$$
-	{X^2\over 2-\alpha}-\mu\eta
-        \big({\cal E}_1^2+{\cal E}_2^2\big)
-	\ge{-\sigma(1+\sqrt 2)\over 2(2-\alpha)}
-    \Big({\hat\delta+\delta\over 2}+{\delta\over 2}\Big)K
-	={1-J\over 2(2-\alpha)}K.
-$$
-Consequently
-\begin{align*}
-{1 \over 2}\dot{V} &+
-    \Big(\sigma + \mu
-        -{\alpha\mu\over 2}
-	-
-        {JK\over 2(2-\alpha)}
-    \Big)
-	\yourdelta X^2 
-	+ {\alpha\over 2}\yourdelta Y^2 +
-    {\alpha\over 2}\yourdelta Z^2\\
-    &\le
-         {2\delta\mu (\sigma + \mu)^2\over \alpha}
-        \int_{t-2\delta}^t
-        \big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}
-		+{4\mu^2\delta^2K\over\alpha}
-			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
-+{\mu\over\eta}.
-\end{align*}
-By hypothesis
-$$
-	{\alpha\mu\over 2}
-    +
-        {JK\over 2(2-\alpha)}
-	\le
-		\mu+\sigma \Big(1-{\alpha\over 2}\Big).
-$$
-Therefore
-\begin{align*}
-    \dot V
-+ \alpha V
-    \leq
-        {4\delta\mu (\sigma + \mu)^2\over \alpha}
-        \int_{t-2\delta}^t V(s)\,ds
-		+{8\mu^2\delta^2K\over\alpha}
-			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
-+{2\mu\over\eta}.
-\end{align*}
-We apply Lemma~\ref{intGronwallerror} as in the proof
-of Proposition~\ref{NLTAprop} except this time 
-taking 
-$$B=
-		{8\mu^2\delta^2K\over\alpha^2}
-			\Big({\delta-\hat\delta\over\hat\delta}\Big)^2
-+{2\mu\over \alpha\eta}
-.$$  The result follows.
-\end{proof}
-
-\section{Numeric Results for Noiseless Coupling}\label{NoiselessComp}
-
-In all our numerical experiments the free-running solution 
-$U$ was obtained by taking 
-$$U_0=(-5.5751, -3.24345, -11.0728).$$
-As this value of $U_0$ lies very close to the global attractor,
-the resulting trajectory
-satisfies the conditions of Theorem~\ref{Ktheorem}
-to within a certain numerical error and therefore 
-we suppose the bound (\ref{numbound}) holds.
-A sharper bound may be obtained {\it a posteriori\/} 
-as the maximum value of the actual numerical solution.  
-In particular, the trajectory for $U$
-considered here satisfies
-\begin{equation}\label{numbound}
-	\|U(t)\|^2\le 1247.0911\qquad\hbox{for}\qquad t\in [0,500]
-\end{equation}
-which is about 20 percent smaller than the theoretical 
-bound.
-
-%Computationally, our free-running solution satisfies
-%$$K=(18.2818, 24.6582, 8.4834)$$
-%and
-%$$k=(-18.8543,-25.7439,-34.55988).$$
-
-\begin{figure}[ht]\label{measd}
-    \centerline{\begin{minipage}[t]{0.9\textwidth}
-    \caption{\label{d025meas}%
-	Illustration of time-averaged exact measurements of $U$
-	for different values of $\delta$.}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{d025meas.eps}}
-\end{figure}
-
-We compute $u$ using equations (\ref{noerra})
-with $\widetilde{\cal R}={\cal R}=R_\delta$ 
-and $u_0=(0,0,0)$ for different values 
-of $\delta$ with $\mu=30$.  
-This value of $\mu$ is comparable
-to the value $\mu=K/40\approx 38.5$ used for Figure 5 
-of \cite{Stuart14}. 
-Figure~$\ref{measd}$ illustrates the 
-phase shift that occurs for $\delta >0$ which delays the measurements of $U$ in time.
-
-\begin{figure}[ht]\label{avgd}
-    \centerline{\begin{minipage}[t]{0.9\textwidth}
-    \caption{\label{e0assim}%
-	Results when coupling time-averaged exact measurements
-	with an averaging window of size $\delta$ when $\delta=\hat\delta$.}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{e0assim.eps}}
-\end{figure}
-
-In particular, Figure~\ref{e0assim} shows the evolution of 
-the error $\|U-u\|^2$ when coupling the free-running solution to the
-driven solution using noise-free time averaged measurements of $X$
-with $\mu=30$ when $\hat\delta=\delta$ for $\delta\in \{ 0, 0.25, 0.375 \}$.
-For $\delta=0$ and $\delta=0.25$ the error converges 
-to zero within the limits of the floating point arithmetic
-used for the computations.
-We point out, however, that the rate of convergence
-appears slightly slower when $\delta=0.25$.
-On the other hand the error remains large for $\delta=0.375$.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[t]{0.9\textwidth}
-    \caption{\label{avgdup}%
-	Results when coupling time-averaged exact measurements
-	with an averaging window of size $\delta$ near
-$\delta_c$ for $T<2000$ when $\hat\delta=\delta$.}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{e0assimupper.eps}}
-\end{figure}
-
-Further computations show that the conditions for convergence
-are intractable when $\delta \approx 0.33$. 
-Intuitively, we suspect there is a value $\delta_c$ such that
-for $\delta < \delta_c$ the rate of convergence is very slow, but
-synchronization is eventually achieved and the error decays to zero,
-and for $\delta > \delta_c$ the systems fail to synchronize.
-Our calculations suggest $\delta_c\in [0.31,0.33]$, provided such
-a critical value exists.
-What we do know, is that numerically for values $\delta>0.33$ there
-is no sign of synchronization, and for values $\delta<0.31$ the
-two solutions synchronize to within the limits of the rounding error
-of the double precision arithmetic used for our calculations.
-Figure~\ref{avgdup} shows instability of the synchronization
-for $\delta = 0.318$, where the error $\|U-u\|^2$ 
-oscillates over time through $20$ decimal orders of magnitude.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[t]{0.9\textwidth}
-    \caption{\label{avgdiffmu}
-	Results when coupling time-averaged exact measurements
-	with an averaging window of size $\delta = 0.334$ using
-    increasing values of $\mu$ where $T<600$ when $\hat\delta=\delta$.}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{e0diffmu.eps}}
-\end{figure}
-
-While the theory requires $\mu$ to be greater than $375.07$,
-a slightly less restrictive bound on $\mu$ may be obtained 
-by using the value for $K$ suggested by the bound (\ref{numbound}).
-Either bound, however, is significantly more restrictive 
-than the value chosen here which 
-works when the size of the averaging window is sufficiently small.
-In this case where $\delta > 0.33$, there are no 
-values of $\mu$ for which the error converges to zero, illustrated in
-Figure~\ref{avgdiffmu}.
-
-By further varying the value of $\delta$ it appears that
-$\delta\le 0.31$ is sufficient to ensure
-$\|U-u\|\to 0$ numerically as $t\to\infty$.
-We further compare the theoretical size of $\delta$ to 
-this numerically determined value.
-To find the largest value of $\delta$ that Proposition~\ref{NLTAprop} 
-guarantees will lead to synchronization
-we maximize the upper bound in 
-(\ref{deltabound32}) with respect to $\alpha$.
-Note that as $\alpha$ vanishes in the bound (\ref{deltabound32}) 
-the length $\delta$ of the time averaging window also 
-vanishes.  Moreover, $\delta$ also vanishes as 
-$\alpha$ approaches 2,
-because $\delta$ depends inversely on $\mu^{3/2}$ and
-$\mu$ approaches infinity as $\alpha$ approaches $2$.
-Simple
-calculus now yields the optimal value of $\alpha$ to be
-$$
-  \alpha^*=-\rho\cos(\phi)+{22\over 15}+\rho\sqrt3\sin\phi
-      \approx 0.28413
-$$
-where
-$$
-  \rho={4\sqrt{25370}\over 75}
-\wwords{and}
-  \phi={1\over 3}\arctan\Big({19\sqrt{1731443695}\over167665}\Big).
-$$
-For $\alpha=\alpha^*$ it follows that we may take
-$$
-  \mu\approx 513.153\wwords{and}\delta\approx 0.0000063216.
-$$
-Using the value for $K$ suggested by the bound 
-(\ref{numbound}) leads to a 30 percent larger value for $\delta$;
-however, in either case the analytic bounds are more than $10\,000$
-times stricter than what works numerically.
-
-In summary our numeric results show
-measurements of $X$ averaged with respect to a small
-averaging window are just as effective for synchronizing the
-driven solution to the free-running solution as exact
-measurements taken instantaneously in time.  However, if
-the averaging window is too large, then the information is
-blurred too much for $u$ to synchronize with $U$.
-This is consistent with the theoretical results of
-Proposition~\ref{NLTAprop} which proves the
-convergence of the driven solution to the free-running
-solution only when $\delta$ is sufficiently small and $\mu$
-sufficiently large.
-We emphasize that our analytic bounds on $\mu$ and $\delta$
-are much more restrictive than what works numerically.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[t]{0.9\textwidth}
-    \caption{\label{avgddhat}%
-	Results when coupling time-averaged exact measurements with
-    window size $\hat\delta=0.25$ using a feedback term with
-	averaging window size $\delta\ne\hat\delta$.  Note that
-	$\Delta\delta=\delta-\hat\delta$.
-	}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{mix3a.eps}}
-    \centerline{\includegraphics[height=0.5\textwidth]{mix3b.eps}}
-\end{figure}
-
-Now consider the case treated by Proposition~\ref{UKNLTAprop} 
-where the exact size of the time averaging 
-window present in the observational measurements is unknown.
-Figure~\ref{avgddhat} describes the evolution of $\|U-u\|^2$ 
-when $\hat\delta=0.25$ and $\delta$ is smaller but near 
-$\hat\delta$.
-Note that $\delta$ greater than
-$\hat\delta$ results in a nearly identical graph.
-The asymptotic error
-%$$\limsup_{t\to\infty} \|U-u\|^2$$
-may be approximated numerically as a function of 
-$\Delta\delta=\delta-\hat\delta$ by
-$$
-%	\limsup_{t\to\infty} \|U-u\|^2
-%		\approx 
-	E(\Delta\delta)=
-	\max \big\{\, \|U-u\|^2 : t\in [50,100]\,\big\}.
-$$
-From Figure~$\ref{avgddhat}$, there is a decrease in the error $\|U-u\|^2$ as
-$\Delta\delta$ decreases before reaching $\Delta\delta=0$. 
-Table~\ref{tableddhat} illustrates the the convergence of the driven solution, where
-the limit supremum is taken over the error for all $t>T$.
-As expected, the error levels 
-decrease as $\delta$ gets closer to $\hat\delta$.
-It is reasonable to determine that there exists a function that will 
-allow us to predict
-the largest value $|\delta -\hat{\delta}|$ that results in convergence.
-We now consider the functional dependency how 
-$E(\Delta\delta)$ depends on $\Delta\delta$.
-
-    \begin{table}[h!]\label{tableddhat}
-    \centerline{\begin{minipage}[t]{0.9\textwidth}
-    \caption{\label{limsupexact}%
-	Limsup of $\| U - u\|^2$ for different values of $\Delta\delta$.
-    }
-    \end{minipage}}
-    \medskip
-    \centering
-    \begin{tabular}{  r | r }
-    \hline\hline
-\vphantom{\raise8pt\hbox{H}}%
-	$\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
-    \hline
-\vphantom{\raise8pt\hbox{H}}%
-$-2^{-2}$&$1267.31$ \\
-$-2^{-5}$&$194.081$ \\
-$-2^{-8}$&$5.61624$ \\
-$-2^{-11}$&$0.0906275$ \\
-$-2^{-14}$&$0.00140762$ \\
-$-2^{-17}$&$2.19772\times 10^{-05}$ \\
-$-2^{-20}$&$3.43361\times 10^{-07}$ \\
-$-2^{-23}$&$5.36495\times 10^{-09}$ \\
-$-2^{-26}$&$8.38272\times 10^{-11}$ \\
-$-2^{-29}$&$1.30979\times 10^{-12}$ \\
-$-2^{-32}$&$2.04656\times 10^{-14}$ \\
-$-2^{-35}$&$3.19773\times 10^{-16}$ \\
-$0.0$&$2.67042\times 10^{-25}$ \\
-[1ex]
-\hline
-\end{tabular}\qquad\qquad
-    \begin{tabular}{  r | r }
-    \hline\hline
-\vphantom{\raise8pt\hbox{H}}%
-	$\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
-    \hline
-\vphantom{\raise8pt\hbox{H}}%
-$2^{-2}$&$2663.41$ \\
-$2^{-5}$&$249.552$ \\
-$2^{-8}$&$5.86352$ \\
-$2^{-11}$&$0.0911086$ \\
-$2^{-14}$&$0.00143265$ \\
-$2^{-17}$&$2.24025\times 10^{-05}$ \\
-$2^{-20}$&$3.50073\times 10^{-07}$ \\
-$2^{-23}$&$5.46996\times 10^{-09}$ \\
-$2^{-26}$&$8.54684\times 10^{-11}$ \\
-$2^{-29}$&$1.33543\times 10^{-12}$ \\
-$2^{-32}$&$2.08664\times 10^{-14}$ \\
-$2^{-35}$&$3.26052\times 10^{-16}$ \\
-$0.0$&$2.67042\times 10^{-25}$ \\
-[1ex]
-\hline
-\end{tabular}
-\label{regress}
-\end{table}
-
-%Empirical evidence allows us to infer that there is an exponential function that will fit the rate of
-%convergence in terms of $\Delta\delta$. We find that the numerical data 
-%supports our results and provides greater
-%detail to the exact coefficients necessary for convergence.
-The theoretical bounds given by 
-Proposition~\ref{UKNLTAprop} suggest that
-$E(\Delta\delta)$ is proportional to 
-the square of $\Delta\delta$.
-In order to test this hypothesis we performed 
-a least squares fit to find $m$ and $s$ such that
-$$
-	\log E(\Delta\delta) \approx \log m + s \log(\Delta\delta).
-$$
-Figure~\ref{ftmix} shows that the least squares fit
-agrees with $E(\Delta\delta)$ to remarkable precision
-over a range of ten decimal orders of magnitude.
-Since the fitted value $s=1.99964$ 
-is so close to $2$, we presume that the $\Delta\delta$ 
-dependency given by our analytic bound is physical
-even though the values for $\mu$ and $\delta$
-are much more restrictive than numerically needed.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[b]{0.9\textwidth}
-    \caption{\label{ftmix}%
-	The numerical data from Table~\ref{limsupexact}
-	when plotted with the least squares fit
-	of $m(\Delta\delta)^s$
-	given by $m=378647$ and $s=1.99964$.}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{ftmix.eps}}
-\end{figure}
-
-It is worth remarking that the theoretical bound in
-Proposition~\ref{UKNLTAprop} actually depends on the 
-relative error $\Delta\delta/\hat\delta$ which,
-as we have held $\hat\delta=0.25$ constant, is
-proportional to the absolute error $\Delta\delta$
-in the above computations.
-Computations using different values for $\hat\delta$
-are a direction for future work described in
-Section~\ref{futurehatdelta}.  
-Preliminary calculations suggest that a better fit
-is obtained for bounds of the form
-$$
-	E(\Delta\delta) \approx m 
-			\Big({\delta-\hat\delta\over
-			\delta_c-\hat\delta}\Big)^2
-$$
-where $\delta_c\approx 0.33$ is the critical 
-value of $\delta$ for which synchronization fails detailed
-in Figure~\ref{avgdup}.
-The numerical dependence of the bound on $\hat\delta$ is 
-a point of future work.
-
-\chapter{Coupling with Noise}
-
-In this chapter we examine the synchronization of the free running and driven
-solutions with the addition of a time-averaged Brownian motion. By
-synchronization we mean that the system driven by noisy observations will converge
-to the true solution within a tolerance determined by the level of observational noise.
-The expected value $\bf E$ of the convergence is examined as we are only able to
-bound the error of the system with some probability for a finite
-amount of time, preventing us from forming a generalized proof for pathwise convergence.
-In particular, we bound the expected value of the error 
-and then use Chebyshev's inequality to find probabilistic 
-bounds on the paths.
-
-\section{Noisy Instantaneous-in-Time Coupling}
-
-Consider when the observations of $U$
-are noisy and satisfy equation~(\ref{tildecO})
-%$$\tilde {\cal O}(U)dt = Xdt + \varepsilon dW_t$$
-where $W_t$ is a one-dimensional 
-standard Brownian motion.
-Thus, the noise present in the observational measurements 
-satisfies ${\bf Var}(\varepsilon W_t)= t\varepsilon^2$.
-In this case, equation~(\ref{drivenX}) becomes
-\begin{equation}\label{dxnoise}
-    dx = -\sigma(y-x)dt+\mu(X-x)dt + \varepsilon \mu dW_t.
-\end{equation}
-Note that the noise present in the observations appears
-in equation~(\ref{dxnoise}) multiplied by the factor $\mu$.
-Therefore, increasing $\mu$ to strengthen the coupling 
-between $U$ and $u$
-also amplifies the noise.
-
-The techniques employed are almost identical to those in \cite{Olson14} 
-but have been detailed here to provide a concrete point of reference
-for comparing our main results which involve time-averaged measurements.
-The results in this section, though slightly sharper,
-are similar to those which appear in \cite{Stuart14}. 
-As in Section~\ref{NLICoupling}, carefully examining the case 
-without time-averages first provides a concrete point of reference 
-for comparing our results which involve time-averaged measurements.
-\begin{proposition}\label{NIprop} 
-Suppose $\delta=0$, $\hat\delta=0$ and $\varepsilon>0$.
-Let $\mu>K/4-\sigma$, then
-$$\limsup_{t\to\infty}{\bf E}\big[||U-u||^2\big] 
-	\le
-{\mu^2\varepsilon^2\over 
-		\sigma+\mu+1-\sqrt{(\sigma+\mu-1)^2+K}
-}$$
-\end{proposition}
-
-\begin{proof}
-With the addition of the noise, equation~(\ref{NLIddotx})
-becomes the stochastic differential equation
-$$
-d(\yourdelta X) = -(\sigma + \mu)\yourdelta X dt + \sigma\yourdelta Y dt
- - \mu
-{\varepsilon} dW_t.
-$$
-Using Ito's formula and the same estimates as in 
-Proposition~\ref{NLIprop} we obtain
-$$d{V} + \alpha V dt \le 
-    2\mu\varepsilon \yourdelta X d W_t +\mu^2\varepsilon^2 dt.$$
-Integrating over the interval $[0,t]$ yields
-$$
-	V(t)e^{\alpha t}-V(0)\le 
-		2\mu\varepsilon\delta \int_0^t e^{\alpha s}\yourdelta X(s) d W_s
-		+{\mu^2\varepsilon^2 \over \alpha}\big( e^{\alpha t} -1 \big).
-$$
-Now, taking expected values obtains
-$$
-	{\bf E}\big[V(t)\big]\le e^{-\alpha t}{\bf E}\big[V(0)\big]
-		+{\mu^2\varepsilon^2 \over \alpha}\big( 1-e^{-\alpha t} \big).
-$$
-Consequently
-$$
-	\limsup_{t\to\infty} {\bf E}[V] \le {\mu^2\varepsilon^2\over\alpha}.
-$$
-Solving for $\alpha$ in equation~(\ref{alphadef}) finishes the proof.
-\end{proof}
-
-\section{Noisy Time-averaged Coupling}\label{NTACsec}
-
-In this section we consider the case when
-the noisy observations
-of $X$ have been averaged in time over a known window of 
-size $\hat\delta$.  Thus we take $\delta=\hat\delta$ and
-%${\cal R}=\widetilde R_\delta$ 
-in equation~(\ref{NLTAUnkSoln}) and
-equation~(\ref{drivenX}) becomes
-$$
-	\dot x = -\sigma(y-x) +\mu(\bar X-\bar x)+\mu\xi
-\words{where} \xi(t)={\varepsilon\over\delta}\big(W_t-W_{t-\delta}\big).
-$$
-Thus
-$$
-	\yourdelta\dot X 
-	=-(\sigma+\mu)\yourdelta X+\sigma\yourdelta Y +
-		\mu(\yourdelta X-\yourdelta\bar X)+\mu\xi.
-$$
-Theoretically the presence of a small time average in the measurements 
-does not substantially affect the results of the instantaneous in
-time case.
-Our results show that measurements averaged over
-small time windows lead to bounds that are similar to those given 
-by Proposition~\ref{NIprop} when there are no time averages.
-The expected value of the difference 
-between the driven solution and the free running solution in
-both cases is bounded by a constant factor of the variance of the noise.
-In particular, we have
-
-\begin{proposition}\label{NTAprop} 
-Let $\alpha\in(0,2)$ and $\mu\ge K/(2-\alpha)^2-\sigma$.  If
-$$	\delta<
-	\sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 32\mu(\sigma+\mu)^2}}.
-$$
-Then
-$$
-	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] <
-	e\Big({8\mu^3\over\alpha^2}+{2\mu\over \alpha^2\delta}\Big)
-		\varepsilon^2.
-$$
-\end{proposition}
-
-\begin{proof} 
-The proof proceeds as the proof of Proposition~\ref{NTAprop}, where the
-only difference is an additional noise term.
-Similar estimates as in the proofs of Lemma~\ref{tadiffit}
-and Lemma~\ref{tadiffithat} yield that
-$$
-	|\Delta X-\Delta\bar X|^2
-		\le
-		4\delta(\sigma+\mu)^2
-		\int_{t-2\delta}^t \big\{|\Delta X|^2+|\Delta Y|^2\big\}
-		+4\mu^2\delta\int_{t-\delta}^t\xi^2.
-$$
-Following similar estimates as before, multiply 
-by $\yourdelta X$ and use Young's inequality as
-\begin{plain}$$\eqalign{
-    \mu(\yourdelta X - \yourdelta\bar{X})\yourdelta X
-		&\le
-    	{4\delta\mu (\sigma + \mu)^2\over \alpha}
-		\int_{t-2\delta}^t 
-		\big\{|\yourdelta X|^2 + |\yourdelta Y|^2\big\}\cr
-		&\qquad
-		+{4\mu^3\delta\over \alpha}\int_{t-\delta}^t\xi^2
-+{\alpha\mu\over 4}|\yourdelta X|^2
-}$$\end{plain}%
-and
-\begin{plain}$$\eqalign{
-\mu\xi \yourdelta X
-&\le 
- {\mu\xi^2 \over
-    \alpha}+
-{\alpha\mu \over 4} |\yourdelta X|^2 .
-}$$\end{plain}
-to obtain
-$$
-    \dot{V} + \alpha V
-    \le {8\delta\mu(\sigma + \mu)^2 \over \alpha}
-	\displaystyle\int_{t-2\delta}^t(\yourdelta X^2 +
-    \yourdelta Y^2) 
-	+{8\mu^3\delta\over\alpha} \int_{t-\delta}^t \xi^2
-	+{2\mu\xi^2 \over \alpha}.
-$$
-Since ${\bf E}[\xi^2]=\varepsilon^2/\delta$ for any time $t$, 
-then setting
-$\cV(\tau)={\bf E}[V(\tau/\alpha)]$ yields
-$$
-{d{\cV}(\tau)\over d\tau} + \cV(\tau) \leq 
-	{8\delta\mu(\sigma + \mu)^2\over \alpha^3}
-		\int_{t-2\alpha\delta}^t \cV(s)\,ds
-+\Big({8\mu^3\over\alpha^2}+{2\mu \over \alpha^2\delta}\Big)\varepsilon^2.
-$$
-We apply Lemma~\ref{intGronwallerror} 
-taking 
-$$A=
-	{8\delta\mu(\sigma + \mu)^2\over \alpha^3},\qquad
-B=
-\Big({8\mu^3\over\alpha^2}+{2\mu \over \alpha^2\delta}\Big)\varepsilon^2
-\qquad\hbox{and}\qquad h=2\alpha\delta.$$
-The result follows.
-\end{proof}
-
-\section{Unknown Noisy Time-averaged Coupling}\label{UNTACsec}
-
-In this section we examine the case when there is noise in
-the measurements and the length of the time averaging window 
-is unknown.  
-Our main result is a version of Proposition~\ref{UKNLTAprop}
-that also allows noise in the observations.
-As before let $\hat\delta$ be the length of the unknown averaging
-window in the observations of the free running solution and
-$\delta$ be an approximation of $\hat\delta$ that will be used 
-in the feedback control of the driven system.
-In this case the equation governing the evolution $x$ in the driven system
-becomes
-$$
-    \dot{x} = -\sigma(y-x)+\mu
-        \Big(
-        {1\over\hat\delta}\int_{t-\hat\delta}^t X(s)ds
-        -{1\over\delta}\int_{t-\delta}^t x(s)ds
-    \Big) + \mu\xi
-$$
-where $\xi$ is as in Section~\ref{NTACsec}.
-Since there is now noise in the observations, exact synchronization does 
-not occur when $\delta=\hat\delta$.  Thus, our theoretical bounds
-on $\|U-u\|^2$ take the form given by equation~(\ref{noisydeltadelta}) consisting
-of two terms, one which vanishes as $\delta\to\hat\delta$ and
-the other which vanishes as $\varepsilon\to 0$.
-In particular, we obtain
-
-\begin{proposition}\label{UKNTAprop}
-Suppose $\delta\ne\hat\delta$ and $\varepsilon>0$.
-Given $\alpha\in(0,2)$,
-let 
-$$\mu \ge JK/(2-\alpha)^2-\sigma
-\words{where}
-		J={\sigma(1+\sqrt 2)}
-        \Big({\hat\delta\over 2} +\delta\Big)+1.
-$$ 
-and 
-$$  \delta<
-    \sqrt{{1-e^{-1}\over 2}\cdot {\alpha\over 32\mu(\sigma+\mu)^2}}.$$
-Then $$\limsup_{t\to\infty}{\bf E}\big[\|U-u\|^2 \big]
-< {5e(2-\alpha)\mu^2\over \alpha}\cdot
-{(\hat\delta-\delta)^2\over\hat{\delta}^2}
-	+
-    e\Big({16\mu^3\over\alpha^2} +{2\mu\over\alpha^2\hat\delta}\Big)\varepsilon^2.
-$$
-\end{proposition}
-
-\begin{proof}
-Modifying the proof of Lemma~\ref{tadiffithat}
-we add the term for measurement error, which yields
-\begin{align*}
-	|\Delta X-\Delta\bar X|^2
-		&\le
-		4\delta(\sigma+\mu)^2
-		\int_{t-2\delta}^t \big\{|\Delta X|^2+|\Delta Y|^2\big\}\\
-		&+16 \mu^2\delta^2 K \Big({\delta-\hat\delta\over\hat\delta}\Big)^2
-		+8\mu^2\delta\int_{t-\delta}^t\xi^2.
-\end{align*}
-Now, modifying the proof of Proposition~\ref{UKNLTAprop} as was done
-for the proof of Proposition~\ref{NTAprop} to add the term which
-represents measurement error yields 
-\begin{align*}
-    {d\cV(\tau)\over d\tau}
-+ \cV(\tau)
-    &\leq
-        {8\delta\mu (\sigma + \mu)^2\over \alpha^3}
-        \int_{\tau-2\alpha\delta}^\tau \cV(s)\,ds\\
-		&+16 \mu^2\delta^2 K \Big({\delta-\hat\delta\over\hat\delta}\Big)^2
-			+{2\mu\over\alpha\eta} 
-            +{16\mu^3 \over \alpha^2}
-	+ {2\mu\varepsilon^2\over \alpha^2\delta}.
-\end{align*}
-Applying Lemma~\ref{intGronwallerror} 
-finishes the proof.
-\end{proof}
-
-\section{Numeric Results for Noisy Coupling}\label{NoisyComp}
-
-The first set computations in this section treat the case 
-where no time averaging is present in the observational measurements.
-Under this hypothesis Proposition~\ref{NIprop} 
-shows that the expected value of the difference between 
-the approximating solution and the exact solution
-is bounded by a factor of the variance of the noise.
-A similar bound was obtained 
-%by Law, Shukla and Stuart 
-as Theorem 4.1 
-in \cite{Stuart14} which, using the notation here, may be written as
-\begin{equation}\label{stubound}
-	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] \le 
-	{\mu^2\varepsilon^2\over 2-K/(2\mu)}
-\qquad\hbox{for}\qquad \mu>K/4.
-\end{equation}
-Optimizing the bound in the bound (\ref{stubound}) with respect to $\mu$ and 
-using the value of $K$ given by Theorem~\ref{Ktheorem}
-we obtain that 
-$$
-	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] \le 
-	{27K^2\varepsilon^2\over 128}\le (5.005\times 10^5)\varepsilon^2.
-$$
-Alternatively, 
-optimizing the bound in Proposition~\ref{NIprop} yields
-$$
-	\limsup_{t\to\infty} {\bf E}\big[\|U-u\|^2\big] \le 
-	(4.838\times 10^5) {\varepsilon^2}
-$$
-which is about 3 percent smaller.  
-Moreover, since
-$$
-{\mu^2\varepsilon^2\over 
-		\sigma+\mu+1-\sqrt{(\sigma+\mu-1)^2+K}}
-<{\mu^2\varepsilon^2\over 2-K/(2\mu)}
-$$
-provided $\mu>K/4$, the bound given in the bound (\ref{stubound}) is
-strict.  Therefore, there exists $T>0$ such that
-by Chebyshev's inequality 
-$$
-	{\bf P}\Big\{\,\omega\in\Omega : \|U-u\|^2\le 
-{10\mu^2\varepsilon^2\over 2-K/(2\mu)}
-\,\Big\}
-		\ge 0.9.
-$$
-Computations in \cite{Stuart14} demonstrate
-numerical bounds on $\|U-u\|$ which are proportional to 
-$\varepsilon$ and therefore consistent with
-the theoretical bounds described above.
-In the present thesis we fix the noise level at 
-$\varepsilon=0.01$ and focus on the effects of the 
-time averaging.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[b]{0.9\textwidth}
-    \caption{\label{e001paths}%
-	Results when coupling noisy instantaneous-in-time measurements
-	with $\mu=30$ and $\varepsilon=0.01$. The expected value was 
-	computed using 500 independent realizations of Brownian motion
-	and $L(t)$ is a computed bound on $90$ percent of the paths at 
-	each point in time.
-	The gray region represents the 500 pathwise solutions, one of which
-    has been plotted in a darker shade for illustration.}
-	\medskip
-    \end{minipage}}
-    \centerline{\includegraphics[height=0.5\textwidth]{e001paths.eps}}
-\end{figure}
-
-For a frame of reference, first consider 500 independent
-realizations of Brownian motion corresponding to 
-$\omega_i\in\Omega$ such that $i=1,2,\ldots,500$ and 
-compute the corresponding pathwise solutions $u_i$ using 
-equation~(\ref{noerra}) with the coupling 
-term ${\cal R}=\widetilde R$.
-The exact algorithm used to compute $u$ shall 
-be described later in Section~\ref{numerics}.
-Approximate the expected value of $\|U-u\|^2$ by
-$$
-	{\bf E}\big[\|U-u\|^2\big]\approx
-		{1\over 500} \sum_{i=1}^{500} \|U-u_i\|^2
-$$
-and let $L(t)$ be the value such that
-$$
-	{\rm card}\big\{\, i\in \{1,2,\ldots,500\} 
-		: \|U-u_i\|^2\le L(t)\,\big\} = 450.
-$$
-Thus, $L(t)$ bounds $90$ percent of the
-paths at each point in time.
-In particular, assuming $500$ samples is statistically large enough, 
-we have
-$$
-	{\bf P}\big\{\,\omega\in\Omega : \|U-u\|^2\le L(t)
-		\,\big\} \approx 0.9.
-$$
-Figure~\ref{e001paths} describes
-the results of this first computation.  Note that the
-expected value of 
-$\|U-u\|^2$ oscillates around $0.01$ and
-that $L(t)$ is about 5 times greater.
-Thus, $L(t)$ is about 2 times smaller than the bound
-given by Chebyshev's inequality (\ref{cheby}).
-Moreover, at each point in time a small percentage 
-of trajectories are significantly more accurate than
-expected and a few satisfy $\|U-u_i\|^2\le\varepsilon^2$.
-
-The computation described in Figure~\ref{e001paths} may
-be directly compared to Figure 5 in \cite{Stuart14}.
-Similar values of $\mu$ and $\varepsilon$ were employed
-in both computations and result in similar looking
-pathwise solutions.  The difference is that our
-expected values have been computed by averaging
-over the pathwise solutions $u_i$ which result from 
-independent Brownian motions and approximate
-the time-dependent expected values which appear in 
-the analysis,
-whereas~\cite{Stuart14} computes expected values that 
-do not change over time and appear to have been computed 
-by taking a long-time average over a single pathwise solution.
-We now consider how the presence of time averaging in the
-observational measurements affects the degree to which 
-$u$ synchronizes with~$U$.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[b]{0.9\textwidth}
-    \caption{\label{e001meas}%
-	Time-averaged noisy measurements 
-	for different values of $\delta$ corresponding to a 
-	representative Brownian path
-    with $\varepsilon=0.01$.}
-	\medskip
-    \end{minipage}}
-    \centerline{\includegraphics[height=0.5\textwidth]{e001mtalk.eps}}
-\end{figure}
-
-Figure~\ref{e001meas} depicts the time evolution of a typical 
-set of noisy observational measurements with and without time 
-averaging.
-Note that when $\hat\delta=0$ there is no time
-averaging and resulting observations show
-oscillation of the trajectory,
-As we are dealing with a chaotic system, we can expect that these oscillations
-will perturb the system enough so that synchronization is only possible within
-a tolerance of the measure of the noise.
-When $\hat\delta>0$
-the noise has been smoothed out at the expense of a phase
-shift that delays the measurements in time.  We now perform
-a number of calculations of $u$ using measurements of
-the kind depicted in Figure~\ref{e001meas}.
-
-Figure~\ref{e001exp} depicts the evolution of the expected
-value of $\|U-u\|^2$ over time for $\mu=30$,
-$\varepsilon=0.01$ and $\delta\in \{ 0, 0.25, 0.375 \}$.
-As in the noise-free case, the difference between $u$ and $U$ 
-remains large when $\delta=0.375$.
-However, the difference between $\delta=0.25$ and $\delta=0$
-appears greater than in the noise-free case.
-Intuitively, the presence of moving time averages seems to 
-result in decreased efficiency of the feedback control 
-that nudges the driven solution towards the free running solution.
-Without noise, only enough nudging to overcome the tendency for 
-nearby trajectories of the Lorenz equation to diverge is needed.
-As the nudging must also overcome the noise in the present case,
-which in turn may account for the expected error levels being 
-slightly greater when $\delta=0.25$.
-Further support for this intuition may also be inferred from 
-the already mentioned slower rate of convergence in the absence of noise 
-$\delta=0.25$ compared to $\delta=0$.
-
-\begin{figure}[ht]
-    \centerline{\begin{minipage}[b]{0.9\textwidth}
-    \caption{\label{e001exp}%
-	Results when coupling time-averaged 
-	noisy measurements with an
-	averaging window of size $\delta$ and
-a noise level $\varepsilon=0.01$.
-	The expected values were computed using 500 independent
-	realizations of Brownian motion.}
-    \end{minipage}}
-	\medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{e001exp.eps}}
-\end{figure}
-
-\begin{figure}[ht]\label{mixassim}\label{mix3ae001}
-    \centerline{\begin{minipage}[b]{0.9\textwidth}
-    \caption{\label{mix3a}%
-    Results when coupling time-averaged noisy measurements with
-	$\varepsilon=0.01$ and
-    window size $\hat\delta=0.25$ using a feedback term with
-    averaging window size $\delta\ne\hat\delta$.  Note that
-    $\mu=30$ and $\Delta\delta=\delta-\hat\delta$.
-    }
-    \end{minipage}}
-    \medskip
-    \centerline{\includegraphics[height=0.5\textwidth]{mix3ae001.eps}}
-    \centerline{\includegraphics[height=0.5\textwidth]{mix3be001.eps}}
-\end{figure}
-
-Figure~\ref{e001exp} depicts the evolution over time of
-the expected value of $\|U-u\|^2$ for $\mu=30$,
-$\varepsilon=0.01$ and $\delta\in \{ 0, 0.25, 0.375 \}$ with
-respect to
-500 independent realizations of noisy measurements of the kind
-depicted in Figure~\ref{e001meas}.
-As in the noiseless case, the difference between $u$ and $U$
-remains large when $\delta=0.375$.
-Similarly, for $\delta=0.25$ and $\delta=0$ the error decreases
-over time; however, unlike the noiseless case
-the asymptotic error level for $\delta=0.25$ is
-noticeably larger than for $\delta=0$.  In particular,
-\vfill\eject
-\begin{plain}$$
-\max\big\{\,{\bf E}\big[\|U-u\|\big]:t\in[50,100]\,\big\}\approx
-\cases{
-    0.0089 & for $\delta=0$\cr
-    0.49 & for $\delta=0.25$.
-}
-$$\end{plain}%
-
-Intuitively, the presence of moving time averages seems to
-result in a decreased efficiency of the feedback control
-that nudges the driven solution towards the free running solution.
-Without noise, this decrease in efficiency doesn't matter
-because the difference between the free running and driven
-solutions tends to zero over time anyway, only perhaps
-with a slightly decreased rate of convergence.
-In the presence of noise, however, the nudging must also
-overcome the noise.
-This leads to a higher error level in the difference
-between $U$ and $u$ over time.
-
-The last set of computations treats the case in
-Proposition~\ref{UKNTAprop} when the length of
-the averaging window used for the observations is unknown.
-Figure~\ref{mix3ae001} depicts the evolution
-of the expected value of $\|U-u\|^2$ when
-$\hat\delta=0.25$ and $\delta$ is smaller but near $\hat\delta$.
-The error level decreases as
-$\delta$ gets closer to $\hat\delta$, but unlike the noiseless
-case, there is very little difference between
-$\Delta\delta=0$ and $\Delta\delta=-2^{-11}$.
-Bounds on the expected error may be approximated
-numerically as
-$$
-    \widetilde E(\Delta\delta)
-    =\max\big\{\, {\bf E}\big[\|U-u\|^2\big] :
-        t\in[50,100]\,\big\}.
-$$
-A summary of our computations are presented in
-Table~\ref{limsupe001}.
-These numeric results show, as do our theoretical bounds,
-that $\delta$ can be tuned to match $\hat\delta$ only up to
-the point where the noise term dominates.
-Specifically,
-when $\hat\delta=0.25$ and $\epsilon=0.01$
-%our computations suggest
-it is possible
-to tune $\delta$ so that $|\delta-\hat\delta|< 2^{-8}$.
-
-As seen in Figure~\ref{e001meas} typical values of $X$
-range from $-10$ to $10$.  Moreover, the free running
-solution used in our experiments satisfies
-$$
-    \Big({1\over 100}\int_0^{100} X(s)^2ds\Big)^{1/2}
-        \approx 7.92731.
-$$
-We finish by noting that $\varepsilon=0.01$ is $1.3$
-percent the root-mean-squared value of $X$ and that
-$2^{-8}$ is $1.6$ percent the value of $\hat\delta$.
-The exact relationship between the value of $\varepsilon$
-and the degree to which $\delta$ can and needs to be tuned
-would be an interesting direction for future study.
-
-\begin{table}[ht]
-    \centerline{\begin{minipage}[b]{0.9\textwidth}
-    \caption{\label{limsupe001}%
-    Values of
-    $\widetilde E(\Delta\delta)=
-    \max \big\{\, {\bf E}\big[\|U-u\|^2\big] : t\in [50,100]\,\big\}$
-    as a function of $\Delta\delta=\delta-\hat\delta$.
-    Here $\hat\delta$ represents
-    the unknown size of the averaging present in the observational
-    measurements and
-    $\delta$ an approximation of $\hat\delta$ used in the feedback
-    control.}
-    \end{minipage}}
-    \bigskip
-    \centering
-    \begin{tabular}{  r | r }
-    \hline\hline
-\vphantom{\raise8pt\hbox{H}}%
-%   $\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
-    $\Delta\delta$ & $\widetilde E(\Delta\delta)$ \\ [0.5ex]
-    \hline
-\vphantom{\raise8pt\hbox{H}}%
-$-2^{-2}$&$1.60729\times 10^{6}$ \\
-$-2^{-5}$&$38419.5$ \\
-$-2^{-8}$&$44.133$ \\
-$-2^{-11}$&$0.693591$ \\
-$0$&$0.491966$ \\
-[1ex]
-\hline
-\end{tabular}\qquad\qquad
-    \begin{tabular}{  r | r }
-    \hline\hline
-\vphantom{\raise8pt\hbox{H}}%
-%   $\Delta\delta$ & $\limsup \|U-u\|^2$ \\ [0.5ex]
-    $\Delta\delta$ & $\widetilde E(\Delta\delta)$ \\ [0.5ex]
-    \hline
-\vphantom{\raise8pt\hbox{H}}%
-$2^{-2}$&$6.09399\times 10^{6}$ \\
-$2^{-5}$&$62104.1$ \\
-$2^{-8}$&$38.5955$ \\
-$2^{-11}$&$0.56483$ \\
-$0$&$0.491966$ \\
-[1ex]
-\hline
-\end{tabular}
-\end{table}
-
-\chapter{Numerical Methods}\label{numerics}
-
-This section described the numerical methods used to obtain the 
-results in Section~\ref{NoiselessComp} and Section~\ref{NoisyComp}.
-We compute both the free running solution and the driven solution
-using Euler's explicit method
-\begin{plain}$$\eqalign{
-	U^{n+1}&=U^{n}+h{\cal F}(U^n)\cr
-	u^{n+1}&=u^{n}+h{\cal F}(u^n)+
-		h\mu\big(R_{\hat\delta}(U^n)-R_\delta(u^n)\big)
-		+h\mu\hat\xi^n
-.\cr
-}$$\end{plain}%
-in double-precision floating-point arithmetic
-with step size $h=1/2048$. 
-Here $\hat\delta=m_0h$ for some $m_0\in{\bf N}$
-but $\delta$ may be any positive floating-point number.
-Upon writing $U^n=(X_n,Y_n,Z_n)$ and $u^n=(x_n,y_n,z_n)$, it 
-follows that $R_\delta={\cal L}\circ{\cal O}_{\delta}$ where
-$$
-	{\cal O}_{\hat\delta}(U^n)={1\over m_0}\sum_{k=0}^{m_0-1} X_{n-k}
-$$
-and 
-by interpolation 
-setting $m_3=\lfloor\delta/h\rfloor$ that
-$$
-	{\cal O}_{\delta}(u^n)=
-	{h\over\delta}\Big\{
-		\Big({\delta\over h}-m_3\Big)
-		x_{n-m_3}+
-			\sum_{k=0}^{m_3-1} x_{n-k}
-		\Big\}.
-$$
-
-%\chapter{Standard Brownian Motion}
-
-The noise term $\hat\xi^n=\hat\xi(nh)$ is given as in Section~\ref{UNTACsec}
-by
-$$
-	\hat\xi(t)={\varepsilon\over\hat\delta}\big(W(t)-W(t-\hat\delta)\big)
-$$
-where $W(t)$ is a standard Brownian motion,
-one of the simplest of the continuous-time stochastic 
-processes.
-Numerically we use the construction of Brownian
-motion as developed by L\'evy and Ciesielski.
-By L\'evy and Ciesielski, there is a probability space $\Omega$ and a sequence
-of independently distributed standard normal random variables $(G_n)_{n\ge 0}$
-such that for $\omega\in\Omega$ and $t\in[0,1]$
-$$
-W(\omega, t)= \lim_{n\to\infty} W_n(\omega,t)
-\wwords{where}
-	W_n(\omega,t)=\displaystyle\sum_{k=0}^n G_k(\omega)S_k(t)
-$$
-is a Brownian motion, where $S_n(t)$ is from the family of Schauder functions.
-The Schauder functions $S_{2^j+k}$ are tent-functions with support $[k2^{-j},
-(k+1)2^{-j}]$ and a maximal value $\textstyle{1\over 2}2^{-j/2}$ at the tip of the
-tent.
-Using an application of Minkowski's inequality, monotone convergence theorem,
-and by the completeness of the space of continuous functions, there is a
-subsequence of $(W_{2^j}(t, \omega))_{j\ge 1}$ which converges uniformly in
-$t\in[0,1]$ for a subset $\Omega_0\subset \Omega$.
-Defining $W(t, \omega)$ as a limiting function, we see that it
-indeed inherits the continuity of $W_{2^j}(t, \omega)$. We conclude that there
-exists a restriction of $W(t, \omega)$ that is a Brownian motion defined on
-$\Omega$.
-
-The algorithm for the construction of Brownian motion is an adaptation based on
-L\'evy's original interpolation argument.
-Let $t_0<t<t_1$ and let $W(t)$ be a Brownian motion. Then,
-$$ 
-G' = W(t) - W(t_0) \wwords{and} G'' = W(t_1) - W(t)
-$$ 
-are Gaussian random variables with mean zero and variances $t-t_0$ and $t_1-t$
-respectively. Let $\Gamma$ be a further $N(0,1)$ random variable which is
-independent of $W(t_0)$ and $W(t_1) - W(t_0)$. 
-If $t$ is the midpoint of $[t_0,
-t_1]$, then $\Gamma$ is a random variable with the same distribution as
-$W(t)$ and is a one-dimensional Brownian motion. 
-\begin{theorem}\label{levy}(Levy 1940)
-    The series 
-    $$
-    W(t, \omega) = \displaystyle\sum_{n=0}^\infty \big(W_{2^{n+1}}(t,\omega) -
-    W_{2^{n}}(t, \omega)\big) + W_1(t,\omega), \qquad t\in[0,1]
-    $$
-    converges a.s. uniformly. In particular, $\big(W(t)\big)_{t\in[0,1]}$ is a
-    Brownian motion.
-\end{theorem}
-$W(t)$ is almost surely continuous and can be constructed
-iteratively using independent increments.
-This algorithm is based on L\'evy's construction of Brownian motion
-by means of a limit as $n\to\infty$ of piecewise linear functions 
-taken on subsequently finer and finer refinements of a dyadic grid
-of size $1/2^n$.
-Numerically, continuous time processes are sampled 
-on a finite grid as we can only generate finitely many values in
-finite time.
-Assuming we have already constructed $W(k2^{-j})$ for some fixed $j\ge 1$ and all $k \in [0,2^j]$, 
-then
-$$
-    W(l2^{-j-1}) = \begin{cases}
-                        W(k2^{-j}) \qquad &l = 2k\\
-                        \textstyle{1\over 2}(W(k2^{-j}) +
-                        W((k+1)2^{-j})) + \Gamma_{2^j +k} \qquad &l = 2k+1\\
-                   \end{cases}
-$$
-so $W_{2^j}(t)$ is therefore a piecewise linear interpolation of the Brownian path
-$W(t)$.
-We take the size of the time steps used in our
-numerical simulations equal to $h=1/2^n$ so that no further 
-processing is needed to compute $W(t)$ at the values needed
-for our numerical simulations.
-This results in a numerical approximation of Brownian motion,
-where any refinement of the discretization yields a refinement of the
-same simulated path.  The points on the discrete time grid are simulated
-linearly, which is possible as Brownian motion has continuous paths.
-
-The seed of the random generator provides a unique random
-variable $\omega$ in the Gaussian space $\Omega$ used to create a unique Brownian motion.
-The refinement of an already simulated path
-is an interpolation in $[t_0, t_1]$
-taken as dyadic points $t= k2^{-j}$ the expansion of $W(t, \omega)$ is finite and
-we are able to calculate the value of
-$W(t, \omega)$, by successive approximations $t \to W(t, \omega)$.
-Set $W(0,\omega)$ to zero and let $W(1,\omega)$ be an $N(0,1)$ 
-distributed random variable.
-The initialization of $\omega \in \Omega$ as an $N(0,1)$ distributed random
-variable is implemented using 1024-bit Marsaglia pseudo-random 
-number generators \cite{Marsaglia2003}.
-The random numbers generator may take a fixed seed as an input, and as such,
-the same Brownian 
-path can be sampled at any resolution on the dyadic grid. In this way we were able
-to change the time-scale of the simulation without changing the results from
-previous experiments.
-We initialize the L\'evy-Ciesielski algorithm with an initial refinement, then refine
-as needed to support our averaging scheme. The algorithm as described in
-the chapter on simulation by Bj\"orn B\"ottcher in
-Schilling and Partzsch \cite{Schilling2012},
-can be described as follows,
-
-\begin{algorithm}[ht]
- \textbf{Algorithm:} (L\'evy-Ciesielski)\\
-Let $J\ge1$ we the order of refinement.\\
-Initialize $w_0 := 0$\\
-Generate $w_1 \sim N(0,1)$\\
- \For{$j=0$ to $J-1$}{
-    \For{$l= 0$ to $2^j - 1$}{
-    1. Generate $y \sim N(0,1)$\\
-    2. Set $w_{(2l+1)/2^{j+1}} = \textstyle{1\over 2}(w_{l/2^j} + w_{(l+1)/2^j}) 
-    + 2^{-(\textstyle{j\over 2} + 1)}y$\\
-    }
- }
-\textbf{Then} $(w_0, w_{1/2^J}, w_{2/2^J},\cdots , w_1) \sim (W_0, W_{1/2^J}, W_{2/2^J},\cdots , W_1)$
-\end{algorithm}
-
-Note that taking $\hat\delta=h$ reduces $\hat\xi^n$
-to exactly the term used in the Euler-Maruyama method
-for the simulation of the stochastic differential
-equation given by equation~(\ref{dxnoise}).  
-Thus, taking $\hat\delta=h$ in our computations corresponds 
-to noisy in\-stan\-tan\-eous-in-time coupling in our analysis.
-Although the sample paths of our Brownian motions 
-do not depend on $h$, 
-the sensitive dependence of the 
-Lorenz system on initial conditions and the 
-resulting deterministic chaos exhibited implies that the 
-free running solution $U$ strongly depends on $h$.
-Therefore, we have fixed $h=1/2048$ to ensure that the same 
-reference solution $U$ is considered in all our simulations.
-
-Theoretically, if $\delta=\hat\delta$, $u_0=U_0$ and $\varepsilon=0$, 
-then $u(t)=U(t)$ for all $t\ge 0$ and any value of $\mu$.  
-This property is preserved at the discrete level in our numerics.
-In particular, when $\delta=\hat\delta$ and $\varepsilon=0$
-exact synchronization of $u^n$ with $U^n$ is possible and was 
-observed in certain simulations.
-Exact bit-for-bit synchronization of $u^n$ with $U^n$ seems to
-result from a lucky coincidence in the rounding of the floating 
-point arithmetic, whereas, in general synchronization is
-only good up to the least significant bits.
-Note when $\delta\ne\hat\delta$ or $\varepsilon>0$ that
-exact synchronization is neither theoretically possible nor 
-was numerically observed.
-
-\chapter{Conclusions}
-
-This thesis considers coupling two systems of equations using
-noisy partial observations of the phase space that have been
-blurred in time by means of a moving time average.
-The inclusion of blur using time averages in the observational 
-measurements is both realistic from a physical point of view
-as well as tractable in our mathematical and numerical frameworks.
-The major contributions of our study are four new theorems 
-that cover time averages and numeric simulations that show
-the coupling works even better than what is guaranteed by
-the analysis.  Namely, the original work in this thesis
-centers on the statements and proofs of Propositions \ref{NLTAprop},
-\ref{UKNLTAprop}, \ref{NTAprop} and \ref{UKNTAprop} and the
-corresponding numeric simulations.
-
-In the context the model system, the Lorenz equations, we have shown that the 
-data-assimilation method introduced in \cite{Olson14} is well-posed
-when the observational data is contaminated by a moving average
-with sufficiently short averaging window. In the noiseless case,
-analysis and numeric simulation shows that synchronization
-of the driven solution to the free-running solution occurs when
-the time averaging window is known and small enough.
-Moreover, when the time averaging window is unknown, the bound on 
-the error is proportional to $(\Delta\delta)^2$ where $\Delta\delta$ 
-is the difference between the size of the actual averaging window 
-and the guess for the size of the window used in the feedback
-control.
-
-In the presence of noise, time averaging smooths out the noise
-in the observational measurements at the expense of a phase
-shift that delays the measurements in time.
-Although averaging gives no improvement in the analytic and numerical
-bounds on $\|U-u\|$, there is also no significant deterioration 
-in those bounds provided the averaging window is small enough.
-In fact, this is the punch line of this thesis:  {\it short time
-averages can be compensated for in the feedback term and as a
-result have minimal effect on the quality of the synchronization 
-between the free-running solution and the driven solution.}
-Note, however, that time averaging appear to slightly weaken the
-coupling between the driven and the free-running solution
-which, in turn, yields a slight increase in the expected error levels.
-
-\chapter{Future Work}
-
-\section{Improved Bound on Fractal Dimension of Attractor}
-	\label{fractalbound}
-Using the improved ellipsoid described in Appendix~A, we conjecture that
-an improved analytic bound on the fractal dimension of the global
-attractor ${\cal A}$ of the Lorenz equations may be found using the
-techniques in Doering and Gibbon \cite{Doering95a}.
-
-\section{Numerically Determined Upper Bound}
-
-In the case where the size of the averaging window is unknown, we conjecture
-that an improvement to the analytical bound given in
-
-Noting that in Figure~\ref{mixassim} the difference between ${\bf E}[\| U - u\|^2]$ and $L(t)$ is less than a factor of $2$, it may be possible to compute a bound numerically that will improve the bound obtained analytically using the Chebyshev inequality.
-By using a non-linear least squares we postulate that an upper bound on $\| U - u\|$ can be determined in the case where the averaging window of $U$ is unknown.
-
-\section{Adapting $\mu$ by Computing Local Lyapunov Exponents}
-
-We postulate that an improvement on convergence can be achieved through the use
-of an adaptive filter that tunes the $\mu$ parameter as the system evolves by
-testing the rate of convergence at time $t$.
-
-We conjecture that an adaptive filter may be constructed by computing local
-Lyapunov numbers. By determining the rate of divergence of the trajectories, we can allow 
-for larger values of $\mu$ when the system is 'well-behaved', 
-In the noiseless case, we can achieve synchronization for unstable values of
-$\delta$ such as $\delta = 0.318$ as shown in Figure~\ref{avgdup}.
-In the noisy case, the noise in the observations can be made
-to be smooth enough that convergence below the level of observational noise can be achieved.
-
-\section{Reconstructing Attractor Dynamics}
-
-Takens' \cite{Takens81} proved that the time-delayed 
-versions 
-$$
-[y(t),y(t-\tau),y(t-2\tau),\cdots,y(t-2n\tau)]
-$$ 
-of one generic signal would suffice 
-to embed the $n$-dimensional manifold. 
-This may be compared to the topological result
-by Whitney \cite{Whitney36} in which a single observation
-in $2n+1$ dimensions can be replaced by $2n+1$ observations
-of one dimension.  Namely, Taken's proved
-
-\begin{theorem} Let $M$ be a compact manifold of dimension $d$. 
-For pairs $(\phi, h)$,
-where $\phi : M \to M$ is a smooth (at least $C^2$) diffeomorphism and 
-$h : M \to R$ a smooth
-function, it is a generic property that the $(2d +1)$-fold observation map
-$H_k[\phi, h] : M \to \R^{2d+1}$
-defined by
-$$
-x \to (h(x), h(\phi(x)), \ldots, h(\phi^{2d} (x)))
-$$
-is an immersion (i.e. $H_k$ is one-to-one between $M$ and its image with both 
-$H_k$ and $H^{-1}_k$ differentiable).
-\end{theorem}
-The theorem can be applied to time series by taking $\phi$ to be the time $T$ map of
-the underlying
-(continuous time) dynamical system, i.e. $\phi_j (x_0) = x(jT)$, 
-where $x(t·)$ is the
-trajectory starting
-at $x_0$. 
-Since $H_k$ is a diffeomorphism 
-its inverse is differentiable) this reconstruction
-preserves the
-dimension of any invariant set and the Lyapunov exponents of the flow.
-\begin{figure}[ht]\label{reconst}
-\begin{center}
-\caption{Lorenz attractor reconstructed in $X$ with time delay $T = 1$.}
-\includegraphics[width=10cm]{lorenz_reconst.eps}
-\end{center}\end{figure}
-
-We can see from Figure~$\ref{reconst}$ that the reconstruction of the Lyapunov
-attractor results in similar, but not identical geometry in the phase space. 
-However, according to Takens' Theorem, the Lyapunov spectrum and the correlation
-dimension are preserved by the embedding. It is therefore reasonable to assume
-that a system constructed by averages where $\delta < \delta_c$ will also
-preserve these properties. In this case he phase space of $U$ will be exactly
-the sets of observational data. It will be difficult to compute $H^{-1}$
-directly or exactly. Therefore we may be able to compute $H^{-1}$ by
-approximating its determining form as defined in \cite{Jolly15}.
-
-\section{Unknown Dynamics of Free Running Solution}
-\label{whatissigma}
-It is realistic to suppose that only an approximation $\widetilde{\cal F}$
-is known of the exact dynamics ${\cal F}$ of the free running solution.
-A simple example for the Lorenz systems is when
-the exact parameters values $\hat\sigma$, $\hat r$ and $\hat b$ are 
-unknown.
-In this case we write
-\begin{align*}
-	{\cal F}(U)=
-    \begin{bmatrix}\hat\sigma(Y-X)\\
-    -\hat\sigma X-Y-XZ\\ -\hat bZ+XY-\hat b(\hat r+\hat\sigma)\end{bmatrix},
-\quad
-	\widetilde {\cal F}(U)=
-    \begin{bmatrix}\sigma(Y-X)\\
-    -\sigma X-Y-XZ\\ -bZ+XY-b(r+\sigma)\end{bmatrix}.
-\end{align*}
-where $\sigma$, $r$ and $b$ are guesses for the
-true values of the parameters.  Just as we obtained bounds on
-$\|U-u\|$ when $\Delta\delta=\delta-\hat\delta\ne 0$ that vanished when 
-$\Delta\delta\to 0$, we expect similar bounds in terms of
-$\Delta\sigma$, $\Delta r$ and $\Delta b$
-
-\section{Existence of $\delta_c$}
-
-Our calculations suggest that $\delta_c$, if it exists, must
-lie somewhere between $0.31$ and $0.33$.  The fact that $\|U-u\|^2$
-oscillates through $20$ decimal orders of magnitude by hitting
-the noise floor due to rounding error when $\delta=0.318$ implies
-that extended precision arithmetic is needed to further characterize
-$\delta_c$.  One could use the GMP Gnu multiprecision library
-to more accurately determine $\delta_c$.  Similar techniques were
-used by Hayden \cite{HaydenThesis} to more accurately characterize 
-the critical sampling interval for discrete in time observations.
-
-\section{Correcting Phase Shift when $\hat\delta\ne\delta$}
-
-In the case where $\hat\delta > \delta_c$, then taking $\delta =
-\hat\delta$ does not lead to synchronization. 
-However, taking $\delta < \delta_c$ may lead to usable
-bounds on $\|U-u\|$.
-We may improve these bounds by time-advancing the measurements by
-$$
-    \hat\delta - \delta \over 2
-$$
-so that the phase shift caused by averaging is the same in both 
-systems even though $\hat\delta \ne \delta$.
-
-\section{Statistical Test Whether $U-u$ is Gaussian}
-
-While $u$ is driven by a Gaussian process, the dynamics of the Lorenz
-equation is highly non-linear.  Figure~\ref{e001paths} indicates 
-that the expected
-value of $\|U-u\|^2$ is quite near the top of the gray region, however,
-this is not unexpected as it is the square of a vector in ${\bf R}^3$.
-The question is, therefore, at any fixed point in time to what extent 
-are probability distributions of $X-x$, $Y-y$ and $Z-z$ distributed
-as Gaussian.  Numerically, this could be tested by plotting a
-histogram of $X-x$, fitting it to a Gaussian, checking the goodness
-of fit and calculating the probability that it arose from a Gaussian
-distribution.
-
-\section{Nonlinear Least Squares Fit of $M$}
-\label{futurehatdelta}
-We consider performing a nonlinear fit
-%
-%$$
-%	\log E \approx \log M +\ 2\log (\delta-\hat\delta) - 
-%		\gamma \log (\delta_c-\hat\delta)
-%$$
-to obtain constants $M$, $\gamma$ and $\delta_c$ such that
-$$
-	E \approx  M (\delta-\hat\delta)^2 / (\delta_c-\hat\delta)^\gamma
-$$
-Here $\delta_c$ represents the largest value for which 
-$\delta=\hat\delta$ leads to convergence.  In particular, 
-for values of $\hat\delta$ too large, there is no good bound 
-on $E$ even when $\delta\approx\hat\delta$.
-Note that $M$ has the same units as $E$ multiplied by
-units of time to the power $\gamma-2$.  Therefore taking $\gamma=2$ 
-yields a constant $M$ which is invariant with respect to a change of 
-scales in time.
-
-\section{Tuning $\delta$ Using Only the Observations}
-
-Our results suggest it is possible to determine the size 
-$\hat\delta$ of the unknown averaging window by 
-varying $\delta$ is a way that minimizes the resulting error.
-In the context of data assimilation, the only 
-information actually available concerning $U$ are the time 
-averaged measurements of $X$.  Therefore, it is
-more relevant to check whether
-$$
-	{\cal E}=\|R_{\hat\delta}(U)-R_\delta(u)\|^2
-        =\bigg|{1\over\hat\delta}\int_{t-\hat\delta}^t X(s)ds
-        -{1\over\delta}\int_{t-\delta}^t x(s)ds\bigg|^2
-$$
-can be used to numerically determine $\delta$.
-
-\section{Extension of Results to Other Dissipative Systems}
-
-The techniques used in our analysis also apply to other model
-problems such as the two-dimensional Navier--Stokes equations and
-the surface quasi-geostrophic equations.
-In those cases, the resulting integro-differential inequality is 
-non-linear.
-Delayed time averages in the noiseless case for 
-is treated by Jolly, Martinez, Olson and Titi for the surface 
-quasi-geostrophic equations in \cite{Jolly16}.
-In the noisy case, the resulting non-linearity makes estimating 
-the expected values of $\|U-u\|^2$ difficult.
-It is possible that a slightly modified coupling algorithm which
-filters statistical outliers from the observational measurements 
-could be used to treat this case.
-
-\section{Same Bounds as Stochastic Case} 
-When $\delta$ tends to zero the differential equations with averages
-tend to the stochastic case covered by Proposition~\ref{NIprop}.
-However, the bounds obtained in Proposition~\ref{NTAprop} blow up
-as $\delta$ vanishes.  It is possible to obtain a version of 
-Proposition~\ref{NTAprop} such that the bounds remain bounded
-when $\delta$ vanishes and are consistent with those which
-cover the $\delta=0$ case of Proposition~\ref{NIprop}.  Namely,
-we write the noise term as
-$$
-	\mu\xi(t)\Delta X(t) =
-	\mu\xi(t)\big(\Delta X(t)-\Delta X(t-\delta)\big) +
-	\mu\xi(t)\Delta X(t-\delta)
-$$
-and then estimate as in Lemma~\ref{tadiffit} to obtain
-\begin{align*}
-	|\Delta X(t)-\Delta X(t-\delta)|^2
-		&\le \Big(\int_{t-\delta}^t |\Delta \dot X(s)|ds\Big)^2\\
-		&\le 4\delta(\sigma +\mu)^2\int_{t-2\delta}^t V
-			+ 4\mu^2\delta\int_{t-\delta}^t \xi^2.
-\end{align*}
-Since $\xi(t)$ is independent of $\Delta X(t-\delta)$ then
-$$
-	{\bf E}\big[\mu\xi(t)\Delta X(t-\delta)\big]
-	=\mu {\bf E}\big[\xi(t)]\cdot {\bf E}[\Delta X(t-\delta)\big]=0.
-$$
-This implies
-\begin{align*}
-	{\bf E}\big[\mu\xi(t)\Delta X(t)\big] 
-		&\le
-	{\bf E}\big[\delta\mu^2\xi^2\big]
-		+{1\over 4\delta}
-		\Big(
-4\delta(\sigma +\mu)^2\int_{t-2\delta}^t V
-            + 4\mu^2\delta\int_{t-\delta}^t 
-				{\bf E}\big[\xi^2 \big] \Big) \\
-		&= 
-(\sigma +\mu)^2\int_{t-2\delta}^t V
-+2\mu^2\varepsilon^2.
-\end{align*}
-To finish the proof requires a modified version of the
-integro-differential Gronwall inequality to handle the case
-when
-$$
-	{d{\cal V}(t)\over dt}
-		+{\cal V}(t)
-	\le (A_0+hA_1)\int_{t-h}^t {\cal V}(s)\,ds + B.
-$$
-We hypothesis that the result is likely to place greater restriction
-on the maximum size of $\delta$---likely of the order $\sqrt \mu$
-smaller.
-
-\chapter*{Appendix A}
-
-We now describe a spherical bound on the Lorenz trajectories that is
-better than existing bounds from Doering and Gibbon \cite{Doering95a}.
-Our bound is based on an additional tuning parameter $\eta$ 
-and is given by
-\begin{equation}\label{Mbound}
-    X^2 + Y^2 + (Z-\eta)^2 
-    {b^2(r + \sigma - \eta)^2 \over \delta(2b - \delta)}
-\end{equation}
-where
-$\delta = 2(b-1)-2 + \epsilon \eta$ and
-$$
-    \epsilon = {-\sigma + 1 + \sqrt{\sigma^2 - 2\sigma + 1 + \eta^2} \over
-    \eta}. 
-$$
-Now, differentiating with respect to $\eta$ gives 
-the optimal value of $\eta \approx 1.8882316669$.
-Substituting this value back into inequality (\ref{Mbound})
-we arrive at
-$$
-    X^2 + Y^2 + (Z-1.8882316669)^2 \le 1456.461665,
-$$
-which is about $5$ percent smaller than previous bounds.
-
-\chapter*{Appendix B}
-
-This section contains C-language source code used in this thesis. There
-are two files:  the first is a pseudo-random number generator 
-and the second is the main routine used to produce our simulations.
-
-\section{Pseudo-random Number Generator}
-
-The random number generator is based on the 
-public domain implementation by Sebastiano Vigna of the
-1024-bit Marsaglia Xorshift algorithm \cite{Marsaglia2003}.
-\bigskip
-
-\lstinputlisting{xonorm.c}
-
-The above source contains modifications to 
-include a routine that generates normally distributed random numbers
-that will be used to create the Brownian paths
-representing the noise terms in the observational measurements
-in this thesis.
-These changes begin on line 44 with the 
-routine{\tt\ xonorm }which returns
-normally distributed random numbers 
-obtained by a polar coordinate transformation.
-
-\section{Main Routine}
-
-The main routine consists of the ODE solver, averaging functions
-and implementation of the L\'evy-Ciesielski algorithm used to
-create our Brownian motions.
-This code was used to perform all our simulations.  
-Prior to compilation the following
-preprocessor definitions need to be made:
-\begin{itemize}
-\item {\rm BETA} --- The value of $\beta=8/3$ in the Lorenz system.
-\item {\rm SIGMA} --- The value of $\sigma=10$ from the Lorenz system.
-\item {\rm RHO} --- The value of $r=10$ from the Lorenz system.
-\item {\rm M0} --- The value $\hat\delta={\rm M0}/{\rm N}$ for observation blur.
-\item {\rm M3} --- The value $\delta={\rm M3}/{\rm N}$ for the feedback.
-\item {\rm N} --- The timestep $h=1/{\rm N}$ where ${\rm N}=2048$ 
-		for the ODE solver.
-\item {\rm EPSILON} --- The amplitude $\varepsilon$ of the noise term.
-\item {\rm MU} --- The relaxation parameter $\mu$ in the feedback term.
-\item {\rm M} --- The time of integration $T={\rm M}$.
-\item {\rm PMOD} --- Output data every ${\rm PMOD}$ time steps.
-\item {\rm L} --- Size ${\rm L}=5$ of the cache for the Brownian paths.
-\end{itemize}
-The exact code used for the simulations in this thesis follows:
-\bigskip
-
-\lstinputlisting{main.c}
-
-Note the averaging routine{\tt\ avg }takes values of 
-${\rm M0}$ and ${\rm M3}$ 
-that need not be integral and performs an interpolation in 
-line 40 to handle decimal part.
-The L\'evy-Ciesielsky algorithm called through
-the function{\tt\ getb }includes a least recently used
-cache as an optimization because the noise term
-$$
-	\xi^n={\varepsilon \over\delta}\big(
-		W(t_n)-W(t_n-\hat\delta)\big)
-$$
-repeatedly samples the Brownian motion at two different points
-in time separated by the distance $\hat\delta$.  
-This routine is seeded by the number given in line 159 by
-default.  If a parameter is supplied on the command line,
-this is used for the seed instead.  The
-program was run 500 times with different seeds on the
-command line to 500 output files which were then
-averaged together to compute the expected values
-${\bf E}[\|U-u\|^2]$.
-
-Lines 152--153 treat the case $\hat\delta=0$ as ${\rm M0}=1$
-and $\delta=0$ as ${\rm M3}=1$, which reduces to the
-Euler--Maruyama method from simulating stochastic differential 
-equations.
-Line 184 computes a numerical bound $K$ on the free running
-solution such that $X^2+Y^2+Z^2\le K$.
-Data was output every 64 timesteps.
-The condition in lines 199 and 201 turn on the coupling only
-after $t>\max\{\delta,\hat\delta\}$ as described in 
-(\ref{intdiff}).
-Line 201 assumes ${\rm M0}$ is an integer when 
-running simulations with noise.  This condition was satisfied
-in our simulations where the values of $\hat\delta$
-considered $\hat\delta=.25$ obtained when ${\rm M0}=512$
-and $\hat\delta=0$ which corresponds to ${\rm M0}=1$.
-
-\end{manuscript}
-
-\nocite{*}
-\bibliography{thesis}
-
-% Figures
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{paper_acm}
 

### 2019-10-02 input.c

@@ -1,34 +1,0 @@
-
-int main(int argc,char *argv[]){
-    int opt;
-    while((opt=getopt(argc,argv,"e:o:t:T:s")) != -1) {
-        switch (opt) {
-case 'e':
-			epsilon=atof(optarg);
-			break;
-case 'o':
-			data=optarg;
-			break;
-case 't':
-            t=atoi(optarg);
-            break;
-case 'T':
-            T=atoi(optarg);
-            break;
-case 's':
-			sflag=1;
-			break;
-default:
-            fprintf(stderr,
-"Usage: %s [options]\n"
-"Options:\n"
-"    -e x    Set noise level to x.\n"
-"    -o s    Set output directory to s.\n"
-"    -T n    Approximate supremum by taking t less than n.\n"
-"    -s      Skip the compile and the generation of data.\n"
-"    -t n    Approximate supremum by taking t greater than n.\n",
-                argv[0]);
-            exit(1);
-        }
-    }
-}

### 2019-10-02 main.c

@@ -1,209 +1,0 @@
-/*  
-    This program uses the original form of the Lorenz equations
-    as stated in 
-
-    Lorenz, Deterministic Nonperiodic Flow, Journal of the Atmospheric
-    Sciences, Volume 20, 1963.
-
-    X' = -sigma X + sigma Y
-    Y' = -XZ + rX - Y
-    Z' = XY - bZ
-
-    The change of variables zeta = Z - r - sigma yields
-
-    X' = -sigma X + sigma Y
-    Y' = -sigma X - Y - X zeta
-    zeta' = - b zeta + XY - b(r+sigma)
-
-    We know theoretically that if (X,Y,zeta) is on the attractor, then
-
-    X^2+Y^2+zeta^2 <= K = b^2(r+sigma)^2/4/(b-1) = 1540.27
-*/
-
-#include <stdio.h>
-#include <stdlib.h>
-#include <math.h>
-#include <float.h>
-#include "xonorm.h"
-
-#define BETA (8.0/3)
-#define SIGMA 10.0
-#define RHO 28.0
-
-#ifndef M0
-#define M0 512.0
-#endif
-#ifndef M3
-#define M3 512.0
-#endif
-#ifndef N
-#define N 2048
-#endif
-#ifndef EPSILON
-#define EPSILON 0.0
-#endif
-#ifndef MU
-#define MU 30
-#endif
-#ifndef M
-#define M 50
-#endif
-#ifndef PMOD
-#define PMOD (N/64)
-#endif
-
-double beta=BETA, sigma=SIGMA, rho=RHO, mu=MU, epsilon=EPSILON;
-double x[6]={ -5.5751, -3.24345, 26.9272, 0,0,0 }, f[6];
-double xmax[6] = { FLT_MIN, FLT_MIN, FLT_MIN, FLT_MIN, FLT_MIN, FLT_MIN };
-double xmin[6] = { FLT_MAX, FLT_MAX, FLT_MAX, FLT_MAX, FLT_MAX, FLT_MAX };
-double vmax = 0;
-double myeta = - SIGMA - RHO;
-double Umax = 0;
-double MM0=M0, MM3=M3;
-
-// Cache of Brownian motion paths
-#define L 5
-static struct {
-    int j,q;
-    double b[N+1];
-} p[L];
-static double e[M+1];
-static uint64_t s[M];
-
-// Return normal N(mu,sigma) distributed random variable
[…]

### 2019-10-02 xonorm.c

@@ -1,56 +1,0 @@
-#include "xonorm.h"
-#include <math.h>
-
-/*  Written in 2014 by Sebastiano Vigna (vigna@acm.org)
-
-To the extent possible under law, the author has dedicated all copyright
-and related and neighboring rights to this software to the public domain
-worldwide. This software is distributed without any warranty.
-
-Modified 2015 to produce normally distributed random numbers for use in
-coupling simulations with noisy observations.  */
-
-static uint64_t x=12455480610190296555ULL;
-static uint64_t s[16] = {
-    9899521803441930453ULL, 4037224574094532358ULL,
-    13192621976843192702ULL, 10923948763034344365ULL,
-    3888343346591572214ULL, 7485323648124204777ULL,
-    8981086447562432722ULL, 1561717205308781184ULL,
-    2780386954292984643ULL, 3863312353808779985ULL,
-    12109031751610640964ULL, 11534438648781303991ULL,
-    9340076221226405573ULL, 219462499049377941ULL,
-    16106326203448552520ULL, 7245732521397473901ULL };
-static int p,flag;
-
-uint64_t xorand64(){
-    x^=x>>12; x^=x<<25; x^=x>>27;
-    return x*2685821657736338717ULL;
-}
-
-uint64_t xorand1024(){
-    uint64_t s0=s[p];
-    uint64_t s1=s[p=(p+1)&15];
-    s1^=s1<<31; s1^=s1>>11; s0^=s0>>30;
-    return (s[p]=s0^s1)*1181783497276652981ULL;
-}
-
-void xoseed(uint64_t seed){
-    x=seed;
-    for(int i=0;i<64;i++) xorand64();
-    for(int i=0;i<16;i++) s[i]=xorand64();
-    p=flag=0;
-}
-
-double xonorm(){
-    static double x2;
-    if(flag) {
-        flag=0;
-        return x2;
-    }
-    flag=1;
-    double u1=(xorand1024()+1.0)/18446744073709551616.0;
-    double u2=(xorand1024()+1.0)/18446744073709551616.0;
-    double r=sqrt(-2*log(u1)), v=2*M_PI*u2;
-    x2=r*sin(v);
-    return r*cos(v);
-}
